### 2010-11-02 Multiresolution_framework/ltx/manuscript.tex
added multiresolution framework

%% bare_jrnl.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.

%    \documentclass[journal,a4paper]{IEEEtran}
%     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
%         \topmargin       -6.0mm
%          \oddsidemargin      0mm
%          \evensidemargin     0mm
%          \textheight     223.5mm
%         \textwidth      170.0mm

% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
\usepackage{amssymb}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
% \usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e 
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
% \usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.
 \ifCLASSOPTIONcompsoc
  \usepackage[tight,normalsize,sf,SF]{subfigure}
\else
  \usepackage[tight,footnotesize]{subfigure}
\fi

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
% This package may be useful when used in conjunction with IEEEtran.cls'
% captionsoff option. Some IEEE journals/societies require that submissions
% have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.3.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% For subfigure.sty:
% \let\MYorigsubfigure\subfigure
% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat/subfig command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation }
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Parham Aram*,
        Michael Dewar and Visakan Kadirkamanathan,~\IEEEmembership{Member,~IEEE}  % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
% \markboth{Journal of }%
% {Aram \MakeLowercase{\textit{et al.}}: Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.
 \ifCLASSOPTIONpeerreview
\else
\fi

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
The Integro Difference Equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a Multiresolution Approximation (MRA) framework for the IDE based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is approached in a Maximum Likelihood (ML) framework using the Expectation Maximisation (EM) algorithm. Examples are given to demonstrate the features of the model.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Dynamic spatio-temporal modelling, Expectation Maximisation (EM) algorithm, Integro-Difference Equation (IDE), Multiresolution Approximation (MRA), wavelets.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
%  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
%  \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{C}{omplex} spatio-temporal behaviour is found in many different systems such as aquatic ecosystems \cite{Schofield2002}, meteorological forecasting \cite{Xu2005}, air pollution \cite{Romanowicz2006}, soil temperature  \cite{Bond-Lamberty2005}, thermal processes \cite{Deng2005}, disease spread \cite{Kuo2009} and real estate markets \cite{Sun2005}. Spatio-temporal modelling aims to represent dynamic system behaviour across time and space. %WEINAND1972

Techniques for modelling spatio-temporal systems are generating growing interest, both in the applied and theoretical literature. Of particular interest are the class of dynamic spatio-temporal models, including Cellular Automata (CA) \cite{Wolfram1984}, Coupled Map Lattices (CMLs) \cite{Billings2002}, Lattice Dynamical Wavelet Neural Network (LDWNN) \cite{Wei2009} and spatially correlated time series  \cite{Pfeifer1980,Glasbey2008,Dewar2007} which have all been used in a system identification context. The extent of the spatial interactions in these models is determined by a discrete neighbourhood structure.

Another such model is the Integro-Difference Equation (IDE). These models have received much attention in population ecology as models for the spatio-temporal spread of organisms \cite{Kot1992,Kot1996}. IDE models combine discrete temporal dynamics with a continuous spatial representation. The dynamics of this model are given by a spatial mixing kernel, which defines the mapping between the current spatial field and the previous spatial field. The IDE model can be applied to data sampled both regularly and irregularly in space due to the continuous representation of each spatial field. Estimating the underlying spatial field in time is of particular interest, and is not straightforward especially when the field displays structure at different spatial scales. Estimation of the underlying spatial field can be achieved by estimating the associated spatial mixing kernel from measured data, and then using this in a filtering framework.

Wikle \cite{Wikle2002} describes the IDE using a state-space formulation by decomposing the kernel and the field using a set of spectral basis functions. An alternative approach for the decomposition of the IDE was introduced in \cite{Dewar2009} where the resulting state and parameter space dimensions are independent of the number of observation locations. This is crucial not only for model parsimony but also has implications for studying systems observed at a high spatial resolution. In this method an Expectation-Maximisation (EM)  algorithm  was used to estimate both the field and the kernel from the observed data. A similar approach is adopted by \cite{Scerri2009} which developed a model selection procedure by considering various spatial scales at which to represent the system. %choose the appropriate model amongst models of varying Gaussian scale parameters incorporating spatio-temporal frequency domain properties of the data.
%  when the system spatial bandwidth and the kernel support are unknown.

Behaviour of the spatial field is often of interest at a variety of scales \cite{Wiens1989,Chelton1994,Schmidt2005,Ribba2006}. At each scale, an appropriate model should be adopted to adequately reflect the underlying phenomenon. The spatial field may have features at multiple scales either naturally or as a consequence of the measurement process \cite{Wilsky2002} and hence modelling methods that represent the field at multiple scales are essential. Multiresolution Approximation (MRA) \cite{Mallat1989a,Mallat1989b,Walnut2002} provides such a modelling framework in which information at different scales can be represented simultaneously.
%  and can be used for the analysis and modelling of systems in which the spatio-temporal dispersal patterns are markedly different at the global and local scales \cite{Chelton1994,WIKLE2003,Schnell2007}. At each scale, an appropriate model should be adopted to adequately reflect the underlying dynamics.

% At the same time, a successful multiresolution representation opens up possibilities to further investigate the system in order to develop more efficient modelling schemes. For instance, in irregular observation scenario information at different scales can be integrated in a model with varying scales each suited for a specific region. %Often a proper scale is not known a priori and hence MRA can gives insight to appropriate levels is necessary to adequately capture the behaviour of the system.

% three distinct
% ways in which multiresolution features can enter into a signal or image analysis problem.

% The spatial field may have features at multiple scales by nature,  or regardless the underlying nature of the field ,  observations might be collected at several different resolutions. In such cases, modelling methods that represent the field at multiple scales are better suited than single scale models.

% The spatial field may possess features at multiple scales by nature,  or regardless the underlying nature of the field ,  observations might be collected at several different resolutions. Therefore modelling methods that represent the field at multiple scales are better suited than single scale models. Multiresolution approximation (MRA) \cite{Meyer1993,Mallat1989a}  provides such modelling framework in which information at different scales can be obtained simultaneously.

% One example is multiresolution representation of the gravity field in which a global trend (coarse level) is computed from the satellite data and the regional and local information (fine level) is obtained from terrestrial and airbone data sets \cite{Schmidt2005}.

% In addition to representing a phenomenon at different scales, MRA approximation properties make them attractive for many identification problems. MRA has been implemented in both static and dynamic spatio-temporal  modelling contexts, for example in static modelling it has been used to provide a multiresolution covariance structure for non-stationary models which can adapt to heterogeneous spatial correlations \cite{D.Nychka2002}. In dynamic modelling MRA is used to identify CML models, which infer spatio-temporal patterns from measured data \cite{Billings2006}.

%   Semi-orthogonal B-spline wavelets are compactly supported and optimally localised in time and frequency.

In practice, MRA can be implemented using different types of wavelet and scaling functions. Semi-orthogonal B-spline wavelets \cite{Chui1992,Unser1993} benefit from distinctive properties which are useful for system identification purposes. They are compactly supported and have a closed-form analytic expression which allows simple manipulations such as integration \cite{Unser1992,Chui1992a}. This class of wavelets has been successfully applied in approximation schemes such as wavelet networks\cite{G.P.Liu2000,Jun2005} and wavelet based CML models \cite{Billings2006}.

In this paper a multiresolution approximation of the IDE based on the model proposed in \cite{Dewar2009} is presented. B-spline scaling and wavelet functions are used to decompose both the kernel and the spatial field. Maximum likelihood estimates of the derived parametric state-space model are obtained using the EM-based algorithm of  \cite{Dewar2009}.  In this model, the kernel and the spatio-temporal dynamics of the field are viewed at different spatial scales. Whereas in \cite{Scerri2009} different spatial scales were examined and one chosen, the work presented herein represents the system at a number of different spatial scales concurrently.
% - a property that the alternative models described above do not typically share.
% Gaussian Radial Basis Functions have been used by  to identify the appropriate scale for the IDE to represent the underlying spatio-temporal dynamic however not in a MRA framework.

  The rest of this paper is set out as follows: in Section 2, the IDE model is briefly reviewed and the MRA of the IDE is presented. Section 3 introduces the B-spline wavelet IDE model and provides necessary formulation  to construct such a model in state-space. Section 4 briefly reviews the EM-based approach for parameter and state estimation. In Section 5, synthetic examples are given to demonstrate the ability of the developed MRA model in estimation of the hidden spatio-temporal field and the spatial mixing kernel. Finally conclusions are drawn in Section 6.

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

%\hfill mds

%\hfill January 11, 2007

%\subsection{Subsection Heading Here}
%Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.
\section{MRA of the IDE in State-Space}
The spatially homogeneous, linear IDE is given by
\begin{equation}
 z_{t+1}\left(\mathbf{s}\right)=\int_{\mathcal{S}}k\left(\mathbf{s}-\mathbf{r}\right)z_{t}\left(\mathbf{r}\right)d\mathbf{r}+e_{t}\left(\mathbf{s}\right)
\label{eq:ConvolutionIntegral}
\end{equation}
where $t\in \mathbb{Z}_0 $ denotes discrete time, $\mathbf{s},\mathbf{r} \in \mathcal{S} \subset \mathbb{R}^{n_\mathcal{S}}$ are spatial locations in $n_{\mathcal S}$-dimensional physical space, where $n_{\mathcal S} \in \left\lbrace 1,2,3 \right\rbrace $. The continuous spatial field at time $t$ and at location $\mathbf s$ is denoted $z_t\left(\mathbf s\right)$. The model dynamics  are defined by the homogeneous time invariant spatial mixing kernel, $k\left(\mathbf{s}-\mathbf{r}\right):\mathbb{R}^{n_\mathcal{S}}\rightarrow \mathbb{R}$ which maps the current spatial field to the next spatial field via the integral (\ref{eq:ConvolutionIntegral}). The disturbance $e_{t}(\mathbf{s})$ is a zero-mean normally distributed noise process, spatially coloured but temporally independent, with covariance 
\begin{equation}
cov\left(e_{t}\left(\mathbf{s}\right),e_{t+\tau}\left(\mathbf{r}\right)\right)=
\begin{cases}
\eta\left(\mathbf{s}-\mathbf{r}\right), & \tau=0 \\
0 & \mathrm{otherwise}
\end{cases}
\label{eq:FieldCovariance}
\end{equation}
for any $\tau \in \mathbb{Z}$, where $\eta\left(\mathbf s-\mathbf r \right)$ is a  spatially homogeneous covariance function. The spatial field is observed by
\begin{equation}
 \mathbf{y}_{t}=\mathbf{z}_{t}+\mathbf{v}_t
\label{eq:observation equation}
\end{equation}
where the observation vector $\mathbf{y}_{t}=[y_t(\mathbf{s}_1) y_t(\mathbf{s}_2)\cdots y_t(\mathbf{s}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise $\mathbf{v}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{v}\right)$ with $\mathbf{\Sigma}_{v}=\sigma_v^2\mathbf I_{n_y} $. It is assumed here that $\boldsymbol\Sigma_v$ and $\eta\left(\mathbf s-\mathbf r \right)$ are known. The superscript $\top$ denotes the transpose operator.

Assuming $z_t(.)$ and $k(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the integral (\ref{eq:ConvolutionIntegral}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$. For the one-dimensional kernel this is given by,
\begin{equation}
 k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(s-r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(s-r\right) 
\label{eq:KernelExpansion}
\end{equation}
In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(s\right)=2^{\frac{j}{2}}\phi\left(2^js-l\right) $ and $\psi_{j,l}\left(s\right)=2^{\frac{j}{2}}\psi\left(2^js-l\right)$. Integers $j$ and $l$ are called scale and translation parameters accordingly. The one-dimensional field can similarly be decomposed as
\begin{equation}
 z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(s\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(s\right)
\label{eq:FieldExpansion}
\end{equation}
where $ x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$.
A  two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up  using the tensor-product approach \cite{Meyer1992,Mallat1998}. We write the 2-D scaling function as
\begin{equation}
 \phi_{j,\mathbf{l}}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)
\label{eq:2Dscalingfunction}
\end{equation}
and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right)$ where $n=1,2,3$ as
\begin{equation}
 \psi_{j,\mathbf{l}}^{(1)}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)
\label{eq:2Dwavelet_1}
\end{equation}
\begin{equation}
 \psi_{j,\mathbf{l}}^{(2)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)
\label{eq:2Dwavelet_2}
\end{equation}
\begin{equation}
 \psi_{j,\mathbf{l}}^{(3)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)
\label{eq:2Dwavelet_3}
\end{equation}
for $j \in \mathbb{Z}$ and, $\mathbf{l} \in \mathbb{Z}^2$, where $\psi_{j,\mathbf{l}}^{(1)},  \psi_{j,\mathbf{l}}^{(2)}$ and $\psi_{j,\mathbf{l}}^{(3)} $ extract fine features of the 2-D field at vertical, horizontal and diagonal orientations respectively.
This can be generalised to $d$-dimensional MRA by introducing the scaling function
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
  \phi_{j,\mathbf{l}}\left(s_1,s_2, \cdots s_d\right)&=&\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right) \cdots \phi_{j,l_d}\left(s_d\right) \label{eq:d-dimensionalscalingfunction}\\
 &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case. Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
 k\left(\mathbf{s}-\mathbf{r}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{s}-\mathbf{r}\right) \nonumber \\
&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}-\mathbf{r}\right) 
\label{eq:MultidimensionalKernelExpansion}
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
\begin{equation}
z_t\left(\mathbf{s}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{s}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}\right)
\label{eq:MultidimensionalFieldExpansion}
\end{equation}
Equations (\ref{eq:MultidimensionalKernelExpansion}) and (\ref{eq:MultidimensionalFieldExpansion}) are infinite series expansions. For practical implementation, (\ref{eq:MultidimensionalKernelExpansion}) and (\ref{eq:MultidimensionalFieldExpansion}) must be truncated at some level $j$, therefore we have
 \begin{equation}
 k\left(\mathbf{s}-\mathbf{r}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{s}-\mathbf{r}\right)
\label{eq:KernelFiniteExpansion}
\end{equation}
\begin{equation}
 z_t\left(\mathbf{s}\right)\approx\boldsymbol\mu\left(\mathbf{s}\right)^\top\mathbf{x}_t
\label{eq:FieldFiniteExpansion}
\end{equation}
where the unknown parameter vector $ \boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and the unknown state vector $ \mathbf{x}_t \in \mathbb{R}^{n_x}$ are defined as 
\begin{equation}
 \boldsymbol\theta^\top=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
\label{KernelWeights}
\end{equation}
\begin{equation}
 \mathbf{x}_{t}^\top=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right] 
\label{FieldWeights}
\end{equation}
and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0,\mathbf l}:\mathbf{l} \in \mathbb{Z}^d \right\rbrace $ and $\left\lbrace x_{t,j_0,\mathbf l}: \mathbf{l} \in \mathbb{Z}^d\right\rbrace$ respectively. The kernel detail coefficient vectors $\boldsymbol \beta_{j}$ and the field detail coefficient vectors $\check{\mathbf{x}}_{t,j}$ are defined by
\begin{equation}
 \boldsymbol\beta_{j}^\top=\left[\boldsymbol\beta_{j}^{(1)\top} \quad \boldsymbol\beta_{j}^{(2)\top} \cdots \boldsymbol\beta_{j}^{(2^d-1)\top}\right] 
\end{equation}
\begin{equation}
\check{\mathbf{x}}_{t,j}^\top=\left[\check{\mathbf{x}}_{t,j}^{(1)\top} \quad \check{\mathbf{x}}_{t,j}^{(2)\top} \cdots \check{\mathbf{x}}_{t,j}^{(2^d-1)\top}\right] 
\end{equation}
where the vector $\boldsymbol\beta_{j}^{(i)}$ contains all the coefficient $\left\lbrace \beta_{j,\mathbf l}^{(i)} :\mathbf{l} \in \mathbb{Z}^d\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}^{(i)}$ contains all the coefficient $\left\lbrace  \check x_{t,j,\mathbf l}^{(i)}:\mathbf{l} \in \mathbb{Z}^d\right\rbrace$. 
%and  $\boldsymbol\lambda(\mathbf{s}-\mathbf{r})$ is the vector of the kernel scaling and wavelet functions and   $\boldsymbol\mu(\mathbf{s})$ is the vector of the field scaling and wavelet functions. 
 The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_{\theta}}$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_x}$ are defined by
\begin{eqnarray}
 \boldsymbol\lambda^\top(\mathbf s-\mathbf r)&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s-\mathbf r) \right. \nonumber \\
&&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
\label{KernelBasisVector} 
\end{eqnarray}
\begin{equation}
 \boldsymbol\mu^\top(\mathbf s)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s) \cdots \boldsymbol\psi_{j}^\top(\mathbf s) \right] 
\label{FieldBasisVector}
\end{equation}
Each vector of basis functions on the right hand-side of (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in a way similar to their corresponding weight vectors in (\ref{KernelWeights}) and (\ref{FieldWeights}). Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales. In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.

% however it can be tailored to capture underlying dynamics with desired accuracy for a sufficiently large value of $j$, a value between zero and three is usually sufficient in many applications \cite{Wei2006}. Note that number of translation parameters is always finite and depends on the range of measured data.

The state-space representation of the spatio-temporal IDE proposed in \cite{Dewar2009} is derived for an arbitrary set of basis functions and hence this derivation can be applied using scaling and wavelet basis functions. Let
\begin{equation}
 \mathbf{\Lambda}_{x}=\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\boldsymbol\mu\left(\mathbf{s}\right)^\top d\mathbf{s}
\label{eq:ConstructionIntegral1}
\end{equation}
\begin{equation}
 \mathbf{\Lambda}_{\theta}=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\boldsymbol\theta^\top \boldsymbol\lambda\left(\mathbf{s-r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top d\mathbf{r}d\mathbf{s}
\label{eq:ConstructionIntegral2}
\end{equation}
where $\boldsymbol\Lambda_{x}, \boldsymbol\Lambda_{\theta} \in \mathbb{R}^{n_x \times n_x}$. The spatial IDE model in (\ref{eq:ConvolutionIntegral}) and (\ref{eq:observation equation}) can be represented as linear state-space model of the form  
\begin{equation}
 \mathbf{x}_{t+1}=\mathbf{A}\left(\boldsymbol\theta\right)\mathbf{x}_t+\mathbf{w}_t
\end{equation}
\begin{equation}
\mathbf{y}_t=\mathbf{C}\mathbf{x}_t+\mathbf{v}_t
\end{equation}
where 
\begin{equation}
 \mathbf{A}\left(\boldsymbol\theta\right)=\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda_{\theta}}
\label{eq:TransitionMatrix}
\end{equation}
and  \\ \\ 
$\mathbf{C}=$
$\begin{pmatrix}
\boldsymbol\phi_{j_0}\left(\mathbf{s}_1\right) & \boldsymbol\phi_{j_0}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\phi_{j_0}\left(\mathbf{s}_{n_y}\right) \\
\boldsymbol\psi_{j_0}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j_0}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j_0}\left(\mathbf{s}_{n_y}\right) \\
\boldsymbol\psi_{j_0+1}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j_0+1}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j_0+1}\left(\mathbf{s}_{n_y}\right) \\
\vdots & \vdots & \ddots& \vdots \\
\boldsymbol\psi_{j}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j}\left(\mathbf{s}_{n_y}\right) \\
\end{pmatrix}^{\top}$ \\ \\
\\ \\ and where 
\begin{equation}
 \mathbf{w}_t=\mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)e_t\left(\mathbf{s}\right)d\mathbf{s}
\label{CovofField}
\end{equation}
 is a vector valued, zero-mean normally distributed white noise process with covariance given by (Lemma \ref{lemma:FieldCovariance}, Appendix)
\begin{equation}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{-\top}
\end{equation}
and
\begin{equation}
 \boldsymbol\Pi=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\eta\left(\mathbf{s}-\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^{\top}d\mathbf{r}d\mathbf{s}
\label{eq:Pi}
\end{equation}
By substituting the  parameter vector $\boldsymbol\theta$, the  state vector $\mathbf{x_t}$, the vector of kernel basis functions $\boldsymbol\lambda$ and the vector of field basis functions $\boldsymbol\mu$ in (\ref{eq:ConstructionIntegral1}-\ref{eq:Pi}), the state-space representation of the multiresolution approximation of the IDE can be achieved. It should be noted that the complexity of the model is independent of the number of observation locations, providing more flexibility in handling high resolution data. %The model is also capable of being applicable to scenarios with irregular observation locations.

% In practice, MRA can be implemented using different types of wavelet and scaling functions.  Semi-orthogonal B-spline wavelets are compactly supported and optimally localised in time and frequency. This class of wavelets has been applied in approximation schemes such as wavelet networks\cite{G.P.Liu2000,Jun2005} and wavelet based CML models \cite{Billings2006}.

\section{B-spline wavelet IDE model}
Multiresolution approximation can be implemented using different classes of scaling and wavelet functions. In order to determine the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ convolution and inner product expressions of the basis functions need to be computable. B-spline wavelet and scaling functions are particularly convenient in the above decomposition as their convolution and inner product expressions can be found analytically.

The  $m$th order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992} 
\begin{eqnarray}
N_{m}\left(s\right)&=&\left(N_{m-1}\ast N_{1}\right)\left(s\right)\nonumber \\
&=&\int_0^{1} N_{m-1}\left( s-r\right)dr \quad m>1 
\label{SplineConvolutionIntegral}
\end{eqnarray}
Here $\ast$ denotes the convolution operator and $N_1\left(s\right)$ is the characteristic function of the unit interval  $\left[ 0,1\right) $
\begin{equation}
N_{1}\left(s\right)=
\begin{cases}
1 & \text{if $ 0\le s<1$}, \\
0 & \mathrm{elsewhere}
\end{cases}
\end{equation}
In order to compute the  integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}) we need to be able to calculate the convolution and inner product of B-spline scaling functions. Equation (\ref{SplineConvolutionIntegral}) can be rewritten as $(m-1)$ times convolution of indicator function with itself 
\begin{equation}
 N_{m}\left(s\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(s\right)
\end{equation}
then by using the associativity property of the convolution operator, it is clear that
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
N_{m}\left(s\right) \ast N_{m'}\left(s\right)&=&\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(s\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(s\right)\nonumber\\
&=&N_{m+m'}\left(s\right)
\label{eq:BsplineConvolution}
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
This result can be used to show that (Lemma \ref{lemma:InProduct}, Appendix)
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
 \left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right)
\label{eq:BsplineInnerProduct}
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
where $\left\langle  .,.\right\rangle $ denotes the inner product.

The $m$th order compactly supported B-spline wavelet function is defined as \cite{Chui1992} 
\begin{equation}
 \varphi_{m}\left(s\right)=\sum_{n=0}^{3m-2} q_n N_{m}\left(2s-n\right)
\end{equation}
with the coefficients given by:\\ 
\begin{equation}
 q_n= \frac{\left(-1\right)^n}{2^{m-1}} \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right) \quad \text{ $0\le n\le 3m-2$}
\end{equation}

By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}) can be computed. In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, scaling and wavelet basis functions should be expanded  in terms of $N_m$ at the appropriate scale. It is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}: 
\begin{equation}
 \left\langle \psi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
\label{PsiPsiOrthogonality}
\end{equation}
\begin{equation}
 \left\langle \phi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2
\label{PhiPsiOrthogonality}
\end{equation}
Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions. In the two dimensional case, the convolution integral can be factorised as follows, e.g. 
\setlength{\arraycolsep}{0.14em}
\begin{IEEEeqnarray}{!l l }
 \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right)\ast \psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)&=\left[\phi_{m;j,l_1}\left(s_{1}\right)\ast\phi_{m;j,l'_1}\left(s_{1}\right)\right] \nonumber \\
&\times \left[ \phi_{m;j,l_2}\left(s_{2}\right) \ast \psi_{m;j,l'_2}\left(s_{2}\right)\right] \nonumber \\
&
\end{IEEEeqnarray}
\setlength{\arraycolsep}{5pt}
The preceding factorisation can be also applied to the 2D-inner product integral. Non-zero quantities can  be then expressed by
\setlength{\arraycolsep}{0.14em}
\begin{IEEEeqnarray}{!l l }
\left\langle \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\phi_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle &=\left\langle \phi_{m;j,l_1}\left(s_{1}\right),\phi_{m;j,l'_1}\left(s_{1}\right)\right\rangle \nonumber \\
& \times\left\langle \phi_{m;j,l_2}\left(s_{2}\right) , \phi_{m;j,l'_2}\left(s_{2}\right)\right\rangle \nonumber \\
&
\end{IEEEeqnarray}
\setlength{\arraycolsep}{5pt}
likewise we can compute 
$\left\langle  \psi^{1}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$
, \\
$\left\langle  \psi^{2}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{2}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$ and \\
$
\left\langle \psi^{3}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right), \psi^{3}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle $. \\ \\
Using these expansions it becomes straightforward to calculate the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}). In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
\section{Estimation of the Multiresolution Spatio-temporal IDE Model}
A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm to infer both the kernel and the spatial field from the noise corrupted spatio-temporal data. In this context, the EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the spatial mixing kernel parameters and the posterior distribution of the field weights. In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$ \cite{Gibsona2005}. This can be achieved for the state-space representation of the IDE model via Theorem 2 of \cite{Dewar2009} under very mild conditions.

In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother can be employed to determine the posterior state sequence. It can be shown that \cite{Dempster1977,Gibsona2005} every EM iteration increases the lower bound on the likelihood function and hence improving the state and parameter estimates. The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
\begin{equation}
\left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\varepsilon 
\end{equation}
where $\varepsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norm  of the successive estimates of $\mathbf{A} $ matrices. It has been shown \cite{Dewar2009} that the state dimension is a critical factor in the complexity of the estimation procedure, however using the above decomposition, this is decoupled from the number of observation locations.
% The complexity of this algorithm is $O\left(n_{x}^2n_{\theta}^2\right)+O \left(Tn_{x}^{3}\right)+O\left(Tn_{y}^3\right) $ showing that
\section{Simulation}
This section demonstrates the identification of the proposed IDE model. Primarily, the MRA of a synthetic model is demonstrated, which is able to represent the system at different spatial scales. In addition, the complexity of the field decomposition is shown to be independent to the number and spatial regularity of the observation locations. This allows the construction of parsimonious models using spatially dense observations, and demonstrates the utility of the approach to situations where the observations are not arranged on a regular lattice, i.e. sensor networks \cite{Sahu2008}.
\subsection{One dimensional example}
 Consider the following homogeneous multiscale spatial mixing kernel 
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
k\left(s-r\right)&=& -\phi_{4;0,-3}\left(s-r\right)+\phi_{4;0,-2}\left(s-r\right)\nonumber\\
&&{-}\:0.5\psi_{4;1,-6}\left(s-r\right)+0.5\psi_{4;1,-3}\left(s-r\right)
\label{eq:1DSimulationKernel}
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
The kernel and its decomposition are plotted in  \figurename{\ref{fig:SpatialMixingKernel}}. The dynamics associated with the IDE defined by (\ref{eq:1DSimulationKernel}) will be oscillatory and dissipative to initial conditions. The field is decomposed using scaling functions $\phi_{4;0,k} $ and the associated wavelet functions $\psi_{4;j,k} $ with $j=0,1$. Observations are then generated from (\ref{eq:ConstructionIntegral1}-\ref{eq:Pi}) for spatial domain defined as $\mathcal{S}=\left[0,10 \right] $ in response to an initial condition where $\boldsymbol\Sigma_v=0.2 \times \mathbf{I}_{n_y}$ and $ \eta(s-r)=2.5\times\phi_{4,3,-2}(s-r)$. The response was sampled at 50 irregularly spaced random locations, at $t=1, \cdots 400 $.
\begin{figure}[!h] 
\centering
\includegraphics[width=0.5\textwidth]{./Graph/aram1.eps}
\caption{Multiresolution decomposition of a complex spatial mixing kernel (dark line) and the corresponding scaling and wavelet basis functions (light lines).}
\label{fig:SpatialMixingKernel}
\end{figure} 
\begin{figure}[!h] 
\centering
\includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
\caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$. }
\label{fig:SpatialMixingKernelEstimate}
\end{figure}
\begin{figure*}[!hb] 
% \renewcommand*{\thesubfigure}{}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
\caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
\label{fig:1DFieldEstimation}
\end{figure*}
In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
\begin{equation}
 k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
\label{1DKernelDecompositionForSimulation}
\end{equation}
\begin{equation}
 z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
\label{1DFieldDecompositionForSimulation}
\end{equation}
Note that the number of translation operations depends on the spatial range of the data. It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively. The estimated kernel in \figurename{\ref{fig:SpatialMixingKernelEstimate} } is obtained for the cubic B-spline, with initial scale 0 and maximum scale 1. The EM algorithm is allowed to run for 30 iterations to avoid any issues regarding early stopping, though typically the change in $\parallel \mathbf{A} \parallel_{F}$ falls below $10^{-4} $ after less than 15 iterations. A total number of 500 estimation experiments are performed, where $v_t$ and $w_t$ are re-generated each trial.

 The performance measure employed here is the Mean Integrated Squared Error (MISE) defined as
\begin{equation}
 \mathbf{E}\left[\int_{\mathcal{S}}\left[e\left(s\right) \right]^2ds  \right]
\label{MISE} 
\end{equation}
 where  $e\left(s\right)$ is the error between the unknown function, $f\left( s\right) $ and its estimate, $\hat{f}\left( s\right) $. In this example the original kernel and the field are known and hence the integral in  (\ref{MISE}) can be computed analytically. For spatial mixing kernel we have
\begin{eqnarray}
 \lefteqn{\int_{\mathcal{S}}\left[e\left(s\right)\right]^2ds}\nonumber \\  &=\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)^\top\left[ \int_{\mathcal{S}}\boldsymbol\lambda\left(s\right)\boldsymbol\lambda\left(s\right)^\top ds\right] \left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)&
\label{MISEKernel}
\end{eqnarray}
  Here, we are particularly interested in assessing the performance improvement as the scale of the details in MRA is increased. Performance based on (\ref{MISEKernel}) at different spatial scales and over 500 trials have been evaluated. The MISE of the model at $j=0$ is 0.024 and reduces to 0.005 when $\psi_{4;1,k}$ terms are also included in the model, in fact estimation performance is improved by a factor of 4.8. The coarsest approximation of the kernel along with its approximation at $j=1$ are illustrated in \figurename{\ref{fig:SpatialMixingKernelEstimate}. It can be seen that the model is able to estimate both slowly and rapidly varying segments of the  kernel with very high accuracy.  Field estimates  at a selection of time instants are shown in \figurename{\ref{fig:1DFieldEstimation}}. It is clearly observed that the coarse and fine features of the original field have been captured accurately over regions where observations are available. Observation locations are generated randomly, as shown in \figurename{ \ref{fig:FieldVariance}}. Assuming the observed field can be fully described by the  decomposed IDE model, the variance of the field can be computed to express the  uncertainty of the estimation, at each point in space and at time $t$ we have 
\begin{equation}
 \text{Var}(\hat z_t(s_i))=\boldsymbol\mu^{\top}(s_i) \mathbf P_{t|T}\boldsymbol\mu(s_i)
\label{eq:FieldVariance}
\end{equation}
where $\mathbf P_{t|T} $ is the covariance matrix associated with the  state estimates obtained from the RTS smoother. Variance based on (\ref{eq:FieldVariance}) at each spatial location and at $t=50$ is shown in \figurename{\ref{fig:FieldVariance}}. The uncertainty of the estimation is higher at almost  every spatial location at $j=1$ compared to $j=0$. This is to be expected as there are more wavelet basis functions at higher resolution and hence more associated weights need to be estimated. Peaks in the variance of the field coincide with regions where no observations have been made. Increasing the number of observation locations, or using equally spaced observation locations would reduce the variance of the field estimation.
\begin{figure}[!h] 
\centering
\includegraphics[width=0.5\textwidth]{./Graph/aram4.eps}
\caption{Variance of the field at each spatial location for $j=0$ (dotted line) and $j=1$ (solid line). The observation locations are described with a cross.}
\label{fig:FieldVariance}
\end{figure} 
\subsection{Two dimensional example}
In order to demonstrate the ability of the developed model in higher dimensions, a two dimensional IDE model with a single B-spline kernel $\phi_{4;0,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right) $ and $\mathbf l=[-2,-2]^ \top$ is used with parameter $\theta=1$. In this example spatial region $\mathcal{S}=[0,4]^2 $ is simulated over $t=\left\lbrace1 \cdots 200  \right\rbrace $ using $7$ scaling and wavelet functions at $j=0$ together with $24$ wavelet functions at $j=1$. Univariate cubic B-spline scaling and wavelet functions are used to generate 2-D basis functions using (\ref{eq:2Dscalingfunction}-\ref{eq:2Dwavelet_3}). A set of $250$ random  observation locations is used; $\mathbf{\Sigma}_v$ is taken the same as that in example 1 and $ \eta\left(s_1-r_1,s_2-r_2\right) =2.5\times\phi_{4,3,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right)$ where $\mathbf l=[-2,-2]^ \top$. The histogram of the parameter estimates  in \figurename{\ref{fig:2DHist} is generated using 500 runs of the EM algorithm. For comparison, snapshots for the original and the corresponding coarse and fine field estimates at time instants 5, 50 and 150 are illustrated in \figurename{\ref{fig:2DFieldEstimation1}-\ref{fig:2DFieldEstimation3}}. In addition, the MISE of the dynamic field at some time instants are presented in Table \ref{table:ValidationResultField}.  This shows that the multiresolution IDE model can estimate the spatio-temporal dynamics of the original system accurately. The accuracy of the estimation remains consistent over time. Performance is improved significantly at $j=1$ compared to the case where $j=0$.
\begin{figure}[!t] 
\centering
\includegraphics[width=0.5\textwidth]{./Graph/aram5.eps}
\caption{Distribution of the parameter estimate for 2-D Example over 500 runs of the EM algorithm. The dotted line indicates the true parameter.}
\label{fig:2DHist}
\end{figure}
\begin{figure*}[!th] 
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6a.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6b.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6c.eps}}\\ 
\caption{Spatial field at t=5; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
\label{fig:2DFieldEstimation1}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7a.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7b.eps}} 
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7c.eps}}\\
\caption{Spatial field at t=50; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
\label{fig:2DFieldEstimation2}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8a.eps}}
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8b.eps}} 
\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8c.eps}}
\caption{Spatial field at t=150; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
\label{fig:2DFieldEstimation3}
\end{figure*}
\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption {MISE  at particular scale between measured and estimated 2D-field  at a particular time}
\label{table:ValidationResultField}
\centering
\begin{tabular}{cccc}
\hline \hline
\multicolumn{2}{r}{Time}&\multicolumn{2}{c}{MISE} \\
\cline{3-4}
&&$j=0$&$j=1$ \\ 
\hline 
&$5$ &$5.424$&$0.609$ \\
&$20$ &$5.422$&$0.596$ \\
&$50$ &$5.519$&$0.626$ \\
&$100$ &$5.488$&$0.611$ \\
&$150$ &$5.494$&$0.587$ \\
\hline \hline
\end{tabular}
\end {table}
\section{Conclusion}
A multi-resolution approach to modelling spatio-temporal systems has been presented. This model is able to represent continuous-space, discrete-time dynamics at a number of spatial scales simultaneously. This ability greatly extends the class of system which the Integro-Difference Equation can represent.

By decomposing both the spatial field and the spatial mixing kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details. This is an essential component of any practical spatio-temporal model, without which the model must be artificially separated into global and local modes a-priori.

The complexity of the model is not affected by the spatial resolution of the observation process, rather it reflects the underlying complexity of the system under study. Therefore, increasing the resolution at which the system is observed does not necessarily increase the complexity of the system identification problem. However the developed algorithm is sensitive to the state dimension, equivalent to the detail represented in the field, and hence intelligent approaches to reduce the number of basis functions is noted as future work.

By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework. Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed
% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
\newtheorem{lemma}{Lemma}
\begin{lemma}
Consider the zero-mean process $e_t\left(s\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then
\begin{equation}
 \mathbf{w}_t=\mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)e_t\left(\mathbf{s}\right)d\mathbf{s}
\label{eq:AppendixWt}
\end{equation}
is a vector valued, zero mean normally distributed white noise process with covariance
\begin{equation}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
\end{equation}
and
\begin{equation}
 \boldsymbol\Pi=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)\eta\left(\mathbf s-\mathbf r\right)\boldsymbol\mu\left(\mathbf r\right)^\top d\mathbf{r}d\mathbf{s}
\end{equation}
\label{lemma:FieldCovariance}
\end{lemma}
\begin{IEEEproof}
 Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf s)$ and hence $\mathbf{w}_t$ is also normally distributed. The expected value of $\mathbf w_t$ is given by 
\begin{eqnarray}
 \mathbf E\left[ \mathbf w_t\right]&=& \mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)\mathbf E\left[e_t\left(\mathbf{s}\right)\right] d\mathbf{s} \nonumber \\
&=&0
\end{eqnarray}
and 
\begin{eqnarray}
\mathbf \Sigma_w&{}={}&\mathbf E[ \mathbf w_t \mathbf w_{t}^{\top}]\nonumber\\
&=& \mathbf{\Lambda}_{x}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Lambda}_{x}^{- \top} \nonumber \\
&=&\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
&=&{}\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \eta\left(\mathbf s- \mathbf r \right)\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
&=&\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
\end{IEEEproof}
\begin{lemma}
Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively. Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by 
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
\left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
\label{lemma:InProduct}
\end{lemma}
\begin{IEEEproof}
The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
\begin{equation}
 N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
\label{SymmetrySplieEq}
\end{equation}
A direct consequence of (\ref{SymmetrySplieEq}) is 
\begin{equation}
 N_{m}\left(s\right)=N_{m}\left(m-s\right)
\end{equation}
Therefore
\setlength{\arraycolsep}{0.0em}
\begin{IEEEeqnarray}{l}
\int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
\qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
\end{IEEEeqnarray}
\setlength{\arraycolsep}{5pt}
\end{IEEEproof}

%\appendices
%\section{Proof of the First Zonklar Equation}
%Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section{}
%Appendix two text goes here.

% use section* for acknowledgement
%\section*{Acknowledgment}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
  \newpage
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,../../../Papers/SpatioTemporalSystems,../../../Papers/Wavelet}

% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

% \begin{thebibliography}{1}
% 
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
% 
%  \end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:
% \begin{IEEEbiography}{Parham Aram}
% 
%  
% \end{IEEEbiography}
% 
% \begin{IEEEbiography}{Visakan Kadirkamanathan}
% % Biography text here.
% (M’90) received the
% B.A. and Ph.D. degrees in electrical and information
% engineering from the University of Cambridge, U.K.
% He held Research Associate positions at the University
% of Surrey, U.K., and the University of Cambridge,
% U.K., before joining the Department of Automatic
% Control and Systems Engineering, The University
% of Sheffield, U.K., as a Lecturer in 1993, where
% he is currently a Professor of Signal and Information
% Processing and is affiliated to the Centre for Signal
% Processing and Complex Systems. His research interests
% include nonlinear signal processing, system identification, intelligent control
% and fault diagnosis with applications in systems biology, aerospace systems,
% and wireless communication. He has coauthored a book on intelligent control
% and has published more than 120 papers in refereed journals and proceedings of
% international conferences.
% Prof. Kadirkamanathan is the Co-Editor of the International Journal of Systems
% Science and has served as an Associate Editor for the IEEE TRANSACTIONS
% ON NEURAL NETWORKS and the IEEE TRANSACTIONS ON SYSTEMS, MAN, AND
% CYBERNETICS, PART B.
%  \end{IEEEbiography}
% \begin{IEEEbiography}{Michael Dewar}
%  received the M.Eng. degree in
% control systems engineering and the Ph.D. degree
% in systems engineering both from The University of
% Sheffield, U.K., in 2002 and 2007, respectively.
%  He is currently working as
% a Research Associate in the Institute for Adaptive
% and Neural Computation, School of Informatics,
% The University of Edinburgh, U.K. 
% \end{IEEEbiography}

% if you will not have a photo at all:
% \begin{IEEEbiographynophoto}{John Doe}
% Biography text here.
% \end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

% \begin{IEEEbiographynophoto}{Jane Doe}
% Biography text here.
% \end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2010-11-08 Multiresolution_framework/ltx/manuscript.tex
added bib file
edits to estimation section

@@
 
+ % TO DELETE
+\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
 %    \documentclass[journal,a4paper]{IEEEtran}
@@
 The continuous spatial field at time $t$ and at location $\mathbf s$ is denoted $z_t\left(\mathbf s\right)$.
-The model dynamics  are defined by the homogeneous time invariant spatial mixing kernel, $k\left(\mathbf{s}-\mathbf{r}\right):\mathbb{R}^{n_\mathcal{S}}\rightarrow \mathbb{R}$ which maps the current spatial field to the next spatial field via the integral (\ref{eq:ConvolutionIntegral}).
-The disturbance $e_{t}(\mathbf{s})$ is a zero-mean normally distributed noise process, spatially coloured but temporally independent, with covariance
-\begin{equation}
-cov\left(e_{t}\left(\mathbf{s}\right),e_{t+\tau}\left(\mathbf{r}\right)\right)=
-\begin{cases}
-\eta\left(\mathbf{s}-\mathbf{r}\right), & \tau=0 \\
-0 & \mathrm{otherwise}
-\end{cases}
-\label{eq:FieldCovariance}
-\end{equation}
-for any $\tau \in \mathbb{Z}$, where $\eta\left(\mathbf s-\mathbf r \right)$ is a  spatially homogeneous covariance function. The spatial field is observed by
+The model dynamics  are defined by the homogeneous time invariant spatial mixing kernel, $k\left(\mathbf{s}-\mathbf{r}\right):\mathbb{R}^{n_\mathcal{S}}\rightarrow \mathbb{R}$ which maps the current spatial field to the next spatial field via the integral (\ref{eq:ConvolutionIntegral}) and $e_t(\mathbf s)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$.
+Here $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
+The spatial field is observed by
 \begin{equation}
@@
  \mathbf{x}_{t+1}=\mathbf{A}\left(\boldsymbol\theta\right)\mathbf{x}_t+\mathbf{w}_t
+\label{eq:StateEquation}
 \end{equation}
@@
 \mathbf{y}_t=\mathbf{C}\mathbf{x}_t+\mathbf{v}_t
+\label{eq:ObservationEquation}
 \end{equation}
@@
 In this context, the EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the spatial mixing kernel parameters and the posterior distribution of the field weights.
-In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$ \cite{Gibsona2005}.
-This can be achieved for the state-space representation of the IDE model via Theorem 2 of \cite{Dewar2009} under very mild conditions.
+In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$ \cite{McLachlan1997}.
+In the E-step, given an estimate of $\boldsymbol\theta$, filtering methods can be used to determine the posterior state sequence.
+Here we compare three techniques namely based on  the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005}, Ensemble Kalman Smoother (EnKS) \cite{Evensen2003} and a heuristic separable RTS to solve the joint estimation problem.
+For the first method we modify the framework proposed in \cite{Dewar2009} by computing the required elements once instead of at each iteration, the modified algorithm is computationally less demanding.
+see Appendix ...
 
@@
 \section{Simulation}
-This section demonstrates the identification of the proposed IDE model.
+In this section, we compare the performance of the different algorithms mentioned above on a synthetic example .....This section demonstrates the identification of the proposed IDE model.
 Primarily, the MRA of a synthetic model is demonstrated, which is able to represent the system at different spatial scales.
@@
 \end{IEEEproof}
+\section*{Reducing the computational complexity}
+The state-space representation of the spatio-temporal IDE \eqref{eq:StateEquation} and \eqref{eq:ObservationEquation} has a quadratic $\mathcal Q$-function in a form of \cite{Dewar2009}
+\begin{equation}
+\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)=2 \boldsymbol\theta^\top\boldsymbol\upsilon -\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta
+\label{eq:QFunction}
+\end{equation}
+which has a maximum at
+\begin{equation}
+ \boldsymbol\theta=\boldsymbol\Upsilon^{-1}\boldsymbol\upsilon
+\end{equation}
+where
+\begin{equation}
+ \boldsymbol\Upsilon=\sum_{i,j,k,m=1}^{n_x}\left[ \Xi_1\right] _{ij}\boldsymbol\gamma^{\left(k,j\right)}\left[\boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1} \boldsymbol\Lambda_{x}^{-1}\right]_{km} \boldsymbol\gamma^{\left(m,i\right)\mathsf{T}}
+\end{equation}
+and
+\begin{equation}
+ \boldsymbol \upsilon=\sum_{i,j=1}^{n_x}\left[\Xi_0\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1} \right]_{ij}\boldsymbol\gamma^{\left(j,i\right)} 
+\end{equation}
+where
+\begin{equation}
+ \boldsymbol\gamma^{(i,j)}=\int_{\mathcal S}\left[ \mu(s)\right]_i\left[ \mathbf M(s)\right] _{:j}ds
+\end{equation}
+and $\left[ \mathbf M(s)\right] _{:j}$ denotes the $j$th column of $\mathbf M(s)$.
+The definitions of the $\Xi_0$ and $\Xi_1$ are the same as in \cite{Dewar2009}.
+Note that constant values with respect to $\boldsymbol \theta$ are ignored in \eqref{eq:QFunction}.
 
@@
   \newpage
+% \bibliographystyle{unsrt} 
+% \bibliography{MRAIDE}
+
 \bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,../../../Papers/SpatioTemporalSystems,../../../Papers/Wavelet}
+ \bibliography{IEEEabrv,MRAIDE}
 

### 2011-01-13 Multiresolution_framework/ltx/manuscript.tex
minor changes

@@
 % \hyphenation{op-tical net-works semi-conduc-tor}
+% Algorithms
+\usepackage{float}
+\floatstyle{ruled}
+\newfloat{algorithm}{htbp}{loa}%[chapter]
+\floatname{algorithm}{Algorithm}
 
@@
 
-\author{Parham Aram*,
-        Michael Dewar and Visakan Kadirkamanathan,~\IEEEmembership{Member,~IEEE}  % <-this % stops a space
+\author{In no particular order: P. Aram, M. Dewar, D.R. Freestone, K.Scerri, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
 \thanks{P.
@@
 In the E-step, given an estimate of $\boldsymbol\theta$, filtering methods can be used to determine the posterior state sequence.
-Here we compare three techniques namely based on  the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005}, Ensemble Kalman Smoother (EnKS) \cite{Evensen2003} and a heuristic separable RTS to solve the joint estimation problem.
-For the first method we modify the framework proposed in \cite{Dewar2009} by computing the required elements once instead of at each iteration, the modified algorithm is computationally less demanding.
-see Appendix ...
+Here we compare three techniques namely based on  the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005}, Ensemble Kalman smoother (EnKs) \cite{Evensen2003} and a heuristic separable RTS smoother for state estimation problem.
+For the first method we modify the framework proposed in \cite{Dewar2009} by computing and storing the required elements prior to the iterative estimation algorithm, the modified algorithm is computationally less demanding (see Appendix \ref{App:ReducedRTS}).
+In Ensemble Kalman filter (EKf) an ensemble of model states, $\mathbf X_t \in \mathbb R^{n_x \times N} \sim \mathcal N(\mathbf x_t,\mathbf P_t)$ is propogated through the state equation to calculate the forecast estimates $\hat{\mathbf x}^f_t$ and the error covariance of the predicted model state, $\mathbf P_t^f$ where $N$ is the number of ensemble members.
+Then  the model state is updated to compute analysed estimates, $\hat {\mathbf x}_t^a$.
+This is important for model with high dimensional state space where standard Kalman filter  is computationally infeasible to implement as the state covariance matrix needs to be stored and propogated in time.
+The EnKs updates the filtered ensembles at the current and all prior times every time a new set of measurements becomes available.
+The algorithm is given in Algorithm \ref{alg:EnKS} for completeness.
+It is essential that the observations be also treated as an ensemble of random variables, $\mathbf Y_t$, having a distribution with mean equal to the observed value, $\mathbf y_t$ and covariance equal to $\boldsymbol\Sigma_v$ \cite{Houtekamer2005}.
+
+% represents the predicted state covariance matrix, $\mathbf P_{t|t+1}$ using a large stochastic ensemble of the predicted states $\hat{\mathbf x}_{t+1|t}$.
+
+\begin{algorithm}
+\caption{Ensemble Kalman smoother}
+\label{alg:EnKS}
+% \begin{tabbing}
+\begin{enumerate}
+\item Initialise:
+\begin{center}
+ $\hat{\mathbf x}_0 $, $\mathbf P_0$  
+\end{center}
+\item
+for $t\in\left\lbrace 0, \dots, T\right\rbrace $, calculate the state ensembles $\hat{\mathbf X}_t$ and the model errors ensemble $\mathbf W_t$ and propogate through the state equation:
+\begin{equation*}
+\hat{\mathbf X}_{i,t+1}^f=\mathbf A \hat{\mathbf X}_{i,t}^a+\mathbf W_{i,t}
+\end{equation*}
+calculate the predicted state and the predicted covariance matrix
+\begin{equation*}
+ \hat{\mathbf x}_{t+1}^f=\frac{1}{N}\sum_{i=1}^{N}\hat{\mathbf X}_{i,t+1}^f
+\end{equation*}
+\begin{equation*}
+ \mathbf P_{t+1}^f=\frac{1}{N-1}\sum_{i=1}^{N}\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)^\top
+\end{equation*}
+\item
+compute $\mathbf X_4(t+1)$ and $\mathbf X_5(t+1)$ and the filtered state and the filtered covariance matrix:
+\begin{equation*}
+ \mathcal K_t=\mathbf C^{\top}(\mathbf C\mathbf{P}_{t+1}^f\mathbf C^{\top}+\boldsymbol\Sigma_v)^{-1}
+\end{equation*}
+
+\begin{equation*}
+ \mathbf X_4(t+1)=\frac{1}{N-1}\sum_{i=1}^{N}(\hat{\mathbf X}_{i,t+1}^f-\hat{\mathbf x}^f_{t+1} )^\top\mathcal K_t (\mathbf Y_{i,t+1}-\mathbf C\hat{\mathbf{X}}_{i,t+1}^f)
+\end{equation*}
+\begin{equation*}
+ \mathbf X_5(t+1)= \mathbf I +\mathbf X_4(t+1)
+\end{equation*}
+\begin{equation*}
+ \hat{\mathbf X}_{t+1}^a=\hat{\mathbf X}_{t+1}^f \mathbf X_5(t+1)
+\end{equation*}
+\item compute the smooth ensemble for $t\in\left\lbrace 0, \dots, T\right\rbrace $
+\begin{equation*}
+ \hat{\mathbf{X}}_{t}^s=\hat{\mathbf X}_{t}^a \prod_{j=t+1}^{T}X_5(j)
+\end{equation*}
+\end{enumerate}
+% \end{tabbing}
+\end{algorithm}
 
@@
 The response was sampled at 50 irregularly spaced random locations, at $t=1, \cdots 400 $.
-\begin{figure}[!h] 
-\centering
-\includegraphics[width=0.5\textwidth]{./Graph/aram1.eps}
-\caption{Multiresolution decomposition of a complex spatial mixing kernel (dark line) and the corresponding scaling and wavelet basis functions (light lines).}
-\label{fig:SpatialMixingKernel}
-\end{figure} 
-\begin{figure}[!h] 
-\centering
-\includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
-\caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$.
+% \begin{figure}[!h] 
+% \centering
+% \includegraphics[width=0.5\textwidth]{./Graph/aram1.eps}
+% \caption{Multiresolution decomposition of a complex spatial mixing kernel (dark line) and the corresponding scaling and wavelet basis functions (light lines).}
+% \label{fig:SpatialMixingKernel}
+% \end{figure} 
+% \begin{figure}[!h] 
+% \centering
+% \includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
+% \caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$.
 }
-\label{fig:SpatialMixingKernelEstimate}
-\end{figure}
-\begin{figure*}[!hb] 
-% \renewcommand*{\thesubfigure}{}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
-\caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
-\label{fig:1DFieldEstimation}
-\end{figure*}
+% \label{fig:SpatialMixingKernelEstimate}
+% \end{figure}
+% \begin{figure*}[!hb] 
+% % \renewcommand*{\thesubfigure}{}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
+% \caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
+% \label{fig:1DFieldEstimation}
+% \end{figure*}
 In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
@@
 Increasing the number of observation locations, or using equally spaced observation locations would reduce the variance of the field estimation.
-\begin{figure}[!h] 
-\centering
-\includegraphics[width=0.5\textwidth]{./Graph/aram4.eps}
-\caption{Variance of the field at each spatial location for $j=0$ (dotted line) and $j=1$ (solid line). The observation locations are described with a cross.}
-\label{fig:FieldVariance}
-\end{figure} 
+% \begin{figure}[!h] 
+% \centering
+% \includegraphics[width=0.5\textwidth]{./Graph/aram4.eps}
+% \caption{Variance of the field at each spatial location for $j=0$ (dotted line) and $j=1$ (solid line). The observation locations are described with a cross.}
+% \label{fig:FieldVariance}
+% \end{figure} 
 \subsection{Two dimensional example}
@@
 Performance is improved significantly at $j=1$ compared to the case where $j=0$.
-\begin{figure}[!t] 
-\centering
-\includegraphics[width=0.5\textwidth]{./Graph/aram5.eps}
-\caption{Distribution of the parameter estimate for 2-D Example over 500 runs of the EM algorithm. The dotted line indicates the true parameter.}
-\label{fig:2DHist}
-\end{figure}
-\begin{figure*}[!th] 
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6a.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6b.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6c.eps}}\\ 
-\caption{Spatial field at t=5; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-\label{fig:2DFieldEstimation1}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7a.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7b.eps}} 
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7c.eps}}\\
-\caption{Spatial field at t=50; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-\label{fig:2DFieldEstimation2}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8a.eps}}
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8b.eps}} 
-\subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8c.eps}}
-\caption{Spatial field at t=150; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-\label{fig:2DFieldEstimation3}
-\end{figure*}
+% \begin{figure}[!t] 
+% \centering
+% \includegraphics[width=0.5\textwidth]{./Graph/aram5.eps}
+% \caption{Distribution of the parameter estimate for 2-D Example over 500 runs of the EM algorithm. The dotted line indicates the true parameter.}
+% \label{fig:2DHist}
+% \end{figure}
+% \begin{figure*}[!th] 
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6a.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6b.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6c.eps}}\\ 
+% \caption{Spatial field at t=5; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
+% \label{fig:2DFieldEstimation1}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7a.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7b.eps}} 
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7c.eps}}\\
+% \caption{Spatial field at t=50; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
+% \label{fig:2DFieldEstimation2}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8a.eps}}
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8b.eps}} 
+% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8c.eps}}
+% \caption{Spatial field at t=150; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
+% \label{fig:2DFieldEstimation3}
+% \end{figure*}
 \begin{table}[!h]
@@
 \end{IEEEproof}
-\section*{Reducing the computational complexity}
+\section*{Reducing the computational complexity}\label{App:ReducedRTS}
 The state-space representation of the spatio-temporal IDE \eqref{eq:StateEquation} and \eqref{eq:ObservationEquation} has a quadratic $\mathcal Q$-function in a form of \cite{Dewar2009}
@@
 where
-\begin{equation}
+\begin{equation}\label{eq:Upsilon}
  \boldsymbol\Upsilon=\sum_{i,j,k,m=1}^{n_x}\left[ \Xi_1\right] _{ij}\boldsymbol\gamma^{\left(k,j\right)}\left[\boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1} \boldsymbol\Lambda_{x}^{-1}\right]_{km} \boldsymbol\gamma^{\left(m,i\right)\mathsf{T}}
@@
 Note that constant values with respect to $\boldsymbol \theta$ are ignored in \eqref{eq:QFunction}.
+We define $n_x \times n_x$ block matrix $\mathbf U$ such that
+\begin{equation}\label{eq:UMatrix}
+ [\mathbf U]_{i,j}=\boldsymbol\gamma^{(i,j)\mathsf{T}}
+\end{equation}
+substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we get
+\begin{equation}\label{eq:UpsilonU}
+ \boldsymbol\Upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}
+\end{equation}
+and similarly substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we have
+\begin{equation}\label{eq:upsilonU}
+ \boldsymbol\upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}
+\end{equation}
+with this substitution the second terms in \eqref{eq:UpsilonU} and \eqref{eq:upsilonU} can be pre-calculated and stored.
+This lowers the comutational complexity of the estimation algorithm and provides a dramatic increase in estimation speed.
+\section*{Cross covariance matrix}\label{App:EnCrossCov}
 

### 2011-02-14 Multiresolution_framework/ltx/manuscript.tex
added neural field modelling

@@
 %\boldmath
-The Integro Difference Equation (IDE) is an increasingly popular model of spatio-temporal processes.
+% The Integro Difference Equation (IDE) is an increasingly popular model of spatio-temporal processes.
 Here we develop a Multiresolution Approximation (MRA) framework for the IDE based on semi-orthogonal cardinal B-spline wavelets.
@@
 \section{Introduction}
+To Do
 % The very first letter is a 2 line initial drop letter followed
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{C}{omplex} spatio-temporal behaviour is found in many different systems such as aquatic ecosystems \cite{Schofield2002}, meteorological forecasting \cite{Xu2005}, air pollution \cite{Romanowicz2006}, soil temperature  \cite{Bond-Lamberty2005}, thermal processes \cite{Deng2005}, disease spread \cite{Kuo2009} and real estate markets \cite{Sun2005}.
-Spatio-temporal modelling aims to represent dynamic system behaviour across time and space.
-%WEINAND1972
-
-Techniques for modelling spatio-temporal systems are generating growing interest, both in the applied and theoretical literature.
-Of particular interest are the class of dynamic spatio-temporal models, including Cellular Automata (CA) \cite{Wolfram1984}, Coupled Map Lattices (CMLs) \cite{Billings2002}, Lattice Dynamical Wavelet Neural Network (LDWNN) \cite{Wei2009} and spatially correlated time series  \cite{Pfeifer1980,Glasbey2008,Dewar2007} which have all been used in a system identification context.
-The extent of the spatial interactions in these models is determined by a discrete neighbourhood structure.
-
-Another such model is the Integro-Difference Equation (IDE).
-These models have received much attention in population ecology as models for the spatio-temporal spread of organisms \cite{Kot1992,Kot1996}.
-IDE models combine discrete temporal dynamics with a continuous spatial representation.
-The dynamics of this model are given by a spatial mixing kernel, which defines the mapping between the current spatial field and the previous spatial field.
-The IDE model can be applied to data sampled both regularly and irregularly in space due to the continuous representation of each spatial field.
-Estimating the underlying spatial field in time is of particular interest, and is not straightforward especially when the field displays structure at different spatial scales.
-Estimation of the underlying spatial field can be achieved by estimating the associated spatial mixing kernel from measured data, and then using this in a filtering framework.
-
-Wikle \cite{Wikle2002} describes the IDE using a state-space formulation by decomposing the kernel and the field using a set of spectral basis functions.
-An alternative approach for the decomposition of the IDE was introduced in \cite{Dewar2009} where the resulting state and parameter space dimensions are independent of the number of observation locations.
-This is crucial not only for model parsimony but also has implications for studying systems observed at a high spatial resolution.
-In this method an Expectation-Maximisation (EM)  algorithm  was used to estimate both the field and the kernel from the observed data.
-A similar approach is adopted by \cite{Scerri2009} which developed a model selection procedure by considering various spatial scales at which to represent the system.
-%choose the appropriate model amongst models of varying Gaussian scale parameters incorporating spatio-temporal frequency domain properties of the data.
-%  when the system spatial bandwidth and the kernel support are unknown.
-
-Behaviour of the spatial field is often of interest at a variety of scales \cite{Wiens1989,Chelton1994,Schmidt2005,Ribba2006}.
-At each scale, an appropriate model should be adopted to adequately reflect the underlying phenomenon.
-The spatial field may have features at multiple scales either naturally or as a consequence of the measurement process \cite{Wilsky2002} and hence modelling methods that represent the field at multiple scales are essential.
-Multiresolution Approximation (MRA) \cite{Mallat1989a,Mallat1989b,Walnut2002} provides such a modelling framework in which information at different scales can be represented simultaneously.
-%  and can be used for the analysis and modelling of systems in which the spatio-temporal dispersal patterns are markedly different at the global and local scales \cite{Chelton1994,WIKLE2003,Schnell2007}.
-At each scale, an appropriate model should be adopted to adequately reflect the underlying dynamics.
-
-% At the same time, a successful multiresolution representation opens up possibilities to further investigate the system in order to develop more efficient modelling schemes.
-For instance, in irregular observation scenario information at different scales can be integrated in a model with varying scales each suited for a specific region.
-%Often a proper scale is not known a priori and hence MRA can gives insight to appropriate levels is necessary to adequately capture the behaviour of the system.
-
-% three distinct
-% ways in which multiresolution features can enter into a signal or image analysis problem.
-
-% The spatial field may have features at multiple scales by nature,  or regardless the underlying nature of the field ,  observations might be collected at several different resolutions.
-In such cases, modelling methods that represent the field at multiple scales are better suited than single scale models.
-
-% The spatial field may possess features at multiple scales by nature,  or regardless the underlying nature of the field ,  observations might be collected at several different resolutions.
-Therefore modelling methods that represent the field at multiple scales are better suited than single scale models.
-Multiresolution approximation (MRA) \cite{Meyer1993,Mallat1989a}  provides such modelling framework in which information at different scales can be obtained simultaneously.
-
-% One example is multiresolution representation of the gravity field in which a global trend (coarse level) is computed from the satellite data and the regional and local information (fine level) is obtained from terrestrial and airbone data sets \cite{Schmidt2005}.
-
-% In addition to representing a phenomenon at different scales, MRA approximation properties make them attractive for many identification problems.
-MRA has been implemented in both static and dynamic spatio-temporal  modelling contexts, for example in static modelling it has been used to provide a multiresolution covariance structure for non-stationary models which can adapt to heterogeneous spatial correlations \cite{D.Nychka2002}.
-In dynamic modelling MRA is used to identify CML models, which infer spatio-temporal patterns from measured data \cite{Billings2006}.
-
-%   Semi-orthogonal B-spline wavelets are compactly supported and optimally localised in time and frequency.
-
-In practice, MRA can be implemented using different types of wavelet and scaling functions.
-Semi-orthogonal B-spline wavelets \cite{Chui1992,Unser1993} benefit from distinctive properties which are useful for system identification purposes.
-They are compactly supported and have a closed-form analytic expression which allows simple manipulations such as integration \cite{Unser1992,Chui1992a}.
-This class of wavelets has been successfully applied in approximation schemes such as wavelet networks\cite{G.P.Liu2000,Jun2005} and wavelet based CML models \cite{Billings2006}.
-
-In this paper a multiresolution approximation of the IDE based on the model proposed in \cite{Dewar2009} is presented.
-B-spline scaling and wavelet functions are used to decompose both the kernel and the spatial field.
-Maximum likelihood estimates of the derived parametric state-space model are obtained using the EM-based algorithm of  \cite{Dewar2009}.
-In this model, the kernel and the spatio-temporal dynamics of the field are viewed at different spatial scales.
-Whereas in \cite{Scerri2009} different spatial scales were examined and one chosen, the work presented herein represents the system at a number of different spatial scales concurrently.
-% - a property that the alternative models described above do not typically share.
-% Gaussian Radial Basis Functions have been used by  to identify the appropriate scale for the IDE to represent the underlying spatio-temporal dynamic however not in a MRA framework.
-
-  The rest of this paper is set out as follows: in Section 2, the IDE model is briefly reviewed and the MRA of the IDE is presented.
-Section 3 introduces the B-spline wavelet IDE model and provides necessary formulation  to construct such a model in state-space.
-Section 4 briefly reviews the EM-based approach for parameter and state estimation.
-In Section 5, synthetic examples are given to demonstrate the ability of the developed MRA model in estimation of the hidden spatio-temporal field and the spatial mixing kernel.
-Finally conclusions are drawn in Section 6.
+% \IEEEPARstart{C}{omplex}
 
@@
 % stfloats package.
+\section{Integro-Difference Equation Neural Field Model}
+The stochastic  integro-difference equation (IDE) form of the model based on the Wilson-Cowan \cite{Wilson1973} or Amari neural field \cite{Amari1977} formulation is given by (cite NeuroImage paper)
+\begin{equation}\label{DiscreteTimeModel} 
+	v_{t+T_s}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \int_\Omega { 
+	    w\left(\mathbf{r},\mathbf{r'}\right)
+	    f\left(v_t\left(\mathbf{r}'\right)\right) 
+	\, d\mathbf{r}'} 
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
+where the local post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$, parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$ where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
+The spatial connectivity between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$, for an isotropic and homogeneous neural field.
+The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function $f\left(.\right)$.
+The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
+Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
+\begin{equation}
+	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
+		0, & v_t(\mathbf{r}') \le v_1 \\
+		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
+		1, & v_t(\mathbf{r}') \ge v_2 \\ 
+		\end{array}\right.
+\end{equation}
+where the parameter $\varsigma$ governs the slope of the sigmoid. Furthermore, we assume the field is in the linear region of the piecewise function giving
+\begin{equation}\label{DiscreteTimeModel} 
+	v_{t+1}\left(\mathbf{r}\right) = 
+	\xi v_t\left(\mathbf{r}\right) + 
+	T_s \varsigma\int_\Omega { 
+	    w\left(\mathbf{r}-\mathbf{r'}\right)
+	    v_t\left(\mathbf{r}'\right) 
+	\, d\mathbf{r}'} 
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
+For simplicity, 
 \section{MRA of the IDE in State-Space}

### 2011-02-14 Multiresolution_framework/ltx/manuscript.tex
added observation equation

@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function $f\left(.\right)$.
-The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
+The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+For simplicity, we denote hereafter the current time step by $t$ and the future time step by $t+1$.
 Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
@@
 \end{equation}
-For simplicity, 
+observation equation is given by 
+\begin{equation}\label{eq:ObservationEquation}
+	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
+\end{equation}
+where electrophysiological recordings $\mathbf{y}_{t}=[y_t(\mathbf{r}_1) y_t(\mathbf{r}_2)\cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$ via the observation kernel  $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$, is corrupted by an i.i.d normally distributed zero-mean white noise $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ with $\mathbf{\Sigma}_{\epsilon}=\sigma_{\epsilon}^2\mathbf I_{n_y} $.
+The superscript $\top$ denotes the transpose operator.
 \section{MRA of the IDE in State-Space}
-The spatially homogeneous, linear IDE is given by
-\begin{equation}
- z_{t+1}\left(\mathbf{s}\right)=\int_{\mathcal{S}}k\left(\mathbf{s}-\mathbf{r}\right)z_{t}\left(\mathbf{r}\right)d\mathbf{r}+e_{t}\left(\mathbf{s}\right)
-\label{eq:ConvolutionIntegral}
-\end{equation}
-where $t\in \mathbb{Z}_0 $ denotes discrete time, $\mathbf{s},\mathbf{r} \in \mathcal{S} \subset \mathbb{R}^{n_\mathcal{S}}$ are spatial locations in $n_{\mathcal S}$-dimensional physical space, where $n_{\mathcal S} \in \left\lbrace 1,2,3 \right\rbrace $.
-The continuous spatial field at time $t$ and at location $\mathbf s$ is denoted $z_t\left(\mathbf s\right)$.
-The model dynamics  are defined by the homogeneous time invariant spatial mixing kernel, $k\left(\mathbf{s}-\mathbf{r}\right):\mathbb{R}^{n_\mathcal{S}}\rightarrow \mathbb{R}$ which maps the current spatial field to the next spatial field via the integral (\ref{eq:ConvolutionIntegral}) and $e_t(\mathbf s)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$.
-Here $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}.
-The spatial field is observed by
-\begin{equation}
- \mathbf{y}_{t}=\mathbf{z}_{t}+\mathbf{v}_t
-\label{eq:observation equation}
-\end{equation}
-where the observation vector $\mathbf{y}_{t}=[y_t(\mathbf{s}_1) y_t(\mathbf{s}_2)\cdots y_t(\mathbf{s}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise $\mathbf{v}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{v}\right)$ with $\mathbf{\Sigma}_{v}=\sigma_v^2\mathbf I_{n_y} $.
-It is assumed here that $\boldsymbol\Sigma_v$ and $\eta\left(\mathbf s-\mathbf r \right)$ are known.
-The superscript $\top$ denotes the transpose operator.
-
 Assuming $z_t(.)$ and $k(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the integral (\ref{eq:ConvolutionIntegral}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$.

### 2011-02-14 Multiresolution_framework/ltx/manuscript.tex
edits to MRA section

@@
 %    \documentclass[journal,a4paper]{IEEEtran}
-%     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
-     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
+     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
+%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
 %         \topmargin       -6.0mm
@@
 The stochastic  integro-difference equation (IDE) form of the model based on the Wilson-Cowan \cite{Wilson1973} or Amari neural field \cite{Amari1977} formulation is given by (cite NeuroImage paper)
-\begin{equation}\label{DiscreteTimeModel} 
+\begin{equation}
 	v_{t+T_s}\left(\mathbf{r}\right) = 
@@
 Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
-\begin{equation}
+\begin{equation}\label{DiscreteTimeModel} 
 	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
@@
 \section{MRA of the IDE in State-Space}
-Assuming $z_t(.)$ and $k(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the integral (\ref{eq:ConvolutionIntegral}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$.
+Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$.
 For the one-dimensional kernel this is given by,
 \begin{equation}
- k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(s-r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(s-r\right) 
+ w\left(r-r'\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(r-r'\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(r-r'\right) 
 \label{eq:KernelExpansion}
 \end{equation}
-In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(s\right)=2^{\frac{j}{2}}\phi\left(2^js-l\right) $ and $\psi_{j,l}\left(s\right)=2^{\frac{j}{2}}\psi\left(2^js-l\right)$.
+In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$.
 Integers $j$ and $l$ are called scale and translation parameters accordingly.
@@
 \begin{equation}
- z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(s\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(s\right)
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(r\right)
 \label{eq:FieldExpansion}
@@
 \begin{equation}
- \phi_{j,\mathbf{l}}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)
+ \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
 \label{eq:2Dscalingfunction}
 \end{equation}
-and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right)$ where $n=1,2,3$ as
-\begin{equation}
- \psi_{j,\mathbf{l}}^{(1)}\left(s_1,s_2\right)=\phi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)
+and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as
+\begin{equation}
+ \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
 \label{eq:2Dwavelet_1}
@@
 \begin{equation}
- \psi_{j,\mathbf{l}}^{(2)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right)
+ \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
 \label{eq:2Dwavelet_2}
@@
 \begin{equation}
- \psi_{j,\mathbf{l}}^{(3)}\left(s_1,s_2\right)=\psi_{j,l_1}\left(s_1\right)\psi_{j,l_2}\left(s_2\right)
+ \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
 \label{eq:2Dwavelet_3}
@@
 \begin{eqnarray}
-  \phi_{j,\mathbf{l}}\left(s_1,s_2, \cdots s_d\right)&=&\phi_{j,l_1}\left(s_1\right)\phi_{j,l_2}\left(s_2\right) \cdots \phi_{j,l_d}\left(s_d\right) \label{eq:d-dimensionalscalingfunction}\\
+  \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\
  &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
@@
 \setlength{\arraycolsep}{5pt}
-and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{s}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
+and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
 Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by
@@
 \begin{eqnarray}
- k\left(\mathbf{s}-\mathbf{r}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{s}-\mathbf{r}\right) \nonumber \\
-&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}-\mathbf{r}\right) 
+ k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
+&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 
 \label{eq:MultidimensionalKernelExpansion}
@@
 \begin{equation}
-z_t\left(\mathbf{s}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{s}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{s}\right)
+z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)
 \label{eq:MultidimensionalFieldExpansion}
@@
  \begin{equation}
- k\left(\mathbf{s}-\mathbf{r}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{s}-\mathbf{r}\right)
+ w\left(\mathbf{r}-\mathbf{r'}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
 \label{eq:KernelFiniteExpansion}
@@
 \begin{equation}
- z_t\left(\mathbf{s}\right)\approx\boldsymbol\mu\left(\mathbf{s}\right)^\top\mathbf{x}_t
+ v_t\left(\mathbf{r}\right)\approx\boldsymbol\mu\left(\mathbf{r}\right)^\top\mathbf{x}_t
 \label{eq:FieldFiniteExpansion}
@@
 \begin{eqnarray}
- \boldsymbol\lambda^\top(\mathbf s-\mathbf r)&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s-\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s-\mathbf r) \right.
+ \boldsymbol\lambda^\top(\mathbf r-\mathbf r')&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right.
 \nonumber \\
@@
 \begin{equation}
- \boldsymbol\mu^\top(\mathbf s)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0}^\top(\mathbf s) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf s) \cdots \boldsymbol\psi_{j}^\top(\mathbf s) \right]
+ \boldsymbol\mu^\top(\mathbf r)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r) \cdots \boldsymbol\psi_{j}^\top(\mathbf r) \right]
 \label{FieldBasisVector}

### 2011-02-15 Multiresolution_framework/ltx/manuscript.tex
edits to MRA section

@@
  % TO DELETE
-\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
-\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
-%    \documentclass[journal,a4paper]{IEEEtran}
-     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
+
+    \documentclass[journal,a4paper]{IEEEtran}
+ %    \documentclass[10pt,twocolumn,twoside]{IEEEtran}
 %     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
@@
 %         \textwidth      170.0mm
+
+\usepackage{color}
+\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
+\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
 
@@
 \section{MRA of the IDE in State-Space}
-Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$.
+Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 For the one-dimensional kernel this is given by,
@@
 In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.
-
+\parham{Mike you can add state-space derivation using Galerkin projection here.}
 % however it can be tailored to capture underlying dynamics with desired accuracy for a sufficiently large value of $j$, a value between zero and three is usually sufficient in many applications \cite{Wei2006}.

### 2011-02-22 Multiresolution_framework/ltx/manuscript.tex
added state space representation of the model

@@
 Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
-\begin{equation}\label{DiscreteTimeModel} 
+\begin{equation}\label{eq:PiecewiseSigmoid} 
 	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
@@
 	\xi v_t\left(\mathbf{r}\right) + 
-	T_s \varsigma\int_\Omega { 
+	T_s \int_\Omega { 
 	    w\left(\mathbf{r}-\mathbf{r'}\right)
@@
 \end{equation}
-observation equation is given by 
+Note that the parameter $\varsigma$ is absorbed into the kernel for simplicity. Oservation equation is given by 
 \begin{equation}\label{eq:ObservationEquation}
@@
 In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.
+
+To derive the state-space representation of the model we substitute decompositions \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} into equation \eqref{DiscreteTimeModel} and then cross-multiply the decomposed model by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the spatial domain, $\Omega$, giving
+\begin{align}\label{eq:DecomposedModel2} 
+	&\int_{\Omega} \boldsymbol\mu  \left(\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top  d\mathbf{r}\mathbf{x}_{t+1}= 
+	\xi\int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top d\mathbf{r}\mathbf{x}_t \nonumber \\
+	&+T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \int_\Omega { 
+	   \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
+	    \boldsymbol\mu^\top\left(\mathbf{r'}\right)\mathbf{x}_t 
+	\, d\mathbf{r}'d\mathbf{r}}
+	+ \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}, 
+\end{align}
+Now defning 
+\begin{equation}\label{eq:Lambdax}
+ \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) d\mathbf{r}
+\end{equation}
+\begin{equation}\label{eq:Lambdatheta}
+ \mathbf{\Lambda}_{\theta}\triangleq\int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \int_\Omega { 
+	   \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
+	    \boldsymbol\mu^\top\left(\mathbf{r'}\right)\mathbf{x}_t 
+	\, d\mathbf{r}'d\mathbf{r}}
+\end{equation}
+and substituting these into \eqref{eq:DecomposedModel2} and cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
+\begin{equation}\label{eq:StateEquation}
+ \mathbf x_{t+1}=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t
+\end{equation}
+where
+\begin{equation}\label{eq:A_theta}
+ \mathbf A(\boldsymbol \theta)=(T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I)
+\end{equation}
+and $\mathbf I$ is the identity matrix, and 
+\begin{equation}\label{eq:Disturbance}
+\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}
+\end{equation}
+which is a vector valued, zero-mean normally distributed white noise process with covariance \cite{Scerri2009}
+\begin{equation}
+\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\eta\left(\mathbf{r}-\mathbf{r'}\right)\boldsymbol\mu^{\top}\left(\mathbf{r'}\right)d\mathbf{r'}d\mathbf{r}\mathbf{\Lambda}_{x}^{-\top}.
+\end{equation}
+Similarly, the observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
+ into equation \eqref{eq:ObservationEquation} giving
+\begin{equation}\label{ObservationEquation} 
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+\end{equation}
+where each element of the observation matrix is 
+\begin{equation}
+	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\mu}_j(\mathbf{r}') \, d\mathbf{r}'.
+\end{equation}
+
 \parham{Mike you can add state-space derivation using Galerkin projection here.}
-% however it can be tailored to capture underlying dynamics with desired accuracy for a sufficiently large value of $j$, a value between zero and three is usually sufficient in many applications \cite{Wei2006}.
-Note that number of translation parameters is always finite and depends on the range of measured data.
-
-The state-space representation of the spatio-temporal IDE proposed in \cite{Dewar2009} is derived for an arbitrary set of basis functions and hence this derivation can be applied using scaling and wavelet basis functions.
-Let
-\begin{equation}
- \mathbf{\Lambda}_{x}=\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\boldsymbol\mu\left(\mathbf{s}\right)^\top d\mathbf{s}
-\label{eq:ConstructionIntegral1}
-\end{equation}
-\begin{equation}
- \mathbf{\Lambda}_{\theta}=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\boldsymbol\theta^\top \boldsymbol\lambda\left(\mathbf{s-r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top d\mathbf{r}d\mathbf{s}
-\label{eq:ConstructionIntegral2}
-\end{equation}
-where $\boldsymbol\Lambda_{x}, \boldsymbol\Lambda_{\theta} \in \mathbb{R}^{n_x \times n_x}$.
-The spatial IDE model in (\ref{eq:ConvolutionIntegral}) and (\ref{eq:observation equation}) can be represented as linear state-space model of the form
-\begin{equation}
- \mathbf{x}_{t+1}=\mathbf{A}\left(\boldsymbol\theta\right)\mathbf{x}_t+\mathbf{w}_t
-\label{eq:StateEquation}
-\end{equation}
-\begin{equation}
-\mathbf{y}_t=\mathbf{C}\mathbf{x}_t+\mathbf{v}_t
-\label{eq:ObservationEquation}
-\end{equation}
-where 
-\begin{equation}
- \mathbf{A}\left(\boldsymbol\theta\right)=\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda_{\theta}}
-\label{eq:TransitionMatrix}
-\end{equation}
-and  \\ \\ 
-$\mathbf{C}=$
-$\begin{pmatrix}
-\boldsymbol\phi_{j_0}\left(\mathbf{s}_1\right) & \boldsymbol\phi_{j_0}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\phi_{j_0}\left(\mathbf{s}_{n_y}\right) \\
-\boldsymbol\psi_{j_0}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j_0}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j_0}\left(\mathbf{s}_{n_y}\right) \\
-\boldsymbol\psi_{j_0+1}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j_0+1}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j_0+1}\left(\mathbf{s}_{n_y}\right) \\
-\vdots & \vdots & \ddots& \vdots \\
-\boldsymbol\psi_{j}\left(\mathbf{s}_1\right) & \boldsymbol\psi_{j}\left(\mathbf{s}_2\right)  &\cdots &\boldsymbol\psi_{j}\left(\mathbf{s}_{n_y}\right) \\
-\end{pmatrix}^{\top}$ \\ \\
-\\ \\ and where 
-\begin{equation}
- \mathbf{w}_t=\mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)e_t\left(\mathbf{s}\right)d\mathbf{s}
-\label{CovofField}
-\end{equation}
- is a vector valued, zero-mean normally distributed white noise process with covariance given by (Lemma \ref{lemma:FieldCovariance}, Appendix)
-\begin{equation}
-\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{-\top}
-\end{equation}
-and
-\begin{equation}
- \boldsymbol\Pi=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf{s}\right)\eta\left(\mathbf{s}-\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^{\top}d\mathbf{r}d\mathbf{s}
-\label{eq:Pi}
-\end{equation}
 By substituting the  parameter vector $\boldsymbol\theta$, the  state vector $\mathbf{x_t}$, the vector of kernel basis functions $\boldsymbol\lambda$ and the vector of field basis functions $\boldsymbol\mu$ in (\ref{eq:ConstructionIntegral1}-\ref{eq:Pi}), the state-space representation of the multiresolution approximation of the IDE can be achieved.

### 2011-02-22 Multiresolution_framework/ltx/manuscript.tex
edits to  state space representation of the model

@@
 \end{equation}
-
+This completes the state-space representation of the multiresolution approximation of the neural field model. 
 \parham{Mike you can add state-space derivation using Galerkin projection here.}
-By substituting the  parameter vector $\boldsymbol\theta$, the  state vector $\mathbf{x_t}$, the vector of kernel basis functions $\boldsymbol\lambda$ and the vector of field basis functions $\boldsymbol\mu$ in (\ref{eq:ConstructionIntegral1}-\ref{eq:Pi}), the state-space representation of the multiresolution approximation of the IDE can be achieved.
-It should be noted that the complexity of the model is independent of the number of observation locations, providing more flexibility in handling high resolution data.
-%The model is also capable of being applicable to scenarios with irregular observation locations.
-
-% In practice, MRA can be implemented using different types of wavelet and scaling functions.
-Semi-orthogonal B-spline wavelets are compactly supported and optimally localised in time and frequency.
-This class of wavelets has been applied in approximation schemes such as wavelet networks\cite{G.P.Liu2000,Jun2005} and wavelet based CML models \cite{Billings2006}.
-
 \section{B-spline wavelet IDE model}

### 2011-02-22 Multiresolution_framework/ltx/manuscript.tex
added figures

@@
 
-\begin{algorithm}
-\caption{Ensemble Kalman smoother}
-\label{alg:EnKS}
-% \begin{tabbing}
-\begin{enumerate}
-\item Initialise:
-\begin{center}
- $\hat{\mathbf x}_0 $, $\mathbf P_0$  
-\end{center}
-\item
-for $t\in\left\lbrace 0, \dots, T\right\rbrace $, calculate the state ensembles $\hat{\mathbf X}_t$ and the model errors ensemble $\mathbf W_t$ and propogate through the state equation:
-\begin{equation*}
-\hat{\mathbf X}_{i,t+1}^f=\mathbf A \hat{\mathbf X}_{i,t}^a+\mathbf W_{i,t}
-\end{equation*}
-calculate the predicted state and the predicted covariance matrix
-\begin{equation*}
- \hat{\mathbf x}_{t+1}^f=\frac{1}{N}\sum_{i=1}^{N}\hat{\mathbf X}_{i,t+1}^f
-\end{equation*}
-\begin{equation*}
- \mathbf P_{t+1}^f=\frac{1}{N-1}\sum_{i=1}^{N}\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)^\top
-\end{equation*}
-\item
-compute $\mathbf X_4(t+1)$ and $\mathbf X_5(t+1)$ and the filtered state and the filtered covariance matrix:
-\begin{equation*}
- \mathcal K_t=\mathbf C^{\top}(\mathbf C\mathbf{P}_{t+1}^f\mathbf C^{\top}+\boldsymbol\Sigma_v)^{-1}
-\end{equation*}
-
-\begin{equation*}
- \mathbf X_4(t+1)=\frac{1}{N-1}\sum_{i=1}^{N}(\hat{\mathbf X}_{i,t+1}^f-\hat{\mathbf x}^f_{t+1} )^\top\mathcal K_t (\mathbf Y_{i,t+1}-\mathbf C\hat{\mathbf{X}}_{i,t+1}^f)
-\end{equation*}
-\begin{equation*}
- \mathbf X_5(t+1)= \mathbf I +\mathbf X_4(t+1)
-\end{equation*}
-\begin{equation*}
- \hat{\mathbf X}_{t+1}^a=\hat{\mathbf X}_{t+1}^f \mathbf X_5(t+1)
-\end{equation*}
-\item compute the smooth ensemble for $t\in\left\lbrace 0, \dots, T\right\rbrace $
-\begin{equation*}
- \hat{\mathbf{X}}_{t}^s=\hat{\mathbf X}_{t}^a \prod_{j=t+1}^{T}X_5(j)
-\end{equation*}
-\end{enumerate}
-% \end{tabbing}
-\end{algorithm}
-
 In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother can be employed to determine the posterior state sequence.
@@
 The response was sampled at 50 irregularly spaced random locations, at $t=1, \cdots 400 $.
-% \begin{figure}[!h] 
-% \centering
-% \includegraphics[width=0.5\textwidth]{./Graph/aram1.eps}
-% \caption{Multiresolution decomposition of a complex spatial mixing kernel (dark line) and the corresponding scaling and wavelet basis functions (light lines).}
-% \label{fig:SpatialMixingKernel}
-% \end{figure} 
+\begin{figure}[!h] 
+ \centering
+ \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
+ \caption{The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
+ \label{fig:FreqResponse}
+ \end{figure} 
+\begin{figure}[!h] 
+ \centering
+ \includegraphics[scale=1]{./Graph/Hist.pdf}
+ \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
+the solid lines show the actual parameter values and the dotted lines show the means of the estimated
+parameters. Left panel: The histogram of the central excitatory connectivity kernel basis function parameter
+estimates, $\theta_0$. Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter
+estimates, $\theta_1$.}
+ \label{fig:ParametersHistogram}
+ \end{figure} 
+\begin{figure}[!h] 
+ \centering
+ %\includegraphics[width=0.5\textwidth]{./Graph/RMSE.pdf}
+\includegraphics[scale=1]{./Graph/RMSE.pdf}
+ \caption{RMSE of the estimated field at different spatial resolution.}
+ \label{fig:RMSE}
+ \end{figure} 
+\begin{figure}[!h] 
+ \centering
+ \includegraphics[scale=1]{./Graph/Field.pdf}
+ \caption{Spatial field at one time instant for different spatial resolutions; estimated and true fields are
+shown by dashed and solid lines respectively.}
+ \label{fig:FreqResponse}
+ \end{figure}
+
 % \begin{figure}[!h] 
@@
 % \end{figure} 
-\subsection{Two dimensional example}
-In order to demonstrate the ability of the developed model in higher dimensions, a two dimensional IDE model with a single B-spline kernel $\phi_{4;0,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right) $ and $\mathbf l=[-2,-2]^ \top$ is used with parameter $\theta=1$.
-In this example spatial region $\mathcal{S}=[0,4]^2 $ is simulated over $t=\left\lbrace1 \cdots 200  \right\rbrace $ using $7$ scaling and wavelet functions at $j=0$ together with $24$ wavelet functions at $j=1$.
-Univariate cubic B-spline scaling and wavelet functions are used to generate 2-D basis functions using (\ref{eq:2Dscalingfunction}-\ref{eq:2Dwavelet_3}).
-A set of $250$ random  observation locations is used; $\mathbf{\Sigma}_v$ is taken the same as that in example 1 and $ \eta\left(s_1-r_1,s_2-r_2\right) =2.5\times\phi_{4,3,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right)$ where $\mathbf l=[-2,-2]^ \top$.
-The histogram of the parameter estimates  in \figurename{\ref{fig:2DHist} is generated using 500 runs of the EM algorithm.
-For comparison, snapshots for the original and the corresponding coarse and fine field estimates at time instants 5, 50 and 150 are illustrated in \figurename{\ref{fig:2DFieldEstimation1}-\ref{fig:2DFieldEstimation3}}.
-In addition, the MISE of the dynamic field at some time instants are presented in Table \ref{table:ValidationResultField}.
-This shows that the multiresolution IDE model can estimate the spatio-temporal dynamics of the original system accurately.
-The accuracy of the estimation remains consistent over time.
-Performance is improved significantly at $j=1$ compared to the case where $j=0$.
-% \begin{figure}[!t] 
-% \centering
-% \includegraphics[width=0.5\textwidth]{./Graph/aram5.eps}
-% \caption{Distribution of the parameter estimate for 2-D Example over 500 runs of the EM algorithm. The dotted line indicates the true parameter.}
-% \label{fig:2DHist}
-% \end{figure}
-% \begin{figure*}[!th] 
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6a.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6b.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6c.eps}}\\ 
-% \caption{Spatial field at t=5; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-% \label{fig:2DFieldEstimation1}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7a.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7b.eps}} 
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7c.eps}}\\
-% \caption{Spatial field at t=50; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-% \label{fig:2DFieldEstimation2}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8a.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8b.eps}} 
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8c.eps}}
-% \caption{Spatial field at t=150; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
-% \label{fig:2DFieldEstimation3}
-% \end{figure*}
 \begin{table}[!h]
@@
 \begin{lemma}
-Consider the zero-mean process $e_t\left(s\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then
-\begin{equation}
- \mathbf{w}_t=\mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)e_t\left(\mathbf{s}\right)d\mathbf{s}
-\label{eq:AppendixWt}
-\end{equation}
-is a vector valued, zero mean normally distributed white noise process with covariance
-\begin{equation}
-\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
-\end{equation}
-and
-\begin{equation}
- \boldsymbol\Pi=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)\eta\left(\mathbf s-\mathbf r\right)\boldsymbol\mu\left(\mathbf r\right)^\top d\mathbf{r}d\mathbf{s}
-\end{equation}
-\label{lemma:FieldCovariance}
-\end{lemma}
-\begin{IEEEproof}
- Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf s)$ and hence $\mathbf{w}_t$ is also normally distributed. The expected value of $\mathbf w_t$ is given by 
-\begin{eqnarray}
- \mathbf E\left[ \mathbf w_t\right]&=& \mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)\mathbf E\left[e_t\left(\mathbf{s}\right)\right] d\mathbf{s} \nonumber \\
-&=&0
-\end{eqnarray}
-and 
-\begin{eqnarray}
-\mathbf \Sigma_w&{}={}&\mathbf E[ \mathbf w_t \mathbf w_{t}^{\top}]\nonumber\\
-&=& \mathbf{\Lambda}_{x}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Lambda}_{x}^{- \top} \nonumber \\
-&=&\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
-&=&{}\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \eta\left(\mathbf s- \mathbf r \right)\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
-&=&\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
-\end{IEEEproof}
-\begin{lemma}
 Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively.
@@
 \end{IEEEproof}
-\section*{Reducing the computational complexity}\label{App:ReducedRTS}
-The state-space representation of the spatio-temporal IDE \eqref{eq:StateEquation} and \eqref{eq:ObservationEquation} has a quadratic $\mathcal Q$-function in a form of \cite{Dewar2009}
-\begin{equation}
-\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)=2 \boldsymbol\theta^\top\boldsymbol\upsilon -\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta
-\label{eq:QFunction}
-\end{equation}
-which has a maximum at
-\begin{equation}
- \boldsymbol\theta=\boldsymbol\Upsilon^{-1}\boldsymbol\upsilon
-\end{equation}
-where
-\begin{equation}\label{eq:Upsilon}
- \boldsymbol\Upsilon=\sum_{i,j,k,m=1}^{n_x}\left[ \Xi_1\right] _{ij}\boldsymbol\gamma^{\left(k,j\right)}\left[\boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1} \boldsymbol\Lambda_{x}^{-1}\right]_{km} \boldsymbol\gamma^{\left(m,i\right)\mathsf{T}}
-\end{equation}
-and
-\begin{equation}
- \boldsymbol \upsilon=\sum_{i,j=1}^{n_x}\left[\Xi_0\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1} \right]_{ij}\boldsymbol\gamma^{\left(j,i\right)} 
-\end{equation}
-where
-\begin{equation}
- \boldsymbol\gamma^{(i,j)}=\int_{\mathcal S}\left[ \mu(s)\right]_i\left[ \mathbf M(s)\right] _{:j}ds
-\end{equation}
-and $\left[ \mathbf M(s)\right] _{:j}$ denotes the $j$th column of $\mathbf M(s)$.
-The definitions of the $\Xi_0$ and $\Xi_1$ are the same as in \cite{Dewar2009}.
-Note that constant values with respect to $\boldsymbol \theta$ are ignored in \eqref{eq:QFunction}.
-We define $n_x \times n_x$ block matrix $\mathbf U$ such that
-\begin{equation}\label{eq:UMatrix}
- [\mathbf U]_{i,j}=\boldsymbol\gamma^{(i,j)\mathsf{T}}
-\end{equation}
-substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we get
-\begin{equation}\label{eq:UpsilonU}
- \boldsymbol\Upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}
-\end{equation}
-and similarly substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we have
-\begin{equation}\label{eq:upsilonU}
- \boldsymbol\upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}
-\end{equation}
-with this substitution the second terms in \eqref{eq:UpsilonU} and \eqref{eq:upsilonU} can be pre-calculated and stored.
-This lowers the comutational complexity of the estimation algorithm and provides a dramatic increase in estimation speed.
-\section*{Cross covariance matrix}\label{App:EnCrossCov}
 

### 2011-02-23 Multiresolution_framework/ltx/manuscript.tex
deleted extra files

@@
 \end{equation}
-Note that the parameter $\varsigma$ is absorbed into the kernel for simplicity. Oservation equation is given by 
+Note that the parameter $\varsigma$ is absorbed into the kernel for simplicity. Observation equation is given by 
 \begin{equation}\label{eq:ObservationEquation}
@@
 where $ x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$.
-A  two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up  using the tensor-product approach \cite{Meyer1992,Mallat1998}. We write the 2-D scaling function as
-\begin{equation}
- \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
-\label{eq:2Dscalingfunction}
-\end{equation}
-and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as
-\begin{equation}
- \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
-\label{eq:2Dwavelet_1}
-\end{equation}
-\begin{equation}
- \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
-\label{eq:2Dwavelet_2}
-\end{equation}
-\begin{equation}
- \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
-\label{eq:2Dwavelet_3}
-\end{equation}
-for $j \in \mathbb{Z}$ and, $\mathbf{l} \in \mathbb{Z}^2$, where $\psi_{j,\mathbf{l}}^{(1)},  \psi_{j,\mathbf{l}}^{(2)}$ and $\psi_{j,\mathbf{l}}^{(3)} $ extract fine features of the 2-D field at vertical, horizontal and diagonal orientations respectively.
-This can be generalised to $d$-dimensional MRA by introducing the scaling function
-\setlength{\arraycolsep}{0.0em}
-\begin{eqnarray}
-  \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\
- &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
-and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
+% A  two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up  using the tensor-product approach \cite{Meyer1992,Mallat1998}. We write the 2-D scaling function as
+% \begin{equation}
+%  \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dscalingfunction}
+% \end{equation}
+% and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_1}
+% \end{equation}
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_2}
+% \end{equation}
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_3}
+% \end{equation}
+% for $j \in \mathbb{Z}$ and, $\mathbf{l} \in \mathbb{Z}^2$, where $\psi_{j,\mathbf{l}}^{(1)},  \psi_{j,\mathbf{l}}^{(2)}$ and $\psi_{j,\mathbf{l}}^{(3)} $ extract fine features of the 2-D field at vertical, horizontal and diagonal orientations respectively.
+% This can be generalised to $d$-dimensional MRA by introducing the scaling function
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+%   \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\
+%  &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
 Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by
-\setlength{\arraycolsep}{0.0em}
-\begin{eqnarray}
- k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
-&+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 
-\label{eq:MultidimensionalKernelExpansion}
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
-\begin{equation}
-z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)
-\label{eq:MultidimensionalFieldExpansion}
-\end{equation}
-Equations (\ref{eq:MultidimensionalKernelExpansion}) and (\ref{eq:MultidimensionalFieldExpansion}) are infinite series expansions.
-For practical implementation, (\ref{eq:MultidimensionalKernelExpansion}) and (\ref{eq:MultidimensionalFieldExpansion}) must be truncated at some level $j$, therefore we have
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+%  k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
+% &+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 
+% \label{eq:MultidimensionalKernelExpansion}
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \begin{equation}
+% z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)
+% \label{eq:MultidimensionalFieldExpansion}
+% \end{equation}
+Equations \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions.
+For practical implementation,  \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} must be truncated at some level $j$, therefore we have
  \begin{equation}
@@
 Each vector of basis functions on the right hand-side of (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in a way similar to their corresponding weight vectors in (\ref{KernelWeights}) and (\ref{FieldWeights}).
-Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales.
+% Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales.
 In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.
@@
 This completes the state-space representation of the multiresolution approximation of the neural field model. 
-\parham{Mike you can add state-space derivation using Galerkin projection here.}
+% \parham{Mike you can add state-space derivation using Galerkin projection here.}
 \section{B-spline wavelet IDE model}
@@
 \begin{equation}
- N_{m}\left(s\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(s\right)
+ N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right)
 \end{equation}
@@
 \setlength{\arraycolsep}{0.0em}
+\begin{align}\label{eq:BsplineConvolution}
+N_{m}\left( r\right) \ast N_{m'}\left(r\right)&=\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(r\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(r\right)\nonumber\\
+&=N_{m+m'}\left(r\right)
+\end{align}
+A direct consequence of \eqref{eq:BsplineConvolution} is 
 \begin{eqnarray}
-N_{m}\left(s\right) \ast N_{m'}\left(s\right)&=&\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(s\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(s\right)\nonumber\\
-&=&N_{m+m'}\left(s\right)
-\label{eq:BsplineConvolution}
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
-This result can be used to show that (Lemma \ref{lemma:InProduct}, Appendix)
-\setlength{\arraycolsep}{0.0em}
-\begin{eqnarray}
- \left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
+ \left\langle N_{m}\left(r-l_{1}\right), N_{m'}\left(r-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
 &=&N_{m+m'}\left(m'+l_{2}-l_{1}\right)
@@
 \end{eqnarray}
-\setlength{\arraycolsep}{5pt}
 where $\left\langle  .,.\right\rangle $ denotes the inner product.
@@
 \end{equation}
-Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.
+% Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.
 In the two dimensional case, the convolution integral can be factorised as follows, e.g.
-\setlength{\arraycolsep}{0.14em}
-\begin{IEEEeqnarray}{!l l }
- \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right)\ast \psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)&=\left[\phi_{m;j,l_1}\left(s_{1}\right)\ast\phi_{m;j,l'_1}\left(s_{1}\right)\right] \nonumber \\
-&\times \left[ \phi_{m;j,l_2}\left(s_{2}\right) \ast \psi_{m;j,l'_2}\left(s_{2}\right)\right] \nonumber \\
-&
-\end{IEEEeqnarray}
-\setlength{\arraycolsep}{5pt}
-The preceding factorisation can be also applied to the 2D-inner product integral. Non-zero quantities can  be then expressed by
-\setlength{\arraycolsep}{0.14em}
-\begin{IEEEeqnarray}{!l l }
-\left\langle \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\phi_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle &=\left\langle \phi_{m;j,l_1}\left(s_{1}\right),\phi_{m;j,l'_1}\left(s_{1}\right)\right\rangle \nonumber \\
-& \times\left\langle \phi_{m;j,l_2}\left(s_{2}\right) , \phi_{m;j,l'_2}\left(s_{2}\right)\right\rangle \nonumber \\
-&
-\end{IEEEeqnarray}
-\setlength{\arraycolsep}{5pt}
-likewise we can compute 
-$\left\langle  \psi^{1}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$
-, \\
-$\left\langle  \psi^{2}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{2}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$ and \\
-$
-\left\langle \psi^{3}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right), \psi^{3}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle $. \\ \\
-Using these expansions it becomes straightforward to calculate the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}).
+% \setlength{\arraycolsep}{0.14em}
+% \begin{IEEEeqnarray}{!l l }
+%  \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right)\ast \psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)&=\left[\phi_{m;j,l_1}\left(s_{1}\right)\ast\phi_{m;j,l'_1}\left(s_{1}\right)\right] \nonumber \\
+% &\times \left[ \phi_{m;j,l_2}\left(s_{2}\right) \ast \psi_{m;j,l'_2}\left(s_{2}\right)\right] \nonumber \\
+% &
+% \end{IEEEeqnarray}
+% \setlength{\arraycolsep}{5pt}
+% The preceding factorisation can be also applied to the 2D-inner product integral. Non-zero quantities can  be then expressed by
+% \setlength{\arraycolsep}{0.14em}
+% \begin{IEEEeqnarray}{!l l }
+% \left\langle \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\phi_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle &=\left\langle \phi_{m;j,l_1}\left(s_{1}\right),\phi_{m;j,l'_1}\left(s_{1}\right)\right\rangle \nonumber \\
+% & \times\left\langle \phi_{m;j,l_2}\left(s_{2}\right) , \phi_{m;j,l'_2}\left(s_{2}\right)\right\rangle \nonumber \\
+% &
+% \end{IEEEeqnarray}
+% \setlength{\arraycolsep}{5pt}
+% likewise we can compute 
+% $\left\langle  \psi^{1}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$
+% , \\
+% $\left\langle  \psi^{2}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{2}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$ and \\
+% $
+% \left\langle \psi^{3}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right), \psi^{3}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle $. \\ \\
 In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
@@
 It can be shown that \cite{Dempster1977,Gibsona2005} every EM iteration increases the lower bound on the likelihood function and hence improving the state and parameter estimates.
-The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
-The stopping rule adopted herein is
-\begin{equation}
-\left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\varepsilon 
-\end{equation}
-where $\varepsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norm  of the successive estimates of $\mathbf{A} $ matrices.
-It has been shown \cite{Dewar2009} that the state dimension is a critical factor in the complexity of the estimation procedure, however using the above decomposition, this is decoupled from the number of observation locations.
 % The complexity of this algorithm is $O\left(n_{x}^2n_{\theta}^2\right)+O \left(Tn_{x}^{3}\right)+O\left(Tn_{y}^3\right) $ showing that
@@
  Consider the following homogeneous multiscale spatial mixing kernel 
-\setlength{\arraycolsep}{0.0em}
-\begin{eqnarray}
-k\left(s-r\right)&=& -\phi_{4;0,-3}\left(s-r\right)+\phi_{4;0,-2}\left(s-r\right)\nonumber\\
-&&{-}\:0.5\psi_{4;1,-6}\left(s-r\right)+0.5\psi_{4;1,-3}\left(s-r\right)
-\label{eq:1DSimulationKernel}
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+% k\left(s-r\right)&=& -\phi_{4;0,-3}\left(s-r\right)+\phi_{4;0,-2}\left(s-r\right)\nonumber\\
+% &&{-}\:0.5\psi_{4;1,-6}\left(s-r\right)+0.5\psi_{4;1,-3}\left(s-r\right)
+% \label{eq:1DSimulationKernel}
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
 The kernel and its decomposition are plotted in  \figurename{\ref{fig:SpatialMixingKernel}}.
@@
  \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
- \caption{The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
+ \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
+functions (dashed lines), representing local excitation and lateral inhibition.
+(b) The average (over time) power in dB of the spatial frequency of the observations generated by the kernel in (a).
+The dashed line shows the cutoff frequency (-3 dB point).}
  \label{fig:FreqResponse}
@@
  \includegraphics[scale=1]{./Graph/Field.pdf}
- \caption{Spatial field at one time instant for different spatial resolutions; estimated and true fields are
-shown by dashed and solid lines respectively.}
+ \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are
+shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
  \label{fig:FreqResponse}
@@
 In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
-\begin{equation}
- k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
-\label{1DKernelDecompositionForSimulation}
-\end{equation}
-\begin{equation}
- z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
-\label{1DFieldDecompositionForSimulation}
-\end{equation}
+% \begin{equation}
+%  k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
+% \label{1DKernelDecompositionForSimulation}
+% \end{equation}
+% \begin{equation}
+%  z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
+% \label{1DFieldDecompositionForSimulation}
+% \end{equation}
 Note that the number of translation operations depends on the spatial range of the data.
@@
 % \end{figure} 
-\begin{table}[!h]
-\renewcommand{\arraystretch}{1.3}
-\caption {MISE  at particular scale between measured and estimated 2D-field  at a particular time}
-\label{table:ValidationResultField}
-\centering
-\begin{tabular}{cccc}
-\hline \hline
-\multicolumn{2}{r}{Time}&\multicolumn{2}{c}{MISE} \\
-\cline{3-4}
-&&$j=0$&$j=1$ \\ 
-\hline 
-&$5$ &$5.424$&$0.609$ \\
-&$20$ &$5.422$&$0.596$ \\
-&$50$ &$5.519$&$0.626$ \\
-&$100$ &$5.488$&$0.611$ \\
-&$150$ &$5.494$&$0.587$ \\
-\hline \hline
-\end{tabular}
-\end {table}
-\section{Conclusion}
-A multi-resolution approach to modelling spatio-temporal systems has been presented.
+% \begin{table}[!h]
+% \renewcommand{\arraystretch}{1.3}
+% \caption {MISE  at particular scale between measured and estimated 2D-field  at a particular time}
+% \label{table:ValidationResultField}
+% \centering
+% \begin{tabular}{cccc}
+% \hline \hline
+% \multicolumn{2}{r}{Time}&\multicolumn{2}{c}{MISE} \\
+% \cline{3-4}
+% &&$j=0$&$j=1$ \\ 
+% \hline 
+% &$5$ &$5.424$&$0.609$ \\
+% &$20$ &$5.422$&$0.596$ \\
+% &$50$ &$5.519$&$0.626$ \\
+% &$100$ &$5.488$&$0.611$ \\
+% &$150$ &$5.494$&$0.587$ \\
+% \hline \hline
+% \end{tabular}
+% \end {table}
+% \section{Conclusion}
+% A multi-resolution approach to modelling spatio-temporal systems has been presented.
 This model is able to represent continuous-space, discrete-time dynamics at a number of spatial scales simultaneously.
 This ability greatly extends the class of system which the Integro-Difference Equation can represent.
-
-By decomposing both the spatial field and the spatial mixing kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
+% 
+% 
+% By decomposing both the spatial field and the spatial mixing kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
 This is an essential component of any practical spatio-temporal model, without which the model must be artificially separated into global and local modes a-priori.
-
-The complexity of the model is not affected by the spatial resolution of the observation process, rather it reflects the underlying complexity of the system under study.
+% 
+% 
+% The complexity of the model is not affected by the spatial resolution of the observation process, rather it reflects the underlying complexity of the system under study.
 Therefore, increasing the resolution at which the system is observed does not necessarily increase the complexity of the system identification problem.
 However the developed algorithm is sensitive to the state dimension, equivalent to the detail represented in the field, and hence intelligent approaches to reduce the number of basis functions is noted as future work.
-
-By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework.
+% 
+% By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework.
 Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
@@
 % or
-\appendix  % for no appendix heading
+% \appendix  % for no appendix heading
 % do not use \section anymore after \appendix, only \section*
@@
 %
-\newtheorem{lemma}{Lemma}
-\begin{lemma}
-Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively.
+% \newtheorem{lemma}{Lemma}
+% \begin{lemma}
+% Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively.
 Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by
-\setlength{\arraycolsep}{0.0em}
-\begin{eqnarray}
-\left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
-&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
-\end{eqnarray}
-\setlength{\arraycolsep}{5pt}
-\label{lemma:InProduct}
-\end{lemma}
-\begin{IEEEproof}
-The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
-\begin{equation}
- N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
-\label{SymmetrySplieEq}
-\end{equation}
-A direct consequence of (\ref{SymmetrySplieEq}) is 
-\begin{equation}
- N_{m}\left(s\right)=N_{m}\left(m-s\right)
-\end{equation}
-Therefore
-\setlength{\arraycolsep}{0.0em}
-\begin{IEEEeqnarray}{l}
-\int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
-\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
-\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
-\qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
-\qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
-\qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
-\end{IEEEeqnarray}
-\setlength{\arraycolsep}{5pt}
-\end{IEEEproof}
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+% \left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
+% &=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \label{lemma:InProduct}
+% \end{lemma}
+% \begin{IEEEproof}
+% The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
+% \begin{equation}
+%  N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
+% \label{SymmetrySplieEq}
+% \end{equation}
+% A direct consequence of (\ref{SymmetrySplieEq}) is 
+% \begin{equation}
+%  N_{m}\left(s\right)=N_{m}\left(m-s\right)
+% \end{equation}
+% Therefore
+% \setlength{\arraycolsep}{0.0em}
+% \begin{IEEEeqnarray}{l}
+% \int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
+% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
+% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
+% \qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
+% \qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
+% \qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
+% \end{IEEEeqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \end{IEEEproof}
 

### 2011-02-23 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 where the parameter $\varsigma$ governs the slope of the sigmoid. Furthermore, we assume the field is in the linear region of the piecewise function giving
-\begin{equation}\label{DiscreteTimeModel} 
+\begin{equation}\label{eq:DiscreteTimeModel} 
 	v_{t+1}\left(\mathbf{r}\right) = 
@@
 \section{MRA of the IDE in State-Space}
-Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
+Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{eq:DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 For the one-dimensional kernel this is given by,
@@
 
-To derive the state-space representation of the model we substitute decompositions \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} into equation \eqref{DiscreteTimeModel} and then cross-multiply the decomposed model by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the spatial domain, $\Omega$, giving
+To derive the state-space representation of the model we substitute decompositions \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} into equation \eqref{eq:DiscreteTimeModel} and then cross-multiply the decomposed model by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the spatial domain, $\Omega$, giving
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \section{Simulation}
-In this section, we compare the performance of the different algorithms mentioned above on a synthetic example .....This section demonstrates the identification of the proposed IDE model.
-Primarily, the MRA of a synthetic model is demonstrated, which is able to represent the system at different spatial scales.
-In addition, the complexity of the field decomposition is shown to be independent to the number and spatial regularity of the observation locations.
-This allows the construction of parsimonious models using spatially dense observations, and demonstrates the utility of the approach to situations where the observations are not arranged on a regular lattice, i.e.
-sensor networks \cite{Sahu2008}.
-\subsection{One dimensional example}
- Consider the following homogeneous multiscale spatial mixing kernel 
-% \setlength{\arraycolsep}{0.0em}
-% \begin{eqnarray}
-% k\left(s-r\right)&=& -\phi_{4;0,-3}\left(s-r\right)+\phi_{4;0,-2}\left(s-r\right)\nonumber\\
-% &&{-}\:0.5\psi_{4;1,-6}\left(s-r\right)+0.5\psi_{4;1,-3}\left(s-r\right)
-% \label{eq:1DSimulationKernel}
-% \end{eqnarray}
-% \setlength{\arraycolsep}{5pt}
-The kernel and its decomposition are plotted in  \figurename{\ref{fig:SpatialMixingKernel}}.
-The dynamics associated with the IDE defined by (\ref{eq:1DSimulationKernel}) will be oscillatory and dissipative to initial conditions.
+This section demonstrates the identification of the proposed IDE model.
+The MRA of a synthetic model is demonstrated, which is able to represent the system at different spatial scales.
+The spectral analysis was used to choose the spatial scale adequate to represent the spatial field.
+
+One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1.5\times\phi_{4,3,-2}(r-r')$.
+Sampling time and the synaptic time constant are set to 1 and 10 milliseconds respectively.
+The sensors were arranged regularly where the distance between adjacent sensors was set to 0.5 mm resulting into 161 observation locations.
+Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel.
+The connectivity kernel and its decomposition are plotted in  \figurename{\ref{fig:KernelAndFreqResponse}} (a).
+The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b).
+The observed field has an approximate spatial bandwidth $1.38$ cycles/mm.
+This suggests the use of wavelets upto level $j=3$.
+
+% is obtained  and The dynamics associated with the IDE defined by (\ref{eq:1DSimulationKernel}) will be oscillatory and dissipative to initial conditions.
 The field is decomposed using scaling functions $\phi_{4;0,k} $ and the associated wavelet functions $\psi_{4;j,k} $ with $j=0,1$.
-Observations are then generated from (\ref{eq:ConstructionIntegral1}-\ref{eq:Pi}) for spatial domain defined as $\mathcal{S}=\left[0,10 \right] $ in response to an initial condition where $\boldsymbol\Sigma_v=0.2 \times \mathbf{I}_{n_y}$ and $ \eta(s-r)=2.5\times\phi_{4,3,-2}(s-r)$.
-The response was sampled at 50 irregularly spaced random locations, at $t=1, \cdots 400 $.
 \begin{figure}[!h]
@@
 The dashed line shows the cutoff frequency (-3 dB point).}
- \label{fig:FreqResponse}
+\label{fig:KernelAndFreqResponse} 
   \end{figure} 
@@
 
-% \begin{figure}[!h] 
-% \centering
-% \includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
-% \caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$.
-}
-% \label{fig:SpatialMixingKernelEstimate}
-% \end{figure}
-% \begin{figure*}[!hb] 
-% % \renewcommand*{\thesubfigure}{}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
-% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
-% \caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
-% \label{fig:1DFieldEstimation}
-% \end{figure*}
-In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
-% \begin{equation}
-%  k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
-% \label{1DKernelDecompositionForSimulation}
-% \end{equation}
-% \begin{equation}
-%  z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
-% \label{1DFieldDecompositionForSimulation}
-% \end{equation}
-Note that the number of translation operations depends on the spatial range of the data.
+% In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
+% Note that the number of translation operations depends on the spatial range of the data.
 It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively.
@@
 
- The performance measure employed here is the Mean Integrated Squared Error (MISE) defined as
-\begin{equation}
- \mathbf{E}\left[\int_{\mathcal{S}}\left[e\left(s\right) \right]^2ds  \right]
-\label{MISE} 
-\end{equation}
- where  $e\left(s\right)$ is the error between the unknown function, $f\left( s\right) $ and its estimate, $\hat{f}\left( s\right) $.
+%  The performance measure employed here is the Mean Integrated Squared Error (MISE) defined as
+% \begin{equation}
+%  \mathbf{E}\left[\int_{\mathcal{S}}\left[e\left(s\right) \right]^2ds  \right]
+% \label{MISE} 
+% \end{equation}
+%  where  $e\left(s\right)$ is the error between the unknown function, $f\left( s\right) $ and its estimate, $\hat{f}\left( s\right) $.
 In this example the original kernel and the field are known and hence the integral in  (\ref{MISE}) can be computed analytically.
 For spatial mixing kernel we have
-\begin{eqnarray}
- \lefteqn{\int_{\mathcal{S}}\left[e\left(s\right)\right]^2ds}\nonumber \\  &=\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)^\top\left[ \int_{\mathcal{S}}\boldsymbol\lambda\left(s\right)\boldsymbol\lambda\left(s\right)^\top ds\right] \left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)&
-\label{MISEKernel}
-\end{eqnarray}
-  Here, we are particularly interested in assessing the performance improvement as the scale of the details in MRA is increased.
+% \begin{eqnarray}
+%  \lefteqn{\int_{\mathcal{S}}\left[e\left(s\right)\right]^2ds}\nonumber \\  &=\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)^\top\left[ \int_{\mathcal{S}}\boldsymbol\lambda\left(s\right)\boldsymbol\lambda\left(s\right)^\top ds\right] \left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)&
+% \label{MISEKernel}
+% \end{eqnarray}
+%   Here, we are particularly interested in assessing the performance improvement as the scale of the details in MRA is increased.
 Performance based on (\ref{MISEKernel}) at different spatial scales and over 500 trials have been evaluated.
@@
 Assuming the observed field can be fully described by the  decomposed IDE model, the variance of the field can be computed to express the  uncertainty of the estimation, at each point in space and at time $t$ we have
-\begin{equation}
- \text{Var}(\hat z_t(s_i))=\boldsymbol\mu^{\top}(s_i) \mathbf P_{t|T}\boldsymbol\mu(s_i)
-\label{eq:FieldVariance}
-\end{equation}
-where $\mathbf P_{t|T} $ is the covariance matrix associated with the  state estimates obtained from the RTS smoother.
+% \begin{equation}
+%  \text{Var}(\hat z_t(s_i))=\boldsymbol\mu^{\top}(s_i) \mathbf P_{t|T}\boldsymbol\mu(s_i)
+% \label{eq:FieldVariance}
+% \end{equation}
+% where $\mathbf P_{t|T} $ is the covariance matrix associated with the  state estimates obtained from the RTS smoother.
 Variance based on (\ref{eq:FieldVariance}) at each spatial location and at $t=50$ is shown in \figurename{\ref{fig:FieldVariance}}.

### 2011-02-23 Multiresolution_framework/ltx/manuscript.tex
changed the histogram plot

@@
 
-One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1.5\times\phi_{4,3,-2}(r-r')$.
+One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1\times\phi_{4,3,-2}(r-r')$.
 Sampling time and the synaptic time constant are set to 1 and 10 milliseconds respectively.

### 2011-02-23 Multiresolution_framework/ltx/manuscript.tex
changed the title
edit to simulation

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation }
+\title{A Multiresolution Framework for One Dimensional Neural Field Modelling }
 %
@@
 The sensors were arranged regularly where the distance between adjacent sensors was set to 0.5 mm resulting into 161 observation locations.
-Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel.
+Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
 The connectivity kernel and its decomposition are plotted in  \figurename{\ref{fig:KernelAndFreqResponse}} (a).

### 2011-02-25 Multiresolution_framework/ltx/manuscript.tex
added reference
edit to simulation section

@@
 \end{align}
-A direct consequence of \eqref{eq:BsplineConvolution} is 
+A direct consequence of \eqref{eq:BsplineConvolution} is \cite{Chui1992} 
 \begin{eqnarray}
@@
 The observed field has an approximate spatial bandwidth $1.38$ cycles/mm.
-This suggests the use of wavelets upto level $j=3$.
+This suggests the use of wavelets up to level $j=3$.
+Field reconstruction at different level of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
+The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field.
+Root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:RMSE}}.
+The histogram of the parameter estimates in \figurename{\ref{fig:ParametersHistogram}} is generated using 100 runs of the EM algorithm, although the estimates of $\theta_1$ is biased (7.4 \%) the RMSE between the true and estimated kernels is $1.83$.
 
@@
  \centering
- \includegraphics[scale=1]{./Graph/Hist.pdf}
- \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
-the solid lines show the actual parameter values and the dotted lines show the means of the estimated
-parameters. Left panel: The histogram of the central excitatory connectivity kernel basis function parameter
-estimates, $\theta_0$. Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter
-estimates, $\theta_1$.}
- \label{fig:ParametersHistogram}
- \end{figure} 
-\begin{figure}[!h] 
- \centering
  %\includegraphics[width=0.5\textwidth]{./Graph/RMSE.pdf}
@@
 shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
- \label{fig:FreqResponse}
+ \label{fig:FieldEstimates}
+ \end{figure} 
+\begin{figure}[!h] 
+ \centering
+ \includegraphics[scale=1]{./Graph/Hist.pdf}
+ \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
+the solid lines show the actual parameter values and the dotted lines show the means of the estimated
+parameters. Left panel: The histogram of the central excitatory connectivity kernel basis function parameter
+estimates, $\theta_0$. Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter
+estimates, $\theta_1$.}
+ \label{fig:ParametersHistogram}
  \end{figure}

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
added EM algorithm

@@
  into equation \eqref{eq:ObservationEquation} giving
-\begin{equation}\label{ObservationEquation} 
+\begin{equation}\label{eq:ReducedObservationEquation} 
 	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
@@
 \section{Estimation of the Multiresolution Spatio-temporal IDE Model}
-A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm to infer both the kernel and the spatial field from the noise corrupted spatio-temporal data.
-In this context, the EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the spatial mixing kernel parameters and the posterior distribution of the field weights.
+A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm to infer both the kernel and the field from the electrophysiological data.
+The EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
 In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$ \cite{McLachlan1997}.
-In the E-step, given an estimate of $\boldsymbol\theta$, filtering methods can be used to determine the posterior state sequence.
-Here we compare three techniques namely based on  the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005}, Ensemble Kalman smoother (EnKs) \cite{Evensen2003} and a heuristic separable RTS smoother for state estimation problem.
-For the first method we modify the framework proposed in \cite{Dewar2009} by computing and storing the required elements prior to the iterative estimation algorithm, the modified algorithm is computationally less demanding (see Appendix \ref{App:ReducedRTS}).
-In Ensemble Kalman filter (EKf) an ensemble of model states, $\mathbf X_t \in \mathbb R^{n_x \times N} \sim \mathcal N(\mathbf x_t,\mathbf P_t)$ is propogated through the state equation to calculate the forecast estimates $\hat{\mathbf x}^f_t$ and the error covariance of the predicted model state, $\mathbf P_t^f$ where $N$ is the number of ensemble members.
-Then  the model state is updated to compute analysed estimates, $\hat {\mathbf x}_t^a$.
-This is important for model with high dimensional state space where standard Kalman filter  is computationally infeasible to implement as the state covariance matrix needs to be stored and propogated in time.
-The EnKs updates the filtered ensembles at the current and all prior times every time a new set of measurements becomes available.
-The algorithm is given in Algorithm \ref{alg:EnKS} for completeness.
-It is essential that the observations be also treated as an ensemble of random variables, $\mathbf Y_t$, having a distribution with mean equal to the observed value, $\mathbf y_t$ and covariance equal to $\boldsymbol\Sigma_v$ \cite{Houtekamer2005}.
-
-% represents the predicted state covariance matrix, $\mathbf P_{t|t+1}$ using a large stochastic ensemble of the predicted states $\hat{\mathbf x}_{t+1|t}$.
-
-In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother can be employed to determine the posterior state sequence.
-It can be shown that \cite{Dempster1977,Gibsona2005} every EM iteration increases the lower bound on the likelihood function and hence improving the state and parameter estimates.
+In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} can be employed to determine the posterior state sequence.
+The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of
+\begin{equation}
+ \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=2T_s\boldsymbol\upsilon_0-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta-2T_s\boldsymbol\upsilon_1
+\end{equation}
+with a maximum at
+\begin{align}
+ \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top).
+\end{align}
+Where
+\begin{equation}
+ \boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
+\end{equation}
+\begin{equation}
+ \boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
+\end{equation}
+and
+\begin{equation}
+ \boldsymbol\Upsilon=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}.
+\end{equation}
+The $\left(i,j\right)^{th}$ element of the  block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\begin{align}
+\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}[\mu(\mathbf r)]_i[\int_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r'}\right)\boldsymbol\lambda^\top\left(\mathbf{r-r'}\right) d\mathbf{r'}]_{j:}d\mathbf r.
+\end{align}
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
 % The complexity of this algorithm is $O\left(n_{x}^2n_{\theta}^2\right)+O \left(Tn_{x}^{3}\right)+O\left(Tn_{y}^3\right) $ showing that

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
edit to  EM algorithm

@@
 For simplicity, we denote hereafter the current time step by $t$ and the future time step by $t+1$.
-Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
+\parham{Dean, can you replace it by linear firing rate plus referencing plz?}Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
 \begin{equation}\label{eq:PiecewiseSigmoid} 
@@
 \end{equation}
-and $\mathbf I$ is the identity matrix, and 
+and where $\mathbf I$ is the identity matrix, and 
 \begin{equation}\label{eq:Disturbance}
@@
 \end{equation}
-where each element of the observation matrix is 
+where each element of the observation matrix, $\mathbf C$ is given by
 \begin{equation}
@@
 \end{equation}
-% Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.
-In the two dimensional case, the convolution integral can be factorised as follows, e.g.
+ Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.  
+% In the two dimensional case, the convolution integral can be factorised as follows, e.g. 
 % \setlength{\arraycolsep}{0.14em}
@@
 \begin{equation}
- \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=2T_s\boldsymbol\upsilon_0-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta-2T_s\boldsymbol\upsilon_1
+ \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta
 \end{equation}
@@
 Where
-\begin{equation}
+\begin{equation}\label{eq:upsilon0}
  \boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq:upsilon1}
  \boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
 \end{equation}
-and
-\begin{equation}
- \boldsymbol\Upsilon=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}.
-\end{equation}
-The $\left(i,j\right)^{th}$ element of the  block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\begin{equation}\label{eq:Upsilon}
+ \boldsymbol\Upsilon=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i},
+\end{equation}
+and $\beta$ is constant with respect to the connectivity kernel parameters. The $\left(i,j\right)^{th}$ element of the  block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-% The complexity of this algorithm is $O\left(n_{x}^2n_{\theta}^2\right)+O \left(Tn_{x}^{3}\right)+O\left(Tn_{y}^3\right) $ showing that
+The second terms in equations (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed before EM implementation which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.
+$\Xi$-variables can be calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$ and the cross-covariance matrix $\mathbf M_t$ using \cite{Shumway2000}
+\begin{align}\label{eq:Xivariables}
+\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
+\end{align}
 \section{Simulation}

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
edit to  Bsspline model

@@
 \end{equation}
-and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0,\mathbf l}:\mathbf{l} \in \mathbb{Z}^d \right\rbrace $ and $\left\lbrace x_{t,j_0,\mathbf l}: \mathbf{l} \in \mathbb{Z}^d\right\rbrace$ respectively.
-The kernel detail coefficient vectors $\boldsymbol \beta_{j}$ and the field detail coefficient vectors $\check{\mathbf{x}}_{t,j}$ are defined by
-\begin{equation}
- \boldsymbol\beta_{j}^\top=\left[\boldsymbol\beta_{j}^{(1)\top} \quad \boldsymbol\beta_{j}^{(2)\top} \cdots \boldsymbol\beta_{j}^{(2^d-1)\top}\right] 
-\end{equation}
-\begin{equation}
-\check{\mathbf{x}}_{t,j}^\top=\left[\check{\mathbf{x}}_{t,j}^{(1)\top} \quad \check{\mathbf{x}}_{t,j}^{(2)\top} \cdots \check{\mathbf{x}}_{t,j}^{(2^d-1)\top}\right] 
-\end{equation}
-where the vector $\boldsymbol\beta_{j}^{(i)}$ contains all the coefficient $\left\lbrace \beta_{j,\mathbf l}^{(i)} :\mathbf{l} \in \mathbb{Z}^d\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}^{(i)}$ contains all the coefficient $\left\lbrace  \check x_{t,j,\mathbf l}^{(i)}:\mathbf{l} \in \mathbb{Z}^d\right\rbrace$.
+and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
+Similarly the kernel detail coefficient vectors $\boldsymbol\beta_{j}$ contains all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}$ contains all the coefficient $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$.
 %and  $\boldsymbol\lambda(\mathbf{s}-\mathbf{r})$ is the vector of the kernel scaling and wavelet functions and   $\boldsymbol\mu(\mathbf{s})$ is the vector of the field scaling and wavelet functions.
@@
 
-By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}) can be computed.
+By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta}) can be computed.
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, scaling and wavelet basis functions should be expanded  in terms of $N_m$ at the appropriate scale.
-It is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}:
-\begin{equation}
- \left\langle \psi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
-\label{PsiPsiOrthogonality}
-\end{equation}
-\begin{equation}
- \left\langle \phi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2
-\label{PhiPsiOrthogonality}
-\end{equation}
- Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.  
-% In the two dimensional case, the convolution integral can be factorised as follows, e.g. 
-% \setlength{\arraycolsep}{0.14em}
-% \begin{IEEEeqnarray}{!l l }
-%  \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right)\ast \psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)&=\left[\phi_{m;j,l_1}\left(s_{1}\right)\ast\phi_{m;j,l'_1}\left(s_{1}\right)\right] \nonumber \\
-% &\times \left[ \phi_{m;j,l_2}\left(s_{2}\right) \ast \psi_{m;j,l'_2}\left(s_{2}\right)\right] \nonumber \\
-% &
-% \end{IEEEeqnarray}
-% \setlength{\arraycolsep}{5pt}
-% The preceding factorisation can be also applied to the 2D-inner product integral. Non-zero quantities can  be then expressed by
-% \setlength{\arraycolsep}{0.14em}
-% \begin{IEEEeqnarray}{!l l }
-% \left\langle \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\phi_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle &=\left\langle \phi_{m;j,l_1}\left(s_{1}\right),\phi_{m;j,l'_1}\left(s_{1}\right)\right\rangle \nonumber \\
-% & \times\left\langle \phi_{m;j,l_2}\left(s_{2}\right) , \phi_{m;j,l'_2}\left(s_{2}\right)\right\rangle \nonumber \\
-% &
-% \end{IEEEeqnarray}
-% \setlength{\arraycolsep}{5pt}
-% likewise we can compute 
-% $\left\langle  \psi^{1}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$
-% , \\
-% $\left\langle  \psi^{2}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{2}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$ and \\
-% $
-% \left\langle \psi^{3}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right), \psi^{3}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle $. \\ \\
-In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
+In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
 \section{Estimation of the Multiresolution Spatio-temporal IDE Model}
@@
 Where
-\begin{equation}\label{eq:upsilon0}
- \boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
-\end{equation}
-\begin{equation}\label{eq:upsilon1}
- \boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
-\end{equation}
-\begin{equation}\label{eq:Upsilon}
- \boldsymbol\Upsilon=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i},
-\end{equation}
+\begin{align}\label{eq:upsilon0}
+ \boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}
+\end{align}
 and $\beta$ is constant with respect to the connectivity kernel parameters. The $\left(i,j\right)^{th}$ element of the  block matrix $\mathbf U_{n_x \times n_x}$ is given by

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
edit to EM

@@
 Similarly the kernel detail coefficient vectors $\boldsymbol\beta_{j}$ contains all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}$ contains all the coefficient $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$.
-%and  $\boldsymbol\lambda(\mathbf{s}-\mathbf{r})$ is the vector of the kernel scaling and wavelet functions and   $\boldsymbol\mu(\mathbf{s})$ is the vector of the field scaling and wavelet functions.
  The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_{\theta}}$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_x}$ are defined by
@@
 \end{equation}
-In order to compute the  integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}) we need to be able to calculate the convolution and inner product of B-spline scaling functions.
+In order to compute the  integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta}) we need to be able to calculate the convolution and inner product of B-spline scaling functions.
 Equation (\ref{SplineConvolutionIntegral}) can be rewritten as $(m-1)$ times convolution of indicator function with itself
@@
 In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
-\section{Estimation of the Multiresolution Spatio-temporal IDE Model}
-A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm to infer both the kernel and the field from the electrophysiological data.
+\section{State and Parameter Estimation}
+A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from the electrophysiological data.
 The EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
-In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$ \cite{McLachlan1997}.
+In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$.
 In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} can be employed to determine the posterior state sequence.
@@
 The second terms in equations (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed before EM implementation which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.
-$\Xi$-variables can be calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$ and the cross-covariance matrix $\mathbf M_t$ using \cite{Shumway2000}
+$\Xi$-variables can be calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$ and the cross-covariance matrix $\mathbf M_t$ using \cite{Gibsona2005}
 \begin{align}\label{eq:Xivariables}
@@
 The histogram of the parameter estimates in \figurename{\ref{fig:ParametersHistogram}} is generated using 100 runs of the EM algorithm, although the estimates of $\theta_1$ is biased (7.4 \%) the RMSE between the true and estimated kernels is $1.83$.
-
-% is obtained  and The dynamics associated with the IDE defined by (\ref{eq:1DSimulationKernel}) will be oscillatory and dissipative to initial conditions.
-The field is decomposed using scaling functions $\phi_{4;0,k} $ and the associated wavelet functions $\psi_{4;j,k} $ with $j=0,1$.
 \begin{figure}[!h]

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \begin{IEEEkeywords}
-Dynamic spatio-temporal modelling, Expectation Maximisation (EM) algorithm, Integro-Difference Equation (IDE), Multiresolution Approximation (MRA), wavelets.
+Neural field model, Expectation Maximisation (EM) algorithm, Multiresolution Approximation (MRA), wavelets.
 \end{IEEEkeywords}
@@
 In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} can be employed to determine the posterior state sequence.
-The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of
+The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a quadratic $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of
 \begin{equation}

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{equation}
-where the unknown parameter vector $ \boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and the unknown state vector $ \mathbf{x}_t \in \mathbb{R}^{n_x}$ are defined as 
+where the unknown parameter $ \boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and the unknown state  $ \mathbf{x}_t \in \mathbb{R}^{n_x}$ are defined as 
 \begin{equation}
@@
 and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
-Similarly the kernel detail coefficient vectors $\boldsymbol\beta_{j}$ contains all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}$ contains all the coefficient $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$.
- The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_{\theta}}$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu: \mathbb{R}^{n_{\mathcal S}}\rightarrow \mathbb{R}^{n_x}$ are defined by
-\begin{eqnarray}
- \boldsymbol\lambda^\top(\mathbf r-\mathbf r')&=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right.
+Similarly the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and  $\check{\mathbf{x}}_{t,j}$ contain all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ accordingly.
+ The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu$ are defined by
+\begin{align}
+ \boldsymbol\lambda^\top(\mathbf r-\mathbf r')=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right.
 \nonumber \\
-&&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
+&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
 \label{KernelBasisVector} 
-\end{eqnarray}
+\end{align}
 \begin{equation}
@@
 	    \boldsymbol\mu^\top\left(\mathbf{r'}\right)\mathbf{x}_t 
-	\, d\mathbf{r}'d\mathbf{r}}
-	+ \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}, 
+	\, d\mathbf{r}'d\mathbf{r}} \nonumber \\
+	+& \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}, 
 \end{align}
@@
 \end{equation}
-and substituting these into \eqref{eq:DecomposedModel2} and cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
+and substituting these into \eqref{eq:DecomposedModel2} and then cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
 \begin{equation}\label{eq:StateEquation}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to intro

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{A Multiresolution Framework for One Dimensional Neural Field Modelling }
+\title{Multiresolution Neural Field Estimation }
 %
@@
 \begin{IEEEkeywords}
-Neural field model, Expectation Maximisation (EM) algorithm, Multiresolution Approximation (MRA), wavelets.
+Neural field model, Expectation Maximization (EM) algorithm, Multiresolution Approximation (MRA), wavelets.
 \end{IEEEkeywords}
@@
 
+We have a clear definition and where to stimulate and how to stimulate.
+
 \section{Introduction}
-To Do
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-% \IEEEPARstart{C}{omplex}
-
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-
-%\hfill mds
-
-%\hfill January 11, 2007
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
+\IEEEPARstart{T}{his} paper introduces a multiresolution data-driven framework for neural field modeling.
+Neural field models describe the meso and macroscopic dynamics of the human brain.
+Modeling the brain this level is extremely important, since diseases such as epilepsy and Parkinson's disease are manifested at this scale through pathological oscillations.
+The ability to create patient-specific neural field models will not only contribute to our knowledge base of poorly understood diseases such as epilepsy, but may also enable the development of new treatment strategies.
+This is particularly poignant with the advent of new devices that use therapeutic electrical stimulation.
+Presently, stimulation strategies for devices using corrective or modulating electrical stimulation operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
+Therefore, there exists an enormous potential to improve the performance of these devices using systems theory.
+The design of a stimulation strategy using systems theory requires a model.
+Neural mass and neural field models are the ideal candidates for estimation and control algorithms.
+It is expected that parameters of the neural fields models will be patient specific and will therefore need to be inferred from data.
+
+Creating patient specific neural models has been approach from a number of different standpoints.
+\dean{need to add proper citations here.} Valdes et al.
+(1999) used the neural mass model of Lopes Da Silva (1976) and Zetterberg et al.
+(1978) to fit EEG data.
+This approach was extended by David and Friston (2003) to coupled neural masses (using the equations of Jansen and Ritt (1995)) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM).
+Following this work, Galka et al.
+(2008), Sauer et al.
+(2008), Daunizeau et al.
+(2009), and Freestone et al (2011) developed the estimation frameworks for continuum neural field equations that explain the richer dynamics of spatiotemporal neural fields.
+
+The work can be considered an extension to the framework of Freestone et al.
+(2011), where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate state and parameter estimation.
+The basis function decomposition in this previous study did not account for all of the spatial dynamics.
+Thus, it can be improved..
+In this current paper, a multiresolution approach is taken...
+
 \section{Integro-Difference Equation Neural Field Model}
-The stochastic  integro-difference equation (IDE) form of the model based on the Wilson-Cowan \cite{Wilson1973} or Amari neural field \cite{Amari1977} formulation is given by (cite NeuroImage paper)
+The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see \dean{cite NeuroImage paper} for a full derivation)
 \begin{equation}
@@
 \end{equation}
-where the local post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$, parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$ where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
-The spatial connectivity between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$, for an isotropic and homogeneous neural field.
-The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function $f\left(.\right)$.
+where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$.
+Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
+The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
+The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, we denote hereafter the current time step by $t$ and the future time step by $t+1$.
-\parham{Dean, can you replace it by linear firing rate plus referencing plz?}Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function
-\begin{equation}\label{eq:PiecewiseSigmoid} 
-	\hat{f}(v_t(\mathbf{r}')) = \left\{ \begin{array}{ll}
-		0, & v_t(\mathbf{r}') \le v_1 \\
-		\varsigma v_t(\mathbf{r}'), &  v_1 < v_t(\mathbf{r}') < v_2 \\
-		1, & v_t(\mathbf{r}') \ge v_2 \\ 
-		\end{array}\right.
-\end{equation}
-where the parameter $\varsigma$ governs the slope of the sigmoid. Furthermore, we assume the field is in the linear region of the piecewise function giving
-\begin{equation}\label{eq:DiscreteTimeModel} 
-	v_{t+1}\left(\mathbf{r}\right) = 
-	\xi v_t\left(\mathbf{r}\right) + 
-	T_s \int_\Omega { 
-	    w\left(\mathbf{r}-\mathbf{r'}\right)
-	    v_t\left(\mathbf{r}'\right) 
-	\, d\mathbf{r}'} 
-	+ e_t\left(\mathbf{r}\right), 
-\end{equation}
-Note that the parameter $\varsigma$ is absorbed into the kernel for simplicity. Observation equation is given by 
+For simplicity, we denote the current time step by $t$ and the future time step by $t+1$.
+The observation equation is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 The superscript $\top$ denotes the transpose operator.
+
 \section{MRA of the IDE in State-Space}
-Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{eq:DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
-For the one-dimensional kernel this is given by,
-\begin{equation}
- w\left(r-r'\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(r-r'\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(r-r'\right) 
+The multiresolution approximation (MRA) of the neural IDE is be obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
+Considering a one-dimensional field, the connectivity kernel is decomposed by,
+\begin{equation}
+ w\left(r-r'\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(r-r'\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(r-r'\right), 
 \label{eq:KernelExpansion}
 \end{equation}
-In this expansion, $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$ and $ \beta_{j,l}$ represent the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$.
-Integers $j$ and $l$ are called scale and translation parameters accordingly.
-The one-dimensional field can similarly be decomposed as
-\begin{equation}
- v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(r\right)
+where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$.
+Integers $j$ and $l$ are the scale and translation parameters respectively.
+The field is decomposed as
+\begin{equation}
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(r\right),
 \label{eq:FieldExpansion}
@@
 % \end{equation}
-Equations \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions.
-For practical implementation,  \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} must be truncated at some level $j$, therefore we have
- \begin{equation}
- w\left(\mathbf{r}-\mathbf{r'}\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
+Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$. Therefore, we have
+ \begin{equation}
+ w\left(r-r'\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
 \label{eq:KernelFiniteExpansion}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to model section

@@
 % \end{equation}
-Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$. Therefore, we have
- \begin{equation}
- w\left(r-r'\right)\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-\label{eq:KernelFiniteExpansion}
-\end{equation}
-\begin{equation}
- v_t\left(\mathbf{r}\right)\approx\boldsymbol\mu\left(\mathbf{r}\right)^\top\mathbf{x}_t
+Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
+Therefore, the field and the connectivity kernel is approximated by
+ \begin{align}
+ w\left(r-r'\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right) 
+\label{eq:KernelFiniteExpansion} \\
+ v_t\left(r\right) &\approx \boldsymbol\mu\left(r\right)^\top\mathbf{x}_t,
 \label{eq:FieldFiniteExpansion}
-\end{equation}
-where the unknown parameter $ \boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and the unknown state  $ \mathbf{x}_t \in \mathbb{R}^{n_x}$ are defined as 
-\begin{equation}
- \boldsymbol\theta^\top=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
-\label{KernelWeights}
-\end{equation}
-\begin{equation}
- \mathbf{x}_{t}^\top=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right] 
+\end{align}
+where the unknown parameter and state vectors \dean{(block matrices?)}, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
+\begin{align}
+ \boldsymbol\theta^\top &=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
+\label{KernelWeights} \\
+ \mathbf{x}_{t}^\top &=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right].
 \label{FieldWeights}
-\end{equation}
-and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
-Similarly the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and  $\check{\mathbf{x}}_{t,j}$ contain all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ accordingly.
+\end{align}
+The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
+Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
+
 The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu$ are defined by

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
more edits to derivation

@@
 
-The work can be considered an extension to the framework of Freestone et al.
+This paper is an extension to the framework presented Freestone et al.
 (2011), where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate state and parameter estimation.
@@
 
+By taking the multiresolution approach, the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales.
+In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously...
+
 \section{Integro-Difference Equation Neural Field Model}
 The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see \dean{cite NeuroImage paper} for a full derivation)
-\begin{equation}
+\begin{equation}\label{eq:DiscreteTimeModel}
 	v_{t+T_s}\left(\mathbf{r}\right) = 
@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
+\dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
@@
 
-The vector of the kernel scaling and wavelet functions $\boldsymbol\lambda$ and the vector of the field scaling and wavelet functions $\boldsymbol\mu$ are defined by
+The vectors \dean{(block matrices?)} of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
 \begin{align}
- \boldsymbol\lambda^\top(\mathbf r-\mathbf r')=&\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0}^\top(\mathbf r-\mathbf r') \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r-\mathbf r') \right.
-\nonumber \\
-&\left. \cdots \quad \boldsymbol\psi_{j}^\top(\mathbf s-\mathbf r)\right]
-\label{KernelBasisVector} 
+ \boldsymbol\lambda^\top(r-r')=&\left[ \boldsymbol\phi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0+1}^\top(r-r') \right. \nonumber \\
+&\left. \cdots \quad \boldsymbol\psi_{j}^\top(r-r')\right] \label{KernelBasisVector} \\
+ \boldsymbol\mu^\top(r)=&\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right] 
+\label{FieldBasisVector}
 \end{align}
-\begin{equation}
- \boldsymbol\mu^\top(\mathbf r)=\left[ \boldsymbol\phi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0}^\top(\mathbf r) \quad \boldsymbol\psi_{j_0+1}^\top(\mathbf r) \cdots \boldsymbol\psi_{j}^\top(\mathbf r) \right]
-\label{FieldBasisVector}
-\end{equation}
-Each vector of basis functions on the right hand-side of (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in a way similar to their corresponding weight vectors in (\ref{KernelWeights}) and (\ref{FieldWeights}).
-% Note that the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales.
-In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously.
-
-To derive the state-space representation of the model we substitute decompositions \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} into equation \eqref{eq:DiscreteTimeModel} and then cross-multiply the decomposed model by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the spatial domain, $\Omega$, giving
+The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
+
+To derive the state-space model, Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are substituted into Eq.
+\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
 \begin{align}\label{eq:DecomposedModel2} 
-	&\int_{\Omega} \boldsymbol\mu  \left(\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top  d\mathbf{r}\mathbf{x}_{t+1}= 
-	\xi\int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu\left(\mathbf{r}\right)^\top d\mathbf{r}\mathbf{x}_t \nonumber \\
-	&+T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \int_\Omega { 
-	   \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
-	    \boldsymbol\mu^\top\left(\mathbf{r'}\right)\mathbf{x}_t 
-	\, d\mathbf{r}'d\mathbf{r}} \nonumber \\
-	+& \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}, 
+	&\int_{\Omega} \boldsymbol\mu  \left(r\right)\boldsymbol\mu\left(r\right)^\top  dr\mathbf{x}_{t+1}= 
+	\xi\int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu\left(r\right)^\top d\mathbf{r}\mathbf{x}_t \nonumber \\
+	&+T_s \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    \boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t 
+	\, dr'd\mathbf{r}} \nonumber \\
+	+& \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
 \end{align}
-Now defning 
-\begin{equation}\label{eq:Lambdax}
- \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) d\mathbf{r}
-\end{equation}
-\begin{equation}\label{eq:Lambdatheta}
- \mathbf{\Lambda}_{\theta}\triangleq\int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \int_\Omega { 
-	   \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r'}\right)
-	    \boldsymbol\mu^\top\left(\mathbf{r'}\right)\mathbf{x}_t 
-	\, d\mathbf{r}'d\mathbf{r}}
-\end{equation}
-and substituting these into \eqref{eq:DecomposedModel2} and then cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
+The simplify the model we define 
+\begin{align}\label{eq:Lambdax}
+ \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
+\label{eq:Lambdatheta}
+ \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t 
+	\, dr'dr}
+\end{align}
+and substitute it into Eq.~\eqref{eq:DecomposedModel2}. Then cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
 \begin{equation}\label{eq:StateEquation}
- \mathbf x_{t+1}=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t
+ \mathbf x_{t+1}=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
 \end{equation}
@@
 \begin{equation}\label{eq:A_theta}
- \mathbf A(\boldsymbol \theta)=(T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I)
+ \mathbf A(\boldsymbol \theta)=(T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
 \end{equation}
@@
 \begin{equation}
-\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\eta\left(\mathbf{r}-\mathbf{r'}\right)\boldsymbol\mu^{\top}\left(\mathbf{r'}\right)d\mathbf{r'}d\mathbf{r}\mathbf{\Lambda}_{x}^{-\top}.
+\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
 \end{equation}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
more edits to derivation

@@
 For simplicity, we denote the current time step by $t$ and the future time step by $t+1$.
-The observation equation is given by
+The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \end{equation}
-where electrophysiological recordings $\mathbf{y}_{t}=[y_t(\mathbf{r}_1) y_t(\mathbf{r}_2)\cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$ via the observation kernel $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$, is corrupted by an i.i.d normally distributed zero-mean white noise $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ with $\mathbf{\Sigma}_{\epsilon}=\sigma_{\epsilon}^2\mathbf I_{n_y} $.
+where $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$, is corrupted by an i.i.d normally distributed zero-mean white noise $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ with $\mathbf{\Sigma}_{\epsilon}=\sigma_{\epsilon}^2\mathbf I_{n_y} $.
 The superscript $\top$ denotes the transpose operator.
@@
 &\left. \cdots \quad \boldsymbol\psi_{j}^\top(r-r')\right] \label{KernelBasisVector} \\
- \boldsymbol\mu^\top(r)=&\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right] 
+ \boldsymbol\mu^\top(r)=&\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right]. 
 \label{FieldBasisVector}
@@
 \end{align}
-The simplify the model we define 
+The simplify the model we define the matrices
 \begin{align}\label{eq:Lambdax}
@@
 \end{align}
-and substitute it into Eq.~\eqref{eq:DecomposedModel2}. Then cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ yields
-\begin{equation}\label{eq:StateEquation}
- \mathbf x_{t+1}=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
+and substitute them into Eq.~\eqref{eq:DecomposedModel2}. Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
+\begin{align}\label{eq:StateEquation}
+ \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t \\
+\label{eq:A_theta}
+ \mathbf A(\boldsymbol \theta) &= (T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
+\end{align}
+where $\mathbf I$ is the identity matrix. The disturbance becomes 
+\begin{equation}\label{eq:Disturbance}
+\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r},
 \end{equation}
-where
-\begin{equation}\label{eq:A_theta}
- \mathbf A(\boldsymbol \theta)=(T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
-\end{equation}
-and where $\mathbf I$ is the identity matrix, and 
-\begin{equation}\label{eq:Disturbance}
-\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r}
-\end{equation}
-which is a vector valued, zero-mean normally distributed white noise process with covariance \cite{Scerri2009}
+which is a vector valued, zero-mean normally distributed white noise process with covariance (see \cite{Scerri2009} for proof)
 \begin{equation}
@@
 \end{equation}
-Similarly, the observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
+The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
  into equation \eqref{eq:ObservationEquation} giving
@@
 \end{equation}
-where each element of the observation matrix, $\mathbf C$ is given by
+where each element of the observation matrix is given by
 \begin{equation}
@@
 \end{equation}
-This completes the state-space representation of the multiresolution approximation of the neural field model. 
+This completes derivation of the state-space representation of the multiresolution approximation of the neural field model. 
 % \parham{Mike you can add state-space derivation using Galerkin projection here.}
+
 \section{B-spline wavelet IDE model}
-Multiresolution approximation can be implemented using different classes of scaling and wavelet functions.
-In order to determine the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ convolution and inner product expressions of the basis functions need to be computable.
-B-spline wavelet and scaling functions are particularly convenient in the above decomposition as their convolution and inner product expressions can be found analytically.
-
-The  $m$th order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992} 
-\begin{eqnarray}
-N_{m}\left(s\right)&=&\left(N_{m-1}\ast N_{1}\right)\left(s\right)\nonumber \\
-&=&\int_0^{1} N_{m-1}\left( s-r\right)dr \quad m>1 
+The multiresolution approximation can be implemented using various classes of scaling and wavelet functions.
+B-spline functions were chosen due their compact support and the ability to analytically calculate convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
+\begin{align}
+N_{m}\left(r\right)=&\left(N_{m-1}\ast N_{1}\right)\left(r\right)\nonumber \\
+=&\int_0^{1} N_{m-1}\left( r-r'\right)dr' \quad m>1,
 \label{SplineConvolutionIntegral}
-\end{eqnarray}
-Here $\ast$ denotes the convolution operator and $N_1\left(s\right)$ is the characteristic function of the unit interval  $\left[ 0,1\right) $
+\end{align}
+where $\ast$ denotes convolution and $N_1\left(s\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$
 \begin{equation}
-N_{1}\left(s\right)=
+N_{1}\left(r\right)=
 \begin{cases}
-1 & \text{if $ 0\le s<1$}, \\
-0 & \mathrm{elsewhere}
+1 & \text{if $ 0\le r<1$}, \\
+0 & \mathrm{elsewhere}.
 \end{cases}
 \end{equation}
-In order to compute the  integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta}) we need to be able to calculate the convolution and inner product of B-spline scaling functions.
-Equation (\ref{SplineConvolutionIntegral}) can be rewritten as $(m-1)$ times convolution of indicator function with itself
+Eq.~\ref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ times convolution of indicator function with itself since
 \begin{equation}
- N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right)
+ N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right).
 \end{equation}
-then by using the associativity property of the convolution operator, it is clear that
+Using the associativity property of convolution we have
 \setlength{\arraycolsep}{0.0em}
@@
 N_{m}\left( r\right) \ast N_{m'}\left(r\right)&=\underbrace{\overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m-1 \quad \text{convolutions}}\left(r\right) \ast \overbrace{\left(N_{1} \ast \cdots \ast N_{1}\right)}^{m'-1\quad \text{convolutions}}}_{m+m'-1 \quad \text{convolutions}}\left(r\right)\nonumber\\
-&=N_{m+m'}\left(r\right)
-\end{align}
-A direct consequence of \eqref{eq:BsplineConvolution} is \cite{Chui1992} 
-\begin{eqnarray}
- \left\langle N_{m}\left(r-l_{1}\right), N_{m'}\left(r-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
-&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right)
+&=N_{m+m'}\left(r\right).
+\end{align}
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is (see \cite{Chui1992} for proof) 
+\begin{align}
+ \left\langle N_{m}\left(r-l_{1}\right), N_{m'}\left(r-l_{2}\right)\right\rangle=&N_{m+m'}\left(m+l_{1}-l_{2}\right)\nonumber \\
+=&N_{m+m'}\left(m'+l_{2}-l_{1}\right),
 \label{eq:BsplineInnerProduct}
-\end{eqnarray}
-where $\left\langle  .,.\right\rangle $ denotes the inner product.
-
-The $m$th order compactly supported B-spline wavelet function is defined as \cite{Chui1992} 
-\begin{equation}
- \varphi_{m}\left(s\right)=\sum_{n=0}^{3m-2} q_n N_{m}\left(2s-n\right)
-\end{equation}
-with the coefficients given by:\\ 
-\begin{equation}
- q_n= \frac{\left(-1\right)^n}{2^{m-1}} \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right) \quad \text{ $0\le n\le 3m-2$}
-\end{equation}
-
-By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta}) can be computed.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, scaling and wavelet basis functions should be expanded  in terms of $N_m$ at the appropriate scale.
-In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.
+\end{align}
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+The $m^{th}$ order compactly supported \dean{(is there a non-compactly supported B-spline?)} B-spline wavelet function is defined as (see \cite{Chui1992})
+\begin{align}
+ \varphi & _{m}\left(r\right) = \sum_{n=0}^{3m-2} q_n N_{m}\left(2r-n\right) \\
+ q & _n = \frac{\left(-1\right)^n}{2^{m-1}} \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$},
+\end{align}
+where $q_n$ are the coefficients.
+By exploiting properties Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed.
+In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+
 \section{State and Parameter Estimation}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
more edits to derivation
added cyan for cutting texts

@@
 \newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
+\newcommand{\cut}[1]{\textsf{\emph{\textbf{\textcolor{cyan}{#1}}}}}
 
@@
 Neural field models describe the meso and macroscopic dynamics of the human brain.
-Modeling the brain this level is extremely important, since diseases such as epilepsy and Parkinson's disease are manifested at this scale through pathological oscillations.
+Modeling the brain at this level is extremely important, since diseases such as epilepsy and \parham{Parkinson's disease} are manifested at this scale through pathological oscillations.
 The ability to create patient-specific neural field models will not only contribute to our knowledge base of poorly understood diseases such as epilepsy, but may also enable the development of new treatment strategies.
@@
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, we denote the current time step by $t$ and the future time step by $t+1$.
-The observation equation describing the electrophysiological recordings is given by
+For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \begin{align}
- \boldsymbol\lambda^\top(r-r')=&\left[ \boldsymbol\phi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0+1}^\top(r-r') \right. \nonumber \\
+ \boldsymbol\lambda^\top & (r-r')=\left[ \boldsymbol\phi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0+1}^\top(r-r') \right. \nonumber \\
 &\left. \cdots \quad \boldsymbol\psi_{j}^\top(r-r')\right] \label{KernelBasisVector} \\
- \boldsymbol\mu^\top(r)=&\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right]. 
+ \boldsymbol\mu^\top & (r)=\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right]. 
 \label{FieldBasisVector}
@@
 
-\section{B-spline wavelet IDE model}
+% \section{B-spline wavelet IDE model}
 The multiresolution approximation can be implemented using various classes of scaling and wavelet functions.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
added cyan for cutting texts
more edits to derivation

@@
 \newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
-\newcommand{\cut}[1]{\textsf{\emph{\textbf{\textcolor{cyan}{#1}}}}}
 
@@
 \begin{IEEEkeywords}
-Neural field model, Expectation Maximization (EM) algorithm, Multiresolution Approximation (MRA), wavelets.
+Neural field model, multiresolution approximation (MRA), expectation maximization (EM) algorithm, wavelets.
 \end{IEEEkeywords}
@@
 Neural field models describe the meso and macroscopic dynamics of the human brain.
-Modeling the brain at this level is extremely important, since diseases such as epilepsy and \parham{Parkinson's disease} are manifested at this scale through pathological oscillations.
+Modeling the brain this level is extremely important, since diseases such as epilepsy and Parkinson's disease are manifested at this scale through pathological oscillations.
 The ability to create patient-specific neural field models will not only contribute to our knowledge base of poorly understood diseases such as epilepsy, but may also enable the development of new treatment strategies.
@@
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The observation equation describing the electrophysiological recordings is given by
+For simplicity, we denote the current time step by $t$ and the future time step by $t+1$.
+The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \section{State and Parameter Estimation}
-A state-space representation of the IDE model allows the use of the Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from the electrophysiological data.
-The EM algorithm is a two part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters and the posterior distribution of the field weights.
-In the M-step a lower bound $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$ of the complete-data log-likelihood  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$, is maximised under the assumption of the system parameters being $\boldsymbol\theta'$.
-In the E-step, given an estimate of $\boldsymbol\theta$, the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} can be employed to determine the posterior state sequence.
-The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a quadratic $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of
+The state-space representation allows the use of the expectation maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from the electrophysiological data.
+The EM algorithm is a two-part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters (M-step) and the posterior distribution of the field weights (E-step).
+The M-step finds an estimate of $\boldsymbol\theta$ that maximizes the lower bound, $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$, of the complete-data log-likelihood,  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$.
+The E-step uses the estimate of $\boldsymbol\theta$, $\boldsymbol\theta'$ and the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} to estimate the posterior state sequence.
+The bound on the log-likelihood is a quadratic in the form of
 \begin{equation}
- \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta
+ \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
 \end{equation}
@@
 \begin{align}
- \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top).
-\end{align}
-Where
+ \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
+\end{align}
+where
 \begin{align}\label{eq:upsilon0}
@@
  \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
- \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}
-\end{align}
-and $\beta$ is constant with respect to the connectivity kernel parameters. The $\left(i,j\right)^{th}$ element of the  block matrix $\mathbf U_{n_x \times n_x}$ is given by
+ \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}.
+\end{align}
+The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}
-\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}[\mu(\mathbf r)]_i[\int_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r'}\right)\boldsymbol\lambda^\top\left(\mathbf{r-r'}\right) d\mathbf{r'}]_{j:}d\mathbf r.
+\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(\mathbf{r-r'}\right) dr'\right]_{j:} dr.
 \end{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex

@@
 
-We have a clear definition and where to stimulate and how to stimulate.
+We have a clear definition and where to stimulate and how to stimulate.\\
+\cut{This color is used to indicate bits we can get rid of if we dont have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
 

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
minor edits

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 
-Creating patient specific neural models has been approach from a number of different standpoints.
+Creating patient specific neural models has been approached from a number of different standpoints.
 \dean{need to add proper citations here.} Valdes et al.
@@
 \section{MRA of the IDE in State-Space}
-The multiresolution approximation (MRA) of the neural IDE is be obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
+The multiresolution approximation (MRA) of the neural IDE is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
 Considering a one-dimensional field, the connectivity kernel is decomposed by,
@@
 \end{align}
-The simplify the model we define the matrices
+In order to simplify the model we define the matrices
 \begin{align}\label{eq:Lambdax}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to results

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 \newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
-\newcommand{\cut}[1]{\textsf{\emph{\textbf{\textcolor{cyan}{#1}}}}}
+\newcommand{\cut}[1]{\textcolor{cyan}{#1}}
 
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The second terms in equations (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed before EM implementation which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.
-$\Xi$-variables can be calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$ and the cross-covariance matrix $\mathbf M_t$ using \cite{Gibsona2005}
+The second terms in Eqs.
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.
+$\Xi$-variables are calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$, and the cross-covariance matrix $\mathbf M_t$ using \cite{Gibsona2005}
 \begin{align}\label{eq:Xivariables}
 \boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
-\end{align}
-\section{Simulation}
-This section demonstrates the identification of the proposed IDE model.
-The MRA of a synthetic model is demonstrated, which is able to represent the system at different spatial scales.
-The spectral analysis was used to choose the spatial scale adequate to represent the spatial field.
-
-One second of data was generated using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} in response to an initial condition where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $ \eta(r-r')=1\times\phi_{4,3,-2}(r-r')$.
-Sampling time and the synaptic time constant are set to 1 and 10 milliseconds respectively.
-The sensors were arranged regularly where the distance between adjacent sensors was set to 0.5 mm resulting into 161 observation locations.
-Sensors are modelled using $\phi_{4,4,k}$, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
-The connectivity kernel and its decomposition are plotted in  \figurename{\ref{fig:KernelAndFreqResponse}} (a).
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+\end{align}
+\dean{Number of iterations and stopping criteria?}
+
+\section{Results}
+To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation} enabling a comparison between true and estimated parameters.
+100 realizations of 1 second of data were generated with an initial condition of $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=1\times\phi_{4,3,-2}(r-r')$.
+The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms respectively.
+The sensors were spaced regularly, where the distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
+The observation kernel width was set to \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
+The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).
+
 The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b).
 The observed field has an approximate spatial bandwidth $1.38$ cycles/mm.
-This suggests the use of wavelets up to level $j=3$.
-Field reconstruction at different level of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
-The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field.
-Root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:RMSE}}.
-The histogram of the parameter estimates in \figurename{\ref{fig:ParametersHistogram}} is generated using 100 runs of the EM algorithm, although the estimates of $\theta_1$ is biased (7.4 \%) the RMSE between the true and estimated kernels is $1.83$.
+This suggests the use of wavelets up to level $j=3$ \dean{since...
+why?}.
+
+Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
+\dean{Needs more info.} The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
+The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:RMSE}}.
+
+The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation.
+\dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)...
+There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
 \begin{figure}[!h]
@@
  \includegraphics[scale=1]{./Graph/Field.pdf}
- \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are
-shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$. (b) $j=1$, $n_x=33$. (c) $j=2$, $n_x=65$. (d) $j=3$, $n_x=131$. (e) $j=4$, $n_x=263$.}
+ \caption{\dean{the label a) is missing from the figure.} Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$.
+(b) $j=1$, $n_x=33$.
+(c) $j=2$, $n_x=65$.
+(d) $j=3$, $n_x=131$.
+(e) $j=4$, $n_x=263$.}
  \label{fig:FieldEstimates}
@@
  \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
-the solid lines show the actual parameter values and the dotted lines show the means of the estimated
-parameters. Left panel: The histogram of the central excitatory connectivity kernel basis function parameter
-estimates, $\theta_0$. Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter
-estimates, $\theta_1$.}
+the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.
+Left panel: The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.}
  \label{fig:ParametersHistogram}
  \end{figure}
+
+\section{Discussion}
+Some discussion points
+\begin{itemize}
+	\item Brief summary of the novel aspects
+	\item Discuss how we are improving the previous work
+	\item Discuss heterogeneity and time delays (at larger spatial scales) and homogeneity (at smaller scales) 
+	\item Discuss assumptions, limitations and future work
+\end{itemize}
 

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to EM

@@
 The E-step uses the estimate of $\boldsymbol\theta$, $\boldsymbol\theta'$ and the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} to estimate the posterior state sequence.
+In this paper we use a standard EM methodology.
+Therefore, we only describe aspects of the algorithm that are specific to MRA neural field equations due to the space limitations.
 The bound on the log-likelihood is a quadratic in the form of
@@
 \section{Results}
-To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation} enabling a comparison between true and estimated parameters.
+To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
 100 realizations of 1 second of data were generated with an initial condition of $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=1\times\phi_{4,3,-2}(r-r')$.
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms respectively.
-The sensors were spaced regularly, where the distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
+The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
 The observation kernel width was set to \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
added stoping criteria to EM
fixed the label of Fig3

@@
 \end{align}
-\dean{Number of iterations and stopping criteria?}
+\dean{Number of iterations and stopping criteria?}The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
 
@@
  \includegraphics[scale=1]{./Graph/Field.pdf}
- \caption{\dean{the label a) is missing from the figure.} Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$.
+ \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$.
 (b) $j=1$, $n_x=33$.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
deleted some of the top matter junk, mostly to see if I can push to the repo
been ruthless with the first paragraph of the state and parameter estimation bit

@@
-%% bare_jrnl.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-
  % TO DELETE
@@
 
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
+\usepackage{cite}
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
 \ifCLASSINFOpdf
@@
 \fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
 
-% *** MATH PACKAGES ***
-%
 \usepackage[cmex10]{amsmath}
 \interdisplaylinepenalty=2500
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
 \usepackage{amssymb}
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-% \usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e 
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-% \usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
 \ifCLASSOPTIONcompsoc
@@
 
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
 \usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
-% This package may be useful when used in conjunction with IEEEtran.cls'
-% captionsoff option. Some IEEE journals/societies require that submissions
-% have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.3.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% For subfigure.sty:
-% \let\MYorigsubfigure\subfigure
-% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat/subfig command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-% \hyphenation{op-tical net-works semi-conduc-tor}
-% Algorithms
 \usepackage{float}
@@
 \section{State and Parameter Estimation}
-The state-space representation allows the use of the expectation maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from the electrophysiological data.
-The EM algorithm is a two-part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters (M-step) and the posterior distribution of the field weights (E-step).
-The M-step finds an estimate of $\boldsymbol\theta$ that maximizes the lower bound, $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$, of the complete-data log-likelihood,  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$.
-The E-step uses the estimate of $\boldsymbol\theta$, $\boldsymbol\theta'$ and the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} to estimate the posterior state sequence.
-In this paper we use a standard EM methodology.
-Therefore, we only describe aspects of the algorithm that are specific to MRA neural field equations due to the space limitations.
-The bound on the log-likelihood is a quadratic in the form of
+
+The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
+The EM algorithm, when used to in this context \cite{Dewar,Scerri,Freestone}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+We use the standard EM-based approach for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
+EM essentially iteratively finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
+For a multivariate linear dynamic system, the bound used is a quadratic of the form
 \begin{equation}
@@
 \end{equation}
-with a maximum at
+which has a maximum at
 \begin{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
still hacking on the first para of sec 4

@@
 The EM algorithm, when used to in this context \cite{Dewar,Scerri,Freestone}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM-based approach for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially iteratively finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
had a crack at tidying up the last bit of §4. Made two suggestions for cuts.

@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar,Scerri,Freestone}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009,Freestone2011}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially iteratively finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
+EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
 For a multivariate linear dynamic system, the bound used is a quadratic of the form
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.
-$\Xi$-variables are calculated using the smoother outputs, i.e., state estimates, $\hat{\mathbf x}_t$ along with their covariance matrix, $\mathbf P_t$, and the cross-covariance matrix $\mathbf M_t$ using \cite{Gibsona2005}
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.\cut{The second terms in Eqs.
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel \cite{Rauch}(RTS) smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_t,\mathbf{x}_{t-1})$
 \begin{align}\label{eq:Xivariables}
@@
 \end{align}
-\dean{Number of iterations and stopping criteria?}The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.
+
+Hence, the algorithm has two distinct steps: the E-step which computes $\Xi_0$ and $\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge; multiple restarts are required to avoid convergence on a local maxima.
+
+\cut{\dean{Number of iterations and stopping criteria?}The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.}
 

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to result section

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
+%% bare_jrnl.tex
+%% V1.3
+%% 2007/01/11
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.7 or later) with an IEEE journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
+%% and
+%% http://www.ieee.org/
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. IEEE's font choices can trigger bugs that do  ***
+% *** not appear when using other class files.                            ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%
+%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
+%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
+%%*************************************************************************
+
+% Note that the a4paper option is mainly intended so that authors in
+% countries using A4 can easily print to A4 and see how their papers will
+% look in print - the typesetting of the document will not typically be
+% affected with changes in paper size (but the bottom and side margins will).
+% Use the testflow package mentioned above to verify correct handling of
+% both paper sizes by the user's LaTeX system.
+%
+% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
+% should be used if it is desired that the figures are to be displayed in
+% draft mode.
+
  % TO DELETE
@@
 
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
 \usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
 
+% *** GRAPHICS RELATED PACKAGES ***
+%
 \ifCLASSINFOpdf
@@
 \fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at: 
+% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
+% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
 
+% *** MATH PACKAGES ***
+%
 \usepackage[cmex10]{amsmath}
 \interdisplaylinepenalty=2500
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
 \usepackage{amssymb}
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+% *** ALIGNMENT PACKAGES ***
+%
+% \usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e 
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+%\usepackage{mdwmath}
+%\usepackage{mdwtab}
+% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
+% especially mdwmath.sty and mdwtab.sty which are used to format equations
+% and tables, respectively. The MDWtools set is already installed on most
+% LaTeX systems. The lastest version and documentation is available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+%\usepackage{eqparbox}
+% Also of notable interest is Scott Pakin's eqparbox package for creating
+% (automatically sized) equal width boxes - aka "natural width parboxes".
+% Available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+
+% *** SUBFIGURE PACKAGES ***
+% \usepackage[tight,footnotesize]{subfigure}
+% subfigure.sty was written by Steven Douglas Cochran. This package makes it
+% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
+% work, it is a good idea to load it with the tight package option to reduce
+% the amount of white space around the subfigures. subfigure.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at:
+% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
+% subfigure.sty has been superceeded by subfig.sty.
  \ifCLASSOPTIONcompsoc
@@
 
+%\usepackage[caption=false]{caption}
+%\usepackage[font=footnotesize]{subfig}
+% subfig.sty, also written by Steven Douglas Cochran, is the modern
+% replacement for subfigure.sty. However, subfig.sty requires and
+% automatically loads Axel Sommerfeldt's caption.sty which will override
+% IEEEtran.cls handling of captions and this will result in nonIEEE style
+% figure/table captions. To prevent this problem, be sure and preload
+% caption.sty with its "caption=false" package option. This is will preserve
+% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
+% (recommended due to many improvements over 1.2) of subfig.sty supports
+% the caption=false option directly:
+%\usepackage[caption=false,font=footnotesize]{subfig}
+%
+% The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+% The latest version and documentation of caption.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
 \usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Documentation is contained in the stfloats.sty comments as well as in the
+% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
+% does not allow \baselineskip to stretch. Authors submitting work to the
+% IEEE should note that IEEE rarely uses double column equations and
+% that authors should try to avoid such use. Do not be tempted to use the
+% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
+% not format its papers in such ways.
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
+% This package may be useful when used in conjunction with IEEEtran.cls'
+% captionsoff option. Some IEEE journals/societies require that submissions
+% have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.3.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% For subfigure.sty:
+% \let\MYorigsubfigure\subfigure
+% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat/subfig command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
+% Read the url.sty source comments for usage information. Basically,
+% \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+% \hyphenation{op-tical net-works semi-conduc-tor}
+% Algorithms
 \usepackage{float}
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-The $m^{th}$ order compactly supported \dean{(is there a non-compactly supported B-spline?)} B-spline wavelet function is defined as (see \cite{Chui1992})
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. The $m^{th}$ order B-spline wavelet function is defined as (see \cite{Chui1992}) 
 \begin{align}
@@
 \section{State and Parameter Estimation}
-
-The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar,Scerri,Freestone}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially iteratively finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
-For a multivariate linear dynamic system, the bound used is a quadratic of the form
+The state-space representation allows the use of the expectation maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from the electrophysiological data.
+The EM algorithm is a two-part iterative algorithm that yields the maximum likelihood estimate of the connectivity kernel parameters (M-step) and the posterior distribution of the field weights (E-step).
+The M-step finds an estimate of $\boldsymbol\theta$ that maximizes the lower bound, $\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)$, of the complete-data log-likelihood,  $p\left(\mathbf{X},\mathbf{Y} \mid \boldsymbol\theta \right)$.
+The E-step uses the estimate of $\boldsymbol\theta$, $\boldsymbol\theta'$ and the Rauch Tung Striebel (RTS) smoother \cite{Gibsona2005} to estimate the posterior state sequence.
+In this paper we use a standard EM methodology.
+Therefore, we only describe aspects of the algorithm that are specific to MRA neural field equations due to the space limitations.
+The bound on the log-likelihood is a quadratic in the form of
 \begin{equation}
@@
 \end{equation}
-which has a maximum at
+with a maximum at
 \begin{align}
@@
 To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated with an initial condition of $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=1\times\phi_{4,3,-2}(r-r')$.
+100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$.
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms respectively.
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-The observation kernel width was set to \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
+\parham{The observation kernel is modeled by $\phi_{4,k}(r-r')$} \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
 The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).
 
-The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b).
-The observed field has an approximate spatial bandwidth $1.38$ cycles/mm.
-This suggests the use of wavelets up to level $j=3$ \dean{since...
-why?}.
+The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
+This suggests the use of wavelets up to level $j=3$ (with the bandwidth $\approx[4.8,8]$ cycles/mm) can fully represent the field.
+Note that wavelets due to their bandpass filter characteristics extract successively lower and lower frequency components.
 
@@
 the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.
-Left panel: The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.}
+(a) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(b) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.}
  \label{fig:ParametersHistogram}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
removed a rogue 'herein'

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009,Freestone2011}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
wrote down the likelhiood

@@
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
+EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
 For a multivariate linear dynamic system, the bound used is a quadratic of the form

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009,Freestone2011}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
 For a multivariate linear dynamic system, the bound used is a quadratic of the form

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
removed ref for Freestone w.r.t. EM

@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009,Freestone2011}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
juggled some citations

@@
 
-The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
+The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,} to infer both the kernel and the field from electrophysiological data.
 The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97,Shumway2000} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 
-The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,} to infer both the kernel and the field from electrophysiological data.
+The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
 The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to result section

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
+The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009,Freestone2011}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence herein only describe aspects of the algorithm that are specific to MRA neural field equations.
+EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood function.
 For a multivariate linear dynamic system, the bound used is a quadratic of the form
@@
 The EM algorithm iterates between these two steps until the parameter estimates converge; multiple restarts are required to avoid convergence on a local maxima.
-
-\cut{\dean{Number of iterations and stopping criteria?}The stopping criterion is usually associated  with  either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}.}
 

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
comment about notation

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 \end{align}
-The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\mike{you need to define and sort out the []_{ij} notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
added citation for EM

@@
 The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97,Shumway2000} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
@@
 \end{align}
-\mike{you need to define and sort out the []_{ij} notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
+The $\left(i,j\right)^{th}$ block of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
removed cite to Ken's paper w.r.t. EM

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+The EM algorithm, when used to in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97,Shumway2000} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
oops made a typo. killed it

@@
 
-\author{In no particular order: P. Aram, M. Dewar, D.R. Freestone, K.Scerri, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
+\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone}, \ken{K.Scerri}, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
 \thanks{P.
@@
 \end{align}
-\mike{you need to define and sort out the []_{ij} notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\mike{you need to define and sort out the $[]_{ij}$ notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar2009,Scerri2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+The EM algorithm, when used to in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
@@
 The $\left(i,j\right)^{th}$ block of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\mike{you need to define and sort out the $[]_{ij}$ notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
resolved the conflict
updated the plots

@@
 The $\left(i,j\right)^{th}$ block of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
-\mike{you need to define and sort out the $[]_{ij}$ notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
+\mike{you need to define and sort out the $[]_{ij}$ notation!}
 \begin{align}
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel \cite{Rauch}(RTS) smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_t,\mathbf{x}_{t-1})$
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_t,\mathbf{x}_{t-1})$
 \begin{align}\label{eq:Xivariables}
@@
 Hence, the algorithm has two distinct steps: the E-step which computes $\Xi_0$ and $\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge; multiple restarts are required to avoid convergence on a local maxima.
+The EM algorithm iterates between these two steps until the parameter estimates converge; \parham{ we dont have local maxima here?} multiple restarts are required to avoid convergence on a local maxima.
 
@@
 The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
-This suggests the use of wavelets up to level $j=3$ (with the bandwidth $\approx[4.8,8]$ cycles/mm) can fully represent the field.
-Note that wavelets due to their bandpass filter characteristics extract successively lower and lower frequency components.
+This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field.
+Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.
 
 Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
-\dean{Needs more info.} The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
-The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:RMSE}}.
+\dean{Needs more info.} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
+The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a).
 
@@
  \centering
- %\includegraphics[width=0.5\textwidth]{./Graph/RMSE.pdf}
-\includegraphics[scale=1]{./Graph/RMSE.pdf}
- \caption{RMSE of the estimated field at different spatial resolution.}
- \label{fig:RMSE}
- \end{figure} 
-\begin{figure}[!h] 
- \centering
  \includegraphics[scale=1]{./Graph/Field.pdf}
@@
  \includegraphics[scale=1]{./Graph/Hist.pdf}
- \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
-the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.
-(a) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(b) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.}
+ \caption{(a) RMSE of the estimated field at different spatial resolution, $j$.
+(b) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(c) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
+Histograms are obtained over 100 realizations.
+In each of the histograms
+the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
  \label{fig:ParametersHistogram}

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_t,\mathbf{x}_{t-1})$
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
 \begin{align}\label{eq:Xivariables}
@@
 
-Hence, the algorithm has two distinct steps: the E-step which computes $\Xi_0$ and $\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
 The EM algorithm iterates between these two steps until the parameter estimates converge; \parham{ we dont have local maxima here?} multiple restarts are required to avoid convergence on a local maxima.

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to paper

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
-\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}}% <-this % stops a space
+\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}
+\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
+of Electrical and Electronic Engineering, The University of Melbourne, VIC 3010, Australia {\tt\small dfreestone@bionicear.org, grayden@unimelb.edu.au}}}% <-this % stops a space
 %\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
@@
 %\boldmath
-% The Integro Difference Equation (IDE) is an increasingly popular model of spatio-temporal processes.
-Here we develop a Multiresolution Approximation (MRA) framework for the IDE based on semi-orthogonal cardinal B-spline wavelets.
+The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes.
+Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is approached in a Maximum Likelihood (ML) framework using the Expectation Maximisation (EM) algorithm.
-Examples are given to demonstrate the features of the model.
+Examples are given to demonstrate the framework.
 \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the journal you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals frown on math
-% in the abstract anyway.
 
@@
 \begin{IEEEkeywords}
-Neural field model, multiresolution approximation (MRA), expectation maximization (EM) algorithm, wavelets.
+Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
 \end{IEEEkeywords}
@@
 We have a clear definition and where to stimulate and how to stimulate.\\
-\cut{This color is used to indicate bits we can get rid of if we dont have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
+\cut{This color is used to indicate bits we can get rid of if we don't have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
 
 \section{Introduction}
-\IEEEPARstart{T}{his} paper introduces a multiresolution data-driven framework for neural field modeling.
-Neural field models describe the meso and macroscopic dynamics of the human brain.
-Modeling the brain at this level is extremely important, since diseases such as epilepsy and \parham{Parkinson's disease} are manifested at this scale through pathological oscillations.
-The ability to create patient-specific neural field models will not only contribute to our knowledge base of poorly understood diseases such as epilepsy, but may also enable the development of new treatment strategies.
+\IEEEPARstart{T}{he} human brain has an inherent multiresolution architecture.
+Spatial scales of information processing and transfer range from individual proteins in synapses, to neurons, to networks of neurons.
+The multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
+This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integrodifference equation (MRAIDE), to address this challenge.
+Neural field models typically describe the meso and macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
+
+The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and furthermore, may also enable the development of new treatment strategies.
 This is particularly poignant with the advent of new devices that use therapeutic electrical stimulation.
@@
 (2011), where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate state and parameter estimation.
-The basis function decomposition in this previous study did not account for all of the spatial dynamics.
+The basis function decomposition in this previous study did not account for multiresolution architecture and spatial dynamics of the human cortex.
 Thus, it can be improved..
@@
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
+The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
 \dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
-The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The observation equation describing the electrophysiological recordings is given by
+
+The observation equation describing the electrophysiological recordings is given by 
 \begin{equation}\label{eq:ObservationEquation}
@@
 
-% \section{B-spline wavelet IDE model}
 The multiresolution approximation can be implemented using various classes of scaling and wavelet functions.
@@
 \section{State and Parameter Estimation}
-
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{The observation kernel is modeled by $\phi_{4,k}(r-r')$} \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
+\parham{The observation kernel is modeled by $\phi_{4,k}(r-r')$} \dean{this sounds like you are saying that we used a field basis function as the observation kernel.
+This is hard to justify, because no one will expect the field to be directly related to the sensors.
+Is it just a coincidence they are the same width?
+If so, why not just say we used a B-spline function with width ---?
+Maybe I am missing something.}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
 The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
edits to paper

@@
 This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integrodifference equation (MRAIDE), to address this challenge.
+
 Neural field models typically describe the meso and macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-
 The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and furthermore, may also enable the development of new treatment strategies.
@@
 (2008), Daunizeau et al.
-(2009), and Freestone et al (2011) developed the estimation frameworks for continuum neural field equations that explain the richer dynamics of spatiotemporal neural fields.
+(2009), and most recently Freestone et al (2011) developed the estimation frameworks for continuum neural field equations that explain the richer dynamics of spatiotemporal neural fields.
 

### 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
added refs

--- 2011-02-28 Multiresolution_framework/ltx/manuscript.tex
@@
 Creating patient specific neural models has been approached from a number of different standpoints.
-\dean{need to add proper citations here.} Valdes et al.
-(1999) used the neural mass model of Lopes Da Silva (1976) and Zetterberg et al.
-(1978) to fit EEG data.
-This approach was extended by David and Friston (2003) to coupled neural masses (using the equations of Jansen and Ritt (1995)) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM).
-Following this work, Galka et al.
-(2008), Sauer et al.
-(2008), Daunizeau et al.
-(2009), and Freestone et al (2011) developed the estimation frameworks for continuum neural field equations that explain the richer dynamics of spatiotemporal neural fields.
+The first work describing data driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
+This approach was extended to coupled neural masses (using another model~\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
+Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
+Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 
-This paper is an extension to the framework presented Freestone et al.
-(2011), where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate state and parameter estimation.
+This paper is an extension to this recent study~\cite{Freestone2011}.
 The basis function decomposition in this previous study did not account for multiresolution architecture and spatial dynamics of the human cortex.

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to intro

@@
 \thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, VIC 3010, Australia {\tt\small dfreestone@bionicear.org, grayden@unimelb.edu.au}}}% <-this % stops a space
+of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia,  {\tt\small dfreestone@bionicear.org, grayden@unimelb.edu.au}}}% <-this % stops a space
 %\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
@@
 
-We have a clear definition and where to stimulate and how to stimulate.\\
-\cut{This color is used to indicate bits we can get rid of if we don't have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
+% We have a clear definition and where to stimulate and how to stimulate.\\
+% \cut{This color is used to indicate bits we can get rid of if we don't have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
 
 \section{Introduction}
-\IEEEPARstart{T}{he} human brain has an inherent multiresolution architecture.
-Spatial scales of information processing and transfer range from individual proteins in synapses, to neurons, to networks of neurons.
+\IEEEPARstart{T}{he} human brain has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses, to neurons, to networks of neurons.
 The multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 This is particularly poignant with the advent of new devices that use therapeutic electrical stimulation.
-Presently, stimulation strategies for devices using corrective or modulating electrical stimulation operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
+Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
 Therefore, there exists an enormous potential to improve the performance of these devices using systems theory.
@@
 
-Creating patient specific neural models has been approached from a number of different standpoints.
 The first work describing data driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
@@
 \section{Integro-Difference Equation Neural Field Model}
-The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see \dean{cite NeuroImage paper} for a full derivation)
+The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
 \begin{equation}\label{eq:DiscreteTimeModel}
@@
 where $ x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$.
-% A  two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up  using the tensor-product approach \cite{Meyer1992,Mallat1998}. We write the 2-D scaling function as
-% \begin{equation}
-%  \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
-% \label{eq:2Dscalingfunction}
-% \end{equation}
-% and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as
-% \begin{equation}
-%  \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
-% \label{eq:2Dwavelet_1}
-% \end{equation}
-% \begin{equation}
-%  \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
-% \label{eq:2Dwavelet_2}
-% \end{equation}
-% \begin{equation}
-%  \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
-% \label{eq:2Dwavelet_3}
-% \end{equation}
-% for $j \in \mathbb{Z}$ and, $\mathbf{l} \in \mathbb{Z}^2$, where $\psi_{j,\mathbf{l}}^{(1)},  \psi_{j,\mathbf{l}}^{(2)}$ and $\psi_{j,\mathbf{l}}^{(3)} $ extract fine features of the 2-D field at vertical, horizontal and diagonal orientations respectively.
-% This can be generalised to $d$-dimensional MRA by introducing the scaling function
-% \setlength{\arraycolsep}{0.0em}
-% \begin{eqnarray}
-%   \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\
-%  &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
-% \end{eqnarray}
-% \setlength{\arraycolsep}{5pt}
-% and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
-Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by
-% \setlength{\arraycolsep}{0.0em}
-% \begin{eqnarray}
-%  k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
-% &+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 
-% \label{eq:MultidimensionalKernelExpansion}
-% \end{eqnarray}
-% \setlength{\arraycolsep}{5pt}
-% \begin{equation}
-% z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)
-% \label{eq:MultidimensionalFieldExpansion}
-% \end{equation}
-Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
+
+Eqs.
+\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
 Therefore, the field and the connectivity kernel is approximated by
@@
 \end{align}
-where the unknown parameter and state vectors \dean{(block matrices?)}, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
+where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
 \begin{align}
@@
 \end{align}
-The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
+The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
 Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
 
-The vectors \dean{(block matrices?)} of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
+The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
 \begin{align}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to bib

@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.%\cut{The second terms in Eqs.
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
+The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
 \begin{align}\label{eq:Xivariables}
@@
 \end{align}
-
 Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge; \parham{ we dont have local maxima here?} multiple restarts are required to avoid convergence on a local maxima.
+The EM algorithm iterates between these two steps until the parameter estimates converge.
 
@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{The observation kernel is modeled by $\phi_{4,k}(r-r')$} \dean{this sounds like you are saying that we used a field basis function as the observation kernel.
-This is hard to justify, because no one will expect the field to be directly related to the sensors.
-Is it just a coincidence they are the same width?
-If so, why not just say we used a B-spline function with width ---?
-Maybe I am missing something.}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
+The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
 The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).
@@
  \includegraphics[scale=1]{./Graph/Hist.pdf}
- \caption{(a) RMSE of the estimated field at different spatial resolution, $j$.
-(b) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
-(c) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.
-Histograms are obtained over 100 realizations.
-In each of the histograms
-the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
+ \caption{(a) RMSE of the estimated field at different spatial scales.
+(b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
+The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
  \label{fig:ParametersHistogram}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to discussion

@@
 functions (dashed lines), representing local excitation and lateral inhibition.
-(b) The average (over time) power in dB of the spatial frequency of the observations generated by the kernel in (a).
+(b) The average (over time) power in dB of the spatial frequency of the observations.
 The dashed line shows the cutoff frequency (-3 dB point).}
@@
  \includegraphics[scale=1]{./Graph/Field.pdf}
- \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$.
+ \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions.
+(a) $j=0$, $n_x=17$.
 (b) $j=1$, $n_x=33$.
@@
 \section{Discussion}
-Some discussion points
-\begin{itemize}
-	\item Brief summary of the novel aspects
-	\item Discuss how we are improving the previous work
-	\item Discuss heterogeneity and time delays (at larger spatial scales) and homogeneity (at smaller scales) 
-	\item Discuss assumptions, limitations and future work
-\end{itemize}
+In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
+
+This work extends previous work by... alternative ARMA model...
+
+Other groups have previously highlighted the importance of a multiresolution approach in neural field modeling.
+For example, it is thought that the connectivity structure differs at different spatial scales, where at a fine scale a homogeneous connectivity exists and at a larger scale the connectivity become~\cite{Qubbaj2009}....
+
+In order to apply the framework to real data several assumptions must be made, such as stationarity of the parameters over the estimation period.
+Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
+The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
+An obvious discrepancy is, for example, the linear activation function.
+Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
+Furthermore, the theory presented in this paper can be adapted to more sophisticated nonlinear forms of the field equations.
+The key development in this paper is the multiresolution decomposition forming the state-space model, which holds for a nonlinear activation function.
+If a nonlinear activation function was used, then unscented RTSS should be used in the E-step of the estimation algorithm.
+
+Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.
+Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.
+Most importantly, future work should be directed towards applying and validating the framework on real data.
 

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to intro
edits to discussion

@@
 \title{Multiresolution Neural Field Estimation }
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
 
-\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone}, \ken{K.Scerri}, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
+\author{In no particular order: \parham{P.
+Aram}, \mike{M.
+Dewar}, \dean{D.R.
+Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B.
+Grayden,~\IEEEmembership{Member,~IEEE,} and V.
+Kadirkamanathan % <-this % stops a space
 \thanks{P.
@@
 %\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
 
@@
 
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
 % make the title area
@@
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-%  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
-%  \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
-
-% We have a clear definition and where to stimulate and how to stimulate.\\
-% \cut{This color is used to indicate bits we can get rid of if we don't have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
 
@@
 \dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
+A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
 
@@
 \begin{equation}\label{eq:ObservationEquation}
-	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
+	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
 \end{equation}
@@
 The superscript $\top$ denotes the transpose operator.
-
 \section{MRA of the IDE in State-Space}
@@
 Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
-
 \section{State and Parameter Estimation}
@@
 
-This work extends previous work by... alternative ARMA model...
+This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems, ....
 
@@
 
-% In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
-% Note that the number of translation operations depends on the spatial range of the data.
-It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively.
-The estimated kernel in \figurename{\ref{fig:SpatialMixingKernelEstimate} } is obtained for the cubic B-spline, with initial scale 0 and maximum scale 1.
-The EM algorithm is allowed to run for 30 iterations to avoid any issues regarding early stopping, though typically the change in $\parallel \mathbf{A} \parallel_{F}$ falls below $10^{-4} $ after less than 15 iterations.
-A total number of 500 estimation experiments are performed, where $v_t$ and $w_t$ are re-generated each trial.
-
-%  The performance measure employed here is the Mean Integrated Squared Error (MISE) defined as
-% \begin{equation}
-%  \mathbf{E}\left[\int_{\mathcal{S}}\left[e\left(s\right) \right]^2ds  \right]
-% \label{MISE} 
-% \end{equation}
-%  where  $e\left(s\right)$ is the error between the unknown function, $f\left( s\right) $ and its estimate, $\hat{f}\left( s\right) $.
-In this example the original kernel and the field are known and hence the integral in  (\ref{MISE}) can be computed analytically.
-For spatial mixing kernel we have
-% \begin{eqnarray}
-%  \lefteqn{\int_{\mathcal{S}}\left[e\left(s\right)\right]^2ds}\nonumber \\  &=\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)^\top\left[ \int_{\mathcal{S}}\boldsymbol\lambda\left(s\right)\boldsymbol\lambda\left(s\right)^\top ds\right] \left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)&
-% \label{MISEKernel}
-% \end{eqnarray}
-%   Here, we are particularly interested in assessing the performance improvement as the scale of the details in MRA is increased.
-Performance based on (\ref{MISEKernel}) at different spatial scales and over 500 trials have been evaluated.
-The MISE of the model at $j=0$ is 0.024 and reduces to 0.005 when $\psi_{4;1,k}$ terms are also included in the model, in fact estimation performance is improved by a factor of 4.8.
-The coarsest approximation of the kernel along with its approximation at $j=1$ are illustrated in \figurename{\ref{fig:SpatialMixingKernelEstimate}.
-It can be seen that the model is able to estimate both slowly and rapidly varying segments of the  kernel with very high accuracy.
-Field estimates  at a selection of time instants are shown in \figurename{\ref{fig:1DFieldEstimation}}.
-It is clearly observed that the coarse and fine features of the original field have been captured accurately over regions where observations are available.
-Observation locations are generated randomly, as shown in \figurename{ \ref{fig:FieldVariance}}.
-Assuming the observed field can be fully described by the  decomposed IDE model, the variance of the field can be computed to express the  uncertainty of the estimation, at each point in space and at time $t$ we have
-% \begin{equation}
-%  \text{Var}(\hat z_t(s_i))=\boldsymbol\mu^{\top}(s_i) \mathbf P_{t|T}\boldsymbol\mu(s_i)
-% \label{eq:FieldVariance}
-% \end{equation}
-% where $\mathbf P_{t|T} $ is the covariance matrix associated with the  state estimates obtained from the RTS smoother.
-Variance based on (\ref{eq:FieldVariance}) at each spatial location and at $t=50$ is shown in \figurename{\ref{fig:FieldVariance}}.
-The uncertainty of the estimation is higher at almost  every spatial location at $j=1$ compared to $j=0$.
-This is to be expected as there are more wavelet basis functions at higher resolution and hence more associated weights need to be estimated.
-Peaks in the variance of the field coincide with regions where no observations have been made.
-Increasing the number of observation locations, or using equally spaced observation locations would reduce the variance of the field estimation.
-% \begin{figure}[!h] 
-% \centering
-% \includegraphics[width=0.5\textwidth]{./Graph/aram4.eps}
-% \caption{Variance of the field at each spatial location for $j=0$ (dotted line) and $j=1$ (solid line). The observation locations are described with a cross.}
-% \label{fig:FieldVariance}
-% \end{figure} 
-% \begin{table}[!h]
-% \renewcommand{\arraystretch}{1.3}
-% \caption {MISE  at particular scale between measured and estimated 2D-field  at a particular time}
-% \label{table:ValidationResultField}
-% \centering
-% \begin{tabular}{cccc}
-% \hline \hline
-% \multicolumn{2}{r}{Time}&\multicolumn{2}{c}{MISE} \\
-% \cline{3-4}
-% &&$j=0$&$j=1$ \\ 
-% \hline 
-% &$5$ &$5.424$&$0.609$ \\
-% &$20$ &$5.422$&$0.596$ \\
-% &$50$ &$5.519$&$0.626$ \\
-% &$100$ &$5.488$&$0.611$ \\
-% &$150$ &$5.494$&$0.587$ \\
-% \hline \hline
-% \end{tabular}
-% \end {table}
-% \section{Conclusion}
-% A multi-resolution approach to modelling spatio-temporal systems has been presented.
-This model is able to represent continuous-space, discrete-time dynamics at a number of spatial scales simultaneously.
-This ability greatly extends the class of system which the Integro-Difference Equation can represent.
-% 
-% 
-% By decomposing both the spatial field and the spatial mixing kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
-This is an essential component of any practical spatio-temporal model, without which the model must be artificially separated into global and local modes a-priori.
-% 
-% 
-% The complexity of the model is not affected by the spatial resolution of the observation process, rather it reflects the underlying complexity of the system under study.
-Therefore, increasing the resolution at which the system is observed does not necessarily increase the complexity of the system identification problem.
-However the developed algorithm is sensitive to the state dimension, equivalent to the detail represented in the field, and hence intelligent approaches to reduce the number of basis functions is noted as future work.
-% 
-% By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework.
-Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-% \appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-% \newtheorem{lemma}{Lemma}
-% \begin{lemma}
-% Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively.
-Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by
-% \setlength{\arraycolsep}{0.0em}
-% \begin{eqnarray}
-% \left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
-% &=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
-% \end{eqnarray}
-% \setlength{\arraycolsep}{5pt}
-% \label{lemma:InProduct}
-% \end{lemma}
-% \begin{IEEEproof}
-% The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
-% \begin{equation}
-%  N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
-% \label{SymmetrySplieEq}
-% \end{equation}
-% A direct consequence of (\ref{SymmetrySplieEq}) is 
-% \begin{equation}
-%  N_{m}\left(s\right)=N_{m}\left(m-s\right)
-% \end{equation}
-% Therefore
-% \setlength{\arraycolsep}{0.0em}
-% \begin{IEEEeqnarray}{l}
-% \int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
-% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
-% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
-% \qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
-% \qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
-% \qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
-% \end{IEEEeqnarray}
-% \setlength{\arraycolsep}{5pt}
-% \end{IEEEproof}
-
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-
 % use section* for acknowledgement
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
   \newpage
@@
 
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% \begin{thebibliography}{1}
-% 
-% \bibitem{IEEEhowto:kopka}
-% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-% 
-%  \end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-% \begin{IEEEbiography}{Parham Aram}
-% 
-%  
-% \end{IEEEbiography}
-% 
-% \begin{IEEEbiography}{Visakan Kadirkamanathan}
-% % Biography text here.
-% (M’90) received the
-% B.A. and Ph.D. degrees in electrical and information
-% engineering from the University of Cambridge, U.K.
-% He held Research Associate positions at the University
-% of Surrey, U.K., and the University of Cambridge,
-% U.K., before joining the Department of Automatic
-% Control and Systems Engineering, The University
-% of Sheffield, U.K., as a Lecturer in 1993, where
-% he is currently a Professor of Signal and Information
-% Processing and is affiliated to the Centre for Signal
-% Processing and Complex Systems. His research interests
-% include nonlinear signal processing, system identification, intelligent control
-% and fault diagnosis with applications in systems biology, aerospace systems,
-% and wireless communication. He has coauthored a book on intelligent control
-% and has published more than 120 papers in refereed journals and proceedings of
-% international conferences.
-% Prof. Kadirkamanathan is the Co-Editor of the International Journal of Systems
-% Science and has served as an Associate Editor for the IEEE TRANSACTIONS
-% ON NEURAL NETWORKS and the IEEE TRANSACTIONS ON SYSTEMS, MAN, AND
-% CYBERNETICS, PART B.
-%  \end{IEEEbiography}
-% \begin{IEEEbiography}{Michael Dewar}
-%  received the M.Eng. degree in
-% control systems engineering and the Ph.D. degree
-% in systems engineering both from The University of
-% Sheffield, U.K., in 2002 and 2007, respectively.
-%  He is currently working as
-% a Research Associate in the Institute for Adaptive
-% and Neural Computation, School of Informatics,
-% The University of Edinburgh, U.K. 
-% \end{IEEEbiography}
-
-% if you will not have a photo at all:
-% \begin{IEEEbiographynophoto}{John Doe}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-% \begin{IEEEbiographynophoto}{Jane Doe}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to results

@@
 
-The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
+\cut{The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
 This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field.
-Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.
+Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
 

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
changed the notation for block matrix

@@
 \end{align}
-The $\left(i,j\right)^{th}$ block of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
-\mike{you need to define and sort out the $[]_{ij}$ notation!}
+\parham{where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix}
+  $\mathbf U$ is given by
 \begin{align}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
minor edits
trivial edits

--- 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
@@
 \title{Multiresolution Neural Field Estimation }
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
 
-\author{In no particular order: \parham{P.
-Aram}, \mike{M.
-Dewar}, \dean{D.R.
-Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B.
-Grayden,~\IEEEmembership{Member,~IEEE,} and V.
-Kadirkamanathan % <-this % stops a space
+\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone}, \ken{K.Scerri}, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
 \thanks{P.
@@
 (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
-\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}
-\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia,  {\tt\small dfreestone@bionicear.org, grayden@unimelb.edu.au}}}% <-this % stops a space
+\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}}% <-this % stops a space
 %\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
 
@@
 
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
 % make the title area
@@
 %\boldmath
-The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes.
-Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
+% The Integro Difference Equation (IDE) is an increasingly popular model of spatio-temporal processes.
+Here we develop a Multiresolution Approximation (MRA) framework for the IDE based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is approached in a Maximum Likelihood (ML) framework using the Expectation Maximisation (EM) algorithm.
-Examples are given to demonstrate the framework.
+Examples are given to demonstrate the features of the model.
 \end{abstract}
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the journal you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals frown on math
+% in the abstract anyway.
 
@@
 \begin{IEEEkeywords}
-Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+Neural field model, multiresolution approximation (MRA), expectation maximization (EM) algorithm, wavelets.
 \end{IEEEkeywords}
 
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+%  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
+%  \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
 
+We have a clear definition and where to stimulate and how to stimulate.\\
+\cut{This color is used to indicate bits we can get rid of if we dont have enough space, use the command: \textbackslash cut$\left\lbrace  \right\rbrace$}
+
 \section{Introduction}
-\IEEEPARstart{T}{he} human brain has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses, to neurons, to networks of neurons.
-The multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integrodifference equation (MRAIDE), to address this challenge.
-
-Neural field models typically describe the meso and macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and furthermore, may also enable the development of new treatment strategies.
+\IEEEPARstart{T}{his} paper introduces a multiresolution data-driven framework for neural field modeling.
+Neural field models describe the meso and macroscopic dynamics of the human brain.
+Modeling the brain at this level is extremely important, since diseases such as epilepsy and \parham{Parkinson's disease} are manifested at this scale through pathological oscillations.
+The ability to create patient-specific neural field models will not only contribute to our knowledge base of poorly understood diseases such as epilepsy, but may also enable the development of new treatment strategies.
 This is particularly poignant with the advent of new devices that use therapeutic electrical stimulation.
-Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
+Presently, stimulation strategies for devices using corrective or modulating electrical stimulation operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
 Therefore, there exists an enormous potential to improve the performance of these devices using systems theory.
@@
 
-The first work describing data driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
-This approach was extended to coupled neural masses (using another model~\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
-Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Creating patient specific neural models has been approached from a number of different standpoints.
+\dean{need to add proper citations here.} Valdes et al.
+(1999) used the neural mass model of Lopes Da Silva (1976) and Zetterberg et al.
+(1978) to fit EEG data.
+This approach was extended by David and Friston (2003) to coupled neural masses (using the equations of Jansen and Ritt (1995)) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM).
+Following this work, Galka et al.
+(2008), Sauer et al.
+(2008), Daunizeau et al.
+(2009), and Freestone et al (2011) developed the estimation frameworks for continuum neural field equations that explain the richer dynamics of spatiotemporal neural fields.
 
-This paper is an extension to this recent study~\cite{Freestone2011}.
-The basis function decomposition in this previous study did not account for multiresolution architecture and spatial dynamics of the human cortex.
+This paper is an extension to the framework presented Freestone et al.
+(2011), where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate state and parameter estimation.
+The basis function decomposition in this previous study did not account for all of the spatial dynamics.
 Thus, it can be improved..
@@
 \section{Integro-Difference Equation Neural Field Model}
-The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
+The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see \dean{cite NeuroImage paper} for a full derivation)
 \begin{equation}\label{eq:DiscreteTimeModel}
@@
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
+\dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
-\dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
-A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-
-The observation equation describing the electrophysiological recordings is given by 
+For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
-	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
+	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
 \end{equation}
@@
 The superscript $\top$ denotes the transpose operator.
+
 \section{MRA of the IDE in State-Space}
@@
 where $ x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$.
-
-Eqs.
-\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
+% A  two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up  using the tensor-product approach \cite{Meyer1992,Mallat1998}. We write the 2-D scaling function as
+% \begin{equation}
+%  \phi_{j,\mathbf{l}}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dscalingfunction}
+% \end{equation}
+% and three 2-D wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right)$ where $n=1,2,3$ as
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(1)}\left(r_1,r_2\right)=\phi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_1}
+% \end{equation}
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(2)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_2}
+% \end{equation}
+% \begin{equation}
+%  \psi_{j,\mathbf{l}}^{(3)}\left(r_1,r_2\right)=\psi_{j,l_1}\left(r_1\right)\psi_{j,l_2}\left(r_2\right)
+% \label{eq:2Dwavelet_3}
+% \end{equation}
+% for $j \in \mathbb{Z}$ and, $\mathbf{l} \in \mathbb{Z}^2$, where $\psi_{j,\mathbf{l}}^{(1)},  \psi_{j,\mathbf{l}}^{(2)}$ and $\psi_{j,\mathbf{l}}^{(3)} $ extract fine features of the 2-D field at vertical, horizontal and diagonal orientations respectively.
+% This can be generalised to $d$-dimensional MRA by introducing the scaling function
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+%   \phi_{j,\mathbf{l}}\left(r_1,r_2, \cdots r_d\right)&=&\phi_{j,l_1}\left(r_1\right)\phi_{j,l_2}\left(r_2\right) \cdots \phi_{j,l_d}\left(r_d\right) \label{eq:d-dimensionalscalingfunction}\\
+%  &&j \in \mathbb{Z}, \quad \mathbf{l} \in \mathbb{Z}^d \nonumber
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% and $2^d-1$ wavelet functions $ \psi^{(n)} \left(\mathbf{r}\right), n=1, \cdots,2^d-1$ with a procedure similar to the 2-D case.
+Using these basis functions, multi-dimensional MRA of the kernel and the field can be obtained by
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+%  k\left(\mathbf{r}-\mathbf{r'}\right)&=&\sum_{\mathbf{l}\in \mathbb{Z}^d}\alpha_{j_0,\mathbf{l}}\phi_{j_0,\mathbf{l}}\left(\mathbf{r}-\mathbf{r'}\right) \nonumber \\
+% &+&\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1}\beta_{j,\mathbf{l}}^{(i)} \psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}-\mathbf{r'}\right) 
+% \label{eq:MultidimensionalKernelExpansion}
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \begin{equation}
+% z_t\left(\mathbf{r}\right)=\sum_{\mathbf{l}\in \mathbb{Z}^d}x_{t,j_{0},\mathbf{l}}\phi_{j_{0},\mathbf{l}}\left(\mathbf{r}\right)+\sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l}\in \mathbb{Z}^d}\sum_{i=1}^{2^d-1} \check{x}_{t,j,\mathbf{l}}^{(i)}\psi_{j,\mathbf{l}}^{(i)}\left(\mathbf{r}\right)
+% \label{eq:MultidimensionalFieldExpansion}
+% \end{equation}
+Eqs \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
 Therefore, the field and the connectivity kernel is approximated by
@@
 \end{align}
-where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
+where the unknown parameter and state vectors \dean{(block matrices?)}, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
 \begin{align}
@@
 \end{align}
-The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
+The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively.
 Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
 
-The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
+The vectors \dean{(block matrices?)} of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
 \begin{align}
@@
 
+% \section{B-spline wavelet IDE model}
 The multiresolution approximation can be implemented using various classes of scaling and wavelet functions.
@@
 Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+
 \section{State and Parameter Estimation}
+
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
 The EM algorithm, when used to in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis97,Shumway2000} \mike{Roweis and Gharamani, 1997, A Unifying Review of Linear Guassian Models} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
- \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
  \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
-The $\left(i,j\right)^{th}$ block of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
-\mike{you need to define and sort out the $[]_{ij}$ notation!}
+\mike{you need to define and sort out the $[]_{ij}$ notation!}The $\left(i,j\right)^{th}$ element of the block matrix $\mathbf U_{n_x \times n_x}$ is given by
 \begin{align}
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.%\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
-The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.\cut{The second terms in Eqs.
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.} The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel \cite{Rauch}(RTS) smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_t,\mathbf{x}_{t-1})$
 \begin{align}\label{eq:Xivariables}
@@
 \end{align}
-Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge.
+
+Hence, the algorithm has two distinct steps: the E-step which computes $\Xi_0$ and $\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge; multiple restarts are required to avoid convergence on a local maxima.
 
@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
-The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
+\parham{The observation kernel is modeled by $\phi_{4,k}(r-r')$} \dean{?}, providing a width of 0.8 mm at half the maximum amplitude of the observation kernel, allowing for some cross talk in the recordings.
 The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).
@@
 The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
-This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field.
-Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.
+This suggests the use of wavelets up to level $j=3$ (with the bandwidth $\approx[4.8,8]$ cycles/mm) can fully represent the field.
+Note that wavelets due to their bandpass filter characteristics extract successively lower and lower frequency components.
 
 Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
-\dean{Needs more info.} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
-The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a).
+\dean{Needs more info.} The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
+The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:RMSE}}.
 
@@
 functions (dashed lines), representing local excitation and lateral inhibition.
-(b) The average (over time) power in dB of the spatial frequency of the observations.
+(b) The average (over time) power in dB of the spatial frequency of the observations generated by the kernel in (a).
 The dashed line shows the cutoff frequency (-3 dB point).}
@@
  \centering
+ %\includegraphics[width=0.5\textwidth]{./Graph/RMSE.pdf}
+\includegraphics[scale=1]{./Graph/RMSE.pdf}
+ \caption{RMSE of the estimated field at different spatial resolution.}
+ \label{fig:RMSE}
+ \end{figure} 
+\begin{figure}[!h] 
+ \centering
  \includegraphics[scale=1]{./Graph/Field.pdf}
- \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$.
+ \caption{Spatial field at one time instant for different spatial resolutions, estimated and true fields are shown by dashed and solid lines respectively; (a) $j=0$, $n_x=17$.
 (b) $j=1$, $n_x=33$.
@@
  \includegraphics[scale=1]{./Graph/Hist.pdf}
- \caption{(a) RMSE of the estimated field at different spatial scales.
-(b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
-The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
+ \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
+the solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.
+(a) The histogram of the central excitatory connectivity kernel basis function parameter estimates, $\theta_0$.
+(b) The histogram of the surround inhibition connectivity kernel basis function parameter estimates, $\theta_1$.}
  \label{fig:ParametersHistogram}
@@
 \section{Discussion}
-In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
+Some discussion points
+\begin{itemize}
+	\item Brief summary of the novel aspects
+	\item Discuss how we are improving the previous work
+	\item Discuss heterogeneity and time delays (at larger spatial scales) and homogeneity (at smaller scales) 
+	\item Discuss assumptions, limitations and future work
+\end{itemize}
 
-This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems, ....
+% In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
+% Note that the number of translation operations depends on the spatial range of the data.
+It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively.
+The estimated kernel in \figurename{\ref{fig:SpatialMixingKernelEstimate} } is obtained for the cubic B-spline, with initial scale 0 and maximum scale 1.
+The EM algorithm is allowed to run for 30 iterations to avoid any issues regarding early stopping, though typically the change in $\parallel \mathbf{A} \parallel_{F}$ falls below $10^{-4} $ after less than 15 iterations.
+A total number of 500 estimation experiments are performed, where $v_t$ and $w_t$ are re-generated each trial.
 
-Other groups have previously highlighted the importance of a multiresolution approach in neural field modeling.
-For example, it is thought that the connectivity structure differs at different spatial scales, where at a fine scale a homogeneous connectivity exists and at a larger scale the connectivity become~\cite{Qubbaj2009}....
+%  The performance measure employed here is the Mean Integrated Squared Error (MISE) defined as
+% \begin{equation}
+%  \mathbf{E}\left[\int_{\mathcal{S}}\left[e\left(s\right) \right]^2ds  \right]
+% \label{MISE} 
+% \end{equation}
+%  where  $e\left(s\right)$ is the error between the unknown function, $f\left( s\right) $ and its estimate, $\hat{f}\left( s\right) $.
+In this example the original kernel and the field are known and hence the integral in  (\ref{MISE}) can be computed analytically.
+For spatial mixing kernel we have
+% \begin{eqnarray}
+%  \lefteqn{\int_{\mathcal{S}}\left[e\left(s\right)\right]^2ds}\nonumber \\  &=\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)^\top\left[ \int_{\mathcal{S}}\boldsymbol\lambda\left(s\right)\boldsymbol\lambda\left(s\right)^\top ds\right] \left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}\right)&
+% \label{MISEKernel}
+% \end{eqnarray}
+%   Here, we are particularly interested in assessing the performance improvement as the scale of the details in MRA is increased.
+Performance based on (\ref{MISEKernel}) at different spatial scales and over 500 trials have been evaluated.
+The MISE of the model at $j=0$ is 0.024 and reduces to 0.005 when $\psi_{4;1,k}$ terms are also included in the model, in fact estimation performance is improved by a factor of 4.8.
+The coarsest approximation of the kernel along with its approximation at $j=1$ are illustrated in \figurename{\ref{fig:SpatialMixingKernelEstimate}.
+It can be seen that the model is able to estimate both slowly and rapidly varying segments of the  kernel with very high accuracy.
+Field estimates  at a selection of time instants are shown in \figurename{\ref{fig:1DFieldEstimation}}.
+It is clearly observed that the coarse and fine features of the original field have been captured accurately over regions where observations are available.
+Observation locations are generated randomly, as shown in \figurename{ \ref{fig:FieldVariance}}.
+Assuming the observed field can be fully described by the  decomposed IDE model, the variance of the field can be computed to express the  uncertainty of the estimation, at each point in space and at time $t$ we have
+% \begin{equation}
+%  \text{Var}(\hat z_t(s_i))=\boldsymbol\mu^{\top}(s_i) \mathbf P_{t|T}\boldsymbol\mu(s_i)
+% \label{eq:FieldVariance}
+% \end{equation}
+% where $\mathbf P_{t|T} $ is the covariance matrix associated with the  state estimates obtained from the RTS smoother.
+Variance based on (\ref{eq:FieldVariance}) at each spatial location and at $t=50$ is shown in \figurename{\ref{fig:FieldVariance}}.
+The uncertainty of the estimation is higher at almost  every spatial location at $j=1$ compared to $j=0$.
+This is to be expected as there are more wavelet basis functions at higher resolution and hence more associated weights need to be estimated.
+Peaks in the variance of the field coincide with regions where no observations have been made.
+Increasing the number of observation locations, or using equally spaced observation locations would reduce the variance of the field estimation.
+% \begin{figure}[!h] 
+% \centering
+% \includegraphics[width=0.5\textwidth]{./Graph/aram4.eps}
+% \caption{Variance of the field at each spatial location for $j=0$ (dotted line) and $j=1$ (solid line). The observation locations are described with a cross.}
+% \label{fig:FieldVariance}
+% \end{figure} 
+% \begin{table}[!h]
+% \renewcommand{\arraystretch}{1.3}
+% \caption {MISE  at particular scale between measured and estimated 2D-field  at a particular time}
+% \label{table:ValidationResultField}
+% \centering
+% \begin{tabular}{cccc}
+% \hline \hline
+% \multicolumn{2}{r}{Time}&\multicolumn{2}{c}{MISE} \\
+% \cline{3-4}
+% &&$j=0$&$j=1$ \\ 
+% \hline 
+% &$5$ &$5.424$&$0.609$ \\
+% &$20$ &$5.422$&$0.596$ \\
+% &$50$ &$5.519$&$0.626$ \\
+% &$100$ &$5.488$&$0.611$ \\
+% &$150$ &$5.494$&$0.587$ \\
+% \hline \hline
+% \end{tabular}
+% \end {table}
+% \section{Conclusion}
+% A multi-resolution approach to modelling spatio-temporal systems has been presented.
+This model is able to represent continuous-space, discrete-time dynamics at a number of spatial scales simultaneously.
+This ability greatly extends the class of system which the Integro-Difference Equation can represent.
+% 
+% 
+% By decomposing both the spatial field and the spatial mixing kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
+This is an essential component of any practical spatio-temporal model, without which the model must be artificially separated into global and local modes a-priori.
+% 
+% 
+% The complexity of the model is not affected by the spatial resolution of the observation process, rather it reflects the underlying complexity of the system under study.
+Therefore, increasing the resolution at which the system is observed does not necessarily increase the complexity of the system identification problem.
+However the developed algorithm is sensitive to the state dimension, equivalent to the detail represented in the field, and hence intelligent approaches to reduce the number of basis functions is noted as future work.
+% 
+% By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework.
+Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+% \appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+% \newtheorem{lemma}{Lemma}
+% \begin{lemma}
+% Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively.
+Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by
+% \setlength{\arraycolsep}{0.0em}
+% \begin{eqnarray}
+% \left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
+% &=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
+% \end{eqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \label{lemma:InProduct}
+% \end{lemma}
+% \begin{IEEEproof}
+% The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
+% \begin{equation}
+%  N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
+% \label{SymmetrySplieEq}
+% \end{equation}
+% A direct consequence of (\ref{SymmetrySplieEq}) is 
+% \begin{equation}
+%  N_{m}\left(s\right)=N_{m}\left(m-s\right)
+% \end{equation}
+% Therefore
+% \setlength{\arraycolsep}{0.0em}
+% \begin{IEEEeqnarray}{l}
+% \int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
+% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
+% \qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
+% \qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
+% \qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
+% \qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
+% \end{IEEEeqnarray}
+% \setlength{\arraycolsep}{5pt}
+% \end{IEEEproof}
 
-In order to apply the framework to real data several assumptions must be made, such as stationarity of the parameters over the estimation period.
-Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
-The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
-An obvious discrepancy is, for example, the linear activation function.
-Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-Furthermore, the theory presented in this paper can be adapted to more sophisticated nonlinear forms of the field equations.
-The key development in this paper is the multiresolution decomposition forming the state-space model, which holds for a nonlinear activation function.
-If a nonlinear activation function was used, then unscented RTSS should be used in the E-step of the estimation algorithm.
+%\appendices
+%\section{Proof of the First Zonklar Equation}
+%Appendix one text goes here.
 
-Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.
-Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.
-Most importantly, future work should be directed towards applying and validating the framework on real data.
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+%\section{}
+%Appendix two text goes here.
 
@@
 
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
   \newpage
@@
 
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+% \begin{thebibliography}{1}
+% 
+% \bibitem{IEEEhowto:kopka}
+% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+% 
+%  \end{thebibliography}
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+% \begin{IEEEbiography}{Parham Aram}
+% 
+%  
+% \end{IEEEbiography}
+% 
+% \begin{IEEEbiography}{Visakan Kadirkamanathan}
+% % Biography text here.
+% (M’90) received the
+% B.A. and Ph.D. degrees in electrical and information
+% engineering from the University of Cambridge, U.K.
+% He held Research Associate positions at the University
+% of Surrey, U.K., and the University of Cambridge,
+% U.K., before joining the Department of Automatic
+% Control and Systems Engineering, The University
+% of Sheffield, U.K., as a Lecturer in 1993, where
+% he is currently a Professor of Signal and Information
+% Processing and is affiliated to the Centre for Signal
+% Processing and Complex Systems. His research interests
+% include nonlinear signal processing, system identification, intelligent control
+% and fault diagnosis with applications in systems biology, aerospace systems,
+% and wireless communication. He has coauthored a book on intelligent control
+% and has published more than 120 papers in refereed journals and proceedings of
+% international conferences.
+% Prof. Kadirkamanathan is the Co-Editor of the International Journal of Systems
+% Science and has served as an Associate Editor for the IEEE TRANSACTIONS
+% ON NEURAL NETWORKS and the IEEE TRANSACTIONS ON SYSTEMS, MAN, AND
+% CYBERNETICS, PART B.
+%  \end{IEEEbiography}
+% \begin{IEEEbiography}{Michael Dewar}
+%  received the M.Eng. degree in
+% control systems engineering and the Ph.D. degree
+% in systems engineering both from The University of
+% Sheffield, U.K., in 2002 and 2007, respectively.
+%  He is currently working as
+% a Research Associate in the Institute for Adaptive
+% and Neural Computation, School of Informatics,
+% The University of Edinburgh, U.K. 
+% \end{IEEEbiography}
+
+% if you will not have a photo at all:
+% \begin{IEEEbiographynophoto}{John Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+% \begin{IEEEbiographynophoto}{Jane Doe}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
fixed hist plot

--- 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
@@
 \usepackage{cite}
+%Reduce the spacing between figures and captions
+% \usepackage[belowskip=-15pt,aboveskip=10pt]{caption}
+%  \setlength{\intextsep}{2pt plus 2pt minus 2pt}
 
@@
 Grayden,~\IEEEmembership{Member,~IEEE,} and V.
-Kadirkamanathan % <-this % stops a space
+Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
 \thanks{P.
@@
 (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
-\thanks{M. Dewar is with the School of Informatics, University of Edinburgh, Edinburgh, EH8 9AB, U.K. (e-mail:mike.dewar@inf.ed.ac.uk)}
 \thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia,  {\tt\small dfreestone@bionicear.org, grayden@unimelb.edu.au}}}% <-this % stops a space
+of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia, (e-mail: dfreestone@bionicear.org; grayden@unimelb.edu.au)}
+\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA (e-mail:mike.dewar@columbia.edu)}
+\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
+of Malta, Msida, MSD 2080, Malta (e-mail: kenneth.scerri@um.edu.mt).}}
+% <-this % stops a space
 %\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
@@
 \begin{equation}\label{eq:DiscreteTimeModel}
-	v_{t+T_s}\left(\mathbf{r}\right) = 
+	v_{t+1}\left(\mathbf{r}\right) = 
 	\xi v_t\left(\mathbf{r}\right) + 
@@
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-For simplicity, \cut{we denote the current time step by $t$ and the future time step by $t+1$.} The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
 \dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
@@
 \end{equation}
-This completes derivation of the state-space representation of the multiresolution approximation of the neural field model. 
-% \parham{Mike you can add state-space derivation using Galerkin projection here.}
+\cut{This completes derivation of the state-space representation of the multiresolution approximation of the neural field model. }
 
@@
 \end{align}
-A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is (see \cite{Chui1992} for proof) 
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is 
 \begin{align}
@@
 The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used to in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
+The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
 We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.%\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
 The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
@@
 \end{align}
-Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge.
+\cut{Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge.}
+%\cut{The second terms in Eqs.
+\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
 

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
free up some spaces

@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
- \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
  \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
-\parham{where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix}
+where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix.
   $\mathbf U$ is given by
@@
  \centering
- \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
+ \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
  \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
@@
  \centering
- \includegraphics[scale=1]{./Graph/Field.pdf}
+ \includegraphics[scale=0.9]{./Graph/Field.pdf}
  \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions.
@@
 (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
-The solid lines show the actual parameter values and the dotted lines show the means of the estimated parameters.}
+The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
  \label{fig:ParametersHistogram}
@@
 
-  \newpage
+%   \newpage
 % \bibliographystyle{unsrt} 

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
very minor
fixed bold rs
fixed bold r and s

@@
 	&\int_{\Omega} \boldsymbol\mu  \left(r\right)\boldsymbol\mu\left(r\right)^\top  dr\mathbf{x}_{t+1}= 
-	\xi\int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu\left(r\right)^\top d\mathbf{r}\mathbf{x}_t \nonumber \\
+	\xi\int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu\left(r\right)^\top dr\mathbf{x}_t \nonumber \\
 	&+T_s \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
@@
 	    \boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t 
-	\, dr'd\mathbf{r}} \nonumber \\
+	\, dr'dr} \nonumber \\
 	+& \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
@@
 \begin{equation}\label{eq:Disturbance}
-\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)d\mathbf{r},
+\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
 \end{equation}
@@
 \begin{equation}
-	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\mu}_j(\mathbf{r}') \, d\mathbf{r}'.
+	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
 \end{equation}
@@
 \end{align}
-where $\ast$ denotes convolution and $N_1\left(s\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$
+where $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$
 \begin{equation}
@@
 \end{align}
-where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix.
-  $\mathbf U$ is given by
+where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
 \begin{align}
-\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(\mathbf{r-r'}\right) dr'\right]_{j:} dr.
+\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
 \end{align}

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
removed email addresses from everyone expect Parham

@@
 \thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia, (e-mail: dfreestone@bionicear.org; grayden@unimelb.edu.au)}
-\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA (e-mail:mike.dewar@columbia.edu)}
+of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
+\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
 \thanks{K. Scerri is with the Department of Systems and Control Engineering, University
-of Malta, Msida, MSD 2080, Malta (e-mail: kenneth.scerri@um.edu.mt).}}
+of Malta, Msida, MSD 2080, Malta.}}
 % <-this % stops a space

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edit to spatial freq analysis

@@
 \end{align}
- \cut{Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+ \cut{The algorithm has two steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
 The EM algorithm iterates between these two steps until the parameter estimates converge.}
@@
 
- \cut{The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal.
-This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field.
-Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
+The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
+Fig.~\ref{fig:KernelAndFreqResponse} (b), shows the field spatial frequency and cuttoff of \dean{??}.
+Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field.
+\cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
 

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
edit to figure and intro

@@
 The multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integrodifference equation (MRAIDE), to address this challenge.
+This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integro-difference equation (MRAIDE), to address this challenge.
 
-Neural field models typically describe the meso and macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
+Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics of the EEG.
+They typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
 The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and furthermore, may also enable the development of new treatment strategies.
@@
 Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
-Therefore, there exists an enormous potential to improve the performance of these devices using systems theory.
-The design of a stimulation strategy using systems theory requires a model.
-Neural mass and neural field models are the ideal candidates for estimation and control algorithms.
+Therefore, there exists an enormous potential to improve the performance of these devices using systems theory, but first a suitable model is required.
+Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
 It is expected that parameters of the neural fields models will be patient specific and will therefore need to be inferred from data.
 
-The first work describing data driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
+The first work describing data-driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
 This approach was extended to coupled neural masses (using another model~\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
@@
 The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-Fig.~\ref{fig:KernelAndFreqResponse} (b), shows the field spatial frequency and cuttoff of \dean{??}.
+Fig.~\ref{fig:KernelAndFreqResponse} (b), shows the field spatial frequency and cutoff of \dean{??}.
 Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field.
@@
 There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
-\begin{figure}[!h]
- \centering
- \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
- \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
-functions (dashed lines), representing local excitation and lateral inhibition.
+% \begin{figure}[!h]
+%  \centering
+%  \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
+%  \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
+% functions (dashed lines), representing local excitation and lateral inhibition.
 (b) The average (over time) power in dB of the spatial frequency of the observations.
 The dashed line shows the cutoff frequency (-3 dB point).}
-\label{fig:KernelAndFreqResponse} 
-  \end{figure} 
+% \label{fig:KernelAndFreqResponse} 
+%   \end{figure} 
 \begin{figure}[!h] 
@@
  \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$.
-(b) $j=1$, $n_x=33$.
-(c) $j=2$, $n_x=65$.
-(d) $j=3$, $n_x=131$.
-(e) $j=4$, $n_x=263$.}
+(a) $j=0$, $n_x=17$, RMSE = .
+(b) $j=1$, $n_x=33$, RMSE = .
+(c) $j=2$, $n_x=65$, RMSE = .
+(d) $j=3$, $n_x=131$, RMSE = .
+(e) $j=4$, $n_x=263$, RMSE = .}
  \label{fig:FieldEstimates}
  \end{figure} 
+% \begin{figure}[!h] 
+%  \centering
+%  \includegraphics[scale=1]{./Graph/Hist.pdf}
+%  \caption{(a) RMSE of the estimated field at different spatial scales.
+(b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
+The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
+%  \label{fig:ParametersHistogram}
+%  \end{figure} 
 \begin{figure}[!h] 
  \centering
- \includegraphics[scale=1]{./Graph/Hist.pdf}
- \caption{(a) RMSE of the estimated field at different spatial scales.
-(b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
-The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
- \label{fig:ParametersHistogram}
+ \includegraphics[scale=1]{./Graph/KernelEstimate.pdf}
+ \caption{The actual connectivity kernel is shown the the black solid line.
+The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std).
+The 7 weighted kernel basis functions are shown by the black dashed lines.}
+ \label{fig:KernelEstimate}
  \end{figure}

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
small edits
changed model derivation to free up some spaces

@@
 
-To derive the state-space model, Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
-\begin{align}\label{eq:DecomposedModel2} 
-	&\int_{\Omega} \boldsymbol\mu  \left(r\right)\boldsymbol\mu\left(r\right)^\top  dr\mathbf{x}_{t+1}= 
-	\xi\int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu\left(r\right)^\top dr\mathbf{x}_t \nonumber \\
-	&+T_s \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
-	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t 
-	\, dr'dr} \nonumber \\
-	+& \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
-\end{align}
-In order to simplify the model we define the matrices
+\parham{To derive the state-space model, we first define the matrices}
 \begin{align}\label{eq:Lambdax}
@@
 \end{align}
-and substitute them into Eq.~\eqref{eq:DecomposedModel2}. Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
+Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
+\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+\begin{align}\label{eq:DecomposedModel2} 
+	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
+	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
+\end{align}
+Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
 \begin{align}\label{eq:StateEquation}
- \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t \\
+ \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
 \label{eq:A_theta}

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
added reference for Xi variables

@@
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Gibsona2005,Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$
+The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
 \begin{align}\label{eq:Xivariables}

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
added blockwise matrix multiplication
changed fig2

@@
 \end{align}
-where
+\parham{where $\beta$ is constant with respect to $\boldsymbol\theta$ and }
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
- \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}.
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
-where $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix. Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
+\parham{where $\odot$ denotes block-wise matrix multiplication} and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
+Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
 \begin{align}
@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+\parham{Since $n_x<161$ at each level, this provides enough information for state estiamation due to the orthogonality properties of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
@@
  \centering
- \includegraphics[scale=0.9]{./Graph/Field.pdf}
- \caption{Actual (solid line) and estimated (dashed line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, RMSE = .
-(b) $j=1$, $n_x=33$, RMSE = .
-(c) $j=2$, $n_x=65$, RMSE = .
-(d) $j=3$, $n_x=131$, RMSE = .
-(e) $j=4$, $n_x=263$, RMSE = .}
+ \includegraphics[scale=1]{./Graph/Field.pdf}
+ \caption{Actual (black line) and estimated (gray line) neural fields at a time instant for different spatial resolutions.
+(a) $j=0$, $n_x=17$, RMSE =4.44 .
+(b) $j=1$, $n_x=33$, RMSE =1.87 .
+(c) $j=2$, $n_x=65$, RMSE =1.2 .
+(d) $j=3$, $n_x=131$, RMSE = 1.04 .
+(e) $j=4$, $n_x=263$, RMSE = 1.04 .}
  \label{fig:FieldEstimates}
@@
  \centering
- \includegraphics[scale=1]{./Graph/KernelEstimate.pdf}
- \caption{The actual connectivity kernel is shown the the black solid line.
+ \includegraphics[scale=1]{./Graph/Kernel.pdf}
+ \caption{The actual connectivity kernel is shown with the black solid line.
 The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std).

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
small edit

--- 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
@@
 
-\parham{To derive the state-space model, we first define the matrices}
+To derive the state-space model, Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are substituted into Eq.
+\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+\begin{align}\label{eq:DecomposedModel2} 
+	&\int_{\Omega} \boldsymbol\mu  \left(r\right)\boldsymbol\mu\left(r\right)^\top  dr\mathbf{x}_{t+1}= 
+	\xi\int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu\left(r\right)^\top dr\mathbf{x}_t \nonumber \\
+	&+T_s \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    \boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t 
+	\, dr'dr} \nonumber \\
+	+& \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
+\end{align}
+In order to simplify the model we define the matrices
 \begin{align}\label{eq:Lambdax}
@@
 \end{align}
-Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
-\begin{align}\label{eq:DecomposedModel2} 
-	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
-	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
-\end{align}
-Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
+and substitute them into Eq.~\eqref{eq:DecomposedModel2}. Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
 \begin{align}\label{eq:StateEquation}
- \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
+ \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t \\
 \label{eq:A_theta}
@@
 \end{equation}
- \cut{This completes derivation of the state-space representation of the multiresolution approximation of the neural field model. }
 

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
general edits to paper to save space

--- 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
@@
 \newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
-\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
-\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
+\newcommand{\dean}[1]{\textcolor{green}{#1}}
+\newcommand{\parham}[1]{\textcolor{blue}{#1}} 
 \newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
@@
 Dewar}, \dean{D.R.
-Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B.
-Grayden,~\IEEEmembership{Member,~IEEE,} and V.
+Freestone~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B.
+Grayden~\IEEEmembership{Member,~IEEE,} and V.
 Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
@@
 Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
+In this way a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.
 
-This paper is an extension to this recent study~\cite{Freestone2011}.
-The basis function decomposition in this previous study did not account for multiresolution architecture and spatial dynamics of the human cortex.
-Thus, it can be improved..
-In this current paper, a multiresolution approach is taken...
-
-By taking the multiresolution approach, the identified IDE model will approximate the underlying spatio-temporal dynamics at different spatial scales.
-In this way both macroscopic and microscopic behaviour of the system can be represented simultaneously...
-
-\section{Integro-Difference Equation Neural Field Model}
+\section{IDE Neural Field Model}
 The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
@@
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-
 The observation equation describing the electrophysiological recordings is given by
@@
 \end{equation}
-where $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$, is corrupted by an i.i.d normally distributed zero-mean white noise $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ with $\mathbf{\Sigma}_{\epsilon}=\sigma_{\epsilon}^2\mathbf I_{n_y} $.
-The superscript $\top$ denotes the transpose operator.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel and the observation noise is an i.i.d.
+white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
+% $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
 \section{MRA of the IDE in State-Space}
@@
 \end{equation}
-where $ x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$.
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$. \dean{Need to define these guys as the states here!}
 
-Eqs.
-\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions, but  for a practical implementation they must be truncated at some level $j$.
-Therefore, the field and the connectivity kernel is approximated by
+Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions \cut{, but  for a practical implementation they } (and) must be truncated at some level $j$.
+The field and the connectivity kernel is approximated by
  \begin{align}
@@
 For a multivariate linear dynamic system, the bound used is a quadratic of the form
-\begin{equation}
+\begin{equation}\label{eq:Qfunction}
  \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
 \end{equation}
-which has a maximum at
+\parham{where $\beta$ is constant with respect to $\boldsymbol\theta$. Eq.~\ref{eq:Qfunction} is maximum at
 \begin{align}
@@
 \end{align}
-\parham{where $\beta$ is constant with respect to $\boldsymbol\theta$ and }
+where }
 \begin{align}\label{eq:upsilon0}
@@
 \end{align}
-\parham{where $\odot$ denotes block-wise matrix multiplication} and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
+\parham{The operator $\odot$ denotes block-wise matrix multiplication} and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
 Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel (RTS)\cite{RAUCH1965} smoother outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
+The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
 \begin{align}\label{eq:Xivariables}
@@
 To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$.
-The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms respectively.
+100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$ (\dean{Defining the covariance this way is confusing, just like it was for the sensor kernel.
+It implies that the disturbance covariance to directly related to the field, or the basis was chosen because of the disturbance.
+Can we simply say that the disturbance covariance was a b-spline with dilation xx?}).
+The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{Since $n_x<161$ at each level, this provides enough information for state estiamation due to the orthogonality properties of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+\parham{Since $n_x<161$ at each level, this provides enough information for state estiamation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
-The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a).
-
-The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-Fig.~\ref{fig:KernelAndFreqResponse} (b), shows the field spatial frequency and cutoff of \dean{??}.
+The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
+The spatial cutoff frequency was \dean{??} cycles/mm.
 Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field.
@@
 Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
-\dean{Needs more info.} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
+\dean{Needs more info.
+Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field, where the RMSE .
 The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a).
-
+The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a). 
 The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation.

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
update to results

@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{Since $n_x<161$ at each level, this provides enough information for state estiamation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+\parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
@@
 \dean{Needs more info.
-Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field, where the RMSE .
-The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a).
-The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a). 
-The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation.
+Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{xx}.
+\dean{j=3 seems like where it converges?} The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
 \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)...

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edits to result section

--- 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
@@
 Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
-\dean{Needs more info.} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field \dean{since the error converges?}.
-The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a).
+\dean{Needs more info.} The figure confirms that $j=3$ is adequate to capture the dynamic of the underlying field \dean{since the root mean square error (RMSE) converges to 1.04.}
 

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex

--- 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
@@
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.
+In this way, a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.
 
@@
 The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f\left(.\right)$.
-\dean{The activation function is of the form $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function \dean{$f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
@@
 \section{MRA of the IDE in State-Space}
-The multiresolution approximation (MRA) of the neural IDE is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
+The multi-resolution approximation (MRA) of the neural IDE is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 Considering a one-dimensional field, the connectivity kernel is decomposed by,
@@
 \dean{j=3 seems like where it converges?} The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
-\dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)...
-There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
-% \begin{figure}[!h]
-%  \centering
-%  \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
-%  \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
-% functions (dashed lines), representing local excitation and lateral inhibition.
-(b) The average (over time) power in dB of the spatial frequency of the observations.
-The dashed line shows the cutoff frequency (-3 dB point).}
-% \label{fig:KernelAndFreqResponse} 
-%   \end{figure} 
+The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+The small error in the estimate results is attributed to the MRA of the true field used to form the estimator.
 \begin{figure}[!h] 
@@
 \end{figure} 
-% \begin{figure}[!h] 
-%  \centering
-%  \includegraphics[scale=1]{./Graph/Hist.pdf}
-%  \caption{(a) RMSE of the estimated field at different spatial scales.
-(b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively.
-The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
-%  \label{fig:ParametersHistogram}
-%  \end{figure} 
 \begin{figure}[!h] 
@@
 \end{figure}
-
 \section{Discussion}

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
some general edits

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multiresolution Neural Field Estimation }
+\title{Multi-resolution Neural Field Estimation }
 
@@
 \end{align}
-The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
+The vectors in Eqs.
+(\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs.
+(\ref{KernelWeights}) and (\ref{FieldWeights}).
+\dean{Comment on how the kernel basis functions are placed.}
 
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-The small error in the estimate results is attributed to the MRA of the true field used to form the estimator.
+The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \begin{figure}[!h] 
@@
 		\includegraphics[scale=1]{./Graph/Field.pdf}
-		\caption{Actual (black line) and estimated (gray line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, RMSE =4.44 .
-(b) $j=1$, $n_x=33$, RMSE =1.87 .
-(c) $j=2$, $n_x=65$, RMSE =1.2 .
-(d) $j=3$, $n_x=131$, RMSE = 1.04 .
-(e) $j=4$, $n_x=263$, RMSE = 1.04 .}
+		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions.
+(a) $j=0$, $n_x=17$, RMSE = 4.44.
+(b) $j=1$, $n_x=33$, RMSE = 1.87.
+(c) $j=2$, $n_x=65$, RMSE = 1.2.
+(d) $j=3$, $n_x=131$, RMSE = 1.04.
+(e) $j=4$, $n_x=263$, RMSE=1.04.}
 	\label{fig:FieldEstimates}
@@
 		\caption{The actual connectivity kernel is shown with the black solid line.
-The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std).
+The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
 The 7 weighted kernel basis functions are shown by the black dashed lines.}
@@
 
-Other groups have previously highlighted the importance of a multiresolution approach in neural field modeling.
+Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
 For example, it is thought that the connectivity structure differs at different spatial scales, where at a fine scale a homogeneous connectivity exists and at a larger scale the connectivity become~\cite{Qubbaj2009}....

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edit to results

--- 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
@@
 To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$ (\dean{Defining the covariance this way is confusing, just like it was for the sensor kernel.
-It implies that the disturbance covariance to directly related to the field, or the basis was chosen because of the disturbance.
-Can we simply say that the disturbance covariance was a b-spline with dilation xx?}).
+100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.}
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edit to results

@@
 \dean{Needs more info.
-Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{xx}.
-\dean{j=3 seems like where it converges?} The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
+Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{1.04}.
+The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 
-Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions \cut{, but  for a practical implementation they } (and) must be truncated at some level $j$.
-The field and the connectivity kernel is approximated by
+Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel is approximated by
 \begin{align}

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
a few minor edits

--- 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
@@
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
-The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+The term $e_t(\mathbf r)$ is an i.i.d.
+disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function \dean{$f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
  \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The matrices $\Xi_0$ and $\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
 \begin{align}\label{eq:Xivariables}
@@
 To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.}
+100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$ (\dean{Defining the covariance this way is confusing, just like it was for the sensor kernel.
+It implies that the disturbance covariance to directly related to the field, or the basis was chosen because of the disturbance.
+Can we simply say that the disturbance covariance was a b-spline with dilation xx?}).
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 
-\author{In no particular order: \parham{P.
+\author{\parham{P.
 Aram}, \mike{M.
@@
 The spatial cutoff frequency was \dean{??} cycles/mm.
-Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field.
+Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field.
 \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
@@
 \dean{Needs more info.
-Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{1.04}.
+Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{0.72}.
 The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
@@
 		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, RMSE = 4.44.
-(b) $j=1$, $n_x=33$, RMSE = 1.87.
-(c) $j=2$, $n_x=65$, RMSE = 1.2.
-(d) $j=3$, $n_x=131$, RMSE = 1.04.
-(e) $j=4$, $n_x=263$, RMSE=1.04.}
+(a) $j=0$, $n_x=17$, RMSE = 2.10.
+(b) $j=1$, $n_x=33$, RMSE = 1.42.
+(c) $j=2$, $n_x=65$, RMSE = 0.80.
+(d) $j=3$, $n_x=131$, RMSE = 0.72.
+(e) $j=4$, $n_x=263$, RMSE=0.72.}
 	\label{fig:FieldEstimates}

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edits to result section
added some bits to keep in case of extra space

@@
 Integers $j$ and $l$ are the scale and translation parameters respectively.
-The field is decomposed as
+\parham{ Scaling functions retain lowest frequency and wavelet functions extract successively higher and higher frequency components (by increasing $j$) due their low and band pass sepctral characteristics respectively.} The field is decomposed as
 \begin{equation}
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. The $m^{th}$ order B-spline wavelet function is defined as (see \cite{Chui1992}) 
+\parham{where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+This holds as $N_m\left(r\right)$ is symmetric with respect to $r=\frac{m}{2}$}.
+The $m^{th}$ order B-spline wavelet function is defined as (see \cite{Chui1992})
 \begin{align}
@@
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+\parham{It is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}:
+\begin{equation}
+ \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
+\label{PsiPsiOrthogonality}
+\end{equation}
+\begin{equation}
+ \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2
+\label{PhiPsiOrthogonality}
+\end{equation}}
+ \parham{In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.} Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
 \section{State and Parameter Estimation}
@@
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field.
-\cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
+% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
 
-Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}.
+\parham{Field reconstruction obtained by applying the EM algorithm at different levels of approximations separately using same observation set.
+(\figurename{\ref{fig:FieldEstimates}})}.
 \dean{Needs more info.

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
authors edits
a few minor edits

--- 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
@@
 The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+\dean{The estimation problem is well-posed since there is less state then observations at each level of the decomposition and basis functions are orthogonal.} \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
general edits

--- 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
@@
 \author{\parham{P.
-Aram}, \mike{M.
-Dewar}, \dean{D.R.
-Freestone~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B.
+Aram}, \dean{D.R.
+Freestone~\IEEEmembership{Graduate Student Member,~IEEE}}, \mike{M.
+Dewar}, \ken{K.Scerri}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
-It is expected that parameters of the neural fields models will be patient specific and will therefore need to be inferred from data.
+It is expected that parameters of the neural fields models will be patient specific and will therefore, need to be inferred from data.
 
@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function \dean{$f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
@@
 \section{MRA of the IDE in State-Space}
-The multi-resolution approximation (MRA) of the neural IDE is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
+The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 Considering a one-dimensional field, the connectivity kernel is decomposed by,
@@
 where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$.
-Integers $j$ and $l$ are the scale and translation parameters respectively.
-\parham{ Scaling functions retain lowest frequency and wavelet functions extract successively higher and higher frequency components (by increasing $j$) due their low and band pass sepctral characteristics respectively.} The field is decomposed as
+Integers $j$ and $l$ are the scale and translation parameters, respectively.
+\parham{ Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components (by increasing $j$) due their low and band-pass spectral characteristics, respectively.} The field is decomposed as
 \begin{equation}
@@
 \end{equation}
-where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion at time $t$. \dean{Need to define these guys as the states here!}
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion, and constitute the state vector at time $t$. %\dean{Need to define these guys as the states here!}
 
-Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel is approximated by
+Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
 \begin{align}
@@
 \end{align}
-The kernel and field approximation coefficient vectors $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$ contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
+The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
 Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
@@
 \end{align}
-Then we cross-multiply by $\mathbf{\Lambda}_{x}^{-1}$ giving
+Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
 \begin{align}\label{eq:StateEquation}
@@
 
-The multiresolution approximation can be implemented using various classes of scaling and wavelet functions.
+The MRAIDE can be implemented using various classes of scaling and wavelet functions.
 B-spline functions were chosen due their compact support and the ability to analytically calculate convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
@@
 This holds as $N_m\left(r\right)$ is symmetric with respect to $r=\frac{m}{2}$}.
-The $m^{th}$ order B-spline wavelet function is defined as (see \cite{Chui1992})
+The $m^{th}$-order B-spline wavelet function is defined as (see \cite{Chui1992})
 \begin{align}
@@
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-\parham{It is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}:
+\parham{It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
 \begin{equation}
@@
 \end{align}
- \cut{The algorithm has two steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+ \cut{The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
 The EM algorithm iterates between these two steps until the parameter estimates converge.}
@@
 \section{Results}
-To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ \dean{and the disturbance covariance was a B-spline with $j=3$.}
-The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
-The distance between adjacent sensors was $0.5$~mm resulting into 161 observations.
-\parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
+100 realizations of 1 second of data were generated.
+\dean{The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,0}(r-r')$ (B-spline, $j=3$).} The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
+\dean{The number of states $n_x = ??$.} The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
+\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.} \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
edits with parham

@@
 disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function \dean{$f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}) + v_0$}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
@@
 Integers $j$ and $l$ are the scale and translation parameters, respectively.
-\parham{ Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components (by increasing $j$) due their low and band-pass spectral characteristics, respectively.} The field is decomposed as
+Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components (by increasing $j$) due their low and band-pass spectral characteristics, respectively.
+The field is decomposed as
 \begin{equation}
@@
 \end{align}
-The vectors in Eqs.
-(\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs.
-(\ref{KernelWeights}) and (\ref{FieldWeights}).
-\dean{Comment on how the kernel basis functions are placed.}
+The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
-\parham{To derive the state-space model, we first define the matrices}
+To derive the state-space model, we first define the matrices
 \begin{align}\label{eq:Lambdax}
@@
 \end{align}
-A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is 
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is \dean{the inner product between two B-splines is another translated B-spline, such that}
 \begin{align}
@@
 \end{align}
-\parham{where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-This holds as $N_m\left(r\right)$ is symmetric with respect to $r=\frac{m}{2}$}.
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+This holds as $N_m\left(r\right)$ is isotropic.
 The $m^{th}$-order B-spline wavelet function is defined as (see \cite{Chui1992})
@@
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-\parham{It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
+It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
 \begin{equation}
@@
 \begin{equation}
- \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2
+ \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
 \label{PhiPsiOrthogonality}
-\end{equation}}
- \parham{In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.} Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+\end{equation}
+In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
 \section{State and Parameter Estimation}
@@
 \end{equation}
-\parham{where $\beta$ is constant with respect to $\boldsymbol\theta$. Eq.~\ref{eq:Qfunction} is maximum at
+where $\beta$ is constant with respect to $\boldsymbol\theta$. Eq.~\ref{eq:Qfunction} is maximum at
 \begin{align}
@@
 \end{align}
-where }
+where
 \begin{align}\label{eq:upsilon0}
@@
 \end{align}
-\parham{The operator $\odot$ denotes block-wise matrix multiplication} and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
+The operator $\odot$ denotes block-wise matrix multiplication and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
 Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
@@
 \end{align}
- \cut{The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge.}
+The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge.
 %\cut{The second terms in Eqs.
@@
 100 realizations of 1 second of data were generated.
-\dean{The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,0}(r-r')$ (B-spline, $j=3$).} The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
+The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
+The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
 \dean{The number of states $n_x = ??$.} The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
-\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.} \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.} The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-The spatial cutoff frequency was \dean{??} cycles/mm.
+Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field.
@@
 
-\parham{Field reconstruction obtained by applying the EM algorithm at different levels of approximations separately using same observation set.
+\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set.
 (\figurename{\ref{fig:FieldEstimates}})}.
-\dean{Needs more info.
-Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{0.72}.
+The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
+The confirms good state estimation performance, where the estimated field is in good accordance with the true field.
 The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
more edits with parham

@@
 \begin{equation}\label{eq:ObservationEquation}
-	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
+	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
 \end{equation}
@@
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
-\dean{The number of states $n_x = ??$.} The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
-\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.} The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
+The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{freestone2011}.
-Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field.
+Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
+Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = ??$ states.
+\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}
 % \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
@@
 The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
-The confirms good state estimation performance, where the estimated field is in good accordance with the true field.
+Figure 3 confirms good state estimation performance, where the estimated field is in good accordance with the true field.
+
 The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
edits to discussion
added reference to discussion

@@
 \section{Discussion}
-In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
+In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
+The novel aspects include the multiresolution final elemnt representation of the cortex and the connectivity kernel support estimation where the width of the kernel is unknown to the estimator.
 
-This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems, ....
+This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems \cite{Wikle2002}, ....
 

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
added reference to discussion
edits to discussion

--- 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
@@
 \section{Discussion}
-In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
+In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
+The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
+For example, it is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009}.
 
-This work extends previous work by... alternative ARMA model... The MRA IDE can be applied to fluid dynamics, weather systems, ....
-
-Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-For example, it is thought that the connectivity structure differs at different spatial scales, where at a fine scale a homogeneous connectivity exists and at a larger scale the connectivity become~\cite{Qubbaj2009}....
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems describing fluid dynamics, weather systems and others \cite{Wikle2002}.
 
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-Furthermore, the theory presented in this paper can be adapted to more sophisticated nonlinear forms of the field equations.
-The key development in this paper is the multiresolution decomposition forming the state-space model, which holds for a nonlinear activation function.
-If a nonlinear activation function was used, then unscented RTSS should be used in the E-step of the estimation algorithm.
+The key development in this paper is the multi-resolution decomposition forming the state-space model, which holds for a nonlinear activation function.
+Furthermore, the theory can be adapted to more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.
 

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex

@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems describing fluid dynamics, weather systems and others \cite{Wikle2002}.
+This work extends previous work by...
+alternative ARMA model...
+The MRA IDE can be applied to fluid dynamics, weather systems \cite{Wikle2002,Xu2005}, ecological system \cite{Fort2008}, \parham{Mike,Ken: can add to this list?}, ....
 

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
edits to discussion

--- 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
@@
 The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our the understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems describing fluid dynamics, weather systems and others \cite{Wikle2002}.
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems such as fluid dynamics, weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+\parham{Mike,Ken: can add to this list?}
 

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
edits to discussion

@@
 The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
-The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel.
+The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude.
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
@@
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = ??$ states.
-\dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}
+\dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}
 % \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
@@
 The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
-Figure 3 confirms good state estimation performance, where the estimated field is in good accordance with the true field.
+Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
 
@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution dynamical systems such as fluid dynamics, weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as fluid dynamics, weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
 \parham{Mike,Ken: can add to this list?}
@@
 The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
-An obvious discrepancy is, for example, the linear activation function.
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as fluid dynamics, weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems and ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
 \parham{Mike,Ken: can add to this list?}

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems and ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
 \parham{Mike,Ken: can add to this list?}

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
added varsigma to the equations in the paper
minor correction

@@
 	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
-	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
+	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
 \end{align}
@@
 \label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= (T_s\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
+ \mathbf A(\boldsymbol \theta) &= (T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
 \end{align}
@@
 \begin{equation}\label{eq:Qfunction}
- \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
+ \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
 \end{equation}
@@
  \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
- \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
@@
 The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
-This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our the understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
+This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
new figure2
a bunch of little comments, edits and suggestions for cutting

@@
 \section{Introduction}
-\IEEEPARstart{T}{he} human brain has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses, to neurons, to networks of neurons.
-The multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multiresolution data-driven framework for neural field modeling, the multiresolution approximate integro-difference equation (MRAIDE), to address this challenge.
+\IEEEPARstart{T}{he} human brain \mike{cortex?} has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons.
+This multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
+This paper introduces a multiresolution data-driven framework for neural field modeling, the MultiResolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.
 
 Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics of the EEG.
-They typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and furthermore, may also enable the development of new treatment strategies.
-This is particularly poignant with the advent of new devices that use therapeutic electrical stimulation.
+These models typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
+The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and \cut{furthermore,} may also enable the development of new treatment strategies.
+This is particularly \cut{poignant with}\mike{relevant to} the advent of new devices that use therapeutic electrical stimulation.
 Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
-Therefore, there exists an enormous potential to improve the performance of these devices using systems theory, but first a suitable model is required.
-Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
+Therefore, there exists an enormous potential to improve the performance of these devices using control theory,\mike{which in turn requires a suitable dynamic model.}\cut{ but first a suitable model is required.} Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
 It is expected that parameters of the neural fields models will be patient specific and will therefore, need to be inferred from data.
@@
 The first work describing data-driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
-This approach was extended to coupled neural masses (using another model~\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
+This approach was extended to coupled neural masses \cut{(using another model~}\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
 Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
@@
 Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
-The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
+The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the \mike{connectivity} kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$\mike{:}\cut{, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes} a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-The observation equation describing the electrophysiological recordings is given by
+The observation equation describing the electrophysiological recordings is given by \mike{should the $r_n$ be $r_{n_y}$ below?}
 \begin{equation}\label{eq:ObservationEquation}
@@
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel and the observation noise is an i.i.d.
-white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
+\mike{Gaussian} white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
 % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
@@
 The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
-Considering a one-dimensional field, the connectivity kernel is decomposed by,
+Considering a one-dimensional field, the connectivity kernel is decomposed using,
 \begin{equation}
@@
 Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components (by increasing $j$) due their low and band-pass spectral characteristics, respectively.
-The field is decomposed as
+The field is decomposed using
 \begin{equation}
@@
 \end{align}
-The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
+\mike{I think it would be much clearer to simply define these vectors as vectors, rather than hoping that the reader will make the same mapping from the sets defined here to the vectors you actually use.} The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
 Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
@@
 \end{align}
-The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
+\mike{is it worth defining $s=r-r'$ somewhere and using that throughout?
+It may save some lines!} The vectors in Eqs.
+(\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs.
+(\ref{KernelWeights}) and (\ref{FieldWeights}).
 
-To derive the state-space model, we first define the matrices
+To derive the state-space model, we first define the matrices \mike{bold $r$s here and everywhere (or nowhere)?}
 \begin{align}\label{eq:Lambdax}
@@
 Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+\eqref{eq:DiscreteTimeModel}, then we \mike{do you mean pre-multiply?
+- I'm not sure what cross multiply means here} cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
 \begin{align}\label{eq:DecomposedModel2} 
@@
 The MRAIDE can be implemented using various classes of scaling and wavelet functions.
-B-spline functions were chosen due their compact support and the ability to analytically calculate convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+B-spline functions were chosen due their compact support and the ability to analytically calculate \cut{the convolution and inner product to form} the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
 To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
@@
 \end{equation}
-Eq.~\ref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ times convolution of indicator function with itself since
+Eq.~\ref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
 \begin{equation}
@@
 where $q_n$ are the coefficients.
-By exploiting properties Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
+By exploiting \cut{properties} Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
+In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale\mike{\cite{Goswami1999}}.\cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
 \begin{equation}
@@
 In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.}
 \section{State and Parameter Estimation}
@@
 \end{align}
-The operator $\odot$ denotes block-wise matrix multiplication and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
+The operator $\odot$ denotes block-wise matrix multiplication \mike{this still doesn't work!
+block matrix multiplication isn't a different thing to regular matrix multiplication I think?
+Isn't it just a different way to do regular matrix multiplication?
+Also one still doesn't know if the indices in eqs 31-33 are block indices or element indices.
+Also it's hard to invent notation, and if you do you need to make sure it's defined!
+Maybe check out the tensor literature?
+(or simply just index all this properly)}and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
 Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/Kernel.pdf}
-		\caption{The actual connectivity kernel is shown with the black solid line.
+		\includegraphics[scale=1]{./Graph/test.pdf}
+		\caption{Cconnectivity kernel estimate.
+(a) The actual kernel is shown with the black solid line.
+The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
+(b) Weighted kernel scaling functions at $j=1$.
+(c) Weighted kernel wavelet functions at $j=1$.}
+	\label{fig:KernelEstimate}
+\end{figure}
+% \caption{The actual connectivity kernel is shown with the black solid line.
 The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
 The 7 weighted kernel basis functions are shown by the black dashed lines.}
-	\label{fig:KernelEstimate}
-\end{figure}
 \section{Discussion}

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

--- 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
@@
 		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, RMSE = 2.10.
-(b) $j=1$, $n_x=33$, RMSE = 1.42.
-(c) $j=2$, $n_x=65$, RMSE = 0.80.
-(d) $j=3$, $n_x=131$, RMSE = 0.72.
-(e) $j=4$, $n_x=263$, RMSE=0.72.}
+(a) $j=0$, $n_x=17$, $RMSE = 2.10$.
+(b) $j=1$, $n_x=33$, $RMSE = 1.42$.
+(c) $j=2$, $n_x=65$, $RMSE = 0.80$.
+(d) $j=3$, $n_x=131$, $RMSE = 0.72$.
+(e) $j=4$, $n_x=263$, $RMSE=0.72$.}
 	\label{fig:FieldEstimates}
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/Kernel.pdf}
-		\caption{The actual connectivity kernel is shown with the black solid line.
+		\includegraphics[scale=1]{./Graph/test.pdf}
+		\caption{Connectivity kernel estimate.
+(a) The actual kernel is shown with the black solid line.
+The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
+(b) Weighted kernel scaling functions at $j=1$.
+(c) Weighted kernel wavelet functions at $j=1$.}
+	\label{fig:KernelEstimate}
+\end{figure}
+% \caption{The actual connectivity kernel is shown with the black solid line.
 The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
 The 7 weighted kernel basis functions are shown by the black dashed lines.}
-	\label{fig:KernelEstimate}
-\end{figure}
 \section{Discussion}
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model, which holds for a nonlinear activation function.
-Furthermore, the theory can be adapted to more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.
+The key development in this paper is the multi-resolution decomposition forming the state-space model.
+The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.
 

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex

--- 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
@@
 		\includegraphics[scale=1]{./Graph/test.pdf}
-		\caption{Cconnectivity kernel estimate.
+		\caption{Connectivity kernel estimate.
 (a) The actual kernel is shown with the black solid line.

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
some edits to Mike comments

@@
 Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
-The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the \mike{connectivity} kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
+The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$\mike{:}\cut{, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes} a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-The observation equation describing the electrophysiological recordings is given by \mike{should the $r_n$ be $r_{n_y}$ below?}
+The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
-	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
+	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel and the observation noise is an i.i.d.
-\mike{Gaussian} white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and the observation noise is an i.i.d.
+Gaussian white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
 % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
@@
 \end{align}
-\mike{I think it would be much clearer to simply define these vectors as vectors, rather than hoping that the reader will make the same mapping from the sets defined here to the vectors you actually use.} The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
+The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
 Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
@@
 \end{align}
-\mike{is it worth defining $s=r-r'$ somewhere and using that throughout?
-It may save some lines!} The vectors in Eqs.
-(\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs.
-(\ref{KernelWeights}) and (\ref{FieldWeights}).
+The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
@@
 Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we \mike{do you mean pre-multiply?
-- I'm not sure what cross multiply means here} cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+\eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \end{align}
-A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is \dean{the inner product between two B-splines is another translated B-spline, such that}
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline, such that
 \begin{align}

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
edits to EM

@@
 By exploiting \cut{properties} Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale\mike{\cite{Goswami1999}}.\cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
-\begin{equation}
- \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
-\label{PsiPsiOrthogonality}
-\end{equation}
-\begin{equation}
- \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
-\label{PhiPsiOrthogonality}
-\end{equation}
+In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
 In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.}
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+
+% \cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}: 
+% \begin{equation}
+%  \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
+% \label{PsiPsiOrthogonality}
+% \end{equation}
+% \begin{equation}
+%  \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
+% \label{PhiPsiOrthogonality}
+% \end{equation}
 \section{State and Parameter Estimation}
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
+\begin{equation}
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta^\top
+\end{equation}
+
 The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
minor edit
correction to lambdatheta
minor changes
added new plots for kernel estimates
minor edits

@@
 Freestone~\IEEEmembership{Graduate Student Member,~IEEE}}, \mike{M.
-Dewar}, \ken{K.Scerri}, D.B.
+Dewar}, \ken{K.Scerri~\IEEEmembership{Member,~IEEE,}}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 
-To derive the state-space model, we first define the matrices \mike{bold $r$s here and everywhere (or nowhere)?}
+To derive the state-space model, we first define the matrices 
 \begin{align}\label{eq:Lambdax}
@@
 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t 
+	    \boldsymbol\mu^\top\left(r\right) 
 	\, dr'dr}
@@
 \label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= (T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
+ \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I,
 \end{align}
@@
 The MRAIDE can be implemented using various classes of scaling and wavelet functions.
-B-spline functions were chosen due their compact support and the ability to analytically calculate \cut{the convolution and inner product to form} the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+B-spline functions were chosen due their compact support and the ability to analytically calculate the convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
 To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
@@
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta^\top
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta
 \end{equation}
@@
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
+The firing rate slop, $\varsigma$ was set to $0.56  ~mV^{-1}$.
 The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/test.pdf}
+		\includegraphics[scale=1]{./Graph/KernelUnknownSupportWithVarsigma.pdf}
 		\caption{Connectivity kernel estimate.
@@
 The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
-(b) Weighted kernel scaling functions at $j=1$.
-(c) Weighted kernel wavelet functions at $j=1$.}
+(b) Kernel scaling functions at $j=1$.
+(c) Kernel wavelet functions at $j=1$.}
 	\label{fig:KernelEstimate}

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
-State and parameter estimation is approached in a Maximum Likelihood (ML) framework using the Expectation Maximisation (EM) algorithm.
-Examples are given to demonstrate the framework.
+State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
 \end{abstract}
@@
 where $q_n$ are the coefficients.
-By exploiting \cut{properties} Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
+By exploiting Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
@@
 Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
-Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = ??$ states.
+Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
 \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
edit to EM algorithm

@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For a multivariate linear dynamic system, the bound used is a quadratic of the form
+\parham{For the linear state-space model given by Eqs.~\ref{eq:StateEquation} and \ref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
 \begin{equation}\label{eq:Qfunction}
@@
 To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-100 realizations of 1 second of data were generated.
+200 realizations of 1 second of data were generated.
 The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
deleted extra plots
delete Eqs from the manuscript

@@
 \end{abstract}
-
 % Note that keywords are not normally used for peerreview papers.
@@
 \end{IEEEkeywords}
-
-\IEEEpeerreviewmaketitle
-
+% \IEEEpeerreviewmaketitle
 \section{Introduction}
@@
 
-Eqs.\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
+Equations \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
 \begin{align}
@@
 \end{align}
-The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
+The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
@@
 \end{align}
-Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+Equations ~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into \eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
 \begin{align}\label{eq:DecomposedModel2} 
@@
 The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
- into equation \eqref{eq:ObservationEquation} giving
+ into \eqref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation} 
@@
 \end{equation}
-Eq.~\ref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
+Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
 \begin{equation}
@@
 \end{align}
-A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline, such that
+A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline, such that
 \begin{align}
@@
 where $q_n$ are the coefficients.
-By exploiting Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
+By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct} the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
 In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta}.
 
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-\parham{For the linear state-space model given by Eqs.~\ref{eq:StateEquation} and \ref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
+\parham{For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
 \begin{equation}\label{eq:Qfunction}
@@
 \end{equation}
-where $\beta$ is constant with respect to $\boldsymbol\theta$. Eq.~\ref{eq:Qfunction} is maximum at
+where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation \eqref{eq:Qfunction} is maximum at
 \begin{align}
@@
 The EM algorithm iterates between these two steps until the parameter estimates converge.
-%\cut{The second terms in Eqs.
-\ref{eq:upsilon0}, \ref{eq:upsilon1}, and \ref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
+%\cut{The second terms in  \eqref{eq:upsilon0}, \eqref{eq:upsilon1}, and \eqref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
 
 \section{Results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
 200 realizations of 1 second of data were generated.

### 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
changed the format
removed index terms
added ken comments

@@
 
-   \documentclass[journal,a4paper]{IEEEtran}
+%    \documentclass[journal,a4paper]{IEEEtran}
+    \documentclass[journal]{IEEEtran}
+
 %     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
@@
 % Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
-\end{IEEEkeywords}
+% \begin{IEEEkeywords}
+% Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+% \end{IEEEkeywords}
 % \IEEEpeerreviewmaketitle
@@
 Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
-Therefore, there exists an enormous potential to improve the performance of these devices using control theory,\mike{which in turn requires a suitable dynamic model.}\cut{ but first a suitable model is required.} Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
+Therefore, there exists an enormous potential to improve the performance of these devices using control theory,\mike{which in turn requires a suitable dynamic model.}\cut{ but first a suitable model is required.} \ken{I's rather not mentioning control when our model has no input.} Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
 It is expected that parameters of the neural fields models will be patient specific and will therefore, need to be inferred from data.
@@
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-The observation equation describing the electrophysiological recordings is given by
+\ken{Doing something just for computational efficiency only might be weak ...
+is there other work we can reference that makes the linearity assumption?
+...
+or are there practical situations when this known to be a good approximations?} The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \end{align}
-Equations ~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into \eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+Equations ~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into \eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving \ken{Substituting Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives}
 \begin{align}\label{eq:DecomposedModel2} 
@@
 (or simply just index all this properly)}and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
-Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  $\mathbf U$ is given by
+Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  \ken{I am getting confused here too ...
+is this a matrix of $n_x \times n_x$ blocks or just an $n_x \times n_x$ matrix - what is the problem to define simple matrices?} $\mathbf U$ is given by
 \begin{align}
@@
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
-The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
+\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table} The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
 Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
@@
 (\figurename{\ref{fig:FieldEstimates}})}.
-The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
+\ken{Parham, can't understand the previous sentence.} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
 Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
@@
 In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+The novel and key developments of the paper include the multi-resolution FEM \ken{(I might have missed it but did we define this acronym)} representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
 This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+(This is copy and paste from my thesis ...
+parham I'll get you the references later)}.
 \parham{Mike,Ken: can add to this list?}
 
-In order to apply the framework to real data several assumptions must be made, such as stationarity of the parameters over the estimation period.
+In order to apply the framework to real data several \ken{better say some} assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor edit

--- 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
@@
 Freestone~\IEEEmembership{Graduate Student Member,~IEEE}}, \mike{M.
-Dewar}, \ken{K.Scerri~\IEEEmembership{Member,~IEEE,}}, D.B.
+Dewar}, \ken{K.Scerri}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
-State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
+State and parameter estimation is approached in a Maximum Likelihood (ML) framework using the Expectation Maximisation (EM) algorithm.
+Examples are given to demonstrate the framework.
 \end{abstract}
@@
 Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
-The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
+The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the \mike{connectivity} kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$\mike{:}\cut{, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes} a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-The observation equation describing the electrophysiological recordings is given by
+The observation equation describing the electrophysiological recordings is given by \mike{should the $r_n$ be $r_{n_y}$ below?}
 \begin{equation}\label{eq:ObservationEquation}
-	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
+	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and the observation noise is an i.i.d.
-Gaussian white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel and the observation noise is an i.i.d.
+\mike{Gaussian} white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
 % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
@@
 \end{align}
-The vectors in Eqs. (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs. (\ref{KernelWeights}) and (\ref{FieldWeights}).
+\mike{is it worth defining $s=r-r'$ somewhere and using that throughout?
+It may save some lines!} The vectors in Eqs.
+(\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in Eqs.
+(\ref{KernelWeights}) and (\ref{FieldWeights}).
 
-To derive the state-space model, we first define the matrices 
+To derive the state-space model, we first define the matrices \mike{bold $r$s here and everywhere (or nowhere)?}
 \begin{align}\label{eq:Lambdax}
@@
 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right) 
+	    \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t 
 	\, dr'dr}
@@
 Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into Eq.
-\eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
+\eqref{eq:DiscreteTimeModel}, then we \mike{do you mean pre-multiply?
+- I'm not sure what cross multiply means here} cross-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I,
+ \mathbf A(\boldsymbol \theta) &= (T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I),
 \end{align}
@@
 The MRAIDE can be implemented using various classes of scaling and wavelet functions.
-B-spline functions were chosen due their compact support and the ability to analytically calculate the convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+B-spline functions were chosen due their compact support and the ability to analytically calculate \cut{the convolution and inner product to form} the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
 To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
@@
 \end{align}
-A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline, such that
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is \dean{the inner product between two B-splines is another translated B-spline, such that}
 \begin{align}
@@
 where $q_n$ are the coefficients.
-By exploiting Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+By exploiting \cut{properties} Eqs.~\ref{eq:BsplineConvolution} and \ref{eq:BsplineInnerProduct} the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta} can be computed analytically.
+In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale\mike{\cite{Goswami1999}}.\cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}:
+\begin{equation}
+ \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
+\label{PsiPsiOrthogonality}
+\end{equation}
+\begin{equation}
+ \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
+\label{PhiPsiOrthogonality}
+\end{equation}
 In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.
-
-% \cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}: 
-% \begin{equation}
-%  \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
-% \label{PsiPsiOrthogonality}
-% \end{equation}
-% \begin{equation}
-%  \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
-% \label{PhiPsiOrthogonality}
-% \end{equation}
+Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in Eqs.~\ref{eq:Lambdax} and \ref{eq:Lambdatheta}.}
 \section{State and Parameter Estimation}
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-\parham{For the linear state-space model given by Eqs.~\ref{eq:StateEquation} and \ref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
+For a multivariate linear dynamic system, the bound used is a quadratic of the form
 \begin{equation}\label{eq:Qfunction}
@@
  \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
-\begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta
-\end{equation}
-
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
 The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
@@
 To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-200 realizations of 1 second of data were generated.
+100 realizations of 1 second of data were generated.
 The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
-The firing rate slop, $\varsigma$ was set to $0.56  ~mV^{-1}$.
 The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
@@
 Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
-Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
+Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = ??$ states.
 \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/KernelUnknownSupportWithVarsigma.pdf}
+		\includegraphics[scale=1]{./Graph/test.pdf}
 		\caption{Connectivity kernel estimate.
@@
 The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
-(b) Kernel scaling functions at $j=1$.
-(c) Kernel wavelet functions at $j=1$.}
+(b) Weighted kernel scaling functions at $j=1$.
+(c) Weighted kernel wavelet functions at $j=1$.}
 	\label{fig:KernelEstimate}

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
changed indexing in the EM

--- 2011-03-05 Multiresolution_framework/ltx/manuscript.tex
@@
 \end{align}
-Equations ~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into \eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving \ken{Substituting Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives}
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-\parham{For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
+For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form
 \begin{equation}\label{eq:Qfunction}
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}\left[ \sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \label{eq:upsilon1}\\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\right]\label{eq:Upsilon}.
 \end{align}
-The operator $\odot$ denotes block-wise matrix multiplication \mike{this still doesn't work!
-block matrix multiplication isn't a different thing to regular matrix multiplication I think?
-Isn't it just a different way to do regular matrix multiplication?
-Also one still doesn't know if the indices in eqs 31-33 are block indices or element indices.
-Also it's hard to invent notation, and if you do you need to make sure it's defined!
-Maybe check out the tensor literature?
-(or simply just index all this properly)}and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
-Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  \ken{I am getting confused here too ...
-is this a matrix of $n_x \times n_x$ blocks or just an $n_x \times n_x$ matrix - what is the problem to define simple matrices?} $\mathbf U$ is given by
+where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [\mathbf U]^{i,j}$ denotes $\left(i,j\right)$-block of the $n_x \times n_x$ block matrix $\mathbf U$.
+Each $1\times n_{\theta}$ block of $\mathbf U$ is given by
 \begin{align}
-\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
+The second terms in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
+Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta
 \end{equation}

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 
-\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set.
-(\figurename{\ref{fig:FieldEstimates}})}.
-\ken{Parham, can't understand the previous sentence.} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
+Field reconstruction at different levels of approximations shown in \figurename{\ref{fig:FieldEstimates}}.
+The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
 Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
suggestions for cutting

@@
 
-The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
 parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}
+\parham{Mike,Ken: can add to this list?}}
 
@@
 
-Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.
-Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.
-Most importantly, future work should be directed towards applying and validating the framework on real data.
+Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.\cut{ Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.} Most importantly, future work should be directed towards applying and validating the framework on real data.
 

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edit to abstract
defined FEM in the introduction

@@
 State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
+A synthetic example is given
+to demonstrate the framework.
 \end{abstract}
@@
 Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Most recently a framework was developed where a finite element model \parham{(FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edits to EM

@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-The second terms in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
+All $\left(i,j\right)$-blocks in the second brackets in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor edit to IDE neural field model

@@
 \section{IDE Neural Field Model}
-The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
+The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
 \begin{equation}\label{eq:DiscreteTimeModel}

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
suggestion for cutting

@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$\cut{~\cite{Rasmussen2005}}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor changes

@@
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and the observation noise is an i.i.d.
-Gaussian white noise process and $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
+Gaussian white noise process .
 % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor changes
for merge

--- 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
@@
 State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
-A synthetic example is given
-to demonstrate the framework.
 \end{abstract}
@@
 Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where a finite element model \parham{(FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 \section{IDE Neural Field Model}
-The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
+The stochastic integro-difference equation (IDE) form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
 \begin{equation}\label{eq:DiscreteTimeModel}
@@
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives
+Equations ~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} are then substituted into \eqref{eq:DiscreteTimeModel}, then we pre-multiply by $\boldsymbol\mu\left(\mathbf r\right)$ and integrate over the space giving \ken{Substituting Eqs.~\eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives}
 \begin{align}\label{eq:DecomposedModel2} 
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form
+\parham{For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form}
 \begin{equation}\label{eq:Qfunction}
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}\left[ \sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\right]\label{eq:Upsilon}.
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf U]_{j,i}\label{eq:upsilon1} \\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T}\odot \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\odot\mathbf{U}]_{j,i}\label{eq:Upsilon}.
 \end{align}
-where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [\mathbf U]^{i,j}$ denotes $\left(i,j\right)$-block of the $n_x \times n_x$ block matrix $\mathbf U$.
-Each $1\times n_{\theta}$ block of $\mathbf U$ is given by
+The operator $\odot$ denotes block-wise matrix multiplication \mike{this still doesn't work!
+block matrix multiplication isn't a different thing to regular matrix multiplication I think?
+Isn't it just a different way to do regular matrix multiplication?
+Also one still doesn't know if the indices in eqs 31-33 are block indices or element indices.
+Also it's hard to invent notation, and if you do you need to make sure it's defined!
+Maybe check out the tensor literature?
+(or simply just index all this properly)}and  $[.]_{i,j}$ denotes $\left(i,j\right)^{th}$ (block) element of the (block) matrix.
+Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix,  \ken{I am getting confused here too ...
+is this a matrix of $n_x \times n_x$ blocks or just an $n_x \times n_x$ matrix - what is the problem to define simple matrices?} $\mathbf U$ is given by
 \begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
+\left[ \mathbf U\right] _{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-All $\left(i,j\right)$-blocks in the second brackets in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
-Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right] _{i,j}\boldsymbol\theta
 \end{equation}
@@
 
-Field reconstruction at different levels of approximations shown in \figurename{\ref{fig:FieldEstimates}}.
-The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
+\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set.
+(\figurename{\ref{fig:FieldEstimates}})}.
+\ken{Parham, can't understand the previous sentence.} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
 Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
@@
 
-\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
 parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}}
+\parham{Mike,Ken: can add to this list?}
 
@@
 
-Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.\cut{ Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.} Most importantly, future work should be directed towards applying and validating the framework on real data.
+Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.
+Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.
+Most importantly, future work should be directed towards applying and validating the framework on real data.
 

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
deleted a paragraph from the results section

--- 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
@@
 The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
-Considering a one-dimensional field, the connectivity kernel is decomposed using,
+Considering a one-dimensional field, the connectivity kernel is decomposed as,
 \begin{equation}
@@
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
-\dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}
+
+% \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}  
 % \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edits following mikes nd kens comments

@@
 \section{Introduction}
-\IEEEPARstart{T}{he} human brain \mike{cortex?} has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons.
-This multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multiresolution data-driven framework for neural field modeling, the MultiResolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.
+\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons.
+This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
+This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.
 
@@
 These models typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy, and \cut{furthermore,} may also enable the development of new treatment strategies.
-This is particularly \cut{poignant with}\mike{relevant to} the advent of new devices that use therapeutic electrical stimulation.
+The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy and will enable the development of new treatment strategies.
+This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
 Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
-Therefore, there exists an enormous potential to improve the performance of these devices using control theory,\mike{which in turn requires a suitable dynamic model.}\cut{ but first a suitable model is required.} \ken{I's rather not mentioning control when our model has no input.} Neural mass and neural field models are the ideal candidates for estimation and control algorithms, due to their strong links with the underlying physiology and their parsimony.
+Therefore, there exists an enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model.
+Neural mass and neural field models are the ideal candidates for estimation algorithms, due to their strong links with the underlying physiology and their parsimony.
 It is expected that parameters of the neural fields models will be patient specific and will therefore, need to be inferred from data.
 
-The first work describing data-driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data.
-This approach was extended to coupled neural masses \cut{(using another model~}\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
+The first work describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\cite{Valdes1999}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
 Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where a finite element model \parham{(FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Most recently a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$\cut{~\cite{Rasmussen2005}}.
+disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
@@
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
-The firing rate slop, $\varsigma$ was set to $0.56  ~mV^{-1}$.
-The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations.
+The firing rate slop, $\varsigma$ was set to $0.56~mV^{-1}$.
+The distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
 The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude.
@@
 
-Field reconstruction at different levels of approximations shown in \figurename{\ref{fig:FieldEstimates}}.
+The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.
 The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
@@
 In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution FEM \ken{(I might have missed it but did we define this acronym)} representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
 This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
@@
 
-Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.\cut{ Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.} Most importantly, future work should be directed towards applying and validating the framework on real data.
+Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
+Most importantly, future work should be directed towards applying and validating the framework on real data.
 

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edits shortening eqation

@@
 The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes.
-Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
+Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
@@
 ...
-or are there practical situations when this known to be a good approximations?} The observation equation describing the electrophysiological recordings is given by
+or are there practical situations when this known to be a good approximations?}
+The observation equation describing the electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \begin{align}
- \boldsymbol\lambda^\top & (r-r')=\left[ \boldsymbol\phi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0}^\top(r-r') \quad \boldsymbol\psi_{j_0+1}^\top(r-r') \right. \nonumber \\
-&\left. \cdots \quad \boldsymbol\psi_{j}^\top(r-r')\right] \label{KernelBasisVector} \\
- \boldsymbol\mu^\top & (r)=\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \cdots \boldsymbol\psi_{j}^\top(r) \right]. 
+ \boldsymbol\lambda^\top & (s)=\left[ \boldsymbol\phi_{j_0}^\top(s) \quad \boldsymbol\psi_{j_0}^\top(s) \quad \boldsymbol\psi_{j_0+1}^\top(s) \quad \cdots \quad \boldsymbol\psi_{j}^\top(s)\right] \label{KernelBasisVector} \\
+ \boldsymbol\mu^\top & (r)=\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \quad \cdots \quad \boldsymbol\psi_{j}^\top(r) \right]. 
 \label{FieldBasisVector}
 \end{align}
-The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
+where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
@@
 To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
-\begin{align}
-N_{m}\left(r\right)=&\left(N_{m-1}\ast N_{1}\right)\left(r\right)\nonumber \\
-=&\int_0^{1} N_{m-1}\left( r-r'\right)dr' \quad m>1,
+\begin{equation}
+N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)dr',
 \label{SplineConvolutionIntegral}
-\end{align}
-where $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$
-\begin{equation}
-N_{1}\left(r\right)=
-\begin{cases}
-1 & \text{if $ 0\le r<1$}, \\
-0 & \mathrm{elsewhere}.
-\end{cases}
 \end{equation}
+where $m>1$ and $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ ($rect$ function).
+% \begin{equation}
+% N_{1}\left(r\right)=
+% \begin{cases}
+% 1 & \text{if $ 0\le r<1$}, \\
+% 0 & \mathrm{elsewhere}.
+% \end{cases}
+% \end{equation}
 Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
@@
 \begin{align}
- \varphi & _{m}\left(r\right) = \sum_{n=0}^{3m-2} q_n N_{m}\left(2r-n\right) \\
- q & _n = \frac{\left(-1\right)^n}{2^{m-1}} \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$},
+ \varphi & _{m}\left(r\right) = \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}}  q_n N_{m}\left(2r-n\right) \\
+ q & _n = \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$},
 \end{align}
@@
 The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
-\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table} The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
+%\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table}
+The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
 Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
@@
 
-\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
+\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
 parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}}
+\parham{Mike,Ken: can add to this list?}
 
-In order to apply the framework to real data several \ken{better say some} assumptions must be made, such as stationarity of the parameters over the estimation period.
+In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
changed EM equations

@@
 Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta}.
-
-% \cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}: 
-% \begin{equation}
-%  \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
-% \label{PsiPsiOrthogonality}
-% \end{equation}
-% \begin{equation}
-%  \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
-% \label{PhiPsiOrthogonality}
-% \end{equation}
 \section{State and Parameter Estimation}
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}\left[ \sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\right]\label{eq:Upsilon}.
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Gamma_1]^{j,i} \\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_2]^{j,i} \label{eq:upsilon1}\\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}.
 \end{align}
-where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [\mathbf U]^{i,j}$ denotes $\left(i,j\right)$-block of the $n_x \times n_x$ block matrix $\mathbf U$.
-Each $1\times n_{\theta}$ block of $\mathbf U$ is given by
+where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [.]^{i,j}$ denotes $\left(i,j\right)$-block of the  block matrix and where
+\begin{align}
+ [\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
+ [\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
+[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\label{eq:Gamma3}.
+\end{align}
+ Each $1\times n_{\theta}$ block of $n_x \times n_x$ block matrix $\mathbf U$ is given by
 \begin{align}
@@
 where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
-All $\left(i,j\right)$-blocks in the second brackets in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
+All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
correction to  EM equations
defined new indexing for  EM equations

@@
 \end{align}
-where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [.]^{i,j}$ denotes $\left(i,j\right)$-block of the  block matrix and where
+where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
 \begin{align}
@@
  [\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
-[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\label{eq:Gamma3}.
+[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
 \end{align}
@@
 \end{align}
-where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
+where $[.]_{p:} $ denotes $p^{th}$ row of the matrix.
 All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
minor edit for  EM
put theta in line

@@
 \end{equation}
-where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation \eqref{eq:Qfunction} is maximum at
-\begin{align}
- \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
-\end{align}
-where
+where $\beta$ is constant with respect to $\boldsymbol\theta$.
+Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$ where
+% \begin{align}
+%  \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
+% \end{align}
+% where
 \begin{align}\label{eq:upsilon0}
@@
 where $[.]_{p:} $ denotes $p^{th}$ row of the matrix.
-All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
+All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta, 
 \end{equation}
@@
  \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+
+%  \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
put ken comment back in
minor edit

--- 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
@@
 \end{equation}
-where $m>1$ and $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ ($rect$ function).
+where $m>1$, $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ ($rect$ function).
 % \begin{equation}
@@
 Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta}.
+
+% \cut{ It is important to note that B-spline scaling and wavelet functions have the following orthogonality properties \cite{Unser1993}: 
+% \begin{equation}
+%  \left\langle \psi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
+% \label{PsiPsiOrthogonality}
+% \end{equation}
+% \begin{equation}
+%  \left\langle \phi_{j_1,l_1}(s),\psi_{j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
+% \label{PhiPsiOrthogonality}
+% \end{equation}
 \section{State and Parameter Estimation}
@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Gamma_1]^{j,i} \\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}.
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}\left[ \sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\right] \label{eq:upsilon1}\\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}\left[\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\right]\label{eq:Upsilon}.
 \end{align}
-where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
-\begin{align}
- [\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
- [\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
-[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
-\end{align}
- Each $1\times n_{\theta}$ block of $n_x \times n_x$ block matrix $\mathbf U$ is given by
+where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [\mathbf U]^{i,j}$ denotes $\left(i,j\right)$-block of the $n_x \times n_x$ block matrix $\mathbf U$.
+Each $1\times n_{\theta}$ block of $\mathbf U$ is given by
 \begin{align}
@@
 \end{align}
-where $[.]_{p:} $ denotes $p^{th}$ row of the matrix.
-All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
+where $[.]_{j:} $ denotes $j^{th}$ row of the matrix.
+All $\left(i,j\right)$-blocks in the second brackets in  (\ref{eq:upsilon0}-\ref{eq:Upsilon}) can be computed as a once-off before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
@@
 		\includegraphics[scale=1]{./Graph/Field.pdf}
-		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions.
+		\caption{Actual (grey) and estimated (black) neural fields at a time instant for different spatial resolutions.
 (a) $j=0$, $n_x=17$, $RMSE = 2.10$.

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex

--- 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
@@
  \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-
-%  \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
not sure about all the millions of refs in the conlclusion

--- 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
@@
  \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-
-%  \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
 parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}
+\parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing?
+Also it's not terribly specific.}
 

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
added more to my comment about the list of refs
made a few more commends about the block matrix stuff, and caught some typos. Still not sure what we're doing about bold 'r's.

@@
  \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}.
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}
 \end{align}
-where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
+where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where
 \begin{align}
@@
 \end{align}
- Each $1\times n_{\theta}$ block of $n_x \times n_x$ block matrix $\mathbf U$ is given by
+Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix $\mathbf U$ is given by \mike{just checking, does $n_x = \mathrm{constant} \times n_\theta$?
+or is each block $n_x \times n_x$ making $U$ something like $n_x \times n_xn_\theta$?
+It's probably worth being specific here, making sure that we use the idea of block matrices purely as a mechanism for fancy indexing, rather than treating them as special in some sense.}
 \begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr
 \end{align}
-where $[.]_{p:} $ denotes $p^{th}$ row of the matrix.
-All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
+\mike{bold $r$s?}where $[.]_{j:} $ denotes the $j^{th}$ row.
+All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
@@
 \parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing?
-Also it's not terribly specific.}
+Also it's not terribly specific.
+I think it's better to stick to how it has the potential to model brains in a manner that rocks, rather than loosely saying it could be applied to any spatiotemporal system, i.e.
+literally everything.}
 

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
now down to four pages

--- 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
@@
 A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-\ken{Doing something just for computational efficiency only might be weak ...
+% \ken{Doing something just for computational efficiency only might be weak ...
 is there other work we can reference that makes the linearity assumption?
@@
 Integers $j$ and $l$ are the scale and translation parameters, respectively.
-Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components (by increasing $j$) due their low and band-pass spectral characteristics, respectively.
+Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components due their low and band-pass characteristics, respectively.
 The field is decomposed using
@@
 \begin{align}
-\boldsymbol\theta^\top &=\left[ \boldsymbol\alpha_{j_0}^\top \quad \boldsymbol\beta_{j_0}^\top \quad \boldsymbol\beta_{j_0+1}^\top \cdots \boldsymbol\beta_{j}^\top\right] 
+\boldsymbol\theta^\top &=\left[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}\right] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top &=\left[\mathbf{x}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}}^\top \quad  \check{\mathbf{x}}_{t,j_{0}+1}^\top \cdots \check{\mathbf{x}}_{t,j}^\top\right].
+\mathbf{x}_{t}^\top &=\left[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}\right].
 \label{FieldWeights}
@@
 \begin{align}
- \boldsymbol\lambda^\top & (s)=\left[ \boldsymbol\phi_{j_0}^\top(s) \quad \boldsymbol\psi_{j_0}^\top(s) \quad \boldsymbol\psi_{j_0+1}^\top(s) \quad \cdots \quad \boldsymbol\psi_{j}^\top(s)\right] \label{KernelBasisVector} \\
- \boldsymbol\mu^\top & (r)=\left[ \boldsymbol\phi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0}^\top(r) \quad \boldsymbol\psi_{j_0+1}^\top(r) \quad \cdots \quad \boldsymbol\psi_{j}^\top(r) \right]. 
+&\boldsymbol\lambda^\top(s)=\left[
+	\begin{array}{ccccc}
+		 \boldsymbol\phi_{j_0}^\top(s) & \boldsymbol\psi_{j_0}^\top(s) & \boldsymbol\psi_{j_0+1}^\top(s) & \cdots & \boldsymbol\psi_{j}^\top(s)
+		\end{array}
+		\right] \label{KernelBasisVector} \\
+&\boldsymbol\mu^\top (r)= \left[
+			\begin{array}{ccccc}
+				\boldsymbol\phi_{j_0}^\top(r) & \boldsymbol\psi_{j_0}^\top(r) & \boldsymbol\psi_{j_0+1}^\top(r) & \cdots & \boldsymbol\psi_{j}^\top(r) 
+			\end{array} 
+				\right]. 
 \label{FieldBasisVector}
@@
 The MRAIDE can be implemented using various classes of scaling and wavelet functions.
-B-spline functions were chosen due their compact support and the ability to analytically calculate the convolution and inner product to form the matrices $ \boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
-To show how the matrices are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
+B-spline functions were chosen due their compact support and the ability to analytically calculate the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
 \begin{equation}
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-This holds as $N_m\left(r\right)$ is isotropic.
-The $m^{th}$-order B-spline wavelet function is defined as (see \cite{Chui1992})
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as $N_m\left(r\right)$ is isotropic. The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
 \begin{align}
@@
 where $\beta$ is constant with respect to $\boldsymbol\theta$.
-Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$ where
+Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$, where
 % \begin{align}
@@
  \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}.
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}
 \end{align}
-where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
+and $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
 \begin{align}
@@
 
-The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}.
+The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
 \begin{figure}[!h] 
@@
 
- \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems described by IDEs, such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
+%\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex

@@
 \end{align}
-and $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where
+where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where
 \begin{align}
@@
 \end{align}
-Each $1\times n_{\theta}$ block of $n_x \times n_x$ block matrix $\mathbf U$ is given by
+Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix $\mathbf U$ is given by \mike{just checking, does $n_x = \mathrm{constant} \times n_\theta$?
+or is each block $n_x \times n_x$ making $U$ something like $n_x \times n_xn_\theta$?
+It's probably worth being specific here, making sure that we use the idea of block matrices purely as a mechanism for fancy indexing, rather than treating them as special in some sense.}
 \begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr
 \end{align}
-where $[.]_{p:} $ denotes $p^{th}$ row of the matrix.
-All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations.
+\mike{bold $r$s?}where $[.]_{j:} $ denotes the $j^{th}$ row.
+All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
@@
 
-\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems described by IDEs, such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-%\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+ \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
+\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
 parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}
+\parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing?
+Also it's not terribly specific.
+I think it's better to stick to how it has the potential to model brains in a manner that rocks, rather than loosely saying it could be applied to any spatiotemporal system, i.e.
+literally everything.}
 

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
made Gamma bold
made mu bold in 33
comment in result section

@@
 \begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Gamma_1]^{j,i} \\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i} \label{eq:upsilon1}\\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_3]^{j,i}\label{eq:Upsilon}
 \end{align}
@@
 \begin{align}
- [\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
- [\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
-[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
+ [\boldsymbol\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
+ [\boldsymbol\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
+[\boldsymbol\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
 \end{align}
@@
 \begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr
 \end{align}
 \mike{bold $r$s?}where $[.]_{j:} $ denotes the $j^{th}$ row.
-All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed before the commencement of the EM iterations.
+All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$ and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
@@
 
-The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
+\parham{The actual connectivity kernel} and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
minor chanegs
did  Mike  comment on the EM

@@
 Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Most recently a framework was developed where \mike{a finite element model (FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 \end{align}
-Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix $\mathbf U$ is given by \mike{just checking, does $n_x = \mathrm{constant} \times n_\theta$?
-or is each block $n_x \times n_x$ making $U$ something like $n_x \times n_xn_\theta$?
-It's probably worth being specific here, making sure that we use the idea of block matrices purely as a mechanism for fancy indexing, rather than treating them as special in some sense.}
+Each $1\times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is given by 
 \begin{align}
@@
 \end{align}
-\mike{bold $r$s?}where $[.]_{j:} $ denotes the $j^{th}$ row.
+where $[.]_{j:} $ denotes the $j^{th}$ row.
 All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$ and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/KernelUnknownSupportWithVarsigma.pdf}
+% 		\includegraphics[scale=1]{./Graph/KernelUnknownSupportWithVarsigma.pdf}
+		\includegraphics[scale=1]{./Graph/test.pdf}
 		\caption{Connectivity kernel estimate.
@@
 In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+The novel and key developments of the paper include the multi-resolution \mike{FEM} representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
 This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
have compressed a bit the final two paragraphs of the conclusion.

--- 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
@@
 
-In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
+\mike{The presented framework makes two key assumptions about the cortex: a linear activiation function and stationary dynamics.
+Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition.
+While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
+Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays at lower spatial resolutions.
+The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel.
+Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}
+
+\cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
@@
 Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
-Most importantly, future work should be directed towards applying and validating the framework on real data.
+Most importantly, future work should be directed towards applying and validating the framework on real data.}
 

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
caught a little typo

@@
 The key development in this paper is the multi-resolution decomposition forming the state-space model.
-The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.
+The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}
 
-Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
+\cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
 Most importantly, future work should be directed towards applying and validating the framework on real data.}

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
changed figure name to IEEE format
edits to the whole paper

@@
 	\label{eq:KernelFiniteExpansion} \\
-	v_t\left(r\right) &\approx \boldsymbol\mu\left(r\right)^\top\mathbf{x}_t,
+	v_t\left(r\right) &\approx \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t,
 	\label{eq:FieldFiniteExpansion}
@@
 \begin{align}
-\boldsymbol\theta^\top &=\left[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}\right] 
+\boldsymbol\theta^\top &=[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top &=\left[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}\right].
+\mathbf{x}_{t}^\top &=[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}].
 \label{FieldWeights}
@@
 \begin{align}
-&\boldsymbol\lambda^\top(s)=\left[
+&\boldsymbol\lambda^\top(s)=[
 	\begin{array}{ccccc}
@@
 		\end{array}
-		\right] \label{KernelBasisVector} \\
-&\boldsymbol\mu^\top (r)= \left[
+		] \label{KernelBasisVector} \\
+&\boldsymbol\mu^\top (r)= [
 			\begin{array}{ccccc}
@@
 			\end{array} 
-				\right]. 
+				].
 \label{FieldBasisVector}
@@
 \end{equation}
-which is a vector valued, zero-mean normally distributed white noise process with covariance (see \cite{Scerri2009} for proof)
+which is a vector valued, zero-mean normally distributed white noise process with covariance \parham{(see \cite{Scerri2009} for proof)}
 \begin{equation}
@@
 where each element of the observation matrix is given by
-\begin{equation}
+\begin{equation}\label{eq:Observationmatrix}
 	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
@@
 \end{equation}
-where $m>1$, $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ ($rect$ function).
+where $m>1$, $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ \parham{($rect$ function, is different)}.
 % \begin{equation}
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as $N_m\left(r\right)$ is isotropic. The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+\parham{This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.} The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
 \begin{align}
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound used is a quadratic of the form
+For the linear state-space model given by (\ref{eq:StateEquation}-\ref{eq:Observationmatrix}), the bound used is a quadratic of the form
 \begin{equation}\label{eq:Qfunction}
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/Field.pdf}
+		\includegraphics[scale=1]{./Graph/fig1.pdf}
 		\caption{Actual (grey) and estimated (black) neural fields at a time instant for different spatial resolutions.
@@
 	\centering
-% 		\includegraphics[scale=1]{./Graph/KernelUnknownSupportWithVarsigma.pdf}
-		\includegraphics[scale=1]{./Graph/test.pdf}
+		\includegraphics[scale=1]{./Graph/fig2.pdf}
 		\caption{Connectivity kernel estimate.
 (a) The actual kernel is shown with the black solid line.
-The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
+The estimated kernel and \mike{confidence interval} is shown by the red line and red shaded region ($\pm2$ std.).
 (b) Kernel scaling functions at $j=1$.

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
updated figure1
edit to result section

@@
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm \cite{Freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
@@
 The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.
-The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72.
+The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.78.
 Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
@@
 		\caption{Actual (grey) and estimated (black) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, $RMSE = 2.10$.
-(b) $j=1$, $n_x=33$, $RMSE = 1.42$.
-(c) $j=2$, $n_x=65$, $RMSE = 0.80$.
-(d) $j=3$, $n_x=131$, $RMSE = 0.72$.
-(e) $j=4$, $n_x=263$, $RMSE=0.72$.}
+(a) $j=0$, $n_x=17$, $RMSE = 1.93$.
+(b) $j=1$, $n_x=33$, $RMSE = 1.39$.
+(c) $j=2$, $n_x=65$, $RMSE = 0.90$.
+(d) $j=3$, $n_x=131$, $RMSE = 0.78$.
+(e) $j=4$, $n_x=263$, $RMSE=0.78$.}
 	\label{fig:FieldEstimates}

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-200 realizations of 1 second of data were generated.
-The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
+200 realizations of 1 second of data were generated \parham{and the estimation was applied to the final 900 ms, allowing the model's initial transients to die out.} The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
@@
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm \cite{Freestone2011}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This is obtained by examining the average (over time) power of the spatial frequency of the observations} \cite{Freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
@@
 (a) The actual kernel is shown with the black solid line.
-The estimated kernel and \mike{confidence interval} is shown by the red line and red shaded region ($\pm2$ std.).
+The mean kernel estimates over 200 realizations and \mike{confidence interval} are shown by the red line and red shaded region ($\pm2$ std.).
 (b) Kernel scaling functions at $j=1$.

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
edits to result section

@@
 
-\parham{The actual connectivity kernel} and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
-The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
+\parham{It is assumed that the support of the kernel is unknown to the estimator.} The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
davids edits to intro

@@
 \section{Introduction}
-\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons.
+\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels to networks of millions of neurons.
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 These models typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-The ability to create patient-specific neural models will contribute to our knowledge base of poorly understood diseases such as epilepsy and will enable the development of new treatment strategies.
+The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
 This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
-Presently, stimulation strategies for devices operate in an open-loop, where stimulation parameters are chosen using a process of trial and error.
-Therefore, there exists an enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model.
-Neural mass and neural field models are the ideal candidates for estimation algorithms, due to their strong links with the underlying physiology and their parsimony.
-It is expected that parameters of the neural fields models will be patient specific and will therefore, need to be inferred from data.
+Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error.
+Therefore, there exists enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model.
+Neural mass and neural field models are the ideal candidates for estimation algorithms due to their strong links with the underlying physiology and their parsimony.
+It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 
@@
 This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
-Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently a framework was developed where \mike{a finite element model (FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
+Most recently, a framework was developed where \mike{a finite element model (FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously.
 
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$.
-Synaptic dynamics are included through the parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
+Synaptic dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
 The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
davids edits to IDE neiural field model

@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance, such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
+disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
@@
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process .
+Gaussian white noise process.
 % $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
davids edits to state and parameter estimtion

@@
 Integers $j$ and $l$ are the scale and translation parameters, respectively.
-Scaling functions retain the lowest frequency components, whilst the wavelet functions extract successively higher frequency components due their low and band-pass characteristics, respectively.
+Scaling functions retain the lowest frequency components, while the wavelet functions extract successively higher frequency components due to their low-pass and band-pass properties, respectively.
 The field is decomposed using
@@
 \end{equation}
-where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion, and constitute the state vector at time $t$. %\dean{Need to define these guys as the states here!}
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$. %\dean{Need to define these guys as the states here!}
 
@@
 The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
-Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$ contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$ respectively.
+Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$, respectively.
 
-The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$ respectively, are defined by
+The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
 \begin{align}
@@
 			\end{array} 
-				].
+				],
 \label{FieldBasisVector}
@@
 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right) 
+	    \boldsymbol\mu^\top\left(r\right). 
 	\, dr'dr}
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$ and integrating over the space gives
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \end{equation}
-which is a vector valued, zero-mean normally distributed white noise process with covariance \parham{(see \cite{Scerri2009} for proof)}
+which is a vector valued, zero-mean normally distributed, white noise process with covariance \parham{(see \cite{Scerri2009} for proof)}
 \begin{equation}
@@
 \end{equation}
-where $m>1$, $\ast$ denotes convolution and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$ \parham{($rect$ function, is different)}.
+where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$.
 % \begin{equation}
@@
 \end{equation}
-Using the associativity property of convolution we have
+Using the associativity property of convolution, we have
 \setlength{\arraycolsep}{0.0em}
@@
 \end{align}
-A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline, such that
+A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline such that
 \begin{align}
@@
 where $q_n$ are the coefficients.
-By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct} the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$ the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-In this paper $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
+By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
+In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
 Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta}.
@@
  \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_3]^{j,i}\label{eq:Upsilon}
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_3]^{j,i},\label{eq:Upsilon}
 \end{align}
-where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where
+where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
 \begin{align}
@@
 \begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr,
 \end{align}
 where $[.]_{j:} $ denotes the $j^{th}$ row.
-All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$ and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
+All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$, and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
 Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta, 
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta. 
 \end{equation}
 
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005}
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005},
 \begin{align}\label{eq:Xivariables}

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
davids edits to the discussion

@@
 \usepackage{color}
-\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
+\newcommand{\mike}[1]{\textcolor{red}{#1}}
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
@@
 State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
-A synthetic example is given
+A synthetic example is provied
 to demonstrate the framework.
@@
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently, a framework was developed where \mike{a finite element model (FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 \end{align}
-Each $1\times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is given by 
+Each $1\times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is
 \begin{align}
@@
 To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-200 realizations of 1 second of data were generated \parham{and the estimation was applied to the final 900 ms, allowing the model's initial transients to die out.} The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
+200 realizations of 1~s of data were generated, where the estimation was applied to the final 900~ms, allowing the model's initial transients to die out.
+The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
 The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
@@
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This is obtained by examining the average (over time) power of the spatial frequency of the observations} \cite{Freestone2011}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the power (over time \dean{realization?}) of the spatial frequency from the observations} \cite{Freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
@@
 The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
-\parham{It is assumed that the support of the kernel is unknown to the estimator.} The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+\dean{No assumptions where made about the shape of the kernel.} \parham{It was assumed that the support of the kernel is unknown to the estimator.} The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
@@
 In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution \mike{FEM} representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
 This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
@@
 
- \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
-\ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
+\cut{The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
+% \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
 (This is copy and paste from my thesis ...
@@
 
-\mike{The presented framework makes two key assumptions about the cortex: a linear activiation function and stationary dynamics.
+\mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
 Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition.
-While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
+\dean{(our main wasn't really to relax the assumptions)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
 Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays at lower spatial resolutions.
@@
 
-\cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
+% \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
@@
 
-\cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
+% \cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
 Most importantly, future work should be directed towards applying and validating the framework on real data.}

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
some minor edits with Parham

@@
 Therefore, there exists enormous potential to improve the performance of these devices using systems theory, which in turn requires a suitable dynamic model.
-Neural mass and neural field models are the ideal candidates for estimation algorithms due to their strong links with the underlying physiology and their parsimony.
+Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
 It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
-A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
+\dean{A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
+}
 % \ken{Doing something just for computational efficiency only might be weak ...
@@
 
-The MRAIDE can be implemented using various classes of scaling and wavelet functions.
-B-spline functions were chosen due their compact support and the ability to analytically calculate the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
+The MRAIDE can be implemented using various scaling and wavelet functions.
+B-spline functions were chosen due to their compact support and the ability to analytically define the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
 To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
@@
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the power (over time \dean{realization?}) of the spatial frequency from the observations} \cite{Freestone2011}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the power in the spatial frequency (over time) of the spatial frequency from the observations} \cite{Freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
@@
 The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
-\dean{No assumptions where made about the shape of the kernel.} \parham{It was assumed that the support of the kernel is unknown to the estimator.} The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+No assumptions where made about the shape of the kernel.
+The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
@@
 The mean kernel estimates over 200 realizations and \mike{confidence interval} are shown by the red line and red shaded region ($\pm2$ std.).
-(b) Kernel scaling functions at $j=1$.
-(c) Kernel wavelet functions at $j=1$.}
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}
 	\label{fig:KernelEstimate}
@@
 Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition.
-\dean{(our main wasn't really to relax the assumptions)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
+\dean{(our main aim wasn't really to relax the assumptions.
+if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
 Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays at lower spatial resolutions.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
edit to result section

@@
 \end{equation}
-which is a vector valued, zero-mean normally distributed, white noise process with covariance \parham{(see \cite{Scerri2009} for proof)}
+which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
 \begin{equation}
@@
 The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the power in the spatial frequency (over time) of the spatial frequency from the observations} \cite{Freestone2011}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
some typos

@@
 Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
-State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
-A synthetic example is provied
+State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
+A synthetic example is provided
 to demonstrate the framework.
@@
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
 
@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
+disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$ \cite{Rasmussen2005}.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
@@
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 
@@
 		\includegraphics[scale=1]{./Graph/fig1.pdf}
-		\caption{Actual (grey) and estimated (black) neural fields at a time instant for different spatial resolutions.
+		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions.
 (a) $j=0$, $n_x=17$, $RMSE = 1.93$.
@@
 (a) The actual kernel is shown with the black solid line.
-The mean kernel estimates over 200 realizations and \mike{confidence interval} are shown by the red line and red shaded region ($\pm2$ std.).
+The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
 (b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor eits

@@
 where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-\parham{This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.} The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
+This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
+The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
 \begin{align}

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
added reference for the linear activation function

@@
 The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$ \cite{Rasmussen2005}.
+disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
-\dean{A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
+\dean{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
 }

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor correctin

@@
 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right). 
-	\, dr'dr}
+	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
 \end{align}
@@
 %\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table}
-The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
+The spatial cutoff frequency of the observed field, \parham{$y_t(r_n)$}, was used to specify the level of decomposition required to represent the field using the wavelets.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{this was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor correctin

@@
 if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
-Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays at lower spatial resolutions.
+Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.
 The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel.
@@
 
-% \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
+ \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
visakan comments

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multi-resolution Neural Field Estimation }
+\title{Multi-resolution \parham{spatio-temporal} Neural Field Estimation }
 
@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
-\dean{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
-}
+\parham{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator.}
+%  due to high computational demands when using a nonlinear (sigmoidal) activation function. }
 % \ken{Doing something just for computational efficiency only might be weak ...
@@
 
-\cut{The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
 % \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
@@
 
- \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
+ In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
 Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model.
-The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}
+The key development in this paper is the multi-resolution decomposition forming the state-space model \parham{and its ability to approximate the neural field at required resolution.} \cut{The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}
 

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
changed fig2
for merge

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
-State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
-A synthetic example is provided
+State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
+A synthetic example is provied
 to demonstrate the framework.
@@
 \section{Introduction}
-\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels to networks of millions of neurons.
+\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously.
 
@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
-\dean{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
+\dean{A linear form of the activation function was chosen to construct the estimator due to high computational demands when using a nonlinear (sigmoidal) activation function.
 }
@@
 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
+	    \boldsymbol\mu^\top\left(r\right). 
+	\, dr'dr}
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multipling by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \end{equation}
-which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
+which is a vector valued, zero-mean normally distributed, white noise process with covariance \parham{(see \cite{Scerri2009} for proof)}
 \begin{equation}
@@
 where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
-The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
+\parham{This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.} The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
 \begin{align}
@@
 %\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table}
-The spatial cutoff frequency of the observed field, \parham{$y_t(r_n)$}, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{this was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
+The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{This was obtained by averaging the power in the spatial frequency (over time) of the spatial frequency from the observations} \cite{Freestone2011}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
@@
 		\includegraphics[scale=1]{./Graph/fig1.pdf}
-		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions.
+		\caption{Actual (grey) and estimated (black) neural fields at a time instant for different spatial resolutions.
 (a) $j=0$, $n_x=17$, $RMSE = 1.93$.
@@
 (a) The actual kernel is shown with the black solid line.
-The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
+The mean kernel estimates over 200 realizations and \mike{confidence interval} are shown by the red line and red shaded region ($\pm2$ std.).
 (b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\parham{Large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
made some awesome changes that will blow your minds

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multi-resolution \parham{spatio-temporal} Neural Field Estimation }
+\title{Multi-Resolution Spatio-Temporal Neural Field Estimation }
 
@@
 The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
-\begin{align}
-&\boldsymbol\lambda^\top(s)=[
-	\begin{array}{ccccc}
-		 \boldsymbol\phi_{j_0}^\top(s) & \boldsymbol\psi_{j_0}^\top(s) & \boldsymbol\psi_{j_0+1}^\top(s) & \cdots & \boldsymbol\psi_{j}^\top(s)
-		\end{array}
-		] \label{KernelBasisVector} \\
-&\boldsymbol\mu^\top (r)= [
-			\begin{array}{ccccc}
-				\boldsymbol\phi_{j_0}^\top(r) & \boldsymbol\psi_{j_0}^\top(r) & \boldsymbol\psi_{j_0+1}^\top(r) & \cdots & \boldsymbol\psi_{j}^\top(r) 
-			\end{array} 
-				],
+\begin{equation}
+    \label{KernelBasisVector}
+    \boldsymbol\lambda^\top(s)=[
+    \boldsymbol\phi_{j_0}^\top(s) ~
+    \boldsymbol\psi_{j_0}^\top(s) ~ 
+    \boldsymbol\psi_{j_0+1}^\top(s) ~
+    \cdots ~
+    \boldsymbol\psi_{j}^\top(s)]
+\end{equation} 
+\begin{equation}
     \label{FieldBasisVector}
-\end{align}
+    \boldsymbol\mu^\top (r) = [
+    \boldsymbol\phi_{j_0}^\top(r) ~ 
+    \boldsymbol\psi_{j_0}^\top(r) ~ 
+    \boldsymbol\psi_{j_0+1}^\top(r) ~ 
+    \cdots ~ 
+    \boldsymbol\psi_{j}^\top(r)
+]   
+\end{equation}
+
 where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
@@
   \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
-Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition.
-\dean{(our main aim wasn't really to relax the assumptions.
-if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
+Our main aim for this framework in the future is to relax these assumptions using the multi-resolution decomposition.
+While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
 Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
edit to model derivation

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 \section{Introduction}
-\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
+\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels to networks of millions of neurons.
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
-\parham{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator.}
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{Murphy2009}.
 %  due to high computational demands when using a nonlinear (sigmoidal) activation function. }

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
edit result section
monir edit after meeting

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{Murphy2009}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$.
+\parham{A linear form of the activation function \cite{Murphy2009} was chosen to construct the estimator.}
 %  due to high computational demands when using a nonlinear (sigmoidal) activation function. }
@@
 The spatial cutoff frequency of the observed field, \parham{$y_t(r_n)$}, was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{this was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
edit to discussion

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multi-Resolution Spatio-Temporal Neural Field Estimation }
+\title{Multi-Resolution Spatiotemporal Neural Field Estimation }
 
@@
 The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
-\begin{equation}
+\begin{align}
     \label{KernelBasisVector}
-    \boldsymbol\lambda^\top(s)=[
+    \boldsymbol\lambda^\top(s)=&\left[
     \boldsymbol\phi_{j_0}^\top(s) ~
@@
     \cdots ~
-    \boldsymbol\psi_{j}^\top(s)]
-\end{equation} 
-\begin{equation}
+    \boldsymbol\psi_{j}^\top(s)\right] \\
     \label{FieldBasisVector}
-    \boldsymbol\mu^\top (r) = [
+    \boldsymbol\mu^\top (r) =& \left[
     \boldsymbol\phi_{j_0}^\top(r) ~ 
@@
     \boldsymbol\psi_{j}^\top(r)
-]   
-\end{equation}
+\right]   
+\end{align}
 
@@
 %\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table}
-The spatial cutoff frequency of the observed field, \parham{$y_t(r_n)$}, was used to specify the level of decomposition required to represent the field using the wavelets.
+The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
 Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{this was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
@@
 
-  \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
+  % \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
 Our main aim for this framework in the future is to relax these assumptions using the multi-resolution decomposition.
@@
 In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
-Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics.
+A critical assumption is that the model provides an apt description of the cortical dynamics.
 The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model \parham{and its ability to approximate the neural field at required resolution.} \cut{The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}
+The key development in this paper is the multi-resolution decomposition forming the state-space model \cut{and its ability to approximate the neural field at required the level of accuracy.} While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
+Additional avenues for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, and time delays according to spatial resolutions.
+The estimation techniques should also be extended to deal with spatiotemporal heterogeneity in the kernel.
+Finally, future work should be directed towards applying and validating the framework on real data.
 

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
edit to discussion

@@
 The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, \parham{this was obtained by averaging the spectral power of the spatial frequency (over time) from the observations} \cite{Scerri2009}.
+Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-\parham{Large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\parham{the large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
@@
 
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005}.
 % \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model \cut{and its ability to approximate the neural field at required the level of accuracy.} While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
+The key development in this paper is the multi-resolution decomposition forming the state-space model.
+While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
 Additional avenues for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, and time delays according to spatial resolutions.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 
-\author{\parham{P.
-Aram}, \dean{D.R.
-Freestone~\IEEEmembership{Graduate Student Member,~IEEE}}, \mike{M.
-Dewar}, \ken{K.Scerri~\IEEEmembership{Member,~IEEE,}}, D.B.
+\author{P.
+Aram, D.R.
+Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M.
+Dewar, K.Scerri~\IEEEmembership{Member,~IEEE,}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-\parham{the large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\parham{The large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-\parham{The large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\parham{The large standard deviation is due to the high number of parameters need to be estimated.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor edits

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-\parham{The large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+The large standard deviation is due to the high number of parameters need to be estimated.
+The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
added acknowledgement

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 
-\author{P.
-Aram, D.R.
-Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M.
-Dewar, K.Scerri~\IEEEmembership{Member,~IEEE,}, D.B.
+\author{\parham{P.
+Aram}, \dean{D.R.
+Freestone~\IEEEmembership{Graduate Student Member,~IEEE}}, \mike{M.
+Dewar}, \ken{K.Scerri~\IEEEmembership{Member,~IEEE,}}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 \thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
+of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia.
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
 \thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
@@
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+We use the standard EM algorithm for linear dynamic systems \cite{Roweis1999,Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-\parham{The large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+\parham{Large standard deviation is due to the high number of parameters.} The small error in the estimate is attributed to the MRA of the system used to form the estimator.
 \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
@@
 
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005}.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}.
 % \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model.
-While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
+The key development in this paper is the multi-resolution decomposition forming the state-space model \cut{and its ability to approximate the neural field at required the level of accuracy.} While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
 Additional avenues for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, and time delays according to spatial resolutions.

### 2011-03-09 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor change to fig2

--- 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
@@
 Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M.
-Dewar, K.Scerri~\IEEEmembership{Member,~IEEE,}, D.B.
+Dewar, K.Scerri~\IEEEmembership{Member,~IEEE}, D.B.
 Grayden~\IEEEmembership{Member,~IEEE,} and V.
@@
 %  \end{IEEEkeywords}
-% \IEEEpeerreviewmaketitle
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+\ifCLASSOPTIONpeerreview
+  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
+  \fi
+%
+%  For peerreview papers, this IEEEtran command inserts a page break and
+%creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \section{Introduction}

### 2011-03-09 Multiresolution_framework/ltx/ResearchHighlights.tex
added research highlights

%  Created by Parham Aram on 09-03-2011
%  Copyright (c) 2010 . All rights reserved.
%
\documentclass[]{article}

\begin{document}

\textbf{Research Highlights}
\begin{itemize}
	\item We derive a model-based, data-driven estimator of continuum neural field parameters.
	\item Both macroscopic and microscopic behaviour of the system can be represented simultaneosly.
	\item We show how to infer intracortical connectivity kernel with an arbitrary shape from data.
\end{itemize}

\end{document}

### 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
minor edits
final changes
made abstract less than 50 words

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multi-Resolution Spatiotemporal Neural Field Estimation }
+\title{Multi-Resolution Neural Field Estimation }
 
@@
 %\boldmath
-The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes.
-Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
+We develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
@@
 % Note that keywords are not normally used for peerreview papers.
-% \begin{IEEEkeywords}
-%  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
-%  \end{IEEEkeywords}
+ \begin{IEEEkeywords}
+  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+  \end{IEEEkeywords}
 % For peer review papers, you can put extra information on the cover
 % page as needed:
-\ifCLASSOPTIONpeerreview
-  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
-  \fi
+% \ifCLASSOPTIONpeerreview
+%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
+%   \fi
 %

### 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
added emails to affiliatins (required by the journal)

@@
 of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia.
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
-\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
+(e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).}
+\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}
 \thanks{K. Scerri is with the Department of Systems and Control Engineering, University
-of Malta, Msida, MSD 2080, Malta.}}
+of Malta, Msida, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
 % <-this % stops a space

### 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
added emails to affiliatins (required by the journal)

@@
 of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia.
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
-(e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).}
+(e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
 \thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex
added emails to affiliatins (required by the journal)
added kernel components and changed the caption

@@
 \thanks{K. Scerri is with the Department of Systems and Control Engineering, University
-of Malta, Msida, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
+of Malta, Msida, MSD, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
 % <-this % stops a space
@@
 		\includegraphics[scale=1]{./Graph/fig2.pdf}
-		\caption{Connectivity kernel estimate.
-(a) The actual kernel is shown with the black solid line.
+		\caption{\parham{Connectivity kernel estimate.
+(a) The actual kernel and it's components are shown by solid and dashed black line respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}}
 	\label{fig:KernelEstimate}

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex
minor correction for fig2 caption
added ref

--- 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-For example, it is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009}.
+It is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009,Breakspear2005}.
+%\dean{This is a test to see if we can fit something about Breaky's paper in here.
+It would be nice to slot something in here because he used wavelets.}
 
@@
 
-In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period.
+In order to apply the framework to real data some assumptions must be made.
 A critical assumption is that the model provides an apt description of the cortical dynamics.
@@
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The key development in this paper is the multi-resolution decomposition forming the state-space model.
-While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the much larger state-space remains a challenge.
+The key development is the multi-resolution decomposition forming the state-space model.
+While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.
 Additional avenues for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, and time delays according to spatial resolutions.

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex

@@
 		\includegraphics[scale=1]{./Graph/fig2.pdf}
-		\caption{Connectivity kernel estimate.
-(a) The actual kernel is shown with the black solid line.
+		\caption{\parham{Connectivity kernel estimate.
+(a) The actual kernel and its components are shown by solid and dashed black lines respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}}
 	\label{fig:KernelEstimate}

### 2011-03-12 Multiresolution_framework/ltx/ResearchHighlights.tex
added research highlights
edit to research highlights

@@
 \begin{itemize}
-	\item We derive a model-based, data-driven estimator of continuum neural field parameters.
-	\item Both macroscopic and microscopic behaviour of the system can be represented simultaneosly.
-	\item We show how to infer intracortical connectivity kernel with an arbitrary shape from data.
+	\item We derive a multi-resolution model-based, data-driven estimator of continuum neural field parameters.
+	\item With the multi-resolution approach both the macroscopic and microscopic dynamics of the system can be represented simultaneously.
+	\item We show for the first time how to infer an arbitrary shaped intracortical connectivity kernel from data.
 \end{itemize}

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex
edit to research highlights

@@
 		\caption{\parham{Connectivity kernel estimate.
-(a) The actual kernel and its components are shown by solid and dashed black lines respectively.
+(a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
@@
 
-In order to apply the framework to real data some assumptions must be made.
-A critical assumption is that the model provides an apt description of the cortical dynamics.
+% In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics. 
 The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex
minor edit
added lopez da silva paper

@@
 disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{Murphy2009}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
 %  due to high computational demands when using a nonlinear (sigmoidal) activation function. }
@@
 		\includegraphics[scale=1]{./Graph/fig2.pdf}
-		\caption{\parham{Connectivity kernel estimate.
+		\caption{Connectivity kernel estimate.
 (a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}}
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}
 	\label{fig:KernelEstimate}

### 2011-03-13 Multiresolution_framework/ltx/manuscript.tex
edits to abstract

@@
 %\boldmath
-We develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
+We develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.

### 2011-03-13 Multiresolution_framework/ltx/manuscript.tex
edits to keywords
minor correction

@@
  \begin{IEEEkeywords}
-  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+  Neural field model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
   \end{IEEEkeywords}
@@
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 

### 2011-11-02 Multiresolution_framework/ltx/manuscript.tex
changed the title
cited Mallat paper

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Multi-Resolution Neural Field Estimation }
+\title{Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
 
@@
 \section{MRA of the IDE in State-Space}
-The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
+The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 Considering a one-dimensional field, the connectivity kernel is decomposed as,

### 2011-11-02 Multiresolution_framework/ltx/manuscript.tex
added hyperlink to the document
added some proofs to the paper

@@
 \floatstyle{ruled}
+%This bit is how to use hyperlink without stupid coloured rectangles around it
+\usepackage{float}
+\usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \newfloat{algorithm}{htbp}{loa}%[chapter]
@@
 where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$.
-% \begin{equation}
-% N_{1}\left(r\right)=
-% \begin{cases}
-% 1 & \text{if $ 0\le r<1$}, \\
-% 0 & \mathrm{elsewhere}.
-% \end{cases}
-% \end{equation}
+\begin{equation}
+N_{1}\left(r\right)=
+\begin{cases}
+1 & \text{if $ 0\le r<1$}, \\
+0 & \mathrm{elsewhere}.
+\end{cases}
+\end{equation}
 Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
-This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
-The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
+
+The $m^{th}$-order B-spline scaling and wavelet functions are respectively defined as \cite{Chui1992}
 \begin{align}
- \varphi & _{m}\left(r\right) = \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}}  q_n N_{m}\left(2r-n\right) \\
- q & _n = \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$},
+ N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
+  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
  \end{align}
-where $q_n$ are the coefficients.
+ where $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients, and
+ \begin{align}
+\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
+\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}.
+ \end{align}
 By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+This can be done by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
+\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
+ &N_m(r)=\nonumber \\
+&\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-k_{n_1,n_2, \dots, n_j}),
+\end{align}
+where 
+\begin{align}
+ k_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
+\end{align}
+The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix ...).
  In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
@@
 Finally, future work should be directed towards applying and validating the framework on real data.
-
+\appendix
+For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
+\begin{align}
+ N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
+  \end{align}
+which clearly holds (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we have
+\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
+ &N_m(r)=\nonumber \\
+&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
+\end{align}
+$N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
+\begin{align}\label{eq:AppendixNj-1intermsofNj}
+ &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
+&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
+&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}})
+\end{align}
+Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
 % \cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
edits to covariance function definition

@@
 %    \documentclass[journal,a4paper]{IEEEtran}
- \documentclass[journal]{IEEEtran}
+%  \documentclass[journal]{IEEEtran}
 
 %      \documentclass[10pt,twocolumn,twoside]{IEEEtran}
-%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
+     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
 %         \topmargin       -6.0mm
@@
 The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
-The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
-The term $e_t(\mathbf r)$ is an i.i.d.
-disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
+The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
+The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covarianve function
+\begin{equation}
+cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t')
+\label{eq:FieldCovariance}
+\end{equation}
+where $\delta(\cdot)$ is the Dirac-delta function.
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
edits to observation noise
added scale and wavelet decomposition

@@
 \begin{equation}
-cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t')
-\label{eq:FieldCovariance}
+cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
+\label{eq:FieldDisturbance}
 \end{equation}
@@
 The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
-%  due to high computational demands when using a nonlinear (sigmoidal) activation function. }
-% \ken{Doing something just for computational efficiency only might be weak ...
-is there other work we can reference that makes the linearity assumption?
-...
-or are there practical situations when this known to be a good approximations?}
+
 The observation equation describing the electrophysiological recordings is given by
@@
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process.
-% $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
+Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
 \section{MRA of the IDE in State-Space}
@@
 \end{equation}
-where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$. %\dean{Need to define these guys as the states here!}
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$.
 
@@
     \label{KernelBasisVector}
-    \boldsymbol\lambda^\top(s)=&\left[
-    \boldsymbol\phi_{j_0}^\top(s) ~
-    \boldsymbol\psi_{j_0}^\top(s) ~ 
-    \boldsymbol\psi_{j_0+1}^\top(s) ~
+    \boldsymbol\lambda^\top(r-r')=&\left[
+    \boldsymbol\phi_{j_0}^\top(r-r') ~
+    \boldsymbol\psi_{j_0}^\top(r-r') ~ 
+    \boldsymbol\psi_{j_0+1}^\top(r-r') ~
     \cdots ~
-    \boldsymbol\psi_{j}^\top(s)\right] \\
+    \boldsymbol\psi_{j}^\top(r-r')\right] \\
     \label{FieldBasisVector}
@@
 
-where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
+The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
@@
 \end{align}
-where $\mathbf I$ is the identity matrix. The disturbance becomes 
+The disturbance becomes 
 \begin{equation}\label{eq:Disturbance}
@@
 B-spline functions were chosen due to their compact support and the ability to analytically define the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
-To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
+To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m$-th  order cardinal B-spline  function is defined by the recurrence relation \cite{Chui1992}
 \begin{equation}
@@
 \end{equation}
-where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$.
+where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, i.e.
 \begin{equation}
@@
 \end{equation}
+then a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \cite{DeBoor2001}
+\begin{equation}\label{eq:MRA-DoBoorFormula}
+ N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
+ \end{equation}
+The most commonly used form of splines is the Cubic spline $\left(m=4\right)$, comprising of third order polynomials added together at the joining points, with an explicit expression given by
+\begin{align}
+N_{4}\left(r\right)=
+\begin{cases}
+r^3 & \text{if $ 0\le r\le1$}, \\
+4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
+-44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
+64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
+0 & \mathrm{elsewhere}.
+\end{cases}
+\end{align}
 Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
@@
 
-The $m^{th}$-order B-spline scaling and wavelet functions are respectively defined as \cite{Chui1992}
+The $m$-th order B-spline scaling and wavelet functions are respectively defined as \cite{Chui1992}
 \begin{align}
@@
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-This can be done by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
+This can be done for scaling functions by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
 \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
@@
 The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix ...).
+A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
+An example of such an expansion is given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
+
+\begin{figure}[!h] 
+ 	\centering
+ 		\includegraphics[scale=1]{./Graph/ScaleDecomposition.pdf}\\
+ 		\includegraphics[scale=1]{./Graph/WaveletDecomposition.pdf}
+ 		\caption{{\bf The scaling and the wavelet function decomposition}.
+The scaling and the wavelet functions (blue) at $j=0$ are respectively obtained using 625 and 1250 scaling functions (black) at $j=4$.}
+ 	\label{fig:MRA-BasisDecomposition}
+ \end{figure}  
  In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
added derivation of the Q function

@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by (\ref{eq:StateEquation}-\ref{eq:Observationmatrix}), the bound used is a quadratic of the form
-\begin{equation}\label{eq:Qfunction}
+For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:MRA-Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
+ \begin{equation}\label{eq:jointdistribution}
+  p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
+ \end{equation}
+ The $\mathcal Q$-function, or lower-bound on the likelihood, can be expressed in terms of the joint distribution components
+ \begin{align}
+  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \nonumber \\
+ &=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
+ +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+ \end{align}
+% where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes the expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ and $\boldsymbol \Theta'$ is the current parameter estimate maximising $p(\mathbf Y;\boldsymbol\theta)$.
+It should be noted that neither $p(\mathbf y_{t+1}|\mathbf x_{t+1})$ nor $p(\mathbf x_0)$ are functions of the parameter set and therefore the $\mathcal Q$-function can be rewritten as
+\begin{equation}
+\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}
+\end{equation}
+where the constant term can be ignored as it is independent of the parameters.
+Under the condition that the state distribution is Gaussian --- ignoring the constant term, $1/(2\pi)^{\frac{n_x}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as
+\begin{align}
+p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)= \mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}} \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
+\end{align}
+Twice the logarithm of the above distribution, once expanded, is given by
+\begin{align}\label{eq:Qfunction}
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
+&-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
+\end{align}
+Substituting $\mathbf A( \boldsymbol\theta)$ from \eqref{eq:A_theta} into \eqref{eq:Qfunction} gives
+\begin{align}
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
+&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t\nonumber \\
+\end{align}
+where 
+\begin{equation}
+\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t
+\end{equation}
+is constant with respect to parameter $\boldsymbol\theta$ and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
+Taking the trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{align}\label{eq:Qfunctionintrace}
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
+&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace\nonumber \\
+&-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace.
+\end{align}
+Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximised for the optimal parameter estimates. Therefore 
+\begin{align}\label{eq:MRA-QintermsofTraces}
+\mathcal Q(\boldsymbol \theta, \boldsymbol\theta')&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \boldsymbol\Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
+&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace,
+\end{align}
+where
+\begin{align}
+\boldsymbol\Xi_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \label{eq:MRA-Xi0}\\
+\boldsymbol\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right] \label{eq:MRA-Xi1}.
+\end{align}
+The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
+\begin{align}\label{eq:MRA-trace1}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i=1}^{n_x}\left[ \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right]_{ii} \nonumber \\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}  \boldsymbol\Lambda_{\theta}\right]_{ji}\nonumber\\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{jk} \left[ \boldsymbol\Lambda_{\theta}\right]_{ki},
+\end{align}
+where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix. Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
+\begin{equation}\label{eq:MRA-LambdaThetaElements}
+\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta,
+\end{equation}
+where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
+each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+\begin{align}
+\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr,
+\end{align}
+where $[\cdot]_{i:} $ denotes the i-th row.
+By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from \eqref{eq:MRA-LambdaThetaElements} the trace given in \eqref{eq:MRA-trace1} can be written as
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}\boldsymbol\theta \nonumber \\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta
+\end{align}
+where
+\begin{align}
+\left[ \Gamma_1\right]^{j,i} =\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}.
+\end{align}
+The second trace of \eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=
+\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_1\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta.
+\end{align}
+Likewise, the third trace of \eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j,k,m=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}[\boldsymbol\Lambda_{\theta}^{\top}]_{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\boldsymbol\Lambda_{\theta}]_{mi} \nonumber \\
+=&\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}~\boldsymbol\theta \nonumber \\
+&=\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\left[ \Gamma_2\right] ^{j,i}\boldsymbol\theta,
+\end{align}
+where
+\begin{align}
+\left[ \Gamma_2\right] ^{j,i}=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
+\end{align}
+Therefore the $\mathcal Q$-function can be rewritten as
+\begin{equation}\label{eq:MRA-QCompact}
 \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
 \end{equation}
-where $\beta$ is constant with respect to $\boldsymbol\theta$.
-Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$, where
-% \begin{align}
-%  \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
-% \end{align}
-% where
-\begin{align}\label{eq:upsilon0}
- \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \\ 
- \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i} \label{eq:upsilon1}\\
- \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_3]^{j,i},\label{eq:Upsilon}
+where
+\begin{equation}\label{eq:epsilon0}
+\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}
+\end{equation}
+and
+\begin{equation}\label{eq:epsilon1}
+\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i}
+\end{equation}
+\begin{equation}\label{eq:Epsilon}
+\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}
+\end{equation}
+All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \cite{Dewar2009}.
+The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \cite{Dewar2009} is also identified.
+\begin {table}
+\begin{center}
+\scalebox{1}{\begin{tabular}{lllc}
+\hline \hline
+Variable &Equation&Order&Order obtained from \cite{Dewar2009}\\ \hline\\
+$\Xi_0, \Xi_1$&\eqref{eq:MRA-Xi0}, \eqref{eq:MRA-Xi1}&$O(Tn_x^2)$& -\\
+$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&\eqref{eq:epsilon0},\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
+$\boldsymbol\Upsilon$&\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\
+$\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&-\\
+$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
+$\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&-\\
+\hline \hline
+\end{tabular}}
+ \caption {{\bf The Computational complexity of the estimation algorithm}. A comparison between the algorithm proposed herein and that of \cite{Dewar2009}.} 
+\label{table:MRA-ComputationalComplexity}
+\end{center}
+\end {table}
+
+By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
+\begin{align}\label{eq:MRA-QDerivative}
+\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
+&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
 \end{align}
-where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
-\begin{align}
- [\boldsymbol\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
- [\boldsymbol\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
-[\boldsymbol\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
+Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
+\begin{align}\label{eq:MRA-thetahat}
+\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
 \end{align}
-Each $1\times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is
-\begin{align}
-\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr,
-\end{align}
-where $[.]_{j:} $ denotes the $j^{th}$ row.
-All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$, and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
-Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
+The second derivative of the $\mathcal Q$-function is given by
 \begin{equation}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta. 
+\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
 \end{equation}
+The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 2), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator.
+Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
 
@@
 The EM algorithm iterates between these two steps until the parameter estimates converge.
+The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
+\begin{algorithm}
+\caption{Summary of the Rauch-Tung-Striebel smoother}
+\label{alg:MRA-RTS}
+ % \begin{tabbing}
+ \begin{enumerate}
+ \item Forward initialisation: 
+ \begin{equation*}
+ \hat{\mathbf x}_0, \mathbf P_0
+ \end{equation*}
+ \item Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix
+ \begin{align}
+ \hat{\mathbf x}_{t+1}^{f-}&=\mathbf A \hat{\mathbf x}_{t}^{f} \nonumber \\
+ \mathbf P_{t+1}^{f-}&=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e \nonumber 
+ \end{align}
+ \item Compute the filter gain, the filtered state and the filtered covariance matrix
+ \begin{align}
+ \mathcal K_{t+1}&=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1} \nonumber\\
+\hat{\mathbf x}_{t+1}^{f}&=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})\nonumber \\
+ \mathbf P_{t+1}^f&=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} \nonumber 
+ \end{align}
+ \item  Backward initialisation:
+ \begin{equation*}
+ \mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
+ \end{equation*}
+ \item Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix
+ \begin{align}
+  \mathbf S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
+ \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathbf S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
+ \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathbf S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathbf S_t^\top \nonumber
+ \end{align}
+ \item compute the smoothed cross covariance matrix\\
+ initialisation:
+ \begin{align}
+  \mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b \nonumber
+ \end{align}
+ Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $
+ \begin{align}
+ \mathbf M_t= \mathbf P_t^{f}\mathbf S_{t-1}^{\top}+\mathbf S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathbf S_{t-1}^{\top}\nonumber
+ \end{align}
+ \end{enumerate}
+ % \end{tabbing}
+ \end{algorithm}
+The stopping rule adopted herein is
+\begin{equation}
+ \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
+ \end{equation}
+ where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by
+ \begin{equation}
+  \parallel \mathbf{A} \parallel_{F}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
+ \end{equation}
 %\cut{The second terms in  \eqref{eq:upsilon0}, \eqref{eq:upsilon1}, and \eqref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:MRA-Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
+For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
  \begin{equation}\label{eq:jointdistribution}
@@
 2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
-&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t\nonumber \\
+&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t,\nonumber \\
 \end{align}
@@
 \begin{equation}
-\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t
+\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,
 \end{equation}
@@
 \end{align}
-The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
+Note that the expectation distributes over the trace sum.
+The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
+To begin, the first trace is written in terms of element-wise summations
 \begin{align}\label{eq:MRA-trace1}
@@
 $\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&-\\
-$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
+$\boldsymbol\Lambda_{\theta}$&\eqref{eq:Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
 $\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&-\\

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
edits to stopping criteria

@@
  \end{equation}
- where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by
+ where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \cite{Meyer2000}
  \begin{equation}
-  \parallel \mathbf{A} \parallel_{F}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
+  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
  \end{equation}

### 2011-11-04 Multiresolution_framework/ltx/manuscript.tex
commit for fist merge

--- 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
@@
 %    \documentclass[journal,a4paper]{IEEEtran}
-%  \documentclass[journal]{IEEEtran}
+ \documentclass[journal]{IEEEtran}
 
 %      \documentclass[10pt,twocolumn,twoside]{IEEEtran}
-     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
+%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
 %         \topmargin       -6.0mm
@@
 \floatstyle{ruled}
-%This bit is how to use hyperlink without stupid coloured rectangles around it
-\usepackage{float}
-\usepackage{hyperref}
-\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \newfloat{algorithm}{htbp}{loa}%[chapter]
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
+\title{Multi-Resolution Neural Field Estimation }
 
@@
 %\boldmath
-We develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
+We develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
@@
  \begin{IEEEkeywords}
-  Neural field model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
   \end{IEEEkeywords}
@@
 The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
-The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
-The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covarianve function
-\begin{equation}
-cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
-\label{eq:FieldDisturbance}
-\end{equation}
-where $\delta(\cdot)$ is the Dirac-delta function.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
-
+The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}.
+The term $e_t(\mathbf r)$ is an i.i.d.
+disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$: a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{Murphy2009}.
+%  due to high computational demands when using a nonlinear (sigmoidal) activation function. }
+% \ken{Doing something just for computational efficiency only might be weak ...
+is there other work we can reference that makes the linearity assumption?
+...
+or are there practical situations when this known to be a good approximations?}
 The observation equation describing the electrophysiological recordings is given by
@@
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+Gaussian white noise process.
+% $\mathbf{y}_{t} = [y_t(\mathbf{r}_1) y_t(\mathbf{r}_2) \cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations at time $t$ via the observation kernel , is corrupted by The superscript $\top$ denotes the transpose operator.
 \section{MRA of the IDE in State-Space}
-The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
+The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 Considering a one-dimensional field, the connectivity kernel is decomposed as,
@@
 \end{equation}
-where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$.
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$. %\dean{Need to define these guys as the states here!}
 
@@
     \label{KernelBasisVector}
-    \boldsymbol\lambda^\top(r-r')=&\left[
-    \boldsymbol\phi_{j_0}^\top(r-r') ~
-    \boldsymbol\psi_{j_0}^\top(r-r') ~ 
-    \boldsymbol\psi_{j_0+1}^\top(r-r') ~
+    \boldsymbol\lambda^\top(s)=&\left[
+    \boldsymbol\phi_{j_0}^\top(s) ~
+    \boldsymbol\psi_{j_0}^\top(s) ~ 
+    \boldsymbol\psi_{j_0+1}^\top(s) ~
     \cdots ~
-    \boldsymbol\psi_{j}^\top(r-r')\right] \\
+    \boldsymbol\psi_{j}^\top(s)\right] \\
     \label{FieldBasisVector}
@@
 
-The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
+where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
 
@@
 \end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
+Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
 \begin{align}\label{eq:DecomposedModel2} 
@@
 \end{align}
-The disturbance becomes 
+where $\mathbf I$ is the identity matrix. The disturbance becomes 
 \begin{equation}\label{eq:Disturbance}
@@
 B-spline functions were chosen due to their compact support and the ability to analytically define the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
-To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m$-th  order cardinal B-spline  function is defined by the recurrence relation \cite{Chui1992}
+To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m^{th}$ order cardinal B-spline scaling function is defined by the recurrence relation \cite{Chui1992}
 \begin{equation}
@@
 \end{equation}
-where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, i.e.
-\begin{equation}
-N_{1}\left(r\right)=
-\begin{cases}
-1 & \text{if $ 0\le r<1$}, \\
-0 & \mathrm{elsewhere}.
-\end{cases}
-\end{equation}
-then a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \cite{DeBoor2001}
-\begin{equation}\label{eq:MRA-DoBoorFormula}
- N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
- \end{equation}
-The most commonly used form of splines is the Cubic spline $\left(m=4\right)$, comprising of third order polynomials added together at the joining points, with an explicit expression given by
-\begin{align}
-N_{4}\left(r\right)=
-\begin{cases}
-r^3 & \text{if $ 0\le r\le1$}, \\
-4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
--44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
-64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
-0 & \mathrm{elsewhere}.
-\end{cases}
-\end{align}
+where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$.
+% \begin{equation}
+% N_{1}\left(r\right)=
+% \begin{cases}
+% 1 & \text{if $ 0\le r<1$}, \\
+% 0 & \mathrm{elsewhere}.
+% \end{cases}
+% \end{equation}
 Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
-
-The $m$-th order B-spline scaling and wavelet functions are respectively defined as \cite{Chui1992}
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
+The $m^{th}$-order B-spline wavelet is defined as \cite{Chui1992}
 \begin{align}
- N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
-  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
+ \varphi & _{m}\left(r\right) = \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}}  q_n N_{m}\left(2r-n\right) \\
+ q & _n = \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$},
 \end{align}
- where $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients, and
- \begin{align}
-\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
-\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}.
- \end{align}
+where $q_n$ are the coefficients.
 By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
 In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-This can be done for scaling functions by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
-\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
- &N_m(r)=\nonumber \\
-&\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-k_{n_1,n_2, \dots, n_j}),
-\end{align}
-where 
-\begin{align}
- k_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
-\end{align}
-The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix ...).
-A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
-An example of such an expansion is given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
-
-\begin{figure}[!h] 
- 	\centering
- 		\includegraphics[scale=1]{./Graph/ScaleDecomposition.pdf}\\
- 		\includegraphics[scale=1]{./Graph/WaveletDecomposition.pdf}
- 		\caption{{\bf The scaling and the wavelet function decomposition}.
-The scaling and the wavelet functions (blue) at $j=0$ are respectively obtained using 625 and 1250 scaling functions (black) at $j=4$.}
- 	\label{fig:MRA-BasisDecomposition}
- \end{figure}  
 In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
@@
 EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:MRA-Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
- \begin{equation}\label{eq:jointdistribution}
-  p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
- \end{equation}
- The $\mathcal Q$-function, or lower-bound on the likelihood, can be expressed in terms of the joint distribution components
- \begin{align}
-  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \nonumber \\
- &=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
- +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
- \end{align}
-% where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes the expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ and $\boldsymbol \Theta'$ is the current parameter estimate maximising $p(\mathbf Y;\boldsymbol\theta)$.
-It should be noted that neither $p(\mathbf y_{t+1}|\mathbf x_{t+1})$ nor $p(\mathbf x_0)$ are functions of the parameter set and therefore the $\mathcal Q$-function can be rewritten as
-\begin{equation}
-\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}
-\end{equation}
-where the constant term can be ignored as it is independent of the parameters.
-Under the condition that the state distribution is Gaussian --- ignoring the constant term, $1/(2\pi)^{\frac{n_x}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as
-\begin{align}
-p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)= \mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}} \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
-\end{align}
-Twice the logarithm of the above distribution, once expanded, is given by
-\begin{align}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
-&-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
-\end{align}
-Substituting $\mathbf A( \boldsymbol\theta)$ from \eqref{eq:A_theta} into \eqref{eq:Qfunction} gives
-\begin{align}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
-&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t\nonumber \\
-\end{align}
-where 
-\begin{equation}
-\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t
-\end{equation}
-is constant with respect to parameter $\boldsymbol\theta$ and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
-Taking the trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
-\begin{align}\label{eq:Qfunctionintrace}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
-&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace\nonumber \\
-&-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace.
-\end{align}
-Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximised for the optimal parameter estimates. Therefore 
-\begin{align}\label{eq:MRA-QintermsofTraces}
-\mathcal Q(\boldsymbol \theta, \boldsymbol\theta')&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \boldsymbol\Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
-&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace,
-\end{align}
-where
-\begin{align}
-\boldsymbol\Xi_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \label{eq:MRA-Xi0}\\
-\boldsymbol\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right] \label{eq:MRA-Xi1}.
-\end{align}
-The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
-\begin{align}\label{eq:MRA-trace1}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i=1}^{n_x}\left[ \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right]_{ii} \nonumber \\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}  \boldsymbol\Lambda_{\theta}\right]_{ji}\nonumber\\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{jk} \left[ \boldsymbol\Lambda_{\theta}\right]_{ki},
-\end{align}
-where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix. Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
-\begin{equation}\label{eq:MRA-LambdaThetaElements}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta,
-\end{equation}
-where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
-each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}
-\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr,
-\end{align}
-where $[\cdot]_{i:} $ denotes the i-th row.
-By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from \eqref{eq:MRA-LambdaThetaElements} the trace given in \eqref{eq:MRA-trace1} can be written as
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}\boldsymbol\theta \nonumber \\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta
-\end{align}
-where
-\begin{align}
-\left[ \Gamma_1\right]^{j,i} =\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}.
-\end{align}
-The second trace of \eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=
-\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_1\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta.
-\end{align}
-Likewise, the third trace of \eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j,k,m=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}[\boldsymbol\Lambda_{\theta}^{\top}]_{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\boldsymbol\Lambda_{\theta}]_{mi} \nonumber \\
-=&\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}~\boldsymbol\theta \nonumber \\
-&=\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\left[ \Gamma_2\right] ^{j,i}\boldsymbol\theta,
-\end{align}
-where
-\begin{align}
-\left[ \Gamma_2\right] ^{j,i}=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
-\end{align}
-Therefore the $\mathcal Q$-function can be rewritten as
-\begin{equation}\label{eq:MRA-QCompact}
+For the linear state-space model given by (\ref{eq:StateEquation}-\ref{eq:Observationmatrix}), the bound used is a quadratic of the form
+\begin{equation}\label{eq:Qfunction}
  \mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
 \end{equation}
-where
-\begin{equation}\label{eq:epsilon0}
-\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}
+where $\beta$ is constant with respect to $\boldsymbol\theta$.
+Equation \eqref{eq:Qfunction} is maximum at $\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top)$, where
+% \begin{align}
+%  \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0^\top-\boldsymbol\upsilon_1^\top),
+% \end{align}
+% where
+\begin{align}\label{eq:upsilon0}
+ \boldsymbol\upsilon_0 & =\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \\ 
+ \boldsymbol\upsilon_1 & =\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i} \label{eq:upsilon1}\\
+ \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_3]^{j,i},\label{eq:Upsilon}
+\end{align}
+where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
+\begin{align}
+ [\boldsymbol\Gamma_1]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma1} \\ 
+ [\boldsymbol\Gamma_2]^{j,i} & =\sum_{k=1}^{n_x}[\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{j,k}[\mathbf U]^{k,i}\label{eq:Gamma2} \\
+[\boldsymbol\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.
+\end{align}
+Each $1\times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is
+\begin{align}
+\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr,
+\end{align}
+where $[.]_{j:} $ denotes the $j^{th}$ row.
+All $n_x^2$ blocks of $\boldsymbol\Gamma_1$,$\boldsymbol\Gamma_2$, and $\boldsymbol\Gamma_3$  can be computed before the commencement of the EM iterations.
+Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
+\begin{equation}
+\left[ \boldsymbol\Lambda_{\theta}\right] _{i,j} =\left[ \mathbf U\right]^{i,j}\boldsymbol\theta. 
 \end{equation}
-and
-\begin{equation}\label{eq:epsilon1}
-\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i}
-\end{equation}
-\begin{equation}\label{eq:Epsilon}
-\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}
-\end{equation}
-All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \cite{Dewar2009}.
-The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \cite{Dewar2009} is also identified.
-\begin {table}
-\begin{center}
-\scalebox{1}{\begin{tabular}{lllc}
-\hline \hline
-Variable &Equation&Order&Order obtained from \cite{Dewar2009}\\ \hline\\
-$\Xi_0, \Xi_1$&\eqref{eq:MRA-Xi0}, \eqref{eq:MRA-Xi1}&$O(Tn_x^2)$& -\\
-$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&\eqref{eq:epsilon0},\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
-$\boldsymbol\Upsilon$&\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\
-$\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&-\\
-$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
-$\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&-\\
-\hline \hline
-\end{tabular}}
- \caption {{\bf The Computational complexity of the estimation algorithm}. A comparison between the algorithm proposed herein and that of \cite{Dewar2009}.} 
-\label{table:MRA-ComputationalComplexity}
-\end{center}
-\end {table}
-
-By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
-\begin{align}\label{eq:MRA-QDerivative}
-\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
-&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
-\end{align}
-Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
-\begin{align}\label{eq:MRA-thetahat}
-\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
-\end{align}
-The second derivative of the $\mathcal Q$-function is given by
-\begin{equation}
-\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
-\end{equation}
-The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 2), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator.
-Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
 
@@
 The EM algorithm iterates between these two steps until the parameter estimates converge.
-The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
-\begin{algorithm}
-\caption{Summary of the Rauch-Tung-Striebel smoother}
-\label{alg:MRA-RTS}
- % \begin{tabbing}
- \begin{enumerate}
- \item Forward initialisation: 
- \begin{equation*}
- \hat{\mathbf x}_0, \mathbf P_0
- \end{equation*}
- \item Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix
- \begin{align}
- \hat{\mathbf x}_{t+1}^{f-}&=\mathbf A \hat{\mathbf x}_{t}^{f} \nonumber \\
- \mathbf P_{t+1}^{f-}&=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e \nonumber 
- \end{align}
- \item Compute the filter gain, the filtered state and the filtered covariance matrix
- \begin{align}
- \mathcal K_{t+1}&=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1} \nonumber\\
-\hat{\mathbf x}_{t+1}^{f}&=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})\nonumber \\
- \mathbf P_{t+1}^f&=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} \nonumber 
- \end{align}
- \item  Backward initialisation:
- \begin{equation*}
- \mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
- \end{equation*}
- \item Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix
- \begin{align}
-  \mathbf S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
- \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathbf S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
- \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathbf S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathbf S_t^\top \nonumber
- \end{align}
- \item compute the smoothed cross covariance matrix\\
- initialisation:
- \begin{align}
-  \mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b \nonumber
- \end{align}
- Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $
- \begin{align}
- \mathbf M_t= \mathbf P_t^{f}\mathbf S_{t-1}^{\top}+\mathbf S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathbf S_{t-1}^{\top}\nonumber
- \end{align}
- \end{enumerate}
- % \end{tabbing}
- \end{algorithm}
-The stopping rule adopted herein is
-\begin{equation}
- \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
- \end{equation}
- where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by
- \begin{equation}
-  \parallel \mathbf{A} \parallel_{F}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
- \end{equation}
 %\cut{The second terms in  \eqref{eq:upsilon0}, \eqref{eq:upsilon1}, and \eqref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
@@
 		\includegraphics[scale=1]{./Graph/fig2.pdf}
-		\caption{Connectivity kernel estimate.
+		\caption{\parham{Connectivity kernel estimate.
 (a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}}
 	\label{fig:KernelEstimate}
@@
 
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005}.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\cite{Wikle2002,Xu2005}.
 % \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
@@
 Finally, future work should be directed towards applying and validating the framework on real data.
-\appendix
-For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
-\begin{align}
- N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
-  \end{align}
-which clearly holds (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we have
-\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
- &N_m(r)=\nonumber \\
-&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
-\end{align}
-$N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
-\begin{align}\label{eq:AppendixNj-1intermsofNj}
- &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
-&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
-&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}})
-\end{align}
-Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
+
 % \cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.

### 2011-11-07 Multiresolution_framework/ltx/manuscript.tex
added more theory and discussion

--- 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
@@
 
-The observation equation describing the electrophysiological recordings is given by
+The observation equation describing the intracranial electrophysiological recordings is given by
 \begin{equation}\label{eq:ObservationEquation}
@@
 \section{MRA of the IDE in State-Space}
-The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
+The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
 Considering a one-dimensional field, the connectivity kernel is decomposed as,
@@
 \label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I,
+ \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
 \end{align}
@@
 which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
-\begin{equation}
+\begin{equation}\label{eq:CovMatrix}
 \boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
@@
 \end{equation}
+\section{B-spline MRAIDE in State-Space }
+B-spline functions are one of the most basic elements for wavelet construction, these functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines.
+The degree of smoothness is determined by the order of splines \cite{Goswami1999} where the higher the order, the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
+\begin{figure}[!ht]
+\centering
+\includegraphics{./Graph/Figure0a.pdf}
+\includegraphics{./Graph/Figure0b.pdf}
+\caption{{\bf Examples of cardinal B-spline functions}.
+Piecewise polynomial functions (coloured lines) are joined at the break points (black dots).
+(\textbf{a}) B-spline function of order 2 (linear B-spline).
+(\textbf{b}) B-spline function of order 8.}
+\label{fig:Figure0}
+\end{figure}
 
-The MRAIDE can be implemented using various scaling and wavelet functions.
-B-spline functions were chosen due to their compact support and the ability to analytically define the convolution and inner product to form $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$.
-To show how $\boldsymbol\Lambda_x$ and $\boldsymbol \Lambda_{\theta}$ are formed, the $m$-th  order cardinal B-spline  function is defined by the recurrence relation \cite{Chui1992}
+B-spline wavelet and scaling functions are formulated independently by Chui and Wang, and Unser et al \cite{Chui1992b,Chui1992,Unser1993}.
+The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
+B-spline wavelet and scaling functions approach optimal time/frequency localisation as the order of the spline increases.
+In fact for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions \cite{Unser1992}.
+B-spline wavelets have a better approximation rate as other wavelets with the same number of vanishing moments \cite{Unser1999}.
+B-spline wavelet and scaling functions are particularly suitable in this work due to their ability to analytically define the convolution and inner product to form  MRAIDE components.
+The following summarises some important characteristics of B-splines relevant to the proposed modelling framework.
+
+The $m$-th  order cardinal B-spline function is defined by the recurrence relation \cite{Chui1992} 
 \begin{equation}
@@
 \end{equation}
-where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, i.e.
+where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, also known as indicator function, i.e.
 \begin{equation}
@@
 \end{align}
-Equation \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself since
-\begin{equation}
+The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_x$, $\boldsymbol\Lambda_{\theta}$ and $\boldsymbol\Sigma_w$).
+To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
+\begin{equation}\label{eq:N1convolutions}
  N_{m}\left(r\right)=\underbrace{\left(N_{1}\ast N_{1}\ast \cdots \ast N_{1}\right)}_{m-1\quad \text{convolutions}}\left(r\right).
@@
 \end{align}
-where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product. This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$.
+where $\left\langle \cdot,\cdot\right\rangle $ denotes the inner product.
+This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
+$ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see Appendix~\ref{ap:InnerProductOfBsplines} for explicit derivation).
+The values of $N_{m+m'}$ in \eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating \eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
+ \begin{equation}\label{eq:MRA-recursiveBsplineatintegerpoints}
+ \begin{cases}
+ N_2(k)=\delta(k-1)\quad k\in \mathbb{Z}, \\
+ N_{m}\left(k\right)=\frac{k}{m-1}N_{m-1}\left(k\right)+\frac{m-k}{m-1}N_{m-1}\left(k-1\right) \quad k=1,2,\dots,m-1
+  \end{cases}
+ \end{equation}
+Note $N_{m}\left(k\right)=0$ for $k\le0$ or $k\ge m$.
 
-The $m$-th order B-spline scaling and wavelet functions are respectively defined as \cite{Chui1992}
+To determine the level of approximation in the model, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
+To proceed the Fourier transform of $N_1(r)$ is first calculated,
+\begin{align}\label{eq:MRA-N1Fouriertransform}
+\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}.
+\end{align}
+The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
+Therefore, taking Fourier transform of \eqref{eq:N1convolutions} and substituting \eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
+\begin{align}\label{eq:MRA-NmFouriertransform}
+\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^m.
+\end{align}
+The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair which for cardinal B-spline scaling and wavelet functions of order $m$, takes the form of \cite{Chui1992}
 \begin{align}
@@
  \end{align}
-By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta} can be computed analytically.
-In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
-This can be done for scaling functions by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
+ Figure~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero. 
+\begin{figure}[!ht]
+\centering
+\includegraphics{./Graph/Figure1a.pdf}
+\includegraphics{./Graph/Figure1b.pdf}
+\caption{{\bf Examples of B-spline  scaling and wavelet functions}. (\textbf{a}) The cubic B-spline scaling function. (\textbf{b}) The corresponding wavelet function.}
+\label{fig:MRA-Figure1}
+\end{figure}
+
+By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} can be computed analytically.
+In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}:
+\begin{equation}
+  \left\langle \varphi_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
+ \label{eq:MRA-PsiPsiOrthogonality} 
+ \end{equation}
+ \begin{equation}
+  \left\langle N_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
+ \label{eq:MRA-PhiPsiOrthogonality}
+ \end{equation}
+
+In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+For scaling functions this can be done  by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
 \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
  &N_m(r)=\nonumber \\
-&\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-k_{n_1,n_2, \dots, n_j}),
+&\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-l_{n_1,n_2, \dots, n_j}),
 \end{align}
@@
 \begin{align}
- k_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
+ l_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
 \end{align}
@@
 A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
-An example of such an expansion is given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
-
+Examples of such expansions are given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
 \begin{figure}[!h] 
@@
  \end{figure}  
- In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used.
-Therefore, the $8^{th}$ and $12^{th}$ order B-spline values at integer points are required (see \cite{Goswami1999}) to compute the integrals in \eqref{eq:Lambdax} and \eqref{eq:Lambdatheta}.
+ In this paper, 4th order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+\begin {table}[h]
+\begin{center}
+\begin{tabular}{lcccc}
+ & $k$& $7!N_{8}\left(k\right)$ & $11!N_{12}\left(k\right)$\\ \hline\hline
+ & 1  & $1$ & $1$\\
+ & 2  & $120$ & $2,036$\\
+ & 3  & $1,191$ & $152,637$\\
+ & 4  & $2,416$ & $2,203,488$\\
+ & 5  & $\space$ & $9,738,114$\\
+ & 6  & $\space$ & $15,724,248$
+ \end{tabular}
+ \caption {{\bf Cardinal B-Splines at the knot sequence}. Table entries are calculated using \eqref{eq:MRA-recursiveBsplineatintegerpoints} and can be also found in \cite{Goswami1999}.} 
+ \label{table:MRA-BsplineatIntegerPoints}
+ \end{center}
+ \end {table} 
 \section{State and Parameter Estimation}
@@
 where the constant term can be ignored as it is independent of the parameters.
-Under the condition that the state distribution is Gaussian --- ignoring the constant term, $1/(2\pi)^{\frac{n_x}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as
+Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as
 \begin{align}
-p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)= \mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}} \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
+p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
 \end{align}
@@
 \begin{align}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
 &-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
@@
 \begin{equation}
-\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,
+\beta=-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,
 \end{equation}
@@
 
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t-1},\mathbf{x}_{t})$ \cite{Gibsona2005},
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$ \cite{Gibsona2005},
 \begin{align}\label{eq:Xivariables}
@@
 
-\section{Results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters.
-200 realizations of 1~s of data were generated, where the estimation was applied to the final 900~ms, allowing the model's initial transients to die out.
-The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$).
-The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively.
-The firing rate slop, $\varsigma$ was set to $0.56~mV^{-1}$.
-The distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
-The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude.
-The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.
-%\ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table}
-The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
+\section{Results}\label{sec:MRA-results}
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
+In doing so, the synaptic time constant was set to $\tau = 10$~ms \cite{David2003}, and the sampling time was chosen ten times faster \cite{Stephan2008}, i.e.
+$T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
+
+Two different experiments were designed where in the first one, 200 runs of one second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realisation.
+In the second experiment, a single data set was generated and the field estimations are compared for five models, each accounting for a different level of approximation, i.e.
+$j=0$ to $j=4$.
+
+For each of the experiment, the estimation was applied to the final 900~ms, allowing the model's dynamics to stabilise from the initial conditions.
+The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
+The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\gamma(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
+The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \cite{Wendling2005}.
+The observation kernel was modelled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
+The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.
+With this number of observations, the estimation problem was well-posed, i.e.
+the number of states, $n_x < n_y$ at each level of the decomposition.
+This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see (\ref{eq:MRA-PsiPsiOrthogonality}-\ref{eq:MRA-PhiPsiOrthogonality})).
+\subsection{Experiment I}
+The spatial frequency response of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
+This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
+The wavelets at each spatial scale was expanded in terms of the scaling function at the next scale using \eqref{eq:MRA-TwoScalepair2} and the resulting expansion was then used to analytically calculate the spatial bandwidth  via \eqref{eq:MRA-NmFouriertransform}.
+The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
+\begin{figure}[!h] 
+ 	\centering
+ 		\includegraphics[scale=1]{./Graph/Figure2.pdf}
+ 		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}
+ 	\label{fig:ObservationFrequencyResponce}
+ \end{figure}
+
+The EM algorithm was allowed to run until the maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
+The rate of convergence of the EM based algorithm is depicted in Figure~\ref{fig:MRA-Convergence}.
+\begin{figure}[!h] 
+ 	\centering
+ 		\includegraphics[scale=1]{./Graph/ConvergenceRate.pdf}
+ 		\caption{{\bf Convergence of the EM algorithm}. Representative plot of
+the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.}
+ 	\label{fig:MRA-Convergence}
+ \end{figure}     
+% The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
 Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
@@
 
-% \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}  
-% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
-
-The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.
-The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.78.
-Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
-
-The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a).
+The actual connectivity kernel and the decomposition is plotted in Figure~\ref{fig:KernelEstimate}(a).
 No assumptions where made about the shape of the kernel.
@@
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
-\figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
+Figure~\ref{fig:KernelEstimate}(b) and (c) illustrate the kernel scaling and wavelet functions, respectively.
+A total number of 25 basis functions was used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$ accordingly.
+\begin{figure}[!ht]
+\includegraphics{./Graph/Figure5.pdf}
+\includegraphics{./Graph/Figure6.pdf}
+\caption{ {\bf Connectivity kernel estimate}.
+(\textbf{a}) The actual kernel and its components are shown by solid and dashed black lines, respectively.
+The mean kernel estimates over 200 realisations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
+(\textbf{b}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
+\label{fig:KernelEstimate}
+\end{figure}
+
+% \begin{figure}[!h] 
+% 	\centering
+% 		\includegraphics[scale=1]{./Graph/fig2.pdf}
+% 		\caption{Connectivity kernel estimate.
+(a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
+The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
+(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}
+% 	\label{fig:KernelEstimate}
+% \end{figure}
+ One snap shot of the field reconstruction, at different levels of approximation is given in Figures~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
+From this figure, it can be observed that the overall trend of the underlying field can be also captured at the coarser levels.
+\begin{figure}[!ht]
+\centering
+\includegraphics{./Graph/Figure4a.pdf}\\
+\includegraphics{./Graph/Figure4b.pdf}\\
+\includegraphics{./Graph/Figure4c.pdf}\\
+\includegraphics{./Graph/Figure4d.pdf}\\
+\caption{ {\bf Examples of the actual and estimated neural fields for experiment I}.
+Actual (grey) and estimated (black) neural fields at a single time instant for different spatial resolutions.
+(\textbf{a}) $j=0$, $n_x=17$.
+(\textbf{b}) $j=1$, $n_x=33$.
+(\textbf{c}) $j=2$, $n_x=65$.
+(\textbf{d}) $j=3$, $n_x=131$.}
+% (\textbf{e}) $j=4$, $n_x=263$.
+\label{fig:FieldEstimates100}
+\end{figure}
+\subsection{Experiment II}
+To study the performance of different models with various MRA capabilities, a single realisation was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
+The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
+The RMSE of the field estimation at different levels of approximation is shown in Figure~\ref{fig:RMSE}.
+By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.78, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field.
+The estimated field at a single time instant is shown in Figure~\ref{fig:FieldEstimates200}.
+The experiment was performed several times and the results were consistent over each run.
  \begin{figure}[!h] 
  	\centering
-		\includegraphics[scale=1]{./Graph/fig1.pdf}
-		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions.
+ 		\includegraphics[scale=1]{./Graph/Figure3.pdf}
+ 		\caption{{\bf Error in the field reconstruction for experiment II}.
+RMSE of the estimated field of models with different level of approximations.
+$j=0$, $RMSE = 1.93$; $j=1$, $RMSE = 1.39$; $j=2$, $RMSE = 0.90$; $j=3$, $RMSE = 0.78$; $j=4$, $RMSE=0.78$}
+ 	\label{fig:RMSE}
+ \end{figure} 
+\begin{figure}[!ht]
+\centering
+\includegraphics{./Graph/Figure5a.pdf}\\
+\includegraphics{./Graph/Figure5b.pdf}\\
+\includegraphics{./Graph/Figure5c.pdf}\\
+\includegraphics{./Graph/Figure5d.pdf}\\
+\includegraphics{./Graph/Figure5e.pdf}\\
+\caption{ {\bf Examples of the actual and estimated neural fields for experiment II}.
+Actual (grey) and estimated (black) neural fields at a single time instant  for models with different spatial resolutions.
+(\textbf{a}) $j=0$, $n_x=17$.
+(\textbf{b}) $j=1$, $n_x=33$.
+(\textbf{c}) $j=2$, $n_x=65$.
+(\textbf{d}) $j=3$, $n_x=131$.
+(\textbf{e}) $j=4$, $n_x=263$.}
+\label{fig:FieldEstimates200}
+\end{figure}
+% The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.
+The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.78.
+Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
+% \begin{figure}[!h] 
+% 	\centering
+% 		\includegraphics[scale=1]{./Graph/fig1.pdf}
+% 		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions.
 (a) $j=0$, $n_x=17$, $RMSE = 1.93$.
@@
 (e) $j=4$, $n_x=263$, $RMSE=0.78$.}
-	\label{fig:FieldEstimates}
-\end{figure} 
-\begin{figure}[!h] 
-	\centering
-		\includegraphics[scale=1]{./Graph/fig2.pdf}
-		\caption{Connectivity kernel estimate.
-(a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
-The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}
-	\label{fig:KernelEstimate}
-\end{figure}
+% 	\label{fig:FieldEstimates}
+% \end{figure}
+
 % \caption{The actual connectivity kernel is shown with the black solid line.
@@
 It would be nice to slot something in here because he used wavelets.}
+
+For a larger space or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
+One solution to this problem could be expectation-conditional maximisation (ECM) \cite{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
+The ECM is a class of generalised EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximised \cite{Fessler1994}.
+
+For systems with a high number of states, the ensemble Kalman smoother (EnKS) \cite{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
+The EnKS is a sequential Monte Carlo (MC) method where the state covariance matrix is approximated by a large stochastic ensemble of model states, thus alleviating computational load due to the storage and forward integration of the state covariance matrix.
+However, combining the EnKS with the EM algorithm suffers from the loss of monotonicity property --- increase in the likelihood function--- as MC error will be introduced at the E-step.
+
+Typically, a sequence of likelihood values will converge to a stationary point i.e.
+global (local) maximum or a saddle point.
+If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \cite{McLachlan1997}.
+In general, convergence of the EM algorithm to any stationary point depends on the initialisation.
+In the examples presented in this chapter, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
 
@@
 % In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.
+An assumption was made where the firing rate behaves linearly.
+The implementation of the framework in the non-linear case can be addressed as future work.
+Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.
+The reconstruction of the neural field requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
+For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \cite{Meyer1992}.
+In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations.
+Although provided formulations can be easily extended into two dimensions the  computational load of the estimation algorithm will be significant.
+It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
+
 The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
@@
 Finally, future work should be directed towards applying and validating the framework on real data.
-\appendix
+\section{Appendix}
+\subsection{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
+In this section, an analytic formula is derived for the inner product of two B-spline scaling functions.
+Consider two B-spline scaling functions of order $m$ and $m'$.
+The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
+\begin{align}\label{eq:APP-SymmetrySplieEq}
+ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
+\end{align}
+A direct consequence of \eqref{eq:APP-SymmetrySplieEq} is 
+\begin{align}
+ N_{m}\left(r\right)=N_{m}\left(m-r\right).
+\end{align}
+Therefore
+\begin{align}
+\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)ds&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
+&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
+&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
+&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
+&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
+\end{align}
+\subsection{Induction}\label{ap:Induction}
 For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
@@
 which clearly holds (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we have
-\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
+\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
  &N_m(r)=\nonumber \\

### 2011-11-08 Multiresolution_framework/ltx/manuscript.tex
for merge
added a section on multires neural fields

@@
 These models typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
+For example..
+integrate and fire...
+The utility in these models to answer questions in neuroscience lies in the ability to infer parameters from data.
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
@@
 Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
-The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
+This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously \dean{and completely}.
+
+\section{Multi-Resolution Cortical Architecture}
+The human neocortex has an inherent multi-resolution architecture. On finer scales... where any measurable spatiotemporal neural field can be written as 
+\begin{equation}
+	v\left(\mathbf{r},t\right) = \sum_{j} v_j\left(\mathbf{r},t\right),
+\end{equation}
+where $v$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye for example, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location with the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
+
+This multi-resolution structure has been described by numerous methods (Wilson and Cowan).
+This idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths.
+
+Typically, the experimentalist only has access the net field generated by the multi-resolution architecture.
+Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
+The solution to this problem was proposed by \dean{Breakspear and Stam} in using a wavelet decomposition.
+\begin{figure}[t]
+	\centering
+		\includegraphics[scale=0.65]{./Graph/MultiresNeuralField.pdf}
+	\caption{Multi-layer neural field model.}
+	\label{fig:MultiLayerFieldModel}
+\end{figure}
 
@@
 
-Equations \eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
+Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
 \begin{align}

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
added Multilayer neural field model
added Multilayer caption
added field estimation over all time

@@
 	\centering
-		\includegraphics[scale=0.65]{./Graph/MultiresNeuralField.pdf}
-	\caption{Multi-layer neural field model.}
+		\includegraphics[scale=1]{./Graph/MultiResNeuralField.pdf}
+	\caption{{\bf Multi-layer neural field model}. The inset figures show the shape of the
+connectivity kernel components at each spatial resolution.}
 	\label{fig:MultiLayerFieldModel}
@@
 \begin{align}\label{eq:MRA-QDerivative}
-\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
-&=2T_s\varsigma(\boldsymbol\nu_0-\boldsymbol\nu_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
+\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
+&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
 \end{align}
@@
 \label{fig:FieldEstimates100}
+\end{figure}
+\begin{figure}[t]
+	\centering
+		\includegraphics[scale=1]{./Graph/STMultiRes.png}
+	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}.
+(\textbf{A}) The reconstructed field of the reduced model using only scaling functions at $j=0$.
+(\textbf{B}) The reconstructed field using scaling and wavelet functions at $j=0$.
+(\textbf{C}) The reconstructed field using scaling and wavelet functions at $j=1$.
+(\textbf{D}) The reconstructed field using scaling and wavelet functions at $j=2$.
+(\textbf{E}) The reconstructed field using scaling and wavelet functions at $j=3$.
+(\textbf{F}) The actual field.}
+	\label{fig:FieldEstimation}
 \end{figure}

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
added field estimation over all time

@@
 	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}.
-(\textbf{A}) The reconstructed field of the reduced model using only scaling functions at $j=0$.
-(\textbf{B}) The reconstructed field using scaling and wavelet functions at $j=0$.
-(\textbf{C}) The reconstructed field using scaling and wavelet functions at $j=1$.
-(\textbf{D}) The reconstructed field using scaling and wavelet functions at $j=2$.
-(\textbf{E}) The reconstructed field using scaling and wavelet functions at $j=3$.
+(\textbf{A}) The reconstructed field of the reduced model using at $j=0$.
+(\textbf{B}) The reconstructed field at $j=1$.
+(\textbf{C}) The reconstructed field at $j=2$.
+(\textbf{D}) The reconstructed field at $j=3$.
+(\textbf{E}) The reconstructed at $j=4$.
 (\textbf{F}) The actual field.}

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
minor correction

@@
 \end{equation}
-The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 2), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator.
+The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator.
 Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
@@
 This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
-The wavelets at each spatial scale was expanded in terms of the scaling function at the next scale using \eqref{eq:MRA-TwoScalepair2} and the resulting expansion was then used to analytically calculate the spatial bandwidth  via \eqref{eq:MRA-NmFouriertransform}.
+The spatial bandwidths of wavelets was calculated analytically using \eqref{eq:MRA-NmFouriertransform}.
 The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions respectively at $j=0$, $j=1$, $j=2$ and $j=3$.

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
changed RMSE plot to MRMSE

@@
 The RMSE of the field estimation at different levels of approximation is shown in Figure~\ref{fig:RMSE}.
-By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.78, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field.
+By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field.
 The estimated field at a single time instant is shown in Figure~\ref{fig:FieldEstimates200}.
@@
  		\caption{{\bf Error in the field reconstruction for experiment II}.
-RMSE of the estimated field of models with different level of approximations.
-$j=0$, $RMSE = 1.93$; $j=1$, $RMSE = 1.39$; $j=2$, $RMSE = 0.90$; $j=3$, $RMSE = 0.78$; $j=4$, $RMSE=0.78$}
+MRMSE of the estimated field of models with different level of approximations.
+$j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
  	\label{fig:RMSE}

### 2011-11-18 Multiresolution_framework/ltx/manuscript.tex
added subplots

@@
 \centering
-\includegraphics{./Graph/Figure0a.pdf}
-\includegraphics{./Graph/Figure0b.pdf}
+\includegraphics{./Graph/Figure0.pdf}
+% \includegraphics{./Graph/Figure0b.pdf}
 \caption{{\bf Examples of cardinal B-spline functions}.
 Piecewise polynomial functions (coloured lines) are joined at the break points (black dots).
-(\textbf{a}) B-spline function of order 2 (linear B-spline).
-(\textbf{b}) B-spline function of order 8.}
+(\textbf{A}) B-spline function of order 2 (linear B-spline).
+(\textbf{B}) B-spline function of order 8.}
 \label{fig:Figure0}
@@
 \centering
-\includegraphics{./Graph/Figure1a.pdf}
-\includegraphics{./Graph/Figure1b.pdf}
-\caption{{\bf Examples of B-spline  scaling and wavelet functions}. (\textbf{a}) The cubic B-spline scaling function. (\textbf{b}) The corresponding wavelet function.}
+\includegraphics{./Graph/Figure1.pdf}
+% \includegraphics{./Graph/Figure1b.pdf}
+\caption{{\bf Examples of B-spline scaling and wavelet functions}. (\textbf{A}) The cubic B-spline scaling function. (\textbf{B}) The corresponding wavelet function.}
 \label{fig:MRA-Figure1}
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/ScaleDecomposition.pdf}\\
- 		\includegraphics[scale=1]{./Graph/WaveletDecomposition.pdf}
+ 		\includegraphics[scale=1]{./Graph/Decomposition.pdf}
  		\caption{{\bf The scaling and the wavelet function decomposition}.
-The scaling and the wavelet functions (blue) at $j=0$ are respectively obtained using 625 and 1250 scaling functions (black) at $j=4$.}
+(\textbf{A}) The scaling function (blue) at $j=0$ is obtained using 625 scaling functions (black) at $j=4$.
+(\textbf{B}) The wavelet function (blue) at $j=0$ is obtained using 1250 scaling functions (black) at $j=4$.}
  	\label{fig:MRA-BasisDecomposition}
  \end{figure}  
- In this paper, 4th order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+ In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[h]

### 2011-12-10 Multiresolution_framework/ltx/manuscript.tex
test for the mac
minor edit

@@
 
-This multi-resolution structure has been described by numerous methods (Wilson and Cowan).
+This multi-resolution structure has been described by numerous methods \cite{Wilson1973}.
 This idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths.
@@
 Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
-The solution to this problem was proposed by \dean{Breakspear and Stam} in using a wavelet decomposition.
+The solution to this problem was proposed by \cite{Breakspear2005} in using a wavelet decomposition.
 \begin{figure}[t]

### 2012-01-16 Multiresolution_framework/ltx/manuscript.tex

@@
 Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics of the EEG.
-These models typically describe the macroscopic dynamics of the human brain, but are also descriptive of finer-scale neurodynamics.
-For example..
-integrate and fire...
-The utility in these models to answer questions in neuroscience lies in the ability to infer parameters from data.
+The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
+For example, the post-synaptic response kernels (the pulse to wave function) can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
+Furthermore, the activation function (wave to pulse function) can be used used to model spiking statistics across spatial scales from single neurons (where is can be considered a CDF of the probability of firing) to mean firing rates of neural masses.
+The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
+
+The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability the infer parameters from electrophysiological data.
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
@@
 
-The first work describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\cite{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}.
-Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
+The first work describing data-driven mesoscopic neural modelling used a neural mass model to fit EEG data~\cite{Valdes1999}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modelling (DCM)~\cite{David2003}.
+Following this work, data-driven modelling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
 Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously \dean{and completely}.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously \dean{and completely}.
 
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$.
-Synaptic dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the synaptic time constant and $T_s$ is the sampling time.
+Membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time.
 The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
-The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covarianve function
+The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covariance function
 \begin{equation}
@@
 Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+
 \section{MRA of the IDE in State-Space}
@@
 where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$.
+\dean{The decomposition enables a separation of the spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
+}
 
@@
 The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
+
+The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
+Therefore, the goal is to form a parameterised equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 

### 2012-01-16 Multiresolution_framework/ltx/manuscript.tex
added reference for pulse to wave inversion

@@
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-For example, the post-synaptic response kernels (the pulse to wave function) can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
+For example, the post-synaptic response kernels (the pulse to wave function \cite{Jirsa1997}) can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
 Furthermore, the activation function (wave to pulse function) can be used used to model spiking statistics across spatial scales from single neurons (where is can be considered a CDF of the probability of firing) to mean firing rates of neural masses.

### 2012-01-17 Multiresolution_framework/ltx/manuscript.tex
working on MRA SS model section

@@
 \end{equation}
-where $v$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye for example, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location with the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
+where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location with the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
 
@@
 \section{MRA of the IDE in State-Space}
-The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$.
-Considering a one-dimensional field, the connectivity kernel is decomposed as,
+\dean{The purpose of forming the multi-resolution approximation (MRA) of the integro-differential equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.}
+
+The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
+Considering an $n$-dimensional field, the static connectivity kernel is decomposed as,
 \begin{equation}
- w\left(r-r'\right)=\sum_{l \in \mathbb{Z}}\alpha_{j_0,l}\phi_{j_0,l}\left(r-r'\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{j,l}\left(r-r'\right), 
+ w\left(\mathbf{r}\right)=\sum_{\mathbf{l} \in \mathbb{Z}^n}\alpha_{j_0,\mathbf{l}} \underbrace{\phi_{j_0,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l} \in \mathbb{Z}^n}\beta_{j,\mathbf{l}} \underbrace{\psi_{j,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{wavelet}},
 \label{eq:KernelExpansion}
 \end{equation}
-where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with $\phi_{j,l}\left(r\right)=2^{\frac{j}{2}}\phi\left(2^jr-l\right) $ and $\psi_{j,l}\left(r\right)=2^{\frac{j}{2}}\psi\left(2^jr-l\right)$.
-Integers $j$ and $l$ are the scale and translation parameters, respectively.
-Scaling functions retain the lowest frequency components, while the wavelet functions extract successively higher frequency components due to their low-pass and band-pass properties, respectively.
-The field is decomposed using
+where $\alpha_{j_0,\mathbf{l}}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,\mathbf{l}}$ are the detail coefficients at different scales $j$, with
+\begin{align}
+\phi_{j,\mathbf{l}}\left(\mathbf{r}\right) =& 2^{\frac{j}{2}}\phi\left(2^j\mathbf{r}-\mathbf{l}\right) \\	
+\psi_{j,\mathbf{l}}\left(\mathbf{r}\right) =& 2^{\frac{j}{2}}\psi\left(2^j\mathbf{r}-\mathbf{l}\right).
+\end{align}
+The parameters $j$ and $\mathbf{l}$ control the scale (dilation) and translation (spatial shift), respectively.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THEAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+
+% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
+% \begin{equation}
+% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
+% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
+% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
+% \end{cases}
+% \end{equation}
+
+The dynamic neural field is decomposed using
 \begin{equation}
- v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l}\phi_{j_{0},l}\left(r\right)+\sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{j,l}\left(r\right),
+ v_t\left(\mathbf{r}\right)=\sum_{\mathbf{l} \in \mathbb{Z}^n}x_{t,j_{0},\mathbf{l}} \underbrace{\phi_{j_0,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l} \in \mathbb{Z}^n} \check{x}_{t,j,\mathbf{l}} \underbrace{\psi_{j,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{wavelet}},
 \label{eq:FieldExpansion}
 \end{equation}
-where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the coefficients of the expansion and constitute the state vector at time $t$.
-\dean{The decomposition enables a separation of the spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
+where $x_{t,j_{0},\mathbf{l}}$ and $\check{x}_{t,j,\mathbf{l}} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
+\dean{The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
 }
 
-Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated at some level $j$. The field and the connectivity kernel are approximated by
+Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level \dean{$J$} in order to solve the estimation problem.
+In other words, the neural field must be band-limited up to a given spatial frequency.
+Assuming the field and connectivity kernel are spatially band-limited they can be accurately approximated by
 \begin{align}
-	w\left(r-r'\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right) 
+	w\left(\mathbf{r}\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}\right) 
 	\label{eq:KernelFiniteExpansion} \\
-	v_t\left(r\right) &\approx \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t,
+	v_t\left(\mathbf{r}\right) &\approx \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t,
 	\label{eq:FieldFiniteExpansion}
@@
 \begin{align}
-\boldsymbol\theta^\top &=[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 
+\boldsymbol\theta^\top &=[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top &=[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}].
+\mathbf{x}_{t}^\top &=[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
 \label{FieldWeights}
 \end{align}
-The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$, respectively.
-Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$, respectively.
+The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
+Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
 
@@
     \label{KernelBasisVector}
-    \boldsymbol\lambda^\top(r-r')=&\left[
-    \boldsymbol\phi_{j_0}^\top(r-r') ~
-    \boldsymbol\psi_{j_0}^\top(r-r') ~ 
-    \boldsymbol\psi_{j_0+1}^\top(r-r') ~
-    \cdots ~
-    \boldsymbol\psi_{j}^\top(r-r')\right] \\
+    \boldsymbol\lambda^\top(\mathbf{r})=&\left[
+    \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
+    \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
+    \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+    \cdots &
+    \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
     \label{FieldBasisVector}
-    \boldsymbol\mu^\top (r) =& \left[
-    \boldsymbol\phi_{j_0}^\top(r) ~ 
-    \boldsymbol\psi_{j_0}^\top(r) ~ 
-    \boldsymbol\psi_{j_0+1}^\top(r) ~ 
-    \cdots ~ 
-    \boldsymbol\psi_{j}^\top(r)
-\right]   
+    \boldsymbol\mu^\top (\mathbf{r}) =&\left[
+    \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
+    \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
+    \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+    \cdots &
+    \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
 \end{align}

### 2012-01-17 Multiresolution_framework/ltx/manuscript.tex
working on MRA SS model section some more

@@
 
+The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
+Therefore, the goal is to form a parameterised equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+
 The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
@@
 
-Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level \dean{$J$} in order to solve the estimation problem.
+Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level \dean{$j=J$} in order to solve the estimation problem.
 In other words, the neural field must be band-limited up to a given spatial frequency.
-Assuming the field and connectivity kernel are spatially band-limited they can be accurately approximated by
+
+Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions such that
 \begin{align}
-	w\left(\mathbf{r}\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}\right) 
-	\label{eq:KernelFiniteExpansion} \\
-	v_t\left(\mathbf{r}\right) &\approx \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t,
-	\label{eq:FieldFiniteExpansion}
+	\boldsymbol\alpha_{k} \triangleq& \left\lbrace\alpha_{k, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace \\
+	\boldsymbol\beta_{k} \triangleq& \\
+	\mathbf{x}_{t,k} \triangleq& \\
+	\check{\mathbf{x}}_{t,k} \triangleq& \\
+	\boldsymbol\phi_{j_0}^\top(\mathbf{r}) \triangleq& \\
+	\boldsymbol\psi_{k}^\top(\mathbf{r}) \triangleq& ,
 \end{align}
-where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, are defined as 
+where $k = j_0,j$.\dean{ARE THESE EACH $n_{\theta}$ or $n_x$ DIMENSIONAL VECTORS?} Following this we can define the \dean{vectors or matrices} 
 \begin{align}
-\boldsymbol\theta^\top &=[\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
+\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top &=[\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
-\label{FieldWeights}
-\end{align}
-The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
-Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
-
-The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
-\begin{align}
+\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]
+\label{FieldWeights} \\
 \label{KernelBasisVector}
-    \boldsymbol\lambda^\top(\mathbf{r})=&\left[
-    \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
+\boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
+\begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
 \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
@@
 \label{FieldBasisVector}
-    \boldsymbol\mu^\top (\mathbf{r}) =&\left[
+\boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
 \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
@@
 \cdots &
-    \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
+\boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right],
+\end{align}
+which allow us to write the neural field and connectivity kernel decomposition in the compact form of
+\begin{align}
+	w\left(\mathbf{r}\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}\right) 
+	\label{eq:KernelFiniteExpansion} \\
+	v_t\left(\mathbf{r}\right) &\approx \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t.
+	\label{eq:FieldFiniteExpansion}
 \end{align}
 
-The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).
-
-The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-Therefore, the goal is to form a parameterised equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+% where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, \dean{($\boldsymbol\theta \in \mathbb{R}^{n_{\theta}\times (J+2)}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x \times (J+2)}$)} are defined as
+% \begin{align}
+% \boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
+% \label{KernelWeights} \\
+% \mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
+% \label{FieldWeights}
+% \end{align}
+% The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
+Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
+% 
+% The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
+% \begin{align}
+%     \label{KernelBasisVector}
+%     \boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
+%     \begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
+%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
+%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+%     \cdots &
+%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
+%     \label{FieldBasisVector}
+%     \boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
+%     \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
+%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
+%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+%     \cdots &
+%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
+% \end{align}
+% 
+% The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
+Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
+\begin{equation}\label{eq:DiscreteTimeModel}
+	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t = 
+	\xi \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t + 
+	T_s \int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}'}  
+	+ e_t\left(\mathbf{r}\right), 
+\end{equation}
 
@@
 \begin{align}\label{eq:DecomposedModel2} 
-	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
+	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
 	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.

### 2012-01-17 Multiresolution_framework/ltx/manuscript.tex
working on MRA SS model section some more some more

@@
 The parameters $j$ and $\mathbf{l}$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THEAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
 
@@
 Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
-\begin{equation}\label{eq:DiscreteTimeModel}
+\begin{equation}\label{eq:ApproxDiscreteTimeModel}
 	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t = 
@@
 	\, \mathrm{d}\mathbf{r}'}  
-	+ e_t\left(\mathbf{r}\right), 
+	+ e_t\left(\mathbf{r}\right).
+\end{equation}
+The aim of the next part of the derivation is to isolate the state vector on the left hand side of the equation.
+To do this we first multiply both sides of equation~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving (\dean{UP TO HERE})
+\begin{equation}\label{eq:ApproxDiscreteTimeModel2}
+	\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_t = 
+	\xi \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}\mathbf{r} \mathbf{x}_t + 
+	T_s \int_{\Omega}\boldsymbol\mu\left(r\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
+	+ \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(\mathbf{r}\right)\mathrm{d}\mathbf{r}.
 \end{equation}
@@
 \begin{align}\label{eq:Lambdax}
- \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
+ \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}\mathbf{r} \\
 \label{eq:Lambdatheta}

### 2012-01-18 Multiresolution_framework/ltx/manuscript.tex
more edtis to MRA SS section - I think it is ok now for general scenario

--- 2012-01-17 Multiresolution_framework/ltx/manuscript.tex
@@
 	    f\left(v_t\left(\mathbf{r}'\right)\right) 
-	\, d\mathbf{r}'} 
+	\, \mathrm{d}\mathbf{r}'} 
 	+ e_t\left(\mathbf{r}\right), 
@@
 \begin{equation}\label{eq:ObservationEquation}
-	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
+	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
 \end{equation}
@@
 Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
-\begin{equation}\label{eq:DiscreteTimeModel}
-	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t = 
+\begin{equation}\label{eq:ApproxDiscreteTimeModel}
+	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_{t+1} = 
 	\xi \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t + 
@@
 	\, \mathrm{d}\mathbf{r}'}  
-	+ e_t\left(\mathbf{r}\right), 
-\end{equation}
-
-To derive the state-space model, we first define the matrices 
-\begin{align}\label{eq:Lambdax}
- \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
-\label{eq:Lambdatheta}
- \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
-	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
-\end{align}
-Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
-\begin{align}\label{eq:DecomposedModel2} 
-	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
-	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
-\end{align}
+	+ e_t\left(\mathbf{r}\right).
+\end{equation}
+The aim of the next part of the derivation is to isolate the state vector on the left hand side of the equation.
+To do this we first multiply both sides of equation~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
+\begin{equation}\label{eq:ApproxDiscreteTimeModel2}
+	\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_{t+1} = 
+	\xi \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_t + 
+	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
+	+ \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\mathrm{d}\mathbf{r}.
+\end{equation}
+To isolate the state vector, we now define the matrix 
+\begin{equation}
+	\label{eq:Lambdax}
+	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right)\boldsymbol{\mu}^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}
+\end{equation}
+and substitute into equation~\eqref{eq:ApproxDiscreteTimeModel2} giving
+\begin{equation}\label{eq:ApproxDiscreteTimeModel3}
+	\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
+	\xi \mathbf{\Lambda}_{x} \mathbf{x}_t + 
+	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
+	+ \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
+\end{equation}
 Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
-\begin{align}\label{eq:StateEquation}
- \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
-\label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
-\end{align}
-The disturbance becomes 
+\begin{equation}\label{eq:ApproxDiscreteTimeModel4}
+	\mathbf{x}_{t+1} = 
+	\xi \mathbf{x}_t + 
+	T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
+	+ \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
+\end{equation}
+A very nice property of the MRAIDE framework is the the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 
 \begin{equation}\label{eq:Disturbance}
-\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
-\end{equation}
-which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
+\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\,\mathrm{d}\mathbf{r},
+\end{equation}
+with covariance (see \cite{Freestone2011} for proof)
 \begin{equation}\label{eq:CovMatrix}
-\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
-\end{equation}
+\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \eta\left(\mathbf{r}-\mathbf{r}'\right)\boldsymbol\mu^{\top}\left(\mathbf{r}'\right)\,\mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}\mathbf{\Lambda}_{x}^{-\top}.
+\end{equation} 
+% \begin{align}\label{eq:Lambdax}
+%  \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \\
+% \label{eq:Lambdatheta}
+%  \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+% 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+% 	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
+% \end{align}
+% Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
+% \begin{align}\label{eq:DecomposedModel2} 
+% 	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
+% 	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
+% \end{align}
+% Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
+% \begin{align}\label{eq:StateEquation}
+%  \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
+% \label{eq:A_theta}
+%  \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
+% \end{align}
+% The disturbance becomes 
+% \begin{equation}\label{eq:Disturbance}
+% \mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
+% \end{equation}
+% which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
+% \begin{equation}\label{eq:CovMatrix}
+% \boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
+% \end{equation}
+
 The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
@@
 \end{equation}
-where each element of the observation matrix is given by
+where each element of the observation matrix, $\mathbf{C}$, is given by
 \begin{equation}\label{eq:Observationmatrix}
-	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
-\end{equation}
+	\mathbf{C}_{ik} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\mu}_k(\mathbf{r}') \, \mathrm{d}\mathbf{r}'.
+\end{equation}
+
 \section{B-spline MRAIDE in State-Space }
-B-spline functions are one of the most basic elements for wavelet construction, these functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines.
+B-spline functions are one of the most basic elements for wavelet construction.
+These functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines.
 The degree of smoothness is determined by the order of splines \cite{Goswami1999} where the higher the order, the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).

### 2012-01-18 Multiresolution_framework/ltx/manuscript.tex
edits to the section describing the wavelets and some notes in the MRA IDE section

@@
 \end{equation} 
+\dean{Can we define something like the other paper like
+\begin{equation}
+	\left[\Gamma(\mathbf{r}')\right]_{:i} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right) \,\mathrm{d}\mathbf{r}
+\end{equation}
+giving
+\begin{equation}
+	\mathbf{x}_{t+1} = 
+	\xi \mathbf{x}_t + 
+	\int_{\Omega} \Gamma\left(\mathbf{r}'\right)f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right) \mathbf{x}_t\right) 
+	\, \mathrm{d}\mathbf{r}' \boldsymbol\theta
+	+ \mathbf w_t???
+\end{equation}}
 % \begin{align}\label{eq:Lambdax}
@@
 
-\section{B-spline MRAIDE in State-Space }
+\section{B-Spline MRAIDE in State-Space }
+\subsection{A Brief Introduction to B-Spline Wavelets}
 B-spline functions are one of the most basic elements for wavelet construction.
-These functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines.
-The degree of smoothness is determined by the order of splines \cite{Goswami1999} where the higher the order, the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
-\begin{figure}[!ht]
+These functions are composed of piecewise polynomials combined smoothly at some breaking points (knots), which are equally spaced in the case of cardinal B-splines.
+The degree of smoothness is determined by the order of splines \cite{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
+\begin{figure}[!t]
 \centering
@@
 
-B-spline wavelet and scaling functions are formulated independently by Chui and Wang, and Unser et al \cite{Chui1992b,Chui1992,Unser1993}.
+B-spline wavelet and scaling functions were formulated independently by Chui and Wang, and Unser et al \cite{Chui1992b,Chui1992,Unser1993}.
 The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
 B-spline wavelet and scaling functions approach optimal time/frequency localisation as the order of the spline increases.
-In fact for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions \cite{Unser1992}.
-B-spline wavelets have a better approximation rate as other wavelets with the same number of vanishing moments \cite{Unser1999}.
-B-spline wavelet and scaling functions are particularly suitable in this work due to their ability to analytically define the convolution and inner product to form  MRAIDE components.
+In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate then other wavelets with the same number of vanishing moments \cite{Unser1999}.
+
+B-spline wavelet and scaling functions are particularly suited in this framework due to the property of being able to analytically define the convolution and inner product to form MRAIDE components.
 The following summarises some important characteristics of B-splines relevant to the proposed modelling framework.
@@
 \begin{equation}
-N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)dr',
+N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)\,\mathrm{d}r',
 \label{SplineConvolutionIntegral}
@@
 \end{equation}
-then a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \cite{DeBoor2001}
+Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \cite{DeBoor2001}
 \begin{equation}\label{eq:MRA-DoBoorFormula}
@@
  \end{equation}
-The most commonly used form of splines is the Cubic spline $\left(m=4\right)$, comprising of third order polynomials added together at the joining points, with an explicit expression given by
+The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third order polynomials added together at the joining points, with an explicit expression given by
 \begin{align}
@@
 
+\subsection{Frequency Analysis}
 To determine the level of approximation in the model, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
@@
 \end{align}
-The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair which for cardinal B-spline scaling and wavelet functions of order $m$, takes the form of \cite{Chui1992}
+\dean{Need to say how the FT is used somewhere here before proceeding.}
+
+The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which for cardinal B-spline scaling and wavelet functions of order $m$ takes the form of
 \begin{align}
@@
  \end{align}
- where $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients, and
+where 
  \begin{align}
 \left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
-\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}.
- \end{align}
+\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
+ \end{align}
+and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \cite{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}
+
 Figure~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero. 

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
added table - moved around wavelet section to get frequency analysis bit seperate - edit to MRA derivation

@@
 %         \textwidth      170.0mm
-
+\usepackage{setspace} 
 \usepackage{color}
@@
 \section{IDE Neural Field Model}
+
+\singlespacing
+\begin{table*}[!t]
+\begin{tabular}{|l|l|l|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
+	\hline
+	$\Omega$ & spatial domain & n.a.\\
+	$\mathbf{r}$ & spatial location & [mm, mm]\\
+	$t$ & time & s\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Model}}\\
+	\hline
+    $y_t$ & observation & mV\\
+    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
+	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
+	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
+	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$m(\mathbf{r}_n,\mathbf{r}')$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
+	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
+	$h(t)$ & post-synaptic response kernel & mV\\
+	$\zeta$, $\xi$ & inverse synaptic time constant \& time constant parameter & s$^{-1}$, n.a.\\
+	$\eta(t)$ & Heaviside step function & n.a.\\
+	$\delta(t)$ & Dirac-delta function & n.a.\\
+	$\textrm{D}$ & temporal differential operator & n.a.\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
+	\hline
+   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
+   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
+   	$\mathbf{C}$ & observation matrix & n.a. \\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
+	\hline
+	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
+	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Estimation}} \\
+	\hline
+	$\mathcal K_{t} $ & filter gain & n.a.\\
+	\hline
+\end{tabular}
+\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper.
+The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
+\label{tab:Notation}
+\end{table*}
+\doublespacing
+
 The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
@@
 \end{equation}
-\dean{Can we define something like the other paper like
-\begin{equation}
-	\left[\Gamma(\mathbf{r}')\right]_{:i} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right) \,\mathrm{d}\mathbf{r}
+
+The state-transition equation can be simplified by exploiting the isotropy of the scaling functions and the wavelets where
+\begin{equation}
+	\boldsymbol{\lambda}_{j,l}(\mathbf{r}-\mathbf{r}') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+\mathbf{r}'-\mathbf{r}). 
+\end{equation}
+Following this, we can switch the order of operations with the inner product and convolution in equation~\eqref{eq:ApproxDiscreteTimeModel4}.
+With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel.
+This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions.
+This has major computation advantages when solving the estimation problem.
+The predefined convolution can be written as
+\begin{equation}
+	\left[\Gamma(\mathbf{r}')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\lambda\left(2\mathbf{c}_{j,l} + \mathbf{r}'-\mathbf{r}\right) \,\mathrm{d}\mathbf{r}
 \end{equation}
@@
 	\, \mathrm{d}\mathbf{r}' \boldsymbol\theta
-	+ \mathbf w_t???
-\end{equation}}
+	+ \mathbf w_t
+\end{equation}
 % \begin{align}\label{eq:Lambdax}
@@
 
-\subsection{Frequency Analysis}
-To determine the level of approximation in the model, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
-To proceed the Fourier transform of $N_1(r)$ is first calculated,
-\begin{align}\label{eq:MRA-N1Fouriertransform}
-\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}.
-\end{align}
-The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
-Therefore, taking Fourier transform of \eqref{eq:N1convolutions} and substituting \eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
-\begin{align}\label{eq:MRA-NmFouriertransform}
-\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^m.
-\end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.}
-
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which for cardinal B-spline scaling and wavelet functions of order $m$ takes the form of
@@
 Figure~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero. 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering
@@
  \end {table}
+\subsection{Frequency Analysis}
+To determine the level of approximation in the model, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
+To proceed the Fourier transform of $N_1(r)$ is first calculated,
+\begin{align}\label{eq:MRA-N1Fouriertransform}
+\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}.
+\end{align}
+The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
+Therefore, taking Fourier transform of \eqref{eq:N1convolutions} and substituting \eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
+\begin{align}\label{eq:MRA-NmFouriertransform}
+\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^m.
+\end{align}
+\dean{Need to say how the FT is used somewhere here before proceeding.}
+
 \section{State and Parameter Estimation}

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
added some paragraphs to estimation section

@@
 	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n,\mathbf{r}')$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
+	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
 	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
@@
 \end{equation}
-% \begin{align}\label{eq:Lambdax}
-%  \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \\
-% \label{eq:Lambdatheta}
-%  \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
-% 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-% 	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
-% \end{align}
+
 % Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
@@
 Examples of such expansions are given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
-\begin{figure}[!h] 
+\begin{figure}[!t] 
  	\centering
@@
  In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
-\begin {table}[h]
+\begin {table}[t]
 \begin{center}
@@
 \section{State and Parameter Estimation}
-The state-space representation of the MRAIDE allows the use of the well known Expectation Maximization (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
+There exist many variations of state and parameter estimation methods for state-space models.
+The choice of algorithm is normally determined by the dimension of the system, whether the system is linear or nonlinear and whether or not the parameters are considered static or dynamic.
+Up to this point of the paper, we have not made any assumptions on any of these criteria for choosing an estimation algorithm.
+The MRAIDE neural field model formulation may be used in any of the above scenarios.
+
+To demonstrate the MRAIDE framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+Note that there is a difference between forward and inverse modelling when making these assumptions.
+For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
+
+It is important to point out there is no doubt that there will always be a mismatch between neural mass models and actual cortical tissue.
+Nevertheless, the simplifications used in formulating the equation enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.
+The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
+
+By assuming a linear activation function of the form
+\begin{equation}
+	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})
+\end{equation}
+the state transition equation~\eqref{eq:ApproxDiscreteTimeModel4} simplifies to
+\begin{equation}\label{eq:ApproxDiscreteTimeModel_Linear}
+	\mathbf{x}_{t+1} = 
+	\xi \mathbf{x}_t + 
+	\varsigma T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    \boldsymbol\mu^\top\left(\mathbf{r}'\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}} \mathbf{x}_t
+	+ \mathbf{w}_t.
+\end{equation}
+Now we can further simplify the system by defining
+\begin{align}
+	\label{eq:Lambdatheta}
+	 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r}
+\end{align}
+to give the state transition equation
+\begin{align}\label{eq:StateEquation}
+ \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
+\label{eq:A_theta}
+ \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
+\end{align}
+
+The linear state-space representation of the MRAIDE allows the use of the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
-In doing so, the synaptic time constant was set to $\tau = 10$~ms \cite{David2003}, and the sampling time was chosen ten times faster \cite{Stephan2008}, i.e.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
+In doing so, the membrane time constant was set to $\tau = 10$~ms \cite{David2003}, and the sampling time was chosen ten times faster \cite{Stephan2008}, i.e.
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
 
-Two different experiments were designed where in the first one, 200 runs of one second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
+Two different experiments were designed to test the framework.
+In the first one, 200 realisations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
 This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realisation.
@@
 
-For each of the experiment, the estimation was applied to the final 900~ms, allowing the model's dynamics to stabilise from the initial conditions.
+For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilise from the initial conditions.
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
@@
 This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see (\ref{eq:MRA-PsiPsiOrthogonality}-\ref{eq:MRA-PhiPsiOrthogonality})).
+
 \subsection{Experiment I}
@@
 This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
-The spatial bandwidths of wavelets was calculated analytically using \eqref{eq:MRA-NmFouriertransform}.
-The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
-\begin{figure}[!h] 
+The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-NmFouriertransform}.
+The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
+\begin{figure}[!t] 
  	\centering
@@
 
-The EM algorithm was allowed to run until the maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
+The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
 The rate of convergence of the EM based algorithm is depicted in Figure~\ref{fig:MRA-Convergence}.
-\begin{figure}[!h] 
+\begin{figure}[!t] 
  	\centering
@@
 A total number of 25 basis functions was used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$ accordingly.
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \includegraphics{./Graph/Figure5.pdf}
@@
 From this figure, it can be observed that the overall trend of the underlying field can be also captured at the coarser levels.
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering
@@
 The experiment was performed several times and the results were consistent over each run.
- \begin{figure}[!h] 
+ \begin{figure}[!t] 
  	\centering
@@
  \end{figure} 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
edit to introduction for pulse to wave and wave to pulse conversion

@@
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-For example, the post-synaptic response kernels (the pulse to wave function \cite{Jirsa1997}) can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
-Furthermore, the activation function (wave to pulse function) can be used used to model spiking statistics across spatial scales from single neurons (where is can be considered a CDF of the probability of firing) to mean firing rates of neural masses.
-The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
+\parham{Examples are, the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \cite{Jirsa1997}.
+The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
+The latter,  can be used to model spiking statistics across spatial scales from single neurons (where is can be considered a CDF of the probability of firing) to mean firing rates of neural masses.} The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
 
@@
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously \dean{and completely}.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously and completely.
 

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
edits to Bspline section

@@
 
-The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability the infer parameters from electrophysiological data.
+The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability to infer parameters from electrophysiological data.
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
@@
  \end{equation}
-The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third order polynomials added together at the joining points, with an explicit expression given by
+The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third degree polynomials added together at the joining points, with an explicit expression given by
 \begin{align}
@@
 
-The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which for cardinal B-spline scaling and wavelet functions of order $m$ takes the form of
+The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
+For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
 \begin{align}
@@
 
-In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale.
+In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
 For scaling functions this can be done  by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
@@
 \end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.}
+\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order Bspline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} from which the level of approximation, $j$, can be determined.
+This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying neural field estimated from observations.}
 
@@
  \end{algorithm}
-The stopping rule adopted herein is
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
 \begin{equation}

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
changed bold r to scalar

@@
 \begin{equation}
- w\left(\mathbf{r}\right)=\sum_{\mathbf{l} \in \mathbb{Z}^n}\alpha_{j_0,\mathbf{l}} \underbrace{\phi_{j_0,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l} \in \mathbb{Z}^n}\beta_{j,\mathbf{l}} \underbrace{\psi_{j,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{wavelet}},
+ w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelet}},
 \label{eq:KernelExpansion}
 \end{equation}
-where $\alpha_{j_0,\mathbf{l}}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,\mathbf{l}}$ are the detail coefficients at different scales $j$, with
-\begin{align}
-\phi_{j,\mathbf{l}}\left(\mathbf{r}\right) =& 2^{\frac{j}{2}}\phi\left(2^j\mathbf{r}-\mathbf{l}\right) \\	
-\psi_{j,\mathbf{l}}\left(\mathbf{r}\right) =& 2^{\frac{j}{2}}\psi\left(2^j\mathbf{r}-\mathbf{l}\right).
-\end{align}
-The parameters $j$ and $\mathbf{l}$ control the scale (dilation) and translation (spatial shift), respectively.
+where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
+\begin{align}
+\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \\	
+\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).
+\end{align}
+The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
 \dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
@@
 \begin{equation}
- v_t\left(\mathbf{r}\right)=\sum_{\mathbf{l} \in \mathbb{Z}^n}x_{t,j_{0},\mathbf{l}} \underbrace{\phi_{j_0,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{\mathbf{l} \in \mathbb{Z}^n} \check{x}_{t,j,\mathbf{l}} \underbrace{\psi_{j,\mathbf{l}}\left(\mathbf{r}\right)}_{\text{wavelet}},
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelet}},
 \label{eq:FieldExpansion}
 \end{equation}
-where $x_{t,j_{0},\mathbf{l}}$ and $\check{x}_{t,j,\mathbf{l}} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
+where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
 \dean{The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
@@
 \begin{align}
-	\boldsymbol\alpha_{k} \triangleq& \left\lbrace\alpha_{k, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace \\
+	\boldsymbol\alpha_{k} \triangleq& \left\lbrace\alpha_{k, l}:l \in \mathbb{Z} \right\rbrace \\
 	\boldsymbol\beta_{k} \triangleq& \\
@@
 	\check{\mathbf{x}}_{t,k} \triangleq& \\
-	\boldsymbol\phi_{j_0}^\top(\mathbf{r}) \triangleq& \\
-	\boldsymbol\psi_{k}^\top(\mathbf{r}) \triangleq& ,
+	\boldsymbol\phi_{j_0}^\top(r) \triangleq& \\
+	\boldsymbol\psi_{k}^\top(r) \triangleq& ,
 \end{align}
@@
 \label{KernelBasisVector}
-\boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
-\begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
-\boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
-\boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+\boldsymbol\lambda^\top(r) \triangleq& \left[
+\begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(r) &
+\boldsymbol\psi_{j_0}^\top(r) & 
+\boldsymbol\psi_{j_0+1}^\top(r) &
 \cdots &
-\boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
+\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\
 \label{FieldBasisVector}
-\boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
-\begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
-\boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
-\boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
+\boldsymbol\mu^\top (r) \triangleq& \left[
+\begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(r) &
+\boldsymbol\psi_{j_0}^\top(r) & 
+\boldsymbol\psi_{j_0+1}^\top(r) &
 \cdots &
-\boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right],
+\boldsymbol\psi_{J}^\top(r)\end{array}\right],
 \end{align}
@@
 \begin{align}
-	w\left(\mathbf{r}\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}\right) 
+	w\left(r\right) &\approx \boldsymbol\theta^\top\boldsymbol\lambda\left(r\right) 
 	\label{eq:KernelFiniteExpansion} \\
-	v_t\left(\mathbf{r}\right) &\approx \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t.
+	v_t\left(r\right) &\approx \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t.
 	\label{eq:FieldFiniteExpansion}
@@
 \begin{equation}\label{eq:ApproxDiscreteTimeModel}
-	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_{t+1} = 
-	\xi \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t + 
+	\boldsymbol\mu^\top\left(r\right)\mathbf{x}_{t+1} = 
+	\xi \boldsymbol\mu^\top\left(r\right)\mathbf{x}_t + 
 	T_s \int_\Omega { 
-	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
-	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
-	\, \mathrm{d}\mathbf{r}'}  
-	+ e_t\left(\mathbf{r}\right).
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    f\left(\boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}r'}  
+	+ e_t\left(r\right).
 \end{equation}
@@
 \begin{equation}\label{eq:ApproxDiscreteTimeModel2}
-	\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_{t+1} = 
-	\xi \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_t + 
-	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
-	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
-	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
-	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
-	+ \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\mathrm{d}\mathbf{r}.
+	\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}r \mathbf{x}_{t+1} = 
+	\xi \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}r \mathbf{x}_t + 
+	T_s \int_{\Omega}\boldsymbol\mu\left(r\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    f\left(\boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}r'\mathrm{d}r}  
+	+ \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)\mathrm{d}r.
 \end{equation}
@@
 	\label{eq:Lambdax}
-	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right)\boldsymbol{\mu}^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}
+	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r
 \end{equation}
@@
 	\xi \mathbf{\Lambda}_{x} \mathbf{x}_t + 
-	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
-	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
-	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
-	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
-	+ \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
+	T_s \int_{\Omega}\boldsymbol\mu\left(r\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    f\left(\boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}r'\mathrm{d}r}  
+	+ \int_{\Omega}\boldsymbol{\mu}\left(r\right) e_t\left(r\right) \mathrm{d}r.
 \end{equation}
@@
 	\xi \mathbf{x}_t + 
-	T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
-	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
-	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
-	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
-	+ \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
+	T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(r\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+	    f\left(\boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t\right) 
+	\, \mathrm{d}r'\mathrm{d}r}  
+	+ \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol{\mu}\left(r\right) e_t\left(r\right) \mathrm{d}r.
 \end{equation}
@@
 \begin{equation}\label{eq:Disturbance}
-\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\,\mathrm{d}\mathbf{r},
+\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)\,\mathrm{d}r,
 \end{equation}
@@
 \begin{equation}\label{eq:CovMatrix}
-\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \eta\left(\mathbf{r}-\mathbf{r}'\right)\boldsymbol\mu^{\top}\left(\mathbf{r}'\right)\,\mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}\mathbf{\Lambda}_{x}^{-\top}.
+\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)\,\mathrm{d}r'\mathrm{d}r\mathbf{\Lambda}_{x}^{-\top}.
 \end{equation}
@@
 \begin{equation}
-	\boldsymbol{\lambda}_{j,l}(\mathbf{r}-\mathbf{r}') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+\mathbf{r}'-\mathbf{r}). 
+	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 
 \end{equation}
@@
 \begin{equation}
-	\left[\Gamma(\mathbf{r}')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\lambda\left(2\mathbf{c}_{j,l} + \mathbf{r}'-\mathbf{r}\right) \,\mathrm{d}\mathbf{r}
+	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r
 \end{equation}
@@
 	\xi \mathbf{x}_t + 
-	\int_{\Omega} \Gamma\left(\mathbf{r}'\right)f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right) \mathbf{x}_t\right) 
-	\, \mathrm{d}\mathbf{r}' \boldsymbol\theta
+	\int_{\Omega} \Gamma\left(r'\right)f\left(\boldsymbol\mu^\top\left(r'\right) \mathbf{x}_t\right) 
+	\, \mathrm{d}r' \boldsymbol\theta
 	+ \mathbf w_t
@@
 \begin{equation}\label{eq:Observationmatrix}
-	\mathbf{C}_{ik} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\mu}_k(\mathbf{r}') \, \mathrm{d}\mathbf{r}'.
+	\mathbf{C}_{ik} \triangleq \int_{\Omega}m(r_i -r')\boldsymbol{\mu}_k(r') \, \mathrm{d}r'.
 \end{equation}

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
minor edits
edits to different parts

@@
 where $\delta(\cdot)$ is the Dirac-delta function.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
+The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r}))$ \parham{Dean: can you add the bit about different type of activatin functions here}.%$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
 
@@
 Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+\parham{the lead field thingy}
 
 \section{MRA of the IDE in State-Space}
-\dean{The purpose of forming the multi-resolution approximation (MRA) of the integro-differential equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+\dean{The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
 Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.}
@@
 The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
-Considering an $n$-dimensional field, the static connectivity kernel is decomposed as,
+Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
 \begin{equation}
@@
 
-Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions such that
-\begin{align}
-	\boldsymbol\alpha_{k} \triangleq& \left\lbrace\alpha_{k, l}:l \in \mathbb{Z} \right\rbrace \\
-	\boldsymbol\beta_{k} \triangleq& \\
-	\mathbf{x}_{t,k} \triangleq& \\
-	\check{\mathbf{x}}_{t,k} \triangleq& \\
-	\boldsymbol\phi_{j_0}^\top(r) \triangleq& \\
-	\boldsymbol\psi_{k}^\top(r) \triangleq& ,
+Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions \parham{and their corresponding coefficients such that}
+\begin{align}      
+	\boldsymbol\phi_{j_0}(r) \triangleq&\left\lbrace{\phi_{j_0,l}(r)}:l \in \mathbb{Z} \right\rbrace \\
+	\boldsymbol\psi_{j}(r) \triangleq& \left\lbrace{\psi_{j,l}(r)}:l \in \mathbb{Z} \right\rbrace\\
+	\boldsymbol\alpha_{j_0} \triangleq& \left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace \\
+	\boldsymbol\beta_{j} \triangleq& \left\lbrace\beta_{j, l}:l \in \mathbb{Z} \right\rbrace \\
+	\mathbf{x}_{t,j_0} \triangleq& \left\lbrace{x}_{t,j_{0},l}:l \in \mathbb{Z} \right\rbrace \\
+	\check{\mathbf{x}}_{t,j} \triangleq& \left\lbrace{\check{x}}_{t,j,l}:l \in \mathbb{Z} \right\rbrace,
 \end{align}
@@
 To do this we first multiply both sides of equation~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
-\begin{equation}\label{eq:ApproxDiscreteTimeModel2}
-	\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}r \mathbf{x}_{t+1} = 
+\begin{align}\label{eq:ApproxDiscreteTimeModel2}
+	\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}r \mathbf{x}_{t+1} &= 
 	\xi \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) \mathrm{d}r \mathbf{x}_t + 
@@
 	    f\left(\boldsymbol\mu^\top\left(r'\right)\mathbf{x}_t\right) 
-	\, \mathrm{d}r'\mathrm{d}r}  
-	+ \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)\mathrm{d}r.
-\end{equation}
+	\, \mathrm{d}r'\mathrm{d}r}  \nonumber\\
+	&+ \int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)\mathrm{d}r.
+\end{align}
 To isolate the state vector, we now define the matrix 
@@
 
-The state-transition equation can be simplified by exploiting the isotropy of the scaling functions and the wavelets where
+\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic  where}
 \begin{equation}
@@
 This has major computation advantages when solving the estimation problem.
-The predefined convolution can be written as
+\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field.
+} The predefined convolution can be written as
 \begin{equation}
@@
 \end{align}
-The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_x$, $\boldsymbol\Lambda_{\theta}$ and $\boldsymbol\Sigma_w$).
+The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$, $\boldsymbol\Gamma$ and $\boldsymbol\Sigma_w$).
 To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
edits to EM algorithm

@@
 
-The linear state-space representation of the MRAIDE allows the use of the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977} to infer both the kernel and the field from electrophysiological data.
-The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate and the posterior distribution of the field over time.
-We use the standard EM algorithm for linear dynamic systems \cite{Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
-EM essentially finds increasingly tighter lower bounds on the likelihood of the kernel $p(\mathbf{y}_1 \ldots \mathbf{y}_T|w)$ so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
+The linear state-space representation of the MRAIDE allows the use of the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
+The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+\begin{equation}
+	\boldsymbol\theta_{\text{ML}}=\arg\max_{\boldsymbol\theta}~p(\mathbf Y;\boldsymbol\theta),
+ \end{equation}
+ %We use the standard EM algorithm for linear dynamic systems \cite{Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
+ and the posterior distribution of the field over time.
+Here $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the entire sequence of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
+When maximisation of the likelihood function is difficult to achieve directly the EM algorithm can be used to find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
+By exploiting the total probability rule it is rather straightforward to show that
+\begin{equation}
+	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right], 
+\end{equation}
+is a lower bound on the log-likelihood function \cite{Bishop2006} where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probabilty distribution of the states and the observations.
+Maximising the likelihood in terms of the parameter set is equivalent to the log-likelihood maximisation, as both the likelihood and log-likelihood functions share the same maximiser due to the monotonicity of the logarithm function....
+The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
+The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
  \begin{equation}\label{eq:jointdistribution}

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
added appendix for the lower bound

@@
 Here $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the entire sequence of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
-When maximisation of the likelihood function is difficult to achieve directly the EM algorithm can be used to find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
+The goal of the EM algorithm is to maximise  the likelihood function in the presence of the hidden variables, the weights of the field basis functions in this case.
+The EM finds increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
 By exploiting the total probability rule it is rather straightforward to show that
@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probabilty distribution of the states and the observations.
-Maximising the likelihood in terms of the parameter set is equivalent to the log-likelihood maximisation, as both the likelihood and log-likelihood functions share the same maximiser due to the monotonicity of the logarithm function....
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations.
+....
 The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
@@
 Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof. 
-% \cut{Future work should be directed towards extending the framework to account for a second-order synaptic response kernel, heterogeneity in the connectivity and perhaps time delays at lower spatial resolutions.
-Most importantly, future work should be directed towards applying and validating the framework on real data.}
-
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
+\subsection{Lower bound on likelihood function}
+A derivation of the lower bound that is based on \cite{Bishop2006} is provided in this Appendix.
+Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\Theta$.
+Maximising the likelihood in terms of the parameter set is equivalent to the log-likelihood maximisation, as both the likelihood and log-likelihood functions share the same maximiser due to the monotonicity of the logarithm function.
+By exploiting the  total probability rule the following expression can be written \cite{Koralov2007}
+\begin{equation}
+ \ln~p(\mathbf Y;\boldsymbol\Theta)=\ln\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\Theta)d\mathbf X.
+\end{equation}
+For any choice of distribution defined over the latent variables, $q(\mathbf X)$, the following decomposition holds
+\begin{equation}\label{eq:EM-loglikelihooddecomposition}
+ \ln~p(\mathbf Y\mid\boldsymbol\Theta)=\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p),
+\end{equation}
+where
+\begin{align}
+ \mathcal{L}(q,\boldsymbol\Theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \label{eq:EM-decomposition1}\\
+\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
+\end{align}
+Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$ in \eqref{eq:EM-decomposition1} after noting that $q(\mathbf X)$ is a normalised distribution that integrates to one.
+Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$ and $q(\mathbf X)$ and as a distance it is always non-negative, $\mathrm{KL}(q\parallel p)\ge 0$, with equality if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
+It therefore follows from \eqref{eq:EM-loglikelihooddecomposition} that $\mathcal{L}(q,\boldsymbol\Theta)\le \ln~p(\mathbf Y\mid\boldsymbol\Theta)$, in other words \eqref{eq:EM-decomposition1} is a lower bound on the log-likelihood function.
+The EM algorithm alternates between maximising the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\Theta$, respectively, while holding the other fixed.
+Suppose that the current estimate of the parameter set is $\boldsymbol\Theta'$, in the E-step the lower bound is maximised with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\Theta'$ is fixed.
+Since the value of $p(\mathbf Y;\boldsymbol\Theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the Kullback-Liebler distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
+At this point, the lower bound becomes equal to the log-likelihood function.
+The maximum in the M-step is obtained by maximising the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
+Since the distribution $q(\mathbf X)$ is computed using the old parameter estimates and kept fixed during the M-step, it is not equal to $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$, resulting in a non-zero KL distance.
+Therefore, the growth of the log-likelihood function is greater than the growth of the lower bound.
+Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta')$ for $q(\mathbf X)$ in \eqref{eq:EM-decomposition1} gives
+\begin{align}
+ \mathcal{L}(q,\boldsymbol\Theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')~d\mathbf X \nonumber \\
+&= \mathbf E_{\boldsymbol\Theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)\right] +\mathrm{const.}\nonumber\\
+&=\mathcal{Q}(\boldsymbol\Theta,\boldsymbol\Theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
+\end{align}
+where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
+The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\Theta$.
+It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.
+
 \ifCLASSOPTIONcaptionsoff

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
edit to appendix

@@
 Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\Theta$.
+We want to maximise the likelihood function which is difficult to maximise directly
+\begin{equation}
+ p(\mathbf Y;\boldsymbol\Theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\Theta)d\mathbf X.
+\end{equation}   
 Maximising the likelihood in terms of the parameter set is equivalent to the log-likelihood maximisation, as both the likelihood and log-likelihood functions share the same maximiser due to the monotonicity of the logarithm function.
-By exploiting the  total probability rule the following expression can be written \cite{Koralov2007}
-\begin{equation}
- \ln~p(\mathbf Y;\boldsymbol\Theta)=\ln\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\Theta)d\mathbf X.
-\end{equation}
 For any choice of distribution defined over the latent variables, $q(\mathbf X)$, the following decomposition holds
 \begin{equation}\label{eq:EM-loglikelihooddecomposition}
- \ln~p(\mathbf Y\mid\boldsymbol\Theta)=\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p),
+ \ln~p(\mathbf Y;\boldsymbol\Theta)=\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p),
 \end{equation}
@@
  \mathcal{L}(q,\boldsymbol\Theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \label{eq:EM-decomposition1}\\
-\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
-\end{align}
-Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$ in \eqref{eq:EM-decomposition1} after noting that $q(\mathbf X)$ is a normalised distribution that integrates to one.
-Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$ and $q(\mathbf X)$ and as a distance it is always non-negative, $\mathrm{KL}(q\parallel p)\ge 0$, with equality if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
-It therefore follows from \eqref{eq:EM-loglikelihooddecomposition} that $\mathcal{L}(q,\boldsymbol\Theta)\le \ln~p(\mathbf Y\mid\boldsymbol\Theta)$, in other words \eqref{eq:EM-decomposition1} is a lower bound on the log-likelihood function.
+\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
+\end{align}
+Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$ in \eqref{eq:EM-decomposition1} giving
+\begin{align}
+	\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)p(\mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \nonumber\\
+	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X\nonumber\\
+	&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)d\mathbf X.
+\end{align}
+Noting  $q(\mathbf X)$ is a normalised distribution that integrates to one gives the log-likelihood function.
+Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$ and $q(\mathbf X)$, therefore,
+\begin{equation}
+	\mathrm{KL}(q\parallel p)\ge 0.
+\end{equation}   
+The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
+It follows from equation \eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\Theta)$ is a lower bound on the log-likelihood function, i.e.
+\begin{equation}
+ \mathcal{L}(q,\boldsymbol\Theta)\le \ln~p(\mathbf Y\mid\boldsymbol\Theta)
+	\end{equation}
+
 The EM algorithm alternates between maximising the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\Theta$, respectively, while holding the other fixed.

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
aded bullet points for the EM algorithm

@@
 \end{align}
-
+\parham{
+ \begin{itemize}
+	\item when likelihood is difficult to maximise directly (when we have hidden variable) so we maximise the joint likelihood function 
+	\item EM maximises the lower bound and show what exactly this lower bound is (shown in Appendix).
+	\item E-step for state-space model is the smoothing problem
+	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case
+\end{itemize}}
 The linear state-space representation of the MRAIDE allows the use of the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
@@
 \subsection{Lower bound on likelihood function}
-A derivation of the lower bound that is based on \cite{Bishop2006} is provided in this Appendix.
+A derivation of the lower bound on the likelihood function that is based on \cite{Bishop2006} is provided in this Appendix.
 Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\Theta$.
@@
 Suppose that the current estimate of the parameter set is $\boldsymbol\Theta'$, in the E-step the lower bound is maximised with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\Theta'$ is fixed.
-Since the value of $p(\mathbf Y;\boldsymbol\Theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the Kullback-Liebler distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
+Since the value of $p(\mathbf Y;\boldsymbol\Theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the KL distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
 At this point, the lower bound becomes equal to the log-likelihood function.
+Note in statespace model the E-step is equiavalent to the smoothing problem.
 The maximum in the M-step is obtained by maximising the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.

### 2012-01-19 Multiresolution_framework/ltx/manuscript.tex
added bullet point for the EM

@@
 	\item E-step for state-space model is the smoothing problem
-	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case
+	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case so DCM is rubbish
 \end{itemize}}

### 2012-01-20 Multiresolution_framework/ltx/manuscript.tex
general edits

@@
 B-spline wavelet and scaling functions approach optimal time/frequency localisation as the order of the spline increases.
-In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate then other wavelets with the same number of vanishing moments \cite{Unser1999}.
+In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \cite{Unser1999}.
 
@@
 \begin{align}
-N_{4}\left(r\right)=
+3!N_{4}\left(r\right)=
 \begin{cases}
@@
  \end{equation}
+  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} Bspline wavelets are semiorthogonal as they are not orthogonal with respect to translation on a given scale.}
 
@@
 	\begin{tabular}{lcccc}
- & $k$& $7!N_{8}\left(k\right)$ & $11!N_{12}\left(k\right)$\\ \hline\hline
- & 1  & $1$ & $1$\\
- & 2  & $120$ & $2,036$\\
- & 3  & $1,191$ & $152,637$\\
- & 4  & $2,416$ & $2,203,488$\\
- & 5  & $\space$ & $9,738,114$\\
- & 6  & $\space$ & $15,724,248$
+	\hline \hline
+	& $k$ & $3!N_{4}\left(k\right)$ & $7!N_{8}\left(k\right)$ & $11!N_{12}\left(k\right)$\\ 
+	\hline 
+	& 1 & $1$ & $1$ & $1$\\
+	& 2 & $4$ & $120$ & $2,036$\\
+	& 3 & $\space$ & $1,191$ & $152,637$\\
+	& 4 & $\space$ & $2,416$ & $2,203,488$\\
+	& 5 & $\space$ & $\space$ & $9,738,114$\\
+	& 6 & $\space$ & $\space$ & $15,724,248$\\
+	\hline \hline
 	\end{tabular}

### 2012-01-22 Multiresolution_framework/ltx/manuscript.tex
edit to EM algorithm, discussion and added plots for model components

@@
 The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
-The latter,  can be used to model spiking statistics across spatial scales from single neurons (where is can be considered a CDF of the probability of firing) to mean firing rates of neural masses.} The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
+The latter,  can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a CDF of the probability of firing) to mean firing rates of neural masses.} The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
 
@@
 \end{equation}
-where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location with the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
+where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location \parham{with} the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
 
@@
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
+The components of the model are shown in Figure~\ref{fig:Modelcomponents}
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=.6]{./Graph/ConnectivityKernel.pdf}
+\includegraphics[scale=.6]{./Graph/Synaptickernel.pdf}
+\includegraphics[scale=.6]{./Graph/Sigmoid.pdf}
+\caption{ {\bf The IDE neural field model components}.
+(\textbf{a}) The mexican hat connectivity kernel.
+(\textbf{b}) First order synaptic kernel.
+(\textbf{c}) A representative of the activation function.}
+\label{fig:Modelcomponents}
+\end{figure}
+
  The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covariance function 
@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, j, and can be chosen such that the basis functions cover the spatial range.
+The number of scales depends on the spatial characteristics of the field which will be described later.}Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
 
@@
 Figure~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero.
+Note in general the supports of the scaling and wavelet functions are given by
+\begin{align}
+	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \\  
+  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right] 
+	\end{align} 
 \begin{figure}[!t]
@@
 \end{itemize}}
-The linear state-space representation of the MRAIDE allows the use of the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel and the field from electrophysiological data.
+The problem of joint state and parameter estimation for the state-space model given by () can be formulated as 
+\begin{equation}
+	{\hat{\mathbf X},\hat{\boldsymbol\theta}}=\arg\max_{\mathbf X,\boldsymbol\theta}p(\mathbf Y;\boldsymbol\theta),
+ \end{equation}  
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations at all time, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
+This problem cannot be solved separately as for the state estimation we need the parameter of the system and for parameter estimation the state of the system should be known.
+One approach is to iteratively solve the state and parameter of the system, a natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel (parameter set) and the field (states) from electrophysiological data (obsrevations).
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
  \end{equation}   
- %We use the standard EM algorithm for linear dynamic systems \cite{Shumway2000} and hence only describe aspects of the algorithm that are specific to MRA neural field equations.
 and the posterior distribution of the field over time.
-Here $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the entire sequence of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
-The goal of the EM algorithm is to maximise  the likelihood function in the presence of the hidden variables, the weights of the field basis functions in this case.
-The EM finds increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-By exploiting the total probability rule it is rather straightforward to show that
+There are two main applications of the EM algorithm.
+The first is when the observations are incomplete due to a faulty observation process or limitations.
+The second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables, the weights of the field basis functions in this case \cite{Bilmes1998}.
+
+Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
+For state-space model the E step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For the M-step the lower bound on the likelihood function should be constructed, the steps needed
+to compute the required quantities are very dependent on the particular application which is described in detail for our problem.
+In summary, to solve the joint state and parameter estimation for the state space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
+A schematic representation of the EM algorithm is represented in Figure
+
+It is rather straightforward to show that 
 \begin{equation}
@@
 is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations.
-....
+
  The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
@@
  \end{align}   
-% where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes the expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \Theta') $ and $\boldsymbol \Theta'$ is the current parameter estimate maximising $p(\mathbf Y;\boldsymbol\theta)$.
 It should be noted that neither $p(\mathbf y_{t+1}|\mathbf x_{t+1})$ nor $p(\mathbf x_0)$ are functions of the parameter set and therefore the $\mathcal Q$-function can be rewritten as
@@
 While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.
-Additional avenues for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, and time delays according to spatial resolutions.
-The estimation techniques should also be extended to deal with spatiotemporal heterogeneity in the kernel.
+
+Additional extension for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, The second order postsynaptic kernel proposed in \cite{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
+
+Another extension of this framework is the inclusion of finite distant-dependant action potential propagation velocity into the parametric neural field equations.
+In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks.
+For instance, it is shown by \cite{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
 Finally, future work should be directed towards applying and validating the framework on real data.

### 2012-01-22 Multiresolution_framework/ltx/manuscript.tex
added E and M subsections
edits to the E-step

@@
 A schematic representation of the EM algorithm is represented in Figure
-
+  \subsection{E-step}
+  As mentioned earlier the E-step for the state-space models is equivalent to the smoothing problem.
+We use the RTS smoother in order to infer the state of the system.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$.
+Following \cite{Gibsona2005} the RTS Smoother, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
+Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates and covariance matrices, and also the final value of the Kalman gain in order to initialise the cross-covariance calculations.
+ \subsection{M-step}
 It is rather straightforward to show that 

### 2012-01-22 Multiresolution_framework/ltx/manuscript.tex
changed my email
edits to EM algorithm

--- 2012-01-22 Multiresolution_framework/ltx/manuscript.tex
@@
 Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K.
-(e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
+(e-mail:parham.aram@univ-amu.fr; visakan@sheffield.ac.uk).}% <-this % stops a space
 \thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
@@
 where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations at all time, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
-This problem cannot be solved separately as for the state estimation we need the parameter of the system and for parameter estimation the state of the system should be known.
-One approach is to iteratively solve the state and parameter of the system, a natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the kernel (parameter set) and the field (states) from electrophysiological data (obsrevations).
+This problem cannot be separated as for the state estimation the knowledge of the system's parameter is required and for the parameter estimation the states of the system need to be known.
+One approach is to iteratively solve the state and parameter of the system and monitor the convergence of the estimates.
+A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from observations corresponding to the connectivity kernel, neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or limitations and the second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
 The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
 and the posterior distribution of the field over time.
-There are two main applications of the EM algorithm.
-The first is when the observations are incomplete due to a faulty observation process or limitations.
-The second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables, the weights of the field basis functions in this case \cite{Bilmes1998}.
 
@@
 A schematic representation of the EM algorithm is represented in Figure
-
+  \subsection{E-step}
+  As mentioned earlier the E-step for the state-space models is equivalent to the smoothing problem.
+We use the RTS smoother in order to infer the state of the system.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$.
+Following \cite{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
+Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates and covariance matrices, and also the final value of the Kalman gain in order to initialise the backward cross-covariance computation.
+ \subsection{M-step}
 It is rather straightforward to show that 

### 2012-01-22 Multiresolution_framework/ltx/manuscript.tex
added partition unity property of Bsplines

@@
 \end{align}
+\parham{One important feature of B-spline is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
+\begin{equation}
+	\sum_{l}N_m(r+l)\equiv1
+	\end{equation}
+	This is important as the underlying field can be reconstructed in saturation without introducing numerical errors which is not the case for example in the case of Gaussian basis functions. }
+
 The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$, $\boldsymbol\Gamma$ and $\boldsymbol\Sigma_w$).

### 2012-01-23 Multiresolution_framework/ltx/manuscript.tex
added block diagram for the EM algorithm
minor edits

@@
 In summary, to solve the joint state and parameter estimation for the state space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
-A schematic representation of the EM algorithm is represented in Figure
+A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=1]{./Graph/EMBlockDiagram.pdf}
+\caption{{\bf Schematic of the EM algorithm}.
+The RTS smoother (E-step) and the maximisation of the lower bound (M-step) are shown.
+The dashed box shows the iterative two step algorithm once it is initialised.}
+\label{fig:EMBlockDiagram}
+\end{figure}
   \subsection{E-step}

### 2012-01-23 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations.
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\Theta'$ i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
+Note that this is actually the smoother output.
 

### 2012-01-23 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space model the E step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
-For the M-step the lower bound on the likelihood function should be constructed, the steps needed
+For state-space model the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For the M-step the lower bound on the likelihood function should be constructed where the steps needed
 to compute the required quantities are very dependent on the particular application which is described in detail for our problem.
-In summary, to solve the joint state and parameter estimation for the state space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
+In summary, to solve the joint state and parameter estimation for the state-,space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
 A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
@@
 \caption{{\bf Schematic of the EM algorithm}.
-The RTS smoother (E-step) and the maximisation of the lower bound (M-step) are shown.
+The RTS smoother (E-step) and the maximisation of the lower bound, $\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')$, (M-step) are shown.
 The dashed box shows the iterative two step algorithm once it is initialised.}
@@
 We use the RTS smoother in order to infer the state of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates $\hat{\mathbf x}_t$ and covariance, $\hat{\mathbf P}_t=\mathrm{cov}(\hat{\mathbf{x}}_t)$.
 Following \cite{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.

### 2012-01-23 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{itemize}}
-The problem of joint state and parameter estimation for the state-space model given by () can be formulated as 
+The problem of joint state and parameter estimation for the state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} can be formulated as 
 \begin{equation}

### 2012-01-23 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{align}
-\parham{One important feature of B-spline is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
+\parham{One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
 \begin{equation}

### 2012-01-24 Multiresolution_framework/ltx/manuscript.tex
small edit to IDE neural field model section to generalise it

@@
 \section{Multi-Resolution Cortical Architecture}
-The human neocortex has an inherent multi-resolution architecture. On finer scales... where any measurable spatiotemporal neural field can be written as 
+The human neocortex has an inherent multi-resolution architecture. The spatiotemporal neural field can be written as 
 \begin{equation}
@@
 \end{equation}
-where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location \parham{with} the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
-
-This multi-resolution structure has been described by numerous methods \cite{Wilson1973}.
-This idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths.
+where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location within the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
+
+This multi-resolution structure has been described by numerous methods.
+For example, this idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \cite{Wilson1973}.
 
@@
 The solution to this problem was proposed by \cite{Breakspear2005} in using a wavelet decomposition.
+This paper is directed at developing a framework for patient-specific multi-resolution neural field models.
 \begin{figure}[t]
@@
 \section{IDE Neural Field Model}
-
 \singlespacing
@@
 
+The neural field model in the most general form is described by the equation
+\begin{equation}
+	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{field} =
+	\int_{-\infty}^t 
+	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
+	\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
+	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
+\end{equation}
+where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted by $v_t\left(\mathbf r\right)$, $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity.
+These are shown in Figure~\ref{fig:Modelcomponents}.
+Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.
+These are also shown in Figure~\ref{fig:Modelcomponents}.
+
 The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
@@
 \end{equation}
-where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$.
-Membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time.
-The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
+where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time.
+% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
very minor edit
edits to EM algorithm

@@
 \begin{equation}
-	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{field} =
+	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
 	\int_{-\infty}^t 
@@
 \end{align} 
-\parham{
- \begin{itemize}
-	\item when likelihood is difficult to maximise directly (when we have hidden variable) so we maximise the joint likelihood function 
-	\item EM maximises the lower bound and show what exactly this lower bound is (shown in Appendix).
-	\item E-step for state-space model is the smoothing problem
-	\item so when we have joint state parameter estimation for stae-space models  we only need to do two things: 1- use smoother for the E-step 2- construct the lower bound which might not be straightforward even in linear case so DCM is rubbish
-\end{itemize}}
 The problem of joint state and parameter estimation for the state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} can be formulated as 
@@
  \end{equation}  
-where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations at all time, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
-This problem cannot be separated as for the state estimation the knowledge of the system's parameter is required and for the parameter estimation the states of the system need to be known.
-One approach is to iteratively solve the state and parameter of the system and monitor the convergence of the estimates.
-A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from observations corresponding to the connectivity kernel, neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or limitations and the second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
-The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations, $\mathbf Y$, parameterised  by $\boldsymbol\theta$, known as the likelihood function.
+This problem cannot be solved separately as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
+One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
+A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second  when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm, when used in the latter context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
 \begin{equation}
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space model the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
-For the M-step the lower bound on the likelihood function should be constructed where the steps needed
+For state-space models, the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For the M-step, a lower bound on the likelihood function should be constructed where the steps needed
 to compute the required quantities are very dependent on the particular application which is described in detail for our problem.
-In summary, to solve the joint state and parameter estimation for the state-,space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
+
+In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
 A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
@@
   \subsection{E-step}
-  As mentioned earlier the E-step for the state-space models is equivalent to the smoothing problem.
-We use the RTS smoother in order to infer the state of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates $\hat{\mathbf x}_t$ and covariance, $\hat{\mathbf P}_t=\mathrm{cov}(\hat{\mathbf{x}}_t)$.
-Following \cite{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
-Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates and covariance matrices, and also the final value of the Kalman gain in order to initialise the backward cross-covariance computation.
+  As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem.
+We use the RTS smoother in order to infer the states of the system.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximised in the M-step.
+Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\mathbf{x}_t^{f-}$, $\mathbf{x}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialise the backward cross-covariance computation.
  \subsection{M-step}
@@
 \begin{equation}
-	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right], 
-\end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\Theta'$ i.e.
-$p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
+	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right], 
+\end{equation}
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
 Note that this is actually the smoother output.
@@
  The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
-The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as
+The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
  \begin{equation}\label{eq:jointdistribution}
-  p(\mathbf X,\mathbf Y;\boldsymbol \Theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
+  p(\mathbf X,\mathbf Y;\boldsymbol \theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
  \end{equation}
@@
 \end{align}
-Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximised for the optimal parameter estimates. Therefore 
+Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximised for the optimal parameter estimates.
+Note that the expectation distributes over the trace sum.
+Therefore,
 \begin{align}\label{eq:MRA-QintermsofTraces}
@@
 \end{align}
-Note that the expectation distributes over the trace sum.
-The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
-To begin, the first trace is written in terms of element-wise summations
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see Appendix~ for more details)
+\begin{align}\label{eq:Xivariables}
+\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+\end{align}
+
+The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
 \begin{align}\label{eq:MRA-trace1}
@@
 
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$ \cite{Gibsona2005},
-\begin{align}\label{eq:Xivariables}
-\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
-\end{align}
 The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
added a section for stopping criterion

@@
 
-The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
 The EM algorithm iterates between these two steps until the parameter estimates converge.
@@
  \end{algorithm}
+\subsection{Stopping rule}
 The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
edit to model derivation and changed reference style

--- 2012-01-24 Multiresolution_framework/ltx/manuscript.tex
@@
 \fi
+
+\usepackage{natbib}
 
@@
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-\parham{Examples are, the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \cite{Jirsa1997}.
+\parham{Examples are, the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1997}.
 The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
@@
 
-The first work describing data-driven mesoscopic neural modelling used a neural mass model to fit EEG data~\cite{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modelling (DCM)~\cite{David2003}.
-Following this work, data-driven modelling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}.
+The first work (to the authors best knowledge) describing data-driven mesoscopic neural modelling used a neural mass model to fit EEG data~\citep{Valdes1999}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modelling (DCM)~\citep{David2003}.
+Following this work, data-driven modelling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
+Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location within the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
-
-This multi-resolution structure has been described by numerous methods.
-For example, this idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \cite{Wilson1973}.
-
-Typically, the experimentalist only has access the net field generated by the multi-resolution architecture.
-Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
-The solution to this problem was proposed by \cite{Breakspear2005} in using a wavelet decomposition.
-This paper is directed at developing a framework for patient-specific multi-resolution neural field models.
+This multi-resolution structure is depicted in Figure~\ref{fig:MultiLayerFieldModel}.
 \begin{figure}[t]
@@
 \end{figure}
+
+The multi-resolution structure has been described by numerous methods.
+For example, this idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \citep{Wilson1973}.
+
+Typically, the experimentalist only has access the net field generated by the multi-resolution architecture.
+Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
+The solution to this problem was proposed by \citet{Breakspear2005} in using a wavelet decomposition.
+This paper is directed at developing a framework for patient-specific multi-resolution neural field models.
 
@@
 
-The neural field model in the most general form is described by the equation
-\begin{equation}
-	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{field} =
+The single layer homogeneous neural field model in the most general form is described by the equation
+\begin{equation}
+	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
 	\int_{-\infty}^t 
 	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
-	\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
+	\theta\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
 	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
@@
 \end{equation}
-where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted by $v_t\left(\mathbf r\right)$, $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$.
+The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively.
 There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity.
@@
 These are also shown in Figure~\ref{fig:Modelcomponents}.
+The form of $w(\mathbf{r})$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field.
+By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
+In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Figure~\ref{fig:Modelcomponents}.
 
@@
 \section{MRA of the IDE in State-Space}
-\dean{The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
-Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.}
+The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.
 
@@
 
-The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
+The multi-resolution approximation \citep{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$.
 Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, j, and can be chosen such that the basis functions cover the spatial range.
-The number of scales depends on the spatial characteristics of the field which will be described later.}Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain.
+The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
 
@@
 where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
-\dean{The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
-}
+\dean{The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.}
 
@@
 \end{align}
-where $k = j_0,j$.\dean{ARE THESE EACH $n_{\theta}$ or $n_x$ DIMENSIONAL VECTORS?} Following this we can define the \dean{vectors or matrices} 
+where $k = j_0,j$. Following this we can define the \dean{vectors} 
 \begin{align}
@@
 \end{equation}
-with covariance (see \cite{Freestone2011} for proof)
+with covariance (see \citep{Freestone2011} for proof)
 \begin{equation}\label{eq:CovMatrix}
@@
 These functions are composed of piecewise polynomials combined smoothly at some breaking points (knots), which are equally spaced in the case of cardinal B-splines.
-The degree of smoothness is determined by the order of splines \cite{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
+The degree of smoothness is determined by the order of splines \citep{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
 \begin{figure}[!t]
@@
 
-B-spline wavelet and scaling functions were formulated independently by Chui and Wang, and Unser et al \cite{Chui1992b,Chui1992,Unser1993}.
+B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.
 The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
 B-spline wavelet and scaling functions approach optimal time/frequency localisation as the order of the spline increases.
-In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \cite{Unser1999}.
+In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \citep{Unser1999}.
 
@@
 
-The $m$-th  order cardinal B-spline function is defined by the recurrence relation \cite{Chui1992} 
+The $m$-th  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
 \begin{equation}
@@
 \end{equation}
-Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \cite{DeBoor2001}
+Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citep{DeBoor2001}
 \begin{equation}\label{eq:MRA-DoBoorFormula}
@@
  \end{align}
-and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \cite{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}
+and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \citep{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}
 
@@
 By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} can be computed analytically.
-In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}:
+In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}:
 \begin{equation}
@@
 	\end{tabular}
- \caption {{\bf Cardinal B-Splines at the knot sequence}. Table entries are calculated using \eqref{eq:MRA-recursiveBsplineatintegerpoints} and can be also found in \cite{Goswami1999}.} 
+ \caption {{\bf Cardinal B-Splines at the knot sequence}. Table entries are calculated using \eqref{eq:MRA-recursiveBsplineatintegerpoints} and can be also found in \citet{Goswami1999}.} 
  \label{table:MRA-BsplineatIntegerPoints}
@@
  \end {table}
+
 \subsection{Frequency Analysis}
@@
 One approach is to iteratively solve the state and parameter of the system and monitor the convergence of the estimates.
-A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from observations corresponding to the connectivity kernel, neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or limitations and the second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
-The EM algorithm, when used in this context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from observations corresponding to the connectivity kernel, neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or limitations and the second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \citep{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm, when used in this context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
 \begin{equation}
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space model the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For state-space model the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \citep{RAUCH1965}.
 For the M-step the lower bound on the likelihood function should be constructed where the steps needed
@@
 We use the RTS smoother in order to infer the state of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates $\hat{\mathbf x}_t$ and covariance, $\hat{\mathbf P}_t=\mathrm{cov}(\hat{\mathbf{x}}_t)$.
-Following \cite{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
+The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates $\hat{\mathbf x}_t$ and covariance, $\hat{\mathbf P}_t=\mathrm{cov}(\hat{\mathbf{x}}_t)$.
+Following \citet{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
 Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates and covariance matrices, and also the final value of the Kalman gain in order to initialise the backward cross-covariance computation.
@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\Theta'$ i.e.
+is a lower bound on the log-likelihood function \citep{Bishop2006} (see Appendix~\ref{ap:MStep})  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\Theta'$ i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
@@
 \end{equation}
-All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \cite{Dewar2009}.
-The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \cite{Dewar2009} is also identified.
+All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
+The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
 \begin {table}
@@
 \hline \hline
-Variable &Equation&Order&Order obtained from \cite{Dewar2009}\\ \hline\\
+Variable &Equation&Order&Order obtained from \citet{Dewar2009}\\ \hline\\
 $\Xi_0, \Xi_1$&\eqref{eq:MRA-Xi0}, \eqref{eq:MRA-Xi1}&$O(Tn_x^2)$& -\\
@@
 \end{tabular}}
- \caption {{\bf The Computational complexity of the estimation algorithm}. A comparison between the algorithm proposed herein and that of \cite{Dewar2009}.} 
+ \caption {{\bf The Computational complexity of the estimation algorithm}. A comparison between the algorithm proposed herein and that of \citet{Dewar2009}.} 
 \label{table:MRA-ComputationalComplexity}
@@
 \end{equation}
-The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\cite{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorisation operator.
+The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\citep{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorization operator.
 Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
 
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \cite{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$ \cite{Gibsona2005},
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \citep{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$ \citep{Gibsona2005},
 \begin{align}\label{eq:Xivariables}
@@
  \end{algorithm}
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
 \begin{equation}
@@
  \end{equation}
- where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \cite{Meyer2000}
+ where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \citet{Meyer2000}
  \begin{equation}
@@
 To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
-In doing so, the membrane time constant was set to $\tau = 10$~ms \cite{David2003}, and the sampling time was chosen ten times faster \cite{Stephan2008}, i.e.
+In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
@@
 The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\gamma(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
-The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \cite{Wendling2005}.
+The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
 The observation kernel was modelled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
@@
 The spatial frequency response of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
+This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
 The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-NmFouriertransform}.
@@
 \end{figure}
+
 \subsection{Experiment II}
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-It is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009,Breakspear2005}.
+It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005}.
 %\dean{This is a test to see if we can fit something about Breaky's paper in here.
@@
 For a larger space or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
-One solution to this problem could be expectation-conditional maximisation (ECM) \cite{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
-The ECM is a class of generalised EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximised \cite{Fessler1994}.
-
-For systems with a high number of states, the ensemble Kalman smoother (EnKS) \cite{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
+One solution to this problem could be expectation-conditional maximisation (ECM) \citep{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
+The ECM is a class of generalised EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximised \citep{Fessler1994}.
+
+For systems with a high number of states, the ensemble Kalman smoother (EnKS) \citep{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
 The EnKS is a sequential Monte Carlo (MC) method where the state covariance matrix is approximated by a large stochastic ensemble of model states, thus alleviating computational load due to the storage and forward integration of the state covariance matrix.
@@
 global (local) maximum or a saddle point.
-If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \cite{McLachlan1997}.
+If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}.
 In general, convergence of the EM algorithm to any stationary point depends on the initialisation.
@@
 
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005}.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}.
 % \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
@@
 % In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.
-An assumption was made where the firing rate behaves linearly.
+
+To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly.
 The implementation of the framework in the non-linear case can be addressed as future work.
@@
 The reconstruction of the neural field requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
-For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \cite{Meyer1992}.
+For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}.
 In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations.
@@
 
-Additional extension for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, The second order postsynaptic kernel proposed in \cite{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
+Additional extension for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
 
@@
 In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks.
-For instance, it is shown by \cite{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
+For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
 Finally, future work should be directed towards applying and validating the framework on real data.
+
 \section{Appendix}
@@
 Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
-\subsection{Lower bound on likelihood function}
-A derivation of the lower bound on the likelihood function that is based on \cite{Bishop2006} is provided in this Appendix.
+
+\subsection{Lower bound on likelihood function}\label{ap:MStep}
+A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
 Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\Theta$.
@@
 At this point, the lower bound becomes equal to the log-likelihood function.
-Note in statespace model the E-step is equiavalent to the smoothing problem.
+Note in the state-space model the E-step is equivalent to the smoothing problem.
 The maximum in the M-step is obtained by maximising the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
@@
 % \bibliographystyle{unsrt} 
-% \bibliography{MRAIDE}
-
-\bibliographystyle{IEEEtran}
+\bibliographystyle{apalike}
+\bibliography{MRAIDE}
+
+% \bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
- \bibliography{IEEEabrv,MRAIDE}
+ % \bibliography{IEEEabrv,MRAIDE}
 

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex

@@
  \end{equation}  
-where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations at all time, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of observations $\mathbf Y$ parameterised  by $\boldsymbol\theta$ known as the likelihood function.
-This problem cannot be separated as for the state estimation the knowledge of the system's parameter is required and for the parameter estimation the states of the system need to be known.
-One approach is to iteratively solve the state and parameter of the system and monitor the convergence of the estimates.
-A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from observations corresponding to the connectivity kernel, neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or limitations and the second is the case when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \citep{Bilmes1998}, the weights of the field basis functions in this case.
-The EM algorithm, when used in this context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations, $\mathbf Y$, parameterised  by $\boldsymbol\theta$, known as the likelihood function.
+This problem cannot be solved separately as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
+One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
+A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second  when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm, when used in the latter context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
 \begin{equation}
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space model the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \citep{RAUCH1965}.
-For the M-step the lower bound on the likelihood function should be constructed where the steps needed
+For state-space models, the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For the M-step, a lower bound on the likelihood function should be constructed where the steps needed
 to compute the required quantities are very dependent on the particular application which is described in detail for our problem.
-In summary, to solve the joint state and parameter estimation for the state-,space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
+
+In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
 A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
@@
   \subsection{E-step}
-  As mentioned earlier the E-step for the state-space models is equivalent to the smoothing problem.
-We use the RTS smoother in order to infer the state of the system.
-The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: state estimates $\hat{\mathbf x}_t$ and covariance, $\hat{\mathbf P}_t=\mathrm{cov}(\hat{\mathbf{x}}_t)$.
-Following \citet{Gibsona2005}, an additional backwards recursion is included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required to construct the lower bound.
-Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates and covariance matrices, and also the final value of the Kalman gain in order to initialise the backward cross-covariance computation.
+  As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem.
+We use the RTS smoother in order to infer the states of the system.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximised in the M-step.
+Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\mathbf{x}_t^{f-}$, $\mathbf{x}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialise the backward cross-covariance computation.
  \subsection{M-step}
@@
 \begin{equation}
-	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right], 
-\end{equation}
-is a lower bound on the log-likelihood function \citep{Bishop2006} (see Appendix~\ref{ap:MStep})  where $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\Theta'$ i.e.
-$p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
+	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right], 
+\end{equation}
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
 Note that this is actually the smoother output.
@@
 
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the Rauch Tung Streibel smoother \citep{RAUCH1965} outputs: state estimates, $\hat{\mathbf x}_t$, covariance, $\mathbf P_t=\mathrm{cov}(\mathbf{x_t})$, and cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$ \citep{Gibsona2005},
-\begin{align}\label{eq:Xivariables}
-\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
-\end{align}
-The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$.
+The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
 The EM algorithm iterates between these two steps until the parameter estimates converge.
@@
  \end{algorithm}
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
+\subsection{Stopping rule}
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
 \begin{equation}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
added appendix for smoother

--- 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
@@
 It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.
+\section{Calculating $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}
+The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
+The expression for  $\Xi_{0}$ as defined in equation~\ref{eq:defofXi0} of the main text is given by
+\begin{equation}\label{eq:Xi0}
+ \Xi_1=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t+1}\mathbf x_{t+1}^\top\right].
+\end{equation}
+We start by expanding the covariance matrix as following
+\begin{align}
+ \mathbf P_{t}&=\mathbf E_{\theta'}\left[(\mathbf x_{t}-\mathbf{\hat x}_{t})(\mathbf x_{t}-\mathbf{\hat x}_{t})^\top\right] \nonumber \\
+&=\mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]-\mathbf E_{\Theta'}\left[\mathbf x_{t}\mathbf{\hat x}_{t}^\top\right]-\mathbf E_{\theta'}\left[\mathbf{\hat x}_{t}\mathbf x_{t}^\top\right]+\mathbf E_{\theta'}\left[\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right] \nonumber \\
+&=\mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]-\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top-\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top \nonumber \\
+&=\mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]-\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
+\end{align}
+therefore we can write
+\begin{equation}\label{eq:Xi0derivation1}
+ \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
+\end{equation}
+substituting \ref{eq:Xi0derivation1} in \ref{eq:Xi0} we get
+\begin{equation}
+ \Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
+\end{equation}
+To calculate $\Xi_0$, from equation~\ref{eq:defofXi1} of the main text we have
+\begin{equation}\label{eq:Xi1}
+ \Xi_0=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right].
+\end{equation}
+An expression for $\Xi_1$ in terms of the smoothed states can be also found in a similar way by expanding the cross-covariance matrix,
+\begin{align}
+ \mathbf M_{t+1}&=\mathbf E_{\Theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1})^\top\right] \nonumber \\
+&=\mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
+\end{align}
+therefore we can write
+\begin{equation}\label{eq:Xi1derivation1}
+ \mathbf E_{\Theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
+\end{equation}
+substituting \ref{eq:Xi1derivation1} in \ref{eq:Xi1} we get
+\begin{equation}
+ \Xi_1=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
+\end{equation}
 

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
edits to Xi appendix

--- 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
@@
 The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see Appendix~ for more details)
-\begin{align}\label{eq:Xivariables}
-\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).
+\begin{align}
+\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:Xi0} \\
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).  \label{eq:Xi1}
 \end{align}
@@
 It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.
-
+\section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}
+The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
+The expression for  $\boldsymbol\Xi_{0}$ as defined in equation~\eqref{eq:Xi0} of the main text is given by
+   \begin{equation}\label{eq:appXi0}
+	 \boldsymbol\Xi_0=\mathbf E_{\theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right].
+	\end{equation}                                                                                                
+	We start by expanding the equation \eqref{eq:appXi0}, giving
+
+\begin{align}\label{eq:Xi0derivation0} 
+ \mathbf M_{t+1}&=\mathbf E_{\theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1})^\top\right] \nonumber \\
+&=\mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\mathbf x_t\hat{\mathbf x}_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\mathbf x_{t+1}^\top\right]+\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\right]  \nonumber \\
+&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top+\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\nonumber \\
+&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top.
+\end{align}
+Rearranging  equation \eqref{eq:Xi0derivation0} we get
+\begin{equation}\label{eq:Xi0derivation1}
+ \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
+\end{equation}
+substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum we get
+\begin{equation}
+ \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
+\end{equation}   
+An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by expanding the covariance matrix,
+\begin{equation}\label{eq:appXi1}
+ \boldsymbol\Xi_1=\mathbf E_{\theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t}\mathbf x_{t}^\top\right],
+\end{equation}
+therefore we can write
+\begin{equation}\label{eq:Xi1derivation1}
+ \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
+\end{equation}
+substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
+\begin{equation}
+ \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
+\end{equation}
 \ifCLASSOPTIONcaptionsoff

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
edits to lower bound appendix

@@
 A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
-Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\Theta$.
+Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\theta$.
 We want to maximise the likelihood function which is difficult to maximise directly
 \begin{equation}
- p(\mathbf Y;\boldsymbol\Theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\Theta)d\mathbf X.
+ p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)d\mathbf X.
 \end{equation}   
@@
 \begin{equation}\label{eq:EM-loglikelihooddecomposition}
- \ln~p(\mathbf Y;\boldsymbol\Theta)=\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p),
+ \ln~p(\mathbf Y;\boldsymbol\theta)=\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p),
 \end{equation}
@@
 \begin{align}
- \mathcal{L}(q,\boldsymbol\Theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \label{eq:EM-decomposition1}\\
-\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
-\end{align}
-Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$ in \eqref{eq:EM-decomposition1} giving
-\begin{align}
-	\mathcal{L}(q,\boldsymbol\Theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)p(\mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \nonumber\\
-	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)}{q(\mathbf X)} \right\rbrace d\mathbf X\nonumber\\
+ \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \label{eq:EM-decomposition1}\\
+\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
+\end{align}
+Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in \eqref{eq:EM-decomposition1} giving
+\begin{align}
+	\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \nonumber\\
+	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X\nonumber\\
 	&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)d\mathbf X.
@@
 Noting  $q(\mathbf X)$ is a normalised distribution that integrates to one gives the log-likelihood function.
-Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$ and $q(\mathbf X)$, therefore,
+Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$, therefore,
 \begin{equation}
@@
 \end{equation}   
-The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
-It follows from equation \eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\Theta)$ is a lower bound on the log-likelihood function, i.e.
-\begin{equation}
- \mathcal{L}(q,\boldsymbol\Theta)\le \ln~p(\mathbf Y\mid\boldsymbol\Theta)
-	\end{equation}
-
-The EM algorithm alternates between maximising the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\Theta$, respectively, while holding the other fixed.
-Suppose that the current estimate of the parameter set is $\boldsymbol\Theta'$, in the E-step the lower bound is maximised with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\Theta'$ is fixed.
-Since the value of $p(\mathbf Y;\boldsymbol\Theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the KL distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$.
+The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
+It follows from equation \eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\theta)$ is a lower bound on the log-likelihood function, i.e.
+\begin{equation}
+ \mathcal{L}(q,\boldsymbol\theta)\le \ln~p(\mathbf Y\mid\boldsymbol\theta)
+	\end{equation}
+
+The EM algorithm alternates between maximising the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
+Suppose that the current estimate of the parameter set is $\boldsymbol\theta'$, in the E-step the lower bound is maximised with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\theta'$ is fixed.
+Since the value of $p(\mathbf Y;\boldsymbol\theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the KL distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
 At this point, the lower bound becomes equal to the log-likelihood function.
@@
 The maximum in the M-step is obtained by maximising the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
-Since the distribution $q(\mathbf X)$ is computed using the old parameter estimates and kept fixed during the M-step, it is not equal to $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta)$, resulting in a non-zero KL distance.
+Since the distribution $q(\mathbf X)$ is computed using the old parameter estimates and kept fixed during the M-step, it is not equal to $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$, resulting in a non-zero KL distance.
 Therefore, the growth of the log-likelihood function is greater than the growth of the lower bound.
-Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\Theta')$ for $q(\mathbf X)$ in \eqref{eq:EM-decomposition1} gives
-\begin{align}
- \mathcal{L}(q,\boldsymbol\Theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\Theta')~d\mathbf X \nonumber \\
-&= \mathbf E_{\boldsymbol\Theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)\right] +\mathrm{const.}\nonumber\\
-&=\mathcal{Q}(\boldsymbol\Theta,\boldsymbol\Theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
-\end{align}
-where $ \mathbf E_{\boldsymbol \Theta'}\left[ .\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
-$p(\mathbf X\mid\mathbf Y;\boldsymbol \Theta'$).
-The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\Theta$.
+Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta')$ for $q(\mathbf X)$ in \eqref{eq:EM-decomposition1} gives
+\begin{align}
+ \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')~d\mathbf X \nonumber \\
+&= \mathbf E_{\boldsymbol\theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)\right] +\mathrm{const.}\nonumber\\
+&=\mathcal{Q}(\boldsymbol\theta,\boldsymbol\theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
+\end{align}
+where $ \mathbf E_{\boldsymbol \theta'}\left[ \cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
+The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\theta$.
 It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 In general, convergence of the EM algorithm to any stationary point depends on the initialisation.
-In the examples presented in this chapter, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
+In the examples presented in this paper, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
 
@@
 
-Additional extension for future work include extending the model to capture a $2^{nd}$-order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
-
-Another extension of this framework is the inclusion of finite distant-dependant action potential propagation velocity into the parametric neural field equations.
+Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
+
+Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
 In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks.

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
  \begin{align}
-  \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=\mathbf E_{\boldsymbol \Theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \Theta)\right] \nonumber \\
- &=\mathbf E_{\boldsymbol\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
+  \mathcal Q(\boldsymbol \theta,\boldsymbol\theta')&=\mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right] \nonumber \\
+ &=\mathbf E_{\boldsymbol\theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
  +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
@@
 \begin{equation}
-\mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}
+\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}
 \end{equation}
 where the constant term can be ignored as it is independent of the parameters.
-Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)$ can be written as
-\begin{align}
-p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\Theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
+Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as
+\begin{align}
+p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
 \end{align}
@@
 \begin{align}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
 &-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
@@
 \begin{align}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
 &-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t,\nonumber \\
@@
 \begin{align}\label{eq:Qfunctionintrace}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
 &-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace\nonumber \\

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edit to appendix

@@
 A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
-Let the entire sequence of observations is denoted by $\mathbf Y$, and the sequence of hidden variables by $\mathbf X$ and the parameter set by $\boldsymbol\theta$.
-We want to maximise the likelihood function which is difficult to maximise directly
+We want to maximise the likelihood function which is difficult to perform directly
 \begin{equation}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
  \end{equation}  
-where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations, $\mathbf Y$, parameterised  by $\boldsymbol\theta$, known as the likelihood function.
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterised  by $\boldsymbol\theta$, known as the likelihood function.
 This problem cannot be solved separately as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix...)  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix~\ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
@@
 \end{align}
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see Appendix~ for more details)
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see Appendix~\ref{ap:Xiderivation} for more details)
 \begin{align}
@@
 
-\subsection{Lower bound on likelihood function}\label{ap:MStep}
+\subsection{Lower bound on likelihood function}\label{ap:Lowerbound}
 A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
@@
 It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.
-\section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}
+\section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}
 The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits
added new figure for model components

@@
 \centering
-\includegraphics[scale=.6]{./Graph/ConnectivityKernel.pdf}
-\includegraphics[scale=.6]{./Graph/Synaptickernel.pdf}
-\includegraphics[scale=.6]{./Graph/Sigmoid.pdf}
+\includegraphics[scale=.8]{./Graph/ModelComponents.pdf}
 \caption{ {\bf The IDE neural field model components}.
-(\textbf{a}) The mexican hat connectivity kernel.
-(\textbf{b}) First order synaptic kernel.
-(\textbf{c}) A representative of the activation function.}
+(\textbf{A}) The Mexican hat (red) and Wizard hat (blue) connectivity kernels.
+(\textbf{B}) First order (red) and second order (blue) synaptic kernels.
+(\textbf{C}) A representative of the activation function.}
 \label{fig:Modelcomponents}
@@
 \end{equation}
-where $\delta(\cdot)$ is the Dirac-delta function.
-The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r}))$ \parham{Dean: can you add the bit about different type of activatin functions here}.%$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
+where $\delta(\cdot)$ is the Dirac-delta function. %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
 

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{align}
-\parham{One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
+One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
 \begin{equation}
@@
 	\end{equation}
-	This is important as the underlying field can be reconstructed in saturation without introducing numerical errors which is not the case for example in the case of Gaussian basis functions. }
+	This is important as the underlying field can be reconstructed in saturation without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.
 

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
-	\theta\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
+	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
 	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
@@
 	\end{equation}
-	This is important as the underlying field can be reconstructed in saturation without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.
+	This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.
 
@@
  \end{equation}
-  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} Bspline wavelets are semiorthogonal as they are not orthogonal with respect to translation on a given scale.}
+  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semiorthogonal as they are not orthogonal with respect to translation on a given scale.}
 
@@
 \end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order Bspline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} from which the level of approximation, $j$, can be determined.
+\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} from which the level of approximation, $j$, can be determined.
 This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying neural field estimated from observations.}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edit
change to the model component plot

@@
 \centering
-\includegraphics[scale=.8]{./Graph/ModelComponents.pdf}
+\includegraphics[scale=1]{./Graph/ModelComponents.pdf}
 \caption{ {\bf The IDE neural field model components}.
-(\textbf{A}) The Mexican hat (red) and Wizard hat (blue) connectivity kernels.
-(\textbf{B}) First order (red) and second order (blue) synaptic kernels.
+(\textbf{A}) The Mexican hat (dotted line) and Wizard hat (solid line) connectivity kernels.
+(\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.
 (\textbf{C}) A representative of the activation function.}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
change to EM block Diagram

@@
 	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
-	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
+	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
 	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ (width $\sigma_m$) & n.a. \\
+	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
 	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
 	$h(t)$ & post-synaptic response kernel & mV\\
-	$\zeta$, $\xi$ & inverse synaptic time constant \& time constant parameter & s$^{-1}$, n.a.\\
-	$\eta(t)$ & Heaviside step function & n.a.\\
+	$\tau$, $\xi$ & synaptic time constant \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
-	$\textrm{D}$ & temporal differential operator & n.a.\\
 	\hline
@@
 	\hline
+	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
+	$\hat{\mathbf{x}}_t^{b}$ & backward posterior state estimates & mV\\
+	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
+	$P^b_t$ & backward posterior covariance matrices & mV$^2$\\
+	$M_t$& cross-covariance matrix & mV$^2$\\
 	$\mathcal K_{t} $ & filter gain & n.a.\\ 
+	$\mathcal S_{t} $ & smoother gain & n.a.\\
 	\hline
@@
  \begin{align}
-  \mathbf S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
- \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathbf S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
- \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathbf S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathbf S_t^\top \nonumber
+  \mathcal S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
+ \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
+ \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top \nonumber
  \end{align}
@@
  \begin{align}
- \mathbf M_t= \mathbf P_t^{f}\mathbf S_{t-1}^{\top}+\mathbf S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathbf S_{t-1}^{\top}\nonumber
+ \mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}\nonumber
  \end{align}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
edits to induction appendix

@@
 \end{align}
-\subsection{Induction}\label{ap:Induction}
+\subsection{Scaling function expansion}\label{ap:Induction}  
+In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
 For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
@@
   \end{align}
-which clearly holds (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we have
+which clearly holds from two-scale relation pair (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
 \begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
@@
 \end{align}
-$N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
+in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
 \begin{align}\label{eq:AppendixNj-1intermsofNj}
@@
 &\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
-&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}})
-\end{align}
-Substituting \eqref{eq:AppendixNj-1intermsofNj} in to \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
+&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
+\end{align}
+Substituting \eqref{eq:AppendixNj-1intermsofNj} into \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
 

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 
-\author{P.
-Aram, D.R.
-Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M.
-Dewar, K.Scerri~\IEEEmembership{Member,~IEEE}, D.B.
-Grayden~\IEEEmembership{Member,~IEEE,} and V.
-Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
+\author{P. Aram, D.R. Freestone, M. Dewar, K.Scerri, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
 \thanks{P.
@@
 	$h(t)$ & post-synaptic response kernel & mV\\
-	$\tau$, $\xi$ & synaptic time constant \& time constant parameter & s, n.a.\\
+	$\tau$, $\xi$ & \parham{synaptic time constant} \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
@@
 \begin{equation}
- w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelet}},
+ w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
 \label{eq:KernelExpansion}
@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
 The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
@@
 \begin{equation}
- v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelet}},
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
 \label{eq:FieldExpansion}
@@
 where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
-\dean{The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.}
-
-Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level \dean{$j=J$} in order to solve the estimation problem.
+The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
+
+Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem.
 In other words, the neural field must be band-limited up to a given spatial frequency.
 
-Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions \parham{and their corresponding coefficients such that}
+Now we will simplify the notation by defining vectors that contain all the translations of the wavelets and scaling functions 
 \begin{align}      
@@
 \end{align}
-where $k = j_0,j$. Following this we can define the \dean{vectors} 
+where $k = j_0,j$. Following this we can define the vectors 
 \begin{align}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
changed the format to NeuroImage

@@
- % TO DELETE
-
-%    \documentclass[journal,a4paper]{IEEEtran}
-%  \documentclass[journal]{IEEEtran}
-
-%     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
-     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
-%         \topmargin       -6.0mm
-%          \oddsidemargin      0mm
-%          \evensidemargin     0mm
-%          \textheight     223.5mm
-%         \textwidth      170.0mm
+\documentclass[review,authoryear,3p]{elsarticle}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
 \usepackage{setspace} 
-\usepackage{color}
-\newcommand{\mike}[1]{\textcolor{red}{#1}}
+\usepackage[usenames,dvipsnames]{color}
+
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
-\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
-\newcommand{\cut}[1]{\textcolor{cyan}{#1}}
-
-\usepackage{cite}
-%Reduce the spacing between figures and captions
-% \usepackage[belowskip=-15pt,aboveskip=10pt]{caption}
-%  \setlength{\intextsep}{2pt plus 2pt minus 2pt}
-
-\ifCLASSINFOpdf
-   \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-
-\usepackage[cmex10]{amsmath}
-\interdisplaylinepenalty=2500
-\usepackage{amssymb}
-\ifCLASSOPTIONcompsoc
-  \usepackage[tight,normalsize,sf,SF]{subfigure}
-\else
-  \usepackage[tight,footnotesize]{subfigure}
-\fi
-
-\usepackage{natbib}
-
-\usepackage{stfloats}
-\usepackage{float}
-\floatstyle{ruled}
-%This bit is how to use hyperlink without stupid coloured rectangles around it
-\usepackage{float}
-\usepackage{hyperref}
-\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\newfloat{algorithm}{htbp}{loa}%[chapter]
-\floatname{algorithm}{Algorithm}
-
+% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
+
+%\newfloat{algorithm}{htbp}{loa}%[chapter]
+%\floatname{algorithm}{Algorithm}
+\journal{Neuroimage}
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
+\begin{frontmatter}
 \title{Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
 
-\author{P. Aram, D.R. Freestone, M. Dewar, K.Scerri, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
-\thanks{P.
-Aram* and V.
-Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K.
-(e-mail:parham.aram@univ-amu.fr; visakan@sheffield.ac.uk).}% <-this % stops a space
-\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
-of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia.
-(e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).
-The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
-\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}
-\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
-of Malta, Msida, MSD, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
-% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
-
-% The paper headers
-% \markboth{Journal of }%
-% {Aram \MakeLowercase{\textit{et al.}}: Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
- \ifCLASSOPTIONpeerreview
-\else
-\fi
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% make the title area
-\maketitle
+\author[US]{P. Aram\corref{cor1}}
+\ead{p.aram@sheffield.ac.uk}
+\author[DEEE,BEI,UE]{D. R. Freestone}
+\ead{dfreestone@bionicear.org} 
+\author[UE,CU]{M. Dewar}
+\ead{mike.dewar@columbia.edu}
+\author[UM]{K. Scerri}
+\ead{kenneth.scerri@um.edu.mt}
+\author[DEEE,BEI]{D. B. Grayden}
+\ead{grayden@unimelb.edu.au}
+\author[US]{V. Kadirkamanathan}
+\ead{visakan@sheffield.ac.uk}
+
+\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
+\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
+\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
+\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
+\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
+\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+
+\cortext[cor1]{Corresponding author}
 
@@
 \end{abstract} 
-% Note that keywords are not normally used for peerreview papers.
- \begin{IEEEkeywords}
-  Neural field model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
-  \end{IEEEkeywords}
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
-%   \fi
-%
-%  For peerreview papers, this IEEEtran command inserts a page break and
-%creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+%\begin{keyword}
+ % Neural Field Model \sep multi-resolution approximation (MRA) \sep Expectation Maximisation (EM) algorithm \sepWavelets
+%\end{keyword}
+
+\end{frontmatter}
 
 \section{Introduction}
-\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
+The human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
-\begin{algorithm}
-\caption{Summary of the Rauch-Tung-Striebel smoother}
+\renewcommand{\arraystretch}{1.7}
+\begin{table*}[!ht]
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
+$\hat{\mathbf x}_{t+1}^{f-}=\mathbf A \hat{\mathbf x}_{t}^{f}$  \\ 
+$\mathbf P_{t+1}^{f-}=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e$  \\
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})$\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
+ $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\  
+$\mathcal S_{t}=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1}$ \\
+ $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})$ \\
+ $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top$\\  
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{5.} Compute the smoothed cross covariance matrix, initialization}\\
+$\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
+\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\
+$\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
+\hline
+\end{tabular}
+\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
+The lower bound is maximised after each iteration to update the parameter estimates.}
 \label{alg:MRA-RTS}
- % \begin{tabbing}
- \begin{enumerate}
- \item Forward initialisation: 
- \begin{equation*}
- \hat{\mathbf x}_0, \mathbf P_0
- \end{equation*}
- \item Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix
- \begin{align}
- \hat{\mathbf x}_{t+1}^{f-}&=\mathbf A \hat{\mathbf x}_{t}^{f} \nonumber \\
- \mathbf P_{t+1}^{f-}&=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e \nonumber 
- \end{align}
- \item Compute the filter gain, the filtered state and the filtered covariance matrix
- \begin{align}
- \mathcal K_{t+1}&=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1} \nonumber\\
-\hat{\mathbf x}_{t+1}^{f}&=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})\nonumber \\
- \mathbf P_{t+1}^f&=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} \nonumber 
- \end{align}
- \item  Backward initialisation:
- \begin{equation*}
- \mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
- \end{equation*}
- \item Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix
- \begin{align}
-  \mathcal S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
- \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
- \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top \nonumber
- \end{align}
- \item compute the smoothed cross covariance matrix\\
- initialisation:
- \begin{align}
-  \mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b \nonumber
- \end{align}
- Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $
- \begin{align}
- \mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}\nonumber
- \end{align}
- \end{enumerate}
- % \end{tabbing}
- \end{algorithm}
+\end{table*}
+\renewcommand{\arraystretch}{1}
 \subsection{Stopping rule}
@@
 \end{equation}
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-%   \newpage
-% \bibliographystyle{unsrt} 
-\bibliographystyle{apalike}
+
+\bibliographystyle{./elsarticle/model2-names} 
 \bibliography{MRAIDE}
 
-% \bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
- % \bibliography{IEEEabrv,MRAIDE}
-
 \end{document}

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor edit
edit for the table of parameters

@@
 \author[US]{P. Aram\corref{cor1}}
-\ead{p.aram@sheffield.ac.uk}
+\ead{parham.aram@univ-amu.fr}
 \author[DEEE,BEI,UE]{D. R. Freestone}
@@
 	$h(t)$ & post-synaptic response kernel & mV\\
-	$\tau$, $\xi$ & \parham{synaptic time constant} \& time constant parameter & s, n.a.\\
+	$\tau$, $\xi$ & membrane time constant \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
@@
 \end{equation}
-
+\newpage
 \bibliographystyle{./elsarticle/model2-names} 

### 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
added keywords
minor edit

@@
 \end{abstract} 
-%\begin{keyword}
- % Neural Field Model \sep multi-resolution approximation (MRA) \sep Expectation Maximisation (EM) algorithm \sepWavelets
-%\end{keyword}
+\begin{keyword}
+  Neural Field Model, multi-resolution approximation (MRA), Expectation Maximisation (EM) algorithm
+\end{keyword}
 
@@
 	\end{equation}
-	This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.
+	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.}
 

### 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
rearranged the EM section and added computational complexity

@@
 \end{equation}
+By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
+\begin{align}\label{eq:MRA-QDerivative}
+\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
+&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
+\end{align}
+Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
+\begin{align}\label{eq:MRA-thetahat}
+\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
+\end{align}
+The second derivative of the $\mathcal Q$-function is given by
+\begin{equation}
+\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
+\end{equation}
+The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\citep{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorization operator.
+Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
+
+\subsection{Stopping rule}
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
+\begin{equation}
+ \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
+ \end{equation}
+ where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \citet{Meyer2000}
+ \begin{equation}
+  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
+ \end{equation}
+\subsection{Computational complexity} 
 All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
@@
 \end {table}
-
-By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
-\begin{align}\label{eq:MRA-QDerivative}
-\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
-&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
-\end{align}
-Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
-\begin{align}\label{eq:MRA-thetahat}
-\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
-\end{align}
-The second derivative of the $\mathcal Q$-function is given by
-\begin{equation}
-\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
-\end{equation}
-The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\citep{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorization operator.
-Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
-
 The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
@@
 The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
+
 \renewcommand{\arraystretch}{1.7}
@@
 \renewcommand{\arraystretch}{1}
-\subsection{Stopping rule}
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
-\begin{equation}
- \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
- \end{equation}
- where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \citet{Meyer2000}
- \begin{equation}
-  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
- \end{equation}
 %\cut{The second terms in  \eqref{eq:upsilon0}, \eqref{eq:upsilon1}, and \eqref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}

### 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
edit to computational complexity

@@
 The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
+It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to \citet{Dewar2009}.
+This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.
 \begin {table}
@@
 \end {table}
+
 The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
@@
 \renewcommand{\arraystretch}{1} 
-%\cut{The second terms in  \eqref{eq:upsilon0}, \eqref{eq:upsilon1}, and \eqref{eq:Upsilon} can be computed as a once-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the method in \cite{Dewar2009}.}
-
 \section{Results}\label{sec:MRA-results}

### 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
minor edit
minor edited to author list
minor edit to author list

--- 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
@@
-\documentclass[review,authoryear,3p]{elsarticle}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
+ % TO DELETE
+
+%    \documentclass[journal,a4paper]{IEEEtran}
+%  \documentclass[journal]{IEEEtran}
+
+%     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
+     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
+%         \topmargin       -6.0mm
+%          \oddsidemargin      0mm
+%          \evensidemargin     0mm
+%          \textheight     223.5mm
+%         \textwidth      170.0mm
 \usepackage{setspace} 
-\usepackage[usenames,dvipsnames]{color}
-
+\usepackage{color}
+\newcommand{\mike}[1]{\textcolor{red}{#1}}
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
 \newcommand{\parham}[1]{\textcolor{blue}{#1}} 
-% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
-
-%\newfloat{algorithm}{htbp}{loa}%[chapter]
-%\floatname{algorithm}{Algorithm}
-\journal{Neuroimage}
+\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
+\newcommand{\cut}[1]{\textcolor{cyan}{#1}}
+
+\usepackage{cite}
+%Reduce the spacing between figures and captions
+% \usepackage[belowskip=-15pt,aboveskip=10pt]{caption}
+%  \setlength{\intextsep}{2pt plus 2pt minus 2pt}
+
+\ifCLASSINFOpdf
+   \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+
+\usepackage[cmex10]{amsmath}
+\interdisplaylinepenalty=2500
+\usepackage{amssymb}
+\ifCLASSOPTIONcompsoc
+  \usepackage[tight,normalsize,sf,SF]{subfigure}
+\else
+  \usepackage[tight,footnotesize]{subfigure}
+\fi
+
+\usepackage{natbib}
+
+\usepackage{stfloats}
+\usepackage{float}
+\floatstyle{ruled}
+%This bit is how to use hyperlink without stupid coloured rectangles around it
+\usepackage{float}
+\usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\newfloat{algorithm}{htbp}{loa}%[chapter]
+\floatname{algorithm}{Algorithm}
+
 \begin{document}
-\begin{frontmatter}
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
 \title{Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
 
-\author[US]{P. Aram\corref{cor1}}
-\ead{parham.aram@univ-amu.fr}
-\author[DEEE,BEI,UE]{D. R. Freestone}
-\ead{dfreestone@bionicear.org} 
-\author[UE,CU]{M. Dewar}
-\ead{mike.dewar@columbia.edu}
-\author[UM]{K. Scerri}
-\ead{kenneth.scerri@um.edu.mt}
-\author[DEEE,BEI]{D. B. Grayden}
-\ead{grayden@unimelb.edu.au}
-\author[US]{V. Kadirkamanathan}
-\ead{visakan@sheffield.ac.uk}
-
-\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
-\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
-\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
-\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
-\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
-\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
-
-\cortext[cor1]{Corresponding author}
+\author{P. Aram, D.R. Freestone, M. Dewar, K.Scerri, D.B. Grayden and V. Kadirkamanathan % <-this % stops a space
+\thanks{P.
+Aram* and V.
+Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K.
+(e-mail:parham.aram@univ-amu.fr; visakan@sheffield.ac.uk).}% <-this % stops a space
+\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
+of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia.
+(e-mail:dfreestone@bionicear.org; grayden@unimelb.edu.au).
+The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
+\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA. (e-mail:mike.dewar@columbia.edu).}
+\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
+of Malta, Msida, MSD, Malta. (e-mail:kenneth.scerri@um.edu.mt).}}
+% <-this % stops a space
+%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
+
+% The paper headers
+% \markboth{Journal of }%
+% {Aram \MakeLowercase{\textit{et al.}}: Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+ \ifCLASSOPTIONpeerreview
+\else
+\fi
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% make the title area
+\maketitle
 
@@
 \end{abstract}
-\begin{keyword}
-  Neural Field Model, multi-resolution approximation (MRA), Expectation Maximisation (EM) algorithm
-\end{keyword}
-
-\end{frontmatter}
+% Note that keywords are not normally used for peerreview papers.
+ \begin{IEEEkeywords}
+  Neural field model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
+  \end{IEEEkeywords}
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
+%   \fi
+%
+%  For peerreview papers, this IEEEtran command inserts a page break and
+%creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-The human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
+\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons.
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
@@
 	$h(t)$ & post-synaptic response kernel & mV\\
-	$\tau$, $\xi$ & membrane time constant \& time constant parameter & s, n.a.\\
+	$\tau$, $\xi$ & \parham{synaptic time constant} \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
 The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
@@
 	\end{equation}
-	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.}
+	This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.
 
@@
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
+This is important for constructing the wavelets.
 For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
@@
 The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
-\renewcommand{\arraystretch}{1.7}
-\begin{table*}[!ht]
-\begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
-$\hat{\mathbf x}_0, \mathbf P_0$ \\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
-$\hat{\mathbf x}_{t+1}^{f-}=\mathbf A \hat{\mathbf x}_{t}^{f}$  \\ 
-$\mathbf P_{t+1}^{f-}=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e$  \\
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})$\\
-$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
- $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$\\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\  
-$\mathcal S_{t}=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1}$ \\
- $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})$ \\
- $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top$\\  
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{5.} Compute the smoothed cross covariance matrix, initialization}\\
-$\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
-\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\
-$\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
-\hline
-\end{tabular}
-\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound is maximised after each iteration to update the parameter estimates.}
+\begin{algorithm}
+\caption{Summary of the Rauch-Tung-Striebel smoother}
 \label{alg:MRA-RTS}
-\end{table*}
-\renewcommand{\arraystretch}{1}
+ % \begin{tabbing}
+ \begin{enumerate}
+ \item Forward initialisation: 
+ \begin{equation*}
+ \hat{\mathbf x}_0, \mathbf P_0
+ \end{equation*}
+ \item Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix
+ \begin{align}
+ \hat{\mathbf x}_{t+1}^{f-}&=\mathbf A \hat{\mathbf x}_{t}^{f} \nonumber \\
+ \mathbf P_{t+1}^{f-}&=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e \nonumber 
+ \end{align}
+ \item Compute the filter gain, the filtered state and the filtered covariance matrix
+ \begin{align}
+ \mathcal K_{t+1}&=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1} \nonumber\\
+\hat{\mathbf x}_{t+1}^{f}&=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})\nonumber \\
+ \mathbf P_{t+1}^f&=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-} \nonumber 
+ \end{align}
+ \item  Backward initialisation:
+ \begin{equation*}
+ \mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T
+ \end{equation*}
+ \item Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix
+ \begin{align}
+  \mathcal S_{t}&=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1} \nonumber\\
+ \hat{\mathbf x}_t^b&=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})\nonumber \\
+ \mathbf P_{t}^{b}&=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top \nonumber
+ \end{align}
+ \item compute the smoothed cross covariance matrix\\
+ initialisation:
+ \begin{align}
+  \mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b \nonumber
+ \end{align}
+ Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $
+ \begin{align}
+ \mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}\nonumber
+ \end{align}
+ \end{enumerate}
+ % \end{tabbing}
+ \end{algorithm}
 \subsection{Stopping rule}
@@
 \end{equation}
+\ifCLASSOPTIONcaptionsoff
   \newpage
-\bibliographystyle{./elsarticle/model2-names} 
+\fi
+
+%   \newpage
+% \bibliographystyle{unsrt} 
+\bibliographystyle{apalike}
 \bibliography{MRAIDE}
 
+% \bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+ % \bibliography{IEEEabrv,MRAIDE}
+
 \end{document}

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
minor edits
added a table for joint state parameter estimation

--- 2012-02-01 Multiresolution_framework/ltx/manuscript.tex
@@
 \usepackage[usenames,dvipsnames]{color}  
+\usepackage{enumerate}
 
@@
 
-\author[US]{P. Aram\corref{cor1}}
+\author[TNG]{P. Aram\corref{cor1}}
 \ead{parham.aram@univ-amu.fr}
@@
 
-\address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
+\address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
 \address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
@@
 \address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
+ \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
 
@@
  \begin{equation}
-  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}
+  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}.
  \end{equation}
 \subsection{Computational complexity} 
-All $n_x^2$ blocks of $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
+All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
 The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
@@
 \renewcommand{\arraystretch}{1} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\renewcommand{\arraystretch}{1.7}
+\begin{table*}[!ht]
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Initialization:  } \\ 
+\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence and set $\mathbf P_t$ and $\mathbf M_t$ large} \\
+\multicolumn{1}{|p{16cm}|}{Compute} \\
+$\mathbf{\Lambda}_{x}=\int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r$\\
+\multicolumn{1}{|p{16cm}|}{Compute all the $n^2_x$ blocks of block matrices $\mathbf U$, $\Gamma_1$ and  $\Gamma_2$ using} \\
+$\left[ \mathbf U\right] ^{k,i}=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr$\\
+$\left[ \Gamma_1\right]^{j,i} =\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}$\\
+$\left[ \Gamma_2\right] ^{j,i}=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Estimate the connectivity kernel parameters} \\
+$\boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)$\\
+$\boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)$\\
+$\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}$\\
+$\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i}$\\
+$\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}$\\
+$\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space model}\\
+\multicolumn{1}{|p{16cm}|}{Compute all the elements of $\boldsymbol\Lambda_{\theta}$ using} \\
+$\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta$\\
+\multicolumn{1}{|p{16cm}|}{Compute transition matrix $\mathbf A(\boldsymbol\theta)$ } \\
+$\mathbf A(\boldsymbol \theta) = T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\mathbf x_t^b$, the smoothed covariance,$\mathbf P^b_t$ and cross-covariance $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{5.} Convergence: go back to Step~2 unless }\\
+$ \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon$\\
+\hline
+\end{tabular}
+\caption{\textbf{State and parameter estimation for the MRAIDE model.} This table shows the steps for joint state and parameter estimation using the EM based algorithm.}
+\label{alg:EMsteps}
+\end{table*}
+\renewcommand{\arraystretch}{1}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}\label{sec:MRA-results}
@@
 \begin{align}
-\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)ds&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
+\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)dr&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
 &=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
rearranged the algorithms

@@
 The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
-Following \cite{Gibsona2005}, an additional backwards recursion is also included (step 6 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximised in the M-step.
+The RTS  algorithm is given in Table~\ref{alg:MRA-RTS}.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximised in the M-step.
 Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\mathbf{x}_t^{f-}$, $\mathbf{x}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
 Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialise the backward cross-covariance computation.
+\renewcommand{\arraystretch}{1.7}
+\begin{table*}[!ht]
+\begin{tabular}{|c|}\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
+$\hat{\mathbf x}_0, \mathbf P_0$ \\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
+$\hat{\mathbf x}_{t+1}^{f-}=\mathbf A \hat{\mathbf x}_{t}^{f}$  \\ 
+$\mathbf P_{t+1}^{f-}=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e$  \\
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
+$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
+$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
+\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
+$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
+$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})$\\
+$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
+ $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\  
+$\mathcal S_{t}=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1}$ \\
+ $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})$ \\
+ $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top$\\  
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{5.} Compute the smoothed cross covariance matrix, initialization}\\
+$\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
+\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\
+$\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
+\hline
+\end{tabular}
+\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
+The lower bound is maximised after each iteration to update the parameter estimates.}
+\label{alg:MRA-RTS}
+\end{table*}
+\renewcommand{\arraystretch}{1}
  \subsection{M-step}
@@
 The EM algorithm iterates between these two steps until the parameter estimates converge.
-The RTS  algorithm is given in Algorithm~\ref{alg:MRA-RTS} for completeness.
-
-\renewcommand{\arraystretch}{1.7}
-\begin{table*}[!ht]
-\begin{tabular}{|c|}\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{1.} Forward initialization} \\ 
-$\hat{\mathbf x}_0, \mathbf P_0$ \\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
-$\hat{\mathbf x}_{t+1}^{f-}=\mathbf A \hat{\mathbf x}_{t}^{f}$  \\ 
-$\mathbf P_{t+1}^{f-}=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e$  \\
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
-$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
-$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-})$\\
-$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Backward initialization}\\
- $\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$\\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Backward iteration: for $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute the smoother gain, the smoothed state and the smoothed covariance matrix}\\  
-$\mathcal S_{t}=\mathbf P_{t}^{f}\mathbf A^{\top}\left[ \mathbf P_{t +1}^{f-}\right]^{-1}$ \\
- $\hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathcal S_t(\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{f-})$ \\
- $\mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathcal S_t(\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{f-})\mathcal S_t^\top$\\  
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{5.} Compute the smoothed cross covariance matrix, initialization}\\
-$\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
-\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\
-$\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
-\hline
-\end{tabular}
-\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound is maximised after each iteration to update the parameter estimates.}
-\label{alg:MRA-RTS}
-\end{table*}
-\renewcommand{\arraystretch}{1} 
+A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{tabular}
-\caption{\textbf{State and parameter estimation for the MRAIDE model.} This table shows the steps for joint state and parameter estimation using the EM based algorithm.}
+\caption{\textbf{State and parameter estimation for the MRAIDE model.} This table shows the steps for the joint state and parameter estimation using the EM based algorithm.}
 \label{alg:EMsteps}

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
spell checking

@@
 \begin{keyword}
-  Neural Field Model, multi-resolution approximation (MRA), Expectation Maximisation (EM) algorithm
+  Neural Field Model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm
 \end{keyword}
@@
 
-The first work (to the authors best knowledge) describing data-driven mesoscopic neural modelling used a neural mass model to fit EEG data~\citep{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modelling (DCM)~\citep{David2003}.
-Following this work, data-driven modelling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
+The first work (to the authors best knowledge) describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\citep{Valdes1999}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003}.
+Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
 Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
-In this way, a flexible framework is created, whereby both macroscopic and microscopic behaviour of the system can be represented simultaneously and completely.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously and completely.
 
@@
 The multi-resolution structure has been described by numerous methods.
-For example, this idea of multi-resolution can be thought of a generalisation of modelling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \citep{Wilson1973}.
+For example, this idea of multi-resolution can be thought of a generalization of modeling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \citep{Wilson1973}.
 
@@
 
-The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covariance function 
+The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially colored but temporally white, with covariance function 
 \begin{equation}
@@
 The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-Therefore, the goal is to form a parameterised equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+Therefore, the goal is to form a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 
@@
 \caption{{\bf Examples of cardinal B-spline functions}.
-Piecewise polynomial functions (coloured lines) are joined at the break points (black dots).
+Piecewise polynomial functions (colored lines) are joined at the break points (black dots).
 (\textbf{A}) B-spline function of order 2 (linear B-spline).
@@
 The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
-B-spline wavelet and scaling functions approach optimal time/frequency localisation as the order of the spline increases.
+B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases.
 In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \citep{Unser1999}.
@@
 B-spline wavelet and scaling functions are particularly suited in this framework due to the property of being able to analytically define the convolution and inner product to form MRAIDE components.
-The following summarises some important characteristics of B-splines relevant to the proposed modelling framework.
+The following summarizes some important characteristics of B-splines relevant to the proposed modeling framework.
 
@@
  \end{equation}
-  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semiorthogonal as they are not orthogonal with respect to translation on a given scale.}
+  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}
 
@@
 To demonstrate the MRAIDE framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
-Note that there is a difference between forward and inverse modelling when making these assumptions.
+Note that there is a difference between forward and inverse modeling when making these assumptions.
 For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
@@
  \end{equation}  
-where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterised  by $\boldsymbol\theta$, known as the likelihood function.
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function.
 This problem cannot be solved separately as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
 One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
-A natural framework to perform this is the well known Expectation Maximisation (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second  when the direct maximisation of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
+A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second  when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
 The EM algorithm, when used in the latter context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
 
-In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximising the lower bound in the M-step.
+In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step.
 A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
@@
 \caption{{\bf Schematic of the EM algorithm}.
-The RTS smoother (E-step) and the maximisation of the lower bound, $\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')$, (M-step) are shown.
-The dashed box shows the iterative two step algorithm once it is initialised.}
+The RTS smoother (E-step) and the maximization of the lower bound, $\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')$, (M-step) are shown.
+The dashed box shows the iterative two step algorithm once it is initialized.}
 \label{fig:EMBlockDiagram}
@@
 The RTS  algorithm is given in Table~\ref{alg:MRA-RTS}.
-Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximised in the M-step.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
 Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\mathbf{x}_t^{f-}$, $\mathbf{x}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
-Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialise the backward cross-covariance computation.
+Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
 \renewcommand{\arraystretch}{1.7}
@@
 \caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound is maximised after each iteration to update the parameter estimates.}
+The lower bound is maximized after each iteration to update the parameter estimates.}
 \label{alg:MRA-RTS}
@@
 where the constant term can be ignored as it is independent of the parameters.
-Under the condition that the state distribution is Gaussian --- ignoring the normalising term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as
+Under the condition that the state distribution is Gaussian --- ignoring the normalizing term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as
 \begin{align}
@@
 \end{align}
-Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximised for the optimal parameter estimates.
+Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximized for the optimal parameter estimates.
 Note that the expectation distributes over the trace sum.
@@
 All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
-The complexity of each step of the algorithm is summarised in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
+The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
 It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to \citet{Dewar2009}.
@@
 Two different experiments were designed to test the framework.
-In the first one, 200 realisations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
-This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realisation.
+In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
 In the second experiment, a single data set was generated and the field estimations are compared for five models, each accounting for a different level of approximation, i.e.
@@
 
-For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilise from the initial conditions.
+For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilize from the initial conditions.
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
@@
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
-The observation kernel was modelled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
+The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
 The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.
@@
 (\textbf{a}) The actual kernel and its components are shown by solid and dashed black lines, respectively.
-The mean kernel estimates over 200 realisations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
+The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
 (\textbf{b}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
@@
 \subsection{Experiment II}
-To study the performance of different models with various MRA capabilities, a single realisation was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
+To study the performance of different models with various MRA capabilities, a single realization was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
 The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
@@
 For a larger space or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
-One solution to this problem could be expectation-conditional maximisation (ECM) \citep{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
-The ECM is a class of generalised EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximised \citep{Fessler1994}.
+One solution to this problem could be expectation-conditional maximization (ECM) \citep{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
+The ECM is a class of generalized EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximized \citep{Fessler1994}.
 
@@
 If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}.
-In general, convergence of the EM algorithm to any stationary point depends on the initialisation.
-In the examples presented in this paper, a bounded sequence of the state vectors was used to initialise the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
+In general, convergence of the EM algorithm to any stationary point depends on the initialization.
+In the examples presented in this paper, a bounded sequence of the state vectors was used to initialize the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
 
@@
 In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks.
-For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
+For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks.
 Finally, future work should be directed towards applying and validating the framework on real data.
@@
 A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
-We want to maximise the likelihood function which is difficult to perform directly
+We want to maximize the likelihood function which is difficult to perform directly
 \begin{equation}
@@
 \end{equation}   
-Maximising the likelihood in terms of the parameter set is equivalent to the log-likelihood maximisation, as both the likelihood and log-likelihood functions share the same maximiser due to the monotonicity of the logarithm function.
+Maximizing the likelihood in terms of the parameter set is equivalent to the log-likelihood maximization, as both the likelihood and log-likelihood functions share the same maximizer due to the monotonicity of the logarithm function.
 For any choice of distribution defined over the latent variables, $q(\mathbf X)$, the following decomposition holds
@@
 \end{align}
-Noting  $q(\mathbf X)$ is a normalised distribution that integrates to one gives the log-likelihood function.
+Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
 Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$, therefore,
@@
 
-The EM algorithm alternates between maximising the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
-Suppose that the current estimate of the parameter set is $\boldsymbol\theta'$, in the E-step the lower bound is maximised with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\theta'$ is fixed.
+The EM algorithm alternates between maximizing the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
+Suppose that the current estimate of the parameter set is $\boldsymbol\theta'$, in the E-step the lower bound is maximized with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\theta'$ is fixed.
 Since the value of $p(\mathbf Y;\boldsymbol\theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the KL distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
@@
 Note in the state-space model the E-step is equivalent to the smoothing problem.
-The maximum in the M-step is obtained by maximising the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
+The maximum in the M-step is obtained by maximizing the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
 Since the distribution $q(\mathbf X)$ is computed using the old parameter estimates and kept fixed during the M-step, it is not equal to $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$, resulting in a non-zero KL distance.
@@
 The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\theta$.
-It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximises the expectation of the complete data log-likelihood.
+It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
 \section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
edit to covariance function

@@
 \end{equation}
-where $\delta(\cdot)$ is the Dirac-delta function. %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
+where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function} and $\delta(\cdot)$ is the Dirac-delta function.
+%$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
 
@@
 Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
-\parham{the lead field thingy}
+\parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}
 

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
corrections at different places

@@
 \section{MRA of the IDE in State-Space}
-The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+\parham{The purpose of} forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
 Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.
 
-The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-Therefore, the goal is to form a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+\parham{The goal of this section is to demonstrate} how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
+\parham{Therefore, the goal is to form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 
@@
 	\mathbf{x}_{t,j_0} \triangleq& \left\lbrace{x}_{t,j_{0},l}:l \in \mathbb{Z} \right\rbrace \\
-	\check{\mathbf{x}}_{t,j} \triangleq& \left\lbrace{\check{x}}_{t,j,l}:l \in \mathbb{Z} \right\rbrace,
-\end{align}
-where $k = j_0,j$. Following this we can define the vectors 
+	\check{\mathbf{x}}_{t,j} \triangleq& \left\lbrace{\check{x}}_{t,j,l}:l \in \mathbb{Z} \right\rbrace.
+\end{align}
+Following this we can define the vectors 
 \begin{align}
@@
 % The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
-Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
+Now we have the compact form of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
 \begin{equation}\label{eq:ApproxDiscreteTimeModel}
@@
 	\label{eq:Lambdax}
-	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r
+	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r,
 \end{equation}
@@
 \end{equation}
-A very nice property of the MRAIDE framework is the the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 
+A very nice property of the MRAIDE framework is the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 
 \begin{equation}\label{eq:Disturbance}
@@
 } The predefined convolution can be written as
-\begin{equation}
-	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r
+\begin{equation}\label{eq:Gammaij}
+	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r,
 \end{equation}
@@
 	\, \mathrm{d}r' \boldsymbol\theta
-	+ \mathbf w_t
+	+ \mathbf w_t.
 \end{equation}
@@
 B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases.
-In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions and they have a better approximation rate than other wavelets with the same number of vanishing moments \citep{Unser1999}.
+In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions\citep{Unser1999}.
+%and they have a better approximation rate than other wavelets with the same number of vanishing moments
 
@@
 	\end{equation}
-	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example in the case of Gaussian basis functions.}
-
-The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$, $\boldsymbol\Gamma$ and $\boldsymbol\Sigma_w$).
+	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.}
+
+The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$).
 To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
@@
 
-By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} can be computed analytically.
+By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Gammaij} can be computed analytically.
 In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}:

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
general edits

--- 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
@@
 \end{align}
-The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix ...).
+The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix~\ref{ap:Induction}).
 A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
@@
  \end{figure}  
- In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax}, \eqref{eq:Lambdatheta} and \eqref{eq:CovMatrix} whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+ In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax} and \eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[t]
@@
 \subsection{Frequency Analysis}
-To determine the level of approximation in the model, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
+To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
 To proceed the Fourier transform of $N_1(r)$ is first calculated,
@@
 It is important to point out there is no doubt that there will always be a mismatch between neural mass models and actual cortical tissue.
-Nevertheless, the simplifications used in formulating the equation enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.
+Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
@@
 \begin{equation}
-	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})
+	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}),
 \end{equation}
@@
 		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r}
+		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r},
 \end{align}
 to give the state transition equation
-\begin{align}\label{eq:StateEquation}
- \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
-\label{eq:A_theta}
- \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
-\end{align} 
+\begin{equation}\label{eq:StateEquation}
+ \mathbf x_{t+1} =\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
+\end{equation} 
+where
+\begin{equation}\label{eq:A_theta}
+ \mathbf A(\boldsymbol \theta)= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
+\end{equation} 
 The problem of joint state and parameter estimation for the state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} can be formulated as 
@@
 each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}
+\begin{align}\label{eq:Uij}
 \left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr,

### 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
general corrections

@@
 The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
-The RTS  algorithm is given in Table~\ref{alg:MRA-RTS}.
+The RTS  algorithm is given in Table~\ref{alg:MRA-RTS} for completeness.
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
-Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\mathbf{x}_t^{f-}$, $\mathbf{x}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
 Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space model}\\
-\multicolumn{1}{|p{16cm}|}{Compute all the elements of $\boldsymbol\Lambda_{\theta}$ using} \\
+\multicolumn{1}{|p{16cm}|}{Compute all elements of $\boldsymbol\Lambda_{\theta}$ using} \\
 $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta$\\

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor edit
correction to rts algorithm

--- 2012-02-02 Multiresolution_framework/ltx/manuscript.tex
@@
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
+\multicolumn{1}{|p{16cm}|}{\textbf{2.} Forward iteration: for $t\in\left\lbrace 0,\cdots,T-1\right\rbrace $, calculate the predicted state and the predicted covariance matrix } \\
 $\hat{\mathbf x}_{t+1}^{f-}=\mathbf A \hat{\mathbf x}_{t}^{f}$  \\ 
@@
 $\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
-\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,0\right\rbrace $ compute}\\
+\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\
 $\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
@@
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-Note that this is actually the smoother output.
+Note that this is actually the smoother output which is obtained at the E-step.
 

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
edit to the em alg
minor edit

@@
 A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
+Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors.
+Here the latter is chosen as shown in the block diagram ensuring the resultant kernel is stable.
 \begin{figure}[!t]
@@
 
- The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
+ The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
 The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor edit
minor edit to the appendix

@@
 \end{align}
-to give the state transition equation
+to give the state equation
 \begin{equation}\label{eq:StateEquation}
@@
 \end{equation} 
-where
+with the parameterized transition matrix
 \begin{equation}\label{eq:A_theta}
@@
  &=\mathbf E_{\boldsymbol\theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
- +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right],
+ +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
  \end{align}   
@@
 \end{equation}
-is constant with respect to parameter $\boldsymbol\theta$ and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
+is constant with respect to the parameter $\boldsymbol\theta$, and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
 Taking the trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
@@
 The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
-The expression for  $\boldsymbol\Xi_{0}$ as defined in equation~\eqref{eq:Xi0} of the main text is given by
+The expression for  $\boldsymbol\Xi_{0}$ as defined in equation~\eqref{eq:MRA-Xi0} of the main text is given by
    \begin{equation}\label{eq:appXi0}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
edit to the appendix
edits to the appendix

@@
 	\end{equation}                                                                                                
-	We start by expanding the equation \eqref{eq:appXi0}, giving
+	We start by computing the cross-covariance matrix as
 
@@
 \end{align}
-Rearranging  equation \eqref{eq:Xi0derivation0} we get
+Rearranging  equation \eqref{eq:Xi0derivation0} gives
 \begin{equation}\label{eq:Xi0derivation1}
- \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
-\end{equation}
-substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum we get
+ \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top.
+\end{equation}
+Substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum yields
 \begin{equation}
@@
 \end{equation}   
-An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by expanding the covariance matrix,
-\begin{equation}\label{eq:appXi1}
- \boldsymbol\Xi_1=\mathbf E_{\theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t}\mathbf x_{t}^\top\right],
-\end{equation}
-therefore we can write
-\begin{equation}\label{eq:Xi1derivation1}
- \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
-\end{equation}
-substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
-\begin{equation}
- \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
-\end{equation}
+An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t$.
+%\begin{equation}\label{eq:Xi1derivation1}
+% \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
+%\end{equation}
+%substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
+%\begin{equation}
+ %\boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
+%\end{equation}
 \newpage

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
general edits

@@
 \mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}\boldsymbol\theta \nonumber \\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta,
 \end{align}
@@
 \begin{equation}\label{eq:epsilon0}
-\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}
+\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i},
+\end{equation}
+\begin{equation}\label{eq:epsilon1}
+\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i},
 \end{equation}                                                                                 
 and
-\begin{equation}\label{eq:epsilon1}
-\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i}
-\end{equation}
 \begin{equation}\label{eq:Epsilon}
-\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}
+\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}.
 \end{equation}
@@
 \end{align}
-Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ yields
+Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
 \begin{align}\label{eq:MRA-thetahat}
@@
 Variable &Equation&Order&Order obtained from \citet{Dewar2009}\\ \hline\\
-$\Xi_0, \Xi_1$&\eqref{eq:MRA-Xi0}, \eqref{eq:MRA-Xi1}&$O(Tn_x^2)$& -\\
+$\Xi_0, \Xi_1$&\eqref{eq:Xi0}, \eqref{eq:Xi1}&$O(Tn_x^2)$& -\\
 $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&\eqref{eq:epsilon0},\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
@@
 $\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&-\\
-$\boldsymbol\Lambda_{\theta}$&\eqref{eq:Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
+$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&-\\
 $\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&-\\
@@
 \end{tabular}}
- \caption {{\bf The Computational complexity of the estimation algorithm}. A comparison between the algorithm proposed herein and that of \citet{Dewar2009}.} 
+ \caption {{\bf The Computational complexity of the estimation algorithm}.
+A comparison between the algorithm proposed herein and that of \citet{Dewar2009} is also provided.
+The dashes indicate equal complexities for both algorithms.}
 \label{table:MRA-ComputationalComplexity}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
added FT of the wavelet

@@
 \end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} from which the level of approximation, $j$, can be determined.
-This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying neural field estimated from observations.}
+\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} giving
+\begin{align}      
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m}} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
+\end{align}
+ From \eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
+This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
 
@@
 Variable &Equation&Order&Order obtained from \citet{Dewar2009}\\ \hline\\
-$\Xi_0, \Xi_1$&\eqref{eq:Xi0}, \eqref{eq:Xi1}&$O(Tn_x^2)$& -\\
+$\Xi_0, \Xi_1$&\eqref{eq:Xi0}, \eqref{eq:Xi1}&$O(Tn_x^2)$& \----\\
 $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&\eqref{eq:epsilon0},\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
 $\boldsymbol\Upsilon$&\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\
-$\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&-\\
-$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&-\\
-$\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&-\\
+$\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&\----\\
+$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&\----\\
+$\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&\----\\
 \hline \hline
@@
 A comparison between the algorithm proposed herein and that of \citet{Dewar2009} is also provided.
-The dashes indicate equal complexities for both algorithms.}
+"\----'' indicate equal complexities for both algorithms.}
 \label{table:MRA-ComputationalComplexity}
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{1.} Initialization:  } \\ 
-\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence and set $\mathbf P_t$ and $\mathbf M_t$ large} \\
+\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence and choose large values for $\mathbf P_t$ and $\mathbf M_t$} \\
 \multicolumn{1}{|p{16cm}|}{Compute} \\
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space model}\\
-\multicolumn{1}{|p{16cm}|}{Compute all elements of $\boldsymbol\Lambda_{\theta}$ using} \\
+\multicolumn{1}{|p{16cm}|}{Compute all $n_x^2$ elements of $\boldsymbol\Lambda_{\theta}$ using} \\
 $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta$\\
@@
 This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
-The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-NmFouriertransform}.
+The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-Wavelettransform}.
 The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
general edits

@@
 where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location within the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
-This multi-resolution structure is depicted in Figure~\ref{fig:MultiLayerFieldModel}.
+This multi-resolution structure is depicted in Fig.~\ref{fig:MultiLayerFieldModel}.
 \begin{figure}[t]
@@
 There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity.
-These are shown in Figure~\ref{fig:Modelcomponents}.
+These are shown in Fig.~\ref{fig:Modelcomponents}.
 Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.
-These are also shown in Figure~\ref{fig:Modelcomponents}.
+These are also shown in Fig.~\ref{fig:Modelcomponents}.
 The form of $w(\mathbf{r})$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field.
 By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
-In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Figure~\ref{fig:Modelcomponents}.
+In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
 
@@
 The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
-The components of the model are shown in Figure~\ref{fig:Modelcomponents}
+The components of the model are shown in Fig.~\ref{fig:Modelcomponents}
 \begin{figure}[!t]
@@
 These functions are composed of piecewise polynomials combined smoothly at some breaking points (knots), which are equally spaced in the case of cardinal B-splines.
-The degree of smoothness is determined by the order of splines \citep{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
+The degree of smoothness is determined by the order of splines \citep{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Fig.~\ref{fig:Figure0}).
 \begin{figure}[!t]
@@
 
-Figure~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero.
+Fig.~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero.
 Note in general the supports of the scaling and wavelet functions are given by
@@
 A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
-Examples of such expansions are given in Figure~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
+Examples of such expansions are given in Fig.~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
 \begin{figure}[!t] 
@@
 In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step.
-A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.
+A schematic representation of the EM algorithm is represented in Fig.~\ref{fig:EMBlockDiagram}.
 Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors.
@@
 The spatial frequency response of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-This is shown in Figure~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
+This is shown in Fig.~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
 The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-Wavelettransform}.
 The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
-\begin{figure}[!t] 
+\begin{figure}[!t]\label{fig:ObservationFrequencyResponce}
  	\centering
@@
  		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}
- 	\label{fig:ObservationFrequencyResponce}
  \end{figure}
@@
 The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
-The rate of convergence of the EM based algorithm is depicted in Figure~\ref{fig:MRA-Convergence}.
-\begin{figure}[!t] 
+The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}.
+\begin{figure}[!t]\label{fig:MRA-Convergence} 
  	\centering
@@
 the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.}
- 	\label{fig:MRA-Convergence}
  \end{figure}     
@@
 
-The actual connectivity kernel and the decomposition is plotted in Figure~\ref{fig:KernelEstimate}(a).
+The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A).
 No assumptions where made about the shape of the kernel.
@@
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
-Figure~\ref{fig:KernelEstimate}(b) and (c) illustrate the kernel scaling and wavelet functions, respectively.
+Fig.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
 A total number of 25 basis functions was used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$ accordingly.
@@
 % \end{figure}
- One snap shot of the field reconstruction, at different levels of approximation is given in Figures~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
+ One snap shot of the field reconstruction, at different levels of approximation is given in Fig.~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
 From this figure, it can be observed that the overall trend of the underlying field can be also captured at the coarser levels.
@@
 \end{figure}
+\subsection{Experiment II}
+To study the performance of different models with various MRA capabilities, a single realization was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
+The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
+The RMSE of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
+By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ is in fact adequate to capture the dynamics of the underlying field.
+The spatiotemporal characteristics of the reconstructed fields (A-E) along with the actual field (F)  are shown in Fig.~\ref{fig:FieldEstimation}.
+The experiment was performed several times and the results were consistent over each run.
+ \begin{figure}[!t]	\label{fig:RMSE} 
+ 	\centering
+ 		\includegraphics[scale=1]{./Graph/Figure3.pdf}
+ 		\caption{{\bf Error in the field reconstruction for experiment II}.
+The mean (over time) of average (over space) RMSE of the estimated field of state-space models with different MRA capabilities.
+$j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
+ \end{figure}
+
 \begin{figure}[t]
@@
 		\includegraphics[scale=1]{./Graph/STMultiRes.png}
-	\caption{{\bf Actual and estimated spatiotemporal neural field at different spatial resolutions}.
-(\textbf{A}) The reconstructed field of the reduced model using at $j=0$.
+	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
+(\textbf{A}) The reconstructed field of the reduced model at $j=0$.
 (\textbf{B}) The reconstructed field at $j=1$.
@@
 (\textbf{D}) The reconstructed field at $j=3$.
-(\textbf{E}) The reconstructed at $j=4$.
+(\textbf{E}) The reconstructed field at $j=4$.
 (\textbf{F}) The actual field.}
@@
 
-\subsection{Experiment II}
-To study the performance of different models with various MRA capabilities, a single realization was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
-The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
-The RMSE of the field estimation at different levels of approximation is shown in Figure~\ref{fig:RMSE}.
-By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field.
-The estimated field at a single time instant is shown in Figure~\ref{fig:FieldEstimates200}.
-The experiment was performed several times and the results were consistent over each run.
- \begin{figure}[!t] 
- 	\centering
- 		\includegraphics[scale=1]{./Graph/Figure3.pdf}
- 		\caption{{\bf Error in the field reconstruction for experiment II}.
-MRMSE of the estimated field of models with different level of approximations.
-$j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
- 	\label{fig:RMSE}
- \end{figure} 
-\begin{figure}[!t]
-\centering
-\includegraphics{./Graph/Figure5a.pdf}\\
-\includegraphics{./Graph/Figure5b.pdf}\\
-\includegraphics{./Graph/Figure5c.pdf}\\
-\includegraphics{./Graph/Figure5d.pdf}\\
-\includegraphics{./Graph/Figure5e.pdf}\\
-\caption{ {\bf Examples of the actual and estimated neural fields for experiment II}.
+%\begin{figure}[!t]
+%\centering
+%\includegraphics{./Graph/Figure5a.pdf}\\
+%\includegraphics{./Graph/Figure5b.pdf}\\
+%\includegraphics{./Graph/Figure5c.pdf}\\
+%\includegraphics{./Graph/Figure5d.pdf}\\
+%\includegraphics{./Graph/Figure5e.pdf}\\
+%\caption{ {\bf Examples of the actual and estimated neural fields for experiment II}.
 Actual (grey) and estimated (black) neural fields at a single time instant  for models with different spatial resolutions.
@@
 (\textbf{e}) $j=4$, $n_x=263$.}
-\label{fig:FieldEstimates200}
-\end{figure}
+%\label{fig:FieldEstimates200}
+%\end{figure}
 % The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
overal edits
fixes figure captions

@@
 The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
-\begin{figure}[!t]\label{fig:ObservationFrequencyResponce}
+\begin{figure}[!t]
  	\centering
@@
  		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}  
+\label{fig:ObservationFrequencyResponce} 
  \end{figure}
@@
 The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}.
-\begin{figure}[!t]\label{fig:MRA-Convergence} 
+\begin{figure}[t]
  	\centering
@@
 the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.} 
+\label{fig:MRA-Convergence}  
  \end{figure}     
@@
 \caption{ {\bf Connectivity kernel estimate}.
-(\textbf{a}) The actual kernel and its components are shown by solid and dashed black lines, respectively.
+(\textbf{A}) The actual kernel and its components are shown by solid and dashed black lines, respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(\textbf{b}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
+(\textbf{B}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
 \label{fig:KernelEstimate}
@@
 The experiment was performed several times and the results were consistent over each run.
- \begin{figure}[!t]	\label{fig:RMSE} 
+ \begin{figure}[!t]	 
  	\centering
@@
 $j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
+\label{fig:RMSE}
  \end{figure}
@@
 \bibliographystyle{./elsarticle/model2-names}  
+%\bibliographystyle{plain}
+
 \bibliography{MRAIDE}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor edit to result section

@@
 This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
-In the second experiment, a single data set was generated and the field estimations are compared for five models, each accounting for a different level of approximation, i.e.
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting for a different level of approximation, i.e.
 $j=0$ to $j=4$.
@@
 The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
+The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}.
 The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
changed the figure for the kernel estimate and deleted extra figs
changed field estimation plot and deleted extra figures
changed figure name in tex file
changed all the equations to Eq.

@@
 	\centering
-		\includegraphics[scale=1]{./Graph/MultiResNeuralField.pdf}
+		\includegraphics[scale=1]{./Graph/fig1.pdf}
 	\caption{{\bf Multi-layer neural field model}. The inset figures show the shape of the
@@
 \centering
-\includegraphics[scale=1]{./Graph/ModelComponents.pdf}
+\includegraphics[scale=1]{./Graph/fig2.pdf}
 \caption{ {\bf The IDE neural field model components}.
@@
 % The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
-Now we have the compact form of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
+Now we have the compact form of the decomposition we can substitute this into the neural field Eq.~\eqref{eq:DiscreteTimeModel} giving
 \begin{equation}\label{eq:ApproxDiscreteTimeModel}
@@
 The aim of the next part of the derivation is to isolate the state vector on the left hand side of the equation.
-To do this we first multiply both sides of equation~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
+To do this we first multiply both sides of Eq.~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
 \begin{align}\label{eq:ApproxDiscreteTimeModel2}
@@
 \end{equation}
-and substitute into equation~\eqref{eq:ApproxDiscreteTimeModel2} giving
+and substitute into Eq.~\eqref{eq:ApproxDiscreteTimeModel2} giving
 \begin{equation}\label{eq:ApproxDiscreteTimeModel3}
@@
 \end{equation}
-Following this, we can switch the order of operations with the inner product and convolution in equation~\eqref{eq:ApproxDiscreteTimeModel4}.
+Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
 With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel.
@@
 
-% Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
+% Substituting Eq.~\eqref{eq:KernelFiniteExpansion} and Eq.~\eqref{eq:FieldFiniteExpansion} in Eq.~\eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
 % \begin{align}\label{eq:DecomposedModel2} 
@@
 The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
- into \eqref{eq:ObservationEquation} giving
+ into Eq.~\eqref{eq:ObservationEquation} giving
 \begin{equation}\label{eq:ReducedObservationEquation} 
@@
 \centering
-\includegraphics{./Graph/Figure0.pdf}
+\includegraphics{./Graph/fig3.pdf}
 % \includegraphics{./Graph/Figure0b.pdf}
@@
 The convolution and inner product of B-spline functions are required in order to formulate the multi-resolution framework described in the previous section (construction of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$).
-To show how the convolution of two B-splines is calculated, \eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
+To show how the convolution of two B-splines is calculated, Eq.~\eqref{SplineConvolutionIntegral} can be rewritten as $(m-1)$ convolutions of the indicator function with itself
 \begin{equation}\label{eq:N1convolutions}
@@
 \end{align}
-A direct consequence of \eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline such that
+A direct consequence of Eq.~\eqref{eq:BsplineConvolution} is the inner product between two B-splines is another translated B-spline such that
 \begin{align}
@@
 $ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see Appendix~\ref{ap:InnerProductOfBsplines} for explicit derivation).
-The values of $N_{m+m'}$ in \eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating \eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
+The values of $N_{m+m'}$ in Eq.~\eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating Eq.~\eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
  \begin{equation}\label{eq:MRA-recursiveBsplineatintegerpoints}
@@
 \centering
-\includegraphics{./Graph/Figure1.pdf}
+\includegraphics{./Graph/fig4.pdf}
 % \includegraphics{./Graph/Figure1b.pdf}
@@
 
-By exploiting \eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in \eqref{eq:Lambdax} and \eqref{eq:Gammaij} can be computed analytically.
+By exploiting Eq.~\eqref{eq:BsplineConvolution} and Eq.~\eqref{eq:BsplineInnerProduct}, the integrals in Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Gammaij} can be computed analytically.
 In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}:
@@
  \end{equation}
-  \parham{Note from \eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}
+  \parham{Note from Eq.~\eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}
 
 In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
-For scaling functions this can be done  by using \eqref{eq:MRA-TwoScalepair1} recursively, giving
+For scaling functions this can be done  by usingEq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
 \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
@@
 The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix~\ref{ap:Induction}).
-A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using \eqref{eq:MRA-TwoScalepair2}.
+A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using Eq.~\eqref{eq:MRA-TwoScalepair2}.
 Examples of such expansions are given in Fig.~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/Decomposition.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig5.pdf}
  		\caption{{\bf The scaling and the wavelet function decomposition}.
@@
  \end{figure}  
- In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating \eqref{eq:Lambdax} and \eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+ In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[t]
@@
 	\end{tabular}
- \caption {{\bf Cardinal B-Splines at the knot sequence}. Table entries are calculated using \eqref{eq:MRA-recursiveBsplineatintegerpoints} and can be also found in \citet{Goswami1999}.} 
+ \caption {{\bf Cardinal B-Splines at the knot sequence}. Table entries are calculated using Eq.~\eqref{eq:MRA-recursiveBsplineatintegerpoints} and can be also found in \citet{Goswami1999}.} 
  \label{table:MRA-BsplineatIntegerPoints}
@@
 \subsection{Frequency Analysis}
-To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to \eqref{eq:N1convolutions}.
+To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}.
 To proceed the Fourier transform of $N_1(r)$ is first calculated,
@@
 The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
-Therefore, taking Fourier transform of \eqref{eq:N1convolutions} and substituting \eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
+Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
 \begin{align}\label{eq:MRA-NmFouriertransform}
@@
 \end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using \eqref{eq:MRA-TwoScalepair2} giving
+\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
 \begin{align}      
@@
 \end{align}
- From \eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
+ From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
 This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
@@
 \end{equation} 
-The problem of joint state and parameter estimation for the state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} can be formulated as 
+The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can be formulated as 
 \begin{equation}
@@
 \centering
-\includegraphics[scale=1]{./Graph/EMBlockDiagram.pdf}
+\includegraphics[scale=1]{./Graph/fig6.pdf}
 \caption{{\bf Schematic of the EM algorithm}.
@@
 
- The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
+ The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation}.
 The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
@@
 \end{align}
-Substituting $\mathbf A( \boldsymbol\theta)$ from \eqref{eq:A_theta} into \eqref{eq:Qfunction} gives
+Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
 \begin{align}
@@
 
-The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
+The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
 \begin{align}\label{eq:MRA-trace1}
@@
 where $[\cdot]_{i:} $ denotes the i-th row.
-By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from \eqref{eq:MRA-LambdaThetaElements} the trace given in \eqref{eq:MRA-trace1} can be written as
+By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:MRA-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
 \begin{align}
@@
 \end{align}
-The second trace of \eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
+The second trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
 \begin{align}
@@
 \end{align}
-Likewise, the third trace of \eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
+Likewise, the third trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
 \begin{align}
@@
 \end{align}
-Equating \eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
+Equating Eq.~\eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
 \begin{align}\label{eq:MRA-thetahat}
@@
 Variable &Equation&Order&Order obtained from \citet{Dewar2009}\\ \hline\\
-$\Xi_0, \Xi_1$&\eqref{eq:Xi0}, \eqref{eq:Xi1}&$O(Tn_x^2)$& \----\\
-$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&\eqref{eq:epsilon0},\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
-$\boldsymbol\Upsilon$&\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\
-$\mathbf A(\boldsymbol\theta)$&\eqref{eq:A_theta}&$O(n_x^3)$&\----\\
-$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&\----\\
-$\hat{\boldsymbol\theta} $&\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&\----\\
+$\Xi_0, \Xi_1$&Eq.~\eqref{eq:Xi0}, Eq.~\eqref{eq:Xi1}&$O(Tn_x^2)$& \----\\
+$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&Eq.~\eqref{eq:epsilon0}, Eq.~\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
+$\boldsymbol\Upsilon$&Eq.~\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\
+$\mathbf A(\boldsymbol\theta)$&Eq.~\eqref{eq:A_theta}&$O(n_x^3)$&\----\\
+$\boldsymbol\Lambda_{\theta}$&Eq.~\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&\----\\
+$\hat{\boldsymbol\theta} $&Eq.~\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&\----\\
 \hline \hline
@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using equations \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
 In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.
@@
 This is shown in Fig.~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
-The spatial bandwidths of wavelets was calculated analytically using equation \eqref{eq:MRA-Wavelettransform}.
+The spatial bandwidths of wavelets was calculated analytically using  Eq.~\eqref{eq:MRA-Wavelettransform}.
 The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/Figure2.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig7.pdf}
  		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}  
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/ConvergenceRate.pdf}
- 		\caption{{\bf Convergence of the EM algorithm}. Representative plot of
+ 		\includegraphics[scale=1]{./Graph/fig8.pdf}
+ 		\caption{{\bf Convergence of the EM based algorithm}. Representative plot of
 the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.} 
@@
 \begin{figure}[!t]  
-\includegraphics{./Graph/Figure5.pdf}
-\includegraphics{./Graph/Figure6.pdf}
+ \centering
+\includegraphics{./Graph/fig9.pdf}
 \caption{ {\bf Connectivity kernel estimate}.
@@
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(\textbf{B}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
+(\textbf{B},\textbf{C}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
 \label{fig:KernelEstimate}
@@
 \centering
-\includegraphics{./Graph/Figure4a.pdf}\\
-\includegraphics{./Graph/Figure4b.pdf}\\
-\includegraphics{./Graph/Figure4c.pdf}\\
-\includegraphics{./Graph/Figure4d.pdf}\\
+\includegraphics{./Graph/fig10.pdf}
 \caption{ {\bf Examples of the actual and estimated neural fields for experiment I}.
 Actual (grey) and estimated (black) neural fields at a single time instant for different spatial resolutions.
-(\textbf{a}) $j=0$, $n_x=17$.
-(\textbf{b}) $j=1$, $n_x=33$.
-(\textbf{c}) $j=2$, $n_x=65$.
-(\textbf{d}) $j=3$, $n_x=131$.}
+(\textbf{A}) $j=0$, $n_x=17$.
+(\textbf{B}) $j=1$, $n_x=33$.
+(\textbf{C}) $j=2$, $n_x=65$.
+(\textbf{D}) $j=3$, $n_x=131$.}
 % (\textbf{e}) $j=4$, $n_x=263$.
@@
 \subsection{Experiment II}
-To study the performance of different models with various MRA capabilities, a single realization was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
+To study the performance of different models with various MRA capabilities, a single realization was obtained using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
 The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/Figure3.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig11.pdf}
  		\caption{{\bf Error in the field reconstruction for experiment II}.
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/STMultiRes.png}
+		\includegraphics[scale=1]{./Graph/fig12.png}
 	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
@@
 \end{figure}
-
-%\begin{figure}[!t]
-%\centering
-%\includegraphics{./Graph/Figure5a.pdf}\\
-%\includegraphics{./Graph/Figure5b.pdf}\\
-%\includegraphics{./Graph/Figure5c.pdf}\\
-%\includegraphics{./Graph/Figure5d.pdf}\\
-%\includegraphics{./Graph/Figure5e.pdf}\\
-%\caption{ {\bf Examples of the actual and estimated neural fields for experiment II}.
-Actual (grey) and estimated (black) neural fields at a single time instant  for models with different spatial resolutions.
-(\textbf{a}) $j=0$, $n_x=17$.
-(\textbf{b}) $j=1$, $n_x=33$.
-(\textbf{c}) $j=2$, $n_x=65$.
-(\textbf{d}) $j=3$, $n_x=131$.
-(\textbf{e}) $j=4$, $n_x=263$.}
-%\label{fig:FieldEstimates200}
-%\end{figure}
-% The field reconstruction, at different levels of approximations, is shown in \figurename{\ref{fig:FieldEstimates}}.
-The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.78.
-Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
-% \begin{figure}[!h] 
-% 	\centering
-% 		\includegraphics[scale=1]{./Graph/fig1.pdf}
-% 		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions.
-(a) $j=0$, $n_x=17$, $RMSE = 1.93$.
-(b) $j=1$, $n_x=33$, $RMSE = 1.39$.
-(c) $j=2$, $n_x=65$, $RMSE = 0.90$.
-(d) $j=3$, $n_x=131$, $RMSE = 0.78$.
-(e) $j=4$, $n_x=263$, $RMSE=0.78$.}
-% 	\label{fig:FieldEstimates}
-% \end{figure}
-
 % \caption{The actual connectivity kernel is shown with the black solid line.
@@
 \end{align}
-A direct consequence of \eqref{eq:APP-SymmetrySplieEq} is 
+A direct consequence of Eq.~\eqref{eq:APP-SymmetrySplieEq} is 
 \begin{align}
@@
 In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
-For $n_1$ in equation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
+For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
 \begin{align}
@@
   \end{align}
-which clearly holds from two-scale relation pair (see \eqref{eq:MRA-TwoScalepair1}). Now assuming \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
+which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
 \begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
@@
 \end{align}
-Substituting \eqref{eq:AppendixNj-1intermsofNj} into \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
+Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
 
@@
 \end{align}
-Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in \eqref{eq:EM-decomposition1} giving
+Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
 \begin{align}
@@
 Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
-Note \eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$, therefore,
+Note Eq.~\eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$, therefore,
 \begin{equation}
@@
 The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
-It follows from equation \eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\theta)$ is a lower bound on the log-likelihood function, i.e.
+It follows from  Eq.~\eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\theta)$ is a lower bound on the log-likelihood function, i.e.
 \begin{equation}
@@
 Therefore, the growth of the log-likelihood function is greater than the growth of the lower bound.
-Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta')$ for $q(\mathbf X)$ in \eqref{eq:EM-decomposition1} gives
+Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta')$ for $q(\mathbf X)$ in Eq.~\eqref{eq:EM-decomposition1} gives
 \begin{align}
@@
 The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\theta$.
-It becomes clear from \eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
+It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
 \section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}
 The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
-The expression for  $\boldsymbol\Xi_{0}$ as defined in equation~\eqref{eq:MRA-Xi0} of the main text is given by
+The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:MRA-Xi0} of the main text is given by
    \begin{equation}\label{eq:appXi0}
@@
 \end{align}
-Rearranging  equation \eqref{eq:Xi0derivation0} gives
+Rearranging   Eq.~\eqref{eq:Xi0derivation0} gives
 \begin{equation}\label{eq:Xi0derivation1}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
added hyperlink package and changed my color to red
very minor correction

@@
 \usepackage[usenames,dvipsnames]{color}  
-\usepackage{enumerate}
+%This bit is how to use hyperlink without stupid coloured rectangles around it
+\usepackage{float}
+\usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
 
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
-\newcommand{\parham}[1]{\textcolor{blue}{#1}}
+\newcommand{\parham}[1]{\textcolor{red}{#1}}
 % \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
@@
 
-Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem.
+Eqs.~\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem.
 In other words, the neural field must be band-limited up to a given spatial frequency.

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
corrected the appendix format

@@
 The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
-
 % At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
@@
 % \end{equation}
-
 The dynamic neural field is decomposed using
@@
 \end{align}
-
 % where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, \dean{($\boldsymbol\theta \in \mathbb{R}^{n_{\theta}\times (J+2)}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x \times (J+2)}$)} are defined as
@@
 \end{equation}
-
 % Substituting Eq.~\eqref{eq:KernelFiniteExpansion} and Eq.~\eqref{eq:FieldFiniteExpansion} in Eq.~\eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
@@
 % \end{equation}
-
 The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
@@
 \end{equation}
-
 \section{B-Spline MRAIDE in State-Space }
@@
 This holds as the support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
-$ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see Appendix~\ref{ap:InnerProductOfBsplines} for explicit derivation).
+$ N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right)$ (see \ref{ap:InnerProductOfBsplines} for explicit derivation).
 The values of $N_{m+m'}$ in Eq.~\eqref{eq:BsplineInnerProduct} can be easily determined recursively by evaluating Eq.~\eqref{eq:MRA-DoBoorFormula} at integer points, i.e.
@@
 \end{align}
-The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see Appendix~\ref{ap:Induction}).
+The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see \ref{ap:Induction}).
 A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using Eq.~\eqref{eq:MRA-TwoScalepair2}.
@@
  \end {table}
-
 \subsection{Frequency Analysis}
@@
 This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
-
 \section{State and Parameter Estimation}
@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see Appendix~\ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+is a lower bound on the log-likelihood function \cite{Bishop2006} (see \ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
@@
 \end{align}
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see Appendix~\ref{ap:Xiderivation} for more details)
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see \ref{ap:Xiderivation} for more details)
 \begin{align}
@@
 This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see (\ref{eq:MRA-PsiPsiOrthogonality}-\ref{eq:MRA-PhiPsiOrthogonality})).
-
 \subsection{Experiment I}
@@
  \end{figure}
-
 The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
@@
 Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
-
 The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A).
@@
 \end{figure}
-
-% \begin{figure}[!h] 
-% 	\centering
-% 		\includegraphics[scale=1]{./Graph/fig2.pdf}
-% 		\caption{Connectivity kernel estimate.
-(a) The actual kernel and its components are shown by solid and dashed black lines, respectively.
-The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}
-% 	\label{fig:KernelEstimate}
-% \end{figure}
  One snap shot of the field reconstruction, at different levels of approximation is given in Fig.~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
@@
  \end{figure} 
-
 \begin{figure}[t]
@@
 
-\section{Appendix}
-\subsection{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
+\appendix
+\section{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
 In this section, an analytic formula is derived for the inner product of two B-spline scaling functions.
@@
 \end{align}
-\subsection{Scaling function expansion}\label{ap:Induction}  
+\section{Scaling function expansion}\label{ap:Induction}  
 In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
@@
 
-\subsection{Lower bound on likelihood function}\label{ap:Lowerbound}
+\section{Lower bound on likelihood function}\label{ap:Lowerbound}
 A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
@@
 \end{align}
-Equation \eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
+Eq.~\eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
 \begin{align}
@@
 \bibliographystyle{./elsarticle/model2-names}  
-%\bibliographystyle{plain}
-
 \bibliography{MRAIDE}
-
 \end{document}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor corrections

@@
 Variable &Equation&Order&Order obtained from \citet{Dewar2009}\\ \hline\\
-$\Xi_0, \Xi_1$&Eq.~\eqref{eq:Xi0}, Eq.~\eqref{eq:Xi1}&$O(Tn_x^2)$& \----\\
-$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&Eq.~\eqref{eq:epsilon0}, Eq.~\eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
+$\Xi_0, \Xi_1$&Eqs.~\eqref{eq:Xi0} and \eqref{eq:Xi1}&$O(Tn_x^2)$& \----\\
+$\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$&Eqs.~\eqref{eq:epsilon0} and \eqref{eq:epsilon1} &$O(n_x^2n_{\theta})$ &$O(n_x^2n_{\theta})+O(n_x^3)$ \\
 $\boldsymbol\Upsilon$&Eq.~\eqref{eq:Epsilon}&$O(n_x^2n_{\theta}^2)$&$O(n_x^4n_{\theta}^2)$\\

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
minor corrections

@@
 
- The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation}.
+ The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
 The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
@@
 the number of states, $n_x < n_y$ at each level of the decomposition.
-This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see (\ref{eq:MRA-PsiPsiOrthogonality}-\ref{eq:MRA-PhiPsiOrthogonality})).
+This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
 \subsection{Experiment I}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
general edits

@@
 B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases.
-In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions\citep{Unser1999}.
+In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions \citep{Unser1999}.
 %and they have a better approximation rate than other wavelets with the same number of vanishing moments
@@
 
-In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
+In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
 For scaling functions this can be done  by usingEq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
@@
  From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
-This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
+This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
 \section{State and Parameter Estimation}

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
general corrections

@@
 For the M-step, a lower bound on the likelihood function should be constructed where the steps needed
-to compute the required quantities are very dependent on the particular application which is described in detail for our problem.
+to compute the required quantities are very dependent on the particular application which wii be described in detail for our problem.
 
@@
 We use the RTS smoother in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along withe a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
 The RTS  algorithm is given in Table~\ref{alg:MRA-RTS} for completeness.
-Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 of the RTS algorithm)	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
 Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
general edits to EM

@@
 As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem.
-We use the RTS smoother in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
-The RTS  algorithm is given in Table~\ref{alg:MRA-RTS} for completeness.
+We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
@@
 \multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
-$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
-$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2n_x} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
 $\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex

@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
+\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
 The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+
 % At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
minor corrections

--- 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
@@
 We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
-Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
 Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
@@
 \caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound is maximized after each iteration to update the parameter estimates.}
+The lower bound, $\mathcal{Q}(\boldsymbol{\theta},\boldsymbol{\theta'})$, is maximized after each iteration to update the parameter estimates.}
 \label{alg:MRA-RTS}

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
minor edit
minor edit to EM
minor edits

@@
    	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\ 
+    $\mathbf{A}(\boldsymbol{\theta})$& transition matrix& n.a.\\
    	$\mathbf{C}$ & observation matrix & n.a. \\
@@
 \end{align}
-Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
+The factor of 2 is included to simplify the derivation in the later steps. Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
 \begin{align}
@@
 \end{align} 
-
-The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
+The rest of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
+The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
+To begin, the first trace is written in terms of element-wise summations
 \begin{align}\label{eq:MRA-trace1}
@@
 In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
-This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
-In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting for a different level of approximation, i.e.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization, the frequency response of the observed field used to decide on the level...
+.
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting upto a certain level of approximation, i.e.
 $j=0$ to $j=4$.
@@
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
-The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\gamma(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
+The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex
edit to notation table

@@
 	\hline
-	$\Omega$ & spatial domain & n.a.\\
-	$\mathbf{r}$ & spatial location & [mm, mm]\\
-	$t$ & time & s\\
+	$\Omega$ & Spatial domain & n.a.\\
+	$\mathbf{r}$ & Spatial location & [mm, mm]\\
+	$t$ & Time & s\\
 	\hline
@@
 	\hline
-    $y_t$ & observation & mV\\
-    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
-	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
-	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
-	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
-	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
-	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
-	$h(t)$ & post-synaptic response kernel & mV\\
-	$\tau$, $\xi$ & membrane time constant \& time constant parameter & s, n.a.\\
+    $y_t$ & Observation & mV\\
+    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
+	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
+	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
+	$\boldsymbol\varepsilon_t$ & Observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
+	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
+	$h(t)$ & Post-synaptic response kernel & mV\\
+	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
 	\hline    
+	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
+	\hline                                                   
+	$\phi_{j,l}(r)$&Scaling function&n.a\\
+	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
+	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
+	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
+	$N_m(r)$&$m$-th order B-spline function&n.a.\\
+	$\varphi_m(r)$&$m$-th order B-spline wavelet function&n.a.\\
+	\hline
 	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
 	\hline
-   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
-   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\ 
-    $\mathbf{A}(\boldsymbol{\theta})$& transition matrix& n.a.\\
-   	$\mathbf{C}$ & observation matrix & n.a. \\
+		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
+		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
+   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
+		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$&mV\\ 
+		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
+		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
+   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
+    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
+   	$\mathbf{C}$ & Observation matrix & n.a. \\
 	\hline
@@
 	\hline
-	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
-	$\hat{\mathbf{x}}_t^{b}$ & backward posterior state estimates & mV\\
-	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
-	$P^b_t$ & backward posterior covariance matrices & mV$^2$\\
-	$M_t$& cross-covariance matrix & mV$^2$\\
-	$\mathcal K_{t} $ & filter gain & n.a.\\ 
-	$\mathcal S_{t} $ & smoother gain & n.a.\\
+	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
+	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
+	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
+	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
+	$M_t$& Cross-covariance matrix & mV$^2$\\
+	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
+	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
+	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
+	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
+	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Lambda$&Lower bound coefficient matrices&??\\
 	\hline

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
added table for parameter for result section

@@
 	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
-	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Lambda$&Lower bound coefficient matrices&??\\
+	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Upsilon$&Lower bound coefficient matrices&??\\
 	\hline
@@
 \begin{equation}
-cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
+cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\sigma_d\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
 \label{eq:FieldDisturbance}
 \end{equation}
-where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function} and $\delta(\cdot)$ is the Dirac-delta function.
+where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance} and $\delta(\cdot)$ is the Dirac-delta function.
 %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
@@
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
-The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
+The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations.
 The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}.
@@
 This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
+\begin{table*}[!ht]
+\begin{tabular}{|c|l|c|l|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
+	\hline
+	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
+	\hline
+	$\Delta$ & spatial discretisation step & 0.01 & mm \\
+	$T_s$ & time step & $0.001$ & s\\
+	$T$ & number of time steps used in estimation & 900 & n.a.\\
+	\hline 
+\multicolumn{4}{|c|}{\emph{Model}}\\
+	\hline
+	$\tau$ & membrane time constant & 0.01 & s$^{-1}$ \\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
+	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters (data generation) & $\left[\begin{array}{cc}
+	200 & -100
+	\end{array}
+	\right]^{\top}$ & mV.spike$^{-1}$\\
+	%$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
+	$n_y$ & number of sensors & 161 & n.a.\\ 
+	$\Delta_y$ & distance between adjacent sensors & 0.05 & mm\\
+	$\sigma_{m}$ & observation kernel full width at half maximum & 0.08 & mm \\
+	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
+	$\sigma_{\eta}$& disturbance covariance function full width at half maximum & 0.18 & mm\\
+	$\sigma_{d}$ & disturbance variance & 0.53 & mV \\
+	\hline 
+	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
+	\hline
+	$n_x$ & number of field basis functions&& n.a.\\
+	$   $ &Experiment~I&131&\\
+	$   $ &Experiment~II&17, 33, 65, 131, 263&\\ 
+	\hline 
+	\multicolumn{4}{|c|}{\emph{Estimation}}\\ 
+	\hline
+	$n_{\theta}$&number of connectivity kernel basis functions for estimation&25&n.a.\\
+	\hline 
+\end{tabular}
+\caption{\textbf{Parameters.} Parameters for the neural field model and the reduced model and the estimation procedure.}
+\label{tab:Parameters}
+\end{table*} 
 \subsection{Experiment I}
@@
 	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
-(\textbf{A}) The reconstructed field of the reduced model at $j=0$.
-(\textbf{B}) The reconstructed field at $j=1$.
-(\textbf{C}) The reconstructed field at $j=2$.
-(\textbf{D}) The reconstructed field at $j=3$.
-(\textbf{E}) The reconstructed field at $j=4$.
+(\textbf{A}) The reconstructed field of the reduced model using wavelet upto $j=0$ with $n_x=17$.
+(\textbf{B}) The reconstructed field using wavelets upto $j=1$ with $n_x=33$.
+(\textbf{C}) The reconstructed field  using wavelets upto $j=2$ with $n_x=65$.
+(\textbf{D}) The reconstructed field using wavelets upto $j=3$ with $n_x=131$.
+(\textbf{E}) The reconstructed field using wavelets upto $j=4$ with $n_x=263$.
 (\textbf{F}) The actual field.}

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits
added connectivity kernel generator in result section and clarified the definition of Bspline scaling and wavelet functions

@@
 \begin{align}
-\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \\	
-\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).
+\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \label{eq:generalscalingfinction}\\	
+\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).  \label{eq:generalwaveletfinction}
 \end{align}
@@
 Fig.~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero.
-Note in general the supports of the scaling and wavelet functions are given by
-\begin{align}
-	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \\  
-  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right] 
-	\end{align} 
+Note in general the supports of B-spline scaling and wavelet functions are given by
+\begin{align}
+	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \label{eq:ScalingSupport}\\  
+  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right],\label{eq:WaveletSupport}
+	\end{align}    
+where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.
 \begin{figure}[!t]
@@
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
+Data is generated using the connectivity kernel composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by
+\begin{equation}\label{eq:ConnectivityKernelForData}
+	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r')
+\end{equation}
 
@@
 $j=0$ to $j=4$.
+All parameters for the model are given in Table~\ref{tab:Parameters}.
 

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
-Data is generated using the connectivity kernel composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by
+The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by
 \begin{equation}\label{eq:ConnectivityKernelForData}
-	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r')
+	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r').
 \end{equation}

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor change
added a paper from Breakspear
general correction

@@
 \usepackage[usenames,dvipsnames]{color}  
-%This bit is how to use hyperlink without stupid coloured rectangles around it
+%This bit is how to use hyperlink without  coloured rectangles around it
 \usepackage{float}
@@
 	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
-	$\boldsymbol\varepsilon_t$ & Observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
 	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$.
-The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel \parham{in equation 2 its written $w(r,r')$} and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
 The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively.
@@
 \begin{equation}\label{eq:ObservationEquation}
-	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
+	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
 \end{equation}
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
 \parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}
@@
 \begin{equation}
- v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
 \label{eq:FieldExpansion}
@@
 \begin{align}
-\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
+\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]
+\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}]
 \label{FieldWeights} \\
@@
 \cdots &
-\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\
+\boldsymbol\psi_{j}^\top(r)\end{array}\right] \\
 \label{FieldBasisVector}
@@
 \cdots &
-\boldsymbol\psi_{J}^\top(r)\end{array}\right],
+\boldsymbol\psi_{j}^\top(r)\end{array}\right],
 \end{align}
@@
 
-\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic where}
-\begin{equation}
-	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 
-\end{equation}
+\parham{The state-transition equation can be simplified if the chosen family of scaling and wavelet functions are isotropic where}
+\begin{equation}
+	\boldsymbol{\lambda}_{i}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{i}+r'-r). 
+\end{equation}
+where $c_i$ is the centre of the $i$th basis function of the kernel decomposition.
 Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
 With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel.
-This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions.
+This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined once, since these are static functions.
 This has major computation advantages when solving the estimation problem.
@@
 \begin{equation}\label{eq:Gammaij}
-	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r,
-\end{equation}
-giving
+	\left[\Gamma(r')\right]_{:i} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{i} + r'-r\right) \,\mathrm{d}r,
+\end{equation} 
+ where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$th column of  $\left[\Gamma(r')\right]$ giving
 \begin{equation}
@@
 \begin{equation}\label{eq:ReducedObservationEquation} 
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\epsilon}_t,
 \end{equation}
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005}.
+It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2010}.
 %\dean{This is a test to see if we can fit something about Breaky's paper in here.
@@
 Finally, future work should be directed towards applying and validating the framework on real data.
-
+\newpage
 \appendix

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \end{equation} 
- where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$th column of  $\left[\Gamma(r')\right]$ giving
+ where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$-th column of  $\left[\Gamma(r')\right]$ giving
 \begin{equation}
@@
  N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
-  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
+  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
  \end{align}
@@
 \left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
-\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
+\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
  \end{align}
@@
 	\end{align}    
-where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.
+\parham{where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.}
 \begin{figure}[!t]
@@
 \begin{align}      
-	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m}} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
 \end{align}

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor correction
minor edit
minor correction for result section

@@
 \end{align}
- From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
+ From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
 This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
@@
 \begin{equation}\label{eq:ConnectivityKernelForData}
-	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r').
-\end{equation}
+	w(r-r')=\theta_1\times N_{4;1,2}(r-r')+\theta_2\times N_{4;0,2}(r-r'),
+\end{equation}
+with $\theta_1=200$ and $\theta_2=-100$.
 
@@
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
-The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
+The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor correction to result section

@@
 Two different experiments were designed to test the framework.
-In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
+In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run.
 This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization, the frequency response of the observed field used to decide on the level...

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
another minor correction for result section

@@
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
-The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
+The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.

### 2012-02-06 Multiresolution_framework/ltx/manuscript.tex
edits to intro and method

--- 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
@@
 \usepackage[usenames,dvipsnames]{color}  
-%This bit is how to use hyperlink without  coloured rectangles around it
+%This bit is how to use hyperlink without stupid coloured rectangles around it
 \usepackage{float}
@@
 \ead{parham.aram@univ-amu.fr}
-\author[DEEE,BEI,UE]{D. R. Freestone}
-\ead{dfreestone@bionicear.org} 
+\author[DEEE]{D. R. Freestone}
+\ead{deanrf@unimelb.edu.au} 
 \author[UE,CU]{M. Dewar}
@@
 \ead{kenneth.scerri@um.edu.mt}
-\author[DEEE,BEI]{D. B. Grayden}
+\author[DEEE]{D. B. Grayden}
 \ead{grayden@unimelb.edu.au}
@@
 \address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
-\address[DEEE]{Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
-\address[BEI]{The Bionic Ear Institute, East Melbourne, VIC, Australia}
-\address[UE]{Institute for Adaptive and Neural Computation, University of Edinburgh, Edinburgh, UK}
+\address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
 \address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
@@
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-\parham{Examples are, the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1997}.
+Examples are the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1997}.
 The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
-The latter,  can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a CDF of the probability of firing) to mean firing rates of neural masses.} The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
+The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a CDF of the probability of firing) to mean firing rates of neural masses.
+The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
 
@@
 \begin{figure}[t]
-	\centering
+	% \centering
 		\includegraphics[scale=1]{./Graph/fig1.pdf}
@@
 The solution to this problem was proposed by \citet{Breakspear2005} in using a wavelet decomposition.
-This paper is directed at developing a framework for patient-specific multi-resolution neural field models.
+This paper is directed at developing a framework for patient-specific multi-resolution neural field models, forming a fundamental link between data and theory.
 
@@
 	\hline
-	$\Omega$ & Spatial domain & n.a.\\
-	$\mathbf{r}$ & Spatial location & [mm, mm]\\
-	$t$ & Time & s\\
+	$\Omega$ & spatial domain & n.a.\\
+	$\mathbf{r}$ & spatial location & [mm, mm]\\
+	$t$ & time & s\\
 	\hline
@@
 	\hline
-    $y_t$ & Observation & mV\\
-    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
-	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
-	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
-	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
-	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
-	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
-	$h(t)$ & Post-synaptic response kernel & mV\\
-	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
+    $y_t$ & observation & mV\\
+    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
+	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
+	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
+	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
+	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
+	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
+	$h(t)$ & post-synaptic response kernel & mV\\
+	$\tau$, $\xi$ & membrane time constant \& time constant parameter & s, n.a.\\
 	$\delta(t)$ & Dirac-delta function & n.a.\\
 	\hline
-	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
-	\hline                                                   
-	$\phi_{j,l}(r)$&Scaling function&n.a\\
-	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
-	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
-	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
-	$N_m(r)$&$m$-th order B-spline function&n.a.\\
-	$\varphi_m(r)$&$m$-th order B-spline wavelet function&n.a.\\
-	\hline
 	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
 	\hline
-		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
-		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
-   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
-		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$&mV\\ 
-		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
-		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
-   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
-    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
-   	$\mathbf{C}$ & Observation matrix & n.a. \\
+   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
+   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
+   	$\mathbf{C}$ & observation matrix & n.a. \\
 	\hline
@@
 	\hline
-	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
-	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
-	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
-	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
-	$M_t$& Cross-covariance matrix & mV$^2$\\
-	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
-	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
-	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
-	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
-	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Upsilon$&Lower bound coefficient matrices&??\\
+	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
+	$\hat{\mathbf{x}}_t^{b}$ & backward posterior state estimates & mV\\
+	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
+	$P^b_t$ & backward posterior covariance matrices & mV$^2$\\
+	$M_t$& cross-covariance matrix & mV$^2$\\
+	$\mathcal K_{t} $ & filter gain & n.a.\\ 
+	$\mathcal S_{t} $ & smoother gain & n.a.\\
 	\hline
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$.
-The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel \parham{in equation 2 its written $w(r,r')$} and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
 The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively.
@@
 \end{equation}
-where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time.
+where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step.
 % The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
@@
 \begin{equation}
-cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\sigma_d\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
+cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
 \label{eq:FieldDisturbance}
 \end{equation}
-where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance} and $\delta(\cdot)$ is the Dirac-delta function.
+where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function} and $\delta(\cdot)$ is the Dirac-delta function.
 %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
@@
 \begin{equation}\label{eq:ObservationEquation}
-	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
+	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
 \end{equation}
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
-\parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}
+Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+The observation kernel models the pickup range of the electrical fields of the brain.
+The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.
 
 \section{MRA of the IDE in State-Space}
-\parham{The purpose of} forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
 Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.
 
-\parham{The goal of this section is to demonstrate} how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-\parham{Therefore, the goal is to form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
+form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 
@@
 \begin{align}
-\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \label{eq:generalscalingfinction}\\	
-\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).  \label{eq:generalwaveletfinction}
+\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \\	
+\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).
 \end{align}
@@
 \begin{equation}
- v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
+ v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
 \label{eq:FieldExpansion}
@@
 \begin{align}
-\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 
+\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
 \label{KernelWeights} \\
-\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,j}^\top\end{array}]
+\mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}]
 \label{FieldWeights} \\
@@
 \cdots &
-\boldsymbol\psi_{j}^\top(r)\end{array}\right] \\
+\boldsymbol\psi_{J}^\top(r)\end{array}\right] \\
 \label{FieldBasisVector}
@@
 \cdots &
-\boldsymbol\psi_{j}^\top(r)\end{array}\right],
+\boldsymbol\psi_{J}^\top(r)\end{array}\right],
 \end{align}
@@
 
-\parham{The state-transition equation can be simplified if the chosen family of scaling and wavelet functions are isotropic where}
-\begin{equation}
-	\boldsymbol{\lambda}_{i}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{i}+r'-r). 
-\end{equation}
-where $c_i$ is the centre of the $i$th basis function of the kernel decomposition.
+\parham{The state-transition equation can be simplified if the chosen family of wavelets are isotropic where}
+\begin{equation}
+	\boldsymbol{\lambda}_{j,l}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{j,l}+r'-r). 
+\end{equation}
 Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
 With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel.
-This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined once, since these are static functions.
+This convolution can be calculated analytically when using B-spline wavelets and can be predefined once, since these are static functions.
 This has major computation advantages when solving the estimation problem.
@@
 \begin{equation}\label{eq:Gammaij}
-	\left[\Gamma(r')\right]_{:i} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{i} + r'-r\right) \,\mathrm{d}r,
-\end{equation} 
- where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$-th column of  $\left[\Gamma(r')\right]$ giving
+	\left[\Gamma(r')\right]_{:j,l} = T_s \mathbf{\Lambda}_{x}^{-1}\int_{\Omega} \boldsymbol\mu\left(r\right)\boldsymbol\lambda\left(2c_{j,l} + r'-r\right) \,\mathrm{d}r,
+\end{equation}
+giving
 \begin{equation}
@@
 \begin{equation}\label{eq:ReducedObservationEquation} 
-	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\epsilon}_t,
+	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
 \end{equation}
@@
  N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
-  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
+  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
  \end{align}
@@
 \left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
-\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
+\left[\mathbf q\right]_n&= \sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
  \end{align}
@@
 Fig.~\ref{fig:MRA-Figure1} shows the cubic B-spline scaling function and its associated wavelet function with dilation and translation parameters set to zero.
-Note in general the supports of B-spline scaling and wavelet functions are given by
-\begin{align}
-	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \label{eq:ScalingSupport}\\  
-  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right],\label{eq:WaveletSupport}
-	\end{align}    
-\parham{where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.}
+Note in general the supports of the scaling and wavelet functions are given by
+\begin{align}
+	\mathrm{supp}(N_{m;j,l})&=\left[\frac{l}{2^j},\frac{m+l}{2^j}\right] \\  
+  \mathrm{supp}(\varphi_{m;j,l})&=\left[\frac{l}{2^j},\frac{2m-1+l}{2^j}\right] 
+	\end{align} 
 \begin{figure}[!t]
@@
 \begin{align}      
-	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
-\end{align}
- From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m-1}} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\sum_{n=0}^{3m-2} \frac{\left(-1\right)^n}{2^{m}} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
+\end{align}
+ From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined.
 This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
@@
 We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs: smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
-Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Note that the following quantities from the forward iteration (filtering) should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
 Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
@@
 \caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound, $\mathcal{Q}(\boldsymbol{\theta},\boldsymbol{\theta'})$, is maximized after each iteration to update the parameter estimates.}
+The lower bound is maximized after each iteration to update the parameter estimates.}
 \label{alg:MRA-RTS}
@@
 \end{align}
-The factor of 2 is included to simplify the derivation in the later steps. Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
+Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
 \begin{align}
@@
 \end{align}
-The rest of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
-The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
-To begin, the first trace is written in terms of element-wise summations
+
+The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations
 \begin{align}\label{eq:MRA-trace1}
@@
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
-The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by
-\begin{equation}\label{eq:ConnectivityKernelForData}
-	w(r-r')=\theta_1\times N_{4;1,2}(r-r')+\theta_2\times N_{4;0,2}(r-r'),
-\end{equation}
-with $\theta_1=200$ and $\theta_2=-100$.
 
@@
 In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\varepsilon_t$, were regenerated each run.
-This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization, the frequency response of the observed field used to decide on the level...
-.
-In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting upto a certain level of approximation, i.e.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting for a different level of approximation, i.e.
 $j=0$ to $j=4$.
-All parameters for the model are given in Table~\ref{tab:Parameters}.
 
@@
 The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
-The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
+The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\gamma(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).
 The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
-The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations.
+The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude where the distance between adjacent sensors was $0.5$~mm, resulting into $n_y = 161$ observations.
 The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}.
@@
 This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
-\begin{table*}[!ht]
-\begin{tabular}{|c|l|c|l|}
-	\hline
-	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
-	\hline
-	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
-	\hline
-	$\Delta$ & spatial discretisation step & 0.01 & mm \\
-	$T_s$ & time step & $0.001$ & s\\
-	$T$ & number of time steps used in estimation & 900 & n.a.\\
-	\hline 
-\multicolumn{4}{|c|}{\emph{Model}}\\
-	\hline
-	$\tau$ & membrane time constant & 0.01 & s$^{-1}$ \\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
-	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters (data generation) & $\left[\begin{array}{cc}
-	200 & -100
-	\end{array}
-	\right]^{\top}$ & mV.spike$^{-1}$\\
-	%$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
-	$n_y$ & number of sensors & 161 & n.a.\\ 
-	$\Delta_y$ & distance between adjacent sensors & 0.05 & mm\\
-	$\sigma_{m}$ & observation kernel full width at half maximum & 0.08 & mm \\
-	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
-	$\sigma_{\eta}$& disturbance covariance function full width at half maximum & 0.18 & mm\\
-	$\sigma_{d}$ & disturbance variance & 0.53 & mV \\
-	\hline 
-	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
-	\hline
-	$n_x$ & number of field basis functions&& n.a.\\
-	$   $ &Experiment~I&131&\\
-	$   $ &Experiment~II&17, 33, 65, 131, 263&\\ 
-	\hline 
-	\multicolumn{4}{|c|}{\emph{Estimation}}\\ 
-	\hline
-	$n_{\theta}$&number of connectivity kernel basis functions for estimation&25&n.a.\\
-	\hline 
-\end{tabular}
-\caption{\textbf{Parameters.} Parameters for the neural field model and the reduced model and the estimation procedure.}
-\label{tab:Parameters}
-\end{table*} 
 \subsection{Experiment I}
@@
 	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
-(\textbf{A}) The reconstructed field of the reduced model using wavelet upto $j=0$ with $n_x=17$.
-(\textbf{B}) The reconstructed field using wavelets upto $j=1$ with $n_x=33$.
-(\textbf{C}) The reconstructed field  using wavelets upto $j=2$ with $n_x=65$.
-(\textbf{D}) The reconstructed field using wavelets upto $j=3$ with $n_x=131$.
-(\textbf{E}) The reconstructed field using wavelets upto $j=4$ with $n_x=263$.
+(\textbf{A}) The reconstructed field of the reduced model at $j=0$.
+(\textbf{B}) The reconstructed field at $j=1$.
+(\textbf{C}) The reconstructed field at $j=2$.
+(\textbf{D}) The reconstructed field at $j=3$.
+(\textbf{E}) The reconstructed field at $j=4$.
 (\textbf{F}) The actual field.}
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2010}.
+It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005}.
 %\dean{This is a test to see if we can fit something about Breaky's paper in here.
@@
 Finally, future work should be directed towards applying and validating the framework on real data.
-\newpage
+
 \appendix

### 2012-02-06 Multiresolution_framework/ltx/manuscript.tex

--- 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
@@
 where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
-\parham{The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.}
+Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+The observation kernel models the pickup range of the electrical fields of the brain.
+The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.
 
 \section{MRA of the IDE in State-Space}
-\parham{The purpose of} forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
+The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field.
 Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.
 
-\parham{The goal of this section is to demonstrate} how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-\parham{Therefore, the goal is to form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
+form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
added fig12 in pdf format
loads of minor edits from start to spatial freq section

@@
 
-Typically, the experimentalist only has access the net field generated by the multi-resolution architecture.
+Typically, the experimentalist only has access the net field generated by the multi-resolution architecture of the cortex.
 Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
@@
 
-The single layer homogeneous neural field model in the most general form is described by the equation
+The single layer homogeneous neural field model, in the most general form, is described by the equation
 \begin{equation}
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$.
-The function $h(t)$ describes the post-synaptic response kernel, $w(\mathbf{r})$ describes the connectivity kernel \parham{in equation 2 its written $w(r,r')$} and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
 The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively.
@@
 These are also shown in Fig.~\ref{fig:Modelcomponents}.
-The form of $w(\mathbf{r})$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field.
+The form of $w(\mathbf{r},\mathbf{r}')$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field.
 By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
@@
 \end{figure}
-
 The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially colored but temporally white, with covariance function 
@@
 Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models.
-
 The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-form} a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
+% form a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 
@@
 The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively.
-\dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
-The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
+The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest.
+For example, at scales corresponding to higher spatial frequencies a greater number of wavelets, and thus spatial shifts are required to adequately sample the spatial characteristics of the field.
+The number of scales depends on the spectral characteristics of the field, where higher spatial frequencies require a more scales.
+Spatial frequency analysis will be described later in Section~\ref{sec:freq_anal} in greater detail.
+Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.
 
@@
 \end{equation}
-with covariance (see \citep{Freestone2011} for proof)
+with covariance (see \citet{Freestone2011} for proof)
 \begin{equation}\label{eq:CovMatrix}
@@
 
-\parham{The state-transition equation can be simplified if the chosen family of scaling and wavelet functions are isotropic where}
-\begin{equation}
-	\boldsymbol{\lambda}_{i}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{i}+r'-r). 
-\end{equation}
-where $c_i$ is the centre of the $i$th basis function of the kernel decomposition.
+The state-transition equation can be simplified if the chosen family of scaling and wavelet functions are isotropic where
+\begin{equation}
+	\boldsymbol{\lambda}_{i}(r-r') = \boldsymbol{\lambda}(2\mathbf{c}_{i}+r'-r), 
+\end{equation}
+where $c_i$ is the centre of the $i^{th}$ basis function of the kernel decomposition.
 Following this, we can switch the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
 With this switch the convolution is now between the scaling functions and wavelets for the field and the scaling functions and wavelets for the connectivity kernel.
-This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined once, since these are static functions.
+This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined, since these are static functions.
 This has major computation advantages when solving the estimation problem.
-\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field.
-} The predefined convolution can be written as
+%\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field.
+}
+The predefined convolution can be written as
 \begin{equation}\label{eq:Gammaij}
@@
 \end{equation} 
- where $\left[\Gamma(r')\right]_{:i}$ denotes the $i$-th column of  $\left[\Gamma(r')\right]$ giving
+ where $\left[\Gamma(r')\right]_{:i}$ denotes the $i^{th}$ column of  $\left[\Gamma(r')\right]$ giving
 \begin{equation}
@@
 
-B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.
+B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b}, \citet{Chui1992} and \citet{Unser1993}.
 The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
@@
 \end{equation}
-Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citep{DeBoor2001}
+Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citet{DeBoor2001}
 \begin{equation}\label{eq:MRA-DoBoorFormula}
@@
 \begin{equation}
-	\sum_{l}N_m(r+l)\equiv1
-	\end{equation}
-	\parham{This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.}
+	\sum_{l}N_m(r+l)\equiv1.
+	\end{equation}
+This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.
 
@@
  N_2(k)=\delta(k-1)\quad k\in \mathbb{Z}, \\
- N_{m}\left(k\right)=\frac{k}{m-1}N_{m-1}\left(k\right)+\frac{m-k}{m-1}N_{m-1}\left(k-1\right) \quad k=1,2,\dots,m-1
+ N_{m}\left(k\right)=\frac{k}{m-1}N_{m-1}\left(k\right)+\frac{m-k}{m-1}N_{m-1}\left(k-1\right) \quad k=1,2,\dots,m-1.
   \end{cases}
@@
  \end{align}
-and $\left[\cdot\right]_n$ denotes the $n$-th element of the vector coefficients \citep{Chui1992}. \dean{Need to explicitly say why this is important and what this gives us here.}
+and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.
 
@@
 	\end{align}    
-\parham{where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.}
+where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.
 \begin{figure}[!t]
@@
  \end{equation}
-  \parham{Note from Eq.~\eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.}
+Note from Eq.~\eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.
 
 In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
-For scaling functions this can be done  by usingEq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
+For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
 \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
@@
  \end{figure}  
- In this paper, 4th -- order cardinal B-spline scaling and wavelet functions are used, resulting in  8th and 12th order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+In this paper, $4^{th}$ -- order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^th$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[t]
@@
  \end {table}
-\subsection{Frequency Analysis}
+\subsection{Frequency Analysis}\label{sec:freq_anal}
 To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}.
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/fig12.png}
+		\includegraphics[scale=1]{./Graph/fig12.pdf}
 	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
edits to estimation section

@@
 &=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}.
-\end{align}
+&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
+\end{align}
+where $i=\sqrt{-1}$.
 The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
@@
 \end{align}
-\dean{Need to say how the FT is used somewhere here before proceeding.} \parham{The Fourier transform of the $m$-th order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
+The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
 \begin{align}      
@@
 From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
-This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
+This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
+
 \section{State and Parameter Estimation}
+The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm.
+Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.
+
 There exist many variations of state and parameter estimation methods for state-space models.
@@
 
-To demonstrate the MRAIDE framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
 Note that there is a difference between forward and inverse modeling when making these assumptions.
 For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
+The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm.
+\dean{The loss in model accuracy may be offset estimation accuracy.
+}
 
@@
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
+
+% The linearised activation function is 
+% \begin{align}
+% 	\hat{f}(v_t\left(\mathbf{r}\right)) &= f(v_0) + f'(v_0)(v_t\left(\mathbf{r}\right) - v_0) \\
+% 	&= \frac{2 + \varsigma(v_t\left(\mathbf{r}\right) - v_0)}{4}. \label{eq:LinearActivationFunction} 
+% \end{align}
 
@@
 where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function.
-This problem cannot be solved separately as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
+This dual estimation problem cannot be solved separately, as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
 One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
-A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \cite{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second  when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \cite{Bilmes1998}, the weights of the field basis functions in this case.
-The EM algorithm, when used in the latter context \cite{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \citep{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
 \begin{equation}
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space models, the E-step corresponds to the smoothing problem which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
-For the M-step, a lower bound on the likelihood function should be constructed where the steps needed
-to compute the required quantities are very dependent on the particular application which wii be described in detail for our problem.
+For state-space models, the E-step corresponds to the smoothing problem, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
+to compute the required quantities are very dependent on the particular application. This will be described in detail for our problem.
 
@@
 Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors.
-Here the latter is chosen as shown in the block diagram ensuring the resultant kernel is stable.
+Here the latter is chosen as shown in the block diagram ensuring the resultant initial kernel estimate leads to a stable system.
 \begin{figure}[!t]
@@
 \subsection{E-step}
-As mentioned earlier the E-step for state-space models is equivalent to the smoothing problem.
+As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem.
 We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \cite{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}) along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
 Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
-Also the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
+Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
 \renewcommand{\arraystretch}{1.7}
@@
  \subsection{M-step}
-It is rather straightforward to show that 
+The lower bound on the lower log-likelihood function is given by \citep{Bishop2006} 
 \begin{equation}
@@
 \end{equation}
-is a lower bound on the log-likelihood function \cite{Bishop2006} (see \ref{ap:Lowerbound} )  where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and where $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+(see \ref{ap:Lowerbound} ) where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
edits to results and discussion

@@
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
-Most recently, a framework was developed where a finite element model (FEM) of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
+Most recently, a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 \begin{equation}
-\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{const.}
+\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{constant},
 \end{equation}
@@
 \end{align}
-Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound which is to be maximized for the optimal parameter estimates.
+Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound, which is to be maximized for the optimal parameter estimates.
 Note that the expectation distributes over the trace sum.
@@
 \end{align}
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \cite{Gibsona2005}, (see \ref{ap:Xiderivation} for more details)
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005}, (see \ref{ap:Xiderivation} for more details)
 \begin{align}
@@
 \end{align} 
-The rest of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
+The goal of the remainder of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
 The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
@@
 \end{equation}
-where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix, and where
-each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix. Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
 \begin{align}\label{eq:Uij}
-\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr,
-\end{align}
-where $[\cdot]_{i:} $ denotes the i-th row.
+\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
+\end{align}
+where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
 By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:MRA-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
@@
 \subsection{Stopping rule}
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \cite{McLachlan1997}. The stopping rule adopted herein is
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
 \begin{equation}
@@
 \subsection{Computational complexity} 
-All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation in \citet{Dewar2009}.
-The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method in \citet{Dewar2009} is also identified.
-It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to \citet{Dewar2009}.
+All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
+The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified.
+It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to the method proposed in \citet{Dewar2009}.
 This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.
@@
 \end{equation}
-with $\theta_1=200$ and $\theta_2=-100$.
+with $\theta_1=200$ and $\theta_2=-100$. \dean{This is depicted in Figure~\ref{fig:}}
 
@@
 In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run.
-This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization, the frequency response of the observed field used to decide on the level...
-.
-In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting upto a certain level of approximation, i.e.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
+\dean{the frequency response of the observed field used to decide on the level...} .
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
 $j=0$ to $j=4$.
@@
 This is shown in Fig.~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
-The spatial bandwidths of wavelets was calculated analytically using  Eq.~\eqref{eq:MRA-Wavelettransform}.
-The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions at $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively at $j=0$, $j=1$, $j=2$ and $j=3$.
+The spatial bandwidths of wavelets were calculated analytically using Eq.~\eqref{eq:MRA-Wavelettransform}.
+The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions for $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively for $j=0$, $j=1$, $j=2$ and $j=3$.
 \begin{figure}[!t]
@@
  \end{figure}
+
 The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
@@
 Fig.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
-A total number of 25 basis functions was used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$ accordingly.
+A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively.
 \begin{figure}[!t]  
@@
 \end{figure}
+
 One snap shot of the field reconstruction, at different levels of approximation is given in Fig.~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
@@
 In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
 This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
@@
 
-For a larger space or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
-One solution to this problem could be expectation-conditional maximization (ECM) \citep{Meng1993,Meng1994} which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
+For a larger space, or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
+One solution to this problem could be expectation-conditional maximization (ECM) \citep{Meng1993,Meng1994}, which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
 The ECM is a class of generalized EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximized \citep{Fessler1994}.
-
 For systems with a high number of states, the ensemble Kalman smoother (EnKS) \citep{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
@@
 In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations.
-Although provided formulations can be easily extended into two dimensions the  computational load of the estimation algorithm will be significant.
+The formulations provided in this paper can be easily extended to two dimensions.
+However, the computational load of the estimation algorithm will be significant.
 It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
@@
 
-Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
-
+Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
-In small networks the delays via propagation can be neglected, however they must be accounted for in large scale networks.
+In small networks the delays via propagation can be neglected.
+However, delays must be accounted for in large scale networks.
 For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks.
 Finally, future work should be directed towards applying and validating the framework on real data.
+
 \newpage

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
minor edits to appendix

@@
 \section{Lower bound on likelihood function}\label{ap:Lowerbound}
-A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix.
-We want to maximize the likelihood function which is difficult to perform directly
-\begin{equation}
- p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)d\mathbf X.
-\end{equation}   
+A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix. We want to maximize the likelihood function, 
+\begin{equation}
+ p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)\mathrm{d}\mathbf X,
+\end{equation}
+which is difficult to perform directly.
 Maximizing the likelihood in terms of the parameter set is equivalent to the log-likelihood maximization, as both the likelihood and log-likelihood functions share the same maximizer due to the monotonicity of the logarithm function.
@@
 \begin{align}
- \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \label{eq:EM-decomposition1}\\
-\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X. \label{eq:EM-decomposition2}
+ \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \label{eq:EM-decomposition1}\\
+\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X.
+\label{eq:EM-decomposition2}
 \end{align}
@@
 \begin{align}
-	\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X \nonumber\\
-	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace d\mathbf X\nonumber\\
-	&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)d\mathbf X.
+	\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \nonumber\\
+	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X\nonumber\\
+	&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)\mathrm{d}\mathbf X.
 \end{align}
 Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
-Note Eq.~\eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$, therefore,
+We also note that Eq.~\eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$.
+Therefore,
 \begin{equation}

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
added Viktor to the author list
just highlighted a sentence to discuss

@@
 \ead{deanrf@unimelb.edu.au} 
-\author[UE,CU]{M. Dewar}
+\author[CU]{M. Dewar}
 \ead{mike.dewar@columbia.edu}
@@
 \ead{kenneth.scerri@um.edu.mt} 
+ \author[TNG]{V. Jirsa}
+\ead{viktor.jirsa@univ-amu.fr}
 \author[DEEE]{D. B. Grayden}
@@
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
-This is important for constructing the wavelets.
-For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
+\parham{This is important for constructing the wavelets.} For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
 \begin{align}

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
minor edits to EM algorithm

@@
 	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
-	$N_m(r)$&$m$-th order B-spline function&n.a.\\
-	$\varphi_m(r)$&$m$-th order B-spline wavelet function&n.a.\\
+	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
+	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
 	\hline
@@
 B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b}, \citet{Chui1992} and \citet{Unser1993}.
-The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
+The scaling functions are $m^{th}$ order B-splines and the compact support wavelet functions are a linear combination of scaling functions.
 B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases.
@@
 
-The $m$-th  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
+The $m^{th}$  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
 \begin{equation}
@@
  \end{figure}  
-In this paper, $4^{th}$ -- order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^th$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+In this paper, $4^{th}$ -- order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[t]
@@
 A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-There are two main applications of the EM algorithm:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional however missing (or hidden) variables \citep{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as missing or hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case.
 The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
  \subsection{M-step}
-The lower bound on the lower log-likelihood function is given by \citep{Bishop2006} 
+The lower bound on the log-likelihood function is given by \citep{Bishop2006} 
 \begin{equation}

### 2012-02-10 Multiresolution_framework/ltx/manuscript.tex
minor edits
added latest friction work

@@
 The first work (to the authors best knowledge) describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\citep{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003, Pinotsis2011}.
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
@@
 To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly.
-The implementation of the framework in the non-linear case can be addressed as future work.
+The implementation of the framework in the nonlinear case can be addressed as future work.
 Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.

### 2012-02-10 Multiresolution_framework/ltx/manuscript.tex
changed the citation of the recent work of Friston

--- 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
@@
 This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003}.
-Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009}.
+Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2011}.
 Most recently, a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.

### 2012-02-11 Multiresolution_framework/ltx/manuscript.tex
moved M-step to the appendix

@@
 The lower bound on the log-likelihood function is given by \citep{Bishop2006} 
-\begin{equation}
+\begin{equation}\label{eq:Bishopbound}
 	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right], 
@@
 
-The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
-The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
- \begin{equation}\label{eq:jointdistribution}
-  p(\mathbf X,\mathbf Y;\boldsymbol \theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
- \end{equation}
-The $\mathcal Q$-function, or lower-bound on the likelihood, can be expressed in terms of the joint distribution components
- \begin{align}
-  \mathcal Q(\boldsymbol \theta,\boldsymbol\theta')&=\mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right] \nonumber \\
- &=\mathbf E_{\boldsymbol\theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
- +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
- \end{align}   
-It should be noted that neither $p(\mathbf y_{t+1}|\mathbf x_{t+1})$ nor $p(\mathbf x_0)$ are functions of the parameter set and therefore the $\mathcal Q$-function can be rewritten as
-\begin{equation}
-\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{constant},
-\end{equation}
-where the constant term can be ignored as it is independent of the parameters.
-Under the condition that the state distribution is Gaussian --- ignoring the normalizing term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as
-\begin{align}
-p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
-\end{align}
-Twice the logarithm of the above distribution, once expanded, is given by
-\begin{align}\label{eq:Qfunction}
-2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
-&-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
-\end{align}
-The factor of 2 is included to simplify the derivation in the later steps. Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
-\begin{align}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
-&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t,\nonumber \\
+For the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound defined by Eq.~\eqref{eq:Bishopbound} is a quadratic of the form (see \ref{ap:QDerivation} for derivation)
+\begin{equation}\label{eq:MRA-QCompact}
+\mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
+\end{equation}
+where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation~\eqref{eq:MRA-QCompact} is maximum at
+\begin{align}\label{eq:MRA-thetahat}
+\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top,
 \end{align}
 where
-\begin{equation}
-\beta=-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,
-\end{equation}
-is constant with respect to the parameter $\boldsymbol\theta$, and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
-Taking the trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
-\begin{align}\label{eq:Qfunctionintrace}
-2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
-&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace\nonumber \\
-&-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace.
-\end{align}
-Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound, which is to be maximized for the optimal parameter estimates.
-Note that the expectation distributes over the trace sum.
-Therefore,
-\begin{align}\label{eq:MRA-QintermsofTraces}
-\mathcal Q(\boldsymbol \theta, \boldsymbol\theta')&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \boldsymbol\Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
-&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace,
-\end{align}
-where
-\begin{align}
-\boldsymbol\Xi_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \label{eq:MRA-Xi0}\\
-\boldsymbol\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right] \label{eq:MRA-Xi1}.
-\end{align}
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005}, (see \ref{ap:Xiderivation} for more details)
+\begin{align}
+\boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}\label{eq:epsilon0} \\
+\boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \label{eq:epsilon1}\\
+\boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i},\label{eq:Epsilon}
+\end{align} 
+where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where 
+\begin{align}
+\left[ \Gamma_1\right]^{j,i} &=\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i},\\
+\left[ \Gamma_2\right] ^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
+\end{align}
+Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+\begin{align}\label{eq:Uij}
+\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
+\end{align}
+where $[\cdot]_{i:} $ denotes the $i^{th}$ row.  Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
+\begin{equation}\label{eq:MRA-LambdaThetaElements}
+\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta.
+\end{equation}
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005},
 \begin{align}
@@
  \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).  \label{eq:Xi1}
-\end{align} 
-The goal of the remainder of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
-The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
-To begin, the first trace is written in terms of element-wise summations
-\begin{align}\label{eq:MRA-trace1}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i=1}^{n_x}\left[ \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right]_{ii} \nonumber \\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}  \boldsymbol\Lambda_{\theta}\right]_{ji}\nonumber\\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{jk} \left[ \boldsymbol\Lambda_{\theta}\right]_{ki},
-\end{align}
-where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix. Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
-\begin{equation}\label{eq:MRA-LambdaThetaElements}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta,
-\end{equation}
-where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix. Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}\label{eq:Uij}
-\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
-\end{align}
-where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
-By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:MRA-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}\boldsymbol\theta \nonumber \\
-&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta,
-\end{align}
-where
-\begin{align}
-\left[ \Gamma_1\right]^{j,i} =\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}.
-\end{align}
-The second trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol \Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=
-\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_1\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta.
-\end{align}
-Likewise, the third trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
-\begin{align}
-\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j,k,m=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}[\boldsymbol\Lambda_{\theta}^{\top}]_{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\boldsymbol\Lambda_{\theta}]_{mi} \nonumber \\
-=&\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}~\boldsymbol\theta \nonumber \\
-&=\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\left[ \Gamma_2\right] ^{j,i}\boldsymbol\theta,
-\end{align}
-where
-\begin{align}
-\left[ \Gamma_2\right] ^{j,i}=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
-\end{align}
-Therefore the $\mathcal Q$-function can be rewritten as
-\begin{equation}\label{eq:MRA-QCompact}
-\mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
-\end{equation}
-where
-\begin{equation}\label{eq:epsilon0}
-\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i},
-\end{equation}
-\begin{equation}\label{eq:epsilon1}
-\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i},
-\end{equation}                                                                                 
-and
-\begin{equation}\label{eq:Epsilon}
-\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}.
-\end{equation}
-By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
-\begin{align}\label{eq:MRA-QDerivative}
-\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
-&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
-\end{align}
-Equating Eq.~\eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
-\begin{align}\label{eq:MRA-thetahat}
-\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
 \end{align} 
@@
 It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
+
+\section{Lower bound}\label{ap:QDerivation}
+For the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
+The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
+ \begin{equation}\label{eq:jointdistribution}
+  p(\mathbf X,\mathbf Y;\boldsymbol \theta)=\prod_{t=0}^{T-1} p(\mathbf y_{t+1}|\mathbf x_{t+1})p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)p(\mathbf x_0).
+ \end{equation}
+The $\mathcal Q$-function, or lower-bound on the likelihood, can be expressed in terms of the joint distribution components
+ \begin{align}
+  \mathcal Q(\boldsymbol \theta,\boldsymbol\theta')&=\mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right] \nonumber \\
+ &=\mathbf E_{\boldsymbol\theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf y_{t+1}|\mathbf x_{t+1})+\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)
+ +\sum_{t=0}^{T-1}2\ln p(\mathbf x_0)\right].
+ \end{align}   
+It should be noted that neither $p(\mathbf y_{t+1}|\mathbf x_{t+1})$ nor $p(\mathbf x_0)$ are functions of the parameter set and therefore the $\mathcal Q$-function can be rewritten as
+\begin{equation}
+\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}2\ln p(\mathbf x_{t+1}|\mathbf x_{t};\boldsymbol \theta)\right]+\mathrm{constant},
+\end{equation}
+where the constant term can be ignored as it is independent of the parameters.
+Under the condition that the state distribution is Gaussian --- ignoring the normalizing term, $1/(2\pi)^{\frac{n_x}{2}}\mid\boldsymbol\Sigma_w\mid^{-\frac{1}{2}}$ --- the conditional distribution $p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)$ can be written as
+\begin{align}
+p(\mathbf x_{t+1} | \mathbf x_{t};\boldsymbol\theta)=  \exp\left({-\frac{1}{2}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)^\top\boldsymbol\Sigma_w^{-1}\left(\mathbf x_{t+1}-\mathbf A\left(\boldsymbol\theta\right)\mathbf  x_t\right)}\right).
+\end{align}
+Twice the logarithm of the above distribution, once expanded, is given by
+\begin{align}\label{eq:Qfunction}
+2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\theta)=&-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf A( \boldsymbol\theta)\mathbf x_t\nonumber \\
+&-\mathbf x_t^\top\mathbf A^\top(\boldsymbol\theta)\boldsymbol\Sigma_w^{-1}\mathbf A(\boldsymbol\theta)\mathbf x_t.
+\end{align}
+The factor of 2 is included to simplify the derivation in the later steps. Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
+\begin{align}
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)=&\beta+2 T_s\varsigma\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t \nonumber \\
+&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t,\nonumber \\
+\end{align}
+where 
+\begin{equation}
+\beta=-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,
+\end{equation}
+is constant with respect to the parameter $\boldsymbol\theta$, and will disappear subject to differentiation with respect to $\boldsymbol\theta$.
+Taking the trace and rearranging, using the invariant cyclic permutations property of the trace, this distribution can be written as
+\begin{align}\label{eq:Qfunctionintrace}
+2\ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\theta)&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
+&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace\nonumber \\
+&-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \mathbf x_t\mathbf x_{t}^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace.
+\end{align}
+Rearranging and taking the expectation of the log-likelihood function over all time instants gives the required lower-bound, which is to be maximized for the optimal parameter estimates.
+Note that the expectation distributes over the trace sum.
+Therefore,
+\begin{align}\label{eq:MRA-QintermsofTraces}
+\mathcal Q(\boldsymbol \theta, \boldsymbol\theta')&=\beta+2 T_s\varsigma\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace-2\xi\varsigma T_s\mathrm{tr} \left\lbrace \boldsymbol\Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace \nonumber \\
+&-T_s^2\varsigma^2\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace,
+\end{align}
+where
+\begin{align}
+\boldsymbol\Xi_0&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t+1}^\top\right] \label{eq:app-Xi0}\\
+\boldsymbol\Xi_1&=\mathbf E_{\Theta'}\left[\sum_{t=0}^{T-1}\mathbf x_t\mathbf x_{t}^\top\right] \label{eq:app-Xi1}.
+\end{align}
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs (see \ref{ap:Xiderivation} for more details)
+
+The goal of the remainder of the derivation is to isolate $\boldsymbol\theta$ from the terms forming $\mathcal{Q}$.
+The three traces that form Eq.~\eqref{eq:MRA-QintermsofTraces} are dealt with in turn.
+To begin, the first trace is written in terms of element-wise summations
+\begin{align}\label{eq:MRA-trace1}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i=1}^{n_x}\left[ \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right]_{ii} \nonumber \\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}  \boldsymbol\Lambda_{\theta}\right]_{ji}\nonumber\\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{jk} \left[ \boldsymbol\Lambda_{\theta}\right]_{ki},
+\end{align}
+where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix. Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
+\begin{equation}\label{eq:MRA-LambdaThetaElements}
+\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta,
+\end{equation}
+where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix. Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+\begin{align}\label{eq:Uij}
+\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
+\end{align}
+where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
+By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:MRA-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_0\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}\boldsymbol\theta \nonumber \\
+&=\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_0\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta,
+\end{align}
+where
+\begin{align}
+\left[ \Gamma_1\right]^{j,i} =\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i}.
+\end{align}
+The second trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is dealt with in a similar manner, giving
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol \Xi_1\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=
+\sum_{i,j=1}^{n_x}\left[ \boldsymbol\Xi_1\right]_{ij}\left[ \Gamma_1\right] ^{j,i}\boldsymbol\theta.
+\end{align}
+Likewise, the third trace of Eq.~\eqref{eq:MRA-QintermsofTraces} is broken down into element-wise summations
+\begin{align}
+\mathrm{tr} \left\lbrace \boldsymbol\Xi_1 \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\right\rbrace&=\sum_{i,j,k,m=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}[\boldsymbol\Lambda_{\theta}^{\top}]_{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\boldsymbol\Lambda_{\theta}]_{mi} \nonumber \\
+=&\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}~\boldsymbol\theta \nonumber \\
+&=\boldsymbol\theta^\top\sum_{i,j=1}^{n_x}\left[\boldsymbol\Xi_1\right] _{i,j}\left[ \Gamma_2\right] ^{j,i}\boldsymbol\theta,
+\end{align}
+where
+\begin{align}
+\left[ \Gamma_2\right] ^{j,i}=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
+\end{align}
+Therefore the $\mathcal Q$-function can be rewritten as
+\begin{equation}\label{eq:appQCompact}
+\mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
+\end{equation}
+where
+\begin{equation}\label{eq:appepsilon0}
+\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i},
+\end{equation}
+\begin{equation}\label{eq:appepsilon1}
+\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i},
+\end{equation}                                                                                 
+and
+\begin{equation}\label{eq:appEpsilon}
+\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}.
+\end{equation}
+By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
+\begin{align}\label{eq:MRA-QDerivative}
+\frac{\partial \mathcal Q}{\partial \boldsymbol\theta}&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-T_s\varsigma(\boldsymbol\Upsilon^\top+\boldsymbol\Upsilon)\boldsymbol\theta \nonumber \\
+&=2T_s\varsigma(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top-2T_s\varsigma\boldsymbol\Upsilon^\top\boldsymbol\theta.
+\end{align}
+Equating Eq.~\eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
+\begin{align}\label{eq:MRA-thetahat}
+\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.
+\end{align}   
 \section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
edits to appendix

@@
 Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
-Note that the following quantities from the forward iteration should be stored when implementing the RTS smoother: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
 Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
@@
 \end{align}
-where $[\cdot]_{i:} $ denotes the $i^{th}$ row.  Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
-\begin{equation}\label{eq:MRA-LambdaThetaElements}
-\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta.
-\end{equation}
+where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
 The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005},
@@
 $\mathbf A(\boldsymbol\theta)$&Eq.~\eqref{eq:A_theta}&$O(n_x^3)$&\----\\
-$\boldsymbol\Lambda_{\theta}$&Eq.~\eqref{eq:MRA-LambdaThetaElements}&$O(n_x^2n_{\theta})$&\----\\
+$\boldsymbol\Lambda_{\theta}$&Eq.~\eqref{eq:LambdaThetaElements}&$O(n_x^2n_{\theta})$&\----\\
 $\hat{\boldsymbol\theta} $&Eq.~\eqref{eq:MRA-thetahat}&$O(n_{\theta}^3)$&\----\\
@@
 \end{align}
-where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix. Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
-\begin{equation}\label{eq:MRA-LambdaThetaElements}
+Each element of $\boldsymbol\Lambda_{\theta}$ can be calculated using
+\begin{equation}\label{eq:LambdaThetaElements}
 \left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta,
 \end{equation}
-where $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix. Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}\label{eq:Uij}
+where each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+\begin{align}\label{eq:app-Uij}
 \left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
 \end{align}
-where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
-By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:MRA-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
+By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:app-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
 \begin{align}
@@
 where 
-\begin{equation}\label{eq:appepsilon0}
-\boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i},
-\end{equation}
-\begin{equation}\label{eq:appepsilon1}
-\boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i},
-\end{equation}                                                                                 
-and
-\begin{equation}\label{eq:appEpsilon}
-\boldsymbol\Upsilon=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i}.
-\end{equation}
+$\boldsymbol\upsilon_0$, $\boldsymbol\upsilon_1$ and $\boldsymbol\Upsilon$ are defined in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon}.
+
 By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
@@
 Equating Eq.~\eqref{eq:MRA-QDerivative} to $\mathbf 0$ vector yields
-\begin{align}\label{eq:MRA-thetahat}
+\begin{align}\label{eq:app-thetahat}
 \boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top.

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
edit to the appendix

@@
 
-\section{Lower bound}\label{ap:QDerivation}
+\section{Construction and maximization of the Lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}
 For the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.
@@
 \end{align}
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs (see \ref{ap:Xiderivation} for more details)
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs (see \ref{ap:Xiderivation} for more details).
 
@@
 \end{equation}
-where each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}\label{eq:app-Uij}
-\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
-\end{align}
-By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:app-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
+where $\left[ \mathbf U\right] ^{k,i}$ can be computed using Eq.~\eqref{eq:Uij}.
+By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
 \begin{align}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
moved more bits to appendix

@@
 \end{align}
-The second derivative of the $\mathcal Q$-function is given by
-\begin{equation}
-\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
-\end{equation}
-The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\citep{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorization operator.
-Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
 
@@
 $\boldsymbol\upsilon_0$, $\boldsymbol\upsilon_1$ and $\boldsymbol\Upsilon$ are defined in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon}.
-
 By differentiating the $\mathcal Q$-function with respect to $\boldsymbol\theta$ we have
@@
 \end{align}
+The second derivative of the $\mathcal Q$-function is given by
+\begin{equation}
+\frac{\partial^2\mathcal Q}{\partial\boldsymbol\theta^2}=-2T_s\varsigma\boldsymbol\Upsilon.
+\end{equation}
+The matrix $\boldsymbol\Upsilon$ is positive definite if $n_x^2\times n_{\theta}$ matrix $\mathrm{vec}(\mathbf U)$ is of rank $n_{\theta}$ (\citep{Dewar2009}, Lemma 3), where $\mathrm{vec}(\cdot)$ denotes the vectorization operator.
+Under this condition $\boldsymbol\Upsilon$ is  invertible and the second derivative is negative definite representing a maximum of the $\mathcal Q$-function.
 \section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
some re-arrangement in EM

@@
 \end{align} 
-
+The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge.
+A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
 \subsection{Stopping rule}
@@
 \end {table} 
-
-The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge.
-A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as missing or hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case.
 The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
  \subsection{M-step}
-The lower bound on the log-likelihood function is given by \citep{Bishop2006} 
+The lower bound on the log-likelihood function is given by the expectation of the complete (hidden and observable) data  log-likelihood \citep{Bishop2006} 
 \begin{equation}\label{eq:Bishopbound}
@@
 \begin{align}\label{eq:AppendixNj-1intermsofNj}
- &N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})=\nonumber \\
-&\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
+ N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
 &=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
 \end{align}
-Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} completes the proof.
+Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof.
 
@@
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-The constant term is the negative entropy of $q(\mathbf X)$ and is independent of $\boldsymbol\theta$.
+The constant term is independent of $\boldsymbol\theta$.
 It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
-The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by
+The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape
 \begin{equation}\label{eq:ConnectivityKernelForData}
@@
 \end{equation}
-with $\theta_1=200$ and $\theta_2=-100$. \dean{This is depicted in Figure~\ref{fig:}}
+with $\theta_1=200$ and $\theta_2=-100$. This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
 
@@
 Maximizing the likelihood in terms of the parameter set is equivalent to the log-likelihood maximization, as both the likelihood and log-likelihood functions share the same maximizer due to the monotonicity of the logarithm function.
-For any choice of distribution defined over the latent variables, $q(\mathbf X)$, the following decomposition holds
+For any choice of distribution defined over the hidden variables, $q(\mathbf X)$, the following decomposition holds
 \begin{equation}\label{eq:EM-loglikelihooddecomposition}
@@
 The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
-The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:MRA-Xi0} of the main text is given by
+The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:app-Xi0} of the main text is given by
    \begin{equation}\label{eq:appXi0}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
got rid of the general lower bound in appendix, we can add later if its necessary

@@
 \end{equation}
-(see \ref{ap:Lowerbound} ) where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
@@
 
-\section{Lower bound on likelihood function}\label{ap:Lowerbound}
-A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix. We want to maximize the likelihood function, 
-\begin{equation}
- p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)\mathrm{d}\mathbf X,
-\end{equation}
-which is difficult to perform directly.
+%\section{Lower bound on likelihood function}\label{ap:Lowerbound}
+%A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix. We want to maximize the likelihood function, 
+%\begin{equation}
+ %p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)\mathrm{d}\mathbf X,
+%\end{equation}
+%which is difficult to perform directly.
 Maximizing the likelihood in terms of the parameter set is equivalent to the log-likelihood maximization, as both the likelihood and log-likelihood functions share the same maximizer due to the monotonicity of the logarithm function.
 For any choice of distribution defined over the hidden variables, $q(\mathbf X)$, the following decomposition holds
-\begin{equation}\label{eq:EM-loglikelihooddecomposition}
- \ln~p(\mathbf Y;\boldsymbol\theta)=\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p),
-\end{equation}
-where
-\begin{align}
- \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \label{eq:EM-decomposition1}\\
-\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X.
+%\begin{equation}\label{eq:EM-loglikelihooddecomposition}
+ %\ln~p(\mathbf Y;\boldsymbol\theta)=\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p),
+%\end{equation}
+%where
+%\begin{align}
+ %\mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \label{eq:EM-decomposition1}\\
+%\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X.
 \label{eq:EM-decomposition2}
-\end{align}
-Eq.~\eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
-\begin{align}
-	\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \nonumber\\
-	&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X\nonumber\\
-	&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)\mathrm{d}\mathbf X.
-\end{align}
-Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
+%\end{align}
+%Eq.~\eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
+%\begin{align}
+ % \mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \nonumber\\
+	%&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X\nonumber\\
+	%&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)\mathrm{d}\mathbf X.
+%\end{align}
+%Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
 We also note that Eq.~\eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$.
 Therefore,
-\begin{equation}
-	\mathrm{KL}(q\parallel p)\ge 0.
-\end{equation}   
-The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
+%\begin{equation}
+ % \mathrm{KL}(q\parallel p)\ge 0.
+%\end{equation}   
+%The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
 It follows from  Eq.~\eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\theta)$ is a lower bound on the log-likelihood function, i.e.
-\begin{equation}
- \mathcal{L}(q,\boldsymbol\theta)\le \ln~p(\mathbf Y\mid\boldsymbol\theta)
-	\end{equation}
-
-The EM algorithm alternates between maximizing the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
+%\begin{equation}
+ %\mathcal{L}(q,\boldsymbol\theta)\le \ln~p(\mathbf Y\mid\boldsymbol\theta)
+	%\end{equation}
+
+%The EM algorithm alternates between maximizing the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
 Suppose that the current estimate of the parameter set is $\boldsymbol\theta'$, in the E-step the lower bound is maximized with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\theta'$ is fixed.
@@
 Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta')$ for $q(\mathbf X)$ in Eq.~\eqref{eq:EM-decomposition1} gives
-\begin{align}
- \mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')~d\mathbf X \nonumber \\
-&= \mathbf E_{\boldsymbol\theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)\right] +\mathrm{const.}\nonumber\\
-&=\mathcal{Q}(\boldsymbol\theta,\boldsymbol\theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
-\end{align}
-where $ \mathbf E_{\boldsymbol \theta'}\left[ \cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
+%\begin{align}
+ %\mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')~d\mathbf X \nonumber \\
+%&= \mathbf E_{\boldsymbol\theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)\right] +\mathrm{const.}\nonumber\\
+%&=\mathcal{Q}(\boldsymbol\theta,\boldsymbol\theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
+%\end{align}
+%where $ \mathbf E_{\boldsymbol \theta'}\left[ \cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
@@
 It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
-
 \section{Construction and maximization of the Lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor edit
minor edit to appendix

@@
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
-\parham{This is important for constructing the wavelets.} For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
+For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
 \begin{align}
@@
 The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
-The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:app-Xi0} of the main text is given by
+The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:app-Xi0} is given by
    \begin{equation}\label{eq:appXi0}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor correction

@@
 	\end{equation}
-This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.
+This is important as the underlying field can be reconstructed when it is saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.
 
@@
 
-In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}).
+In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}).
 For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
@@
 \begin{align}\label{eq:MRA-NmFouriertransform}
-\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^m.
+\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
 \end{align}
@@
 	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
+	&=\frac{1}{2}\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
 \end{align}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
added the missing units to the table

@@
    	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
-		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$&mV\\ 
+		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
 		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
@@
 	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
-	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$, $\boldsymbol\Upsilon$&Lower bound coefficient matrices&??\\
+	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
+	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
 	\hline
@@
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\mathbf x_t^b$, the smoothed covariance,$\mathbf P^b_t$ and cross-covariance $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\hat{\mathbf x}_t^b$, the smoothed covariance,$\mathbf P^b_t$ and cross-covariance $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\
 \hline
@@
 	$\tau$ & membrane time constant & 0.01 & s$^{-1}$ \\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
+	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$.spike.s$^{-1}$\\
 	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters (data generation) & $\left[\begin{array}{cc}

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor edit to frequency response of the wavelet

@@
 	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
 \end{align}
@@
 This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
-\dean{the frequency response of the observed field used to decide on the level...} .
-In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
+\dean{the frequency response of the observed field used to decide on the level...} In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
 $j=0$ to $j=4$.

### 2012-02-13 Multiresolution_framework/ltx/manuscript.tex
minor edit to table one
minor edit to Table one
minor edit to teble one

@@
 	\hline
-	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
+	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
 	\hline
@@
 	\hline
-	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
-	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
+	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
 	\hline
@@
 	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
-	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
-	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
-	$M_t$& Cross-covariance matrix & mV$^2$\\
+	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
+	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
+	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
 	$\mathcal K_{t} $ & Filter gain & n.a.\\ 

### 2012-02-19 Multiresolution_framework/ltx/manuscript.tex
small edit
mini edit to M-step

@@
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-Note that this is actually the smoother output which is obtained at the E-step.
+Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is actually the smoother output which is obtained at the E-step.
 
@@
 It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
-\section{Construction and maximization of the Lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}
+\section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}
 For the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}.

### 2012-02-19 Multiresolution_framework/ltx/manuscript.tex
minor edit to appendix D

@@
 where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005},
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),
 \begin{align}
@@
 \section{Calculation of $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$}\label{ap:Xiderivation}
-The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here we present the derivation for completeness.
-The expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:app-Xi0} is given by
+The expressions for $\boldsymbol\Xi_{0}$ and $\boldsymbol\Xi_{1}$ in terms of smoother outputs can be found in \cite{Shumway2000}, here the derivation is presented for completeness.
+We start with the expression for  $\boldsymbol\Xi_{0}$ as defined in Eq.~\eqref{eq:app-Xi0}
    \begin{equation}\label{eq:appXi0}
@@
 	\end{equation}                                                                                                
-	We start by computing the cross-covariance matrix as
+	First we compute the cross-covariance matrix giving
 
@@
 \end{equation}
-Substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum yields
-\begin{equation}
- \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
-\end{equation}   
-An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t$.
+Substituting Eq.~\eqref{eq:Xi0derivation1} into Eq.~\eqref{eq:appXi0}, noting the expectation commutes with the sum yields
+\begin{equation}
+ \boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
+\end{equation}   
+An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t$ and following the above steps.
 %\begin{equation}\label{eq:Xi1derivation1}

### 2012-02-19 Multiresolution_framework/ltx/manuscript.tex
minor edit to result section

@@
 This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
-\dean{the frequency response of the observed field used to decide on the level...} In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
 $j=0$ to $j=4$.

### 2012-02-19 Multiresolution_framework/ltx/manuscript.tex
minor edit to result section
minor edits to result section

@@
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
-Fig.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
+Figs.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
 A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively.
@@
 The RMSE of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
-By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ is in fact adequate to capture the dynamics of the underlying field.
+By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ (used in the first experiment) is in fact adequate to capture the dynamics of the underlying field.
 The spatiotemporal characteristics of the reconstructed fields (A-E) along with the actual field (F)  are shown in Fig.~\ref{fig:FieldEstimation}.

### 2012-03-27 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm.
-\dean{The loss in model accuracy may be offset estimation accuracy.
-}
-
-It is important to point out there is no doubt that there will always be a mismatch between neural mass models and actual cortical tissue.
+The loss in model accuracy may be offset estimation accuracy.
+
+It is important to point out there is no doubt that there will always be a mismatch between neural field models and actual cortical tissue.
 Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.

### 2012-03-27 Multiresolution_framework/ltx/manuscript.tex
added subsection to discussion

@@
 For example, at scales corresponding to higher spatial frequencies a greater number of wavelets, and thus spatial shifts are required to adequately sample the spatial characteristics of the field.
-The number of scales depends on the spectral characteristics of the field, where higher spatial frequencies require a more scales.
+The number of scales depends on the spectral characteristics of the field, where higher spatial frequencies require  more scales.
 Spatial frequency analysis will be described later in Section~\ref{sec:freq_anal} in greater detail.
@@
 
-By exploiting Eq.~\eqref{eq:BsplineConvolution} and Eq.~\eqref{eq:BsplineInnerProduct}, the integrals in Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Gammaij} can be computed analytically.
+By exploiting Eqs.~\eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in Eqs.~\eqref{eq:Lambdax} and \eqref{eq:Gammaij} can be computed analytically.
 In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}:
@@
 
-It is important to point out there is no doubt that there will always be a mismatch between neural field models and actual cortical tissue.
+It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue.
 Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.
@@
 \end{equation} 
-The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can be formulated as 
+The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can now be formulated as 
 \begin{equation}
@@
 The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
-Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound on the likelihood function.
 Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
@@
 It would be nice to slot something in here because he used wavelets.}
-
+\subsection{Estimation algorithm}
 For a larger space, or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
@@
 
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}.
-% \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165].
-(This is copy and paste from my thesis ...
-parham I'll get you the references later)}.
-\parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing?
-Also it's not terribly specific.
-I think it's better to stick to how it has the potential to model brains in a manner that rocks, rather than loosely saying it could be applied to any spatiotemporal system, i.e.
-literally everything.}
-
   % \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
@@
 % In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.
-
-To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly.
-The implementation of the framework in the nonlinear case can be addressed as future work.
-Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.
-The reconstruction of the neural field requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
+ \subsection{Modification to higher dimensions}
+%To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly. The implementation of the framework in the nonlinear case can be addressed as future work. 
+%Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.
+ The reconstruction of the neural field in higher dimensions requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
 For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}.
@@
 It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
-
+\subsection{Extensions to the framework} 
 The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}.
 The key development is the multi-resolution decomposition forming the state-space model.
@@
 However, delays must be accounted for in large scale networks.
-For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks.
+For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
 Finally, future work should be directed towards applying and validating the framework on real data.
@@
 Consider two B-spline scaling functions of order $m$ and $m'$.
-The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
+The support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
 \begin{align}\label{eq:APP-SymmetrySplieEq}

### 2012-03-27 Multiresolution_framework/ltx/manuscript.tex
correction to bibligraphy

@@
 This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003}.
-Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2011}.
+Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2012}.
 Most recently, a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2010}.
+It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2011}.
 %\dean{This is a test to see if we can fit something about Breaky's paper in here.

### 2012-04-06 Multiresolution_framework/ltx/manuscript.tex
added two references

@@
 These are also shown in Fig.~\ref{fig:Modelcomponents}.
-The form of $w(\mathbf{r},\mathbf{r}')$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field.
+The form of $w(\mathbf{r},\mathbf{r}')$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}.
 By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.

### 2012-04-14 Multiresolution_framework/ltx/manuscript.tex
minor edit
added hay kin to bib

@@
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
-For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
+For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
 \begin{align}
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space models, the E-step corresponds to the smoothing problem, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
 For the M-step, a lower bound on the likelihood function is constructed, where the steps needed

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
added Viktor comments

@@
 
-Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics of the EEG.
+Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics leading to the generation of  Electroencephalography (EEG) and Magnetoencephalography (MEG) signals.
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-Examples are the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1997}.
-The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models.
-The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a CDF of the probability of firing) to mean firing rates of neural masses.
+Examples are the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1996,Jirsa1997}.
+The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
+The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) to mean firing rates of neural masses.
 The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
+Large-scale neuroinformatic efforts such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}) are on the way to enable patient-specific full brain modeling.
 This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
@@
 The multi-resolution structure has been described by numerous methods.
-For example, this idea of multi-resolution can be thought of a generalization of modeling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \citep{Wilson1973}.
-
-Typically, the experimentalist only has access the net field generated by the multi-resolution architecture of the cortex.
-Follow this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
+For example, this idea of multi-resolution can be thought of as the generalization of modeling the layers of the cortex separately, where the connectivity kernel, or neural foot-print, has varying widths \citep{Wilson1973}.
+
+Typically, the experimentalist only has access to the net field generated by the multi-resolution architecture of the cortex.
+Following this, it is natural to ask how do we best describe the multi-resolution structure of the neural system.
 The solution to this problem was proposed by \citet{Breakspear2005} in using a wavelet decomposition.
@@
 The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
-The parameter $\theta$ can be thought of the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describes excitation and inhibition, respectively.
+The parameter $\theta$ can be thought of as the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describe excitation and inhibition, respectively.
 There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity.
@@
 \end{equation}
-where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step.
+where in this first-order (in time) formulation of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step.
 % The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
@@
 It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue.
-Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy.
+Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
@@
 The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-The large standard deviation is due to the high number of parameters need to be estimated.
+The large standard deviation is due to the high number of parameters needed to be estimated.
 The small error in the estimate is attributed to the MRA of the system used to form the estimator.
@@
 The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
-This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
-Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling.
-It is thought that the dynamics and connectivity structure differs at different spatial scales~\citep{Qubbaj2009,Breakspear2005,Schultze-Kraft2011}.
-%\dean{This is a test to see if we can fit something about Breaky's paper in here.
-It would be nice to slot something in here because he used wavelets.}
+This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
+Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Qubbaj2009,Breakspear2005,Schultze-Kraft2011}.
 \subsection{Estimation algorithm}
@@
 However, delays must be accounted for in large scale networks.
-For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks.
+For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations in resting state networks (see \citet{Deco2010} for review).
 Finally, future work should be directed towards applying and validating the framework on real data.
@@
 \end{align}
-Twice the logarithm of the above distribution, once expanded, is given by
+The logarithm of the above distribution, once expanded, is given by
 \begin{align}\label{eq:Qfunction}
@@
 \end{align}
-The factor of 2 is included to simplify the derivation in the later steps. Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
+The factor of 2 in front of the logarithm is included to simplify the derivation in the later steps.
+Substituting $\mathbf A( \boldsymbol\theta)$ from Eq.~\eqref{eq:A_theta} into Eq.~\eqref{eq:Qfunction} gives
 \begin{align}

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
minor edit to covariance function

@@
 \end{equation}
-where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance} and $\delta(\cdot)$ is the Dirac-delta function.
+where $\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance and $\delta(\cdot)$ is the Dirac-delta function.
 %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
minor edits
added time delay to the general form of the model

@@
 	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
-	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
+	\underbrace{f\left( v\left( \mathbf{r}',t'-t_d\right)\right)}_{\text{firing}}
 	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
@@
 where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$.
-The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
+The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t-t_d))$ describes the relationship between the mean membrane potential and the mean firing rate where $t_d$ denotes the time delay due to the finite propagation velocity of the action potentials.
 The parameter $\theta$ can be thought of as the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describe excitation and inhibition, respectively.
@@
 \caption{ {\bf The IDE neural field model components}.
-(\textbf{A}) The Mexican hat (dotted line) and Wizard hat (solid line) connectivity kernels.
+(\textbf{A}) The Laplacian (dotted line) and Gaussian (solid line) functions which are typically used in constructing Mexican hat and  Wizard hat connectivity kernels.
 (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
minor edits

--- 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
@@
 
-The single layer homogeneous neural field model, in the most general form, is described by the equation
+In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
 \begin{equation}
@@
 	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
-	\underbrace{f\left( v\left( \mathbf{r}',t' \right)\right)}_{\text{firing}}
+	\underbrace{f\left( v\left( \mathbf{r}',t'\right)\right)}_{\text{firing}}
 	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
minor edits
edit to caption of fig2

@@
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
-\newcommand{\parham}[1]{\textcolor{red}{#1}}
-% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}
+\newcommand{\parham}[1]{\textcolor{blue}{#1}}
+\newcommand{\vik}[1]{\textcolor{red}{#1}}
 
@@
 \caption{ {\bf The IDE neural field model components}.
-(\textbf{A}) The Laplacian (dotted line) and Gaussian (solid line) functions which are typically used in constructing Mexican hat and  Wizard hat connectivity kernels.
+(\textbf{A}) The Mexican hat (solid line) and Wizard hat (dotted line) connectivity kernels composed of Gaussian and Laplacian basis functions respectively.
 (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.
 (\textbf{C}) A representative of the activation function.}
+
 \label{fig:Modelcomponents}

### 2012-05-15 Multiresolution_framework/ltx/manuscript.tex
changed figure2
minor edits

@@
 These are also shown in Fig.~\ref{fig:Modelcomponents}.
-The form of $w(\mathbf{r},\mathbf{r}')$ typically describes an Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}.
+The form of $w(\mathbf{r},\mathbf{r}')$ typically describes a Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}.
 By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
@@
 (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.
-(\textbf{C}) A representative of the activation function.}
+(\textbf{C}) The sigmoidal (solid line) and the Heaviside (dotted line) activation functions.}
 
@@
 $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is actually the smoother output which is obtained at the E-step.
+Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is in fact the smoother output which is obtained at the E-step.
 

### 2012-05-16 Multiresolution_framework/ltx/manuscript.tex
added Viktor comments

@@
 %\boldmath
-We develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
+\parham{Neural fields are spatially continuous state variables described by integro-differential equations, which are well suited to describe the spatiotemporal evolution of cortical activations on multiple scales.
+Here we} develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
 State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.

### 2012-05-21 Multiresolution_framework/ltx/manuscript.tex
added Viktor comments

@@
 \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
-
+\usepackage{psfrag}
 \newcommand{\dean}[1]{\textcolor{green}{#1}}
@@
 %\boldmath
-\parham{Neural fields are spatially continuous state variables described by integro-differential equations, which are well suited to describe the spatiotemporal evolution of cortical activations on multiple scales.
+\vik{Neural fields are spatially continuous state variables described by integro-differential equations, which are well suited to describe the spatiotemporal evolution of cortical activations on multiple scales.
 Here we} develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
@@
 Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics leading to the generation of  Electroencephalography (EEG) and Magnetoencephalography (MEG) signals.
-The key components of these models typically describe the macroscopic dynamics of the human brain, but can also descriptive of finer-scale neurodynamics.
-Examples are the post-synaptic response kernels (the pulse to wave function) and the activation function (wave to pulse function) \citep{Jirsa1996,Jirsa1997}.
-The former can be descriptive of inhibitory and excitatory post-synaptic potentials in microscopic single neural models, such as integrate and fire, or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
-The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) to mean firing rates of neural masses.
-The key factor linking the key functions of the model to particular spatial scales is geometry of the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable to the formulation of a multi-resolution neural field model.
+The key components of these models typically describe the macroscopic dynamics of the human brain, but can also be descriptive of finer-scale neurodynamics.
+Examples are the post-synaptic response kernels (\vik{pulse to wave conversion}) and the activation function (\vik{wave to pulse conversion}) \citep{Jirsa1996,Jirsa1997}.
+The former can be descriptive of inhibitory and excitatory post-synaptic potentials \vik{in populations of microscopic single neural models, such as integrate and fire neurons,} or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
+The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) \vik{as} mean firing rates of neural masses.
+The key factor linking the functions of \vik{neural mass models} to particular spatial scales is \vik{the connectivity}, hence the ability to infer a multi-resolution connectivity kernel will enable the formulation of a multi-resolution neural field model.
 
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
-Large-scale neuroinformatic efforts such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}) are on the way to enable patient-specific full brain modeling.
-This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
+\vik{Large-scale neuroinformatic efforts such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}) are on the way to enable patient-specific full brain modeling.} This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
 Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error.
@@
 It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\vik{The multi-resolution architecture of the brain and connectivity in particular will play an important role in this context for multiple reasons.
+First, there is an on-going debate about the organizational level of the brain at which cognition and behaviour is best represented.
+While clearly single neurons show response changes that map back to learning, memory and motor behaviour, much of the recent work in neuroscience suggest that these elementary features must be organized at a higher level to provide the richness and diversity of the behaving system.
+For example, functional neuroimaging work has confirmed that specific parts of visual cortex are more responsive to particular types of stimuli (e.g.
+faces), but the specificity of this response is dependent on the large-scale pattern of activity across most visual cortical areas \citep{Haxby2001}.
+Further, the evolution of diffusion magnetic resonance imaging (dMRI) has led to the development of tensor-based tractography, which allows for in vivo images of the white matter skeleton of any brain.
+Improvements of the MR sequences (e.g.
+diffusion spectrum imaging) and tractography analysis have made it possible to use tractography as a standard to define connectivity \citep{Hagmann2008}.
+Hence individualized connectivity matrices can be developed for brain models enabling patient-specific functional studies and need to be estimated from the experimental data.}
 
 The first work (to the authors best knowledge) describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\citep{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\citep{David2003}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme \vik{called} Dynamic Causal Modeling (DCM)~\citep{David2003}.
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2012}.
@@
 \caption{{\bf Examples of cardinal B-spline functions}.
-Piecewise polynomial functions (colored lines) are joined at the break points (black dots).
+Piecewise polynomial functions (dotted lines) are joined at the break points (black dots).
 (\textbf{A}) B-spline function of order 2 (linear B-spline).
@@
 \end{align}
-One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
+One important feature of the B-spline functions is the partition of unity property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
 \begin{equation}
@@
  		\caption{{\bf The scaling and the wavelet function decomposition}.
-(\textbf{A}) The scaling function (blue) at $j=0$ is obtained using 625 scaling functions (black) at $j=4$.
-(\textbf{B}) The wavelet function (blue) at $j=0$ is obtained using 1250 scaling functions (black) at $j=4$.}
+(\textbf{A}) The scaling function (dotted line) at $j=0$ is obtained using 625 scaling functions (solid lines) at $j=4$.
+(\textbf{B}) The wavelet function (dotted line) at $j=0$ is obtained using 1250 scaling functions (solid lines) at $j=4$.}
  	\label{fig:MRA-BasisDecomposition}
@@
 
-It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue.
-Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
+\vik{viktor suggested to delete this part: It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue.
+Nevertheless,} the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
@@
 The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
-This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy.
+This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics.
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Qubbaj2009,Breakspear2005,Schultze-Kraft2011}.
@@
 \subsection{Extensions to the framework} 
-The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex.
+Clearly there is, and will always be, a discrepancy between the dynamics of the model and the experimental observation.
 Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
@@
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
-In small networks the delays via propagation can be neglected.
+\vik{In small networks the resulting delays via propagation can be neglected.
 However, delays must be accounted for in large scale networks.
-For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations in resting state networks (see \citet{Deco2010} for review).
-Finally, future work should be directed towards applying and validating the framework on real data.
+For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review).
+In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
+To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.} Finally, future work should be directed towards applying and validating the framework on real data.
+
+\section{Acknowledgements}
+The research reported herein was partly supported by the Brain Network Recovery Group through the James S. McDonnell Foundation and the FP7-ICT BrainScales.
 

### 2012-05-21 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+
 \vik{The multi-resolution architecture of the brain and connectivity in particular will play an important role in this context for multiple reasons.
-First, there is an on-going debate about the organizational level of the brain at which cognition and behaviour is best represented.
-While clearly single neurons show response changes that map back to learning, memory and motor behaviour, much of the recent work in neuroscience suggest that these elementary features must be organized at a higher level to provide the richness and diversity of the behaving system.
+First, there is an on-going debate about the organizational level of the brain at which cognition and behavior is best represented.
+While clearly single neurons show response changes that map back to learning, memory and motor behavior, much of the recent work in neuroscience suggest that these elementary features must be organized at a higher level to provide the richness and diversity of the behaving system.
 For example, functional neuroimaging work has confirmed that specific parts of visual cortex are more responsive to particular types of stimuli (e.g.
@@
 
-In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
+\vik{In a small network with no time delays} the single layer homogeneous neural field model, in the most general form, is described by the equation
 \begin{equation}

### 2012-05-21 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 Here we} develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
+In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
 State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
@@
 		\includegraphics[scale=1]{./Graph/fig1.pdf}
-	\caption{{\bf Multi-layer neural field model}. The inset figures show the shape of the
+	\caption{{\bf Multi-layer neural field structure}. The inset figures show the shape of the
 connectivity kernel components at each spatial resolution.}
@@
 This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics.
-Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Qubbaj2009,Breakspear2005,Schultze-Kraft2011}.
+Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
 \subsection{Estimation algorithm}
@@
 
-Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
+Additional extension for future work include extending the model to capture a second order synaptic response kernel.
+The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.

### 2012-05-24 Multiresolution_framework/ltx/manuscript.tex
updated Mike affiliation
added discussion about isotropy for switching the inner product and convolution

@@
 \author[CU]{M. Dewar}
-\ead{mike.dewar@columbia.edu}
+\ead{md@bit.ly}
 \author[UM]{K. Scerri}
@@
 \address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
-\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
+\address[CU]{bit.ly, New York City, USA}
 \address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
@@
 
+Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
+This simplifies the computational complexity of the estimation algorithm significantly.
+Although this is correct for one dimensional B-spline scaling and wavelet functions, it does not hold at higher dimensions as the resulting B-spline wavelets are not isotropic.
+One alternative could be
+isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
+
   % \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
corrected freq analysis

@@
 	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
-	$h(t)$ & Post-synaptic response kernel & mV\\
+	$h(t)$ & Post-synaptic response kernel & n.a.\\
 	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
@@
 		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
-		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
+		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&s, mV.spike$^{-1}$\\
    	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
@@
 This convolution can be calculated analytically when using B-spline scaling and wavelet functions and can be predefined, since these are static functions.
-This has major computation advantages when solving the estimation problem.
+This has major computational advantages when solving the estimation problem.
 %\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field.
@@
 \end{align}
-where $i=\sqrt{-1}$.
+where $\nu$ is the spatial frequency and $i=\sqrt{-1}$.
 The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
@@
 	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\frac{\pi in\nu}{2}).\label{eq:MRA-Wavelettransform}
 \end{align}

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
minor changes

@@
 	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\frac{\pi in\nu}{2}).\label{eq:MRA-Wavelettransform}
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
 \end{align}

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
minor edits to introduction just typos

@@
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.
-
-Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics leading to the generation of  Electroencephalography (EEG) and Magnetoencephalography (MEG) signals.
+This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE) to address this challenge.
+
+Neural field models describe the mass action of the central nervous system and are a critical link in our understanding of the biophysics leading to the generation of  electroencephalography (EEG) and magnetoencephalography (MEG) signals.
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also be descriptive of finer-scale neurodynamics.
@@
 The former can be descriptive of inhibitory and excitatory post-synaptic potentials \vik{in populations of microscopic single neural models, such as integrate and fire neurons,} or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
-The latter, can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) \vik{as} mean firing rates of neural masses.
+The latter can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) \vik{as} mean firing rates of neural masses.
 The key factor linking the functions of \vik{neural mass models} to particular spatial scales is \vik{the connectivity}, hence the ability to infer a multi-resolution connectivity kernel will enable the formulation of a multi-resolution neural field model.
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
-\vik{Large-scale neuroinformatic efforts such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}) are on the way to enable patient-specific full brain modeling.} This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
+\vik{Large-scale neuroinformatic efforts, such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.} This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
 Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error.
@@
 where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
-The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
+The decomposition enables a separation of the spatial characteristics, which are considered static functions that are weighted by dynamic coefficients.
 

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
edit to the start of the b-spline tutorial

@@
 \subsection{A Brief Introduction to B-Spline Wavelets}
+This section is included to provide the interested reader with an overview of the theory used in constructing the wavelets that form the basis of the multi-resolution model.
+Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.
+
 B-spline functions are one of the most basic elements for wavelet construction.

### 2012-05-29 Multiresolution_framework/ltx/manuscript.tex
edits to discussion about second order synaptic kernel

@@
 Additional extension for future work include extending the model to capture a second order synaptic response kernel.
-The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials.
+The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials ( see \citet{Spiegler2010,Spiegler2011} for example).
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.

### 2012-06-06 Multiresolution_framework/ltx/manuscript.tex
got rid of bspline expansion

@@
 In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}).
-For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
-\begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
- &N_m(r)=\nonumber \\
-&\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-l_{n_1,n_2, \dots, n_j}),
-\end{align}
-where 
-\begin{align}
- l_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
-\end{align}
-The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see \ref{ap:Induction}).
+% For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
+% \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
+%  &N_m(r)=\nonumber \\
+% &\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-l_{n_1,n_2, \dots, n_j}),
+% \end{align}
+% where 
+% \begin{align}
+%  l_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
+% \end{align}  
+% The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see \ref{ap:Induction}).
 A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using Eq.~\eqref{eq:MRA-TwoScalepair2}.
 Examples of such expansions are given in Fig.~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
-\begin{figure}[!t] 
- 	\centering
- 		\includegraphics[scale=1]{./Graph/fig5.pdf}
- 		\caption{{\bf The scaling and the wavelet function decomposition}.
+% \begin{figure}[!t] 
+%  	\centering
+%  		\includegraphics[scale=1]{./Graph/fig5.pdf}
+%  		\caption{{\bf The scaling and the wavelet function decomposition}.
 (\textbf{A}) The scaling function (dotted line) at $j=0$ is obtained using 625 scaling functions (solid lines) at $j=4$.
 (\textbf{B}) The wavelet function (dotted line) at $j=0$ is obtained using 1250 scaling functions (solid lines) at $j=4$.}
- 	\label{fig:MRA-BasisDecomposition}
- \end{figure}  
+%  	\label{fig:MRA-BasisDecomposition}
+%  \end{figure}  
 In this paper, $4^{th}$ -- order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
@@
 \end{align}
-\section{Scaling function expansion}\label{ap:Induction}  
-In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
+% \section{Scaling function expansion}\label{ap:Induction}  
+% In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
 For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
-\begin{align}
- N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
-  \end{align}
-which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
-\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
- &N_m(r)=\nonumber \\
-&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
-\end{align}
-in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
-\begin{align}\label{eq:AppendixNj-1intermsofNj}
- N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
-&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
-\end{align}
-Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof.
-
+% \begin{align}
+%  N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
+%   \end{align}
+% which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
+% \begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
+%  &N_m(r)=\nonumber \\
+% &\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
+% \end{align}
+% in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
+% \begin{align}\label{eq:AppendixNj-1intermsofNj}
+%  N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
+% &=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
+% \end{align}
+% Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof. 
+%                   
 %\section{Lower bound on likelihood function}\label{ap:Lowerbound}

### 2012-06-11 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 The key components of these models typically describe the macroscopic dynamics of the human brain, but can also be descriptive of finer-scale neurodynamics.
-Examples are the post-synaptic response kernels (\vik{pulse to wave conversion}) and the activation function (\vik{wave to pulse conversion}) \citep{Jirsa1996,Jirsa1997}.
-The former can be descriptive of inhibitory and excitatory post-synaptic potentials \vik{in populations of microscopic single neural models, such as integrate and fire neurons,} or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
-The latter can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) \vik{as} mean firing rates of neural masses.
-The key factor linking the functions of \vik{neural mass models} to particular spatial scales is \vik{the connectivity}, hence the ability to infer a multi-resolution connectivity kernel will enable the formulation of a multi-resolution neural field model.
+Examples are the post-synaptic response kernels (pulse to wave conversion) and the activation function (wave to pulse conversion) \citep{Jirsa1996,Jirsa1997}.
+The former can be descriptive of inhibitory and excitatory post-synaptic potentials in populations of microscopic single neural models, such as integrate and fire neurons, or an ensemble response to stimulation in macroscopic neural mass models \citep{Stefanescu2008}.
+The latter can be used to model spiking statistics across spatial scales from single neurons (where it can be considered a cumulative distribution function (CDF) of the probability of firing) as mean firing rates of neural masses.
+The key factor linking the functions of neural mass models to particular spatial scales is the connectivity, hence the ability to infer a multi-resolution connectivity kernel will enable the formulation of a multi-resolution neural field model.
 
@@
 %  \end{figure}  
-In this paper, $4^{th}$ -- order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
 \begin {table}[t]
@@
 
-\vik{viktor suggested to delete this part: It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue.
-Nevertheless,} the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
+The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
@@
 \end{equation} 
-The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can now be formulated as 
+The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:ReducedObservationEquation} and Eq.~\eqref{eq:StateEquation}  can now be formulated as 
 \begin{equation}
@@
 One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
-A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+A natural framework to perform this is the well known EM algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
 The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case.
@@
 
-For the linear state-space model given by Eqs.~\eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}, the bound defined by Eq.~\eqref{eq:Bishopbound} is a quadratic of the form (see \ref{ap:QDerivation} for derivation)
+For the linear state-space model given by Eqs.~\eqref{eq:ReducedObservationEquation} and \eqref{eq:StateEquation}, the bound defined by Eq.~\eqref{eq:Bishopbound} is a quadratic of the form (see \ref{ap:QDerivation} for derivation)
 \begin{equation}\label{eq:MRA-QCompact}
@@
 where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),
-\begin{align}
-\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \label{eq:Xi0} \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right).  \label{eq:Xi1}
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t^b$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),
+\begin{align}
+\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi0} \\
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).  \label{eq:Xi1}
 \end{align} 
@@
 \begin{align}\label{eq:Xi0derivation0} 
- \mathbf M_{t+1}&=\mathbf E_{\theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1})^\top\right] \nonumber \\
-&=\mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\mathbf x_t\hat{\mathbf x}_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\mathbf x_{t+1}^\top\right]+\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\right]  \nonumber \\
-&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top+\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\nonumber \\
-&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top.
+ \mathbf M_{t+1}&=\mathbf E_{\theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t^b)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1}^b)^\top\right] \nonumber \\
+&=\mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\mathbf x_t\hat{\mathbf x}_{t+1}^{b\top}\right]-\mathbf E_{\theta'}\left[\hat{\mathbf x}_t^b\mathbf x_{t+1}^\top\right]+\mathbf E_{\theta'}\left[\hat{\mathbf x}_t^b\hat{\mathbf x}_{t+1}^{b\top}\right]  \nonumber \\
+&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t^b\hat{\mathbf x}_{t+1}^{b\top}-\hat{\mathbf x}_t^b\hat{\mathbf x}_{t+1}^{b\top}+\hat{\mathbf x}_t^b\hat{\mathbf x}_{t+1}^{b\top}\nonumber \\
+&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t^b\hat{\mathbf x}_{t+1}^{b\top}.
 \end{align}
@@
 \begin{equation}\label{eq:Xi0derivation1}
- \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top.
+ \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}.
 \end{equation}
@@
 \begin{equation}
- \boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
-\end{equation}   
-An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t$ and following the above steps.
+ \boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right)
+\end{equation}   
+An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t^b$ and following the above steps.
 %\begin{equation}\label{eq:Xi1derivation1}

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to the discussion
minor edit to discussion

@@
 The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+By decomposing both the spatial field and the connectivity kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
 This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics.
@@
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
-\vik{In small networks the resulting delays via propagation can be neglected.
+In small networks the resulting delays via propagation can be neglected.
 However, delays must be accounted for in large scale networks.
@@
 In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
-To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.} Finally, future work should be directed towards applying and validating the framework on real data.
+To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.
+Finally, future work should be directed towards applying and validating the framework on real data.
 

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
removed the color from the text

@@
 %\boldmath
-\vik{Neural fields are spatially continuous state variables described by integro-differential equations, which are well suited to describe the spatiotemporal evolution of cortical activations on multiple scales.
-Here we} develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
+Neural fields are spatially continuous state variables described by integro-differential equations, which are well suited to describe the spatiotemporal evolution of cortical activations on multiple scales.
+Here we develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets.
 In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
-\vik{Large-scale neuroinformatic efforts, such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.} This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
+Large-scale neuroinformatic efforts, such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.
+This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
 Stimulation strategies for devices currently operate in an open loop, where stimulation parameters are chosen using a process of trial and error.
@@
 
-\vik{The multi-resolution architecture of the brain and connectivity in particular will play an important role in this context for multiple reasons.
+The multi-resolution architecture of the brain and connectivity in particular will play an important role in this context for multiple reasons.
 First, there is an on-going debate about the organizational level of the brain at which cognition and behavior is best represented.
@@
 diffusion spectrum imaging) and tractography analysis have made it possible to use tractography as a standard to define connectivity \citep{Hagmann2008}.
-Hence individualized connectivity matrices can be developed for brain models enabling patient-specific functional studies and need to be estimated from the experimental data.}
+Hence individualized connectivity matrices can be developed for brain models enabling patient-specific functional studies and need to be estimated from the experimental data.
 
 The first work (to the authors best knowledge) describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\citep{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme \vik{called} Dynamic Causal Modeling (DCM)~\citep{David2003}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme called Dynamic Causal Modeling (DCM)~\citep{David2003}.
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2012}.
@@
 
-\vik{In a small network with no time delays} the single layer homogeneous neural field model, in the most general form, is described by the equation
+In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
 \begin{equation}

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor change
minor edit to Bspline intro

@@
 	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
-	\parham{\theta}\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
+	\theta\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
 	\underbrace{f\left( v\left( \mathbf{r}',t'\right)\right)}_{\text{firing}}
@@
 \subsection{A Brief Introduction to B-Spline Wavelets}
-This section is included to provide the interested reader with an overview of the theory used in constructing the wavelets that form the basis of the multi-resolution model.
+This section is included to provide the interested reader with an overview of the theory for the scaling and wavelet functions that form the basis of the multi-resolution model.
 Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.
@@
 	$\sigma_{m}$ & observation kernel full width at half maximum & 0.08 & mm \\
-	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
+	$\Sigma_{\varepsilon}$ & observation noise covariance matrix & $0.1 \times I_{n_y}$ & mm$^2$ \\
 	$\sigma_{\eta}$& disturbance covariance function full width at half maximum & 0.18 & mm\\

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to the caption of the EM convergence plot

@@
 \subsection{A Brief Introduction to B-Spline Wavelets}
-This section is included to provide the interested reader with an overview of the theory for the scaling and wavelet functions that form the basis of the multi-resolution model.
+This section is included to provide the interested reader with an overview of the theory for  scaling and wavelet functions that form the basis of the multi-resolution model.
 Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.
@@
  		\includegraphics[scale=1]{./Graph/fig8.pdf}
- 		\caption{{\bf Convergence of the EM based algorithm}. Representative plot of
-the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.} 
+ 		\caption{{\bf Convergence of the EM based algorithm}. The mean  of
+the $\mathbf A(\boldsymbol\theta)$ Frobenius norm over 200 realizations vs iterations of the EM based algorithm.
+The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.}
 \label{fig:MRA-Convergence}  

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 $\mathbf P_{t+1}^{f-}=\mathbf A \mathbf P_{t}^{f}\mathbf A^{\top}+\boldsymbol\Sigma_e$  \\
-\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix} \\
+\multicolumn{1}{|p{16cm}|}{compute the filter gain, the filtered state and the filtered covariance matrix} \\
 $\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\varepsilon})^{-1}$\\
@@
 $\mathbf M_T=(\mathbf I-\mathcal K_T\mathbf C)\mathbf A\mathbf P_{T-1}^b$\\
-\multicolumn{1}{|p{16cm}|}{For $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\
+\multicolumn{1}{|p{16cm}|}{for $t\in\left\lbrace T-1,\cdots,1\right\rbrace $ compute}\\
 $\mathbf M_t= \mathbf P_t^{f}\mathcal S_{t-1}^{\top}+\mathcal S_{t}(\mathbf M_{t+1}-\mathbf A\mathbf P_t^{f} )\mathcal S_{t-1}^{\top}$\\
@@
 \end{tabular}
-\caption{\textbf{Algorithm for the RTS smoother} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.
-The lower bound, $\mathcal{Q}(\boldsymbol{\theta},\boldsymbol{\theta'})$, is maximized after each iteration to update the parameter estimates.}
+\caption{\textbf{Algorithm for the RTS smoother (E-step).} This table shows the steps in the  Rauch-Tung-Striebel smoother algorithm.}
 \label{alg:MRA-RTS}
@@
 \subsection{Computational complexity} 
-All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations, which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
+All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
 The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified.
@@
 \multicolumn{1}{|p{16cm}|}{\textbf{1.} Initialization:  } \\ 
-\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence and choose large values for $\mathbf P_t$ and $\mathbf M_t$} \\
-\multicolumn{1}{|p{16cm}|}{Compute} \\
+\multicolumn{1}{|p{16cm}|}{Choose a bounded random state vector sequence $\hat{\mathbf X}$, and set $\mathbf P_t$ and $\mathbf M_t$ large} \\
+\multicolumn{1}{|p{16cm}|}{compute} \\
 $\mathbf{\Lambda}_{x}=\int_{\Omega}\boldsymbol{\mu}\left(r\right)\boldsymbol{\mu}^\top\left(r\right) \mathrm{d}r$\\
-\multicolumn{1}{|p{16cm}|}{Compute all the $n^2_x$ blocks of block matrices $\mathbf U$, $\Gamma_1$ and  $\Gamma_2$ using} \\
+\multicolumn{1}{|p{16cm}|}{compute all the $n^2_x$ blocks of block matrices $\mathbf U$, $\Gamma_1$ and  $\Gamma_2$ using} \\
 $\left[ \mathbf U\right] ^{k,i}=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{i:} dr$\\
@@
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space model}\\
-\multicolumn{1}{|p{16cm}|}{Compute all $n_x^2$ elements of $\boldsymbol\Lambda_{\theta}$ using} \\
+\multicolumn{1}{|p{16cm}|}{\textbf{3.} Form a state-space representation}\\
+\multicolumn{1}{|p{16cm}|}{compute all $n_x^2$ elements of $\boldsymbol\Lambda_{\theta}$ using} \\
 $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}=\left[ \mathbf U\right]^{k,i}\boldsymbol\theta$\\
-\multicolumn{1}{|p{16cm}|}{Compute transition matrix $\mathbf A(\boldsymbol\theta)$ } \\
+\multicolumn{1}{|p{16cm}|}{compute transition matrix $\mathbf A(\boldsymbol\theta)$ } \\
 $\mathbf A(\boldsymbol \theta) = T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I$\\
 \hline
-\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\hat{\mathbf x}_t^b$, the smoothed covariance,$\mathbf P^b_t$ and cross-covariance $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\
-\hline
-\multicolumn{1}{|p{16cm}|}{\textbf{5.} Convergence: go back to Step~2 unless }\\
+\multicolumn{1}{|p{16cm}|}{\textbf{4.} Compute the smoothed state $\hat{\mathbf x}_t^b$, the smoothed covariance, $\mathbf P^b_t$ and cross-covariance, $\mathbf M_t$ for $t\in\left\lbrace 0,\cdots,T\right\rbrace $ using the RTS smoother given in Table~\ref{alg:MRA-RTS}.}\\
+\hline
+\multicolumn{1}{|p{16cm}|}{\textbf{5.} Convergence: return to Step~2 unless }\\
 $ \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon$\\

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to table3
minor edit to appendix
deleted old files
minor edits

@@
 \includegraphics{./Graph/fig3.pdf}
-% \includegraphics{./Graph/Figure0b.pdf}
 \caption{{\bf Examples of cardinal B-spline functions}.
@@
 \centering
-\includegraphics[scale=1]{./Graph/fig6.pdf}
+\includegraphics[scale=1]{./Graph/fig5.pdf}
 \caption{{\bf Schematic of the EM algorithm}.
@@
 	\hline
-	$\Delta$ & spatial discretisation step & 0.01 & mm \\
-	$T_s$ & time step & $0.001$ & s\\
-	$T$ & number of time steps used in estimation & 900 & n.a.\\
+	$\Delta$ & Spatial discretisation step & 0.01 & mm \\
+	$T_s$ & Time step & $0.001$ & s\\
+	$T$ & Number of time steps used in estimation & 900 & n.a.\\
 	\hline 
@@
 	\hline
-	$\tau$ & membrane time constant & 0.01 & s$^{-1}$ \\
-	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$.spike.s$^{-1}$\\
-	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters (data generation) & $\left[\begin{array}{cc}
+	$\tau$ & Membrane time constant & 0.01 & s$^{-1}$ \\
+	$\varsigma$ & Slope of activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$.spike.s$^{-1}$\\
+	$\boldsymbol{\theta}$ & Vector of connectivity kernel parameters (data generation) & $\left[\begin{array}{cc}
 	200 & -100
@@
 	%$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
-	$n_y$ & number of sensors & 161 & n.a.\\ 
-	$\Delta_y$ & distance between adjacent sensors & 0.05 & mm\\
-	$\sigma_{m}$ & observation kernel full width at half maximum & 0.08 & mm \\
-	$\Sigma_{\varepsilon}$ & observation noise covariance matrix & $0.1 \times I_{n_y}$ & mm$^2$ \\
-	$\sigma_{\eta}$& disturbance covariance function full width at half maximum & 0.18 & mm\\
-	$\sigma_{d}$ & disturbance variance & 0.53 & mV \\
+	$n_y$ & Number of sensors & 161 & n.a.\\ 
+	$\Delta_y$ & Distance between adjacent sensors & 0.05 & mm\\
+	$\sigma_{m}$ & Observation kernel full width at half maximum & 0.08 & mm \\
+	$\Sigma_{\varepsilon}$ & Observation noise covariance matrix & $0.1 \times I_{n_y}$ & mm$^2$ \\
+	$\sigma_{\eta}$& Disturbance covariance function full width at half maximum & 0.18 & mm\\
+	$\sigma_{d}$ & Disturbance variance & 0.53 & mV \\
 	\hline 
@@
 	\hline
-	$n_x$ & number of field basis functions&& n.a.\\
-	$   $ &Experiment~I&131&\\
-	$   $ &Experiment~II&17, 33, 65, 131, 263&\\ 
+	$n_x$ & Number of field basis functions&& n.a.\\
+	$   $ &Experiment~I, $j=3$&131&\\
+	$   $ &Experiment~II, $j=0,1,2,3,4$&17, 33, 65, 131, 263&\\ 
 	\hline 
@@
 	\hline
-	$n_{\theta}$&number of connectivity kernel basis functions for estimation&25&n.a.\\
+	$n_{\theta}$&Number of connectivity kernel basis functions for estimation&25&n.a.\\
 	\hline 
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/fig7.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig6.pdf}
  		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}  
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/fig8.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig7.pdf}
  		\caption{{\bf Convergence of the EM based algorithm}. The mean  of
@@
  \centering
-\includegraphics{./Graph/fig9.pdf}
+\includegraphics{./Graph/fig8.pdf}
 \caption{ {\bf Connectivity kernel estimate}.
@@
 \centering
-\includegraphics{./Graph/fig10.pdf}
+\includegraphics{./Graph/fig9.pdf}
 \caption{ {\bf Examples of the actual and estimated neural fields for experiment I}.
@@
 The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
-The RMSE of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
+The mean over time of the root mean square error (MRMSE) over space of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
 By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ (used in the first experiment) is in fact adequate to capture the dynamics of the underlying field.
@@
  	\centering
- 		\includegraphics[scale=1]{./Graph/fig11.pdf}
+ 		\includegraphics[scale=1]{./Graph/fig10.pdf}
  		\caption{{\bf Error in the field reconstruction for experiment II}.
@@
 	\centering
-		\includegraphics[scale=1]{./Graph/fig12.pdf}
+		\includegraphics[scale=1]{./Graph/fig11.pdf}
 	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
@@
 \begin{equation}
- \boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right)
+ \boldsymbol\Xi_0=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right).
 \end{equation}   

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to two scale relationship

@@
 The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale.
-For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
-\begin{align}
- N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
-  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
+For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of \citep{Chui1992}
+\begin{align}
+ N_{m}\left(r\right)&=\sum_{n=0}^{m}  p_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
+  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2} q_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
  \end{align}
@@
  \begin{align}
-\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
-\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
- \end{align}
-and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.
+ p_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
+q_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
+ \end{align}
+% and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients .
 

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 \begin{align}      
-	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
 \end{align}

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
minor edit
edit to biplane section

@@
 \subsection{A Brief Introduction to B-Spline Wavelets}
-This section is included to provide the interested reader with an overview of the theory for  scaling and wavelet functions that form the basis of the multi-resolution model.
+This section is included to provide the interested reader with an overview of the theory used in constructing the wavelets that form the basis of the multi-resolution model.
 Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.
@@
 \caption{{\bf Examples of cardinal B-spline functions}.
-Piecewise polynomial functions (dotted lines) are joined at the break points (black dots).
+Piecewise polynomial functions (dotted lines) are joined at the break points (black circles).
 (\textbf{A}) B-spline function of order 2 (linear B-spline).
@@
 \end{align}
-where $[\cdot]_{i:} $ denotes the $i^{th}$ row.
+where $\left[\cdot\right]_k$ denotes the $k^{th}$ element of the vector and $[\cdot]_{i:} $ denotes the $i^{th}$ row.
 The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t^b$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),

### 2012-06-17 Multiresolution_framework/ltx/manuscript.tex
minor edits across paper

@@
 
-The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability to infer parameters from electrophysiological data.
+The utility of these models for answering questions in clinical neuroscience and neurology lies in the ability to infer physiological parameters from electrophysiological data.
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
@@
 A natural framework to perform this is the well known EM algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case.
+The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations, and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, which are the weights of the field basis functions in this case.
 The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
@@
 Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}.
+For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \citep{RAUCH1965}.
 For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
@@
 \end{align} 
-where $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where 
+and $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where 
 \begin{align}
@@
 The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations.
-The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}.
+The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citet{Freestone2011}.
 The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.
@@
 \section{Acknowledgements}
-The research reported herein was partly supported by the Brain Network Recovery Group through the James S. McDonnell Foundation and the FP7-ICT BrainScales.
+The research reported herein was partly supported by the Brain Network Recovery Group through the James S.
+McDonnell Foundation and the FP7-ICT BrainScales.
+This research was also partly supported by the Australian Research Council (Linkage Project LP100200571).
 

### 2012-06-17 Multiresolution_framework/ltx/SubmissionLetter.tex
Paper submitted to NeuroImage.

%
%  untitled
%
%  Created by Dean Freestone on 2010-06-28.
%  Copyright (c) 2010 . All rights reserved.
%
\documentclass[a4paper,10pt]{letter}
\usepackage{anysize} 									%<-use this for checking equation length

\marginsize {1.7cm}{1.5cm}{1cm}{1cm} 				%<-use this for checking equation length

\signature{P. Aram}
\address{Theoretical Neuroscience Group \\
UMR 1106\\ Institut de Neurosciences des Systemes \\ 13385 Marseille \\ France}

\begin{document}
\vspace{-1cm}
\begin{letter}{Editor/Reviewer \\ Neuroimage}

\opening{Dear Sir or Madam,}

% \emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}

I am writing to seek publication of our research article titled `Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model' in Neuroimage.

The novel aspects of this paper include:
\begin{itemize}
	\item a multi-resolution model-based, data-driven estimator of continuum neural field parameters ;
	\item simultaneous representation of both the macroscopic and microscopic dynamics of the system ;
	\item a derivation of an algorithm for estimating intracortical connectivity with an arbitrary shape using the Amari type neural field equations.
\end{itemize}

Thank you for your time and consideration in reviewing this article. We look forward to hearing the outcome of the review.

\closing{Best Regards,}

\end{letter}
\end{document}

### 2012-06-17 Multiresolution_framework/ltx/manuscript.tex
Paper submitted to NeuroImage.

@@
 \usepackage{setspace} 
-\usepackage[usenames,dvipsnames]{color}  
+% \usepackage[usenames,dvipsnames]{color}  
 %This bit is how to use hyperlink without  coloured rectangles around it
 \usepackage{float}
-\usepackage{hyperref}
-\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
-\usepackage{psfrag}
-\newcommand{\dean}[1]{\textcolor{green}{#1}}
-\newcommand{\parham}[1]{\textcolor{blue}{#1}}
-\newcommand{\vik}[1]{\textcolor{red}{#1}}
-
-%\newfloat{algorithm}{htbp}{loa}%[chapter]
-%\floatname{algorithm}{Algorithm}
+% \usepackage{hyperref}
+% \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
+% \newcommand{\dean}[1]{\textcolor{green}{#1}}
+% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+% \newcommand{\vik}[1]{\textcolor{red}{#1}}
+
 \journal{Neuroimage}
@@
 \end{keyword}
-
 \end{frontmatter}
-
 \section{Introduction}
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
-Large-scale neuroinformatic efforts, such as the Virtual Brain project (\href{http://www.thevirtualbrain.org}{www.thevirtualbrain.org} \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.
+Large-scale neuroinformatic efforts, such as the Virtual Brain project (www.thevirtualbrain.org \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.
 This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
@@
 This multi-resolution structure is depicted in Fig.~\ref{fig:MultiLayerFieldModel}.
-\begin{figure}[t]
-	% \centering
-		\includegraphics[scale=1]{./Graph/fig1.pdf}
-	\caption{{\bf Multi-layer neural field structure}. The inset figures show the shape of the
-connectivity kernel components at each spatial resolution.}
-	\label{fig:MultiLayerFieldModel}
-\end{figure}
 
@@
 This paper is directed at developing a framework for patient-specific multi-resolution neural field models, forming a fundamental link between data and theory.
-
 \section{IDE Neural Field Model}
-\singlespacing
-\begin{table*}[!t]
-\begin{tabular}{|l|l|l|}
-	\hline
-	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
-	\hline
-	$\Omega$ & Spatial domain & n.a.\\
-	$\mathbf{r}$ & Spatial location & [mm, mm]\\
-	$t$ & Time & s\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Model}}\\
-	\hline
-    $y_t$ & Observation & mV\\
-    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
-	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
-	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
-	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
-	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
-	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
-	$h(t)$ & Post-synaptic response kernel & n.a.\\
-	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
-	$\delta(t)$ & Dirac-delta function & n.a.\\
-	\hline    
-	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
-	\hline                                                   
-	$\phi_{j,l}(r)$&Scaling function&n.a\\
-	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
-	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
-	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
-	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
-	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
-	\hline
-	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
-	\hline
-		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
-		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
-   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
-		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
-		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
-		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&s, mV.spike$^{-1}$\\
-   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
-    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
-   	$\mathbf{C}$ & Observation matrix & n.a. \\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
-	\hline
-	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
-	\hline
-	\multicolumn{3}{|c|}{\emph{Estimation}} \\
-	\hline
-	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
-	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
-	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
-	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
-	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
-	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
-	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
-	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
-	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
-	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
-	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
-	\hline
-\end{tabular}
-\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper.
-The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
-\label{tab:Notation}
-\end{table*}  
-\doublespacing
-
 In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
@@
 where in this first-order (in time) formulation of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step.
-% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$.
-The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}.
-The components of the model are shown in Fig.~\ref{fig:Modelcomponents}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=1]{./Graph/fig2.pdf}
-\caption{ {\bf The IDE neural field model components}.
-(\textbf{A}) The Mexican hat (solid line) and Wizard hat (dotted line) connectivity kernels composed of Gaussian and Laplacian basis functions respectively.
-(\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.
-(\textbf{C}) The sigmoidal (solid line) and the Heaviside (dotted line) activation functions.}
-
-\label{fig:Modelcomponents}
-\end{figure}
 The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially colored but temporally white, with covariance function
@@
 The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.
-
 \section{MRA of the IDE in State-Space}
@@
 The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
-% form a parameterized equation for coefficients of the field basis functions $\mathbf{x}_t$, which becomes the state vector.
 
@@
 
-% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
-% \begin{equation}
-% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
-% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
-% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
-% \end{cases}
-% \end{equation}
 The dynamic neural field is decomposed using
@@
 \end{align}
-% where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, \dean{($\boldsymbol\theta \in \mathbb{R}^{n_{\theta}\times (J+2)}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x \times (J+2)}$)} are defined as
-% \begin{align}
-% \boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
-% \label{KernelWeights} \\
-% \mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
-% \label{FieldWeights}
-% \end{align}
-% The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
-Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
-% 
-% The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
-% \begin{align}
-%     \label{KernelBasisVector}
-%     \boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
-%     \begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
-%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
-%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
-%     \cdots &
-%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
-%     \label{FieldBasisVector}
-%     \boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
-%     \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
-%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
-%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
-%     \cdots &
-%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
-% \end{align}
-% 
-% The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
 Now we have the compact form of the decomposition we can substitute this into the neural field Eq.~\eqref{eq:DiscreteTimeModel} giving
@@
 \end{equation}
-% Substituting Eq.~\eqref{eq:KernelFiniteExpansion} and Eq.~\eqref{eq:FieldFiniteExpansion} in Eq.~\eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
-% \begin{align}\label{eq:DecomposedModel2} 
-% 	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
-% 	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
-% \end{align}
-% Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
-% \begin{align}\label{eq:StateEquation}
-%  \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
-% \label{eq:A_theta}
-%  \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
-% \end{align}
-% The disturbance becomes 
-% \begin{equation}\label{eq:Disturbance}
-% \mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
-% \end{equation}
-% which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
-% \begin{equation}\label{eq:CovMatrix}
-% \boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
-% \end{equation}
 The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
@@
 The degree of smoothness is determined by the order of splines \citep{Goswami1999}, where the higher the order the smoother the resulting B-spline becomes (see Fig.~\ref{fig:Figure0}).
-\begin{figure}[!t]
-\centering
-\includegraphics{./Graph/fig3.pdf}
-\caption{{\bf Examples of cardinal B-spline functions}.
-Piecewise polynomial functions (dotted lines) are joined at the break points (black circles).
-(\textbf{A}) B-spline function of order 2 (linear B-spline).
-(\textbf{B}) B-spline function of order 8.}
-\label{fig:Figure0}
-\end{figure}
 
@@
 where subscripts $j$ and $l$ in Eqs.~\eqref{eq:ScalingSupport} and \eqref{eq:WaveletSupport} are introduced to $N_{m}(r)$ and $\varphi_{m}(r)$ to indicate the scale and translation parameters as defined in Eqs~\eqref{eq:generalscalingfinction} and \eqref{eq:generalwaveletfinction}.
-\begin{figure}[!t]
-\centering
-\includegraphics{./Graph/fig4.pdf}
-% \includegraphics{./Graph/Figure1b.pdf}
-\caption{{\bf Examples of B-spline scaling and wavelet functions}. (\textbf{A}) The cubic B-spline scaling function. (\textbf{B}) The corresponding wavelet function.}
-\label{fig:MRA-Figure1}
-\end{figure}
 
@@
 In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}).
-% For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving
-% \begin{align}\label{eq:MRA-ConvertingFormulaForscalingFunctions}
-%  &N_m(r)=\nonumber \\
-% &\sum_{n_1,n_2, \dots n_j=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_j}N_m(2^jr-l_{n_1,n_2, \dots, n_j}),
-% \end{align}
-% where 
-% \begin{align}
-%  l_{n_1,n_2, \dots, n_j}=2^{j-1}n_1+2^{j-2}n_2+ \dots +2^{0}n_j.
-% \end{align}  
-% The relation \eqref{eq:MRA-ConvertingFormulaForscalingFunctions} can be also proven by induction (see \ref{ap:Induction}).
-A similar method can be used for wavelet functions noting that they must be written first in terms of scaling functions using Eq.~\eqref{eq:MRA-TwoScalepair2}.
-Examples of such expansions are given in Fig.~\ref{fig:MRA-BasisDecomposition} where the scaling and wavelet functions at $j=0$ are written in terms of 625 and 1250 scaling functions at $j=4$ respectively.
-% \begin{figure}[!t] 
-%  	\centering
-%  		\includegraphics[scale=1]{./Graph/fig5.pdf}
-%  		\caption{{\bf The scaling and the wavelet function decomposition}.
-(\textbf{A}) The scaling function (dotted line) at $j=0$ is obtained using 625 scaling functions (solid lines) at $j=4$.
-(\textbf{B}) The wavelet function (dotted line) at $j=0$ is obtained using 1250 scaling functions (solid lines) at $j=4$.}
-%  	\label{fig:MRA-BasisDecomposition}
-%  \end{figure}  
 In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
+\subsection{Frequency Analysis}\label{sec:freq_anal}
+To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}.
+To proceed the Fourier transform of $N_1(r)$ is first calculated,
+\begin{align}\label{eq:MRA-N1Fouriertransform}
+\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
+\end{align}
+where $\nu$ is the spatial frequency and $i=\sqrt{-1}$.
+The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
+Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
+\begin{align}\label{eq:MRA-NmFouriertransform}
+\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
+\end{align}
+The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
+\begin{align}      
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
+\end{align}
+From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
+This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
+\section{State and Parameter Estimation}
+The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm.
+Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.
+
+There exist many variations of state and parameter estimation methods for state-space models.
+The choice of algorithm is normally determined by the dimension of the system, whether the system is linear or nonlinear and whether or not the parameters are considered static or dynamic.
+Up to this point of the paper, we have not made any assumptions on any of these criteria for choosing an estimation algorithm.
+The MRAIDE neural field model formulation may be used in any of the above scenarios.
+
+To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+Note that there is a difference between forward and inverse modeling when making these assumptions.
+For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
+The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm.
+The loss in model accuracy may be offset estimation accuracy.
+
+The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
+The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
+
+By assuming a linear activation function of the form
+\begin{equation}
+	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}),
+\end{equation}
+the state transition equation~\eqref{eq:ApproxDiscreteTimeModel4} simplifies to
+\begin{equation}\label{eq:ApproxDiscreteTimeModel_Linear}
+	\mathbf{x}_{t+1} = 
+	\xi \mathbf{x}_t + 
+	\varsigma T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
+	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
+	    \boldsymbol\mu^\top\left(\mathbf{r}'\right) 
+	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}} \mathbf{x}_t
+	+ \mathbf{w}_t.
+\end{equation}
+Now we can further simplify the system by defining
+\begin{align}
+	\label{eq:Lambdatheta}
+	 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
+		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
+		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r},
+\end{align}
+to give the state equation
+\begin{equation}\label{eq:StateEquation}
+ \mathbf x_{t+1} =\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
+\end{equation} 
+with the parameterized transition matrix
+\begin{equation}\label{eq:A_theta}
+ \mathbf A(\boldsymbol \theta)= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
+\end{equation} 
+The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:ReducedObservationEquation} and Eq.~\eqref{eq:StateEquation}  can now be formulated as 
+\begin{equation}
+	{\hat{\mathbf X},\hat{\boldsymbol\theta}}=\arg\max_{\mathbf X,\boldsymbol\theta}p(\mathbf Y;\boldsymbol\theta),
+ \end{equation}  
+where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function.
+This dual estimation problem cannot be solved separately, as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
+One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
+A natural framework to perform this is the well known EM algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
+The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations, and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, which are the weights of the field basis functions in this case.
+The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
+\begin{equation}
+	\boldsymbol\theta_{\text{ML}}=\arg\max_{\boldsymbol\theta}~p(\mathbf Y;\boldsymbol\theta),
+ \end{equation}   
+and the posterior distribution of the field over time.
+
+Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
+For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \citep{RAUCH1965}.
+For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
+to compute the required quantities are very dependent on the particular application. This will be described in detail for our problem.
+
+In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step.
+A schematic representation of the EM algorithm is represented in Fig.~\ref{fig:EMBlockDiagram}.
+Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors.
+Here the latter is chosen as shown in the block diagram ensuring the resultant initial kernel estimate leads to a stable system.
+\subsection{E-step}
+As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem.
+We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
+The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
+Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound on the likelihood function.
+Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
+Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
+ \subsection{M-step}
+The lower bound on the log-likelihood function is given by the expectation of the complete (hidden and observable) data  log-likelihood \citep{Bishop2006} 
+\begin{equation}\label{eq:Bishopbound}
+	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right], 
+\end{equation}
+where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
+$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
+Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is in fact the smoother output which is obtained at the E-step.
+
+For the linear state-space model given by Eqs.~\eqref{eq:ReducedObservationEquation} and \eqref{eq:StateEquation}, the bound defined by Eq.~\eqref{eq:Bishopbound} is a quadratic of the form (see \ref{ap:QDerivation} for derivation)
+\begin{equation}\label{eq:MRA-QCompact}
+\mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
+\end{equation}
+where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation~\eqref{eq:MRA-QCompact} is maximum at
+\begin{align}\label{eq:MRA-thetahat}
+\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top,
+\end{align}
+where
+\begin{align}
+\boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}\label{eq:epsilon0} \\
+\boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \label{eq:epsilon1}\\
+\boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i},\label{eq:Epsilon}
+\end{align} 
+and $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where 
+\begin{align}
+\left[ \Gamma_1\right]^{j,i} &=\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i},\\
+\left[ \Gamma_2\right] ^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
+\end{align}
+Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
+\begin{align}\label{eq:Uij}
+\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
+\end{align}
+where $\left[\cdot\right]_k$ denotes the $k^{th}$ element of the vector and $[\cdot]_{i:} $ denotes the $i^{th}$ row.
+The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t^b$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),
+\begin{align}
+\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi0} \\
+ \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).  \label{eq:Xi1}
+\end{align} 
+The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
+The EM algorithm iterates between these two steps until the parameter estimates converge.
+A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
+\subsection{Stopping rule}
+The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
+\begin{equation}
+ \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
+ \end{equation}
+ where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \citet{Meyer2000}
+ \begin{equation}
+  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}.
+ \end{equation}
+\subsection{Computational complexity} 
+All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
+The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified.
+It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to the method proposed in \citet{Dewar2009}.
+This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.
+\section{Results}\label{sec:MRA-results}
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
+In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.
+$T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
+The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape
+\begin{equation}\label{eq:ConnectivityKernelForData}
+	w(r-r')=\theta_1\times N_{4;1,2}(r-r')+\theta_2\times N_{4;0,2}(r-r'),
+\end{equation}
+with $\theta_1=200$ and $\theta_2=-100$. This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
+
+Two different experiments were designed to test the framework.
+In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run.
+This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
+In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
+$j=0$ to $j=4$.
+All parameters for the model are given in Table~\ref{tab:Parameters}.
+
+For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilize from the initial conditions.
+The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
+The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
+The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
+The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations.
+The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citet{Freestone2011}.
+The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.
+With this number of observations, the estimation problem was well-posed, i.e.
+the number of states, $n_x < n_y$ at each level of the decomposition.
+This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
+\subsection{Experiment I}
+The spatial frequency response of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
+This is shown in Fig.~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
+The spatial bandwidths of wavelets were calculated analytically using Eq.~\eqref{eq:MRA-Wavelettransform}.
+The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions for $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively for $j=0$, $j=1$, $j=2$ and $j=3$.
+
+The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
+The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}.
+
+The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A).
+No assumptions where made about the shape of the kernel.
+The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
+The large standard deviation is due to the high number of parameters needed to be estimated.
+The small error in the estimate is attributed to the MRA of the system used to form the estimator.
+Figs.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
+A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively.
+
+One snap shot of the field reconstruction, at different levels of approximation is given in Fig.~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
+From this figure, it can be observed that the overall trend of the underlying field can be also captured at the coarser levels.
+\subsection{Experiment II}
+To study the performance of different models with various MRA capabilities, a single realization was obtained using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
+The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
+The mean over time of the root mean square error (MRMSE) over space of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
+By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ (used in the first experiment) is in fact adequate to capture the dynamics of the underlying field.
+The spatiotemporal characteristics of the reconstructed fields (A-E) along with the actual field (F)  are shown in Fig.~\ref{fig:FieldEstimation}.
+The experiment was performed several times and the results were consistent over each run.
+\section{Discussion}
+In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
+The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
+By decomposing both the spatial field and the connectivity kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
+This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics.
+Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
+\subsection{Estimation algorithm}
+For a larger space, or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
+One solution to this problem could be expectation-conditional maximization (ECM) \citep{Meng1993,Meng1994}, which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
+The ECM is a class of generalized EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximized \citep{Fessler1994}.
+For systems with a high number of states, the ensemble Kalman smoother (EnKS) \citep{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
+The EnKS is a sequential Monte Carlo (MC) method where the state covariance matrix is approximated by a large stochastic ensemble of model states, thus alleviating computational load due to the storage and forward integration of the state covariance matrix.
+However, combining the EnKS with the EM algorithm suffers from the loss of monotonicity property --- increase in the likelihood function--- as MC error will be introduced at the E-step.
+
+Typically, a sequence of likelihood values will converge to a stationary point i.e.
+global (local) maximum or a saddle point.
+If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}.
+In general, convergence of the EM algorithm to any stationary point depends on the initialization.
+In the examples presented in this paper, a bounded sequence of the state vectors was used to initialize the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
+
+Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
+This simplifies the computational complexity of the estimation algorithm significantly.
+Although this is correct for one dimensional B-spline scaling and wavelet functions, it does not hold at higher dimensions as the resulting B-spline wavelets are not isotropic.
+One alternative could be
+isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
+ \subsection{Modification to higher dimensions}
+ The reconstruction of the neural field in higher dimensions requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
+For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}.
+In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations.
+The formulations provided in this paper can be easily extended to two dimensions.
+However, the computational load of the estimation algorithm will be significant.
+It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
+\subsection{Extensions to the framework} 
+Clearly there is, and will always be, a discrepancy between the dynamics of the model and the experimental observation.
+Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
+The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}.
+The key development is the multi-resolution decomposition forming the state-space model.
+While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.
+
+Additional extension for future work include extending the model to capture a second order synaptic response kernel.
+The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials ( see \citet{Spiegler2010,Spiegler2011} for example).
+Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
+In small networks the resulting delays via propagation can be neglected.
+However, delays must be accounted for in large scale networks.
+For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review).
+In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
+To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.
+Finally, future work should be directed towards applying and validating the framework on real data.
+\section{Acknowledgements}
+The research reported herein was partly supported by the Brain Network Recovery Group through the James S.
+McDonnell Foundation and the FP7-ICT BrainScales.
+This research was also partly supported by the Australian Research Council (Linkage Project LP100200571).
+\clearpage
+\newpage
+\section*{Tables}
+ \singlespacing
+\begin{table*}[!t]
+\begin{tabular}{|l|l|l|}
+	\hline
+	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
+	\hline
+	$\Omega$ & Spatial domain & n.a.\\
+	$\mathbf{r}$ & Spatial location & [mm, mm]\\
+	$t$ & Time & s\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Model}}\\
+	\hline
+    $y_t$ & Observation & mV\\
+    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
+	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
+	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
+	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
+	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
+	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
+	$h(t)$ & Post-synaptic response kernel & n.a.\\
+	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
+	$\delta(t)$ & Dirac-delta function & n.a.\\
+	\hline    
+	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
+	\hline                                                   
+	$\phi_{j,l}(r)$&Scaling function&n.a\\
+	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
+	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
+	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
+	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
+	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
+	\hline
+	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
+	\hline
+		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
+		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
+   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
+		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
+		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
+		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&s, mV.spike$^{-1}$\\
+   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
+    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
+   	$\mathbf{C}$ & Observation matrix & n.a. \\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
+	\hline
+	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
+	\hline
+	\multicolumn{3}{|c|}{\emph{Estimation}} \\
+	\hline
+	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
+	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
+	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
+	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
+	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
+	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
+	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
+	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
+	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
+	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
+	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
+	\hline
+\end{tabular}
+\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper.
+The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
+\label{tab:Notation}
+\end{table*}  
+\doublespacing
+\clearpage
+\newpage
 \begin {table}[t]
@@
  \end {table}
-\subsection{Frequency Analysis}\label{sec:freq_anal}
-To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}.
-To proceed the Fourier transform of $N_1(r)$ is first calculated,
-\begin{align}\label{eq:MRA-N1Fouriertransform}
-\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
-\end{align}
-where $\nu$ is the spatial frequency and $i=\sqrt{-1}$.
-The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
-Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
-\begin{align}\label{eq:MRA-NmFouriertransform}
-\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
-\end{align}
-The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
-\begin{align}      
-	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
-\end{align}
-From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
-This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
-
-\section{State and Parameter Estimation}
-The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm.
-Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.
-
-There exist many variations of state and parameter estimation methods for state-space models.
-The choice of algorithm is normally determined by the dimension of the system, whether the system is linear or nonlinear and whether or not the parameters are considered static or dynamic.
-Up to this point of the paper, we have not made any assumptions on any of these criteria for choosing an estimation algorithm.
-The MRAIDE neural field model formulation may be used in any of the above scenarios.
-
-To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
-Note that there is a difference between forward and inverse modeling when making these assumptions.
-For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
-The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm.
-The loss in model accuracy may be offset estimation accuracy.
-
-The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
-The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
-
-% The linearised activation function is 
-% \begin{align}
-% 	\hat{f}(v_t\left(\mathbf{r}\right)) &= f(v_0) + f'(v_0)(v_t\left(\mathbf{r}\right) - v_0) \\
-% 	&= \frac{2 + \varsigma(v_t\left(\mathbf{r}\right) - v_0)}{4}. \label{eq:LinearActivationFunction} 
-% \end{align}
-
-By assuming a linear activation function of the form
-\begin{equation}
-	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}),
-\end{equation}
-the state transition equation~\eqref{eq:ApproxDiscreteTimeModel4} simplifies to
-\begin{equation}\label{eq:ApproxDiscreteTimeModel_Linear}
-	\mathbf{x}_{t+1} = 
-	\xi \mathbf{x}_t + 
-	\varsigma T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
-	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
-	    \boldsymbol\mu^\top\left(\mathbf{r}'\right) 
-	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}} \mathbf{x}_t
-	+ \mathbf{w}_t.
-\end{equation}
-Now we can further simplify the system by defining
-\begin{align}
-	\label{eq:Lambdatheta}
-	 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
-		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
-		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r},
-\end{align}
-to give the state equation
-\begin{equation}\label{eq:StateEquation}
- \mathbf x_{t+1} =\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
-\end{equation} 
-with the parameterized transition matrix
-\begin{equation}\label{eq:A_theta}
- \mathbf A(\boldsymbol \theta)= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
-\end{equation} 
-The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:ReducedObservationEquation} and Eq.~\eqref{eq:StateEquation}  can now be formulated as 
-\begin{equation}
-	{\hat{\mathbf X},\hat{\boldsymbol\theta}}=\arg\max_{\mathbf X,\boldsymbol\theta}p(\mathbf Y;\boldsymbol\theta),
- \end{equation}  
-where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function.
-This dual estimation problem cannot be solved separately, as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known.
-One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm.
-A natural framework to perform this is the well known EM algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application.
-The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations, and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, which are the weights of the field basis functions in this case.
-The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
-\begin{equation}
-	\boldsymbol\theta_{\text{ML}}=\arg\max_{\boldsymbol\theta}~p(\mathbf Y;\boldsymbol\theta),
- \end{equation}   
-and the posterior distribution of the field over time.
-
-Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood.
-For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \citep{RAUCH1965}.
-For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
-to compute the required quantities are very dependent on the particular application. This will be described in detail for our problem.
-
-In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step.
-A schematic representation of the EM algorithm is represented in Fig.~\ref{fig:EMBlockDiagram}.
-Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors.
-Here the latter is chosen as shown in the block diagram ensuring the resultant initial kernel estimate leads to a stable system.
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=1]{./Graph/fig5.pdf}
-\caption{{\bf Schematic of the EM algorithm}.
-The RTS smoother (E-step) and the maximization of the lower bound, $\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')$, (M-step) are shown.
-The dashed box shows the iterative two step algorithm once it is initialized.}
-\label{fig:EMBlockDiagram}
-\end{figure}
-\subsection{E-step}
-As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem.
-We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system.
-The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$.
-Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound on the likelihood function.
-Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$).
-Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
+\clearpage
+\newpage 
 \renewcommand{\arraystretch}{1.7}
@@
 \renewcommand{\arraystretch}{1}  
- \subsection{M-step}
-The lower bound on the log-likelihood function is given by the expectation of the complete (hidden and observable) data  log-likelihood \citep{Bishop2006} 
-\begin{equation}\label{eq:Bishopbound}
-	\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')= \mathbf E_{\boldsymbol \theta'}\left[2\ln p(\mathbf X,\mathbf Y;\boldsymbol \theta)\right], 
-\end{equation}
-where $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ is the joint probability distribution of the states and the observations and $ \mathbf E_{\boldsymbol \theta'}\left[\cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, $\boldsymbol\theta'$ i.e.
-$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-Note that $p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$), is in fact the smoother output which is obtained at the E-step.
-
-For the linear state-space model given by Eqs.~\eqref{eq:ReducedObservationEquation} and \eqref{eq:StateEquation}, the bound defined by Eq.~\eqref{eq:Bishopbound} is a quadratic of the form (see \ref{ap:QDerivation} for derivation)
-\begin{equation}\label{eq:MRA-QCompact}
-\mathcal Q\left(\boldsymbol \theta,\boldsymbol\theta'\right)=\beta+2T_s\varsigma\left(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1\right)\boldsymbol\theta-T_s\varsigma\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta,
-\end{equation}
-where $\beta$ is constant with respect to $\boldsymbol\theta$. Equation~\eqref{eq:MRA-QCompact} is maximum at
-\begin{align}\label{eq:MRA-thetahat}
-\boldsymbol \theta= \boldsymbol\Upsilon^{-\top}(\boldsymbol\upsilon_0-\boldsymbol\upsilon_1)^\top,
-\end{align}
-where
-\begin{align}
-\boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\boldsymbol\Gamma_1]_{j,i}\label{eq:epsilon0} \\
-\boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_1]^{j,i} \label{eq:epsilon1}\\
-\boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\boldsymbol\Gamma_2]^{j,i},\label{eq:Epsilon}
-\end{align} 
-and $[\cdot]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, $ [\cdot]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where 
-\begin{align}
-\left[ \Gamma_1\right]^{j,i} &=\sum_{k=1}^{n_x}\left[ \boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\right]_{jk} \left[ \mathbf U\right]^{k,i},\\
-\left[ \Gamma_2\right] ^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf U^{\top}]^{jk} \left[\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1} \right]_{km}[\mathbf U]^{mi}.
-\end{align}
-Each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
-\begin{align}\label{eq:Uij}
-\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
-\end{align}
-where $\left[\cdot\right]_k$ denotes the $k^{th}$ element of the vector and $[\cdot]_{i:} $ denotes the $i^{th}$ row.
-The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ in Eqs.~\eqref{eq:epsilon0}-\eqref{eq:Epsilon} are calculated using the RTS smoother outputs: $\hat{\mathbf x}_t^b$, covariance, $\mathbf P_t^b$, and cross-covariance matrix, $\mathbf M_t$ \citep{Gibsona2005} (see \ref{ap:Xiderivation} for details),
-\begin{align}
-\boldsymbol\Xi_0&=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t^b\mathbf{\hat x}_{t+1}^{b\top}\right) \label{eq:Xi0} \\
- \boldsymbol\Xi_1&=\sum_{t=0}^{T-1}\left(\mathbf P_t^b+\mathbf{\hat x}_t^b\mathbf{\hat x}_t^{b\top}\right).  \label{eq:Xi1}
-\end{align} 
-The algorithm has two steps: the E-step, which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step, which updates the parameter estimates by computing the (analytic) maximum of $Q(\boldsymbol\theta,\boldsymbol\theta')$.
-The EM algorithm iterates between these two steps until the parameter estimates converge.
-A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
-\subsection{Stopping rule}
-The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
-\begin{equation}
- \left(\parallel \mathbf{A} \parallel_{F}^{(i)}-\parallel \mathbf{A} \parallel_{F}^{(i-1)}\right)<\epsilon,
- \end{equation}
- where $\epsilon$ is a threshold value and $\parallel \mathbf{A} \parallel_{F}^{(i)}$ and $ \parallel \mathbf{A} \parallel_{F}^{(i-1)}$ are the Frobenius norms  of the successive estimates of $\mathbf{A} $ matrices which is defined by \citet{Meyer2000}
- \begin{equation}
-  \parallel \mathbf{A} \parallel_{F}=\sqrt{\sum_{i,j=1}^{n_x}\mid a_{i,j} \mid^2}=\sqrt{\mathrm{tr} (\mathbf A^{\top}\mathbf A)}.
- \end{equation}
-\subsection{Computational complexity} 
-All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
-The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified.
-It can be seen from the table that the state dimension is an important factor at each iteration of the estimation algorithm, emphasizing the advantage of the proposed algorithm compared to the method proposed in \citet{Dewar2009}.
-This also suggests the use of an efficient algorithm to choose the minimum number of basis functions (states of the system) while achieving the desired details of the underlying field.
+\clearpage
+\newpage
 \begin {table}
@@
 \end {table} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
+\newpage
 \renewcommand{\arraystretch}{1.7}
@@
 \renewcommand{\arraystretch}{1}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
-In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.
-$T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small.
-The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape
-\begin{equation}\label{eq:ConnectivityKernelForData}
-	w(r-r')=\theta_1\times N_{4;1,2}(r-r')+\theta_2\times N_{4;0,2}(r-r'),
-\end{equation}
-with $\theta_1=200$ and $\theta_2=-100$. This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
-
-Two different experiments were designed to test the framework.
-In the first one, 200 realizations of 1 second of data were used, where the field disturbance, $e_t$, and the observation noise, $\boldsymbol\epsilon_t$, were regenerated each run.
-This way the net shape of the connectivity kernel could be formed by averaging over the parameters estimates from each realization.
-In the second experiment, a single data set was generated and the field estimations are compared for five state-space models, each accounting up to a certain level of approximation, i.e.
-$j=0$ to $j=4$.
-All parameters for the model are given in Table~\ref{tab:Parameters}.
-
-For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilize from the initial conditions.
-The initial state, parameters and the support of the connectivity kernel were unknown to the estimator.
-The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.
-The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}.
-The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations.
-The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citet{Freestone2011}.
-The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.
-With this number of observations, the estimation problem was well-posed, i.e.
-the number of states, $n_x < n_y$ at each level of the decomposition.
-This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
+\clearpage
+\newpage 
 \begin{table*}[!ht]
@@
 	\right]^{\top}$ & mV.spike$^{-1}$\\
-	%$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
 	$n_y$ & Number of sensors & 161 & n.a.\\ 
@@
 \end{table*}   
-\subsection{Experiment I}
-The spatial frequency response of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-This is shown in Fig.~\ref{fig:ObservationFrequencyResponce} where the graph obtained by averaging the spectral power of the spatial frequency (over time) from the observations \citep{Scerri2009}.
-The spatial bandwidths of wavelets were calculated analytically using Eq.~\eqref{eq:MRA-Wavelettransform}.
-The result suggested that wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field which yields $n_x = 131$ states, corresponding to 9 scaling functions for $j=0$ and 8, 16, 32 and 66 wavelet functions, respectively for $j=0$, $j=1$, $j=2$ and $j=3$.
-\begin{figure}[!t]
- 	\centering
- 		\includegraphics[scale=1]{./Graph/fig6.pdf}
- 		\caption{{\bf Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.}  
-\label{fig:ObservationFrequencyResponce} 
- \end{figure}
-
-The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations.
-The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}.
-\begin{figure}[t]
- 	\centering
- 		\includegraphics[scale=1]{./Graph/fig7.pdf}
- 		\caption{{\bf Convergence of the EM based algorithm}. The mean  of
-the $\mathbf A(\boldsymbol\theta)$ Frobenius norm over 200 realizations vs iterations of the EM based algorithm.
-The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.}
-\label{fig:MRA-Convergence}  
- \end{figure}     
-% The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets.
-Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}.
-Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.
-The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A).
-No assumptions where made about the shape of the kernel.
-The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval.
-The large standard deviation is due to the high number of parameters needed to be estimated.
-The small error in the estimate is attributed to the MRA of the system used to form the estimator.
-Figs.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively.
-A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively.
-\begin{figure}[!t]  
- \centering
-\includegraphics{./Graph/fig8.pdf}
-\caption{ {\bf Connectivity kernel estimate}.
+\newpage
+\clearpage
+\section*{Figure Legends}
+{\bf Figure 1. Multi-layer neural field structure}. The inset figures show the shape of the
+connectivity kernel components at each spatial resolution.
+
+{\bf Figure 2.
+The IDE neural field model components}.
+(\textbf{A}) The Mexican hat (solid line) and Wizard hat (dotted line) connectivity kernels composed of Gaussian and Laplacian basis functions respectively.
+(\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels.
+(\textbf{C}) The sigmoidal (solid line) and the Heaviside (dotted line) activation functions.
+
+{\bf Figure 3.
+Examples of cardinal B-spline functions}.
+Piecewise polynomial functions (dotted lines) are joined at the break points (black circles).
+(\textbf{A}) B-spline function of order 2 (linear B-spline).
+(\textbf{B}) B-spline function of order 8.
+
+{\bf Figure 4. Examples of B-spline scaling and wavelet functions}. (\textbf{A}) The cubic B-spline scaling function. (\textbf{B}) The corresponding wavelet function.
+
+{\bf Figure 5.
+Schematic of the EM algorithm}.
+The RTS smoother (E-step) and the maximization of the lower bound, $\mathcal Q(\boldsymbol \theta,\boldsymbol\theta')$, (M-step) are shown.
+The dashed box shows the iterative two step algorithm once it is initialized.
+
+{\bf Figure 6. Spatial frequency analysis}. The average (over time) power in dB of the spatial frequency of the observations.
+
+{\bf Figure 7.
+Convergence of the EM based algorithm}.
+The mean  of the $\mathbf A(\boldsymbol\theta)$ Frobenius norm over 200 realizations vs iterations of the EM based algorithm.
+The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.
+
+{\bf Figure 8.
+Connectivity kernel estimate}.
 (\textbf{A}) The actual kernel and its components are shown by solid and dashed black lines, respectively.
 The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.).
-(\textbf{B},\textbf{C}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
-\label{fig:KernelEstimate}
-\end{figure}
-
-One snap shot of the field reconstruction, at different levels of approximation is given in Fig.~\ref{fig:FieldEstimates100}, showing small discrepancy between the actual and estimated field at $j=3$.
-From this figure, it can be observed that the overall trend of the underlying field can be also captured at the coarser levels.
-\begin{figure}[!t]
-\centering
-\includegraphics{./Graph/fig9.pdf}
-\caption{ {\bf Examples of the actual and estimated neural fields for experiment I}.
+(\textbf{B},\textbf{C}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.
+
+{\bf Figure 9.
+Examples of the actual and estimated neural fields for experiment I}.
 Actual (grey) and estimated (black) neural fields at a single time instant for different spatial resolutions.
@@
 (\textbf{C}) $j=2$, $n_x=65$.
-(\textbf{D}) $j=3$, $n_x=131$.}
-% (\textbf{e}) $j=4$, $n_x=263$.
-\label{fig:FieldEstimates100}
-\end{figure}
-\subsection{Experiment II}
-To study the performance of different models with various MRA capabilities, a single realization was obtained using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment.
-The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$.
-The mean over time of the root mean square error (MRMSE) over space of the field estimation for different models is shown in Fig.~\ref{fig:RMSE}.
-By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that the model with $j=3$ (used in the first experiment) is in fact adequate to capture the dynamics of the underlying field.
-The spatiotemporal characteristics of the reconstructed fields (A-E) along with the actual field (F)  are shown in Fig.~\ref{fig:FieldEstimation}.
-The experiment was performed several times and the results were consistent over each run.
- \begin{figure}[!t]	 
- 	\centering
- 		\includegraphics[scale=1]{./Graph/fig10.pdf}
- 		\caption{{\bf Error in the field reconstruction for experiment II}.
+(\textbf{D}) $j=3$, $n_x=131$.
+
+{\bf Figure 10.
+Error in the field reconstruction for experiment II}.
 The mean (over time) of average (over space) RMSE of the estimated field of state-space models with different MRA capabilities.
-$j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
-\label{fig:RMSE}
- \end{figure} 
-\begin{figure}[t]
-	\centering
-		\includegraphics[scale=1]{./Graph/fig11.pdf}
-	\caption{{\bf Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
+$j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$
+
+{\bf Figure 11.
+Actual and estimated spatiotemporal neural field using state-space models with different MRA capabilities}.
 (\textbf{A}) The reconstructed field of the reduced model using wavelet upto $j=0$ with $n_x=17$.
@@
 (\textbf{E}) The reconstructed field using wavelets upto $j=4$ with $n_x=263$.
-(\textbf{F}) The actual field.}
+(\textbf{F}) The actual field.
+  \clearpage
+   \newpage 
+   \begin{figure}[t]
+   		\includegraphics[scale=1]{Graph/fig1.pdf}
+   	\caption{}
+   	\label{fig:MultiLayerFieldModel}
+   \end{figure}  
+ \clearpage
+  \newpage 
+  \begin{figure}[!t]
+  \centering
+  \includegraphics[scale=1]{Graph/fig2.pdf}
+  \caption{}
+  \label{fig:Modelcomponents}
+  \end{figure}
+  \clearpage
+  \newpage  
+  \begin{figure}[!t]
+  \centering
+  \includegraphics{Graph/fig3.pdf}
+  \caption{}
+  \label{fig:Figure0}
+  \end{figure} 
+  \clearpage
+  \newpage
+  \begin{figure}[!t]
+  \centering
+  \includegraphics{Graph/fig4.pdf}
+  \caption{}
+  \label{fig:MRA-Figure1}
+  \end{figure}
+  \clearpage
+  \newpage 
+  \begin{figure}[!t]
+  \centering
+  \includegraphics[scale=1]{Graph/fig5.pdf}
+  \caption{}
+  \label{fig:EMBlockDiagram}
+  \end{figure}
+  \clearpage
+  \newpage 
+  \begin{figure}[!t]
+   	\centering
+   		\includegraphics[scale=1]{Graph/fig6.pdf}
+   		\caption{}  
+  \label{fig:ObservationFrequencyResponce} 
+   \end{figure}
+  \clearpage
+  \newpage
+  \begin{figure}[t]
+   	\centering
+   		\includegraphics[scale=1]{Graph/fig7.pdf}
+   		\caption{} 
+  \label{fig:MRA-Convergence}  
+   \end{figure}  
+   \clearpage
+  \newpage
+  \begin{figure}[!t]  
+   \centering
+  \includegraphics{Graph/fig8.pdf}
+  \caption{}
+  \label{fig:KernelEstimate}
+  \end{figure}
+  \clearpage
+  \newpage
+  \begin{figure}[!t]
+  \centering
+  \includegraphics{Graph/fig9.pdf}
+  \caption{}
+  \label{fig:FieldEstimates100}
+  \end{figure}
+  \clearpage
+  \newpage
+   \begin{figure}[!t]	 
+   	\centering
+   		\includegraphics[scale=1]{Graph/fig10.pdf}
+   		\caption{}
+  \label{fig:RMSE}
+   \end{figure}
+   \clearpage
+  \newpage
+  \begin{figure}[t]
+  	\centering
+  		\includegraphics[scale=1]{Graph/fig11.png}
+  	\caption{} 
   \label{fig:FieldEstimation}
   \end{figure}        
-% \caption{The actual connectivity kernel is shown with the black solid line.
-The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.).
-The 7 weighted kernel basis functions are shown by the black dashed lines.}
-\section{Discussion}
-In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements.
-The novel and key developments of the paper include the multi-resolution finite element model representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape.
-By decomposing both the spatial field and the connectivity kernel using a wavelet decomposition, it becomes possible to represent small scale details in the field at the same time as large scale details.
-This work is significant, as the ability to create patient-specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics.
-Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
-\subsection{Estimation algorithm}
-For a larger space, or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.
-One solution to this problem could be expectation-conditional maximization (ECM) \citep{Meng1993,Meng1994}, which replaces the M-step by a series of computationally simplified conditional maximization (CM) steps.
-The ECM is a class of generalized EM (GEM)  algorithms in which the $\mathcal{Q}$-function is increased rather than being maximized \citep{Fessler1994}.
-For systems with a high number of states, the ensemble Kalman smoother (EnKS) \citep{Evensen2003,Evensen2009a,Evensen2009} provides an alternative to the RTS smoother used in this work.
-The EnKS is a sequential Monte Carlo (MC) method where the state covariance matrix is approximated by a large stochastic ensemble of model states, thus alleviating computational load due to the storage and forward integration of the state covariance matrix.
-However, combining the EnKS with the EM algorithm suffers from the loss of monotonicity property --- increase in the likelihood function--- as MC error will be introduced at the E-step.
-
-Typically, a sequence of likelihood values will converge to a stationary point i.e.
-global (local) maximum or a saddle point.
-If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}.
-In general, convergence of the EM algorithm to any stationary point depends on the initialization.
-In the examples presented in this paper, a bounded sequence of the state vectors was used to initialize the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
-
-Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
-This simplifies the computational complexity of the estimation algorithm significantly.
-Although this is correct for one dimensional B-spline scaling and wavelet functions, it does not hold at higher dimensions as the resulting B-spline wavelets are not isotropic.
-One alternative could be
-isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
-
-  % \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics.
-Our main aim for this framework in the future is to relax these assumptions using the multi-resolution decomposition.
-While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge.
-Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.
-The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel.
-Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}
-
-% In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.
- \subsection{Modification to higher dimensions}
-%To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly. The implementation of the framework in the nonlinear case can be addressed as future work. 
-%Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.
- The reconstruction of the neural field in higher dimensions requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
-For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}.
-In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations.
-The formulations provided in this paper can be easily extended to two dimensions.
-However, the computational load of the estimation algorithm will be significant.
-It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
-\subsection{Extensions to the framework} 
-Clearly there is, and will always be, a discrepancy between the dynamics of the model and the experimental observation.
-Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation.
-The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}.
-The key development is the multi-resolution decomposition forming the state-space model.
-While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.
-
-Additional extension for future work include extending the model to capture a second order synaptic response kernel.
-The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials ( see \citet{Spiegler2010,Spiegler2011} for example).
-Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.
-In small networks the resulting delays via propagation can be neglected.
-However, delays must be accounted for in large scale networks.
-For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review).
-In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
-To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.
-Finally, future work should be directed towards applying and validating the framework on real data.
-
-\section{Acknowledgements}
-The research reported herein was partly supported by the Brain Network Recovery Group through the James S.
-McDonnell Foundation and the FP7-ICT BrainScales.
-This research was also partly supported by the Australian Research Council (Linkage Project LP100200571).
-
+\clearpage
 \newpage   
@@
 \end{align}
-% \section{Scaling function expansion}\label{ap:Induction}  
-% In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$.
-For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
-% \begin{align}
-%  N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
-%   \end{align}
-% which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
-% \begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
-%  &N_m(r)=\nonumber \\
-% &\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
-% \end{align}
-% in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
-% \begin{align}\label{eq:AppendixNj-1intermsofNj}
-%  N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
-% &=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
-% \end{align}
-% Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof. 
-%                   
-%\section{Lower bound on likelihood function}\label{ap:Lowerbound}
-%A derivation of the lower bound on the likelihood function that is based on \citet{Bishop2006} is provided in this Appendix. We want to maximize the likelihood function, 
-%\begin{equation}
- %p(\mathbf Y;\boldsymbol\theta)=\int_{\mathbf X}p(\mathbf X,\mathbf Y;\boldsymbol\theta)\mathrm{d}\mathbf X,
-%\end{equation}
-%which is difficult to perform directly.
-Maximizing the likelihood in terms of the parameter set is equivalent to the log-likelihood maximization, as both the likelihood and log-likelihood functions share the same maximizer due to the monotonicity of the logarithm function.
-For any choice of distribution defined over the hidden variables, $q(\mathbf X)$, the following decomposition holds
-%\begin{equation}\label{eq:EM-loglikelihooddecomposition}
- %\ln~p(\mathbf Y;\boldsymbol\theta)=\mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p),
-%\end{equation}
-%where
-%\begin{align}
- %\mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X,\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \label{eq:EM-decomposition1}\\
-%\mathrm{KL}(q\parallel p)&=-\int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X.
-\label{eq:EM-decomposition2}
-%\end{align}
-%Eq.~\eqref{eq:EM-loglikelihooddecomposition} can be verified by applying the probability product rule to the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol\theta)$ in Eq.~\eqref{eq:EM-decomposition1} giving
-%\begin{align}
- % \mathcal{L}(q,\boldsymbol\theta)+\mathrm{KL}(q\parallel p)&= \int_{\mathbf X} q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)p(\mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X \nonumber\\
-	%&- \int_{\mathbf X}q(\mathbf X)\ln\left\lbrace \frac{p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)}{q(\mathbf X)} \right\rbrace \mathrm{d}\mathbf X\nonumber\\
-	%&= \int_{\mathbf X}q(\mathbf X)\ln p(\mathbf Y; \boldsymbol\theta)\mathrm{d}\mathbf X.
-%\end{align}
-%Noting  $q(\mathbf X)$ is a normalized distribution that integrates to one gives the log-likelihood function.
-We also note that Eq.~\eqref{eq:EM-decomposition2} is the Kullback-Liebler distance between distributions $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$ and $q(\mathbf X)$.
-Therefore,
-%\begin{equation}
- % \mathrm{KL}(q\parallel p)\ge 0.
-%\end{equation}   
-%The equality holds if and only if $q(\mathbf X)=p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
-It follows from  Eq.~\eqref{eq:EM-loglikelihooddecomposition}, that the quantity $\mathcal{L}(q,\boldsymbol\theta)$ is a lower bound on the log-likelihood function, i.e.
-%\begin{equation}
- %\mathcal{L}(q,\boldsymbol\theta)\le \ln~p(\mathbf Y\mid\boldsymbol\theta)
-	%\end{equation}
-
-%The EM algorithm alternates between maximizing the lower bound with respect to the distribution $q(\mathbf X)$ and the parameter set $\boldsymbol\theta$, respectively, while holding the other fixed.
-Suppose that the current estimate of the parameter set is $\boldsymbol\theta'$, in the E-step the lower bound is maximized with respect to the distribution $q(\mathbf X)$ while $\boldsymbol\theta'$ is fixed.
-Since the value of $p(\mathbf Y;\boldsymbol\theta')$ is independent of $q(\mathbf X)$ the maximum of the lower bound occurs when the KL distance disappears or in other words when $q(\mathbf X)$ is exactly the conditional distribution $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$.
-At this point, the lower bound becomes equal to the log-likelihood function.
-Note in the state-space model the E-step is equivalent to the smoothing problem.
-The maximum in the M-step is obtained by maximizing the lower bound with respect to the parameter set while the distribution $q(\mathbf X)$ is held fixed.
-Since the distribution $q(\mathbf X)$ is computed using the old parameter estimates and kept fixed during the M-step, it is not equal to $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta)$, resulting in a non-zero KL distance.
-Therefore, the growth of the log-likelihood function is greater than the growth of the lower bound.
-Substituting $p(\mathbf X \mid \mathbf Y;\boldsymbol\theta')$ for $q(\mathbf X)$ in Eq.~\eqref{eq:EM-decomposition1} gives
-%\begin{align}
- %\mathcal{L}(q,\boldsymbol\theta)&=\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)~d\mathbf X-\int_{\mathbf X} p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')\ln p(\mathbf X\mid\mathbf Y;\boldsymbol\theta')~d\mathbf X \nonumber \\
-%&= \mathbf E_{\boldsymbol\theta'}\left[ \ln p(\mathbf X,\mathbf Y;\boldsymbol\theta)\right] +\mathrm{const.}\nonumber\\
-%&=\mathcal{Q}(\boldsymbol\theta,\boldsymbol\theta')+\mathrm{const.}~,\label{eq:EM-ComDaLogLike}
-%\end{align}
-%where $ \mathbf E_{\boldsymbol \theta'}\left[ \cdot\right] $ denotes expectation taken with respect to the marginal distribution of the states conditioned on the observed field and the current estimate of the parameter set, i.e.
-$p(\mathbf X\mid\mathbf Y;\boldsymbol \theta'$).
-The constant term is independent of $\boldsymbol\theta$.
-It becomes clear from Eq.~\eqref{eq:EM-ComDaLogLike} that, the M-step essentially maximizes the expectation of the complete data log-likelihood.
 \section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}
@@
 An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by calculating the covariance matrix, $\mathbf P_t^b$ and following the above steps. 
-%\begin{equation}\label{eq:Xi1derivation1}
-% \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
-%\end{equation}
-%substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
-%\begin{equation}
- %\boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
-%\end{equation}
-\newpage
-\bibliographystyle{./elsarticle/model2-names}  
+\newpage
+% \bibliographystyle{./elsarticle/model2-names}  
+\bibliographystyle{model2-names} 
 \bibliography{MRAIDE}

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
added reviewers questions

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{soul}
\usepackage{anysize} %<-for setting margins
\marginsize {1.6cm}{1.6cm}{2.0cm}{2cm}
\usepackage{color}
\newcommand{\dean}[1]{\textcolor{red}{#1}}
\newcommand{\mike}[1]{\textcolor{green}{#1}}
\newcommand{\parham}[1]{\textcolor{blue}{#1}}

\title{Responses - Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
\author{ P. Aram, D. Freestone, M. Dewar, K. Scerri, V. Jirsa, D. Grayden, V. Kadirkamanathan}

\begin{document}
    \maketitle

    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper. Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript. 
\\

Best Regards,
\\

Parham Aram.

\section{Handling editor}
\begin{enumerate}
\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multiresolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.

\emph{Response here.}

\item  In addition, at least a `proof of principle" inversion from empirical data would enhance the potential impact of the paper.

\emph{Response here.}

\end{enumerate}

    \section{Reviewer 1}

    % It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.

    \begin{enumerate}
        \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in Neuroimage and IEEE Trans on Signal Processing  respectively.

	\emph{Response here.}

        \item The authors say the paper at hand is an ``extension'' of Freestone et al. by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.

	\emph{Response here.}

        \item Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.

	\emph{Response here.}

        \item Section 5 is a review of known results and standard background material from wavelet theory and includes a simple calculation of the Fourier transform of the particular basis used here, which would be more appropriate for an appendix (cf appendix H of the Freestone et al. paper where the Fourier transform of the Gaussian basis functions is calculated).

		\emph{Response here.}

        \item Section 6 also borrows heavily from Dewar et al, e.g. cf equation (58) of this paper with equation (19) of Dewar et al: the state transition matrix is a perturbation of the corresponding matrix used in that earlier paper. The approach used in both papers seems to be the same with an RTS smoother used in the E-step (this was also used and explained in Freestone et al.) and an M step optimizing a cost function, quadratic in the parameters, cf. equation (62) with  equation (29) of Theorem 2 of Dewar et al. In general, the derivations of section 6 and appendix B follow closely or are very similar to those of Dewar et al.

		\emph{Response here.}

        \item Also, Appendix A is the analogue of Appendix D of Freestone et al. and Appendix C includes results known from the literature (as the authors point out).

\emph{Response here.}

        \item Although I value the use of a wavelet as opposed to a Gaussian basis, the advantages in the context of the analysis of brain imaging data have not been demonstrated and a comparison with the authors' earlier approach has not been performed.  The framework of Freestone et al., seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.

\emph{Response here.}

        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behaviour are best explaine'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.

\emph{Response here.}

				\item Similar claims to the ones mentioned here regarding  implications for ``patient-specifi'' modelling have also been made in Freestone et al., so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.

				\emph{Response here.}

				\item The comments about model complexity and parsimony on p. 13 are somehow vague as these quantities are undefined.

				\emph{Response here.}

				\item Also, the comments on large scale networks and delays made on p.20 look irrelevant to the present framework.

				\emph{Response here.}

				\item much of the discussion of the last section focuses on technical issues, while the discussion of the observation kernel chosen on p.17 is limited.

				\emph{Response here.}

    \end{enumerate}

    \section{Reviewer 2}

\begin{enumerate}
    \item As a minor comment, I would suggest changing the notation for the scaling and wavelet coefficients in Eq. (6), for example into normal lowercase `a' and `c', respectively. The $\beta$ might be confused by B-spline notation.

	\emph{Response here.}

\item For the discussion, it might be useful to add a sentence that the basis structure (i.e., non-redundant, versus a (tight) frame representation) is a requirement for this framework.

\emph{Response here.}

\item A small comment might also be considered for Sect 8.2: it is possible to apply other than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands. For example, in 2D, the quincunx scheme is well-known to have better isotropic properties. Unfortunately, in 3D, it is not possible to have a subsampling operator (acting on a Cartesian sampling lattice) that is performing subsampling at equal rate in each dimension at each iteration, see Van De Ville et al,`On the multidimensional extension of the quincunx subsampling lattice', IEEE SPL, 12:2, pp.  112-115, 2005, for a comment on this.

\emph{Response here.}

 % 
 % \begin{figure*}[!ht]
 % \begin{center}
 % \includegraphics{./Graph/pdf/fig1.pdf} 
 % \end{center}
 % \caption{}
 % \label{fig:Figure1}
 % \end{figure*}

\end{enumerate}

    \section{Reviewer 3}  
    \subsection{Main Concerns}
		\begin{enumerate} 
			\item I am not at all sure that isotopic scaling of the multiresolution is appropriate for brain connections, but I cannot say at this point that it is not.

			\emph{Response here.}

			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.

			\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared. In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction. We plan to validate the framework on real data in future work. We have added that validating the framework on real data is required in the Conclusion.}

			\item This audience needs to have all symbols, including commonly used ones such as `equality over distribution', double font domains like R and Z, and jargon terms such as `lead field'.

			\emph{Response here.}

			\item I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.

			\emph{Response here.}

			\item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.

			\emph{Response here.}

			\item I would also recommend archiving code that, for instance generates figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.

 			\emph{Response here.}

			\end{enumerate}  
			\subsection{Moderate concerns} 
			\begin{enumerate} 
			 \item Page 2: the authors should clearly define the difference between neural field and neural mass models.

			\emph{Response here.}

			\item Eqn 3: theta needs indexing

			\emph{Response here.}

			\item Define first and second order synaptic responses (used in figure 2 to explain text that does not refer to these terms)

			\emph{Response here.}

			\item{Eqn 9: the state variables $x$ seem to arise without distinction from $v$}

			\emph{Response here.}

			\item Between eqn 19 and 20 change
			`write the neural field and connectivity kernel decomposition' To `write the connectivity kernel and neural field decomposition'
			To maintain order with eqns 20 and 21.

			\emph{Response here.}

			 \end{enumerate}  
			\subsection{Trivia}
			\begin{enumerate}
			 \item 	Define `one-off' on pg 16

 			\emph{Response here.}

  		\item Figure 8 is referred to in the text out of order

  			\emph{Response here.}

			\item Pg 19: `stationary point i.e. global' should be `stationary point, i.e. a global'

			\emph{Response here.}

				\end{enumerate}

\end{document}

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
edits to the resposnse

@@
 
-        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behaviour are best explaine'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.
+        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behaviour are best explained'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.
 
@@
 
-				\item Similar claims to the ones mentioned here regarding  implications for ``patient-specifi'' modelling have also been made in Freestone et al., so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
+				\item Similar claims to the ones mentioned here regarding  implications for ``patient-specific'' modelling have also been made in Freestone et al., so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
 
@@
 
-				\item The comments about model complexity and parsimony on p. 13 are somehow vague as these quantities are undefined.
+				\item The comments about model complexity and parsimony on p.13 are somehow vague as these quantities are undefined.
 
@@
 
-				\item much of the discussion of the last section focuses on technical issues, while the discussion of the observation kernel chosen on p.17 is limited.
+				\item Much of the discussion of the last section focuses on technical issues, while the discussion of the observation kernel chosen on p.17 is limited.
 

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
answer to R1,Q6

@@
 
-		\emph{Response here.}
+		\emph{As the reviewer correctly pointed out there are similarities in the derivations herein and that of Dewar et al.
+Our main aim here is to adopt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
+As the result some of the derivations are naturally similar.
+For example, the Amari type neural field model in this paper is only different to the IDE model in Dewar et al.
+due to the membrane time constant and the firing rate, as the result the only changes appear in the transition matrix is the presence of the membrane parameter $\xi=1-T_s/\tau$ and the firing rate slope $\varsigma$.
+The use of the RTS smoother in the E-step of the EM algorithm for state space models is an effective, standard and widely used approach.
+In fact, the aim of the IDE representation in a state space form is to adapt the EM and consequently the RTS smoother.
+The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) adapted in Freestone et al.
+The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
+as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
+This reduction is very significant and crucial for high dimensional systems and specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.
+}
 

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
edit to R1, Q5

@@
 		\emph{As the reviewer correctly pointed out there are similarities in the derivations herein and that of Dewar et al.
-Our main aim here is to adopt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
+Our main aim here is to adapt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
 As the result some of the derivations are naturally similar.
@@
 The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) adapted in Freestone et al.
+The cost function of the linear state space model is always quadratic in parameters in the M-step ???
+in fact it is one of the advantages of this representation which gives a closed form solution.
 The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
R1, Q5

@@
 In fact, the aim of the IDE representation in a state space form is to adapt the EM and consequently the RTS smoother.
-The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) adapted in Freestone et al.
+The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) in Freestone et al.
 The cost function of the linear state space model is always quadratic in parameters in the M-step ???
-in fact it is one of the advantages of this representation which gives a closed form solution.
+in fact it is one of the advantages of this representation giving a closed form solution for system's parameters.
 The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.

### 2012-07-26 Multiresolution_framework/ltx/response_to_reviews.tex
R1, Q6

@@
 due to the membrane time constant and the firing rate, as the result the only changes appear in the transition matrix is the presence of the membrane parameter $\xi=1-T_s/\tau$ and the firing rate slope $\varsigma$.
-The use of the RTS smoother in the E-step of the EM algorithm for state space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state space form is to adapt the EM and consequently the RTS smoother.
+The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
+In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother.
 The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) in Freestone et al.
-The cost function of the linear state space model is always quadratic in parameters in the M-step ???
-in fact it is one of the advantages of this representation giving a closed form solution for system's parameters.
+The cost function of a linear state-space model is always quadratic in parameters in the M-step ???
+in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters.
 The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
@@
 
-\emph{Response here.}
+\emph{In order to formulate the state-space representation of the multi-resolution neural field model the inner products of the B-spline functions are required.
+We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
+Appendix D of Freestone et al.
+and Appendix A here are only similar in the sense that the inner product of two basis functions are calculated.
+In Appendix D of Freestone et al.
+two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
+As for Appendix C we think that ...
+}
 

### 2012-07-27 Multiresolution_framework/ltx/response_to_reviews.tex
answers to 4.2.5, 4.3.3 and 4.3.4

@@
 In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother.
-The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state space models) in Freestone et al.
+The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state-space models) in Freestone et al.
 The cost function of a linear state-space model is always quadratic in parameters in the M-step ???
@@
 
-			\emph{Response here.}
+			\emph{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with eqns 20 and 21.}
 
@@
 
-  			\emph{Response here.}
+  			\emph{The cross-referencing has been corrected.}
 
@@
 
-			\emph{Response here.}
+			\emph{We have changed the text to `stationary point, i.e. a global'.}
 

### 2012-07-27 Multiresolution_framework/ltx/manuscript.tex
answers to 4.2.5, 4.3.3 and 4.3.4

@@
 \end{align}
-which allow us to write the neural field and connectivity kernel decomposition in the compact form of
+which allow us to write the connectivity kernel and neural field  decomposition in the compact form of
 \begin{align}
@@
 \end{equation}
-with $\theta_1=200$ and $\theta_2=-100$. This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
+with $\theta_1=200$ and $\theta_2=-100$. 
+% This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
 
@@
 
-Typically, a sequence of likelihood values will converge to a stationary point i.e.
-global (local) maximum or a saddle point.
+Typically, a sequence of likelihood values will converge to a stationary point, i.e.
+a global (local) maximum or a saddle point.
 If the sequence of the EM is trapped in a local maximum or a saddle point, a small random perturbation diverges the algorithm from such stationary values \citep{McLachlan1997}.

### 2012-07-27 Multiresolution_framework/ltx/response_to_reviews.tex
q3.1

@@
 
-\emph{In order to formulate the state-space representation of the multi-resolution neural field model the inner products of the B-spline functions are required.
+\emph{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required.
 We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C we think that ...
+As for Appendix C we think that it would be informative for the broad audience of NI to include the derivation of some of the well-known formulations in the EM algorithm.
 }
@@
 
-	\emph{Response here.}
+	\emph{We have changed the scaling and wavelet coefficients into normal lowercase `a' and `c', respectively.}
 

### 2012-07-27 Multiresolution_framework/ltx/manuscript.tex
q3.1

@@
 \begin{equation}
- w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
+ w\left(r\right)=\sum_{l\in \mathbb{Z}}a_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}c_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
 \label{eq:KernelExpansion}
 \end{equation}
-where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
+where $a_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $c_{j,l}$ are the detail coefficients at different scales $j$, with
 \begin{align}
@@
 	\boldsymbol\psi_{j}(r) \triangleq& \left\lbrace{\psi_{j,l}(r)}:l \in \mathbb{Z} \right\rbrace\\
-	\boldsymbol\alpha_{j_0} \triangleq& \left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace \\
-	\boldsymbol\beta_{j} \triangleq& \left\lbrace\beta_{j, l}:l \in \mathbb{Z} \right\rbrace \\
+	\mathbf{a}_{j_0} \triangleq& \left\lbrace a_{j_0, l}:l \in \mathbb{Z} \right\rbrace \\
+	\mathbf{c}_{j} \triangleq& \left\lbrace c_{j, l}:l \in \mathbb{Z} \right\rbrace \\
 	\mathbf{x}_{t,j_0} \triangleq& \left\lbrace{x}_{t,j_{0},l}:l \in \mathbb{Z} \right\rbrace \\
@@
 \begin{align}
-\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{j}^\top \end{array}] 
+\boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \mathbf{a}_{j_0}^\top & \mathbf{c}_{j_0}^\top & \mathbf{c}_{j_0+1}^\top & \cdots & \mathbf{c}_{j}^\top \end{array}] 
 \label{KernelWeights} \\
@@
 	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
-	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
+	$a_{j_0,l}, c_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
 	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 

### 2012-07-28 Multiresolution_framework/ltx/response_to_reviews.tex
response to R2

--- 2012-07-27 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 
-		\emph{As the reviewer correctly pointed out there are similarities in the derivations herein and that of Dewar et al.
+		\emph{\parham{As the reviewer correctly pointed out there are similarities in the derivations herein and that of Dewar et al.
 Our main aim here is to adapt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
@@
 as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
-This reduction is very significant and crucial for high dimensional systems and specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.
-}
+This reduction is very significant and crucial for high dimensional systems and specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.} }
 
@@
 
-\emph{In order to formulate the state-space representation of the multi-resolution neural field model the inner products of the B-spline functions are required.
+\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required.
 We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C we think that ...
-}
+As for Appendix C we think that it would be informative for the broad audience of NI to include the derivation of some of the well-known formulations in the EM algorithm.} }
 
@@
 
-	\emph{Response here.}
+	\emph{\parham{We have changed the scaling and wavelet coefficients into normal lowercase `a' and `c', respectively.}}
 
@@
 
-\emph{Response here.}
+\emph{\parham{We have added a sentence to Sect 8.1 (last paragraph) for the basis structure requirement.}}
 
@@
 
-\emph{Response here.}
+\emph{\parham{We have added this comment to Sect 8.2.}}
 
@@
 
-			\emph{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with eqns 20 and 21.}
+			\emph{\parham{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with eqns 20 and 21.}}
 
@@
 
-  			\emph{The cross-referencing has been corrected.}
+  			\emph{\parham{The cross-referencing has been corrected.}}
 
@@
 
-			\emph{We have changed the text to `stationary point, i.e. a global'.}
+			\emph{\parham{We have changed the text to `stationary point, i.e. a global'.}}
 

### 2012-07-28 Multiresolution_framework/ltx/manuscript.tex
response to R2

@@
 \usepackage{setspace} 
-% \usepackage[usenames,dvipsnames]{color}  
+ \usepackage[usenames,dvipsnames]{color}  
 %This bit is how to use hyperlink without  coloured rectangles around it
@@
  % \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
-% \newcommand{\dean}[1]{\textcolor{green}{#1}}
-% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+ \newcommand{\dean}[1]{\textcolor{green}{#1}}
+ \newcommand{\parham}[1]{\textcolor{blue}{#1}}
 % \newcommand{\vik}[1]{\textcolor{red}{#1}}
@@
 
-Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
+\parham{The basis structure (i.e., non-redundant, versus a (tight) frame representation) is a requirement for this framework.
+}Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
 This simplifies the computational complexity of the estimation algorithm significantly.
@@
 It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
+\parham{It is also possible to apply other than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands.
+For example, in 2D, the quincunx scheme is well-known to have better isotropic properties.
+Unfortunately, in 3D, it is not possible to have a subsampling operator (acting on a Cartesian sampling lattice) that is performing subsampling at equal rate in each dimension at each iteration \citep{VanDeVille2005a}.}
 \subsection{Extensions to the framework} 
@@
 \newpage
-% \bibliographystyle{./elsarticle/model2-names}  
-\bibliographystyle{model2-names} 
+ \bibliographystyle{./elsarticle/model2-names}  
+% \bibliographystyle{model2-names} 
 \bibliography{MRAIDE}

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
shifted the frequency response of the wavelet to appendix

@@
 \subsection{Frequency Analysis}\label{sec:freq_anal}
-To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}.
-To proceed the Fourier transform of $N_1(r)$ is first calculated,
-\begin{align}\label{eq:MRA-N1Fouriertransform}
-\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
-&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
+\parham{To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines})
+\begin{align}      
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu),\label{eq:MRA-Wavelettransform}
 \end{align}
 where $\nu$ is the spatial frequency and $i=\sqrt{-1}$.
-The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
-Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
-\begin{align}\label{eq:MRA-NmFouriertransform}
-\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
-\end{align}
-The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
-\begin{align}      
-	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
-	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
-\end{align}
 From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
-This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
+This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.}
 \section{State and Parameter Estimation}
@@
 \end{align} 
+\section{Fourier transform of B-spline wavelets}\label{ap:FourierofBsplines}
+To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
+\begin{align}\label{eq:MRA-N1Fouriertransform}
+\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
+&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
+\end{align}
+The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms.
+Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
+\begin{align}\label{eq:MRA-NmFouriertransform}
+\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
+\end{align}
+The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
+\begin{align}      
+	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
+	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{app:MRA-Wavelettransform}
+\end{align}
 \section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
minor edit to Appendix B
an attempt to describe the difference between neural field and mural mass models

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.
+} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 
@@
 \section{Fourier transform of B-spline wavelets}\label{ap:FourierofBsplines}
-To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
+\parham{To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
 \begin{align}\label{eq:MRA-N1Fouriertransform}
@@
 	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{app:MRA-Wavelettransform}
-\end{align}
+\end{align} }
 \section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
attempt to describe the difference between neural field and neural mass models

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.
 } It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
minor edit

--- 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
minor edit to difference between neural field and neural mass models

--- 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.
-} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 

### 2012-07-30 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit
q 4.2.1

@@
 Appendix D of Freestone et al.
-and Appendix A here are only similar in the sense that the inner product of two basis functions are calculated.
+and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated.
 In Appendix D of Freestone et al.
@@
 
-			\emph{Response here.}
+			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}
 

### 2012-07-30 Multiresolution_framework/ltx/manuscript.tex
4.2.3

@@
 The parameter $\theta$ can be thought of as the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describe excitation and inhibition, respectively.
-There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity.
-These are shown in Fig.~\ref{fig:Modelcomponents}.
+There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, \parham{leading to first and second order differential equations}.
+These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line).
+The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features}.
 Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.

### 2012-07-30 Multiresolution_framework/ltx/response_to_reviews.tex
4.2.3
4.2.2

@@
 
-			\emph{Response here.}
+			\emph{\parham{Authors think that the reviewer is after Eqn 2.
+for the correction.
+We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equation and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}
 
@@
 
-			\emph{Response here.}
+			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq.2.}}
 

### 2012-07-30 Multiresolution_framework/ltx/manuscript.tex
minor edit
4.2.2

@@
 	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
-	\theta\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
+	\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
 	\underbrace{f\left( v\left( \mathbf{r}',t'\right)\right)}_{\text{firing}}
@@
 The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
-The parameter $\theta$ can be thought of as the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describe excitation and inhibition, respectively.
 There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, \parham{leading to first and second order differential equations}.
 These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line).
-The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features}.
+The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features \cite{VanRotterdam1982}}.
 Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.
@@
 By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
-In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
+\parham{The connectivity kernel then can be written as a sum of weighted Gaussian or Laplacian functions where the weights can be thought of as the synaptic efficiency or coupling strength where positive and negative weights describe excitation and inhibition, respectively.} In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
 

### 2012-07-31 Multiresolution_framework/ltx/response_to_reviews.tex
some notes to the parsimony and complexity

@@
 The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother.
+In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
 The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state-space models) in Freestone et al.
@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C we think that it would be informative for the broad audience of NI to include the derivation of some of the well-known formulations in the EM algorithm.} }
+As for Appendix C we think that it would be informative for the broad audience of NeuroImage to include the derivation of some of the well-known formulations in the EM algorithm.} }
 
@@
 
-				\emph{Response here.}
+				\emph{\parham{some notes to be added to the manuscript: Parsimony: as few as necessary variables to describe a phenomenon, complexity: to add detail description to the model to increase its accuracy with the natural phenomenon, finding a balance between complexity and parsimony is crucial.
+By parsimony we sacrifice realism ...
+}}
 
@@
 
-			\item I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.
+			\item Frankly, I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.
 

### 2012-08-01 Multiresolution_framework/ltx/response_to_reviews.tex
edits to 2.5

@@
 The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
-as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
-This reduction is very significant and crucial for high dimensional systems and specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.} }
+as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
+Therefore only the dynamic elements are updated at each iteration  to calculate $\boldsymbol\Upsilon$.
+The same simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
+).
+These modifications are significant and crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.} }
 
@@
 			\end{enumerate}  
-			\subsection{Moderate concerns} 
+			\subsection{Moderate Concerns} 
 			\begin{enumerate} 

### 2012-08-01 Multiresolution_framework/ltx/manuscript.tex
edits to 2.5

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 

### 2012-08-01 Multiresolution_framework/ltx/response_to_reviews.tex
4.1.3

@@
 
-\item  In addition, at least a `proof of principle" inversion from empirical data would enhance the potential impact of the paper.
+\item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.
 
@@
 
-			\emph{Response here.}
+			\emph{\parham{The double font domains are added to Table.1.}}
 

### 2012-08-01 Multiresolution_framework/ltx/manuscript.tex
4.1.3

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of \parham{(these models instead neural fields models ??)} the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 
@@
 These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line).
-The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features \cite{VanRotterdam1982}}.
+The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSPs and IPSPs) features \cite{VanRotterdam1982}}.
 Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.
@@
 	$\Omega$ & Spatial domain & n.a.\\ 
+	$\mathbb{R}$&\parham{The et of all real numbers}&n.a.\\
+	$\mathbb{Z}$&\parham{The set of all integers}&n.a.\\
 	$\mathbf{r}$ & Spatial location & [mm, mm]\\

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex
description of lead field
minor edit
4.1.6

@@
 
-			\emph{\parham{The double font domains are added to Table.1.}}
+			\emph{\parham{The double font domains are added to Table.1. A brief description of `lead field' is also added below equation (5). *** equality over distribution should be added***}}
 
@@
 
- 			\emph{Response here.}
+ 			\emph{\parham{we have added footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
 

### 2012-08-04 Multiresolution_framework/ltx/manuscript.tex
description of lead field
reference for lead field
4.1.6

@@
 The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.
+\parham{The lead field parameters incorporate all the information about the head model, and must be accounted for inverse solutions when scalp electrodes are considered \cite{Jirsa2007}.}
 \section{MRA of the IDE in State-Space}
@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters \footnote{The Python source code for our numerical simulations is available from the authors on request.}.
 In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.

### 2012-08-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of \parham{(these models instead neural fields models ??)} the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of \parham{(these models instead of the neural fields models ??)} the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
 

### 2012-08-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters \footnote{The Python source code for our numerical simulations is available from the authors on request.}.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters \footnote{\parham{The Python source code for our numerical simulations is available from the authors on request.}}.
 In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

@@
 for the correction.
-We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equation and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}
+We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}
 

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

@@
 
-			\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
+			\emph{response here.}
+			% \emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
 However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C we think that it would be informative for the broad audience of NeuroImage to include the derivation of some of the well-known formulations in the EM algorithm.} }
+As for Appendix C we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of the well-known formulations in the EM algorithm.} }
 

### 2012-08-08 Multiresolution_framework/ltx/response_to_reviews.tex
A few general comments.

@@
 \newcommand{\parham}[1]{\textcolor{blue}{#1}}
+\newcommand{\ken}[1]{\textcolor{cyan}{#1}}
 
@@
 
-\emph{Response here.}
+\emph{\ken{Guys, I think the editor and reviewers 1 and 3 will be convinced by showing, just through an example, the added accuracy obtained by using the MRA over the Gaussian approximation.
+Is it possible to run such a comparison?
+Also, comparing with the results of our previous NI paper - can strengthen the argument that when operating in the linear region this approach can be superior.}}
 
@@
 
-\emph{Response here.}
+\emph{\ken{Guys - Not sure what the editor means by this - but I feel it would help to highlight further at the start of section 7 that the data is generated by another accepted model and not the model we are trying to estimate.
+Possibly - not using splines to obtain the mexican hat might make it even clearer.}}
 
@@
     % It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.
+
+\ken{Of interest I think is the last comment of Reviewer 1 giving his main concern - ``In summary, this manuscript appears quite technical and I am not convinced that it contains novel material of sufficient interest to the broad readership of Neuroimage." -  novelty over our previous papers seems essential - and I think a comparison of the results highlighting the improvement using MRA might do it - though of course - this might be time consuming to obtain.}
 

### 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
minor efit to table1
Rewording of parts of section 6 to address point 10 of the reply to review 1.

@@
  \newcommand{\parham}[1]{\textcolor{blue}{#1}}
-% \newcommand{\vik}[1]{\textcolor{red}{#1}}
+ \newcommand{\ken}[1]{\textcolor{red}{#1}}
 
@@
 
-To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+% To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
 Note that there is a difference between forward and inverse modeling when making these assumptions.
@@
 
-The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
+% The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
 The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
+
+\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
+A simpler, more parsimonious model might be unable to capture the full detail of the system behaviour but usually results in accurate and computationally efficient estimates.
+On the other hand, more complex and higher dimensional descriptions require computationally costly methods and less accurate estimates.}
+
+\ken{Thus, to demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
+This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates.
+As a result, any loss in model detail may be offset by the estimation accuracy.}
 
@@
 	$\Omega$ & Spatial domain & n.a.\\ 
-	$\mathbb{R}$&\parham{The et of all real numbers}&n.a.\\
+	$\mathbb{R}$&\parham{The set of all real numbers}&n.a.\\
 	$\mathbb{Z}$&\parham{The set of all integers}&n.a.\\

### 2012-08-10 Multiresolution_framework/ltx/response_to_reviews.tex
4.1.3-added i.i.d. definition under equation 5

@@
 
-			\emph{\parham{The double font domains are added to Table.1. A brief description of `lead field' is also added below equation (5). *** equality over distribution should be added***}}
+			\emph{\parham{ We have defined independent and identically distributed (i.i.d.) random variables under Eq.
+(5).
+The double font domains are added to Table.1.
+A brief description of `lead field' is also added below Eq.
+(5).}}
 

### 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
4.1.3-added i.i.d. definition under equation 5

@@
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d.
-Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
 The observation kernel models the pickup range of the electrical fields of the brain.

### 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
Some further changes in Section 6.

--- 2012-08-10 Multiresolution_framework/ltx/manuscript.tex
@@
 \ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
-A simpler, more parsimonious model might be unable to capture the full detail of the system behaviour but usually results in accurate and computationally efficient estimates.
-On the other hand, more complex and higher dimensional descriptions require computationally costly methods and less accurate estimates.}
-
-\ken{Thus, to demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; the simplest model capable of capturing the system behaviour of interest is chosen.
+Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}
+
+\ken{To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
 Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.

### 2012-08-10 Multiresolution_framework/ltx/response_to_reviews.tex
Some further changes in Section 6.
minor edit

@@
 
-				\emph{\parham{some notes to be added to the manuscript: Parsimony: as few as necessary variables to describe a phenomenon, complexity: to add detail description to the model to increase its accuracy with the natural phenomenon, finding a balance between complexity and parsimony is crucial.
+				% \emph{\parham{some notes to be added to the manuscript: Parsimony: as few as necessary variables to describe a phenomenon, complexity: to add detail description to the model to increase its accuracy with the natural phenomenon, finding a balance between complexity and parsimony is crucial.
 By parsimony we sacrifice realism ...
 }}
+
+				\emph{\ken{To clarify this comment, a short paragraph has been include in section 6 to highlight the modelling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.}}
 

### 2012-08-11 Multiresolution_framework/ltx/response_to_reviews.tex
response to 2.4

@@
 
-		\emph{Response here.}
+		\emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus'').
+We think that this brief review can help the interested readers to get familiar with the B-spline scaling and wavelet functions and direct them to the important literature on this matter.
+As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
 

### 2012-08-11 Multiresolution_framework/ltx/response_to_reviews.tex
edit to 1.5

@@
 Our main aim here is to adapt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
-As the result some of the derivations are naturally similar.
-For example, the Amari type neural field model in this paper is only different to the IDE model in Dewar et al.
-due to the membrane time constant and the firing rate, as the result the only changes appear in the transition matrix is the presence of the membrane parameter $\xi=1-T_s/\tau$ and the firing rate slope $\varsigma$.
+As the result some of the derivations are somehow similar, however, there are important changes in the framework highlighted as follows.
+The inverse framework in Dewar et al.
+is based on a general IDE model which is not suitable when electrophysiological data is considered.
+The inclusion of the membrane time constant and the firing rate in this work modify the general IDE equations to account for this type of data.
+As the result of these necessary modifications  the membrane parameter $\xi=1-T_s/\tau$ and the firing rate slope $\varsigma$ appear in the transition matrix.
+The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
+as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
+Therefore only the dynamic elements are updated at each iteration  to calculate $\boldsymbol\Upsilon$.
+The same simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).
+These modifications are significant and crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.
+The efficient M-step provided herein is also applicable in the framework of Freestone et al.
+if only the linear regime of the firing rate is considered.
 The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
@@
 The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state-space models) in Freestone et al.
-The cost function of a linear state-space model is always quadratic in parameters in the M-step ???
-in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters.
-The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
-as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
-Therefore only the dynamic elements are updated at each iteration  to calculate $\boldsymbol\Upsilon$.
-The same simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
-).
-These modifications are significant and crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.} }
+The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
 
@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of the well-known formulations in the EM algorithm.} }
+As for Appendix C, although authors have no objections to remove the presented derivations, we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of the well-known formulations in the EM algorithm.} }
 
@@
 
-				\emph{\ken{To clarify this comment, a short paragraph has been include in section 6 to highlight the modelling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.}}
+				\emph{\ken{To clarify this comment, a short paragraph has been included in section 6 to highlight the modeling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.}}
 

### 2012-08-11 Multiresolution_framework/ltx/manuscript.tex
1.11

@@
 However, delays must be accounted for in large scale networks.
-For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks (see \citet{Deco2010} for review).
-In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
+For instance, \citet{Ghosh2008} demonstrated that inclusion of time delays arising from propagation along connecting fibres are essential for the understanding of the fluctuations in resting state networks.
+Finally, future work should be directed towards applying and validating the framework on real data.
+
+% (see \citet{Deco2010} for review) In fact, \citet{Ghosh2008} emphasize that the couplings in large-scale brain networks have a space-time structure composed of their anatomical connectivity (space) and signal transmission delays (time).
 To capture correctly the constraints posed upon the network dynamics by connectivity, the space-time structure of the brain connectivity must be correctly estimated.
-Finally, future work should be directed towards applying and validating the framework on real data.
 \section{Acknowledgements}

### 2012-08-11 Multiresolution_framework/ltx/response_to_reviews.tex
1.11
broke down 1.7 into two

@@
         \item Although I value the use of a wavelet as opposed to a Gaussian basis, the advantages in the context of the analysis of brain imaging data have not been demonstrated and a comparison with the authors' earlier approach has not been performed.
-The framework of Freestone et al., seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.
+
+\emph{Response here.}
+
+				\item{The framework of Freestone et al., seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive. }
 
@@
 
-				\emph{Response here.}
+				\emph{\parham{In response to this point, we have omitted the last paragraph of the discussion on delays in large scale networks.}}
 

### 2012-08-12 Multiresolution_framework/ltx/response_to_reviews.tex
added a paragraph to Section 8.1

@@
 The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state-space models) in Freestone et al.
-The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
+The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.
+To clarify the advantage of the M-step over the implementation in Dewar et al.
+we have added a paragraph to Section 8.1.}}
 

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
added a paragraph to Section 8.1

@@
 \subsection{Estimation algorithm}
+\parham{The implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by \cite{Dewar2009} as it is shown in Table~\ref{table:MRA-ComputationalComplexity}, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
+This is crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced herein which otherwise would be possible.}
+
 For a larger space, or in a case where the connectivity kernel decomposition comprises of  many scale levels, the number of parameters to be estimated increases significantly.

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
added model reduction subsection to discussion

@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
+\parham{\subsection{Model reduction}
+Alternative basis functions can be used to reduce the neural field formulations, for example Gaussian basis functions are adopted by \cite{Freestone2011}.
+One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the neural field reconstruction at different spatial scales.
+B-spline scaling and wavelet functions are compactly supported, eliminating  numerical errors caused by the Gaussian basis function.
+The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model the neurological disorder such as seizure.
+}
+
 \subsection{Estimation algorithm}

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
7.1

--- 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
+\parham{\subsection{Model reduction}
+Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problem.
+An alternative is Gaussian basis functions  adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
+One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the neural field representation at different spatial scales.
+B-spline scaling and wavelet functions are compactly supported, eliminating  numerical errors caused by the Gaussian basis function.
+The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model neurological disorders such as epilepsy.
+Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.}
+
 \subsection{Estimation algorithm}

### 2012-08-12 Multiresolution_framework/ltx/response_to_reviews.tex
7.1
4.1.2

@@
 To clarify the advantage of the M-step over the implementation in Dewar et al.
-we have added a paragraph to Section 8.1.}}
+we have added a paragraph to Section 8.1}}
 
@@
 
-\emph{Response here.}
+\emph{\parham{To respond to this important comment we have added `model reduction' subsection into the discussion.}}
 
@@
 
-			\emph{response here.}
-			% \emph{The authors appreciate that the only way to truly validate the proposed framework is with real data.
+			 \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
 However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
-In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.
-We plan to validate the framework on real data in future work.
-We have added that validating the framework on real data is required in the Conclusion.}
+The title of the manuscript was chosen such that to reflect this fact, stating this a multi-resolution framework for Amari type neural field model.
+In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Result section.}}
 

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
4.1.2

@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters \footnote{\parham{The Python source code for our numerical simulations is available from the authors on request.}}.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically \parham{using Amari neural field model  (Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation})}, allowing a comparison between true and estimated parameters \footnote{\parham{The Python source code for our numerical simulations is available from the authors on request.}}.
 In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.

### 2012-08-12 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

@@
 		\emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus'').
-We think that this brief review can help the interested readers to get familiar with the B-spline scaling and wavelet functions and direct them to the important literature on this matter.
+We think that this brief review can familiarize interested readers  with  B-spline scaling and wavelet functions and direct them to the important literature on this matter.
 As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
@@
 
- 			\emph{\parham{we have added footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
+ 			\emph{\parham{we have added a footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
 

### 2012-08-12 Multiresolution_framework/ltx/response_to_reviews.tex
4.1.1

@@
 
-			\emph{Response here.}
+			\emph{\parham{It is generally accepted that the intracortical connectivity structure is isotropic, however, as the reviewer pointed out this is not the case  for corto-cortical connectivity.
+The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
+The connectivity kernel can take any arbitrary shapes but this requires more basis functions to accurately estimate the kernel.}}
 
@@
 However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
-The title of the manuscript was chosen such that to reflect this fact, stating this a multi-resolution framework for Amari type neural field model.
+The title of the manuscript was chosen such that to reflect this fact, stating this is a multi-resolution framework for Amari type neural field model.
 In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Result section.}}
@@
 
- 			\emph{\parham{we have added a footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
+ 			\emph{\parham{We have added a footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
 

### 2012-08-12 Multiresolution_framework/ltx/response_to_reviews.tex
small edits

@@
 
-\emph{\parham{We have added a sentence to Sect 8.1 (last paragraph) for the basis structure requirement.}}
+\emph{\parham{We have added a sentence to Sect 8.1 (now 8.2) for the basis structure requirement.}}
 
@@
 
-\emph{\parham{We have added this comment to Sect 8.2.}}
+\emph{\parham{We have added this comment to Sect 8.2 (now 8.3).}}
 

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 An alternative is Gaussian basis functions  adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
-One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the neural field representation at different spatial scales.
+One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the simultaneous representation of the neural field at different spatial scales.
 B-spline scaling and wavelet functions are compactly supported, eliminating  numerical errors caused by the Gaussian basis function.

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
mino edit to Ken comment

@@
 \ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
-Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; the simplest model capable of capturing the system behaviour of interest is chosen.
+Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; choosing the simplest model capable of capturing the system behavior of interest.
 Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
minor edit

@@
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
 The observation kernel models the pickup range of the electrical fields of the brain.

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
edits to response to editor 2

@@
 
+\dean{I think we should ignore this one. Otherwise, I have drafted a response.}
 \emph{\ken{Guys - Not sure what the editor means by this - but I feel it would help to highlight further at the start of section 7 that the data is generated by another accepted model and not the model we are trying to estimate.
 Possibly - not using splines to obtain the mexican hat might make it even clearer.}}
+
+The authors agree that the use of empirical data will strengthen the paper.
+Unfortunately, the authors do not have access to the appropriate data at present.
+However, we understand that several other groups are now collecting high spatiotemporal resolution data that is appropriate for the methods developed in this paper.
+We believe that the methods developed in this paper are equally important as the development of high spatiotemporal resolution recording techniques and together, these approaches have enormous potential to answer some of the biggest questions in neuroscience.
+The ability to use mathematical models as filters, or lenses into the brain if you like, is still a relatively new concept to many members in our community.
+This new lens allows us to image aspects of neurophysiology are normally hidden in electrical recording.
+Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience.
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
edits to response to reviewer 2 q1-3

@@
 
+\dean{Parham: Maybe you can make a list of key differences, highlighting the challenges, the technical details, and the benefits that the MRAIDE offers.}
+
 \item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.
@@
 
-The authors agree that the use of empirical data will strengthen the paper.
+\emph{The authors agree that the use of empirical data will strengthen the paper.
 Unfortunately, the authors do not have access to the appropriate data at present.
@@
 This new lens allows us to image aspects of neurophysiology are normally hidden in electrical recording.
-Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience.
+Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience.}
 
@@
 
-	\emph{Response here.}
+\dean{These first three things are the same point from Reviewer 1.}
+	\emph{The earlier papers (Freestone et al., 2011, Dewar et al., 2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
+Together with this paper, we are building tools that deal with increasing levels of complexity in the spatiotemporal dynamics.
+The first paper describes key work in the PhD thesis of Dewar.
+The second in the PhD thesis of Freestone.
+This paper covers the some of the key results from the PhD thesis of Aram.
+Each of these steps was a major undertaking and should not be under estimated.
+There is similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
+The challenges in forming a multiresolution state-space model ...
+}
 
@@
 As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
+
+\emph{\dean{We understand that this section will not be the central focus of the paper for the non-technical reader.
+This was the motivation for the comments in the section introduction, where we state...
+Although we appreciate R1 comments and suggestions, since R2 commented on the usefulness of this section we would very much like to leave it in.
+}}
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit to response to review

@@
 \dean{I think we should ignore this one. Otherwise, I have drafted a response.}
-\emph{\ken{Guys - Not sure what the editor means by this - but I feel it would help to highlight further at the start of section 7 that the data is generated by another accepted model and not the model we are trying to estimate.
-Possibly - not using splines to obtain the mexican hat might make it even clearer.}}
 
@@
     % It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.
-
-\ken{Of interest I think is the last comment of Reviewer 1 giving his main concern - ``In summary, this manuscript appears quite technical and I am not convinced that it contains novel material of sufficient interest to the broad readership of Neuroimage." -  novelty over our previous papers seems essential - and I think a comparison of the results highlighting the improvement using MRA might do it - though of course - this might be time consuming to obtain.}
 
@@
 
-		\emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus'').
+		% \emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus'').
 We think that this brief review can familiarize interested readers  with  B-spline scaling and wavelet functions and direct them to the important literature on this matter.
@@
 This was the motivation for the comments in the section introduction, where we state...
-Although we appreciate R1 comments and suggestions, since R2 commented on the usefulness of this section we would very much like to leave it in.
-}}
+Although we appreciate R1 comments and suggestions, since R2 commented on the usefulness of this section we would very much like to leave it in.} \parham{As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
drafting the choice of observation kernel

@@
 two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
-As for Appendix C, although authors have no objections to remove the presented derivations, we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of the well-known formulations in the EM algorithm.} }
+As for Appendix C, although authors have no objections to remove the presented derivations, we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of well-known formulations in the EM algorithm.} }
 

### 2012-08-14 Multiresolution_framework/ltx/manuscript.tex
correction to Table 1
drafting the choice of observation kernel

@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
-\parham{\subsection{Model reduction}
+\parham{\subsection{State-space representation}
 Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problem.
@@
 The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model neurological disorders such as epilepsy.
-Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.}
+Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.
+\cite{Freestone2011} showed experimentally that  Gaussian functions are suitable choice for modeling  observation kernel when intracranial measurements are considered.
+B-splines are also suitable for modeling observation kernel due to their close approximation to the Gaussian kernel.
+B-splines converge to the Gaussian function as the order of the B-spline $m$ tends to
+infinity.}
 
@@
    	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
-		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
+		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $a_{j_0,l}$ and $c_{j,l}$& mV.spike$^{-1}$\\ 
 		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\

### 2012-08-14 Multiresolution_framework/ltx/manuscript.tex
drafting the voice of observation kernel

--- 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
@@
 The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model neurological disorders such as epilepsy.
-Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.}
+Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.\\ \cite{Freestone2011} showed experimentally that Gaussian functions are suitable choice for modeling  observation kernel when intracranial measurements are considered.
+B-splines converge to Gaussian functions as the order of the B-spline, $m$, tends to infinity.
+The cubic B-spline is already very close approximation to the Gaussian function, therefore these are also suitable for modeling observation kernel while having the advantage of being compactly supported.}
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
response to 1.13
minor edit

@@
 
-\emph{\parham{To respond to this important comment we have added `model reduction' subsection into the discussion.}}
+\emph{\parham{To respond to this important comment we have added ``State-space representation'' subsection into the discussion.}}
 
@@
 
-				\emph{Response here.}
+				\emph{\parham{We have added a paragraph in new Section ``State-space representation'', regarding the choice of the observation kernel.}}
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
added an alternative respond to R1 q5, based on Parhams

@@
 
-\emph{\dean{We understand that this section will not be the central focus of the paper for the non-technical reader.
-This was the motivation for the comments in the section introduction, where we state...
-Although we appreciate R1 comments and suggestions, since R2 commented on the usefulness of this section we would very much like to leave it in.} \parham{As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
+\emph{\parham{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}}
+
+\emph{\dean{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}}
+
+\emph{\dean{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
+Interestingly, the feedback from the people with expertise in wavelet theory thought that the overview of the estimation methods was essential, but the section on wavelets should be reduced.
+Conversely, people with expertise in the estimation methods thought the overview on wavelets was critical and the section on EM-algorithm should be reduced.
+We completely appreciate R1 comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
+We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation from a wide audience.}}
 
@@
 cf equation (58) of this paper with equation (19) of Dewar et al: the state transition matrix is a perturbation of the corresponding matrix used in that earlier paper.
-The approach used in both papers seems to be the same with an RTS smoother used in the E-step (this was also used and explained in Freestone et al.) and an M step optimizing a cost function, quadratic in the parameters, cf.
+The approach used in both papers seems to be the same with an RTS smoother used in the E-step (this was also used and explained in Freestone et al.) and an M-step optimizing a cost function, quadratic in the parameters, cf.
 equation (62) with equation (29) of Theorem 2 of Dewar et al.
 In general, the derivations of section 6 and appendix B follow closely or are very similar to those of Dewar et al.
+
+		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. Further comments for the reviewer are added below.}}
+
+\emph{\dean{The inverse framework in Dewar et al.
+is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
+As the result the necessary modifications have been made.
+}}
+
+\emph{\dean{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al..
+These modifications are significant and crucial for high-dimensional systems.
+More specifically, implementing the multi-resolution framework introduced in the paper would be impossible without this new contribution.
+The differences are highlighted in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
+A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).} }
+
+\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
+In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
+The RTS algorithm is presented only for completeness.} }
 
@@
 In Appendix D of Freestone et al.
-two  n-dimensional Gaussians are considered while here the inner product of two B-spline functions is calculated.
+two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
 As for Appendix C, although authors have no objections to remove the presented derivations, we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of well-known formulations in the EM algorithm.} }
@@
 
-				\emph{Response here.}
+\emph{\dean{this boils down to a trade-off between temporal accuracy and spatial accuracy.
+the contributions of formulating a MRA neural field model still hold.
+Also, the contribution in the M-step simplification still holds.
+Nonlinear estimation are limited due to computational demands....
+}.}
 

### 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
merged three first questions of R1

@@
         \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in Neuroimage and IEEE Trans on Signal Processing  respectively.
-
-	\emph{Response here.}
-
-        \item The authors say the paper at hand is an ``extension'' of Freestone et al. by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
-
-	\emph{Response here.}
-
-        \item Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
+The authors say the paper at hand is an ``extension'' of Freestone et al.
+by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
+Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
 

### 2012-08-15 Multiresolution_framework/ltx/response_to_reviews.tex
separate three first questions of R1
minor edit to letter

@@
 The ability to use mathematical models as filters, or lenses into the brain if you like, is still a relatively new concept to many members in our community.
-This new lens allows us to image aspects of neurophysiology are normally hidden in electrical recording.
-Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience.}
+This new lens allows us to image aspects of neurophysiology are normally hidden in electrical recordings.
+Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will be standard methods.}
 

### 2012-08-15 Multiresolution_framework/ltx/response_to_reviews.tex

--- 2012-08-14 Multiresolution_framework/ltx/response_to_reviews.tex
@@
         \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in Neuroimage and IEEE Trans on Signal Processing  respectively.
-
-	\emph{Response here.}
-
 				\item The authors say the paper at hand is an ``extension'' of Freestone et al. by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
-
 				\emph{Response here.}

### 2012-08-15 Multiresolution_framework/ltx/response_to_reviews.tex
edits to the responses to reviewer 2 in the letter

@@
 The ability to use mathematical models as filters, or lenses into the brain if you like, is still a relatively new concept to many members in our community.
-This new lens allows us to image aspects of neurophysiology are normally hidden in electrical recordings.
-Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will be standard methods.}
+This new lens allows us to image aspects of neurophysiology of individual subjects that are normally hidden in electrical recordings.
+Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will become standard methods.
+Furthermore, we believe that (good) experimental design is based around the availability of analysis tools.
+Therefore new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
+}
 
@@
 two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
-As for Appendix C, although authors have no objections to remove the presented derivations, we think that it would be informative for the broad audience of NeuroImage to include the derivations of some of well-known formulations in the EM algorithm.} }
+The authors have no objections to remove Appendix C.
+However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
 
@@
 
-\emph{\dean{this boils down to a trade-off between temporal accuracy and spatial accuracy.
-the contributions of formulating a MRA neural field model still hold.
-Also, the contribution in the M-step simplification still holds.
-Nonlinear estimation are limited due to computational demands....
-}.}
+\emph{\dean{The linear activation function in the estimation algorithm was made out of necessity.
+This was due to the high dimensionality and associated computational demands of the estimation problem.}}
+
+\emph{\dean{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
+This derivation is perhaps the most important contribution of the paper.
+We understand that all physical systems are nonlinear.
+However, we also understand that linear approximations are often required in engineering for useful models.
+In the introduction to the estimation section, we have attempted to discuss this issue with regard to forward vs.
+inverse modelling.
+We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
+For example, in a forward model the nonlinearity is required to prevent negative firing rates.
+However in the inverse case, the physiology naturally restricts firing rates to be positive.
+Furthermore, in the mean field case, we do not expect firing rates of all neurons to be zero or all neurons to be simultaneously firing at their maximal rate.
+Therefore, a linear model may suffice to image a multi-resolution neural field and physiological parameters using electrophysiological data .}}
+
+\emph{\dean{Given restrictions of computational complexity, the choice of whether to use the framework presented in Freestone et al.
+or the current paper may boil down to a trade-off between temporal accuracy and spatial accuracy.
+Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
+This is due to the correction step in the algorithm where model error is reduced using measurements.
+}}
 
@@
 
-\emph{Response here.}
+\dean{\emph{Within our framework the alternate levels are defined by the spatial scales of the wavelet decomposition.
+The significant result is the formulation of a model when various spatial scales of a neural field can be simultaneously represented.
+The ability to image the multi-dimensional neural field will lead to a better understanding of the important spatial scales when neural information processing occurs.
+}}
 
@@
 
-				\emph{Response here.}
+				\dean{\emph{Please refer to Response 2 to the handling editor.}}
 

### 2012-08-15 Multiresolution_framework/ltx/response_to_reviews.tex
edit to 2.5

@@
 
-		\emph{\parham{As the reviewer correctly pointed out there are similarities in the derivations herein and that of Dewar et al.
-Our main aim here is to adapt techniques from control systems theory and machine learning, modify and apply them to the Amari type neural field models.
-As the result some of the derivations are somehow similar, however, there are important changes in the framework highlighted as follows.
-The inverse framework in Dewar et al.
-is based on a general IDE model which is not suitable when electrophysiological data is considered.
-The inclusion of the membrane time constant and the firing rate in this work modify the general IDE equations to account for this type of data.
-As the result of these necessary modifications  the membrane parameter $\xi=1-T_s/\tau$ and the firing rate slope $\varsigma$ appear in the transition matrix.
-The novel implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by Dewar et al.
-as it is shown in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
-Therefore only the dynamic elements are updated at each iteration  to calculate $\boldsymbol\Upsilon$.
-The same simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).
-These modifications are significant and crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced here which otherwise would be possible.
-The efficient M-step provided herein is also applicable in the framework of Freestone et al.
-if only the linear regime of the firing rate is considered.
-The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
-The RTS algorithm is presented only for completeness and it is different than Unscented RTS (for non-linear state-space models) in Freestone et al.
-The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.
-To clarify the advantage of the M-step over the implementation in Dewar et al.
-we have added a paragraph to Section 8.1}}
+		\emph{\parham{The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
 

### 2012-08-15 Multiresolution_framework/ltx/response_to_reviews.tex
handling editor: Q1

@@
 
-\emph{\ken{Guys, I think the editor and reviewers 1 and 3 will be convinced by showing, just through an example, the added accuracy obtained by using the MRA over the Gaussian approximation.
-Is it possible to run such a comparison?
-Also, comparing with the results of our previous NI paper - can strengthen the argument that when operating in the linear region this approach can be superior.}}
+\emph{\parham{The first paragraph of the newly added ``State-space representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
+We also added a paragraph to `` Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al..
+Please refer to Response 5 to the reviewer 1 for more details.}}
 
@@
 
-		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. Further comments for the reviewer are added below.}}
+		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. (now 8.2) Further comments for the reviewer are added below.}}
 

### 2012-08-16 Multiresolution_framework/ltx/response_to_reviews.tex
edits to the responses to reviewer 2 in the letter

@@
 Together with this paper, we are building tools that deal with increasing levels of complexity in the spatiotemporal dynamics.
-The first paper describes key work in the PhD thesis of Dewar.
-The second in the PhD thesis of Freestone.
-This paper covers the some of the key results from the PhD thesis of Aram.
+The first paper describes key work in the PhD thesis of Dewar, which introduces what we now call a dynamic Galerkin projection.
+The second in the PhD thesis of Freestone, which recast the estimation problem in the context of neural fields.
+This paper covers the some of the key results from the PhD thesis of Aram, which details methods for achieving a more accurate representation of the neural fields and an elegant estimation scheme.
 Each of these steps was a major undertaking and should not be under estimated.
 There is similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
-The challenges in forming a multiresolution state-space model ...
-}
+The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
+Through our previous work we have demonstrated that we are experts in this area and we can assure you that this paper is a result of a concerted effort from our team over a time period of more then 3 years.
+The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}
 
@@
 We completely appreciate R1 comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
-We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation from a wide audience.}}
+We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}}
 

### 2012-08-16 Multiresolution_framework/ltx/response_to_reviews.tex
merged three first questions of R1

@@
         \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in Neuroimage and IEEE Trans on Signal Processing  respectively.
-				\item The authors say the paper at hand is an ``extension'' of Freestone et al. by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
-				\emph{Response here.}
-
-				\item Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
+The authors say the paper at hand is an ``extension'' of Freestone et al.
+by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
+Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
 

### 2012-08-17 Multiresolution_framework/ltx/response_to_reviews.tex
edits to the responses to reviewer 2 in the letter

--- 2012-08-16 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
-Through our previous work we have demonstrated that we are experts in this area and we can assure you that this paper is a result of a concerted effort from our team over a time period of more then 3 years.
+This paper is a result of a concerted effort from our team over a time period of more then one years work.
 The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}
@@
 
-		\emph{\parham{The cost function of a linear state-space model with separable parameters is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
+		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
 
@@
 
-			\emph{Response here.}
+			\emph{The units of $x$ are also Volts. However the states are weights for particular levels of resolution, where $v$ is the total net field. We have added a sentence to add clarification.}
 

### 2012-08-18 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit to q1 of handling editor
added some comments to Dean responses

@@
 We also added a paragraph to `` Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al..
-Please refer to Response 5 to the reviewer 1 for more details.}}
+Please refer to Responses 1 and 5 to R1 for more details.}}
 
@@
 
-		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
+		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
 
@@
 \emph{\dean{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
-This derivation is perhaps the most important contribution of the paper.
+This derivation is perhaps the most important contribution of the paper \parham{not sure about this because we have already done the derivation in Freestone 2011}.
 We understand that all physical systems are nonlinear.
@@
 Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
-This is due to the correction step in the algorithm where model error is reduced using measurements.
-}}
+This is due to the correction step in the algorithm where model error is reduced using measurements.\parham{not sure this is due to the correction step, the correction step of this paper and Freestone 2011 are the same due to the linearity of the observation equation.}}}
 

### 2012-08-18 Multiresolution_framework/ltx/response_to_reviews.tex
comment on 4.2.4
changed one year to two in q2.1

@@
 The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
-This paper is a result of a concerted effort from our team over a time period of more then one years work.
+This paper is a result of a concerted effort from our team over a time period of more then two years work.
 The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}
@@
 
-			\emph{The units of $x$ are also Volts. However the states are weights for particular levels of resolution, where $v$ is the total net field. We have added a sentence to add clarification.}
+			\emph{The units of $x$ are also Volts.
+However the states are weights for particular levels of resolution, where $v$ is the total net field.
+We have added a sentence to add clarification.
+\parham{please dont forget to add this to manuscript}}
 

### 2012-08-18 Multiresolution_framework/ltx/manuscript.tex
added a sentence to result section to highlight the importance of the second experiment
minor edit to result section
Added reference and minor changes to model choice argument

@@
 \ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
-Such a choice is usually based on the principle of parsimony \cite{Illfindit}, that is; choosing the simplest model capable of capturing the system behavior of interest.
+Such a choice is usually based on the principle of parsimony \cite{burnham2002}, that is; choosing the simplest model capable of capturing the system behavior of interest.
 Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}
@@
 This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates.
-As a result, any loss in model detail may be offset by the estimation accuracy.}
+Consequently, any loss in model detail may be offset by the estimation accuracy.}
 
@@
 $j=0$ to $j=4$.
-All parameters for the model are given in Table~\ref{tab:Parameters}.
+\parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.
 

### 2012-08-18 Multiresolution_framework/ltx/response_to_reviews.tex
Minor change to response 9 to R1 highlighting the addition of a reference for further information.

@@
 
-				\emph{\ken{To clarify this comment, a short paragraph has been included in section 6 to highlight the modeling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.}}
+				\emph{\ken{To clarify this comment, a short paragraph has been included in section 6 to better explain the modeling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.
+For the audience with less experience in system identification, a reference with further information regarding this topic has also been included.}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
edits to the responses to reviewer 2 in the letter

--- 2012-08-18 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 We also added a paragraph to `` Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al..
-Please refer to Responses 1 and 5 to R1 for more details.}}
+Please refer to Response 5 to the reviewer 1 for more details.}}
 
@@
 
-\emph{The authors agree that the use of empirical data will strengthen the paper.
+\dean{\emph{The authors agree that the use of empirical data will strengthen the paper.
 Unfortunately, the authors do not have access to the appropriate data at present.
@@
 Therefore new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
-}
+} }
 
@@
 \dean{These first three things are the same point from Reviewer 1.}
-	\emph{The earlier papers (Freestone et al., 2011, Dewar et al., 2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
+
+	\dean{\emph{The earlier papers (Freestone et al., 2011, Dewar et al., 2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
 Together with this paper, we are building tools that deal with increasing levels of complexity in the spatiotemporal dynamics.
@@
 This paper is a result of a concerted effort from our team over a time period of more then one years work.
-The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}
+The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}}
 
@@
 
-		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
+		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to minimum least squares error.}}
 
@@
 \emph{\dean{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
-This derivation is perhaps the most important contribution of the paper \parham{not sure about this because we have already done the derivation in Freestone 2011}.
+This derivation is perhaps the most important contribution of the paper.
 We understand that all physical systems are nonlinear.
@@
 Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
-This is due to the correction step in the algorithm where model error is reduced using measurements.\parham{not sure this is due to the correction step, the correction step of this paper and Freestone 2011 are the same due to the linearity of the observation equation.}}}
+This is due to the correction step in the algorithm where model error is reduced using measurements.
+}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

--- 2012-08-18 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
-The connectivity kernel can take any arbitrary shapes but this requires more basis functions to accurately estimate the kernel.}}
+The connectivity kernel can take any arbitrary shapes but this may require more basis functions to accurately estimate the kernel.}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
edits to R1 Q5

@@
 The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
-This paper is a result of a concerted effort from our team over a time period of more then two years work.
+This paper is a result of a concerted effort from our team over a time period of more than two years work.
 The progress we have made with the earlier papers has made this paper possible, just as we hope that this paper will inspire future work in this direction.}
@@
 
-		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. (now 8.2) Further comments for the reviewer are added below.}}
+		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}}
 
@@
 
-\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
+\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
 In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
@@
 
-		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
+		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically where the parameters are separable.
+In fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
comment on R1 Q6

@@
 inverse modelling.
-We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
-For example, in a forward model the nonlinearity is required to prevent negative firing rates.
+\parham{We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
+??} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
 However in the inverse case, the physiology naturally restricts firing rates to be positive.

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
R1 Q10
minor edit to R1 Q11

@@
 
-				\emph{\parham{In response to this point, we have omitted the last paragraph of the discussion on delays in large scale networks.}}
+				\emph{\parham{We have omitted the last paragraph of the discussion on delays in large scale networks.}}
 
@@
 
-				\emph{\parham{We have added a paragraph in new Section ``State-space representation'', regarding the choice of the observation kernel.}}
+				\emph{\parham{We have added a paragraph in new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
Minor changes to R1 Q3

--- 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
-As the result the necessary modifications have been made.
+As the result the necessary additions have been made.
 }}
@@
 \emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
-The RTS algorithm is presented only for completeness.} }
+In fact, the aim of the IDE representation in a state-space form is to adopt the EM and consequently the RTS smoother in the E-step.
+The RTS algorithm is presented for completeness to the interested readers.} }
 
-		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically where the parameters are separable.
-In fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
+		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically when the parameters are separable giving results equivalent to the least square estimates.
+In fact this is one of the advantages of this representation, such a closed form solution for the system's parameters results in significant computational savings.}}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
edit to 4.1.2
minor edit

@@
 \item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.
-
-\dean{I think we should ignore this one. Otherwise, I have drafted a response.}
 
@@
 
+			 \emph{\parham{Please refer to Response 2 to the handling editor. Further comments are also added below.}}
+
 			 \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
@@
 
-			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq.2.}}
+			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq 2.}}
 

### 2012-08-21 Multiresolution_framework/ltx/manuscript.tex
Minor changes to section 8.1

@@
 \parham{\subsection{State-space representation}
-Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problem.
-An alternative is Gaussian basis functions  adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
+Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problems.
+An alternative is given by the Gaussian basis functions adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
 One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the simultaneous representation of the neural field at different spatial scales.
@@
 The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model neurological disorders such as epilepsy.
-Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states will be increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.\\ \cite{Freestone2011} showed experimentally that Gaussian functions are suitable choice for modeling  observation kernel when intracranial measurements are considered.
+Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states is increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.\\ \cite{Freestone2011} showed experimentally that Gaussian functions are a suitable choice for modeling the observation kernel when intracranial measurements are considered.
 B-splines converge to Gaussian functions as the order of the B-spline, $m$, tends to infinity.
-The cubic B-spline is already very close approximation to the Gaussian function, therefore these are also suitable for modeling observation kernel while having the advantage of being compactly supported.}
+The cubic B-spline is already a very close approximation to the Gaussian function, therefore these should also be suitable for modeling the observation kernel while having the advantage of being compactly supported.}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
got rid of the color for some of the answers

@@
 
-\dean{Parham: Maybe you can make a list of key differences, highlighting the challenges, the technical details, and the benefits that the MRAIDE offers.}
-
 \item  In addition, at least a ``proof of principle" inversion from empirical data would enhance the potential impact of the paper.
 
-\dean{\emph{The authors agree that the use of empirical data will strengthen the paper.
+\emph{The authors agree that the use of empirical data will strengthen the paper.
 Unfortunately, the authors do not have access to the appropriate data at present.
@@
 This new lens allows us to image aspects of neurophysiology of individual subjects that are normally hidden in electrical recordings.
-Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will become standard methods.
+Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modeling, experimental measures and model-data fusion will become standard methods.
 Furthermore, we believe that (good) experimental design is based around the availability of analysis tools.
-Therefore new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
-} }
+Therefore new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.}
 
@@
 
-\dean{These first three things are the same point from Reviewer 1.}
  \emph{The earlier papers (Freestone et al., 2011, Dewar et al., 2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
@@
 
-\emph{\parham{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}}
+\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}
 
-\emph{\dean{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}}
+\emph{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}
 
-\emph{\dean{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
+\emph{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
 Interestingly, the feedback from the people with expertise in wavelet theory thought that the overview of the estimation methods was essential, but the section on wavelets should be reduced.
@@
 We completely appreciate R1 comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
-We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}}
+We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}
 
@@
 
-		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}}
+		\emph{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}
 
-\emph{\dean{The inverse framework in Dewar et al.
+\emph{The inverse framework in Dewar et al.
 is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
-As the result the necessary additions have been made.
-}}
+As the result the necessary additions have been made.}
 
-\emph{\dean{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al..
+\emph{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al..
 These modifications are significant and crucial for high-dimensional systems.
@@
 The differences are highlighted in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
-A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).} }
+A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).
+}
 
-\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
+\emph{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
 In fact, the aim of the IDE representation in a state-space form is to adopt the EM and consequently the RTS smoother in the E-step.
-The RTS algorithm is presented for completeness to the interested readers.} }
+The RTS algorithm is presented for completeness to interested readers.}
 

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit

@@
 
-\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required.
+\emph{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required.
 We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
@@
 The authors have no objections to remove Appendix C.
-However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
+However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.}
 
@@
 inverse modelling.
-\parham{We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
-??} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
+\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
 However in the inverse case, the physiology naturally restricts firing rates to be positive.

### 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
minor edits

@@
 
-				\emph{\parham{We have added a paragraph in new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
+				\emph{\parham{We have added a paragraph in the new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
 
@@
 
+			% \emph{\parham{To respond to this comment we have added ``State-space representation'' subsection into the discussion.}}
+
 			\item I would also recommend archiving code that, for instance generates figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
edits to letter from David

--- 2012-08-21 Multiresolution_framework/ltx/response_to_reviews.tex
@@
 \title{Responses - Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}
-\author{ P. Aram, D. Freestone, M. Dewar, K. Scerri, V. Jirsa, D. Grayden, V. Kadirkamanathan}
+\author{ P. Aram, D. R. Freestone, M. Dewar, K. Scerri, V. Jirsa, D. B. Grayden, V. Kadirkamanathan}
 
@@
 
-    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper.
-Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript.
+    We thank the reviewers for their encouraging comments and their contribution to improving this paper.
+Please find below our responses to the reviewers questions and suggestions regarding the manuscript.
 \\
@@
 \emph{\parham{The first paragraph of the newly added ``State-space representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
-We also added a paragraph to `` Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al..
+We also added a paragraph to ``Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al.
+(2009).
 Please refer to Responses 1 and 5 to R1 for more details.}}
@@
 
-\emph{The authors agree that the use of empirical data will strengthen the paper.
-Unfortunately, the authors do not have access to the appropriate data at present.
-However, we understand that several other groups are now collecting high spatiotemporal resolution data that is appropriate for the methods developed in this paper.
-We believe that the methods developed in this paper are equally important as the development of high spatiotemporal resolution recording techniques and together, these approaches have enormous potential to answer some of the biggest questions in neuroscience.
-The ability to use mathematical models as filters, or lenses into the brain if you like, is still a relatively new concept to many members in our community.
+\dean{\emph{We agree that the use of empirical data will strengthen the paper.
+Unfortunately, we do not have access to the appropriate data at present.
+However, we understand that several other groups are now collecting high resolution data that is appropriate for the methods developed in this paper.
+We believe that the methods developed in this paper are equally important as the development of high  resolution spatiotemporal recording techniques and together, these approaches have enormous potential to answer some of the biggest questions in neuroscience.
+The ability to use mathematical models as filters, or lenses into the brain, is still a relatively new concept to many members of our community.
 This new lens allows us to image aspects of neurophysiology of individual subjects that are normally hidden in electrical recordings.
-Therefore, we believe it is important to continue improve our methods that will lead to the next era in systems neuroscience, where mathematical modeling, experimental measures and model-data fusion will become standard methods.
-Furthermore, we believe that (good) experimental design is based around the availability of analysis tools.
-Therefore new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.}
+Therefore, we believe it is important to continue to improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will become standard methods.
+Furthermore, we believe that (good) experimental design is based upon the availability of analysis tools.
+Therefore, new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
+} }
 
@@
 
- \emph{The earlier papers (Freestone et al., 2011, Dewar et al., 2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
+	\emph{Freestone et al.
+(2011), Dewar et al.
+(2009) both propose solutions to representing a spatiotemporal field with a finite number of basis functions.
 Together with this paper, we are building tools that deal with increasing levels of complexity in the spatiotemporal dynamics.
@@
 The second in the PhD thesis of Freestone, which recast the estimation problem in the context of neural fields.
-This paper covers the some of the key results from the PhD thesis of Aram, which details methods for achieving a more accurate representation of the neural fields and an elegant estimation scheme.
-Each of these steps was a major undertaking and should not be under estimated.
-There is similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
+This paper covers some of the key results from the PhD thesis of Aram, which details methods for achieving a more accurate representation of the neural fields and an elegant estimation scheme.
+Each of these steps was a major undertaking and should not be underestimated.
+There are similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
 The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
@@
 
-\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}
+\emph{\parham{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}}
 
-\emph{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}
+\emph{\dean{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}}
 
-\emph{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
+\emph{\dean{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
 Interestingly, the feedback from the people with expertise in wavelet theory thought that the overview of the estimation methods was essential, but the section on wavelets should be reduced.
 Conversely, people with expertise in the estimation methods thought the overview on wavelets was critical and the section on EM-algorithm should be reduced.
-We completely appreciate R1 comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
-We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}
+We completely appreciate R1's comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
+We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}}
 
@@
 
-		\emph{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}
+		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. (now 8.2) Further comments for the reviewer are added below.}}
 
-\emph{The inverse framework in Dewar et al.
-is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
-As the result the necessary additions have been made.}
+\emph{\dean{The inverse framework in Dewar et al.
+(2009) is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
+As a result, the necessary modifications have been made.
+}}
 
-\emph{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al..
+\emph{\dean{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al.
+(2009).
 These modifications are significant and crucial for high-dimensional systems.
 More specifically, implementing the multi-resolution framework introduced in the paper would be impossible without this new contribution.
-The differences are highlighted in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al, where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
-A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.).
-}
+The differences are highlighted in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al.
+(2009), where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
+A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
+(2009)).} }
 
-\emph{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state-space form is to adopt the EM and consequently the RTS smoother in the E-step.
-The RTS algorithm is presented for completeness to interested readers.}
+\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
+In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
+The RTS algorithm is presented only for completeness.} }
 
-		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically when the parameters are separable giving results equivalent to the least square estimates.
-In fact this is one of the advantages of this representation, such a closed form solution for the system's parameters results in significant computational savings.}}
+		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
 
@@
 
-\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model the inner product of the B-spline functions are required.
+\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model, the inner product of the B-spline functions are required.
 We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
 Appendix D of Freestone et al.
-and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated.
-In Appendix D of Freestone et al.
-two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
-The authors have no objections to remove Appendix C.
-However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
+(2009) and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated.
+In Appendix D of Freestone et al., two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
+We have no objections to removing Appendix C.
+However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
 
@@
 inverse modelling.
-\parham{We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
-??} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
+We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
+For example, in a forward model the nonlinearity is required to prevent negative firing rates.
 However in the inverse case, the physiology naturally restricts firing rates to be positive.
@@
 
-				\emph{\parham{We have omitted the last paragraph of the discussion on delays in large scale networks.}}
+				\emph{\parham{In response to this point, we have omitted the last paragraph of the discussion on delays in large scale networks.}}
 
@@
 
-				\emph{\parham{We have added a paragraph in new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
+				\emph{\parham{We have added a paragraph in new Section ``State-space representation'', regarding the choice of the observation kernel.}}
 
@@
 The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
-The connectivity kernel can take any arbitrary shapes but this may require more basis functions to accurately estimate the kernel.}}
+The connectivity kernel can take any arbitrary shapes but this requires more basis functions to accurately estimate the kernel.}}
 
 			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.
-
-			 \emph{\parham{Please refer to Response 2 to the handling editor. Further comments are also added below.}}
 
@@
 
-			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq 2.}}
+			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq.2.}}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex

@@
 
-\emph{\parham{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}}
+\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}
 
-\emph{\dean{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}}
+\emph{We understand that this section will not be the central focus of the paper for some members of our research community, however we believe that it is important that this information remains in the paper to allow for implementation without the requirement of digesting information from several texts.}
 
@@
 
-		\emph{\dean{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1. (now 8.2) Further comments for the reviewer are added below.}}
+		\emph{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}
 
@@
 
-\emph{\dean{The use of the RTS smoother in the E-step of the EM algorithm for state-space models is an effective, standard and widely used approach.
-In fact, the aim of the IDE representation in a state-space form is to adapt the EM and consequently the RTS smoother in the E-step.
-The RTS algorithm is presented only for completeness.} }
+\emph{The use of the RTS smoother in the E-step of the EM algorithm for linear state-space models is an effective, standard and widely used approach.
+In fact, the aim of the IDE representation in a state-space form is to adopt the EM and consequently the RTS smoother in the E-step.
+The RTS algorithm is presented for completeness to interested readers.}
 
-		\emph{\parham{The cost function of a linear state-space model with separable parameters (linear w.r.t states) is always quadratic in parameters in the M-step and, in fact it is one of the advantages of this representation, giving a closed form solution for system's parameters which is essentially equivalent to least squares.}}
+		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically when the parameters are separable giving results equivalent to the least square estimates.
+In fact this is one of the advantages of this representation, such a closed form solution for the system's parameters results in significant computational savings.}}
 
@@
 inverse modelling.
-We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.
-For example, in a forward model the nonlinearity is required to prevent negative firing rates.
+\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
 However in the inverse case, the physiology naturally restricts firing rates to be positive.
@@
 
-				\emph{\parham{We have added a paragraph in new Section ``State-space representation'', regarding the choice of the observation kernel.}}
+				\emph{\parham{We have added a paragraph in the new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
 
@@
 The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
-The connectivity kernel can take any arbitrary shapes but this requires more basis functions to accurately estimate the kernel.}}
+The connectivity kernel can take any arbitrary shapes but this may require more basis functions to accurately estimate the kernel.}}
 
 			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.
+
+			 \emph{\parham{Please refer to Response 2 to the handling editor. Further comments are also added below.}}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
completed davids comments to reviewer 2

@@
 
-        \item Also, Appendix A is the analogue of Appendix D of Freestone et al. and Appendix C includes results known from the literature (as the authors point out).
+        \item Appendix A is the analogue of Appendix D of Freestone et al. and Appendix C includes results known from the literature (as the authors point out).
 
@@
 We have no objections to removing Appendix C.
-However as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
+However, as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
 
@@
 
-\emph{\parham{To respond to this important comment we have added ``State-space representation'' subsection into the discussion.}}
+\emph{\parham{To respond to this important comment we have added ``8.1 State-space representation'' subsection into the discussion.}}
 
@@
 inverse modelling.
-\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.} For example, in a forward model the nonlinearity is required to prevent negative firing rates.
-However in the inverse case, the physiology naturally restricts firing rates to be positive.
+\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.} For example, in a forward model, the nonlinearity is required to prevent negative firing rates.
+However, in the inverse case, the physiology naturally restricts firing rates to be positive.
 Furthermore, in the mean field case, we do not expect firing rates of all neurons to be zero or all neurons to be simultaneously firing at their maximal rate.
@@
 \emph{\dean{Given restrictions of computational complexity, the choice of whether to use the framework presented in Freestone et al.
-or the current paper may boil down to a trade-off between temporal accuracy and spatial accuracy.
+or the current paper boils down to a trade-off between temporal accuracy and spatial accuracy.
 Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
@@
 
-\dean{\emph{Within our framework the alternate levels are defined by the spatial scales of the wavelet decomposition.
+\dean{\emph{Within our framework, the alternate levels are defined by the spatial scales of the wavelet decomposition.
 The significant result is the formulation of a model when various spatial scales of a neural field can be simultaneously represented.
@@
 
-				\item Similar claims to the ones mentioned here regarding  implications for ``patient-specific'' modelling have also been made in Freestone et al., so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
+				\item Similar claims to the ones mentioned here regarding implications for ``patient-specific'' modelling have also been made in Freestone et al.
+(2010), so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
 
-				\dean{\emph{Please refer to Response 2 to the handling editor.}}
+				\dean{\emph{Please refer to Response 2 to the handling editor. In summary, ... }}
 
@@
 
-				\emph{\ken{To clarify this comment, a short paragraph has been included in section 6 to better explain the modeling choice facing every user, that is; choosing between a more parsimonious or more complex model structure.
+				\emph{\ken{To clarify this comment, a short paragraph has been included in Section 6 to better explain the modeling choice facing every user, that is, choosing between a more parsimonious or more complex model structure.
 For the audience with less experience in system identification, a reference with further information regarding this topic has also been included.}}
 
-				\item Also, the comments on large scale networks and delays made on p.20 look irrelevant to the present framework.
+				\item The comments on large scale networks and delays made on p.20 look irrelevant to the present framework.
 
@@
 
-				\emph{\parham{We have added a paragraph in the new subsection ``State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
+				\emph{\parham{We have added a paragraph in the new subsection ``8.1 State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
 
@@
 			 \end{enumerate}  
-			\subsection{Trivia}
+			\subsection{Minor Comments}
 			\begin{enumerate}

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
edits in Moderate Concerns

@@
 
-			\emph{\parham{It is generally accepted that the intracortical connectivity structure is isotropic, however, as the reviewer pointed out this is not the case  for corto-cortical connectivity.
-The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions.
+			\emph{\parham{It is generally accepted that the intracortical connectivity structure is isotropic.
+However, as the reviewer pointed out, this is not the case for cortico-cortical connectivity.
+The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form an anisotropic kernel).
 The connectivity kernel can take any arbitrary shapes but this may require more basis functions to accurately estimate the kernel.}}
@@
 			 \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
-However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
-The title of the manuscript was chosen such that to reflect this fact, stating this is a multi-resolution framework for Amari type neural field model.
-In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Result section.}}
+However, before validating the method on real data, we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
+We believe this was achieved in this paper.
+The title of the manuscript was chosen to reflect this fact, stating this is a multi-resolution framework for the Amari type neural field model.
+In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Results section.}}
 
@@
 (5).
-The double font domains are added to Table.1.
+The double font domains are added to Table 1.
 A brief description of `lead field' is also added below Eq.
@@
 
-			\item I would also recommend archiving code that, for instance generates figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.
+			\item I would also recommend archiving code that, for instance generates Figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.
 
  			\emph{\parham{We have added a footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
+
+\dean{Cant we just upload it?}
 
@@
 
-			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}
+			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage, or synaptic activity defined as the statistical expectation taken over a neural population, while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}
 
@@
 
-			\emph{\parham{Authors think that the reviewer is after Eqn 2.
-for the correction.
-We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}
+			\emph{\parham{We think that the Reviewer is referring to Eq.
+2 for the correction.
+We have rewritten Eq.
+2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript, and we have described the coupling strength or synaptic efficiency within the text under Eq.
+2.}}
 
@@
 However the states are weights for particular levels of resolution, where $v$ is the total net field.
-We have added a sentence to add clarification.
+We have added a sentence to add clarification in Section \dean{xx}.
 \parham{please dont forget to add this to manuscript}}
 
-			\item Between eqn 19 and 20 change
+			\item Between Eq. 19 and 20 change
 			`write the neural field and connectivity kernel decomposition' To `write the connectivity kernel and neural field decomposition'
-			To maintain order with eqns 20 and 21.
+			To maintain order with Eqs 20 and 21.
 
-			\emph{\parham{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with eqns 20 and 21.}}
+			\emph{\parham{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with Eqs. 20 and 21.}}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
minor edit to letter

@@
 
-			\item Define first and second order synaptic responses (used in figure 2 to explain text that does not refer to these terms)
+			\item Define first and second order synaptic responses (used in Figure 2 to explain text that does not refer to these terms)
 
@@
 
-			\item{Eqn 9: the state variables $x$ seem to arise without distinction from $v$}
+			\item{Eq. 9: the state variables $x$ seem to arise without distinction from $v$}
 
@@
 			`write the neural field and connectivity kernel decomposition' To `write the connectivity kernel and neural field decomposition'
-			To maintain order with Eqs 20 and 21.
+			To maintain order with Eqs. 20 and 21.
 
@@
 			\begin{enumerate}
-			 \item 	Define `one-off' on pg 16
+			 \item 	Define `one-off' on pg. 16
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
edits to letter and headings in paper

@@
 
-\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the appendix will provide a better flow to the paper. This has been done.}
+\emph{As the reviewer suggested, moving the calculation of the Fourier transform to the Appendix will provide a better flow to the paper. This has been done.}
 
@@
 \emph{\dean{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
-This derivation is perhaps the most important contribution of the paper \parham{not sure about this because we have already done the derivation in Freestone 2011}.
+This derivation to represent different spatial scales in the neural field simultaneously in a state-space format, such that estimation algorithms can be applied, is perhaps the most important contribution of the paper \parham{not sure about this because we have already done the derivation in Freestone 2011}.
 We understand that all physical systems are nonlinear.
@@
 inverse modelling.
-\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand it is required for forward modelling.} For example, in a forward model, the nonlinearity is required to prevent negative firing rates.
+\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand a nonlinear activation function is required for forward modelling.} For example, in a forward model, the nonlinearity is required to prevent negative firing rates.
 However, in the inverse case, the physiology naturally restricts firing rates to be positive.
 Furthermore, in the mean field case, we do not expect firing rates of all neurons to be zero or all neurons to be simultaneously firing at their maximal rate.
-Therefore, a linear model may suffice to image a multi-resolution neural field and physiological parameters using electrophysiological data .}}
+Therefore, a linear model may suffice to image a multi-resolution neural field and physiological parameters using electrophysiological data.}}
 
@@
 Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
-This is due to the correction step in the algorithm where model error is reduced using measurements.\parham{not sure this is due to the correction step, the correction step of this paper and Freestone 2011 are the same due to the linearity of the observation equation.}}}
+This is due to the guaranteed convergence of the EM-algorithm for linear system.
+With convergence, modelling errors can be corrected using data.
+where model error is reduced using measurements.\parham{not sure this is due to the correction step, the correction step of this paper and Freestone 2011 are the same due to the linearity of the observation equation.}}}
 
@@
 
-\emph{\parham{We have added a sentence to Sect 8.1 (now 8.2) for the basis structure requirement.}}
+\emph{\parham{We have added a sentence to Sect. 8.1 (now 8.2) for the basis structure requirement.}}
 
@@
 
-\emph{\parham{We have added this comment to Sect 8.2 (now 8.3).}}
+\emph{\parham{We have added this comment to Sect. 8.2 (now 8.3).}}
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to letter and headings in paper

@@
 Here the latter is chosen as shown in the block diagram ensuring the resultant initial kernel estimate leads to a stable system.
-\subsection{E-step}
+\subsection{E-Step}
 As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem.
@@
 Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation.
- \subsection{M-step}
+ \subsection{M-Step}
 The lower bound on the log-likelihood function is given by the expectation of the complete (hidden and observable) data  log-likelihood \citep{Bishop2006} 
@@
 A summary of the joint state parameter estimation is given in Table~\ref{alg:EMsteps}.
-\subsection{Stopping rule}
+\subsection{Stopping Rule}
 The stopping criterion is usually associated with either the change in the parameter estimates or the log-likelihood variation \citep{McLachlan1997}. The stopping rule adopted herein is
@@
  \end{equation}
-\subsection{Computational complexity} 
+\subsection{Computational Complexity} 
 All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
-\parham{\subsection{State-space representation}
+
+\parham{\subsection{State-Space Representation}
 Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problems.
@@
 
-\subsection{Estimation algorithm}
+\subsection{Estimation Algorithm}
 \parham{The implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by \cite{Dewar2009} as it is shown in Table~\ref{table:MRA-ComputationalComplexity}, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
@@
 isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
- \subsection{Modification to higher dimensions}
+
+ \subsection{Modification to Higher Dimensions}
  The reconstruction of the neural field in higher dimensions requires $2^n-1$ wavelets, where $n$ is the dimension of the space.
@@
 Unfortunately, in 3D, it is not possible to have a subsampling operator (acting on a Cartesian sampling lattice) that is performing subsampling at equal rate in each dimension at each iteration \citep{VanDeVille2005a}.}
-\subsection{Extensions to the framework} 
+\subsection{Extensions to the Framework} 
 Clearly there is, and will always be, a discrepancy between the dynamics of the model and the experimental observation.

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
removing the \dean and \parham from the response letter

@@
 \begin{enumerate}
-\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multiresolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.
+\item Whilst the paper does fit the scope of NI, I agree with R1 and R3, that explicit advantages of going to a multi-resolution frame - in addition to the conceptual ones - compared to the prior work based on Gaussian basis functions needs clarification and elucidation.
 
-\emph{\parham{The first paragraph of the newly added ``State-space representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
+\emph{The first paragraph of the newly added ``State-space representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
 We also added a paragraph to ``Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al.
 (2009).
-Please refer to Responses 1 and 5 to R1 for more details.}}
+Please refer to Responses 1 and 5 to R1 for more details.}
 
@@
 
-\dean{\emph{We agree that the use of empirical data will strengthen the paper.
+\emph{We agree that the use of empirical data will strengthen the paper.
 Unfortunately, we do not have access to the appropriate data at present.
@@
 This new lens allows us to image aspects of neurophysiology of individual subjects that are normally hidden in electrical recordings.
-Therefore, we believe it is important to continue to improve our methods that will lead to the next era in systems neuroscience, where mathematical modelling, experimental measures and model-data fusion will become standard methods.
+Therefore, we believe it is important to continue to improve our methods that will lead to the next era in systems neuroscience, where mathematical modeling, experimental measures and model-data fusion will become standard methods.
 Furthermore, we believe that (good) experimental design is based upon the availability of analysis tools.
 Therefore, new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
-} }
+}
 
@@
     \begin{enumerate}
-        \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in Neuroimage and IEEE Trans on Signal Processing  respectively.
+        \item The exposition of the material and the relevant discussion have many similarities with the papers of the same authors (Freestone et al., 2011) and (Dewar et al., 2009) published in NeuroImage and IEEE Trans on Signal Processing  respectively.
 The authors say the paper at hand is an ``extension'' of Freestone et al.
 by which I understand they mean the use of a wavelet as opposed to a Gaussian basis for the decomposition.
-Since the methodology used is the same as in that earlier Neuroimage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
+Since the methodology used is the same as in that earlier NeuroImage paper, the paper at hand repeats several of  the results of that previous paper, see sections 3 and 4: equations (2)-(5) and (20) -(33) have already appeared or are very similar to equations in Freestone et al.
 
@@
 There are similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
-The challenges in forming a multiresolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
+The challenges in forming a multi-resolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
 This paper is a result of a concerted effort from our team over a time period of more than two years work.
@@
 
-\emph{\dean{The inverse framework in Dewar et al.
+\emph{The inverse framework in Dewar et al.
 (2009) is based on a general integro-differential equation model, which is not suitable when neural field models are considered.
 As a result, the necessary modifications have been made.
-}}
+}
 
-\emph{\dean{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al.
+\emph{This paper has a novel implementation of the M-step, which significantly simplifies the computational complexity of the EM-based algorithm proposed by Dewar et al.
 (2009).
@@
 A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
-(2009)).} }
+(2009)).}
 
@@
 
-		\emph{\parham{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically when the parameters are separable giving results equivalent to the least square estimates.
-In fact this is one of the advantages of this representation, such a closed form solution for the system's parameters results in significant computational savings.}}
+		\emph{For linear state-space models, under Gaussian conditions, the lower bound on the log-likelihood function is always quadratic in parameters, and can be solved analytically when the parameters are separable giving results equivalent to the least square estimates.
+In fact this is one of the advantages of this representation, such a closed form solution for the system's parameters results in significant computational savings.}
 
@@
 
-\emph{\parham{In order to formulate the state-space representation of the multi-resolution neural field model, the inner product of the B-spline functions are required.
+\emph{In order to formulate the state-space representation of the multi-resolution neural field model, the inner product of the B-spline functions are required.
 We believe that it is necessary to provide the interested reader with the required tools to implement the algorithm.
 Appendix D of Freestone et al.
-(2009) and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated.
-In Appendix D of Freestone et al., two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
+(2011) and Appendix A herein are only similar in the sense that the inner product of two basis functions are calculated.
+In Appendix D of Freestone et al.
+(2011), two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
 We have no objections to removing Appendix C.
-However, as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.} }
+However, as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.}
 
@@
 
-\emph{\parham{To respond to this important comment we have added ``8.1 State-space representation'' subsection into the discussion.}}
+\emph{To respond to this important comment we have added ``8.1 State-Space Representation'' subsection into the discussion.}
 
-				\item{The framework of Freestone et al., seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive. }
+				\item{The framework of Freestone et al.
+(2011), seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.
+}
 
-\emph{\dean{The linear activation function in the estimation algorithm was made out of necessity.
-This was due to the high dimensionality and associated computational demands of the estimation problem.}}
+\emph{The linear activation function in the estimation algorithm was made out of necessity. This was due to the high dimensionality and associated computational demands of the estimation problem.}
 
-\emph{\dean{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
-This derivation to represent different spatial scales in the neural field simultaneously in a state-space format, such that estimation algorithms can be applied, is perhaps the most important contribution of the paper \parham{not sure about this because we have already done the derivation in Freestone 2011}.
+\emph{The authors would like to point out that the derivation of the state-space multi-resolution model was made general for all possible activation functions.
+This derivation to represent different spatial scales in the neural field simultaneously in a state-space format, such that estimation algorithms can be applied, is perhaps the most important contribution of the paper.
 We understand that all physical systems are nonlinear.
@@
 In the introduction to the estimation section, we have attempted to discuss this issue with regard to forward vs.
-inverse modelling.
-\parham{Dean: I think something is missing here: We believe that the linear model is more acceptable for inverse modelling, but understand a nonlinear activation function is required for forward modelling.} For example, in a forward model, the nonlinearity is required to prevent negative firing rates.
+inverse modeling.
+We believe that the linear model is more acceptable for inverse modeling, but understand a nonlinear activation function is required for forward modeling.
+For example, in a forward model, the nonlinearity is required to prevent negative firing rates.
 However, in the inverse case, the physiology naturally restricts firing rates to be positive.
 Furthermore, in the mean field case, we do not expect firing rates of all neurons to be zero or all neurons to be simultaneously firing at their maximal rate.
-Therefore, a linear model may suffice to image a multi-resolution neural field and physiological parameters using electrophysiological data.}}
+Therefore, a linear model may suffice to image a multi-resolution neural field and physiological parameters using electrophysiological data.}
 
-\emph{\dean{Given restrictions of computational complexity, the choice of whether to use the framework presented in Freestone et al.
+\emph{Given restrictions of computational complexity, the choice of whether to use the framework presented in Freestone et al.
 or the current paper boils down to a trade-off between temporal accuracy and spatial accuracy.
 Furthermore, the proven convergence of estimation algorithms for linear systems may actually lead to more accurate models given a closed-loop scheme.
-This is due to the guaranteed convergence of the EM-algorithm for linear system.
-With convergence, modelling errors can be corrected using data.
-where model error is reduced using measurements.\parham{not sure this is due to the correction step, the correction step of this paper and Freestone 2011 are the same due to the linearity of the observation equation.}}}
+This is due to the guaranteed convergence of the EM-algorithm for (observable) linear systems.
+With convergence, modeling errors can be corrected using data.}
 
@@
 
-\dean{\emph{Within our framework, the alternate levels are defined by the spatial scales of the wavelet decomposition.
+\emph{Within our framework, the alternate levels are defined by the spatial scales of the wavelet decomposition.
 The significant result is the formulation of a model when various spatial scales of a neural field can be simultaneously represented.
-The ability to image the multi-dimensional neural field will lead to a better understanding of the important spatial scales when neural information processing occurs.
-}}
+The ability to image the multi-dimensional neural field will lead to a better understanding of the important spatial scales when neural information processing occurs.}
 
-				\item Similar claims to the ones mentioned here regarding implications for ``patient-specific'' modelling have also been made in Freestone et al.
-(2010), so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
+				\item Similar claims to the ones mentioned here regarding implications for ``patient-specific'' modeling have also been made in Freestone et al.
+(2011), so it is not clear how these relate to the current multi-resolution approach and also such remarks might look too ambitious given that only synthetic data with fixed parameters are considered.
 
-				\dean{\emph{Please refer to Response 2 to the handling editor. In summary, ... }}
+	\emph{Please refer to Response 2 to the handling editor. In summary, ... }
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
more minor edits to letter in reviewer 2 section

@@
 
-\emph{The first paragraph of the newly added ``State-space representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
+\emph{The first paragraph of the newly added ``8.1 State-Space Representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
 We also added a paragraph to ``Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al.
@@
 Furthermore, we believe that (good) experimental design is based upon the availability of analysis tools.
-Therefore, new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.
-}
+Therefore, new imaging tools, like the framework presented in this paper, will lead to new data being collected and potential advances in our collective knowledge of brain function.}
 
@@
 
-\emph{\dean{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
+\emph{We have had similar feedback to your suggestion from our colleagues prior to submission of the paper.
 Interestingly, the feedback from the people with expertise in wavelet theory thought that the overview of the estimation methods was essential, but the section on wavelets should be reduced.
@@
 We completely appreciate R1's comments and suggestions, but since R2 commented on the usefulness of this section we would very much like to leave it in.
-We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}}
+We believe that different sections will be valuable for people with different specializations, the synthesis of this information is a valuable contribution for implementation for a wide audience.}
 
@@
 		\item{The framework of Freestone et al.
-(2011), seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.
-}
+(2011), seemed not to assume a linear relation between mean membrane potential and firing rate and in that sense the present approach appears more restrictive.}
 
@@
 
-	\emph{Please refer to Response 2 to the handling editor. In summary, ... }
+	\emph{Please refer to Response 2 to the handling editor.
+\dean{In summary, the framework can be used to create patient-specific models when it is applied with patient-specific data.
+Demonstrating convergence with synthetic data, where actual states and parameters are known, is a necessary first step.
+Furthermore, there is a significant body of work where various phenomena have been replicated using the neural field equations.
+This motivates the creation of tools to verify the models and experimentally test hypotheses that computational studies have generated.
+}}
 
@@
 
-				\emph{\ken{To clarify this comment, a short paragraph has been included in Section 6 to better explain the modeling choice facing every user, that is, choosing between a more parsimonious or more complex model structure.
-For the audience with less experience in system identification, a reference with further information regarding this topic has also been included.}}
+		\emph{To clarify this comment, a short paragraph has been included in Section 6 to better explain the modeling choices facing every user.
+That is, choosing between a more parsimonious or more complex model structure.
+For the audience with less experience in system identification, a reference with further information regarding this topic has also been included.}
 
@@
 
-				\emph{\parham{We have omitted the last paragraph of the discussion on delays in large scale networks.}}
+		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks.}
 
@@
 
-				\emph{\parham{We have added a paragraph in the new subsection ``8.1 State-space representation'' in the Discussion, regarding the choice of the observation kernel.}}
+		\emph{We have added a paragraph in the new subsection ``8.1 State-Space Representation'' in the Discussion, regarding the choice of the observation kernel.}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
more minor edits to letter in reviewer 2 section

@@
 \emph{The first paragraph of the newly added ``8.1 State-Space Representation'' subsection in the Discussion  highlights the benefits of the MRAIDE compared to the prior work.
-We also added a paragraph to ``Estimation algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al.
+We also added a paragraph to ``8.2 Estimation Algorithm'' in the Discussion to clarify the benefits of the novel M-step presented in this work compared to the implementation in Dewar et al.
 (2009).
@@
 
-	\emph{\parham{We have changed the scaling and wavelet coefficients into normal lowercase `a' and `c', respectively.}}
+	\emph{We have changed the scaling and wavelet coefficients into normal lowercase `a' and `c', respectively.}
 
@@
 
-\emph{\parham{We have added a sentence to Sect. 8.1 (now 8.2) for the basis structure requirement.}}
+\emph{We have added a sentence to Sect. 8.1 (now 8.2) for the basis structure requirement.}
 
@@
 
-\emph{\parham{We have added this comment to Sect. 8.2 (now 8.3).}}
+\emph{We have added this comment to Sect. 8.2 (now 8.3).}
 
@@
 		\begin{enumerate} 
-			\item I am not at all sure that isotopic scaling of the multiresolution is appropriate for brain connections, but I cannot say at this point that it is not.
+			\item I am not at all sure that isotopic scaling of the multi-resolution is appropriate for brain connections, but I cannot say at this point that it is not.
 
-			\emph{\parham{It is generally accepted that the intracortical connectivity structure is isotropic.
+			\emph{It is generally accepted that the intracortical connectivity structure is isotropic.
 However, as the reviewer pointed out, this is not the case for cortico-cortical connectivity.
-The presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form an anisotropic kernel).
-The connectivity kernel can take any arbitrary shapes but this may require more basis functions to accurately estimate the kernel.}}
+\dean{Nevertheless, the presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form a net anisotropic kernel).} The connectivity kernel can take any arbitrary shapes but this may require more basis functions for an accurate reconstruction.}
 
@@
 
-			 \emph{\parham{Please refer to Response 2 to the handling editor. Further comments are also added below.}}
-
-			 \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
+			 \emph{\dean{We agree with this statement 100 percent.
+We hope that this paper will motivate new experiments, where neural field models can be experimentally validated.
+It has now been nearly 40 years since neural field models where introduced in computational studies.
+For the first time we are at the exciting point in time where computing power and estimation algorithms are sufficiently advanced to link models to actual data.
+This is why we believe the framework the is introduced in this paper has the potential to make an impact.} For further remarks regarding this point please refer to Response 2 to the handling editor.}
+		 % 			
+		 % \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
 However, before validating the method on real data, we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
@@
 
-			\emph{\parham{ We have defined independent and identically distributed (i.i.d.) random variables under Eq.
+		\emph{We have defined independent and identically distributed (i.i.d.) random variables under Eq.
 (5).
@@
 A brief description of `lead field' is also added below Eq.
-(5).}}
+(5).}
 
+	\dean{I am up to here!!!~~~~~~~XXXXXX~~~~~~}		
 		\item Frankly, I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.
@@
 
-			\item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.
-
-			\emph{Response here.}
+			% \item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.
+			% 
+			% \emph{Response here.}
 
@@
 
-			\item Eqn 3: theta needs indexing
+			\item Eq. 3: theta needs indexing
 
-			\emph{\parham{We think that the Reviewer is referring to Eq.
-2 for the correction.
-We have rewritten Eq.
+			\emph{We have rewritten Eq.
 2 by removing the parameter $\theta$ in order to be consistent with the rest of equations in the manuscript, and we have described the coupling strength or synaptic efficiency within the text under Eq.
-2.}}
+2.}
 
@@
 
-			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq 2.}}
+			\emph{Definitions of first and second-order synaptic responses have been added to the text under Eq 2.}
 
@@
 			\emph{The units of $x$ are also Volts.
-However the states are weights for particular levels of resolution, where $v$ is the total net field.
-We have added a sentence to add clarification in Section \dean{xx}.
-\parham{please dont forget to add this to manuscript}}
+However, the states are weights for particular levels of resolution, where $v$ is the total net field.
+We have added a sentence to add clarification in Section \dean{xx}}.
 
@@
 
-			\emph{\parham{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain order with Eqs. 20 and 21.}}
+			\emph{We have changed the text to `the connectivity kernel and neural field decomposition' to maintain consistency with Eqs. 20 and 21.}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
edits to paper

@@
 	\dean{I am up to here!!!~~~~~~~XXXXXX~~~~~~}
+
 		\item Frankly, I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.
 
-			\emph{Response here.}
+			\emph{\dean{Response here.}}
 
@@
 However, the states are weights for particular levels of resolution, where $v$ is the total net field.
-We have added a sentence to add clarification in Section \dean{xx}}.
+We have added a sentence below eq.
+9 to add clarification}.
 
@@
 
- 			\emph{Response here.}
+ 			\emph{\dean{Response here.}}
 
@@
 
-  			\emph{\parham{The cross-referencing has been corrected.}}
+  			\emph{The cross-referencing has been corrected.}
 
@@
 
-			\emph{\parham{We have changed the text to `stationary point, i.e. a global'.}}
+			\emph{We have changed the text to `stationary point, i.e. a global'.}
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to paper

@@
 In this way, a flexible framework is created, whereby both macroscopic and microscopic behavior of the system can be represented simultaneously.
-State and parameter estimation is performed using the Expectation Maximization (EM) algorithm.
+State and parameter estimation is performed using the expectation maximization (EM) algorithm.
 A synthetic example is provided
@@
 \begin{keyword}
-  Neural Field Model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm
+  Neural field model, multi-resolution approximation (MRA), expectation maximization (EM) algorithm
 \end{keyword}
@@
 This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics.
-This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE) to address this challenge.
+This paper introduces a multi-resolution data-driven framework for neural field modeling, the multi-resolution approximate integro-difference equation (MRAIDE) to address this challenge.
 
@@
 The ability to create patient-specific neural models will contribute to our knowledge base of diseases such as epilepsy and will enable the development of new treatment strategies.
-Large-scale neuroinformatic efforts, such as the Virtual Brain project (www.thevirtualbrain.org \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.
+Large-scale neuroinformatic efforts, such as the Virtual Brain Project (www.thevirtualbrain.org \citep{Jirsa2010}), are on the way to enable patient-specific full brain modeling.
 This is particularly relevant to the advent of new devices that use therapeutic electrical stimulation.
@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\parham{The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.} It is expected that parameters of \parham{(these models instead of the neural fields models ??)} the neural fields models will be patient-specific and will, therefore, need to be inferred from data.
+\dean{The main difference between these two classes is that neural field models represent a cortical sheet, making a continuum approximation to describe the spatiotemporal evolution of neural dynamics (such as mean firing rates or mean membrane potentials), while neural mass models describe ensembles of neurons at a localized point, which may be networked to multiple points.
+Both neural field and neural mass models make a mean-field approximation to describe the mass action of the brain.} It is expected that parameters of these models will be patient-specific and will, therefore, need to be inferred from data.
 
@@
 faces), but the specificity of this response is dependent on the large-scale pattern of activity across most visual cortical areas \citep{Haxby2001}.
-Further, the evolution of diffusion magnetic resonance imaging (dMRI) has led to the development of tensor-based tractography, which allows for in vivo images of the white matter skeleton of any brain.
+Further, the evolution of diffusion magnetic resonance imaging (dMRI) has led to the development of tensor-based tractography, which allows for \emph{in vivo} images of the white matter skeleton of any brain.
 Improvements of the MR sequences (e.g.
@@
 The first work (to the authors best knowledge) describing data-driven mesoscopic neural modeling used a neural mass model to fit EEG data~\citep{Valdes1999}.
-This approach was extended to coupled neural masses through a Bayesian estimation scheme called Dynamic Causal Modeling (DCM)~\citep{David2003}.
+This approach was extended to coupled neural masses through a Bayesian estimation scheme called dynamic causal modeling (DCM)~\citep{David2003}.
 Following this work, data-driven modeling was extended to continuum field equations that explained the richer dynamics of spatiotemporal neural fields \citep{Galka2008,schiff2008kalman,Daunizeau2009, Pinotsis2012}.
-Most recently, a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
+Most recently, a framework was developed where a finite-element model of the neural field (via a dynamic Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite-dimensional system to facilitate efficient state and parameter estimation~\citep{Freestone2011}.
 This paper is an extension to the aforementioned study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex.
@@
 \end{equation}
-where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location within the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
+where $v\left(\mathbf{r},t\right)$ is a voltage field that may be measured with a high-resolution multi-electrode array or voltage sensitive dye, $\mathbf{r}\in \mathbb{R}^n$ (where $n\le3$) describes the spatial location within the field, $t$ denotes time, and $j$ indexes the different levels of resolution in the field.
 This multi-resolution structure is depicted in Fig.~\ref{fig:MultiLayerFieldModel}.
@@
 The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate.
-There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, \parham{leading to first and second order differential equations}.
-These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line).
-The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSPs and IPSPs) features \cite{VanRotterdam1982}}.
+There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, leading to first or second-order differential equations.
+These are plotted in Fig.~\ref{fig:Modelcomponents}, showing the second-order (finite rise time) and first-order (instantaneous response) kernels.
+The second-order synaptic kernel reproduces experimental excitatory and inhibitory post-synaptic potentials (EPSPs and IPSPs) features \citep{VanRotterdam1982}.
 Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms.
 These are also shown in Fig.~\ref{fig:Modelcomponents}.
-The form of $w(\mathbf{r},\mathbf{r}')$ typically describes a Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}.
-By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel.
-\parham{The connectivity kernel then can be written as a sum of weighted Gaussian or Laplacian functions where the weights can be thought of as the synaptic efficiency or coupling strength where positive and negative weights describe excitation and inhibition, respectively.} In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
-
-The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
+The form of $w(\mathbf{r},\mathbf{r}')$ typically describes a Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \citep{Breakspear2010,Atay2005}.
+By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multi-layer structure into the connectivity kernel.
+The connectivity kernel then can be written as a sum of weighted (Gaussian, Laplacian or B-Spline) basis functions, where the weights can be thought of as the synaptic efficiency or coupling strength and positive and negative weights describe excitation and inhibition, respectively.
+In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
+
+The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\citet{Freestone2011} for a full derivation)
 \begin{equation}\label{eq:DiscreteTimeModel}
@@
 \end{equation}
-where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
+where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ is an independent and identically distributed (i.i.d.) Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.
 The observation kernel models the pickup range of the electrical fields of the brain.
-The lead field parameters are not included in the observation equation as the intracranial recordings are considered here.
-\parham{The lead field parameters incorporate all the information about the head model, and must be accounted for inverse solutions when scalp electrodes are considered \cite{Jirsa2007}.}
+The lead field parameters, which incorporate information about a realistic head model~\citep{Jirsa2007}, are not included in the observation equation as the intracranial recordings are only considered here.
 \section{MRA of the IDE in State-Space}
@@
 where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$.
+The state vector has the same units as the neural field (volts).
+However, the states are weights for particular levels of resolution, where $v_t\left(r\right)$ is the total net field.
 The decomposition enables a separation of the spatial characteristics, which are considered static functions that are weighted by dynamic coefficients.
 
-Eqs.~\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem.
+Eqs.~\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions but must be truncated to some level $j,$ in order to solve the estimation problem.
 In other words, the neural field must be band-limited up to a given spatial frequency.
@@
 \end{align}
-One important feature of the B-spline functions is the partition of unity property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
+One important feature of the B-spline functions is the partition of unity property, meaning that the unity (zero spatial frequency) can be expressed as a linear sum of B-splines, i.e
 \begin{equation}
@@
 \subsection{Frequency Analysis}\label{sec:freq_anal}
-\parham{To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines})
+To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines})
 \begin{align}      
@@
 From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
-This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.}
+This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
 \section{State and Parameter Estimation}
@@
 
-\ken{Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
-Such a choice is usually based on the principle of parsimony \cite{burnham2002}, that is; choosing the simplest model capable of capturing the system behavior of interest.
-Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.}
-
-\ken{To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
+Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
+Such a choice is usually based on the principle of parsimony \citep{burnham2002}, that is; choosing the simplest model capable of capturing the system behavior of interest.
+Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.
+
+To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
 Note that by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
 This allows for the adoption of the EM algorithm and thus results in computationally efficient and accurate estimates.
-Consequently, any loss in model detail may be offset by the estimation accuracy.}
+Consequently, any loss in model detail may be offset by the estimation accuracy.
 
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
-
 \parham{\subsection{State-Space Representation}
-Different basis functions can be used to reduce the neural field formulations for state and parameter estimation problems.
-An alternative is given by the Gaussian basis functions adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
+In order to apply estimation algorithms to neural field models a finite-dimensional state-space model must be formed.
+The problem of representing a continuous field with a finite number of states is solved by the basis function decomposition.
+An alternative to using the B-spline wavelets is Gaussian basis functions, which was adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
 One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the simultaneous representation of the neural field at different spatial scales.
@@
 Additional extension for future work include extending the model to capture a second order synaptic response kernel.
-The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials ( see \citet{Spiegler2010,Spiegler2011} for example).
+The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials (see \citet{Spiegler2010,Spiegler2011} for example).
 Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations.

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
edits to discussion

@@
 	\emph{Please refer to Response 2 to the handling editor.
-\dean{In summary, the framework can be used to create patient-specific models when it is applied with patient-specific data.
+In summary, the framework can be used to create patient-specific models when it is applied with patient-specific data.
 Demonstrating convergence with synthetic data, where actual states and parameters are known, is a necessary first step.
 Furthermore, there is a significant body of work where various phenomena have been replicated using the neural field equations.
-This motivates the creation of tools to verify the models and experimentally test hypotheses that computational studies have generated.
-}}
+This motivates the creation of tools to verify the models and experimentally test hypotheses that computational studies have generated.}
 
@@
 However, as the reviewer pointed out, this is not the case for cortico-cortical connectivity.
-\dean{Nevertheless, the presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form a net anisotropic kernel).} The connectivity kernel can take any arbitrary shapes but this may require more basis functions for an accurate reconstruction.}
+Nevertheless, the presented framework is also valid for other connectivity kernels provided they are spatially homogeneous and that they can be approximated by a set of weighted isotropic basis functions (that can form a net anisotropic kernel).
+The connectivity kernel can take any arbitrary shapes but this may require more basis functions for an accurate reconstruction.}
 
@@
 
-			 \emph{\dean{We agree with this statement 100 percent.
+			 \emph{We agree with this statement 100 percent.
 We hope that this paper will motivate new experiments, where neural field models can be experimentally validated.
@@
 For the first time we are at the exciting point in time where computing power and estimation algorithms are sufficiently advanced to link models to actual data.
-This is why we believe the framework the is introduced in this paper has the potential to make an impact.} For further remarks regarding this point please refer to Response 2 to the handling editor.}
+This is why we believe the framework the is introduced in this paper has the potential to make an impact.
+For further remarks regarding this point please refer to Response 2 to the handling editor.}
 		 % 			
@@
 
-	\dean{I am up to here!!!~~~~~~~XXXXXX~~~~~~}
-
 		\item Frankly, I would off-load all of the very difficult mathematics to the appendices and supplementary data, and focus a NeuroImage paper on the results of image analysis.
 
-			\emph{\dean{Response here.}}
+			\emph{We attempted to move the derivation from Eq.
+22 to Eq.
+33 to the appendix.
+This led to more complications, where it was very difficult to define the various components of the model and a notational nightmare.
+To guide the reader who may just be interested in the conceptual framework and results we have added ``The conceptual framework and the key results can be interpreted without following this derivation in detail.'' below Eq.
+22.}
 
@@
 
-			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage, or synaptic activity defined as the statistical expectation taken over a neural population, while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}
+			\emph{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models represent a cortical sheet, making a continuum approximation to describe the spatiotemporal evolution of neural dynamics (such as mean firing rates or mean membrane potentials), while neural mass models describe ensembles of neurons at a localized point, which may be networked to multiple points.
+Both neural field and neural mass models make a mean-field approximation to describe the mass action of the brain.}
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to discussion

@@
 Neural mass and neural field models are ideal candidates for estimation algorithms due to their strong links with physiology and their parsimony.
-\dean{The main difference between these two classes is that neural field models represent a cortical sheet, making a continuum approximation to describe the spatiotemporal evolution of neural dynamics (such as mean firing rates or mean membrane potentials), while neural mass models describe ensembles of neurons at a localized point, which may be networked to multiple points.
-Both neural field and neural mass models make a mean-field approximation to describe the mass action of the brain.} It is expected that parameters of these models will be patient-specific and will, therefore, need to be inferred from data.
+The main difference between these two classes is that neural field models represent a cortical sheet, making a continuum approximation to describe the spatiotemporal evolution of neural dynamics (such as mean firing rates or mean membrane potentials), while neural mass models describe ensembles of neurons at a localized point, which may be networked to multiple points.
+Both neural field and neural mass models make a mean-field approximation to describe the mass action of the brain.
+It is expected that parameters of these models will be patient-specific and will, therefore, need to be inferred from data.
 
@@
 The aim of the next part of the derivation is to isolate the state vector on the left hand side of the equation.
-To do this we first multiply both sides of Eq.~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
+The conceptual framework and the key results can be interpreted without following this derivation in detail.
+To isolate the state vector we first multiply both sides of Eq.~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving
 \begin{align}\label{eq:ApproxDiscreteTimeModel2}
@@
 Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling, where the dynamics and connectivity structure differs at different spatial scales~\citep{Jirsa2002,Jirsa2004,Breakspear2005,Qubbaj2009,Schultze-Kraft2011}.
-\parham{\subsection{State-Space Representation}
+\subsection{State-Space Representation}
 In order to apply estimation algorithms to neural field models a finite-dimensional state-space model must be formed.
 The problem of representing a continuous field with a finite number of states is solved by the basis function decomposition.
-An alternative to using the B-spline wavelets is Gaussian basis functions, which was adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
+An alternative to using the B-spline wavelets are Gaussian basis functions, which were adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
 One clear advantage of B-spline scaling and wavelet functions is the MRA capability, allowing the simultaneous representation of the neural field at different spatial scales.
 B-spline scaling and wavelet functions are compactly supported, eliminating  numerical errors caused by the Gaussian basis function.
-The partition of unity of these basis functions enable the reconstruction of the neural field when it saturates, this may be beneficial to model neurological disorders such as epilepsy.
-Attaining fine scale approximation of the neural field using Gaussian basis functions results into an ill-posed problem as the number of states is increased significantly, however, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.\\ \cite{Freestone2011} showed experimentally that Gaussian functions are a suitable choice for modeling the observation kernel when intracranial measurements are considered.
+The partition of unity (ability to represent a zero spatial frequency field) of these basis functions enable the reconstruction of the neural field when it saturates.
+This may be beneficial to model neurological disorders such as epilepsy.
+Attaining fine-scale approximation of the neural field using Gaussian basis functions results in an ill-posed problem as the number of states is increased significantly.
+However, this is not the case when using B-spline scaling and wavelet functions due to their semi-orthogonality property.\\ \citet{Freestone2011} showed experimentally that Gaussian functions are a suitable choice for modeling the observation kernel when intracranial measurements are considered.
 B-splines converge to Gaussian functions as the order of the B-spline, $m$, tends to infinity.
-The cubic B-spline is already a very close approximation to the Gaussian function, therefore these should also be suitable for modeling the observation kernel while having the advantage of being compactly supported.}
+The cubic B-spline is already a very close approximation to the Gaussian function.
+Therefore, these should also be suitable for modeling the observation kernel while having the advantage of being compactly supported.
 
 \subsection{Estimation Algorithm}
-\parham{The implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by \cite{Dewar2009} as it is shown in Table~\ref{table:MRA-ComputationalComplexity}, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$.
-This is crucial for high dimensional systems and more specifically for implementing the multi-resolution framework introduced herein which otherwise would be possible.}
+The implementation of the M-step in this work significantly simplifies the computational complexity of the EM based algorithm proposed by \cite{Dewar2009}, as shown in Table~\ref{table:MRA-ComputationalComplexity} ($O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$).
+This is crucial for high-dimensional systems, and more specifically, for implementing the multi-resolution framework introduced herein.
+Furthermore, choosing isotropic scaling and wavelet functions allows switching the order of operations with the spatial convolution and inner product in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
+This simplifies the computational complexity of the estimation algorithm significantly.
 
@@
 
-\parham{The basis structure (i.e., non-redundant, versus a (tight) frame representation) is a requirement for this framework.
-}Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}.
-This simplifies the computational complexity of the estimation algorithm significantly.
-Although this is correct for one dimensional B-spline scaling and wavelet functions, it does not hold at higher dimensions as the resulting B-spline wavelets are not isotropic.
-One alternative could be
-isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
+\dean{The basis structure (i.e., non-redundant versus a (tight) frame representation) is a requirement for this framework.}
 
@@
 In this case three wavelet functions are required to extract fine features of the field at vertical, horizontal and diagonal orientations.
-The formulations provided in this paper can be easily extended to two dimensions.
-However, the computational load of the estimation algorithm will be significant.
+Theoretically, the formulations provided in this paper can be easily extended to two dimensions.
+However, the increase in computational load of the estimation algorithm will be significant.
+This is not only due to the increase in number of wavelets, but also the switch of convolution and inner product does not hold, as the resulting higher-dimensional B-spline wavelets are not isotropic.
+A possible solution could be to use
+isotropic polyharmonic B-splines scaling functions and wavelets as an alternative \citep{VanDeVille2005}.
+
 It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
-\parham{It is also possible to apply other than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands.
+It is also possible to apply other methods than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands.
 For example, in 2D, the quincunx scheme is well-known to have better isotropic properties.
-Unfortunately, in 3D, it is not possible to have a subsampling operator (acting on a Cartesian sampling lattice) that is performing subsampling at equal rate in each dimension at each iteration \citep{VanDeVille2005a}.}
+Unfortunately, in 3D, it is not possible to have a subsampling operator (acting on a Cartesian sampling lattice) that is performing subsampling at equal rate in each dimension at each iteration \citep{VanDeVille2005a}.
 \subsection{Extensions to the Framework} 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to dean and davids acknowledgement and affiliation
edits to 5.2

@@
 \ead{parham.aram@univ-amu.fr}
-\author[DEEE]{D. R. Freestone}
+\author[DEEE,BI]{D. R. Freestone}
 \ead{deanrf@unimelb.edu.au} 
@@
 \ead{viktor.jirsa@univ-amu.fr}
-\author[DEEE]{D. B. Grayden}
+\author[DEEE,BI]{D. B. Grayden}
 \ead{grayden@unimelb.edu.au}
@@
  \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}
+ \address[BI]{The Bionics Institute, East Melbourne, VIC, Australia}
 
@@
 \subsection{Frequency Analysis}\label{sec:freq_anal}
-To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines})
+To determine the number of basis functions required to reconstruct the field and the level of approximation in the model, $j$, the frequency response of the B-spline wavelets is required.
+This is given by (see~\ref{ap:FourierofBsplines})
 \begin{align}      
@@
 where $\nu$ is the spatial frequency and $i=\sqrt{-1}$.
-From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
-This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
+From Eq.~\eqref{eq:MRA-Wavelettransform}, the frequency response of the wavelets and hence the level of approximation, $j$, can be determined.
+In this way, we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
 \section{State and Parameter Estimation}
@@
 This research was also partly supported by the Australian Research Council (Linkage Project LP100200571).
+The Bionics Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.
 \clearpage

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
edits to 5.2

@@
 $j=0$ to $j=4$.
-\parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.
+\parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM-based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
minor edits

@@
 
-\author[TNG]{P. Aram\corref{cor1}}
+\author[TNG,US]{P. Aram\corref{cor1}}
 \ead{parham.aram@univ-amu.fr}
@@
 	$\Omega$ & Spatial domain & n.a.\\ 
-	$\mathbb{R}$&\parham{The set of all real numbers}&n.a.\\
-	$\mathbb{Z}$&\parham{The set of all integers}&n.a.\\
+	$\mathbb{R}$&The set of all real numbers&n.a.\\
+	$\mathbb{Z}$&The set of all integers&n.a.\\
 	$\mathbf{r}$ & Spatial location & [mm, mm]\\
@@
 \section{Fourier transform of B-spline wavelets}\label{ap:FourierofBsplines}
-\parham{To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
+To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
 \begin{align}\label{eq:MRA-N1Fouriertransform}
@@
 	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{app:MRA-Wavelettransform}
-\end{align} }
+\end{align} 
 \section{Construction and maximization of the lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
comment for tight (frame) and redundancy

@@
 The differences are highlighted in Table.~4 of the manuscript, namely from $O(n_x^4n_{\theta}^2)$ to $O(n_x^2n_{\theta}^2)$, see equation (64) of this paper and equation (31) of Dewar et al.
-(2009), where the static and dynamic components are separated by defining $\boldsymbol \Gamma_1$ and $\mathbf U$ (see equations (65) and (67)).
+(2009), where the static and dynamic components are separated by defining $\boldsymbol \Gamma_2$ and $\mathbf U$ (see equations (66) and (67)).
 A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
@@
 
-\emph{We have added a sentence to Sect. 8.1 (now 8.2) for the basis structure requirement.}
+\emph{We have added a sentence to Sect. 8.1 for the basis structure.}
 
@@
 
-			% \item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.
-			% 
-			% \emph{Response here.}
-
-			% \emph{\parham{To respond to this comment we have added ``State-space representation'' subsection into the discussion.}}
-
 			\item I would also recommend archiving code that, for instance generates Figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.
 
- 			\emph{\parham{We have added a footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}
-
-\dean{Cant we just upload it?}
+ 			\emph{We have uploaded the Python source codes for our numerical simulations as supplementary material.}
 
@@
 
- 			\emph{\dean{Response here.}}
+ 			\emph{We have clarified this point by changing the text to `All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$ can be computed and stored prior to the commencement of the EM iterations' }
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
comment for tight (frame) and redundancy

@@
 This has major computational advantages when solving the estimation problem.
-%\parham{Although this switch holds theoretically it should be noted that it will introduce numerical error, specially close to the edges, due to the finite extent of the field.
-}
 The predefined convolution can be written as
@@
 \subsection{Computational Complexity} 
-All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed as a one-off before the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
+All $n_x^2$ blocks of $\mathbf U$, $\boldsymbol\Gamma_1$ and $\boldsymbol\Gamma_2$  can be computed and stored prior to the commencement of the EM iterations (Step~1 in Table~\ref{alg:EMsteps} ), which increases the speed of the M-step significantly compared to the implementation of \citet{Dewar2009}.
 The complexity of each step of the algorithm is summarized in Table~\ref{table:MRA-ComputationalComplexity} where for ease of comparison the computational complexity of the method of \citet{Dewar2009} is also identified.
@@
 \section{Results}\label{sec:MRA-results}
-To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically \parham{using Amari neural field model  (Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation})}, allowing a comparison between true and estimated parameters \footnote{\parham{The Python source code for our numerical simulations is available from the authors on request.}}.
+To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically using Amari neural field model  (Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}), allowing a comparison between true and estimated parameters.
 In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e.
@@
 with $\theta_1=200$ and $\theta_2=-100$.
-% This is depicted in Fig.~\ref{fig:KernelEstimate}(A).
 
@@
 $j=0$ to $j=4$.
-\parham{We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM-based algorithm.} All parameters for the model are given in Table~\ref{tab:Parameters}.
+We show it is possible to determine the level of approximation to accurately estimate the underlying field prior to the EM-based algorithm.
+All parameters for the model are given in Table~\ref{tab:Parameters}.
 
@@
 The problem of representing a continuous field with a finite number of states is solved by the basis function decomposition.
+The basis structure (i.e., non-redundant versus a (tight) frame representation) is a requirement for the multi-resolution framework.
 An alternative to using the B-spline wavelets are Gaussian basis functions, which were adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.
@@
 In the examples presented in this paper, a bounded sequence of the state vectors was used to initialize the algorithm, which gave a satisfactory convergence and good state and parameter estimations.
-
-\dean{The basis structure (i.e., non-redundant versus a (tight) frame representation) is a requirement for this framework.}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
general edits

@@
 (2009).
-Please refer to Responses 1 and 5 to R1 for more details.}
+Please refer to Responses 1 and 3 to R1 for more details.}
 
@@
 
-		\emph{To clarify the advantage of the M-step over the implementation in Dewar et al. we have added a paragraph to Section 8.1 (now 8.2). Further comments for the reviewer are added below.}
+		\emph{To clarify the advantage of the M-step over the implementation in Dewar et al.
+we have added a paragraph to Section 8.1 (now 8.2 ``Estimation Algorithm'').
+Further comments for the reviewer are added below.}
 
@@
 (2009), where the static and dynamic components are separated by defining $\boldsymbol \Gamma_2$ and $\mathbf U$ (see equations (66) and (67)).
-A simplification is also performed to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
+A simplification is also performed  (by defining $\boldsymbol \Gamma_1$, i.e.
+equation (65)) to calculate $\boldsymbol\upsilon_0, \boldsymbol\upsilon_1$ (see equations (62) and (63) of this paper and equation (30) of Dewar et al.
 (2009)).}
@@
 
-		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks.}
+		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks as the reviewer suggested.}
 
@@
 \item For the discussion, it might be useful to add a sentence that the basis structure (i.e., non-redundant, versus a (tight) frame representation) is a requirement for this framework.
-
-\emph{We have added a sentence to Sect. 8.1 for the basis structure.}
-
-\item A small comment might also be considered for Sect 8.2: it is possible to apply other than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands.
+A small comment might also be considered for Sect 8.2: it is possible to apply other than dyadic subsampling schemes in multiple dimensions, which leads to less wavelet subbands.
 For example, in 2D, the quincunx scheme is well-known to have better isotropic properties.
@@
 
-\emph{We have added this comment to Sect. 8.2 (now 8.3).}
-
- % 
- % \begin{figure*}[!ht]
- % \begin{center}
- % \includegraphics{./Graph/pdf/fig1.pdf} 
- % \end{center}
- % \caption{}
- % \label{fig:Figure1}
- % \end{figure*}
+\emph{We have added a paragraph  to Section~8.2 (now 8.3 ``Modification to Higher Dimensions'') regarding this important point.}
 

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
some general edits to the letter

@@
 \marginsize {1.6cm}{1.6cm}{2.0cm}{2cm}
-\usepackage{color}
-\newcommand{\dean}[1]{\textcolor{red}{#1}}
-\newcommand{\mike}[1]{\textcolor{green}{#1}}
-\newcommand{\parham}[1]{\textcolor{blue}{#1}}
-\newcommand{\ken}[1]{\textcolor{cyan}{#1}}
 
@@
 
-    % It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.
-
     \begin{enumerate}
@@
 There are similarities with the frameworks with all of these papers, where the field is represented by a basis function decomposition.
-The challenges in forming a multi-resolution state-space model included the conceptualisation of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
+The challenges in forming a multi-resolution state-space model included the conceptualization of the problem, the formulation and derivation of the state-space model, and innovations that make dealing with such a large-scale system feasible.
 This paper is a result of a concerted effort from our team over a time period of more than two years work.
@@
 paper where the Fourier transform of the Gaussian basis functions is calculated).
-
-		% \emph{\parham{Section 5 summarizes important characteristics of B-Spline scaling and wavelet functions which are collected from different references, with an attempt to clarify the inner product and convolution of theses functions (please see R2 comment on ``B-spline calculus'').
-We think that this brief review can familiarize interested readers  with  B-spline scaling and wavelet functions and direct them to the important literature on this matter.
-As the reviewer suggested the calculation of the Fourier transform is now moved to the appendix.}}
 
@@
 
-        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behaviour are best explained'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.
+        \item The authors say that a multi-resolution approach would explain the``organizational level of the brain at which cognition and behavior are best explained'' but it is unclear what the alternative levels considered here are and what the significance of the results obtained is.
 
@@
 
-				% \emph{\parham{some notes to be added to the manuscript: Parsimony: as few as necessary variables to describe a phenomenon, complexity: to add detail description to the model to increase its accuracy with the natural phenomenon, finding a balance between complexity and parsimony is crucial.
-By parsimony we sacrifice realism ...
-}}
-
 		\emph{To clarify this comment, a short paragraph has been included in Section 6 to better explain the modeling choices facing every user.
@@
 
-		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks as the reviewer suggested.}
+		\emph{We have omitted the last paragraph of the discussion on delays in large scale networks.}
 
@@
 For the first time we are at the exciting point in time where computing power and estimation algorithms are sufficiently advanced to link models to actual data.
-This is why we believe the framework the is introduced in this paper has the potential to make an impact.
+This is why we believe the framework that is introduced in this paper has the potential to make an impact.
 For further remarks regarding this point please refer to Response 2 to the handling editor.}
-		 % 			
-		 % \emph{\parham{The authors appreciate that the only way to truly validate the proposed framework is with real data.
-However, before validating the method on real data, we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared.
-We believe this was achieved in this paper.
-The title of the manuscript was chosen to reflect this fact, stating this is a multi-resolution framework for the Amari type neural field model.
-In an effort to make the method employed in the paper more explicit, we have added ``data was generated synthetically using Amari neural field model'' to the Results section.}}
 

### 2012-08-22 Multiresolution_framework/src/BsplineBases.py
added python files for simulations

@@ -1,0 +1,403 @@
+#Author Parham Aram
+#Date 12-10-2011
+from __future__ import division
+#built-in modules
+#standard library imports
+#~~~~~~~~~~~~~~~~~~~~~~~~
+import numpy as np
+import pylab as pb
+import operator
+from scipy import io
+#my modules
+#~~~~~~~~~~~~~~~~~~~~
+import spline
+import IDEComponents
+
+# load coefficients mat file for to tranform B-spline scaling andwavelet function to different scales
+
+TransformCoefficients=io.loadmat('TransformCoefficients')
+
+"""Each basis that is to be used in the integrodifference equation model 
+should be defined here.
+
+Each basis needs to have __mul__ and __conv__ operators that define inner products and convolution, respectively."""
+
+class basis():
+	"""Class defining scale and wavelet function properties"""
+	def isbasis(self):
+		return True
+
+
+class convolution:
+
+	"""Defines convolution of two basis functions."""
+
+
+	def __init__(self,j1,j2,k1,k2,name1,name2,Supp,base=None):
+		self.base='convolution'
+		self.j1=j1
+		self.j2=j2
+		self.k1=k1
+		self.k2=k2
+		self.name1=name1
+		self.name2=name2
+		self.Supp=Supp
+
+	def __repr__(self):
+
+		if self.name1=='P':name_1='Scaling function;'
+		else:name_1='Wavelet basis function;'
+
+		if self.name2=='P':name_2='Scaling function;'
+		else:name_2='Wavelet basis function;'
+
+		return 'Convolution of '+name_1+'j='+str(self.j1)+',k='+str(self.k1)+' with '+name_2 +'j='+str(self.j2)+',k='+str(self.k2)
+
+		
+
+	def __mul__(self,g): 	
+	
+
+		'''Inner product of two  basis functions.'''
+
+		#Multiplication is allowed from right.
+
+		assert (g.base == 'scale' or g.base=='wavelet'), 'inner product error'
[…]

### 2012-08-22 Multiresolution_framework/src/DataGenerationandEstimation.py

@@ -1,0 +1,111 @@
+#Author Parham Aram
+#Date 12-10-2011
+'''This module simulates the  neural field model and uses the generated data
+in the state-space model to estimate states and 
+the connectivity kernel parameters.'''
+
+#Standard library imports
+#~~~~~~~~~~~~~~~~~~~~~~~~
+from __future__ import division
+import pylab as pb
+import numpy as np
+import scipy as sp
+#My modules
+#~~~~~~~~~~~~~~~~~~~~
+import IDEComponents
+import BsplineBases
+from MRIDE import *
+from NF import *
+
+dimension=1
+spacewidth=8
+#distance between adjacent sensors
+Delta_s=0.05
+obs_locns=pb.arange(-spacewidth/2.,spacewidth/2.+Delta_s,Delta_s)
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+sensor_kernel=scale(4,-2)
+#time properties
+#~~~~~~~~~~~~~~~
+#sampling rate  
+Fs =1e3                                       
+#sampling period
+Ts = 1/Fs   
+t_end= 1
+NSamples = t_end*Fs
+T = pb.linspace(0,t_end,NSamples)
+#Define synaptic time constant
+zeta=100
+#space properties
+#~~~~~~~~~~~~~~~~
+spacestep=0.01
+simulation_space=pb.arange(-spacewidth/2.,spacewidth/2.+spacestep,spacestep)	
+#Define connectivity kernel for data generation
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+NF_k_1=pb.array([BsplineBases.scale(j,l-3) for j in [1] for l in [1]],ndmin=2).T 
+NF_k_0=pb.array([BsplineBases.scale(j,l-3) for j in [0] for l in [1]],ndmin=2).T
+
+NF_kernel_basis_functions=pb.concatenate([NF_k_1,NF_k_0])
+NF_kernel_weights = pb.array([[200,-100]]).T
+
+
+
+NF_kernel=IDEComponents.Kernel(NF_kernel_weights,NF_kernel_basis_functions)
+#define connectivity kernel for estimation (reduced model)
[…]

### 2012-08-22 Multiresolution_framework/src/IDEComponents.py

@@ -1,0 +1,71 @@
+#Author Parham Aram
+#Date 12-10-2011
+'''This is to generate IDE components: connectivity kernal and the field'''
+import pylab as pb
+
+class Kernel():
+
+	"""class defining the Connectivity kernel of the brain.
+
+	Arguments
+	----------
+
+	Lambda:array
+		array of connectivity kernel basis functions
+	weights: array
+		list of connectivity kernel weights	
+
+	"""
+	
+	def __init__(self,weights,*Lambda):
+
+		
+		self.Lambda=pb.concatenate(Lambda)
+		self.weights = weights
+		self.NoatEachLevel=[len(f) for f in Lambda]
+	def plot(self,width,color='k'):
+		temp1=[]
+		space=pb.linspace(-width,width,1000)
+		for i in range(self.Lambda.shape[0]):
+			temp2=[]
+			for s in space:
+				temp2.append(self.weights[i]*self.Lambda[i,0](s))
+			temp1.append(temp2)
+		pb.plot(space,pb.sum(pb.squeeze(temp1),axis=0),color)
+		
+		
+		
+		
+
+
+
+class Field():	
+
+	"""class defining the field.
+
+	Arguments
+	----------
+
+	Mu:array
+		array of field basis functions; must be of class Bases
+
+	"""
+
+	def __init__(self, *Mu):
+
+		self.Mu=pb.concatenate(Mu)
+		self.NoatEachLevel=[len(f) for f in Mu]
+
+		
+
+class spline8():
+	"""Clasee defining a spline (m=8) in order to calculate convolution in terms of N_8(s)"""
+	def __init__(self,dimension,bases,weights):
+		self.dimension = dimension
+		assert type(bases) is list, 'the bases must be in a list (even if there is only one)'			
+		self.bases = bases
+		self.weights = weights
+		
+	def __call__(self,s):
+		return sum([self.bases[i].evaluate_at_real(s)*self.weights[i] for i in range(len(self.bases))])
+

### 2012-08-22 Multiresolution_framework/src/ML.py

@@ -1,0 +1,52 @@
+#Author Parham Aram
+#Date 12-10-2011
+from __future__ import division
+import pylab as pb
+import numpy as np
+
+class para_state_estimation():
+
+	def __init__(self,model):
+
+		self.model=model
+
+
+
+	def estimate_kernel(self,X,P,M):
+
+		"""estimate the ide model's kernel weights from data stored in the ide object"""
+
+		# form Xi variables
+		Xi_0 = pb.zeros([self.model.nx,self.model.nx])
+		Xi_1 = pb.zeros([self.model.nx,self.model.nx])
+		for t in range(1,len(X)):
+			Xi_0 += pb.dot(X[t-1,:].reshape(self.model.nx,1),X[t,:].reshape(self.model.nx,1).T) + M[t,:].reshape(self.model.nx,self.model.nx)
+			Xi_1 += pb.dot(X[t-1,:].reshape(self.model.nx,1),X[t-1,:].reshape(self.model.nx,1).T) + P[t-1,:].reshape(self.model.nx,self.model.nx)
+
+		# form Upsilon and upsilons
+		Upsilon = pb.zeros([self.model.ntheta,self.model.ntheta])
+		upsilon0 = pb.zeros([1,self.model.ntheta])
+		upsilon1 = pb.zeros([1,self.model.ntheta])
+		for i in range(self.model.nx):
+			for j in range(self.model.nx):
+				Upsilon += Xi_1[i,j] * self.model.Delta_Upsilon[j,i]
+				upsilon0 += Xi_0[i,j]*self.model.Delta_upsilon[j,i]
+				upsilon1 += Xi_1[i,j]*self.model.Delta_upsilon[j,i]
+		upsilon1=upsilon1*self.model.xi
+		Upsilon=Upsilon*self.model.Ts*self.model.varsigma
+
+		
+
+		weights = pb.dot(pb.inv(Upsilon.T),upsilon0.T-upsilon1.T)
+
+
+		return weights
+
+#define matrix multiplication
+def dots(*args):
+	lastItem = 1.
+	for arg in args:
+		lastItem = pb.dot(lastItem, arg)
+	return lastItem		
+
+

### 2012-08-22 Multiresolution_framework/src/MRIDE.py

@@ -1,0 +1,291 @@
+#Author Parham Aram
+#Date 12-10-2011
+
+#Built-in modules
+#~~~~~~~~~~~~~~~~~
+from __future__ import division
+import pylab as pb
+import numpy as np
+import time
+from scipy import signal
+import scipy as sp
+
+
+#My modules
+#~~~~~~~~~
+import SKF
+import ML
+
+class IDE():
+
+	def __init__(self,kernel,field,sensor_kernel,obs_locns,eta,eta_weight,Sigma_epsilon,Ts,zeta,varsigma,x0,P0):
+
+		self.kernel = kernel
+		self.field = field
+		self.sensor_kernel=sensor_kernel
+		self.obs_locns=obs_locns
+		self.eta=eta
+		self.eta_weight=eta_weight
+		self.Sigma_epsilon=Sigma_epsilon
+		self.x0=x0
+		self.P0=P0
+		self.nx=len(self.field.Mu)
+		self.ny=len(obs_locns)
+		self.ntheta=len(self.kernel.Lambda)
+		self.Ts=Ts
+		self.zeta=zeta
+		self.varsigma=varsigma
+		self.xi=1-self.zeta*self.Ts
+    
+    
+	def FroNorm(self):
+		'''returns Frobenius Norm'''
+		fn= pb.sqrt(pb.trace(self.A.T*self.A))
+		return fn
+
+
+
+	def gen_ssmodel(self):
+
+
+		#calculate U
+		#~~~~~~~~~~~
+
+		if not(hasattr(self,'U')):
+
+			t0=time.time()
+			self.U_Index=[]
+			U=pb.empty((self.nx,self.nx),dtype=object) 
+			U_T=pb.empty((self.nx,self.nx),dtype=object)
+			for i in range(self.nx):				
+				for j in range(self.nx):
+					u_temp=pb.vectorize(self.field.Mu[j,0].conv)(self.kernel.Lambda) 
+					U[i,j]=pb.dot(u_temp.T,self.field.Mu[i,0]).astype(float) 
+					U_T[j,i]=U[i,j].T
+
+					if U[i,j].any():
+						self.U_Index.append((i,j))	
+
+			self.U=U
+			self.U_T=U_T
+			print 'Elapsed time in seconds to calculate U is', time.time()-t0
+
+		#calculate the inverse of inner product of field basis functions
+		if not(hasattr(self,'Lambda_x_blocks_inverse')):
+			t0=time.time()
[…]

### 2012-08-22 Multiresolution_framework/src/NF.py

@@ -1,0 +1,212 @@
+#Author Parham Aram
+#Date 12-10-2011
+"""
+This module provides the full neural field class, which describes a linear
+integro-difference equation model and methods to simulate
+the model
+"""
+
+#Standard library imports
+from __future__ import division
+import pylab as pb
+import numpy as np
+import time
+import os
+from scipy import signal
+import scipy as sp
+
+#My modules
+from BsplineBases import *
+
+
+class NF():
+
+	"""class defining full neural model.
+
+	Arguments
+	----------
+	kernel: 
+			connectivity kernel.
+
+	sensor_kernel:
+
+			output kernel, governs the sensor pick-up geometry
+		
+	obs_locns: ndarray
+				sensors locations
+
+	eta : B-spline function
+				covariance function of the field disturbance
+	eta_weight: float
+				amplitude of the field disturbance covariance function
+
+	Sigma_epsilon: ndarray
+				observation noise covariance
+
+	Ts: float
+				sampling step
+
+
+	zeta: float
+				inverse synaptic time constant
+
+
+	simulation_space: ndarray
+				spatiel field
+
+	spacestep: float
+			spatial step size for descritization 
+
+
+	
+	Attributes
+	----------
+	ny: int
+		number of sensors
+
+	xi: float
+		time constant parameter
+
+	gen_ssmodel:
+		generate the full neural field model
+
+	simulate:
+		simulate the full neural field model
+	"""
+
+
+
+	def __init__(self,kernel,sensor_kernel,obs_locns,eta,eta_weight,Sigma_epsilon,Ts,zeta,varsigma,simulation_space,sensorspace,spacestep):
+
+		self.kernel = kernel
+		self.sensor_kernel=sensor_kernel
+		self.obs_locns=obs_locns
+		self.eta=eta
+		self.eta_weight=eta_weight
+		self.Sigma_epsilon=Sigma_epsilon
+		self.Ts=Ts
+		self.zeta=zeta
+		self.varsigma=varsigma
+		self.simulation_space=simulation_space
+		self.sensorspace=sensorspace
+		self.spacestep=spacestep
+		self.ny=len(self.obs_locns)
+		self.ntheta=len(self.kernel.Lambda)
+		self.xi=1-self.zeta*self.Ts
+
+
+	def gen_ssmodel(self):
+
+
[…]

### 2012-08-22 Multiresolution_framework/src/SKF.py

@@ -1,0 +1,249 @@
+#Author Parham Aram
+#Date 12-10-2011
+# built-ins
+from __future__ import division
+import numpy as np
+import pylab as pb
+import scipy as sp
+import copy
+
+
+class SKF():
+
+
+	''' class defining the RTS smoother.
+        
+        
+        
+        
+		Arguments:
+		----------
+		x0: ndarray
+			initial state
+		P0: ndarray
+			initial state covariance matrix
+		A: ndarray
+			transition matrix
+		C: ndarray
+			observation matrix
+
+		Sigma_e: ndarray
+			process noise covariance matrix
+
+		Sigma_epsilon: ndarray
+			observation noise covariance matrix
+
+		
+'''
+
+
+
+
+	def __init__(self,x0,P0,A,C,Sigma_e,Sigma_epsilon):
+		
+		assert 	type(x0) is np.ndarray, 'Initial state must be ndarray'
+		assert 	type(P0) is np.ndarray, 'Initial state covariance matrix must be ndarray'
+		assert 	type(A) is np.ndarray, 'Transition matrix must be ndarray'
+		assert 	type(C) is np.ndarray, 'Observation matrix must be ndarray'
+		assert 	type(Sigma_e) is np.ndarray, 'process noise covariance matrix must be ndarray'
+		assert 	type(Sigma_epsilon) is np.ndarray, 'observation noise covariance matrix must be ndarray'
+
+		self.x0=x0
+		self.P0=P0
+		self.A=A
+		self.C=C
+		self.Sigma_e=Sigma_e
+		self.Sigma_epsilon=Sigma_epsilon
+		self.ny,self.nx=self.C.shape
+		
+
+
+
+	def kfilter(self,Y):
+		
+		
+		"""Standard Kalman Filter
+		
+		Arguments
+		----------
+		Y : list of ndarray
+			A list of observation vectors
+			
+		Returns
+		----------	
+		X : list of ndarray
+			A list of state estimates
+		P : list of ndarray
+			A list of state covariance matrices
+
+		"""
+		
+		
+		# prediction
+        
+		def Kpred(A,P,Sigma_e,x):
+					
+			if (np.rank(A)!=2 or type(self.A)!=np.ndarray):raise TypeError('A should be rank two array')
[…]

### 2012-08-22 Multiresolution_framework/src/spline.py

@@ -1,0 +1,101 @@
+#Author Parham Aram
+#Date 12-10-2011
+# calculate spline order 8 and 12 required to compute convolution and inner product of B-spline scaling and wavelet functions
+from __future__ import division
+import numpy as np
+import pylab as pb
+
+class spline8():
+	"""BSpline order 8  to evaluate convolution of two bases"""
+	def __init__(self,j,k):
+		self.j=j
+		self.k=k
+
+	def __repr__(self):
+		return 'Bspline 8;'+'j='+str(self.j) +',k='+str(self.k) 
+
+	def Supp(self):
+		'''Compute Support of the basis function'''
+		return [(0+self.k)*2**-self.j,(8+self.k)*2**-self.j]
+
+	def evaluate_at_real(self,u):			
+		x=2**self.j*u-self.k
+		if u>= (0+self.k)*2**-self.j and u< (1+self.k)*2**-self.j: output=x**7
+		elif u>= (1+self.k)*2**-self.j and u< (2+self.k)*2**-self.j: output=8-56*x+168*x**2-280*x**3+280*x**4-168*x**5+56*x**6-7*x**7
+		elif u>= (2+self.k)*2**-self.j and u< (3+self.k)*2**-self.j: output=-3576+12488*x-18648*x**2+15400*x**3-7560*x**4+2184*x**5-336*x**6+21*x**7
+		elif u>= (3+self.k)*2**-self.j and u< (4+self.k)*2**-self.j: output=118896-273280*x+267120*x**2-143360*x**3+45360*x**4-8400*x**5+840*x**6-35*x**7
+		elif u>= (4+self.k)*2**-self.j and u< (5+self.k)*2**-self.j: output=-1027984+1733760*x-1238160*x**2+483840*x**3-111440*x**4+15120*x**5-1120*x**6+35*x**7
+		elif u>= (5+self.k)*2**-self.j and u< (6+self.k)*2**-self.j: output=3347016-4391240*x+2436840*x**2-741160*x**3+133560*x**4-14280*x**5+840*x**6-21*x**7
+		elif u>= (6+self.k)*2**-self.j and u< (7+self.k)*2**-self.j: output=-4491192+4753336*x-2135448*x**2+528920*x**3-78120*x**4+6888*x**5-336*x**6+7*x**7
+		elif u>= (7+self.k)*2**-self.j and u<= (8+self.k)*2**-self.j: output=-(-8+x)**7
+		else: output=0
[…]

### 2012-08-22 Multiresolution_framework/ltx/response_to_reviews.tex
minor and last correction

@@
 (2011), two  n-dimensional Gaussians are considered, while here the inner product of two B-spline functions is calculated.
-We have no objections to removing Appendix C.
+We have no objections to removing Appendix C (now Appendix D).
 However, as stated above, we think that it would be informative for the broad audience of NeuroImage to include the model-specific derivations and some of the well-known formulations of the EM algorithm, since it draws on a wide range of literature.}
@@
 
-	\item The comments about model complexity and parsimony on p.13 are somehow vague as these quantities are undefined.
+	\item The comments about model complexity and parsimony on p.13 (now p.12) are somehow vague as these quantities are undefined.
 
@@
 
-		\item The comments on large scale networks and delays made on p.20 look irrelevant to the present framework.
+		\item The comments on large scale networks and delays made on p.20 (now p.21) look irrelevant to the present framework.
 

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
minor edits
general edits
cleaning up the manuscript
minor and last correction

@@
  % \hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}
- \newcommand{\dean}[1]{\textcolor{green}{#1}}
- \newcommand{\parham}[1]{\textcolor{blue}{#1}}
- \newcommand{\ken}[1]{\textcolor{red}{#1}}
 
@@
 
-% To demonstrate the MRAIDE estimation framework we shall consider the parameters to be static and we shall also assume that the relationship between the mean membrane potential and the mean firing rate is predominantly linear.
-Note that there is a difference between forward and inverse modeling when making these assumptions.
-For example, by using a linear activation function in the estimator we are not assuming that there is necessarily a linear relationship between the membrane voltage and firing rate, but that the statistics of the neural masses fall within a linear operating region over the estimation time period.
-The major benefit of modeling the relationship between the mean membrane potential and firing rate is the ability to apply the EM algorithm.
-The loss in model accuracy may be offset estimation accuracy.
-
-% The simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data.
-The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.
-
 Nevertheless, when describing a system, a choice needs to be made regarding the complexity of the mathematical description to be adopted.
 Such a choice is usually based on the principle of parsimony \citep{burnham2002}, that is; choosing the simplest model capable of capturing the system behavior of interest.
-Such a choice in favour of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.
+Such a choice in favor of a simpler model has the added advantages of a smaller parameter space and therefore more accurate estimates and computationally efficient methods.
 
@@
 The problem of representing a continuous field with a finite number of states is solved by the basis function decomposition.
-The basis structure (i.e., non-redundant versus a (tight) frame representation) is a requirement for the multi-resolution framework.
 An alternative to using the B-spline wavelets are Gaussian basis functions, which were adopted by \cite{Freestone2011} to decompose the field and connectivity kernel.

### 2012-08-23 Multiresolution_framework/ltx/ResubmissionLetter.tex
Revised version submitted to NeuroImage

--- 2012-06-17 Multiresolution_framework/ltx/SubmissionLetter.tex
@@
 
-% \emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}
-
-I am writing to seek publication of our research article titled `Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model' in Neuroimage.
-
-The novel aspects of this paper include:
-\begin{itemize}
-	\item a multi-resolution model-based, data-driven estimator of continuum neural field parameters ;
-	\item simultaneous representation of both the macroscopic and microscopic dynamics of the system ;
-	\item a derivation of an algorithm for estimating intracortical connectivity with an arbitrary shape using the Amari type neural field equations.
-\end{itemize}
+    We thank the reviewers for their encouraging comments and their contribution to improving this paper.
+Please find below our responses to the reviewers questions and suggestions regarding the manuscript.
+\\
 
